### 2019-10-31 tex/Beff.tex
big commit

Baldwin (1977) was the first to discover an anti- correlation between the equivalent width (EW) of the \civ $\lambda$1549 emission line and its nearby continuum luminosity in the QSO rest frame (i.e. the Baldwin effect; see a review by Shields 2007).

Explains include:
\begin{itemize}

\item One promising interpretation is the softening of the spectral energy distribution (SED) for increasing luminosity, which lowers the ion (e.g. Netzer et al. 1992; Dietrich et al. 2002).

\item For the Palomar–Green (PG) sample of QSOs, Baskin \& Laor (2004) have found a strong correlation between the \civ EW and $L_{\rm Bol} /L_{\rm} Edd$ , and they have suggested that LBol /LEdd is the primary physical parameter driving the Baldwin effect.

\end{itemize}

### 2019-10-31 tex/CIV_AtomicLineList.tex
big commit

% Atomic Line List version: 2.05b21   Constructed: 2017-11-07 13:41 GMT

% Request: 1

% Wavelength range: 1540 - 1560   Unit: Angstrom   Type: Vacuum
% Radial velocity: 0 km/s
% Wavelength accuracy upper limit: 5%
% Element/Spectrum: C  IV
% Minimum line strength: no restrictions
% Include lines without atomic data: true
% Minimum abundance: no minimum
% Lower level energy range: no restrictions   Unit: cm^-1
% Upper level energy range: no restrictions
% Maximum for principal quantum number n: no restrictions
% Transition types included: all
% Transitions from auto-ionizing levels: included

\begin{table*}
\begin{tabular}{rrr@{ -- }lr@{ -- }lr@{ -- }llrrr@{ -- }rl}
\hline
\multicolumn{1}{c}{$\lambda_{\rm lab}^{\rm obs}$\phantom{0000}} & \multicolumn{1}{c}{$\Delta\lambda_{\rm lab}^{\rm obs}$} & \multicolumn{2}{c}{Configurations} & \multicolumn{2}{c}{Terms} & $J_i$ & $J_k$ & \multicolumn{1}{c}{$A_{\rm ki}$} & \multicolumn{1}{c}{$\log(gf)$} & TP flags & \multicolumn{2}{c}{Levels} & Refs \\
\multicolumn{1}{c}{\AA\phantom{0000}} & \multicolumn{1}{c}{\AA} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{1}{c}{s$^{-1}$} & & & \multicolumn{2}{c}{cm$^{-1}$} & \\
\hline
   1548.203\phantom{0000000} & $2.7-2$ &  $1s^{2}2s$ & $1s^{2}2p$  &       $^{2}{\rm S}$ & $^{2}{\rm P}^\circ$ &  $\frac{1}{2}$ & $\frac{3}{2}$  & $2.65+8$ & $ -0.4198$ &     8 &      $0.00$ &  $64591.00$ & 045 \\
   1550.777\phantom{0000000} & $2.7-2$ &  $1s^{2}2s$ & $1s^{2}2p$  &       $^{2}{\rm S}$ & $^{2}{\rm P}^\circ$ &  $\frac{1}{2}$ & $\frac{1}{2}$  & $2.63+8$ & $ -0.7217$ &     8 &      $0.00$ &  $64483.80$ & 045 \\
\hline
\end{tabular}
\end{table*}

\subsection{Carbon IV}
Table~\ref{tab:civ_configs} from 
Atomic Line List version: 2.05b21  
%%Version 2.05b21 of the line list was created: Nov 7, 2017.
\citep{Tunklev1997} \\

\citep[NIST; ][]{Reader2012AAS, Kramida2018}\\

%Wavelength range: 0 - inf   Unit: Angstrom   Type: Vacuum \\
%Radial velocity: 0 km/s\\
%Element/Spectrum: C  IV  \\
%
%-LAB-WAVL-ANG-VAC-|-SPC-|TT|-TERM--|-J\_i-J\_k-|-LVL-EN--CM-1--|-REF---| \\
 % 1548.203         C IV E1  2S-2Po 1/2 - 3/2 0.00 - 64591.00 045 \\
 % 1550.777         C IV E1  2S-2Po 1/2 - 1/2 0.00 - 64483.80 045 \\
%
%  gk*Aki weighted average wavelength:    1549.06    \\
%

\href{https://physics.nist.gov/cgi-bin/ASD/lines1.pl?spectra=C+IV&limits_type=0&low_w=&upp_w=&unit=1&submit=Retrieve+Data&de=0&format=0&line_out=0&en_unit=0&output=0&bibrefs=1&page_size=15&show_obs_wl=1&show_calc_wl=1&unc_out=1&order_out=0&max_low_enrg=&show_av=2&max_upp_enrg=&tsb_value=0&min_str=&A_out=0&intens_out=on&max_str=&allowed_out=1&forbid_out=1&min_accur=&min_intens=&conf_out=on&term_out=on&enrg_out=on&J_out=on}{NIST Atomic Spectra Database Lines Data; C IV: 228 Lines of Data Found}. \\

\href{https://physics.nist.gov/cgi-bin/ASD/energy1.pl?encodedlist=XXT2&de=0&spectrum=C+IV&submit=Retrieve+Data&units=0&format=0&output=0&page_size=15&multiplet_ordered=0&conf_out=on&term_out=on&level_out=on&unc_out=1&j_out=on&lande_out=on&perc_out=on&biblio=on&temp=}{C IV   91 Levels Found
Z = 6, Li isoelectronic sequence}. \\

%%
Kramida, A., Ralchenko, Yu., Reader, J., and NIST ASD Team (2018). NIST Atomic Spectra Database (ver. 5.6.1), [Online]. Available: https://physics.nist.gov/asd [2019, March 22]. National Institute of Standards and Technology, Gaithersburg, MD. DOI: https://doi.org/10.18434/T4W30F

%% 
%% http://www-personal.umich.edu/~cowley/ionen.htm
%% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)

%%\newpage
%%\input{CIV_AtomicLineList_full}
%%\newpage

%%\newpage
%%\input{CIV_AtomicLineList_mid}
%%\newpage

%%\newpage
%%\input{CIV_AtomicLineList}
%\newpage

\begin{table*}
\begin{tabular}{rrr@{ -- }lr@{ -- }lr@{ -- }llrrr@{ -- }rl}
\hline
\multicolumn{1}{c}{$\lambda_{\rm lab}^{\rm obs}$} & \multicolumn{1}{c}{$\Delta\lambda_{\rm lab}^{\rm obs}$} & \multicolumn{2}{c}{Configurations} & \multicolumn{2}{c}{Terms} & $J_i$ & $J_k$ & \multicolumn{1}{c}{$A_{\rm ki}$} & \multicolumn{1}{c}{$\log(gf)$} & TP flags & \multicolumn{2}{c}{Levels}  \\
\multicolumn{1}{c}{\AA } & \multicolumn{1}{c}{\AA} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{1}{c}{s$^{-1}$} & & & \multicolumn{2}{c}{cm$^{-1}$} & \\
\hline
   1548.203  & $2.7-2$ &  $1s^{2}2s$ & $1s^{2}2p$  &       $^{2}{\rm S}$ & $^{2}{\rm P}^\circ$ &  $\frac{1}{2}$ & $\frac{3}{2}$  & $2.65+8$ & $ -0.4198$ &     8 &      $0.00$ &  $64591.00$  \\
   1550.777  & $2.7-2$ &  $1s^{2}2s$ & $1s^{2}2p$  &       $^{2}{\rm S}$ & $^{2}{\rm P}^\circ$ &  $\frac{1}{2}$ & $\frac{1}{2}$  & $2.63+8$ & $ -0.7217$ &     8 &      $0.00$ &  $64483.80$  \\
\hline
\end{tabular}
\label{tab:civ_configs}
\end{table*}

### 2019-10-31 correspondence/J1638p2827_v1pnt0.py

@@ -1,0 +1,264 @@
+'''
+12h05m44.7s +34d22m52.4s
+'''
+
+import numpy as np
+import seaborn as sns
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+#import pylustrator
+#pylustrator.start()
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1638+2827/'
+
+##  Light Curve
+infile = 'NEOWISER-L1b_J1638+2827.dat'
+NEOWISER = ascii.read(path+infile)
+NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
+NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
+infile = 'NEOWISER-L1b_J1638+2827_averaged.dat'
+NEOWISER_aver = ascii.read(path+infile)
+NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
+NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
+
+##  Spectra
+infile   = 'LRIS_J1638p2827_b_58583.dat'
+LRIS_b  = ascii.read(path+infile)
+infile   = 'LRIS_J1638p2827_r_58583.dat'
+LRIS_r  = ascii.read(path+infile)
+
+LRIS_b_wavelength = LRIS_b['wavelength']
+LRIS_r_wavelength = LRIS_r['wavelength']
+
+## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
+## http://www.stsci.edu/~strolger/docs/UNITS.txt
+## 
+## [Y erg/cm^2/s/Hz]            = 1000 * [X W/m^2/Hz]
+## [Y erg/cm^2/s/A]             = 2.99792458E+21 * [X1 W/m^2/Hz] / [X2 A]^2
+## / 1e-17 to put into 'regular' SDSS flux units 
[…]

### 2019-10-31 correspondence/J2228p2201_v1pnt0.py

@@ -1,0 +1,265 @@
+'''
+12h05m44.7s +34d22m52.4s
+'''
+
+import numpy as np
+import seaborn as sns
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+#import pylustrator
+#pylustrator.start()
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J2228+2201/'
+
+##  Light Curve
+infile = 'NEOWISER-L1b_J2228+2201.dat'
+NEOWISER = ascii.read(path+infile)
+NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
+NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
+infile = 'NEOWISER-L1b_J2228+2201_averaged.dat'
+NEOWISER_aver = ascii.read(path+infile)
+NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
+NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
+
+##  Spectra
+infile   = 'DBSP_J2228p2201_b_56893.dat'
+DBSP_b  = ascii.read(path+infile)
+infile   = 'DBSP_J2228p2201_r_56893.dat'
+DBSP_r  = ascii.read(path+infile)
+
+DBSP_b_wavelength = DBSP_b['wavelength']
+DBSP_r_wavelength = DBSP_r['wavelength']
+
+## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
+## http://www.stsci.edu/~strolger/docs/UNITS.txt
+## 
+## [Y erg/cm^2/s/Hz]            = 1000 * [X W/m^2/Hz]
+## [Y erg/cm^2/s/A]             = 2.99792458E+21 * [X1 W/m^2/Hz] / [X2 A]^2
+## / 1e-17 to put into 'regular' SDSS flux units 
[…]

### 2019-10-31 data/CLQ_line_measurements/LineStrengths_fromSDSS.py

@@ -1,0 +1,37 @@
+''' 
+Super simple program to take in e.g. (emission, line) fluxes, that
+is the Flux density in units of e.g W/m2 or erg/s/cm2 (dimensions of M
+T−^-3) and convert, using a cosmological Luminosity Distance to just
+e.g. line luminosity
+ 
+https://en.wikipedia.org/wiki/Luminosity
+http://www.astro.ucla.edu/~wright/cosmo_02.htm#DL
+'''
+import numpy as np
+from astropy.cosmology import FlatLambdaCDM
+
+
+## Setting up the cosmology
+cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)
+
+print()
+print('Setting up the cosmology')
+print(cosmo)
+print()
+
+lineFlux = float(input ("Enter line flux, [units of 10-17 erg/cm2/s] :  "))
+redshift = float(input ("Enter redshift                              :  "))
+print()
+
+## https://docs.astropy.org/en/stable/cosmology/
+DLum = cosmo.luminosity_distance(redshift)
+
+## Converting (Mega)parsecs to centimeters
+Mpc_to_cm = 3.08567782e18 * 1e6
+
+## Lum = 4.pi.R^2.flux
+lineLum = (((DLum.value * Mpc_to_cm)**2) * (lineFlux * 1e-17) * (4*np.pi)) / 1e42
+    
+print()
+print('The Line Luminosity, in units of 10^42 erg/s is:    ', lineLum)
+print()

### 2019-10-31 data/NEOWISER/average_NEOWISE_lightcurves.py

@@ -1,0 +1,129 @@
+#! /usr/bin/env python
+#------------------------------------------------------------------------------
+# $Id: average_NEOWISE_lightcurves.py 11588 2017-02-12 21:38:25Z NicholasCross $
+"""
+   @author: N.J.G.. Cross
+   @org:    WFAU, IfA, University of Edinburgh
+
+   Usage:: 
+"""
+#------------------------------------------------------------------------------
+from __future__      import division, print_function
+from   operator      import attrgetter, itemgetter
+from   itertools     import groupby
+
+import math
+import os
+import sys
+import numpy
+from astropy.io      import fits, ascii
+from astropy.table   import Table
+
+
+def getMjdRanges(mjdData):
+    """ Looks for groups of data separated by about 6 months, over a few days
+    """
+    startMjd=mjdData[0]
+    mjdGroupList=[]
+    mjdGroup=[]
+    for mjd in mjdData:
+        if mjd<startMjd+20.:
+            mjdGroup.append(mjd)
+        elif mjd>startMjd+130.:
+            startMjd=mjd
+            # calc stats
+            minMjd=min(mjdGroup)
+            maxMjd=max(mjdGroup)
+            meanMjd=numpy.mean(mjdGroup)
+            mjdGroupList.append((minMjd,meanMjd,maxMjd,len(mjdGroup)))
+            mjdGroup=[mjd]
+        else:
+            print("mjd does not fall in group, nor start new group: ",mjd,startMjd)
+    minMjd=min(mjdGroup)
+    maxMjd=max(mjdGroup)
+    meanMjd=numpy.mean(mjdGroup)
+    mjdGroupList.append((minMjd,meanMjd,maxMjd,len(mjdGroup)))
+    return mjdGroupList
+    
+def getAveragePhot(data,mjdRangeMask,band,isVerbose=False):
+    """ Uses weighted mean to average photometry
+    """
+    default_value = numpy.NaN
+
+    mpro=data['w%smpro' % band][mjdRangeMask]
+    sigma_mpro=data['w%ssigmpro' % band][mjdRangeMask]
+    if isVerbose:
+        print("MPRO: ",band,[(mpro,sigma_mpro[ii]) for ii,mpro in enumerate(mpro)])
+    if mpro.size>=2:
[…]

### 2019-10-31 data/QSFIT/QSFit_fitting.py

@@ -1,0 +1,151 @@
+'''
+The beginning of some code that takes the outputs from QSFit
+e.g. the QSFIT.log file, and then overplots the model fit 
+on top of the data spectrum. 
+
+This would be very very much in the same vein as Figure 6 of
+Calderone et al., 2017, MNRAS, 472, 4051 
+
+Useful links/URLs::
+  https://stackoverflow.com/questions/10582795/finding-the-full-width-half-maximum-of-a-peak
+'''
+
+
+import numpy as np
+import pylab as pl
+import scipy.optimize as opt
+
+from scipy.interpolate import UnivariateSpline
+
+
+spectrum_name = 'spec-6118-56189-0720'
+
+infile_data  = spectrum_name+'.fits'
+infile_model = spectrum_name+'_QSFIT.log'
+
+
+def make_norm_dist(x, mean, sd):
+    return 1.0/(sd*np.sqrt(2*np.pi))*np.exp(-(x - mean)**2/(2*sd**2))
+
+x = np.linspace(10, 110, 1000)
+green = make_norm_dist(x, 50, 10)
+pink = make_norm_dist(x, 60, 10)
+
+blue = green + pink   
+
+# create a spline of x and blue-np.max(blue)/2 
+spline = UnivariateSpline(x, blue-np.max(blue)/2, s=0)
+r1, r2 = spline.roots() # find the roots
+
+pl.plot(x, blue)
+pl.axvspan(r1, r2, facecolor='g', alpha=0.5)
+pl.show()
+
+
+def FWHM(X,Y):
+    half_max = max(Y) / 2.
+    
+    #find when function crosses line half_max (when sign of diff flips)
+    #take the 'derivative' of signum(half_max - Y[])
+    d = sign(half_max - array(Y[0:-1])) - sign(half_max - array(Y[1:]))
+    
+    #plot(X[0:len(d)],d) #if you are interested
+    #find the left and right most indexes
+    left_idx = find(d > 0)[0]
+    right_idx = find(d < 0)[-1]
+    
+    #return the difference (full width)
+    return X[right_idx] - X[left_idx]
+
+
+def gauss(x, p): # p[0]==mean, p[1]==stdev
[…]

### 2019-10-31 data/QSFIT/baby_plot.py

@@ -1,0 +1,18 @@
+#!/usr/bin/env python
+
+from astropy.io import ascii
+import matplotlib.pyplot as plt 
+
+data_first  = ascii.read("J1205p3422_58538.dat")
+data_second = ascii.read("J1205p3422_58693.dat")
+
+plt.plot((data_first['wavelength']/(1+2.071)),  data_first['flux'], color='r')
+plt.plot((data_second['wavelength']/(1+2.071)), data_second['flux'],  color='k')
+plt.ylim((-10,50))
+
+#plt.savefig("test.png")
+plt.ylim((-1,50))
+plt.show()  
+
+
+

### 2019-10-31 data/QSFIT/prep_DBSP_LRIS_spectra.py

@@ -1,0 +1,83 @@
+'''
+Just a wee script that takes e.g. the DBSP and LRIS data 
+from the directories above and converts things into 
+columns of wavelength, flux and flux_error with 
+the flux units being 10^-17 erg s^-1 cm^-2 Ang^-1. 
+https://qsfit.inaf.it/cat_1.30/onlinefit.php
+'''
+
+import numpy as np
+from astropy.io    import ascii
+from astropy.table import Table, vstack
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/'
+
+
+##      S P E C T R A
+##
+##  J1205+3422
+#object_name = 'J1205+3422/'
+#infile = 'DBSP_J1205p3422_b_58538.dat'
+#infile = 'DBSP_J1205p3422_b_58693.dat'
+#blue   = ascii.read(path+object_name+infile)
+#infile = 'DBSP_J1205p3422_r_58538.dat'
+#infile = 'DBSP_J1205p3422_r_58693.dat'
+#red    = ascii.read(path+object_name+infile)
+##
+##  J1638+2827
+#object_name = 'J1638+2827/'
+#infile = 'LRIS_J1638p2827_b_58583.dat'
+#blue   = ascii.read(path+object_name+infile)
+#infile = 'LRIS_J1638p2827_r_58583.dat'
+#red    = ascii.read(path+object_name+infile)
+##
+##  J2228+3422
+object_name = 'J2228+2201/'
+infile = 'DBSP_J2228p2201_b_58693.dat'
+blue   = ascii.read(path+object_name+infile)
+infile = 'DBSP_J2228p2201_r_58693.dat'
+red    = ascii.read(path+object_name+infile)
+
+
+print()
+print('Read-in', object_name+infile)
+print()
+
+
+wavelength_blue = blue['wavelength']
+wavelength_red  =  red['wavelength']
+
+
+## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
+## http://www.stsci.edu/~strolger/docs/UNITS.txt
+## 
+## [Y erg/cm^2/s/Hz]            = 1000 * [X W/m^2/Hz]
+## [Y erg/cm^2/s/A]             = 2.99792458E+21 * [X1 W/m^2/Hz] / [X2 A]^2
+## / 1e-17 to put into 'regular' SDSS flux units 
[…]

### 2019-10-31 data/QSO_CIV_catalogs/matchingHam17toKoz17.py

@@ -1,0 +1,59 @@
+
+import numpy  as np 
+import pandas as pd
+from   pandas import DataFrame
+from astropy.io    import fits
+from astropy.io    import ascii
+from astropy.table import Table
+
+
+##  Hamann et al. (2017) ERQ BOSS DR12 catalog
+path       = '/cos_pc19a_npr/data/ERQs/Hamann2017_CIVcatalog/'
+filename   = 'C4N5REWs_DR12v11_MNRAS.fits'
+infile     = path+filename
+data_full  = fits.open(infile)
+Ham17_full = data_full[1].data
+
+#with fits.open(infile) as data:
+#    df_Ham17 = pd.DataFrame(data[0].data)
+
+## knocking out a couple of objects with bad REW values 
+#Ham17 = Ham17_full[np.where( (Ham17['rew'] >0.) & (Ham17['rew'] < 10000.)  )]
+Ham17 = Ham17_full
+
+
+##  Kozłowski_2017_ApJS_228_9.  BOSS DR12 "Value Added" catalog
+path       = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/QSO_CIV_catalogs/'
+filename   = 'SDSS-DR12Q-BH_extra.fits'
+infile     = path+filename
+data_full  = fits.open(infile)
+Koz17_full = data_full[1].data
+Koz17      = Koz17_full
+
+
+## astropy Table to pandas DataFrame #2804
+## https://github.com/astropy/astropy/issues/2804
+Ham17_table = Table(Ham17)
+Ham17_df    = DataFrame(np.array(Ham17_table))
+print('len(Ham17_df)', len(Ham17_df))
+
+
+Koz17_table = Table(Koz17)
+
+## Have to remove this '5 value' columns in order for the
+## DataFrame swith-aroo to work..
+Koz17_table.remove_column('PSFFLUX')
+Koz17_table.remove_column('IVAR_PSFFLUX')
+Koz17_table.remove_column('PSFMAG')
+Koz17_table.remove_column('ERR_PSFMAG')
+
+Koz17_df    = DataFrame(np.array(Koz17_table))
+print('len(Koz17_df)', len(Koz17_df))
+
+## COlumns names are case senstive!
+Koz17_df.rename(columns={'SDSS_NAME':'sdss_name'}, inplace=True)              
+
+## Testing on a wee bit of the DataFrame...
[…]

### 2019-10-31 data/QSO_CIV_catalogs/matchingHam17toKoz17_v0.py

@@ -1,0 +1,54 @@
+
+import numpy as np 
+from astropy.io import fits
+from astropy.io import ascii
+
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines  as mlines
+
+
+##  Hamann et al. (2017) ERQ BOSS DR12 catalog
+path       = '/cos_pc19a_npr/data/ERQs/Hamann2017_CIVcatalog/'
+filename   = 'C4N5REWs_DR12v11_MNRAS.fits'
+infile     = path+filename
+data_full  = fits.open(infile)
+Ham17_full = data_full[1].data
+
+## knocking out a couple of objects with bad REW values 
+#Ham17 = Ham17_full[np.where( (Ham17['rew'] >0.) & (Ham17['rew'] < 10000.)  )]
+Ham17 = Ham17_full
+
+
+##  Kozłowski_2017_ApJS_228_9.  BOSS DR12 "Value Added" catalog
+path       = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/QSO_CIV_catalogs/'
+filename   = 'SDSS-DR12Q-BH_extra.fits'
+infile     = path+filename
+data_full  = fits.open(infile)
+Koz17_full = data_full[1].data
+
+Koz17      = Koz17_full
+
+
+
+file1 = open("temp.txt","w+") 
+
+    
+#for ii in range(len(Koz17)):
+for ii in range(100):
+    print(ii)
+
+    name        = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['SDSS_NAME']
+    REW         = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['rew']
+    bal_flag_vi = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['bal_flag_vi']
+    f1450       = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['f1450']
+    
+    if (len(name) > 0 and  bal_flag_vi <1) :
+        #print(ii, Koz17['SDSS_NAME'][ii], name, REW, f1450)
+        file1.write(str(ii)+str(Koz17['SDSS_NAME'][ii])+str(we_name)+str(we_rew))
[…]

### 2019-10-31 plots/Lags_vs_IPs/Lags_vs_IPs.py

@@ -1,0 +1,74 @@
+
+import numpy   as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+
+from matplotlib.patches import Rectangle
+from matplotlib         import colors as mcolors
+
+from astropy.io import ascii
+from astropy.io import fits
+
+
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/Lags'
+
+## Reading in the data
+data_NGC5548 = ascii.read(path+infile)
+
+
+data_Mrk110 = ascii.read(path+infile)
+
+
+
+
+## Setting up the plot
+fig, ax = plt.subplots(figsize=(5, 3), dpi=80, facecolor='w', edgecolor='k')
+
+## Adjusting the Whitespace for the plots
+left   = 0.18   # the left side of the subplots of the figure
+right  = 0.98   # the right side of the subplots of the figure
+bottom = 0.18   # the bottom of the subplots of the figure
+top    = 0.96   # the top of the subplots of the figure
+wspace = 0.26   # the amount of width reserved for blank space between subplots
+hspace = 0.06   # the amount of height reserved for white space between subplots
+plt.subplots_adjust(left=left, bottom=bottom, right=right, top=top, wspace=wspace, hspace=hspace)
+ 
+## Some NPR defaults
+alpha           = 1.0
+fontsize        = 16
+labelsize       = fontsize
+tickwidth       = 2.0
+linewidth       = 2.4
+tickwidth       = 2.0
+ticklength      = 6.0
+ticklabelsize   = labelsize
+majorticklength = 12
+minorticklength = 6
+
+## Some general links/tips on stylings::
+##
+## https://matplotlib.org/3.1.0/tutorials/introductory/customizing.html
+## https://stackoverflow.com/questions/25451294/best-way-to-display-seaborn-matplotlib-plots-with-a-dark-ipython-notebook-profil
+## https://smashingtheory.blogspot.com/search/label/matplotlib
+## https://earthobservatory.nasa.gov/blogs/elegantfigures/2013/08/05/subtleties-of-color-part-1-of-6/
+
+
+## Axes limits
+xmin =  4.90
+xmax =  7.65
+ymin =  0.0
+ymax = 38.0
+ax.set_xlim([xmin,xmax])
+ax.set_ylim([ymin, ymax])
+
+## Axes labels
+ax.set_xlabel(r'$z$, redshift')
+ax.set_ylabel(r'No. of objects')
+
+## Axes style
[…]

### 2019-10-31 plots/Wilhite/Wilhite_2006_Fig2.py

@@ -1,0 +1,106 @@
+'''
+"Baby" python code that will reproduce, e.g. Figure 2 of Wilhite et
+al. 2006, ApJ, 641:78
+'''
+
+import numpy   as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+import matplotlib.lines  as mlines
+
+from matplotlib          import colors as mcolors
+from matplotlib.patches  import Rectangle
+from matplotlib.gridspec import GridSpec
+
+from astropy.io import ascii
+from astropy.io import fits
+
+## Reading in the data from Wilhite et al., 2006, ApJ, 641 78
+Wilhite_path = '/cos_pc19a_npr/data/SDSS/Wilhite_CIV/'
+Wilhite_file = 'Wilhite_2006_combined_Tables.dat'
+Wilhite_input = Wilhite_path+Wilhite_file
+
+data = ascii.read(Wilhite_input) 
+
+## Set up the Line flux ratio variable...
+flux_ratio = data['HiSNRlineFlux']/data['LoSNRlineFlux']
+## and the Line Width ratio variable...
+LineWidth_ratio =  data['HiSNRlineWidth']/data['LoSNRlineWidth']
+
+
+## J1638+2827
+J1638_path  = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/CLQ_line_measurements/'
+J1638_file  = 'LineStrength_ratios.dat'
+J1638_input = J1638_path+J1638_file
+J1638_data  = ascii.read(J1638_input)
+
+
+## Setting up the plot
+fig, ax = plt.subplots(figsize=(7,5), dpi=80, facecolor='w', edgecolor='k')
+
+## Adjusting the Whitespace for the plots
+left   = 0.14   # the left side of the subplots of the figure
+right  = 0.96   # the right side of the subplots of the figure
+bottom = 0.14   # the bottom of the subplots of the figure
+top    = 0.96   # the top of the subplots of the figure
+wspace = 0.26   # the amount of width reserved for blank space between subplots
+hspace = 0.06   # the amount of height reserved for white space between subplots
+plt.subplots_adjust(left=left, bottom=bottom, right=right, top=top, wspace=wspace, hspace=hspace)
+ 
+## Some NPR defaults
+ms              = 10.
+alpha           = 1.0
+fontsize        = 16
+labelsize       = fontsize
+tickwidth       = 2.0
[…]

### 2019-10-31 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py

@@ -1,0 +1,200 @@
+'''
+A ``hexbin'' plot for the SDSS-III BOSS data from the Hamann et al. (2017) catalog and analysis. 
+This initially concentrated on 'just' f1450 converted into Lum_1450.
+However, matching with the Kozłowski (2017) catalog means we can do the Baldwin plot with LBol directly. 
+'''
+
+
+import numpy as np
+from scipy             import stats
+from astropy.io        import fits
+from astropy.io        import ascii
+from astropy.cosmology import FlatLambdaCDM
+
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines  as mlines
+
+## Setting up the cosmology
+cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                         
+
+## Reading in the data
+path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/CLQ_line_measurements/'
+filename  = 'REW_FWHM.dat'
+CLQs      = ascii.read(path+filename)
+
+CLQ_FWHM   = CLQs['FWHM']    / 1000.
+errFWHM    = CLQs['errFWHM'] / 1000.
+CLQ_logREW = np.log10(CLQs['REW'])
+## have to put the x-errors into log-space
+#log_REW_hi = np.log10(CLQs['REW'] np.log10(CLQs['errREW']))
+#log_REW_lo = np.log10(CLQs['REW']-CLQs['errREW'])
+## and then have them as
+#CLQ_asym_xerr = [log_REW_lo, log_REW_hi] 
+log_errREW = np.log10(CLQs['errREW'])
+
+
+##  Hamann et al. (2017) and Kozłowski (2017) merged BOSS DR12 catalog
+path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/QSO_CIV_catalogs/'
+filename  = 'BOSS_Ham17Koz17_DR12Q.fits'
+infile    = path+filename
+data_full = fits.open(infile)
+tdata     = data_full[1].data
+
+## Knocking out a couple of objects with bad REW values;
+## No BALs
+## qflag; quality flag for the C IV fit: 0 = no problems
+## 2.0 < ze < 3.4  to match "Full Sample" in Hamann++17
+## and kick out the LBol
+data = tdata[np.where( (tdata['rew'] > 0.     )     &
[…]

### 2019-10-31 plots/hexbin_plots/Baldwin/Lum_vs_Lum_hexbin.py

@@ -1,0 +1,199 @@
+'''
+A ``hexbin'' plot for the SDSS-III BOSS data from the Hamann et al. (2017) catalog and analysis. 
+This initially concentrated on 'just' f1450 converted into Lum_1450.
+However, matching with the Kozłowski (2017) catalog means we can do the Baldwin plot with LBol directly. 
+'''
+
+
+import numpy as np
+from scipy             import stats
+from astropy.io        import fits
+from astropy.io        import ascii
+from astropy.cosmology import FlatLambdaCDM
+
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines  as mlines
+
+## Setting up the cosmology
+cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                         
+
+
+## Reading in the data
+path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/CLQ_line_measurements/'
+filename  = 'REW_FWHM.dat'
+CLQs      = ascii.read(path+filename)
+
+CLQ_FWHM   = CLQs['FWHM']    / 1000.
+errFWHM    = CLQs['errFWHM'] / 1000.
+CLQ_logREW = np.log10(CLQs['REW'])
+## have to put the x-errors into log-space
+#log_REW_hi = np.log10(CLQs['REW'] np.log10(CLQs['errREW']))
+#log_REW_lo = np.log10(CLQs['REW']-CLQs['errREW'])
+## and then have them as
+#CLQ_asym_xerr = [log_REW_lo, log_REW_hi] 
+log_errREW = np.log10(CLQs['errREW'])
+
+
+##  Hamann et al. (2017) and Kozłowski (2017) merged BOSS DR12 catalog
+path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/QSO_CIV_catalogs/'
+filename  = 'BOSS_Ham17Koz17_DR12Q.fits'
+infile    = path+filename
+data_full = fits.open(infile)
+tdata     = data_full[1].data
+
+## Knocking out a couple of objects with bad REW values;
+## No BALs
+## qflag; quality flag for the C IV fit: 0 = no problems
+## 2.0 < ze < 3.4  to match "Full Sample" in Hamann++17
+## and kick out the LBol
+data = tdata[np.where( (tdata['rew'] > 0.     )     &
[…]

### 2019-10-31 plots/hexbin_plots/REW_FWHM/REW_FWHM_contour.py

@@ -1,0 +1,151 @@
+
+import numpy as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+
+from matplotlib         import colors as mcolors
+from matplotlib.ticker  import MaxNLocator
+from matplotlib.colors  import BoundaryNorm
+from matplotlib.patches import Rectangle
+
+
+from astropy.io import ascii
+from astropy.io import fits
+
+## https://docs.scipy.org/doc/scipy/reference/stats.html
+## 
+from scipy.stats import kde
+
+
+## Reading in the data
+path      = '/cos_pc19a_npr/data/ERQs/Hamann2017_CIVcatalog/'
+filename  = 'C4N5REWs_DR12v11_MNRAS.fits'
+infile    = path+filename
+data_full = fits.open(infile)
+tdata     = data_full[1].data
+
+data = tdata[np.where(tdata['rew'] < 10000.)]
+## Setting up variable names
+REW  = data['rew']        
+FWHM = data['fwhm']
+
+
+data = np.vstack((REW, FWHM)).T                                                                                                                       
+x, y = data.T
+
+
+## Setting up the plot
+#fig, ax = plt.subplots(figsize=(5, 3), dpi=80, facecolor='w', edgecolor='k')
+## Create a figure with 6 plot areas
+fig, axes = plt.subplots(ncols=6, nrows=1, figsize=(21, 5))
+
+
+## Adjusting the Whitespace for the plots
+left   = 0.18   # the left side of the subplots of the figure
+right  = 0.98   # the right side of the subplots of the figure
+bottom = 0.18   # the bottom of the subplots of the figure
+top    = 0.96   # the top of the subplots of the figure
+wspace = 0.26   # the amount of width reserved for blank space between subplots
+hspace = 0.06   # the amount of height reserved for white space between subplots
+plt.subplots_adjust(left=left, bottom=bottom, right=right, top=top, wspace=wspace, hspace=hspace)
+ 
+## Some NPR defaults
+alpha           = 1.0
+fontsize        = 16
+labelsize       = fontsize
+tickwidth       = 2.0
[…]

### 2019-10-31 plots/hexbin_plots/REW_FWHM/REW_FWHM_hexplot.py

@@ -1,0 +1,199 @@
+'''
+A ``hexbin'' plot for the SDSS-III BOSS data from the Hamann et
+al. (2017) catalog and analysis. This code is for rest equivalent
+widths (REWs), and Full width at half maximum (FWHM). 
+'''
+
+import numpy as np 
+from astropy.io import fits
+from astropy.io import ascii
+
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines  as mlines
+
+##
+## READING IN THE DATA
+##
+##  F U L L    B O S S    D R 1 2    catalog
+path      = '/cos_pc19a_npr/data/ERQs/Hamann2017_CIVcatalog/'
+filename  = 'C4N5REWs_DR12v11_MNRAS.fits'
+infile    = path+filename
+data_full = fits.open(infile)
+tdata     = data_full[1].data
+## knocking out a couple of objects with bad REW values 
+data = tdata[np.where( (tdata['rew'] >0.) & (tdata['rew'] < 10000.)  )]
+
+## Setting up variable names
+REW  = data['rew']        
+FWHM = data['fwhm']
+
+## Putting te Equiv. Widths into log and
+## the FWHMs into '000s of kms^-1.
+log_REW = np.log10(REW)
+FWHM    = FWHM/1000.
+
+
+##  T H E    C I V    C L Q    S A M P L E 
+path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/CLQ_line_measurements/'
+filename  = 'REW_FWHM_CIV.dat'
+CLQs      = ascii.read(path+filename)
+
+CLQ_FWHM    = CLQs['FWHM']    / 1000.
+CLQ_errFWHM = CLQs['errFWHM'] / 1000.
+CLQ_REW     = CLQs['REW']
+CLQ_errREW  = CLQs['errREW'] 
+
+CLQ_logREW = np.log10(CLQs['REW'])
+
+## have to put the x-errors into log-space
+#log_REW_hi = np.log10(CLQs['REW'] np.log10(CLQs['errREW']))
+#log_REW_lo = np.log10(CLQs['REW']-CLQs['errREW'])
+## and then have them as
+#CLQ_asym_xerr = [log_REW_lo, log_REW_hi] 
+log_errREW = np.log10(CLQs['errREW'])
+
+
+
+##   S E T T I N G   U P   T H E    P L O T  
+matplotlib.rc('text', usetex=True)
[…]

### 2019-10-31 plots/hexbin_plots/older_py/Baldwin_hexbin_v0.py

@@ -1,0 +1,176 @@
+'''
+A ``hexbin'' plot for the SDSS-III BOSS data from the Hamann et
+al. (2017) catalog and analysis. This code is for rest equivalent
+widths (REWs), and Full width at half maximum (FWHM). 
+'''
+
+import numpy as np 
+from astropy.io        import fits
+from astropy.io        import ascii
+from astropy.cosmology import FlatLambdaCDM
+
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines  as mlines
+
+## Setting up the cosmology
+cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                         
+
+
+## Reading in the data
+path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/CLQ_line_measurements/'
+filename  = 'REW_FWHM.dat'
+CLQs      = ascii.read(path+filename)
+
+CLQ_FWHM   = CLQs['FWHM']    / 1000.
+errFWHM    = CLQs['errFWHM'] / 1000.
+CLQ_logREW = np.log10(CLQs['REW'])
+## have to put the x-errors into log-space
+#log_REW_hi = np.log10(CLQs['REW'] np.log10(CLQs['errREW']))
+#log_REW_lo = np.log10(CLQs['REW']-CLQs['errREW'])
+## and then have them as
+#CLQ_asym_xerr = [log_REW_lo, log_REW_hi] 
+log_errREW = np.log10(CLQs['errREW'])
+
+
+##  Hamann et al. (2017)  BOSS DR12 catalog
+path      = '/cos_pc19a_npr/data/ERQs/Hamann2017_CIVcatalog/'
+filename  = 'C4N5REWs_DR12v11_MNRAS.fits'
+infile    = path+filename
+data_full = fits.open(infile)
+tdata     = data_full[1].data
+
+## Knocking out a couple of objects with bad REW values;
+## No BALs
+## qflag; quality flag for the C IV fit: 0 = no problems
+## 2.0 < ze < 3.4  to match "Full Sample" in Hamann++17
+data = tdata[np.where( (tdata['rew'] > 0.     )     &
+                       (tdata['rew'] < 10000. )     & 
+                       (tdata['bal_flag_vi'] == 0 ) &
[…]

### 2019-10-31 plots/mnras_sizer.py

@@ -1,0 +1,14 @@
+'''
+Username:: danhey
+https://gist.github.com/danhey/56c3737c0e4c14fee768c83e09f3f745
+'''
+
+def mnras_size(fig_width_pt, square=False):
+    inches_per_pt = 1.0/72.00              # Convert pt to inches
+    golden_mean = (np.sqrt(5)-1.0)/2.0     # Most aesthetic ratio
+    fig_width = fig_width_pt*inches_per_pt # Figure width in inches
+    if square:
+        fig_height = fig_width
+    else:
+        fig_height = fig_width*golden_mean
+    return [fig_width,fig_height]

### 2019-10-31 plots/perObject/J1205p3422_landscape_v1pnt0.py

@@ -1,0 +1,354 @@
+'''
+12h05m44.7s +34d22m52.4s
+'''
+
+import numpy as np
+import seaborn as sns
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+#import pylustrator
+#pylustrator.start()
+
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
+
+##    L I G H T    C U R V E
+## CRTS
+infile = 'J120544.67+342252.4_CRTS.dat'
+CRTS   = ascii.read(path+infile)
+## CRTS MJD offset
+CRTS_MJD_offset = 53500
+CRTS_MJD = CRTS['mjd'] + CRTS_MJD_offset
+
+infile = 'J120544.67+342252_ztf_g.dat'
+ZTF_g  = ascii.read(path+infile)
+
+infile = 'J120544.67+342252_ztf_r.dat'
+ZTF_r  = ascii.read(path+infile)
+
+infile = 'NEOWISER-L1b_J1205p3422.dat'
+NEOWISER = ascii.read(path+infile)
+NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
+NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
+infile = 'NEOWISER-L1b_J1205p3422_averaged.dat'
+NEOWISER_aver = ascii.read(path+infile)
+NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
+NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
+
+
+##    S P E C T R A 
+infile   = 'DBSP_J1205p3422_b_58538.dat'
+DBSP_b1  = ascii.read(path+infile)
+infile   = 'DBSP_J1205p3422_r_58538.dat'
+DBSP_r1  = ascii.read(path+infile)
+infile   = 'DBSP_J1205p3422_b_58693.dat'
[…]

### 2019-10-31 plots/perObject/J1205p3422_portrait_v1pnt0.py

@@ -1,0 +1,349 @@
+'''
+12h05m44.7s +34d22m52.4s
+'''
+
+import numpy as np
+import seaborn as sns
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+#import pylustrator
+#pylustrator.start()
+
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
+
+##    L I G H T    C U R V E
+## CRTS
+infile = 'J120544.67+342252.4_CRTS.dat'
+CRTS   = ascii.read(path+infile)
+## CRTS MJD offset
+CRTS_MJD_offset = 53500
+CRTS_MJD = CRTS['mjd'] + CRTS_MJD_offset
+
+infile = 'J120544.67+342252_ztf_g.dat'
+ZTF_g  = ascii.read(path+infile)
+
+infile = 'J120544.67+342252_ztf_r.dat'
+ZTF_r  = ascii.read(path+infile)
+
+
+infile = 'NEOWISER-L1b_J1205p3422.dat'
+NEOWISER = ascii.read(path+infile)
+NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
+NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
+infile = 'NEOWISER-L1b_J1205p3422_averaged.dat'
+NEOWISER_aver = ascii.read(path+infile)
+NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
+NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
+
+##    S P E C T R A 
+infile   = 'DBSP_J1205p3422_b_58538.dat'
+DBSP_b1  = ascii.read(path+infile)
+infile   = 'DBSP_J1205p3422_r_58538.dat'
+DBSP_r1  = ascii.read(path+infile)
+infile   = 'DBSP_J1205p3422_b_58693.dat'
+DBSP_b2  = ascii.read(path+infile)
[…]

### 2019-10-31 plots/perObject/J1638p2827_landscape_v1pnt0.py

@@ -1,0 +1,344 @@
+'''
+       J 1 6 3 8 + 2 8 2 7 
+     
+16h38m52.9s   +28d27m07.7s
+249.720558407 +28.452158884  
+'''
+
+import numpy as np
+import seaborn as sns
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+#import pylustrator
+#pylustrator.start()
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1638+2827/'
+
+##    L I G H T    C U R V E
+## CRTS
+infile = 'J163852.9+282708_CRTS.dat'
+CRTS   = ascii.read(path+infile)
+## CRTS MJD offset
+CRTS_MJD_offset = 53500
+CRTS_MJD = CRTS['mjd'] + CRTS_MJD_offset
+## ZTF
+infile = 'J163852.9+282708_ztf_g.dat'
+ZTF_g  = ascii.read(path+infile)
+infile = 'J163852.9+282708_ztf_r.dat'
+ZTF_r  = ascii.read(path+infile)
+
+## NEOWISE-R
+infile = 'NEOWISER-L1b_J1638+2827.dat'
+NEOWISER = ascii.read(path+infile)
+NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
+NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
+infile = 'NEOWISER-L1b_J1638+2827_averaged.dat'
+NEOWISER_aver = ascii.read(path+infile)
+NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
+NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
+
+
+##    S P E C T R A 
+infile   = 'LRIS_J1638p2827_b_58583.dat'
+LRIS_b  = ascii.read(path+infile)
+infile   = 'LRIS_J1638p2827_r_58583.dat'
+LRIS_r  = ascii.read(path+infile)
+
[…]

### 2019-10-31 plots/perObject/J2228p2201_landscape_v1pnt0.py

@@ -1,0 +1,347 @@
+'''
+      J 2 2 2 8  +  2 2 0 1
+   
+22h28m18.7s +22d01m02.9s
+337.078194  +22.017478 
+'''
+
+import numpy as np
+import seaborn as sns
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+#import pylustrator
+#pylustrator.start()
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J2228+2201/'
+
+##    L I G H T    C U R V E
+## CRTS
+infile = 'J222818.77+220102.6_CRTS.dat'
+CRTS   = ascii.read(path+infile)
+## CRTS MJD offset
+CRTS_MJD_offset = 53500
+CRTS_MJD = CRTS['mjd'] + CRTS_MJD_offset
+## ZTF
+infile = 'J222818+220102_ztf_g.dat'
+ZTF_g  = ascii.read(path+infile)
+infile = 'J222818+220102_ztf_r.dat'
+ZTF_r  = ascii.read(path+infile)
+
+## NEOWISE-R
+infile = 'NEOWISER-L1b_J2228+2201.dat'
+NEOWISER = ascii.read(path+infile)
+NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
+NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
+infile = 'NEOWISER-L1b_J2228+2201_averaged.dat'
+NEOWISER_aver = ascii.read(path+infile)
+NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
+NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
+
+
+##    S P E C T R A 
+infile   = 'DBSP_J2228p2201_b_58693.dat'
+DBSP_b  = ascii.read(path+infile)
+infile   = 'DBSP_J2228p2201_r_58693.dat'
+DBSP_r  = ascii.read(path+infile)
+
[…]

### 2019-10-31 plots/perObject/older_py/J1205p3422.py

@@ -1,0 +1,175 @@
+
+import numpy as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+from astropy.io import ascii
+from astropy.io import fits
+
+import pylustrator
+pylustrator.start()
+
+## Reading in the data
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
+infile = 'crts1205p3422_b.dat'
+crts_b = ascii.read(path+infile)
+infile = 'crts1205p3422_r.dat'
+crts_r = ascii.read(path+infile)
+
+crts_b_wavelength = crts_b['wavelength']
+crts_r_wavelength = crts_r['wavelength']
+
+## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
+## http://www.stsci.edu/~strolger/docs/UNITS.txt
+## 
+## [Y erg/cm^2/s/Hz]            = 1000 * [X W/m^2/Hz]
+## [Y erg/cm^2/s/A]             = 2.99792458E+21 * [X1 W/m^2/Hz] / [X2 A]^2
+## / 1e-17 to put into 'regular' SDSS flux units 
+crts_b_flux   = (2.99792458E+21* (crts_b['flux_density'] / 1000.))/(crts_b['wavelength']**2)  / 1e-17
+crts_r_flux   = (2.99792458E+21* (crts_r['flux_density'] / 1000.))/(crts_r['wavelength']**2)  / 1e-17
+
+    
+redshift = 2.068
+
+
+## https://jakevdp.github.io/PythonDataScienceHandbook/04.08-multiple-subplots.html
+fig = plt.figure(figsize=(10, 4))
+gs = GridSpec(2, 5, wspace=0.6, hspace=0.3)
+
+## Use ``python slicing syntax'', 
+##   gs[which row, which columnn] 
+##   with e.g. gs[r:, c] then letting you span the whole row,
+##
+## https://stackoverflow.com/questions/49323348/matplotlib-gridspec-how-to-specify-the-location-by-numbers
+## https://images.app.goo.gl/VQ4ELKbWTdgJNLu39
+##
+## gs[0 , :]    i.e. row 0,  all columns
[…]

### 2019-10-31 plots/perObject/older_py/J1205p3422_v0pnt8.py

@@ -1,0 +1,177 @@
+
+import numpy as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+from astropy.io import ascii
+from astropy.io import fits
+
+import pylustrator
+pylustrator.start()
+
+
+## Reading in the data
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
+infile = 'crts1205p3422_b.dat'
+crts_b = ascii.read(path+infile)
+infile = 'crts1205p3422_r.dat'
+crts_r = ascii.read(path+infile)
+
+crts_b_wavelength = crts_b['wavelength']
+crts_r_wavelength = crts_r['wavelength']
+
+## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
+## http://www.stsci.edu/~strolger/docs/UNITS.txt
+## 
+## [Y erg/cm^2/s/Hz]            = 1000 * [X W/m^2/Hz]
+## [Y erg/cm^2/s/A]             = 2.99792458E+21 * [X1 W/m^2/Hz] / [X2 A]^2
+## / 1e-17 to put into 'regular' SDSS flux units 
+crts_b_flux   = (2.99792458E+21* (crts_b['flux_density'] / 1000.))/(crts_b['wavelength']**2)  / 1e-17
+crts_r_flux   = (2.99792458E+21* (crts_r['flux_density'] / 1000.))/(crts_r['wavelength']**2)  / 1e-17
+
+    
+redshift = 2.068
+
+
+## https://jakevdp.github.io/PythonDataScienceHandbook/04.08-multiple-subplots.html
+fig = plt.figure(figsize=(10, 4))
+gs = GridSpec(2, 5, wspace=0.6, hspace=0.3)
+
+## Use ``python slicing syntax'', 
+##   gs[which row, which columnn] 
+##   with e.g. gs[r:, c] then letting you span the whole row,
+##
+## https://stackoverflow.com/questions/49323348/matplotlib-gridspec-how-to-specify-the-location-by-numbers
+## https://images.app.goo.gl/VQ4ELKbWTdgJNLu39
+##
[…]

### 2019-10-31 plots/perObject/older_py/J1205p3422_v0pnt85.py

@@ -1,0 +1,176 @@
+
+import numpy as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+from astropy.io import ascii
+from astropy.io import fits
+
+import pylustrator
+pylustrator.start()
+
+
+## Reading in the data
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
+infile = 'crts1205p3422_b.dat'
+crts_b = ascii.read(path+infile)
+infile = 'crts1205p3422_r.dat'
+crts_r = ascii.read(path+infile)
+
+crts_b_wavelength = crts_b['wavelength']
+crts_r_wavelength = crts_r['wavelength']
+
+## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
+## http://www.stsci.edu/~strolger/docs/UNITS.txt
+## 
+## [Y erg/cm^2/s/Hz]            = 1000 * [X W/m^2/Hz]
+## [Y erg/cm^2/s/A]             = 2.99792458E+21 * [X1 W/m^2/Hz] / [X2 A]^2
+## / 1e-17 to put into 'regular' SDSS flux units 
+crts_b_flux   = (2.99792458E+21* (crts_b['flux_density'] / 1000.))/(crts_b['wavelength']**2)  / 1e-17
+crts_r_flux   = (2.99792458E+21* (crts_r['flux_density'] / 1000.))/(crts_r['wavelength']**2)  / 1e-17
+
+    
+redshift = 2.068
+
+
+## https://jakevdp.github.io/PythonDataScienceHandbook/04.08-multiple-subplots.html
+fig = plt.figure(figsize=(12, 5))
+gs = GridSpec(2, 5, wspace=0.6, hspace=0.3)
+
+## Use ``python slicing syntax'', 
+##   gs[which row, which columnn] 
+##   with e.g. gs[r:, c] then letting you span the whole row,
+##
+## https://stackoverflow.com/questions/49323348/matplotlib-gridspec-how-to-specify-the-location-by-numbers
+## https://images.app.goo.gl/VQ4ELKbWTdgJNLu39
+##
[…]

### 2019-10-31 plots/perObject/older_py/J1205p3422_v0pnt9.py

@@ -1,0 +1,280 @@
+'''
+12h05m44.7s +34d22m52.4s
+'''
+
+import numpy as np
+import seaborn as sns
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+#import pylustrator
+#pylustrator.start()
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
+
+##  Light Curve
+infile = 'NEOWISER-L1b_J1205p3422.dat'
+NEOWISER = ascii.read(path+infile)
+NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
+NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
+infile = 'NEOWISER-L1b_J1205p3422_averaged.dat'
+NEOWISER_aver = ascii.read(path+infile)
+NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
+NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
+
+##  Spectra
+infile   = 'DBSP_J1205p3422_b_58538.dat'
+DBSP_b1  = ascii.read(path+infile)
+infile   = 'DBSP_J1205p3422_r_58538.dat'
+DBSP_r1  = ascii.read(path+infile)
+infile   = 'DBSP_J1205p3422_b_58693.dat'
+DBSP_b2  = ascii.read(path+infile)
+infile   = 'DBSP_J1205p3422_r_58693.dat'
+DBSP_r2  = ascii.read(path+infile)
+
+DBSP_b1_wavelength = DBSP_b1['wavelength']
+DBSP_r1_wavelength = DBSP_r1['wavelength']
+DBSP_b2_wavelength = DBSP_b2['wavelength']
+DBSP_r2_wavelength = DBSP_r2['wavelength']
+
+
+## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
[…]

### 2019-10-31 plots/perObject/older_py/J1638p2827_v1pnt0.py

@@ -1,0 +1,296 @@
+'''
+12h05m44.7s +34d22m52.4s
+'''
+
+import numpy as np
+import seaborn as sns
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+#import pylustrator
+#pylustrator.start()
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1638+2827/'
+
+##  Light Curve
+infile = 'NEOWISER-L1b_J1638+2827.dat'
+NEOWISER = ascii.read(path+infile)
+NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
+NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
+infile = 'NEOWISER-L1b_J1638+2827_averaged.dat'
+NEOWISER_aver = ascii.read(path+infile)
+NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
+NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
+
+##  Spectra
+infile   = 'LRIS_J1638p2827_b_58583.dat'
+LRIS_b  = ascii.read(path+infile)
+infile   = 'LRIS_J1638p2827_r_58583.dat'
+LRIS_r  = ascii.read(path+infile)
+
+LRIS_b_wavelength = LRIS_b['wavelength']
+LRIS_r_wavelength = LRIS_r['wavelength']
+
+## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
+## http://www.stsci.edu/~strolger/docs/UNITS.txt
+## 
+## [Y erg/cm^2/s/Hz]            = 1000 * [X W/m^2/Hz]
+## [Y erg/cm^2/s/A]             = 2.99792458E+21 * [X1 W/m^2/Hz] / [X2 A]^2
+## / 1e-17 to put into 'regular' SDSS flux units 
[…]

### 2019-10-31 plots/perObject/older_py/example.py

@@ -1,0 +1,94 @@
+import numpy
+from matplotlib.pylab import *
+from mpl_toolkits.axes_grid1 import host_subplot
+
+# Sent for figure
+font = {'size'   : 12}
+matplotlib.rc('font', **font)
+
+# Setup figure and subplots
+f0 = figure(num = 0, figsize = (12, 8))#, dpi = 300)
+f0.suptitle("Oscillation decay", fontsize=14)
+ax01 = subplot2grid((2, 2), (0, 0))
+ax02 = subplot2grid((2, 2), (0, 1))
+ax03 = subplot2grid((2, 2), (1, 0), colspan=2, rowspan=1)
+ax04 = ax03.twinx()
+#tight_layout()
+
+# Set titles of subplots
+ax01.set_title('Position vs Time')
+ax02.set_title('Velocity vs Time')
+ax03.set_title('Position and Velocity vs Time')
+
+# set y-limits
+ax01.set_ylim(0,2)
+ax02.set_ylim(-6,6)
+ax03.set_ylim(-0,5)
+ax04.set_ylim(-10,10)
+
+# sex x-limits
+ax01.set_xlim(0,5.0)
+ax02.set_xlim(0,5.0)
+ax03.set_xlim(0,5.0)
+ax04.set_xlim(0,5.0)
+
+# Turn on grids
+ax01.grid(True)
+ax02.grid(True)
+ax03.grid(True)
+
+# set label names
+ax01.set_xlabel("x")
+ax01.set_ylabel("py")
+ax02.set_xlabel("t")
+ax02.set_ylabel("vy")
+ax03.set_xlabel("t")
+ax03.set_ylabel("py")
+ax04.set_ylabel("vy")
+
+
+# Data Placeholders
+yp1=zeros(0)
+yv1=zeros(0)
+yp2=zeros(0)
+yv2=zeros(0)
+t=zeros(0)
+
+# set plots
+p011, = ax01.plot(t,yp1,'b-', label="yp1")
+p012, = ax01.plot(t,yp2,'g-', label="yp2")
+
+p021, = ax02.plot(t,yv1,'b-', label="yv1")
+p022, = ax02.plot(t,yv2,'g-', label="yv2")
+
+p031, = ax03.plot(t,yp1,'b-', label="yp1")
+p032, = ax04.plot(t,yv1,'g-', label="yv1")
+
+# set lagends
[…]

### 2019-10-31 plots/spectral/plot_spectra.py

@@ -1,0 +1,255 @@
+
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+
+from matplotlib.patches import Rectangle
+from matplotlib         import colors as mcolors
+
+from astropy.io import ascii
+from astropy.io import fits
+#from astroquery.sdss import SDSS
+
+
+
+def smooth(x,window_len=11,window='hanning'):
+    """smooth the data using a window with requested size.
+    
+    This method is based on the convolution of a scaled window with the signal.
+    The signal is prepared by introducing reflected copies of the signal 
+    (with the window size) in both ends so that transient parts are minimized
+    in the begining and end part of the output signal.
+    
+    input:
+        x: the input signal 
+        window_len: the dimension of the smoothing window; should be an odd integer
+        window: the type of window from 'flat', 'hanning', 'hamming', 'bartlett', 'blackman'
+            flat window will produce a moving average smoothing.
+
+    output:
+        the smoothed signal
+        
+    example:
+
+    t=linspace(-2,2,0.1)
+    x=sin(t)+randn(len(t))*0.1
+    y=smooth(x)
+    
+    see also: 
+    
+    numpy.hanning, numpy.hamming, numpy.bartlett, numpy.blackman, numpy.convolve
+    scipy.signal.lfilter
+ 
+    TODO: the window parameter could be the window itself if an array instead of a string
+    NOTE: length(output) != length(input), to correct this: return y[(window_len/2-1):-(window_len/2)] instead of just y.
+    """
+
+    if x.ndim != 1:
+        print(len(x.ndim))
+        #raise ValueError, "smooth only accepts 1 dimension arrays."
+
+    if x.size < window_len:
+        print(len(x.ndim))
+        #raise ValueError, "Input vector needs to be bigger than window size."
+
+
+    if window_len<3:
+        return x
+
+
+    if not window in ['flat', 'hanning', 'hamming', 'bartlett', 'blackman']:
+        print(len(x.ndim))
[…]

### 2019-10-31 tex/CIV_CLQs.tex
CIV_CLQs.tex updated, 2019-10-31

\documentclass[a4paper,fleqn,usenatbib]{mnras}

\input{format}

\title[High-redshift CLQs]{The first high-redshift Changing Look Quasars}

\author[Bercow]
{%The RH John~S.~Bercow, MP, {\it et al.} 
Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
 Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
\newauthor and Daniel Stern$^{6}$ 
\\
% List of institutions
%$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

\date{Accepted XXX. Received YYY; in original form ZZZ}
\pubyear{2018}

\hypersetup{draft}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first `Changing-Look'' quasars at high
redshift.  This is also the first time the changing-look behaviour has
been seen in a high-ionization emission line.
%%
SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
in their observed optical light curves, and subsequent spectroscopy
shows significant changes in the \civ\ broad emission line, with both
line collapse and emergence being displayed in rest-frame timescales
of $\sim$240-1640 days.
%%
Where observed, the profile of the Ly$\alpha$/\nv emission complex
also changes, and there is tentative evidence for changes in the \mgii
line.
%%
Although line measurements from the three quasars show large changes
in the \civ\ line flux-line width plane, the quasars are not seen to
be outliers when considered against the full $z\sim2$ quasar population
in terms of (rest) Equivalent Width and FWHM properties.
%%
We put these observations in context with recent ``state-change''
models, but note that even in their `low-state', the \civ\ CLQs are
above $\sim$10\% in Eddington luminosity.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
accretion, accretion discs -- surveys -- quasars: general -- quasars: individual: J1100-0053 
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their
energy output on timescales of weeks to months.  This observation, and
the subsequent mismatch in the expected ``viscous'' timescale, which
for a $\approx$10$^{7}$ M$_{\odot}$ central supermassive black hole
(SMBH) is $\sim$hundreds of years, was noted over 30 years ago
\citep[e.g.][]{Alloin1985}. However, with new photometric light-curve
and repeat spectroscopic data, the desire for a deeper understanding
of AGN accretion disk physics has been recently re-invigorated the
field \citep[e.g.][]{Lawrence2018, Antonucci2018}.

The optical continuum variability of quasars has been recognized since
their first optical identification
\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic changes
in the broad emission lines (BELs) of quasars has only recently been
identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}. The
community uses both these terms as a cover for the underlying
physics. For sake of argument, ``Changing Look'' quasars can
potentially be thought of as the extension to the BELs of quasar
continuum variability \citep[e.g., ][]{MacLeod2012} whereas the
``Changing State'' quasars (CSQs) have a `state-transition' similar to
that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019}. In
this paper, we use the term `Changing Look', as we are currently
agnostic, and somewhat ignorant, to the underlying physical processes.

These CLQs have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, observed from optical
spectroscopy. Recent work \citep{Guo2019, Homan2019} report on discoveries
of \mgii Changing-look AGN. However, current CLQ studies have been at
redshifts $z<1$.

While there have been a slew of studies on triply ionized carbon, i.e
\civ, these have tended to focus on broad absorption line quasars
\citep[BAL QSOs; see Table 1][]{Hemler2019} or the Baldwin Effect
\citep[BEff; ][]{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: the {\it
global} (or {\it ensemble}) Baldwin Effect, which is an
anti-correlation between the EW of the emission line and the
underlying continuum luminosity of {\it single-epoch} observations of
a {\it large number} of AGN and second, the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an {\it individual, variable}
AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
collisionally excited broad {\it emission} line (BEL) of \civ\ (and
indeed \ciii) have not to this point been seen.

\begin{table*}
  \centering
  \begin{tabular}{r l   r ll   r r r r}
    \hline 
    \hline 
    Object                           & \multirow{3}{*}{Redshift}  &                       & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date} & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
    R.A. / deg                     &                                         &   {$g$-band}   &                                 &                                  &                                               &  Time           & Spectrum                 & \\
    Decl. / deg                   &                                         &    magnitude   &                                &                                   &                                              &  / seconds    & Plate-FiberID  & \\
    \hline  
                                         &                                         &                        &                &                            &                    &                              &                              & \\
    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             &  8057                  & 2089-427             & \\
    181.436164                  & 2.071                              &                         &  58538   &  2019-Feb-24    & DBSP            &  1800                  &  ---                      &  Average conditions \\
    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2400                   &  ---                      &   \\
                                         &                                       &                          &                &                          &                    &                               &                              & \\
    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS           &   4801                    &  2948-614              & \\
    249.720558	                 &  2.186$\pm$0.0007     &                          &  55832    & 2011-Sep-28     & BOSS            &   3600                   &  5201-178            & \\
    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10     & LRIS              &  1800                   &  ---                             & \\
                                        &                                      &                          &                &                            &                    &                              &                                & \\
    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                &  56189    & 2012-Sep-19     & BOSS             &  2700                 &   6118-720          & \\
    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30     & BOSS             &  4500                  &   7582-790          & eBOSS reobservation \\ 
    +22.017478                &                                      &                          &  58693    & 2019-Jul-29       & DBSP             & 2400                   &    ---                        &    \\
                                       &                                       &                          &               &                            &                   &                              &                            & \\
    \hline \hline   
  \end{tabular}
  \caption{
    Details of our spectroscopic observations.
    Redshift and redshift errors from SDSS SkyServer for SDSS, BOSS and eBOSS spectra. 
    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and  eBOSS spectra have $\mathcal{R}\sim$2,000.
    DBSP: Double Spectrograph on the Palomar 200-inch telescope.
    LRIS:  Low Resolution Imaging Spectrometer on Keck I 10m telescope.
    %  2019-Feb-24    & DBSP            &  2$\times$900 f
    %  2019-Jul-29     & DBSP            &  2$\times$1200
    %  2019-Apr-10     & LRIS              &  2$\times$900
    %& 2019-Jul-29       & DBSP             & 2$\times$1200
  } 
  \label{tab:obs_notes}
\end{table*}

Here, we report on three quasars  
which show dramatic changes in their \civ\ and \ciii broad emission
line properties as well as in the underlying continuum. We claim these
are the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift. Moreover, these are the first cases for substantial changes
of ions with high ionization potentials (I.P.'s $>$2 Rydberg), thus
linking the ionizing photons to the energetic inner accretion disk,
potentially by inverse Compton scattering of lower energy photons to
higher energies.  Furthermore, the measured rest-wavelengths of
emission lines in quasar spectra, are known to vary from their nominal
laboratory wavelengths especially for the high-ionization broad lines \citep[e.g.][]{VandenBerk2001}.

In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
the \civ\ doublet \citep{Kramida2018}.  The 1548.202 and 1550.774 \AA\
emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
transition, split by total angular momentum $J= 3/2$ and $1/2$,
resulting in energies 64,591 cm$^{-1}$ and 64,484 cm$^{-1}$,
respectively \citep[e.g.][]{Moore1993}. The transition probabilities
of the the 1548 and 1550\AA\ lines are $A_{ki}= 2.65\times10^{8}$ and
2.64$\times10^{8}$ s$^{-1}$.

The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. Using the
\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
Atomic Spectra Database Ionization Energies Form} for ionisation
energies, we note 11.3 eV is the energy required for C~I to dislodge
one electron and become singly-ionised C~II; 24.4 eV is then the
(`additional') energy needed for singly-ionised C~II to dislodge an
additional electron, and become doubly-ionised C~III, and 47.89 eV
(3.519 Ry) is required for doubly-ionised C~III become triply-ionised
\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
itself. This energy corresponds to a thermal temperature of $T
\gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).  \ciii is the
1$s2$2$s$2$p$ $^{3}$P$^{\circ}$ to 1$s^{2}$2$s^{2}$ $^{1}$S transition
(with $J=1\rightarrow0$) resulting in an energy of 52,390.75 cm$^{-1}$ and
a transition probability of $A_{ki} = 1.14\times10^{2}$ s$^{-1}$ \citep{Wiese1996}.

%%   B a c k g r o u n d     L i t e r a t u r e    
\civ\ variability has been long studied, e.g., \citet[][]{Baldwin1977,
Gaskell1982, Gregory1982, Wilkes1986, Espey1989, Espey1990Erratum,
ZhengSulentic1990, Corbin1990, Corbin1991, Weymann1991,
Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
Laor1995, McIntosh1999, Nazarova2003}.

\citet{Wilhite2006} examine the variability of a C~\textsc{iv} sample
of 105 quasars observed at multiple epochs by the Sloan Digital Sky
Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
find a strong correlation between the change in the C~\textsc{iv} line
flux and the change in the line width, but no correlations between the
change in flux and changes in line center and skewness.  These authors
find that the relation between line flux change and line width change
is consistent with a model in which a broad line base varies with
greater amplitude than the line core. The C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  \citet{Wilhite2006}
find no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects.

\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$ SDSS
quasars, concentrating on the properties of the \civ\ emission
line. We consider two well-known effects involving the \civ\ emission
line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
the BEff) and the blueshifting of the peak of \civ\ emission with
respect to the systemic redshift. These authors conclude that these
two \civ\ parameters (EQW and blueshift) are capturing an important
trade-off between ``disk'' and ``wind'' components in the disk-wind
model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
Proga2000}, with one dominating over the other depending on the shape
of the SED \citep[][strong \civ\ EQW indicates a more ionizing SED and
large \civ\ blueshift indicating a less ionizing SED ]{Leighly2004b}.

The Sloan Digital Sky Survey Reverberation Mapping Project
\cite[SDSS-RM; ][]{Shen2015} has a monitored $\sim$350 quasars with
\civ. Noting the biases associated with \civ Emission Line Properties
\citep[e.g. increasing systematic offsets with decreasing
signal-to-noise][]{Denney2016}, \citet{Grier2019} report report
significant time delays between the continuum and the CIV 1549
emission line in 52 quasars, and investigate the \civ
radius-luminosity relationship.

\civ\ is also known to exhibit significant displacements to the
blue and these `blueshifts' almost certainly signal the presence of
strong outflows. As a consequence, single-epoch virial black hole (BH)
mass estimates derived from \civ\ velocity widths are known to be
systematically biased compared to masses from the hydrogen Balmer
lines. \citet{Coatman2017} use a large sample of 230 high-luminosity
($L$Bol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with
both \civ\ and Balmer line spectra, we have quantified the bias in \civ
BH masses as a function of the \civ\ blueshift. \civ\ BH masses are
shown to be a factor of 5 larger than the corresponding Balmer-line
masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated
by almost an order of magnitude at the most extreme blueshifts,
$\gtrsim$5000 km s$^{-1}$.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
Sloan Digital Sky Survey Reverberation Mapping project to investigate
the dependence of the blueshift of \civ\ relative to \mgii on quasar
properties. We confirm that high-blueshift sources tend to have low
\civ\ equivalent widths (EWs), and that the low-EW sources span a range
of blueshift. Other high-ionization lines, such as He II, also show
similar blueshift properties. The ratio of the line width (measured as
both the full width at half maximum and the velocity dispersion) of
\civ\ to that of \mgii increases with blueshift. Quasar variability
enhances the connection between the \civ\ blueshift and quasar
properties (e.g., EW). The variability of the \mgii line center (i.e.,
the wavelength that bisects the cumulative line flux) increases with
blueshift. In contrast, the C IV line center shows weaker variability
at the extreme blueshifts. Quasars with the high-blueshift \civ\ lines
tend to have less variable continuum emission, when controlling for
EW, luminosity, and redshift. Our results support the scenario that
high-blueshift sources tend to have large Eddington ratios.
Therefore, according to this study, the \civ\ or \heii\ EW is not an
accurate indicator of the Eddington ratio or quasar SED.
Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
\citet{Dyer2019} provide a detailed analysis of 340 quasars at high-redshift
($1.62<z<3.30$) from the SDSS-RM project, which we will compare our
results to.

%%   P a p e r    O v e r v i e w
The purpose of this paper is, for the first time, to access and 
report on the Changing-Look quasar phenomenon at high, 
$z>2$ redshift. By doing so, we move from the low-ionization 
energy Balmer emission line series to the high-ionization emission 
lines, in particular \civ\ $\lambda$1549.

This paper is organised as follows. In Section 2, we describe our
sample selection, catalogs and observational data sets.  In Section 3,
we present the high-$z$ quasars and report the line properties for the
quasars at the observed epochs.  We give a very brief theoretical
discussion in Section 4. We present our Conclusions in Section 5.  We
report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
Fukugita1996} unless otherwise stated explicitly. For the WISE bands,
$m_{\rm AB} = m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1
at 3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively
\citep{Cutri2011}.
We adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73$,
$\Omega_{\rm M} = 0.27$, and $h = 0.71$ in order to be consistent with
\citet{Hamann2017}. As a guide this cosmology has a $z=2.000$
comoving radial distance of 5244.3 Mpc, a $\sim$1.25\% difference
compared to 5179.0 Mpc from $\Omega_{\Lambda} = 0.70$, $\Omega_{\rm M}
= 0.30$, and $h = 0.70$ that is used in \citet{Shen2011}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
Our high-$z$ CLQs were identified as follows.  We selected all 64,774
SDSS DR15 sources with $z > 0.35$ classified as `QSO', having at least
two spectra separated by at least 100 days, and with a corresponding
CRTS light curve. We fitted a damped random walk to the CRTS data via
Gaussian process regression and the photometric magnitudes at the
epochs of the SDSS spectra for a given source are predicted. Those
where $|\Delta V| > 0.3$ are then selected for visual
inspection. Three quasars SDSS J120544.7+342252.4 (hereafter
J1205+3422), SDSS J163852.93+282707.7 (hereafter J1638+2827) and SDSS
J222818.76+220102.9 (hereafter J2228+2201), satisfied these selection
criteria and showed interesting or dramatic emission line behaviour.

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20191024.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20191024.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20191024.png}
  \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
    SDSS J1205+3422 (top), 
    SDSS J1638+2827 (middle), 
    SDSS J2228+2201 (bottom). 
The light curve data is present in the panels on the left hand side, with the 
spectral epoch observational timings given by the vertical lines. 
The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
complex, the \civ\ line and the \mgii line. 
  }
  \label{fig:civ_clqs}
\end{figure*}
\subsection{Spectra}
An overview of our spectroscopic observations is given in
Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
\citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011,
Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
Abolfathi2018, Paris2018}.  These quasars were targetted via a range
of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
Myers2015}. The SDSS, BOSS and eBOSS data are supplemented by
spectra from the Low Resolution Imaging Spectrometer (LRIS) on the 10m
Keck {\sc I} telescope \citep{Oke1995}.  and the Double Spectrograph
(DBSP) instrument on the Palomar {\it Hale} 5m telescope.

\subsection{Emission Line and Power-law slope measurements}
We use the measured quasar emission line properties from several catalogues: 
\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017} and
\citet{Calderone2017}.

\citet{Shen2011} present a compilation of properties of the 105,783
quasars in the SDSS Data Release 7 (DR7) quasar catalog \citep[DR7Q;
][]{Schneider2007}. \citet{Shen2011} report non-zero \civ\ FWHM and
EWs for approximately half (51,501) of the full DR7Q, and non-zero
\mgii FWHM and EWs for 80\% (84,183) of the DR7Q quasars).
%%
Measured line values using the methods and catalogue from
\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
$K$-corrected to $z = 2$; Bolometric luminosity computed from the
monochromatic luminosity at 1350\AA\ using the spectral fits and
bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
luminosity, FWHM, rest-frame equivalent width, and their errors for
the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
continuum fit for \civ; Virial BH masses using calibrations of
\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
virial BH mass.

\citet{Calderone2017} present the Quasar Spectral Fitting (QSFIT)
software package which among other quantities provides luminosity
estimates as well as width, velocity offset and equivalent width of 20
emission lines, including \civ, \ciii and \mgii.  We attempt to process and fit
all nine spectra using the lastest version (v1.3.0) of the QSFIT
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online calculator}
and setting $E(B-V)=0.00$.

\citet{Hamann2017} investigate in robust detail the UV continuum and
the \civ\ (and \nv $\lambda$1238, 1242 \AA\ ) emission lines for over
200,000 quasars in BOSS DR12Q \citep{Paris2017}.  The quasar redshift
are limited to the range $1.53 \leq z \leq 5.0$ so that \civ\ and the
adjacent continuum are covered by BOSS. These measurements provide
line profile information and flux ratios\footnote{This emission-line
catalog can be downloaded from
\href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
\citet{Hamann2017} was focused on $z\geq2$ quasars and specifcally
their \civ properties in order to understand the high-$z$ ``Extremely
Red Quasar'' population \citet{Ross2015, Zakamska2016, Perrotta2019,
Zakamska2019}.  As such, these measurements can be taken as the `gold
standard' for \civ line measurement, though this is only for two out of
our nine spectra.

When using the \citet{Shen2011} catalogue, we report line luminosity,
FWHM, rest-frame equivalent width, and their errors for the whole
\mgii profile (this catalogue also quotes values for just the broad
\mgii component, but the differences for our objects is
negligible). The line luminosities in \citet{Calderone2017} are given
in units of $10^{42}$ erg s$^{-1}$, while the line luminosities in
\citet{Shen2011} are in units of $\log(L)$.  We do not report the
\citet{Shen2011} error on the line luminosity.

Power-law continuum slopes, $\alpha$, where $f_{\lambda} \propto
\lambda^{\alpha}$, are also reported in these catalogues and from
QSFit.  We quote the most appropriate value given the emission line
wavelength.

\subsection{Multi-wavelength properties}
Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning of the
Wide-field Infrared Survey Explorer (WISE) mission \citep[2010
January; ][]{Wright2010} through the fifth-year of NEOWISE-R
operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
pattern leads to coverage of the full-sky approximately once every six
months (a ``sky pass''), but the satellite was placed in hibernation
in 2011 February and then reactivated in 2013 October. Hence, our
light curves have a cadence of 6 months with a 32 month sampling gap.
%Radio ??

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Overall Spectral Evolution}
Figure~\ref{fig:civ_clqs} presents the optical and infrared light
curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
shows the spectra for each epoch, with the MJD of observation given by
the dashed vertical lines in the light curves.

For J1205+3422, our spectral observations cover 5195 days observed, 1691 days
in the rest-frame. For J1205+3422 is identified in SDSS as a bright
$g\approx18.0$, blue-sloped quasar with broad \siiv, \civ, \ciii and
\mgii observed in the initial spectrum (MJD 53498; 2005-May-08). \ciii
and \civ\ are seen to have large blueshifts of $\approx$2600$\pm$150
and $\approx$1150$\pm$100 km s$^{-1}$, respectively.  By the time the
2019 spectra were taken (MJD 58538, 2019-Feb-24 and MJD 58693
2019-Jul-29), however, the light curve has dropped by $\sim$1.5
magnitudes and the spectra are significantly less steep.  While \lya
and \nv are detectable in both the MJD 58538 and MJD 58693 DBSP
spectra, \civ\ has all but disappeared in the MJD 58693 spectrum.  The
broad \ciii emission has disappeared between the 2005 and 2019
spectra. {\it The changes in \civ\ and \ciii going from broad emission to
barely detectable have on the timescales of $\approx$50 days in the rest-frame.}

For J1638+2827, our spectral observations cover 4030 days observed, 1265 days
in the rest-frame. Here, in the initial epoch spectrum, \civ\ is broad
and bright, as is \ciii. However, just over 400 days in the rest-frame
later, the broad \civ\ and \ciii BEL have to faded, the continuum
slope around 1400\AA\ has changed from $\approx$-1.48 to
$\approx$-2.25, but the \lya/\nv emission complex is very similar in
shape and line flux intensity. Around 870 days in the rest-frame after
the second spectral epoch, \lya, \nv, \civ, \ciii and \mgii are all
apparent and broad, with \mgii being seen for the first time at high
signal-to-noise. The light curve is consistent with this spectral
brightening, increasing from around $\sim$19.5-20.5th magnitude to
$\sim$18.5 in the optical band. An absorption feature between  \lya and \nv
is seen in all three spectral epochs.

For J2228+2201, our spectral observations cover 2504 days observed,
778 days in the rest-frame. Over the course of 240 days in the rest-frame, \civ\ and \ciii both {\it emerge} as BELs and
the standard UV/blue continuum slope increases in flux.
Then, over the course of 538 days in the rest-frame, the broadline emission, while still
very present, reduces in line flux the UV/blue continuum diminishes,
though is still more luminous than the initial BOSS spectrum.

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Overall Spectral Evolution}
Emission line measurements from the catalogues of  \citet{Shen2011}.
\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of \citet{Calderone2017}
are presented in Table~\ref{tab:LineMeasurement}.
%%
From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

The Balmer series in hydrogen is due to the recombination cascade
between different principal quantum numbers $n$, and
the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
%(and assuming an equilibrium distribution between the angular momentum levels $l$ corresponding to a given $n$).
%%
Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$. 
%%
\civ\ is one of the strongest collisionally excited lines in quasar
spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
canonical BELR parameters deduced over from early analysis of the
\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
H$^{+}$).

\begin{table*}
  \centering
  % \begin{tabular}{lll  cccc r }
  \begin{tabu}{l ll  lccc c r }
    \hline 
    \hline 
    Object                               &   MJD      & line      & Line  Lumin.       &  FWHM                       &  $V_{\rm off}$         & E.W.                          & $\alpha_{\lambda}$  &   Catalogue \\                                   
    \hline                                     
    \rowfont{\color{blue}}       & 53498    & \civ      &  511$\pm$13    &   9593$\pm$287        &  1172$\pm$74      & 15.9$\pm$0.4      & $-1.64\pm0.01$       &  QSFit         \\    %% (NPR) 
    \rowfont{\color{blue}}       & 53498    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    & 30.1$\pm$1.21    & $-1.47\pm0.08$       &  Shen2011 \\
    \rowfont{\color{blue}}       & 53498    & \civ      &   403                  &   5119$^{(a)}$             &    ---                     &  ---                        &  ---                         &  DR12 SAS   \\
                                             & 53498     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    & 25.10$\pm$0.59    & $-1.65\pm0.01$      &  QSFit          \\  %% (NPR) 
                                             & 53498    & \ciii       &   144                 &   5119$^{(a)}$             &  ---                       &   ---                       &  ---                          &  DR12 SAS  \\
  \rowfont{\color{teal}}         & 53498     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     & 26.66$\pm$1.65    &   $-1.65\pm0.01$    &  $^{(d)}$QSFit  \\  %% (NPR) 
  \rowfont{\color{teal}}         & 53498     & \mgii     &  284                  &   4730$\pm$314       &  $-179\pm188$     & 32$\pm$3.88         &  $-1.87\pm0.06$     &  Shen2011 \\
 \multirow{2}{*}{{\bf J1205+3422}}  
                &     \textcolor{teal}{53948}     & \textcolor{teal}{\mgii}   & \textcolor{teal}{130} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\
                                 \cdashline{2-9}
                                            & 58538     & \lya      & 952$\pm$1.1    & 12242$\pm$15    &  $-1679\pm6$          &  165$\pm$0.2        &  ---                       &   QSFit  \\    %% (MJG)
   \rowfont{\color{blue}}       & 58538     & \civ      & 1037$\pm$5    & $>$15000             &  983$\pm$40            &  ---                        &  ---                       &   QSFit  \\   %% (NPR) 
                                            & 58538      & \ciii     &  167$\pm$0.9  & $>$15000            &  2734$\pm$46            &     45$\pm$0.2       &  ---                       &  QSFit  \\    %% (MJG)
    \rowfont{\color{teal}}      & 58538     & \mgii    &  216$\pm$1.4  & 13940$\pm$94    & $-465.2\pm38$         &  88$\pm$0.6	    &  ---                       &   QSFit  \\    %% (MJG)
                                          \cdashline{2-9}
                                           & 58693     & \lya     &  271$\pm$0.9    & 9637$\pm$52     &  $-447\pm13$          &  85.1$\pm$0.3          & ---                        &   QSFit  \\    %% (MJG)
    \rowfont{\color{blue}}    & 58693     & \civ      &   52$\pm$0.9    & 5046$\pm$26     &   1053$\pm$17         &   24.0$\pm$0.2          & ---                        &  QSFit \\     %% (MJG)
                                           & 58693     & \ciii     &   59$\pm$0.9    & 10751$\pm$        &  1097$\pm$77         &   36$\pm$0.6             & ---                        &  QSFit   \\    %% (MJG)
   \rowfont{\color{teal}}      & 58693     & \mgii    &  69$\pm$1.5    & 14983$\pm$346   &  $-190\pm134$       &    72$\pm$1.6           & ---                        &  QSFit   \\    %% (MJG)
\hline
                                                & 54553     & \lya      & 188                 &  3207                     &    ---                        &   ---                         & ---                    &   DR12 SAS  \\
   \rowfont{\color{blue}}          & 54553     & \civ      & 257$\pm$13   &  4550$\pm$371     &   55$\pm$450         &   31.8$\pm$1.5     &                                &  $^{(d)}$QSFit  \\   %% (NPR) 
   \rowfont{\color{blue}}          & 54553     & \civ      & 281                  &    4181$\pm$736   &    680$\pm$133       & 100.5$\pm$12  & $-0.14\pm0.68$        &  Shen2011   \\
   \rowfont{\color{blue}}          & 54553     & \civ      & 170                  &   4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\    %% (NPR) 
                                                & 54553     & \ciii     &  130$\pm$10   &  3852$\pm$402    &  $-236\pm565$       &  36.7$\pm$2.8          &  $-1.47\pm0.20$    &  $^{(d)}$QSFit  \\
                                                & 54553     & \ciii     &  61                    &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\    %% (NPR) 
    \rowfont{\color{teal}}          & 54553      & \mgii  &  139                  &  4757$\pm$2224   &  $-944\pm568$        &   119$\pm$40          &  $-1.49\pm0.54$    &  Shen2011   \\
    \rowfont{\color{teal}}          & 54553      & \mgii  &  69                    &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\   %% (NPR) 
                                                \cdashline{2-9}
                                                & 55832     & \lya     & 288$\pm$11    &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99   &                               &   QSFit  \\
                                                & 55832     & \lya     & 234                  &  4165.6$^{(a)}$         &    ---                       &   ---                         & ---                         &   DR12 SAS  \\    %% (NPR) 
\multirow{2}{*}{\bf {J1638+2827}}
 & \textcolor{blue}{55832} & \textcolor{blue}{\civ}    & \textcolor{blue}{63$\pm$3}  &   \textcolor{blue}{6052$\pm$250}  &  \textcolor{blue}{-117$\pm$103}  &  \textcolor{blue}{43.2$\pm$1.7}  &  \textcolor{blue}{-2.25$\pm$0.05} & QSFit    \\
    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---               &    5210$\pm$226     &    ---                       &   42.8$\pm$2.0         & $-3.35$                 &     Ham17  \\
    \rowfont{\color{blue}}           &  55832   &  \civ     &  46                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\
                                                 & 55832     & \ciii     & 15$\pm$5     &  11421$\pm$3654   &   $>$3000                &   14.8$\pm$4.5         &  $-2.25\pm0.05$   &        QSFit \\
                                                 &  55832    &  \ciii    &  11                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                       &   DR12 SAS \\  
    \rowfont{\color{teal}}           &  55832     & \mgii   &  13                &     5385$^{(a)}$         &  ---                           &   ---                          &  ---                       &   DR12 SAS\\  
                                               \cdashline{2-9}
                                               & 58583       & \lya    &  785$\pm$1      & 4956$\pm$4    	&   $-641\pm2$            &   90$\pm$0.1   	  &  ---                          &  QSFit  \\ %% (MJG)
   \rowfont{\color{blue}}         & 58583      & \civ      &  311$\pm$1     & 5739$\pm$14	 &  $-167\pm6$             &   58$\pm$0.1          & ---                          &   QSFit  \\  %% (MJG)
                                               & 58583      & \ciii      &  52$\pm$0.8   &  3917.4	68.837      &  1514$\pm$127        &  124$\pm$2             & ---                          &   QSFit \\   %% (MJG)
   \rowfont{\color{teal}}           & 58583      & \mgii   &  157$\pm$2    &  10565$\pm$129    &  $-450\pm52$          &   92$\pm$1              & ---                          &   QSFit  \\  %% (MJG)
\hline
    \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &   2994$\pm$620       &     ---                       &   42.2$\pm$5.6      & -1.59                      &    Ham17  \\
    \rowfont{\color{blue}}         &  56189     & \civ    &   19                  &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                        &   DR12 SAS  \\
                                               &  56189      &  \ciii   &  34$\pm$6       &  13748$\pm$2869    &   1851$\pm$1140    &  63$\pm$12          &  $-0.46\pm0.21$    &   QSFit  \\
                                               &  56189      & \ciii    &  7                     &     5218$^{(a)}$          &  ---                         &     ---                     & ---                         &   DR12 SAS \\  
    \rowfont{\color{teal}}          & 56189      & \mgii  &  25$\pm$6       &   7253$\pm$1712     &   $-931\pm708$      &  51$\pm$10.95      &  $-0.46\pm0.21$   &   QSFit   \\
    \rowfont{\color{teal}}         &  56189      &  \mgii &  13                   &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                       &   DR12 SAS \\  
                                                  \cdashline{2-9}
                                              & 56960         & \lya    & 121$\pm$38     & 3580$\pm$673       &     -16$\pm$171     &  13.52 $\pm$4.21    & ---                        &   QSFit   \\  
\multirow{2}{*}{{\bf J2228+2201}}
           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}  & \textcolor{blue}{229$\pm$4}      &  \textcolor{blue}{8911$\pm$169}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{46.8$\pm$0.9}    & ---    & \textcolor{blue}{QSFit}     \\   
                                               & 56960    & \ciii      & 185$\pm$5        &        -                      &  2701$\pm$225      &   47.75$\pm$1.29     & ---                      &   QSFit    \\  
   \rowfont{\color{teal}}           & 56960    & \mgii   &   99$\pm$4        &  7312.6$\pm$340   &   188$\pm$137      &   50.75$\pm$2.21     & ---                      &   QSFit   \\
                                               \cdashline{2-9}
                                               & 58693     & \lya      &  447$\pm$5       & 8133$\pm$93       &   613$\pm$130       &        56$\pm$0.6     &  ---                    	 &   QSFit  \\%% (MJG)
     \rowfont{\color{blue}}        & 58693     & \civ      &  41$\pm$1        &  4914$\pm>$65    &   160$\pm$27         &   25$\pm$0.3          & ---                         & QSFit   \\  %% (MJG)
                                               & 58693     & \ciii      & 107$\pm$1.2    &  $>$15000             &  2422$\pm$67        &   ---                       & ---                          &  QSFit    \\  %% (MJG)
     \rowfont{\color{teal}}        & 58693     & \mgii    & 177$\pm$1.1    &  $>$15000             &  1000$\pm$2617    &   16$\pm$36         & ---                           &   QSFit  \\  %% (NPR) 
\hline
\hline
     %    \end{tabular}
    \end{tabu}
    \caption{Line Measurement information for the nine epochs for the 3 quasars.
      Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM and $V_{\rm off}$ in km s$^{-1}$,
      where positive values of $V_{\rm off}$ means the line is blueshifted.
      Equivalent widths are \AA\.  
      Shen11 is \citet{Shen2011}. 
      Ham17 is \citet{Hamann2017}.
      DR12 SAS is the line measurement information from the SDSS DR12 
      Science Archive Server (SAS).
          $^{(a)}$Emission lines of a common ``width group'', in this case,
    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
    the same intrinsic velocity width in the SDSS spectral line fitting
    procedure \citep{Bolton2012}. 
      %$^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
      Positive values of Voff means the line is blueshifted.
%      $^{(b)}$Bit 3: FWHM value hits a limit in the fit
      Notes: QSFit does not fit the \mgii line for J1638+2827 MJD
      54553 or 55832. QSFit does not fit the \civ line for J2228+2201 MJD 56189.
      $^{(d)}$Emission line modelled with two components.
      The different colours of text are merely for readability.
    }
 \label{tab:LineMeasurement}
\end{table*}

%%
%% %% \eta_{\rm Edd} = log10((10**LBol)/((1.26e38)*(10**MBH)))
%%
%% Using    C IV

%% In [6]: log10((10**47.216)/((1.26e38)*(10**9.49)))                                                                                                                                             
%%Out[6]: -0.37437054511756207
%%
%%In [7]: log10((10**46.166)/((1.26e38)*(10**8.742)))                                                                                                                                            
%%Out[7]: -0.676370545117567
%%
%%In [8]: log10((10**46.721)/((1.26e38)*(10**9.1289)))                                                                                                                                           
%%Out[8]: -0.5082705451175662
%%
%%In [9]: log10((10**46.231)/((1.26e38)*(10**8.733)))                                                                                                                                            
%%Out[9]: -0.6023705451175618
\begin{table*}
  \begin{tabular}{l l  ll ll cc r}
    \hline
    \hline
\multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$} & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref. \\
                                      &                                   &                                      &                                                 & \mgii                  & \civ                    &  \mgii           &  \civ                       &        \\
    \hline
                                     & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen2011\\
 J1205+3422                & 58538                         &                                      &                                                 &                             &                             &                    &                               & \\
                                     & 58693                         &                                     &                                                  &                             &                             &                    &                               &   \\
    \hline 
                                    & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen2011\\
 J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kol017\\
                                    & 58583                          &                                      &                                                &                               &                            &                   &                                      &  \\
    \hline 
                                   & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kol017\\
J2228+2201               & 56960                          &                                       &                                                &                              &                               &                 &                                        & \\
                                  & 58693                          &                                       &                                               &                               &                                &                &                   &  \\
    \hline
    \hline
  \end{tabular}
  \caption{$\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio.
        Shen11 is \citet{Shen2011}. 
        Kol17 is \citet{Kozlowski2017}.
        Measured line values using the methods and catalogue from
\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
$K$-corrected to $z = 2$; Bolometric luminosity computed from the
monochromatic luminosity at 1350\AA\ using the spectral fits and
bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
luminosity, FWHM, rest-frame equivalent width, and their errors for
the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
continuum fit for \civ; Virial BH masses using calibrations of
\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
virial BH mass.}
\label{tab:Eddington_ratios} 
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. Note the REW logarithmic scaling.}
  \label{fig:REWvsFWHM}
\end{figure}

%{\bf Our Eddington ratios \\
%Done 1\% \\
%Coatman, Hewett say \civ\ masses are okay.\\
%But what are these Eddington ratios? \\
%Low state BHs vs. High-mass BHs... \\
%Coatman et al?? Blue-shiftted \\ }
\section{Discussion}
\civ\ probes the photoionization environment produced by the innermost
disk, as indicated by RM time-delay measurements. In standard \citet{SS73}
thin disk models, large changes in the continuum flux are not
permitted over short timescales due to the relatively long viscous
time associated with such disks. Given the observed short timescale
continuum variations, it is not surprising that the \citet{SS73} disk may fail
on other fronts. The \civ\ variations observed in our sources... 
%DO/DO NOT (I can't tell!?! we have to determine this!) fit the Baldwin Effect relationship found by previous authors (cite em again).

%If they DO fit:
This indicates they may comfortably fit into the sample of CIV
variable QSOs explored by \citet{Dyer2019}, and similar to those
authors we suggest slim accretion disk models e.g., 
\citet[][]{Abramowicz1988} or inhomogeneous disk models
\citep[e.g.,][]{DexterAgol2011} may provide viable explanations for
our observations. I want to say a bit more here about the generic
probe of photoionization vs shielding and conditions in the BL region
but that will take more time.

%If they DO NOT fit:
This implies that the variable \civ\ in our sample arises through
different emission mechanisms than is usual for high-$z$ quasar...
%% --and I gotta think more/longer about what else to say here.

\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.  The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales e.g. with
$R_{\rm Sch}= 2GM /c^{2}$ and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$ means
$t_{\rm dyn} \sim 6 G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2}
$.

The X-ray Baldwin Effect \citep[e.g., ][]{Iwasawa_Taniguchi1993}... 
\citet{Bachev2004} find a 10-fold decrease in EW \civ\ with Eddington
ratio (decreasing from $\sim$1 to $\sim$0.01), while \nv shows no
change. These trends suggest a luminosity-independent ``Baldwin
effect'' in which the physical driver may be the Eddington ratio.
\citet{Ge2016} Broad emission lines is a prominent property of type I quasi-stellar objects (QSOs).

\subsection{Eddington ratios and State Changes} 
The broad UV and optical lines in quasars are most sensitive to the
extreme ultraviolet (EUV) part of the spectral energy distribution
(SED), with \civ\ (and indeed \heii and \nv) being at the higher
energy end of the EUV distribution.

The soft X-ray excess – the excess of X-rays below 2 keV with respect
to the extrapo- lation of the hard X-ray spectral continuum model – is
a very common feature among type 1 active galactic nuclei (AGN). 
\citet{NodaDone2018} note that
The soft X-ray excess produces most of the ionizing photons, so its
dramatic drop leads to the disappearance of the broad-line region,
driving the ``changing-look'' phenomena.  major difference is that
radiation pressure should be much more important in AGNs, so that the
sound speed is much faster than expected from the gas temperature.
%%
This spectral hardening appears similar to the soft-to-hard state
transition in black hole binaries at $L / L_{\rm Edd} \sim 0.02$
(i.e. $\eta_{\rm Edd} \sim -1.7$, where the inner disc evaporates into
an advection dominated accretion flow, while the overall drop in
luminosity appears consistent with the hydrogen ionization disc
instability.  Crucially \citet{NodaDone2018} make the prediction that
all changing-look AGNs are similarly associated with the state
transition at $L / L_{\rm Edd} \sim$a few per cent.
%%
\citet{JiangYF2014, JiangYF2016, JiangYF2019}.
\citet{JiangYF2019arXiv} use global three dimensional radiation
magneto-hydrodynamic simulations to study the properties of inner
regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$
black hole with mass accretion rates reaching 7\% and 20\% of the
Eddington value.

We investigate this reporting the Eddington ratios of the three
quasars in Table~\ref{tab:Eddington_ratios}.

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_LBol_20191015.png}
   \vspace{-12pt}
   \caption[]{The Baldwin Plot. The bolometric luminosities are from \citet{Kozlowski2017},
     while the REW measurements are from \citet{Hamann2017}.}
  \label{fig:REWvsFWHM}
\end{figure}

\section{Conclusions}
In this paper we have reported on three redshift $z>2$ quasars with
dramatic changes in their \civ\ emission lines, the first
`Changing-Look'' quasars at high redshift.  This is also the first
time the changing-look behaviour has been seen in a high-ionization
emission line.

\begin{itemize}
  \item SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
in their observed optical light curves, and subsequent spectroscopy
shows significant changes in the \civ\ broad emission line, with both
line collapse and emergence being displayed in rest-frame timescales
of $\sim$240-1640 days.
\item Where observed, the profile of the Ly$\alpha$/\nv emission complex
also changes, and there is tentative evidence for changes in the \mgii
line.
\item Although line measurements from the three quasars show large changes
in the \civ\ line flux-line width plane, the quasars are not seen to
be outliers when considered against the full $z>2$ quasar population
in terms of (rest) Equivalent Width and FWHM properties.
\item 
We put these observations in context with recent ``state-change''
models, but note that even in their `low-state', the \civ\ CLQs are
above $\sim10\%$ in Eddington luminosity.
\end{itemize}

Etiam mollis viverra nisi eget aliquet. Aliquam erat volutpat. Vivamus
tristique, nisl eu malesuada semper, libero tortor convallis elit, a
scelerisque orci nisi lacinia turpis. In lacinia ultrices
volutpat. Proin ultrices luctus tellus, in placerat eros tincidunt
id. Ut varius iaculis quam in consequat. Nulla nec orci est, sit amet
Aliquam ac metus nec odio tempus pharetra sed nec diam. Sed eget arcu
nulla. Etiam elementum ultrices ligula, at iaculis libero feugiat
bibendum. Suspendisse potenti. Nam pharetra adipiscing
euismod. Quisque imperdiet dignissim odio, sed volutpat justo
tincidunt eu. Nunc vehicula pharetra suscipit. Integer aliquet pretium
ipsum vel ultrices. Nam rutrum nibh ac quam pulvinar molestie.

\subsection*{Availability of Data and computer analysis codes} 
All materials, databases, data tables and code are fully available at: 
\href{https://github.com/d80b2t/CIV_CLQs}{\tt https://github.com/d80b2t/CIV\_CLQs}.

\section*{Acknowledgements}
NPR acknowledges support from the STFC and the Ernest Rutherford Fellowship scheme. 
%% KESF \& BM are supported by NSF PAARE AST-1153335. 
%% KESF \& BM thank CalTech/JPL for support during sabbatical.  
\\

\noindent
We thank:
\begin{list}{$\circ$}{}  
  \item Andy Lawrence, Mike Hawkins and David Homan for useful discussion. 
\end{list}

This paper heavily used \href{http://www.star.bris.ac.uk/~mbt/topcat/}{TOPCAT} (v4.4)
\citep[][]{Taylor2005, Taylor2011}.
%%
This research made use of \href{http://www.astropy.org}{\tt Astropy}, 
a community-developed core Python package for Astronomy 
\citep{AstropyCollaboration2013, AstropyCollaboration2018}.

Funding for SDSS-III has been provided by the Alfred P. Sloan
Foundation, the Participating Institutions, the National Science
Foundation, and the U.S. Department of Energy Office of Science. The
SDSS-III web site is
\href{http://www.sdss3.org/}{http://www.sdss3.org/}.
%%
SDSS-III is managed by the Astrophysical Research Consortium for the
Participating Institutions of the SDSS-III Collaboration including the
University of Arizona, the Brazilian Participation Group, Brookhaven
National Laboratory, Carnegie Mellon University, University of
Florida, the French Participation Group, the German Participation
Group, Harvard University, the Instituto de Astrofisica de Canarias,
the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins
University, Lawrence Berkeley National Laboratory, Max Planck
Institute for Astrophysics, Max Planck Institute for Extraterrestrial
Physics, New Mexico State University, New York University, Ohio State
University, Pennsylvania State University, University of Portsmouth,
Princeton University, the Spanish Participation Group, University of
Tokyo, University of Utah, Vanderbilt University, University of
Virginia, University of Washington, and Yale University.

This publication makes use of data products from the Wide-field
Infrared Survey Explorer, which is a joint project of the University
of California, Los Angeles, and the Jet Propulsion
Laboratory/California Institute of Technology, and NEOWISE, which is a
project of the Jet Propulsion Laboratory/California Institute of
Technology. WISE and NEOWISE are funded by the National Aeronautics
and Space Administration. No animals were harmed in the production of
this paper, but there was a large spider in NPRs apartment that
``vanished''.

\bibliographystyle{mnras}
\bibliography{tester_mnras}

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

\end{document}

### 2019-11-01 tex/CIV_CLQs.tex
CIV Baldwid effect updated

@@
 \end{figure}
-\subsection{Overall Spectral Evolution}
+\subsection{Emission line evolution}
 Emission line measurements from the catalogues of  \citet{Shen2011}.
@@
 
+\subsection{The \civ\ Baldwin Effect}
+The Baldwin Effect (Baldwin 1977) is an empirical %inverse
+relation between emission-line REWs and continuum luminosity in
+quasars \citep[][]{Shields2007, Hamann2017, Calderone2017}
+%%
+There is an anti-correlation between the emission-line REWs and e.g. 1450\AA\ rest continuum luminosity,
+so that as the underlying UV continuum luminosity increases, the EW decreses,
+see Figure~\ref{fig:CIV_Baldwin}
+The slope $\beta$ is $-0.1997$. 
+Checking with \citet{Kozlowski2017}, using their bolometric luminosity gives a slope of $\beta=-0.251$,
+in line with that from \citet{Hamann2017} ($\beta=-0.23$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 quasars, however, has been less well studied. Reasons for this include
-more massive systems will tend to have longer timescales e.g. with
-$R_{\rm Sch}= 2GM /c^{2}$ and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$ means
-$t_{\rm dyn} \sim 6 G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2}
-$.
+more massive systems will tend to have longer timescales with e.g.
+$t_{\rm dyn} = \sqrt{ R^{3}/GM} \rightarrow  t_{\rm dyn}  \sim M^{2}$
+if e.g. $R_{\rm Sch}= 2GM /c^{2}$.
+%and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$ means e.g $t_{\rm dyn} \sim 6 G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2}.
 
@@
      while the REW measurements are from \citet{Hamann2017}.}
-  \label{fig:REWvsFWHM}
+  \label{fig:CIV_Baldwin}
 \end{figure}
+
+\subsection{Variability around billion solar mass black holes} 
+The Event Horizon Telescope (EHT) mapped the central compact radio
+source of the elliptical galaxy M87 at 1.3 mm \citep{EHT2019_PaperI, EHT2019_PaperII, EHT2019_PaperIII, EHT2019_PaperIV, EHT2019_PaperV, EHT2019_PaperVI} .
+
+The EHT observsations confirm the observed 1.3mm asymmetric ring
+emission is consistent with predictions of strong
+gravitational lensing of synchrotron emission from a hot plasma
+orbiting near the black hole event horizon \citep{EHT2019_PaperV}.
+
+EHT2017 data includes tracks from four separate
+days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{(EHT_PaperIV} timescale is short
+compared to the decorrelation timescale of simulated images, which is
+$\sim$50 $r_{g}$ $c^{-1}$, and smaller than the light-crossing time of the source
+plasma.
+
+From \citet{EHT_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
+\begin{equation}
+R_{s} = 2 r_{g} =  2 GM/c^{2}  = 9.598 \times10^{12} {\rm m}.
+\end{equation}
+giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c = 32 015 {\rm secs}$ (0.37 days).
+%\begin{equation}
+%t_{\rm lt} = R_{s} / c = 32015 {\rm secs}$
+%\end{equation}
+%and a {\it dynamical timescale}, $t_{\rm dyn}$
+%\begin{equation}
+%$t_{\rm dyn}  =  sqrt{ R_{s}^{3}/G M}
+% \end{equation}
+%also (!!!!!) of $t_{\rm dyn}  =  \sqrt{ R_{s}^{3}/G M}$ = 32015 seconds.
+
+$\log_{10} (M_{M87^{*}} / M_{\odot} ) = 9.813$. 
+which is only about double that of J1205+3422 and J2228+2201,
+and a factor of $\sim$6 that of J1638+2827.
+However, M87
 

### 2019-11-01 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py

@@ -20,12 +20,13 @@ cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)
 
 ## Reading in the data
 path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/CLQ_line_measurements/'
-filename  = 'REW_FWHM.dat'
+filename  = 'Baldwin_CIV.dat'
 CLQs      = ascii.read(path+filename)
 
-CLQ_FWHM   = CLQs['FWHM']    / 1000.
-errFWHM    = CLQs['errFWHM'] / 1000.
-CLQ_logREW = np.log10(CLQs['REW'])
+
+CLQ_FWHM    = CLQs['FWHM']    / 1000.
+CLQ_errFWHM = CLQs['errFWHM'] / 1000.
+CLQ_logREW  = np.log10(CLQs['REW'])
 ## have to put the x-errors into log-space
 #log_REW_hi = np.log10(CLQs['REW'] np.log10(CLQs['errREW']))
 #log_REW_lo = np.log10(CLQs['REW']-CLQs['errREW'])
@@ -55,28 +56,50 @@ data = tdata[np.where( (tdata['rew'] > 0.     )     &
                        (tdata['Lbol']   > 0.0))]
 
 ## Setting up variable names
-f1450     = data['f1450']
-alpha_civ = data['alpha_civ']
-REW       = data['rew']        
-FWHM      = data['fwhm']
-redshift  = data['z_dr12']
-log_LBol  = data['LBol']
-log_L1350 = data['L1350']
+f1450_Ham17     = data['f1450']
+alpha_civ_Ham17 = data['alpha_civ']
+REW_Ham17       = data['rew']        
+FWHM_Ham17      = data['fwhm']
+z_dr12          = data['z_dr12']
+log_LBol_Koz17  = data['LBol']
+log_L1350_Koz17 = data['L1350']
+
+
+##    Q S F I T 
+## CONT*__LUM::  1450, 2245, 3000, 4210 or 5100:
+## AGN continuum (Section 2.2) νLν luminosities and their uncertainties, in units of 1042 erg s−1
+## 
+path        = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/QSO_CIV_catalogs/'
+filename    = 'qsfit_1.2.4.fits'
+infile      = path+filename
+sdata_full  = fits.open(infile)
+sdata       = sdata_full[1].data
+
[…]

### 2019-11-01 calculations/rs_M87.py
EHT M87 discussion started...

@@ -1,0 +1,64 @@
+'''
+Calculate the Schwarzschild radius, R_S, that marks the event horizon
+of a nonrotating black hole: 
+    R_{s} = 2 r_{g} =  2 GM/c^{2}  
+
+
+'''
+
+import numpy as np
+
+import astropy.units as u     
+from astropy import constants as const
+
+
+m_M87 = 6.5e9   ## from the EHT papers
+
+## From EHT Paper I::
+## ``When viewed from infinity, a nonrotating Schwarzschild (1916) black
+## hole has a photon capture radius Rc = sqrt(27) rg, where rg = GM/c2 is
+## the characteristic lengthscale of a black hole. The photon capture
+## radius is larger than the Schwarzschild radius RS that marks the
+## event horizon of a nonrotating black hole, RS ≡ 2 rg.
+
+rs =  (const.G * m_M87 * const.M_sun) / (const.c * const.c)
+rs_in_cm = rs*1e2
+
+
+## Eq. 6 from EHT (2019) Paper V:
+## LEdd = 4.pi.GM.c.m_p / sigma_T where, sigma_T is the Thomson cross section
+#
+## Mdot_edd = L_Edd / epsilonn/c^2
+##
+## emission arises from 5rg 
+## mp is the proton mass
+## n_e is electron number density
+
+n_e  = 1.0547e11 / (u.meter  * u.meter  * u.meter )   ##  1.05995e11 m^-3
+
+Mdot            =  4. * np.pi * ((5*(rs/2.))**2) * n_e * const.m_p * (const.c / np.sqrt(5))
+Mdot_solperyer  = (Mdot.value*3.1556952e7)/2e30
+    
+## Mdot quoted from Eq. (5) in EHT Paper V
+Mdot_quoted = 2.7e-3  ## Msol /yr 
+
+## Equation (6) from EHT Paper V
+## epsilon = radidative efficiency 
+
+epsilion = 0.1
+Mdot_Edd = (2.2/epsilion) * (m_M87 / 1e9) 
+
+
+print()
+print(' Schwarzschild radius, R_S, of M87 (using EHT data), is :   ',  rs_in_cm / 1e15 , ' x 10^15 cm')
+print()
+print(' Mdot is: ', Mdot)
+print('   which is : ',  Mdot_solperyer,   ' M_sol / yr')
+print('   vs.      : ',  Mdot_solperyer/Mdot_quoted)
+
+print
[…]

### 2019-11-04 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py
updating Baldwin plot files

@@ -1,9 +1,10 @@
 '''
-A ``hexbin'' plot for the SDSS-III BOSS data from the Hamann et al. (2017) catalog and analysis. 
-This initially concentrated on 'just' f1450 converted into Lum_1450.
-However, matching with the Kozłowski (2017) catalog means we can do the Baldwin plot with LBol directly. 
+A ``hexbin'' plot for the SDSS-III BOSS data from the Hamann et
+al. (2017) catalog and analysis.  This initially concentrated on
+'just' f1450 converted into Lum_1450.  However, matching with the
+Kozłowski (2017) catalog means we can do the Baldwin plot with LBol
+directly.
 '''
-
 
 import numpy as np
 from scipy             import stats
@@ -19,21 +20,17 @@ import matplotlib.lines  as mlines
 cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                         
 
 ## Reading in the data
-path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/CLQ_line_measurements/'
+path      = '../../../data/CLQ_line_measurements/'
 filename  = 'Baldwin_CIV.dat'
 CLQs      = ascii.read(path+filename)
 
 
-CLQ_FWHM    = CLQs['FWHM']    / 1000.
-CLQ_errFWHM = CLQs['errFWHM'] / 1000.
-CLQ_logREW  = np.log10(CLQs['REW'])
-## have to put the x-errors into log-space
-#log_REW_hi = np.log10(CLQs['REW'] np.log10(CLQs['errREW']))
-#log_REW_lo = np.log10(CLQs['REW']-CLQs['errREW'])
-## and then have them as
-#CLQ_asym_xerr = [log_REW_lo, log_REW_hi] 
-log_errREW = np.log10(CLQs['errREW'])
-
+CLQs_FWHM       = CLQs['FWHM']    / 1000.
+CLQs_errFWHM    = CLQs['errFWHM'] / 1000.
+CLQs_logREW     = np.log10(CLQs['REW'])
+CLQs_logerrREW  = np.log10(CLQs['errREW'])
+CLQs_loglineLum = np.log10(CLQs['lineLum']*1e42)   
+    
 
[…]

### 2019-11-04 plots/hexbin_plots/REW_FWHM/REW_FWHM_hexplot.py

@@ -174,7 +174,7 @@ ax.axis([xmin, xmax, ymin, ymax])
 #ax.set_xlabel(r'log$_{10}$(REW)',         fontsize=fontsize)
 #ax.set_xlabel(r'rest EW / ${ \rm \AA }$', fontsize=fontsize)
 ax.set_xlabel(r'Equiv. Width / ${ \rm \AA }$', fontsize=fontsize)
-ax.set_ylabel(r"FWHM / '000 km s$^{-1}$", fontsize=fontsize)
+ax.set_ylabel(r"FWHM / '000 km s$^{-1}$",      fontsize=fontsize)
 
 ## AXES TICK FORMAT
 ax.tick_params(axis='both', which='major', labelsize=labelsize)

### 2019-11-04 tex/CIV_CLQs.tex
tex/CIV_CLQ Acknowledgement update
CIV_CLQs key update

@@
   % \begin{tabular}{lll  cccc r }
-  \begin{tabu}{l ll  lccc c r }
+  \begin{tabu}{l ll  ll cc c r }
     \hline 
@@
 
+\begin{table}
+  \begin{centering}
+    \begin{tabular}{c c l l}
+      \hline
+      \hline
+      Object             & MJD      & Cont. Lumin        &  Cont. slope \\
+      \hline
+                             & 53498   &  40040$\pm$34  & -1.656$\pm$ 0.006 \\
+      J1205+3422    & 58538   &   ---                   &  ---     \\
+                             & 58693   &   ---                    &  ---     \\
+                             &              &                             & \\
+                             & 54553   &  3774$\pm$111   &  -1.472$\pm$0.197   \\
+      J1638+2827    & 55832  &  2433$\pm$14     &  -2.316$\pm$0.051  \\  
+                             & 58583   &  3292$\pm$9       &    -0.541$\pm$0.010 \\
+                             &              &                             &\\
+                            & 56189    &  ---                      &  ---     \\
+    J2228+2201     & 56960   &  7889$\pm$14      &  -1.729$\pm$0.015     \\
+                            & 58693   &  ---                       &  ---     \\
+    \hline
+    \hline
+  \end{tabular}
+  \caption{Quasar continuum $\nu L_{\nu}$ luminosities and slopes, at
+the fixed rest-frame wavelengths 1450\AA\ from QSFIT.  The
+luminosities are in units of 10$^{42}$~erg~s$^{-1}$.}
+  \label{tab:Baldwin}
+  \end{centering}
+\end{table}
+
 %%
@@
   \centering
-  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
+  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
   {figures/CIV_CLQs_REWvsFWHM_20191029.png}
@@
 of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
-of \citet{Hamann2017}. Note the REW logarithmic scaling.}
+of \citet{Hamann2017}. %Note the REW logarithmic scaling.
+}
   \label{fig:REWvsFWHM}
@@
 more massive systems will tend to have longer timescales with e.g.
-$t_{\rm dyn} = \sqrt{ R^{3}/GM} \rightarrow  t_{\rm dyn}  \sim M^{2}$
-if e.g. $R_{\rm Sch}= 2GM /c^{2}$.
-%and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$ means e.g $t_{\rm dyn} \sim 6 G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2}.
+$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.
 
@@
   \centering
-  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_LBol_20191015.png}
+  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
+  {figures/CIV_CLQs_Baldwin_20191104v3.png}
    \vspace{-12pt}
-   \caption[]{The Baldwin Plot. The bolometric luminosities are from \citet{Kozlowski2017},
-     while the REW measurements are from \citet{Hamann2017}.}
+   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
+     commonly referred to as The Baldwin Plot. The continuum luminosities are
+     from \citet{Kozlowski2017},
+     the REW measurements are Table~\ref{tab:Baldwin}.}
   \label{fig:CIV_Baldwin}
@@
 EHT2017 data includes tracks from four separate
-days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{(EHT_PaperIV} timescale is short
+days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{EHT2019_PaperIV} timescale is short
 compared to the decorrelation timescale of simulated images, which is
@@
 
-From \citet{EHT_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
+From \citet{EHT2019_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
 \begin{equation}
@@
 \begin{list}{$\circ$}{}
+  \item  Dr. Giorgio Calderone for discussions to the utility of the QSFit routine and line measurements. 
   \item Andy Lawrence, Mike Hawkins and David Homan for useful discussion.

### 2019-11-05 calculations/rs_M87.py
calculations/rs_M87.py added

@@ -62,3 +62,11 @@ print('   thus Mdot / Mdot_Edd                 is :: ',          (Mdot_solperyer
 print('   eta where eta = log(Mdot / Mdot_Edd) is :: ', np.log10((Mdot_solperyer/  Mdot_Edd)))
 
 print()
+
+
+
+''' 
+ E [Joules] = M [kg]  . c^2   [m^2 s^-2]
+ L [Watts]  = eta  .    Mdot   . c^2
+ L          = 0.1   * ((2.7e-3*2e30)/(24*3600*365.25 ))*(9e16)       
+'''

### 2019-11-05 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py
plots/hexbin_plots/Baldwin/ update

@@ -14,7 +14,9 @@ from astropy.cosmology import FlatLambdaCDM
 
 import matplotlib
 import matplotlib.pyplot as plt
+import matplotlib.mlab   as mlab
 import matplotlib.lines  as mlines
+
 
 ## Setting up the cosmology
 cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                         
@@ -75,8 +77,9 @@ sdata       = sdata_full[1].data
 data_qsofit = sdata[np.where( (sdata['BR_CIV_1549__LUM'] > 0.   )     &
                              (sdata['BR_CIV_1549__EW']   > 0.   ))    ] 
 
-log_L1450_QSFit = np.log10((data_qsofit['BR_CIV_1549__LUM']*1e42))
-log_LCont_QSFit = np.log10((data_qsofit['CONT1__LUM']*1e42))
+log_L1450_QSFit = np.log10((data_qsofit['BR_CIV_1549__LUM'] * 1e42))
+log_LCont_QSFit = np.log10((data_qsofit['CONT1__LUM']       * 1e42))
+Cont1__WAVE     =           data_qsofit['CONT1__WAVE']
 EW_QSFit        =           data_qsofit['BR_CIV_1549__EW']
 log_EW_QSFit    = np.log10( data_qsofit['BR_CIV_1549__EW'])
 
@@ -283,4 +286,60 @@ ax.text(0.31, 0.91, r'$\beta=%.4f$' % (slope, ), fontsize=14, color='r',
 
 ## SAVING THE FIGURE
 plt.savefig('CIV_CLQs_Baldwin_temp.png', format='png')
+plt.close()
+
+
+
+
+##
+## Just keen to see what the distribution of CONT1__WAVE -- from QSFit
+## and Calderone et al. (2017) -- is.  This is the value of where the
+## continuum luminosities and slopes havw been computed. There are
+## five such quantities whose values are equally spaced in the
+## logarithmic wavelength range [λmin , λmax ];
+## 
+##   S E T T I N G   U P   T H E    P L O T
+##
+matplotlib.rc('text', usetex=True)
+fig, ax = plt.subplots(figsize=(5, 5), dpi=80, facecolor='w', edgecolor='k')  
+
+## Adjusting the Whitespace for the plots
+left   = 0.16   # the left side of the subplots of the figure
+right  = 0.96   # the right side of the subplots of the figure
[…]

### 2019-11-05 plots/MJD_Eddington/mjd_vs_Eddington.py
MJD_Eddington plots, data added

@@ -1,0 +1,216 @@
+'''
+
+Plot of MJD of Quasar observation, and Eddington ratio, 
+e.g. from Shen et al. (2011) or 
+
+'''
+import math
+import numpy as np
+
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.lines  as mlines
+
+from matplotlib import colors as mcolors
+from astropy.io import ascii
+from astropy.io import fits
+
+##
+##  S h e n   et al.  (2 0 1 1)   D R 7 Q  
+##
+path = '../../data/QSO_CIV_catalogs/'
+filename ='Shen_dr7_bh_May_2010.fits'
+infile = path+filename
+
+## Okay, what we really want to do ;-)
+#data_table = pyfits.getdata(infile)
+data_in    = fits.open(infile)
+data_table = data_in[1].data
+
+## Quick check on the format/dimensions of the FITS table file...
+print(type(data_table), '\n')
+print('The number of rows of is.... ',     data_table.shape,  '\n')
+print('The number of columns is...  ', len(data_table.names), '\n\n')
+
+
+## Making some senible selections and cuts 
+mjd_full    = data_table.field('MJD')
+logtau_full = data_table.field('LOGEDD_RATIO')
+
+dr7q        = data_table[np.where(data_table['LOGEDD_RATIO'] > -9.0)]
+dr7q_mjd    = dr7q['MJD']
+dr7q_logtau = dr7q['LOGEDD_RATIO']
+dr7q_tau    = (10**dr7q['LOGEDD_RATIO'])*100
+
+    
+## The data for our CIV CLQs
+path   = '../../data/CLQ_line_measurements/'
+infile = 'MJD_Eddington.dat'
+CLQs   = ascii.read(path+infile)
+
+
+## Setting up the plot
+fig, ax = plt.subplots(figsize=(10.0, 6.0), dpi=80, facecolor='w', edgecolor='k')   # was 14.0, 8.0
+
+## Adjusting the Whitespace for the plots
+left   = 0.08   # the left side of the subplots of the figure
+right  = 0.96   # the right side of the subplots of the figure
+bottom = 0.12   # the bottom of the subplots of the figure
+top    = 0.96   # the top of the subplots of the figure
+wspace = 0.22   # the amount of width reserved for blank space between subplots
[…]

### 2019-11-07 plots/spectral/CIV_fits_notes.tex
examining the CIV QSFIT line fits

\documentclass[11pt,a4paper]{article}

\input{../../tex/format}

\newcommand{\qsfit}{{\sc QSFit}}

\begin{document}

\noindent
So, for br\_CIV\_1549 (NCOMP=1) I start with something like::
  \begin{center}
    \begin{tabular}{l   r    r   r  r  r  r  r  r    }
      \hline
                   & & & & & & &    \\
   LUM        & LUM\_ERR &  FWHM   & FWHM\_ERR   &   VOFF  & VOFF\_ERR  &    EW         &  EW\_ERR  \\
   510.57   &  13.16       & 9592.9  &  287.34         &   1171.7 &  73.785      &     15.898  & 0.40976    \\
                   & & & & & & &    \\
      \hline
\end{tabular}
\end{center}
from the \qsfit{} output log, e.g. from {\tt
spec-2089-53498-0427\_QSFIT\_z2p068.log}.

\begin{equation}
  \mu  = 1548 \; \AA
\end{equation}
Assuming $c$ has units of km s$^{-1}$, $\mu$ is the nominal working wavelength (1548 \AA\ for \civ\ )
\begin{equation}
    {\rm FWHM}_{\lambda}  = ( 9592.9  /3 \times 10^{5}) * \mu 
  \end{equation}
  $\Rightarrow$
\begin{equation}
  {\sigma}     =   {\rm FWHM}_{\lambda}  / 2. (\sqrt(2 * \ln(2)))
\end{equation}
and I now just have $\mu$ and $\sigma$ to plug into the Gaussian PDF: 
\begin{equation}
  f(x\mid \mu ,\sigma ^{2})={\frac {1}{\sqrt {2\pi \sigma ^{2}}}}e^{-{\frac {(x-\mu )^{2}}{2\sigma ^{2}}}}
\end{equation}
and where $x$ is in Angstroms.
I'm assuming $x$ will be $x' = x - V_{\rm Off}$ at some point, but I'm not there yet(!).
% \begin{lstlisting}
 % mu = 1549.
 % ##  $c$ in km/s; nominal wavelength in Ang
%linefit_x =  np.linspace(mu - 3*qsfit_sigma[ii], mu + 3*qsfit_sigma[ii], 100)
%linefit_y  = stats.norm.pdf(linefit_x, mu, qsfit_sigma[ii])
%\end{lstlisting}

\vspace{16pt}
\noindent
Now, for the line luminosites, I have: 
\begin{eqnarray}
     f &  = &   L / (4 \; \pi   \;  D_{L}^{2})  \\
  &  = &   (5.1057 \times 10^{44} [{\rm erg  \;  s^{-1}}] ) /   (4 \; \pi \; ((5.094 \times 10^{28})^{2} [{\rm cm}])) \\
         & = & 1.56 \times 10^{-14}  [{\rm erg  \;  s^{-1} cm^{-2}} ]
\end{eqnarray}
where $L$ is (line) luminosity, $D_{L}$ is Luminosity Distance
($z=2.071$), $f$ is flux.  So I think I'm still missing 'something'
here as the e.g. SDSS data are in $10^{-17} {\rm erg \; s^{-1}
cm^{-2}}$, where the peak \civ\ luminosity for J1205+3422 (MJD 53498)
is around 45 in these units.

\vspace{34pt}
\noindent
Python code (pseudo or actual!)::  
\begin{lstlisting}
import matplotlib.pyplot as plt
import numpy as np
import scipy.stats as stats
import math

mu        = 0
variance = 1
sigma      = math.sqrt(variance)
x         = np.linspace(mu - 3*sigma, mu + 3*sigma, 100)
plt.plot(x, stats.norm.pdf(x, mu, sigma))
plt.show()
  \end{lstlisting}

\end{document}

### 2019-11-07 plots/spectral/CIV_fits.py

@@ -1,0 +1,201 @@
+'''
+
+Plotting the observed CIV emission lines from the z~2 CLQs and
+comparing those to the e.g. QSFIT model parameters
+
+'''
+
+import math
+import numpy as np
+import scipy.stats as stats
+
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '../../data/QSFIT/'
+
+
+##  J 1 2 0 5 +  3 4 2 2 
+sdssname   = 'spec-2089-53498-0427.fits'
+J12_first  = fits.open(path+sdssname)
+J12_second = ascii.read(path+'J1205p3422_58538.dat')
+J12_third  = ascii.read(path+'J1205p3422_58693.dat')
+
+J12_redshift    = 2.071
+J12_first_flux  =       J12_first[1].data.flux
+J12_first_wave  = (10**(J12_first[1].data.loglam)) / (1 + J12_redshift)
+J12_second_wave = J12_second['wavelength'] / (1 + J12_redshift)
+J12_second_flux = J12_second['flux'] 
+J12_third_wave  = J12_third['wavelength']  / (1 + J12_redshift)
+J12_third_flux  = J12_third['flux']    
+
+
+##  J 1 6 3 8 +  2 8 2 7
+sdssname   = 'spec-2948-54553-0614.fits'
+J16_first  = fits.open(path+sdssname)
+bossname   = 'spec-5201-55832-0178_v5_10_0.fits'
+J16_second = fits.open(path+sdssname)
+J16_third  = ascii.read(path+'J1638p2827_58583.dat')
+
+J16_redshift    = 2.182
+J16_first_flux  =        J16_first[1].data.flux
+J16_first_wave  = (10**( J16_first[1].data.loglam))  / (1 + J16_redshift)
[…]

### 2019-11-07 tex/other_tex/201909/CIV_CLQs_20190926.tex
CIV tex/ tidy up

--- 2019-10-31 tex/CIV_CLQs.tex
@@
 \author[Bercow]
-{%The RH John~S.~Bercow, MP, {\it et al.} 
-Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
- Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
-\newauthor and Daniel Stern$^{6}$ 
+{The RH John~S.~Bercow, MP, {\it et al.} 
+%Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
+%K. E. Saavik Ford$^{2,3,4}$,  Matthew Graham$^{5}$,  Barry McKernan$^{2,3,4}$,  
+%\newauthor Daniel Stern$^{6}$, 
 \\
 % List of institutions
-%$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
-$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
-$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
-$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
-$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
-$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
-$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
+$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
+%$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
+%$^{2}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
+%$^{3}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
+%$^{4}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
+%$^{5}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
+%$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
 }
@@
 \hypersetup{draft}
-
 \begin{document}
@@
 redshift.  This is also the first time the changing-look behaviour has
-been seen in a high-ionization emission line.
+been seen in a high-ionization emissions line.
 %%
@@
 in the \civ\ line flux-line width plane, the quasars are not seen to
-be outliers when considered against the full $z\sim2$ quasar population
+be outliers when considered against the full $z>2$ quasar population
 in terms of (rest) Equivalent Width and FWHM properties.
@@
 models, but note that even in their `low-state', the \civ\ CLQs are
-above $\sim$10\% in Eddington luminosity.
+above $\sim10\%$ in Eddington luminosity.
 \end{abstract}
@@
 the subsequent mismatch in the expected ``viscous'' timescale, which
-for a $\approx$10$^{7}$ M$_{\odot}$ central supermassive black hole
-(SMBH) is $\sim$hundreds of years, was noted over 30 years ago
-\citep[e.g.][]{Alloin1985}. However, with new photometric light-curve
-and repeat spectroscopic data, the desire for a deeper understanding
-of AGN accretion disk physics has been recently re-invigorated the
-field \citep[e.g.][]{Lawrence2018, Antonucci2018}.
+for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was
+noted over 30 years ago \citep[e.g.][]{Alloin1985}. However, with new
+photometric light-curve and repeat spectroscopic data, the desire for
+a deeper understanding of AGN accretion disk physics has been recently
+re-invigorated the field \citep[e.g.][]{Lawrence2018, Antonucci2018}.
 
@@
 their first optical identification
-\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic changes
-in the broad emission lines (BELs) of quasars has only recently been
-identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
-``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
-have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}. The
-community uses both these terms as a cover for the underlying
+\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic
+changes in the broad emission lines (BELs) of quasars has only
+recently been identified \citep[e.g., ][]{LaMassa2015}.  Samples of over
+100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars
+(CSQs) have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}.
+The community uses both these terms as a cover for the underlying
 physics. For sake of argument, ``Changing Look'' quasars can
@@
 ``Changing State'' quasars (CSQs) have a `state-transition' similar to
-that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019}. In
-this paper, we use the term `Changing Look', as we are currently
-agnostic, and somewhat ignorant, to the underlying physical processes.
+that in Galactic X-ray binaries \citep[][]{NodaDone2018,
+Ruan2019}. In this paper, we use the term `Changing Look', as we are
+currently agnostic, and somewhat ignorant, to the underlying physical
+processes.
 
@@
 (recombination) Balmer emission line properties with particular
-attention paid to the H$\beta$ emission line, observed from optical
-spectroscopy. Recent work \citep{Guo2019, Homan2019} report on discoveries
-of \mgii Changing-look AGN. However, current CLQ studies have been at
+attention paid to the H$\beta$ emission line, usually observed from
+optical spectroscopy.  As such, current CLQ studies have been at
 redshifts $z<1$.
@@
 
-\begin{table*}
-  \centering
-  \begin{tabular}{r l   r ll   r r r r}
-    \hline 
-    \hline 
-    Object                           & \multirow{3}{*}{Redshift}  &                       & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date} & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
-    R.A.
-/ deg                     &                                         &   {$g$-band}   &                                 &                                  &                                               &  Time           & Spectrum                 & \\
-    Decl.
-/ deg                   &                                         &    magnitude   &                                &                                   &                                              &  / seconds    & Plate-FiberID  & \\
-    \hline  
-                                         &                                         &                        &                &                            &                    &                              &                              & \\
-    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             &  8057                  & 2089-427             & \\
-    181.436164                  & 2.071                              &                         &  58538   &  2019-Feb-24    & DBSP            &  1800                  &  ---                      &  Average conditions \\
-    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2400                   &  ---                      &   \\
-                                         &                                       &                          &                &                          &                    &                               &                              & \\
-    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS           &   4801                    &  2948-614              & \\
-    249.720558	                 &  2.186$\pm$0.0007     &                          &  55832    & 2011-Sep-28     & BOSS            &   3600                   &  5201-178            & \\
-    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10     & LRIS              &  1800                   &  ---                             & \\
-                                        &                                      &                          &                &                            &                    &                              &                                & \\
-    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                &  56189    & 2012-Sep-19     & BOSS             &  2700                 &   6118-720          & \\
-    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30     & BOSS             &  4500                  &   7582-790          & eBOSS reobservation \\
-    +22.017478                &                                      &                          &  58693    & 2019-Jul-29       & DBSP             & 2400                   &    ---                        &    \\
-                                       &                                       &                          &               &                            &                   &                              &                            & \\
-    \hline \hline   
-  \end{tabular}
-  \caption{
-    Details of our spectroscopic observations.
-    Redshift and redshift errors from SDSS SkyServer for SDSS, BOSS and eBOSS spectra. 
-    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and  eBOSS spectra have $\mathcal{R}\sim$2,000.
-    DBSP: Double Spectrograph on the Palomar 200-inch telescope.
-    LRIS:  Low Resolution Imaging Spectrometer on Keck I 10m telescope.
-    %  2019-Feb-24    & DBSP            &  2$\times$900 f
-    %  2019-Jul-29     & DBSP            &  2$\times$1200
-    %  2019-Apr-10     & LRIS              &  2$\times$900
-    %& 2019-Jul-29       & DBSP             & 2$\times$1200
-  } 
-  \label{tab:obs_notes}
-\end{table*}
-
 Here, we report on three quasars  
@@
 In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
-the \civ\ doublet \citep{Kramida2018}.  The 1548.202 and 1550.774 \AA\
-emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
-transition, split by total angular momentum $J= 3/2$ and $1/2$,
-resulting in energies 64,591 cm$^{-1}$ and 64,484 cm$^{-1}$,
-respectively \citep[e.g.][]{Moore1993}. The transition probabilities
-of the the 1548 and 1550\AA\ lines are $A_{ki}= 2.65\times10^{8}$ and
-2.64$\times10^{8}$ s$^{-1}$.
-
-The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. Using the
+the \civ\ doublet \citep{Kramida2018}. The ground state of carbon is
+1$s^2$ 2$s^2$ 2$p^2$.  Using the
 \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
@@
 \civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
-itself. This energy corresponds to a thermal temperature of $T
-\gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
-X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).  \ciii is the
-1$s2$2$s$2$p$ $^{3}$P$^{\circ}$ to 1$s^{2}$2$s^{2}$ $^{1}$S transition
-(with $J=1\rightarrow0$) resulting in an energy of 52,390.75 cm$^{-1}$ and
-a transition probability of $A_{ki} = 1.14\times10^{2}$ s$^{-1}$ \citep{Wiese1996}.
+itself. The 1548.202 and 1550.774 \AA\ emission doublet is created by
+the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition with energies 64,484
+cm$^{-1}$ and 64,591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.
 
@@
 
-\citet{Wilhite2006} examine the variability of a C~\textsc{iv} sample
-of 105 quasars observed at multiple epochs by the Sloan Digital Sky
-Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
-find a strong correlation between the change in the C~\textsc{iv} line
-flux and the change in the line width, but no correlations between the
-change in flux and changes in line center and skewness.  These authors
-find that the relation between line flux change and line width change
-is consistent with a model in which a broad line base varies with
-greater amplitude than the line core. The C~\textsc{iv} lines in these
-high-luminosity quasars appear to be less responsive to continuum
-variations than those in lower luminosity AGN.  \citet{Wilhite2006}
-find no evidence for variability of the well known blueshift of the
-C~\textsc{iv} line with respect to the low-ionization
-Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects.
+\citet{Wilhite2006} examine
+the variability of a C~\textsc{iv} sample of 105 quasars observed at
+multiple epochs by the SDSS.  They find a strong correlation between
+the change in the C~\textsc{iv} line flux and the change in the line
+width, but no correlations between the change in flux and changes in
+line center and skewness.  These authors find that the relation
+between line flux change and line width change is consistent with a
+model in which a broad line base varies with greater amplitude than
+the line core. The C~\textsc{iv} lines in these high-luminosity
+quasars appear to be less responsive to continuum variations than
+those in lower luminosity AGN.  \citet{Wilhite2006} find no evidence
+for variability of the well known blueshift of the C~\textsc{iv} line
+with respect to the low-ionization Mg~\textsc{ii}$\lambda$2798 line in
+the highest flux objects.
 
@@
 model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
-Proga2000}, with one dominating over the other depending on the shape
+Proga2000}.  with one dominating over the other depending on the shape
 of the SED \citep[][strong \civ\ EQW indicates a more ionizing SED and
-large \civ\ blueshift indicating a less ionizing SED ]{Leighly2004b}.
+large \civ\ blueshift indicating a less ionizing SED]{Leighly2004b}.
 
 The Sloan Digital Sky Survey Reverberation Mapping Project
-\cite[SDSS-RM; ][]{Shen2015} has a monitored $\sim$350 quasars with
+\cite[(SDSS-RM)][]{Shen2015} has a monitored $\sim$350 quasars with
 \civ. Noting the biases associated with \civ Emission Line Properties
@@
 accurate indicator of the Eddington ratio or quasar SED.
+%%
 Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}.
-\citet{Dyer2019} provide a detailed analysis of 340 quasars at high-redshift
-($1.62<z<3.30$) from the SDSS-RM project, which we will compare our
-results to.
 
-%%   P a p e r    O v e r v i e w
 The purpose of this paper is, for the first time, to access and 
@@
 at 3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively
-\citep{Cutri2011}.
-We adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73$,
-$\Omega_{\rm M} = 0.27$, and $h = 0.71$ in order to be consistent with
-\citet{Hamann2017}. As a guide this cosmology has a $z=2.000$
-comoving radial distance of 5244.3 Mpc, a $\sim$1.25\% difference
-compared to 5179.0 Mpc from $\Omega_{\Lambda} = 0.70$, $\Omega_{\rm M}
-= 0.30$, and $h = 0.70$ that is used in \citet{Shen2011}.
+\citep{Cutri2011}. We choose the cosmological parameters
+$\Omega_{\Lambda} = 0.7$, $\Omega_{\rm M} = 0.3$, and $h = 0.7$ in
+order to be consistent with \citet{Shen2011}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}
+  \centering
+  \begin{tabular}{r  r  r r r   r r r r}
+    \hline 
+    \hline 
+    Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{$g$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
+    R.A.
+/ deg                   &                                         &                                                          &                                 &                                   &                                               &  Time           & Spectrum                 & \\
+    Decl.
+/ deg                 &                                         &                                                          &                                &                                     &                                              &  / seconds    & Plate-FiberID  & \\
+    \hline 
+                                   &                                          &                        &             &                            &                    &                             &                              & \\
+    J120544.7+342252.4  & 2.068$\pm$0.0003          &   18.27             & 53498  &  2005-May-08   & SDSS             & tbd                          & 2089-427             & \\
+    181.436164          & 2.071                               & {\bf 17.99?}   & 58538  &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions? \\
+    +34.381229           &                                        &                          & 58693  &  2019-Jul-29     & DBSP            &  2$\times$1200   &                              &   \\
+                                   &                                        &                          &              &                          &                   &                                &                              & \\
+    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77               & 54553 & 2008-Mar-28     & SDSS             & tbd                          &  2948-614              & \\
+    249.720558	             &  2.186$\pm$0.0007      &                           & 55832  & 2011-Sep-28     & BOSS            &   3603                  &  5201-178            & \\
+    +28.452159             &  2.182                           &                           & 58583 & 2019-Apr-10      & LRIS              &  2$\times$900    &                              & \\
+                                   &                                      &                          &              &                           &                   &                              &                                & \\
+    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                 & 56189 & 2012-Sep-19      & BOSS             &  2702                 &   6118-720          & \\
+    337.078194             & 2.222$\pm$0.0004      &                          & 56960 & 2014-Oct-30      & BOSS             & tbd                         &   7582-790          & QSO1-REOBS \\ 
+    +22.017478            &                                      &                          & 58693 & 2019-Jul-29        & DBSP              & 2$\times$1200  &                           &    \\
+                                   &                                     &                           &            &                             &                   &                              &                            & \\
+    \hline \hline   
+  \end{tabular}
+  \caption{
+    Details of our spectroscopic observations. 
+    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and
+    eBOSS spectra have $\mathcal{R}\sim$2,000.  DBSP is the
+    $\mathcal{R}\sim$1,000-10,000 resolution Double Spectrograph for the
+    Palomar 200-inch telescope.  LRIS is the Low Resolution Imaging
+    Spectrometer on the Keck I 10m telescope.} 
+  \label{tab:obs_notes}
+\end{table*}
 \section{Data}
-Our high-$z$ CLQs were identified as follows.  We selected all 64,774
-SDSS DR15 sources with $z > 0.35$ classified as `QSO', having at least
-two spectra separated by at least 100 days, and with a corresponding
-CRTS light curve. We fitted a damped random walk to the CRTS data via
-Gaussian process regression and the photometric magnitudes at the
-epochs of the SDSS spectra for a given source are predicted. Those
-where $|\Delta V| > 0.3$ are then selected for visual
-inspection. Three quasars SDSS J120544.7+342252.4 (hereafter
-J1205+3422), SDSS J163852.93+282707.7 (hereafter J1638+2827) and SDSS
-J222818.76+220102.9 (hereafter J2228+2201), satisfied these selection
-criteria and showed interesting or dramatic emission line behaviour.
+%% \subsection{Selection/Identification}
+{\bf MJG to write a few notes on how the CIV CLQs were identified} 
+lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam
+porta sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
+
+SDSS J120544.7+342252.4  (hereafter J1205+3422), 
+SDSS J163852.93+282707.7 (hereafter J1638+2827) and
+SDSS J222818.76+220102.9 (hereafter J2228+2201). 
+Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
+pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
+id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
+dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
+euismod. Cras vel auctor neque. Nam quis diam risus.
 
@@
   %% trim=l b r t
-  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
-  {figures/J1205+3422_landscape_20191024.png}
-  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
-  {figures/J1638+2827_landscape_20191024.png}
-  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
-  {figures/J2228+2201_landscape_20191024.png}
+  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
+  {figures/J1205+3422_landscape_20190920.png}
+  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
+  {figures/J1638+2827_landscape_20190920.png}
+  \includegraphics[width=16.7cm, trim=0.0cm 0.0cm  0.2cm 0.1cm, clip]
+  {figures/J2228+2201_landscape_20190920.png}
   \vspace{-12pt}
@@
 Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
-Abolfathi2018, Paris2018}.  These quasars were targetted via a range
-of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
-Myers2015}. The SDSS, BOSS and eBOSS data are supplemented by
-spectra from the Low Resolution Imaging Spectrometer (LRIS) on the 10m
-Keck {\sc I} telescope \citep{Oke1995}.  and the Double Spectrograph
-(DBSP) instrument on the Palomar {\it Hale} 5m telescope.
+Abolfathi2018, Paris2018}.  These quasars were targetted via a range of
+techniques and algorithms \citep[][]{Richards2002, Ross2012,
+Myers2015}.  These data are supplemented by spectra from the Low
+Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I}
+telescope \citep{Oke1995}.  and the Double Spectrograph (DBSP)
+instrument on the Palomar {\it Hale} 5m telescope.
 
-\subsection{Emission Line and Power-law slope measurements}
-We use the measured quasar emission line properties from several catalogues: 
-\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017} and
-\citet{Calderone2017}.
+\begin{table*}
+\begin{tabular}{ l rrrr rrrr rrrr rrrr rrrr rr|}
+\hline
+\hline 
+Object (MJD)               & $f$1450 & $\alpha_{\rm C IV}$    & $\alpha$    & REW                       & cREW   &  wREW  & FWHM              & cFWHM  &  wFWHM  & $\sigma$     \\
+\hline 
+J1638+2827 (55832) & 1.4659    & -3.3547             & -4.026$\pm$0.452 & 42.76$\pm$1.96  & 26.72  & 16.03  & 5210$\pm$226 & 4651      & 13444    & 3702          \\
+J2228+2201 (56189) & 0.5101    & -1.5931             & -0.657$\pm$0.004 & 42.18$\pm$5.59  &  6.42   & 35.76  & 2994$\pm$620 & 1458      &   7636    & 3002           \\
+\hline
+\end{tabular}
+ \caption{
+Measured line values using the methods and catalogue from \citet{Hamann2017}. 
+\noindent {\tt f1450} = flux in the uncorrected BOSS spectrum at 1450 \AA\ rest (10$^{-17}$ ergs s$^{-1}$ cm$^{-2}$ \AA$^{-1}$) used to anchor the power law continuum fits beneath \civ\ and \nv , 
+                                     e.g., $f_{\lambda} = f_{1450}\, (\lambda /1450{\rm \AA})^{\alpha}$; 
+\noindent {\tt $\alpha_{\rm C IV}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) measured from the BOSS spectrum on either side of \civ ; 
+\noindent {\tt $\alpha$}                            = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) between 1350 \AA\ and 2200 \AA\ in the flux corrected BOSS spectrum; 
+\noindent {\tt REW} = \civ\ REW (\AA ) from the line profile fit;
+\noindent {\tt cREW} = \civ\ REW (\AA ) for the core Gaussian component;
+\noindent {\tt wREW} = \civ\ REW (\AA ) for the wing Gaussian component; 
+\noindent {\tt FWHM} = \civ\ FWHM (km/s) from the line profile fit; 
+\noindent {\tt fwhmc} = \civ\ FWHM (km/s) for the core Gaussian only.
+\noindent {\tt fwhmw} = \civ\ FWHM (km/s) for the wing Gaussian only.
+\noindent {\tt $\sigma$} = \civ\ velocity dispersion (km/s) measured from the profile fit \citep{Peterson2004}.
+Errors were given are 1$\sigma$ uncertainties. 
+} 
+ \label{tab:Ham17_lines}
+\end{table*}
 
-\citet{Shen2011} present a compilation of properties of the 105,783
-quasars in the SDSS Data Release 7 (DR7) quasar catalog \citep[DR7Q;
-][]{Schneider2007}. \citet{Shen2011} report non-zero \civ\ FWHM and
-EWs for approximately half (51,501) of the full DR7Q, and non-zero
-\mgii FWHM and EWs for 80\% (84,183) of the DR7Q quasars).
+\begin{table*}
+\begin{tabular}{ l rrr rrr rrr rrr}
+\hline
+\hline
+  \multicolumn{1}{c}{Object (MJD)} &
+  \multicolumn{1}{c}{$M_{\rm I}(z=2)$} &
+  \multicolumn{1}{c}{$\log$($L_{\rm Bol} / {\rm erg s}^{-1}$} &
+  \multicolumn{1}{c}{$\log(L_{\rm CIV})$} &
+  \multicolumn{1}{c}{FWHM} &
+  \multicolumn{1}{c}{EW} &
+  \multicolumn{1}{c}{$\alpha$} &
+  \multicolumn{1}{c}{$\log$BH } &
+  \multicolumn{1}{c}{Edd. ratio, \%)} \\
+\hline
+  J1205+3422 (53498)   & 
+  -27.742                      & 47.22$\pm$0.004    &    %46.37$\pm$0.009    & 46.634$\pm$0.004   & 44.896$\pm$0.013 & 
+44.896$\pm$0.014     &   5230$\pm$219          & 30.1$\pm$1.21        &  -1.467$\pm$0.076    &  % & 27.59                         & 1118$\pm$133.5 & 
+  9.494$\pm$0.036    &  42 \\
 %%
+ J1638+2827 (54553)   & 
+ -26.750                      & 46.17$\pm$0.040    & %45.50$\pm$0.086      & 45.586$\pm$0.040 & 44.449$\pm$0.036   & 
+44.449$\pm$0.036    &  4180$\pm$736          & 100.5$\pm$11.9      & -0.137$\pm$0.677    &   % & 4.630                      & 680$\pm$133.5         & 
+  8.743$\pm$0.154     & 21  \\
+\hline
+\hline
+\end{tabular}
+ \caption{
 Measured line values using the methods and catalogue from
@@
 virial BH mass.
+}
+ \label{tab:Shen11_lines}
+\end{table*}
 
-\citet{Calderone2017} present the Quasar Spectral Fitting (QSFIT)
-software package which among other quantities provides luminosity
-estimates as well as width, velocity offset and equivalent width of 20
-emission lines, including \civ, \ciii and \mgii.  We attempt to process and fit
-all nine spectra using the lastest version (v1.3.0) of the QSFIT
-\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online calculator}
-and setting $E(B-V)=0.00$.
-
-\citet{Hamann2017} investigate in robust detail the UV continuum and
-the \civ\ (and \nv $\lambda$1238, 1242 \AA\ ) emission lines for over
-200,000 quasars in BOSS DR12Q \citep{Paris2017}.  The quasar redshift
-are limited to the range $1.53 \leq z \leq 5.0$ so that \civ\ and the
-adjacent continuum are covered by BOSS. These measurements provide
-line profile information and flux ratios\footnote{This emission-line
+\subsection{Line Properties}  
+We use the measured quasar emission line properties from
+\citet{Shen2011} and \citet{Hamann2017}. \citet{Hamann2017} in
+particular investigate in robust detail the UV continuum and the \civ\
+(and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000
+quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line
 catalog can be downloaded from
 \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
-\citet{Hamann2017} was focused on $z\geq2$ quasars and specifcally
-their \civ properties in order to understand the high-$z$ ``Extremely
-Red Quasar'' population \citet{Ross2015, Zakamska2016, Perrotta2019,
-Zakamska2019}.  As such, these measurements can be taken as the `gold
-standard' for \civ line measurement, though this is only for two out of
-our nine spectra.
-
-When using the \citet{Shen2011} catalogue, we report line luminosity,
-FWHM, rest-frame equivalent width, and their errors for the whole
-\mgii profile (this catalogue also quotes values for just the broad
-\mgii component, but the differences for our objects is
-negligible). The line luminosities in \citet{Calderone2017} are given
-in units of $10^{42}$ erg s$^{-1}$, while the line luminosities in
-\citet{Shen2011} are in units of $\log(L)$.  We do not report the
-\citet{Shen2011} error on the line luminosity.
-
-Power-law continuum slopes, $\alpha$, where $f_{\lambda} \propto
-\lambda^{\alpha}$, are also reported in these catalogues and from
-QSFit.  We quote the most appropriate value given the emission line
-wavelength.
+The quasar redshift are limited to the range $1.53 \leq z \leq 5.0$ so
+that \civ\ and the adjacent continuum are covered by BOSS. These
+measurements provide line profile information and N V/C IV flux
+ratios.
 
 \subsection{Multi-wavelength properties}
-Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning of the
-Wide-field Infrared Survey Explorer (WISE) mission \citep[2010
+We use data from the beginning of the WISE mission \citep[2010
 January; ][]{Wright2010} through the fifth-year of NEOWISE-R
@@
 \section{Results}
-\subsection{Overall Spectral Evolution}
-Figure~\ref{fig:civ_clqs} presents the optical and infrared light
-curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
-shows the spectra for each epoch, with the MJD of observation given by
-the dashed vertical lines in the light curves.
-
-For J1205+3422, our spectral observations cover 5195 days observed, 1691 days
-in the rest-frame. For J1205+3422 is identified in SDSS as a bright
-$g\approx18.0$, blue-sloped quasar with broad \siiv, \civ, \ciii and
-\mgii observed in the initial spectrum (MJD 53498; 2005-May-08). \ciii
-and \civ\ are seen to have large blueshifts of $\approx$2600$\pm$150
-and $\approx$1150$\pm$100 km s$^{-1}$, respectively.  By the time the
-2019 spectra were taken (MJD 58538, 2019-Feb-24 and MJD 58693
-2019-Jul-29), however, the light curve has dropped by $\sim$1.5
-magnitudes and the spectra are significantly less steep.  While \lya
-and \nv are detectable in both the MJD 58538 and MJD 58693 DBSP
-spectra, \civ\ has all but disappeared in the MJD 58693 spectrum.  The
-broad \ciii emission has disappeared between the 2005 and 2019
-spectra. {\it The changes in \civ\ and \ciii going from broad emission to
-barely detectable have on the timescales of $\approx$50 days in the rest-frame.}
-
-For J1638+2827, our spectral observations cover 4030 days observed, 1265 days
-in the rest-frame. Here, in the initial epoch spectrum, \civ\ is broad
-and bright, as is \ciii. However, just over 400 days in the rest-frame
-later, the broad \civ\ and \ciii BEL have to faded, the continuum
-slope around 1400\AA\ has changed from $\approx$-1.48 to
-$\approx$-2.25, but the \lya/\nv emission complex is very similar in
-shape and line flux intensity. Around 870 days in the rest-frame after
-the second spectral epoch, \lya, \nv, \civ, \ciii and \mgii are all
-apparent and broad, with \mgii being seen for the first time at high
-signal-to-noise. The light curve is consistent with this spectral
-brightening, increasing from around $\sim$19.5-20.5th magnitude to
-$\sim$18.5 in the optical band. An absorption feature between  \lya and \nv
-is seen in all three spectral epochs.
-
-For J2228+2201, our spectral observations cover 2504 days observed,
-778 days in the rest-frame. Over the course of 240 days in the rest-frame, \civ\ and \ciii both {\it emerge} as BELs and
-the standard UV/blue continuum slope increases in flux.
-Then, over the course of 538 days in the rest-frame, the broadline emission, while still
-very present, reduces in line flux the UV/blue continuum diminishes,
-though is still more luminous than the initial BOSS spectrum.
+Figure~\ref{fig:civ_clqs} presents the threes high-$z$ CLQ quasars. 
+%%
+%%
+For J1205+3422, over the course of 5040 days observed, 1640 days in the
+rest-frame. 
+For J1638+2827, over the course of 1279 days observed, 400 days in the
+rest-frame, the broad \civ\ and \ciii BEL start to fade.  For
+J2228+2201, over the course of 771 days observed, 240 days in the
+rest-frame, broad \civ\ and \ciii BELs both emerge and the standard
+UV/blue continuum slope increases in flux.  the UV/blue continuum
+diminishes and the shape of \lya changes.
+%%
+Gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
+cursus, dui nisl egestas augue, non fermentum nisl est nec
+nisi. Vestibulum nec mi justo, eget dapibus velit.
 
@@
 \end{figure}
-\subsection{Overall Spectral Evolution}
-Emission line measurements from the catalogues of  \citet{Shen2011}.
-\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of \citet{Calderone2017}
-are presented in Table~\ref{tab:LineMeasurement}.
-%%
 From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
@@
 
-The Balmer series in hydrogen is due to the recombination cascade
-between different principal quantum numbers $n$, and
-the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
-%(and assuming an equilibrium distribution between the angular momentum levels $l$ corresponding to a given $n$).
-%%
-Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
-H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
-Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$. 
-%%
-\civ\ is one of the strongest collisionally excited lines in quasar
-spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
-at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
-canonical BELR parameters deduced over from early analysis of the
-\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
-ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
-speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
-H$^{+}$).
+In the context of CLQs at lower-$z$...  
+(Balmer CLQs vs. \civ CLQs...) 
+Sociis natoque penatibus et
+magnis dis parturient montes, nascetur ridiculus mus. Duis tempus,
+lectus nec ultricies mollis, mi orci feugiat nulla, a bibendum velit
+orci nec lacus. Duis a odio in nisi egestas dictum. Nullam vel quam
+mauris, eget consectetur orci. Morbi ac mi sit amet neque consectetur
+tempus ac eget est. Curabitur malesuada arcu sit amet metus dictum at
+dapibus arcu accumsan. Fusce sollicitudin luctus rutrum.
 
@@
   \centering
-  % \begin{tabular}{lll  cccc r }
-  \begin{tabu}{l ll  lccc c r }
+  \begin{tabular}{l  lll  lll lll lll }
     \hline 
     \hline 
-    Object                               &   MJD      & line      & Line  Lumin.
-&  FWHM                       &  $V_{\rm off}$         & E.W.
-& $\alpha_{\lambda}$  &   Catalogue \\
-    \hline                                     
-    \rowfont{\color{blue}}       & 53498    & \civ      &  511$\pm$13    &   9593$\pm$287        &  1172$\pm$74      & 15.9$\pm$0.4      & $-1.64\pm0.01$       &  QSFit         \\    %% (NPR) 
-    \rowfont{\color{blue}}       & 53498    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    & 30.1$\pm$1.21    & $-1.47\pm0.08$       &  Shen2011 \\
-    \rowfont{\color{blue}}       & 53498    & \civ      &   403                  &   5119$^{(a)}$             &    ---                     &  ---                        &  ---                         &  DR12 SAS   \\
-                                             & 53498     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    & 25.10$\pm$0.59    & $-1.65\pm0.01$      &  QSFit          \\  %% (NPR) 
-                                             & 53498    & \ciii       &   144                 &   5119$^{(a)}$             &  ---                       &   ---                       &  ---                          &  DR12 SAS  \\
-  \rowfont{\color{teal}}         & 53498     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     & 26.66$\pm$1.65    &   $-1.65\pm0.01$    &  $^{(d)}$QSFit  \\  %% (NPR) 
-  \rowfont{\color{teal}}         & 53498     & \mgii     &  284                  &   4730$\pm$314       &  $-179\pm188$     & 32$\pm$3.88         &  $-1.87\pm0.06$     &  Shen2011 \\
- \multirow{2}{*}{{\bf J1205+3422}}  
-                &     \textcolor{teal}{53948}     & \textcolor{teal}{\mgii}   & \textcolor{teal}{130} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\
-                                 \cdashline{2-9}
-                                            & 58538     & \lya      & 952$\pm$1.1    & 12242$\pm$15    &  $-1679\pm6$          &  165$\pm$0.2        &  ---                       &   QSFit  \\    %% (MJG)
-   \rowfont{\color{blue}}       & 58538     & \civ      & 1037$\pm$5    & $>$15000             &  983$\pm$40            &  ---                        &  ---                       &   QSFit  \\   %% (NPR)
-                                            & 58538      & \ciii     &  167$\pm$0.9  & $>$15000            &  2734$\pm$46            &     45$\pm$0.2       &  ---                       &  QSFit  \\    %% (MJG)
-    \rowfont{\color{teal}}      & 58538     & \mgii    &  216$\pm$1.4  & 13940$\pm$94    & $-465.2\pm38$         &  88$\pm$0.6	    &  ---                       &   QSFit  \\    %% (MJG)
-                                          \cdashline{2-9}
-                                           & 58693     & \lya     &  271$\pm$0.9    & 9637$\pm$52     &  $-447\pm13$          &  85.1$\pm$0.3          & ---                        &   QSFit  \\    %% (MJG)
-    \rowfont{\color{blue}}    & 58693     & \civ      &   52$\pm$0.9    & 5046$\pm$26     &   1053$\pm$17         &   24.0$\pm$0.2          & ---                        &  QSFit \\     %% (MJG)
-                                           & 58693     & \ciii     &   59$\pm$0.9    & 10751$\pm$        &  1097$\pm$77         &   36$\pm$0.6             & ---                        &  QSFit   \\    %% (MJG)
-   \rowfont{\color{teal}}      & 58693     & \mgii    &  69$\pm$1.5    & 14983$\pm$346   &  $-190\pm134$       &    72$\pm$1.6           & ---                        &  QSFit   \\    %% (MJG)
-\hline
-                                                & 54553     & \lya      & 188                 &  3207                     &    ---                        &   ---                         & ---                    &   DR12 SAS  \\
-   \rowfont{\color{blue}}          & 54553     & \civ      & 257$\pm$13   &  4550$\pm$371     &   55$\pm$450         &   31.8$\pm$1.5     &                                &  $^{(d)}$QSFit  \\   %% (NPR)
-   \rowfont{\color{blue}}          & 54553     & \civ      & 281                  &    4181$\pm$736   &    680$\pm$133       & 100.5$\pm$12  & $-0.14\pm0.68$        &  Shen2011   \\
-   \rowfont{\color{blue}}          & 54553     & \civ      & 170                  &   4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\    %% (NPR)
-                                                & 54553     & \ciii     &  130$\pm$10   &  3852$\pm$402    &  $-236\pm565$       &  36.7$\pm$2.8          &  $-1.47\pm0.20$    &  $^{(d)}$QSFit  \\
-                                                & 54553     & \ciii     &  61                    &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\    %% (NPR)
-    \rowfont{\color{teal}}          & 54553      & \mgii  &  139                  &  4757$\pm$2224   &  $-944\pm568$        &   119$\pm$40          &  $-1.49\pm0.54$    &  Shen2011   \\
-    \rowfont{\color{teal}}          & 54553      & \mgii  &  69                    &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\   %% (NPR)
-                                                \cdashline{2-9}
-                                                & 55832     & \lya     & 288$\pm$11    &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99   &                               &   QSFit  \\
-                                                & 55832     & \lya     & 234                  &  4165.6$^{(a)}$         &    ---                       &   ---                         & ---                         &   DR12 SAS  \\    %% (NPR)
-\multirow{2}{*}{\bf {J1638+2827}}
- & \textcolor{blue}{55832} & \textcolor{blue}{\civ}    & \textcolor{blue}{63$\pm$3}  &   \textcolor{blue}{6052$\pm$250}  &  \textcolor{blue}{-117$\pm$103}  &  \textcolor{blue}{43.2$\pm$1.7}  &  \textcolor{blue}{-2.25$\pm$0.05} & QSFit    \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---               &    5210$\pm$226     &    ---                       &   42.8$\pm$2.0         & $-3.35$                 &     Ham17  \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &  46                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\
-                                                 & 55832     & \ciii     & 15$\pm$5     &  11421$\pm$3654   &   $>$3000                &   14.8$\pm$4.5         &  $-2.25\pm0.05$   &        QSFit \\
-                                                 &  55832    &  \ciii    &  11                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                       &   DR12 SAS \\
-    \rowfont{\color{teal}}           &  55832     & \mgii   &  13                &     5385$^{(a)}$         &  ---                           &   ---                          &  ---                       &   DR12 SAS\\
-                                               \cdashline{2-9}
-                                               & 58583       & \lya    &  785$\pm$1      & 4956$\pm$4    	&   $-641\pm2$            &   90$\pm$0.1   	  &  ---                          &  QSFit  \\ %% (MJG)
-   \rowfont{\color{blue}}         & 58583      & \civ      &  311$\pm$1     & 5739$\pm$14	 &  $-167\pm6$             &   58$\pm$0.1          & ---                          &   QSFit  \\  %% (MJG)
-                                               & 58583      & \ciii      &  52$\pm$0.8   &  3917.4	68.837      &  1514$\pm$127        &  124$\pm$2             & ---                          &   QSFit \\   %% (MJG)
-   \rowfont{\color{teal}}           & 58583      & \mgii   &  157$\pm$2    &  10565$\pm$129    &  $-450\pm52$          &   92$\pm$1              & ---                          &   QSFit  \\  %% (MJG)
-\hline
-    \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &   2994$\pm$620       &     ---                       &   42.2$\pm$5.6      & -1.59                      &    Ham17  \\
-    \rowfont{\color{blue}}         &  56189     & \civ    &   19                  &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                        &   DR12 SAS  \\
-                                               &  56189      &  \ciii   &  34$\pm$6       &  13748$\pm$2869    &   1851$\pm$1140    &  63$\pm$12          &  $-0.46\pm0.21$    &   QSFit  \\
-                                               &  56189      & \ciii    &  7                     &     5218$^{(a)}$          &  ---                         &     ---                     & ---                         &   DR12 SAS \\
-    \rowfont{\color{teal}}          & 56189      & \mgii  &  25$\pm$6       &   7253$\pm$1712     &   $-931\pm708$      &  51$\pm$10.95      &  $-0.46\pm0.21$   &   QSFit   \\
-    \rowfont{\color{teal}}         &  56189      &  \mgii &  13                   &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                       &   DR12 SAS \\
-                                                  \cdashline{2-9}
-                                              & 56960         & \lya    & 121$\pm$38     & 3580$\pm$673       &     -16$\pm$171     &  13.52 $\pm$4.21    & ---                        &   QSFit   \\  
-\multirow{2}{*}{{\bf J2228+2201}}
-           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}  & \textcolor{blue}{229$\pm$4}      &  \textcolor{blue}{8911$\pm$169}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{46.8$\pm$0.9}    & ---    & \textcolor{blue}{QSFit}     \\
-                                               & 56960    & \ciii      & 185$\pm$5        &        -                      &  2701$\pm$225      &   47.75$\pm$1.29     & ---                      &   QSFit    \\
-   \rowfont{\color{teal}}           & 56960    & \mgii   &   99$\pm$4        &  7312.6$\pm$340   &   188$\pm$137      &   50.75$\pm$2.21     & ---                      &   QSFit   \\
-                                               \cdashline{2-9}
-                                               & 58693     & \lya      &  447$\pm$5       & 8133$\pm$93       &   613$\pm$130       &        56$\pm$0.6     &  ---                    	 &   QSFit  \\%% (MJG)
-     \rowfont{\color{blue}}        & 58693     & \civ      &  41$\pm$1        &  4914$\pm>$65    &   160$\pm$27         &   25$\pm$0.3          & ---                         & QSFit   \\  %% (MJG)
-                                               & 58693     & \ciii      & 107$\pm$1.2    &  $>$15000             &  2422$\pm$67        &   ---                       & ---                          &  QSFit    \\  %% (MJG)
-     \rowfont{\color{teal}}        & 58693     & \mgii    & 177$\pm$1.1    &  $>$15000             &  1000$\pm$2617    &   16$\pm$36         & ---                           &   QSFit  \\  %% (NPR) 
+                    & \multicolumn{3}{l}{ {\bf J1205+3422}}          &  \multicolumn{6}{l}{{\bf J1638+2827}}                                                                                   &  \multicolumn{3}{l}{ {\bf J2228+2201}} \\
+Emission      & \multicolumn{3}{l}{MJD 53498}                        & \multicolumn{3}{l}{MJD 54553}                        & \multicolumn{3}{l}{MJD 55832}                     &  \multicolumn{3}{l}{MJD 56189}     \\
+line              & Line  $\sigma$ & Line  Flux &   Cont.
+Flux   & Line  $\sigma$   & Line  Flux      & Cont.
+Flux  & Line  $\sigma$ & Line  Flux  &   Cont.
+Flux  & Line  $\sigma$ & Line  Flux       &   Cont.
+Flux  \\    \hline
+Ly$\alpha$  &   ---	        &	---      & ---                 &  1362	            &	510.5	    &	7.224          & 1769                 &  633.9	 &  5.376             & ---                   &  ---                & ---    \\
+\nv	            & 1604	        & 1251        &  853.5             &  \; 854.6	    &	122.4   	    &	5.546          & 1012                 &  107.1	 &  4.645             &  5501	        &  611.3	          & -2.58  \\
+$^{(a)}$\civ     & 2174	        & 1254	   &  661.6             &  1927	            &	462.6	    &	2.722         & 2287	               &  125.1	 &  1.256             &  2216	        & \; 48.67          &   0.49  \\
+$^{(a)}$\heii    &  2174    	        & \;\; 33.2  &  620.3             &  1927    	            & \;\;\; 8.067  &	2.447         & 2287	               &  \; 10.7	 &  1.001             &  2216	        &  \;\;\; 0.35      &   0.39  \\
+$^{(a)}$\ciii     & 2174	        & \;  449.4  &  523.6             &  1927    	            & \;\;\; 8.067  &	2.447         & 2287	               &  \; 10.7	 &  1.001             &  2216	        & \; 17.2             &  0.41  \\
+$^{(a)}$\mgii   &  2174	        & \;	405.4  &  334.1             &  1927    	            & \;\;\; 8.067  &	2.447         & 2287	               &  \; 10.7	 &  1.001             &  2216	        & \; 33.6	           &  0.29  \\
     \hline 
    \hline   
-     %    \end{tabular}
-    \end{tabu}
-    \caption{Line Measurement information for the nine epochs for the 3 quasars.
-      Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM and $V_{\rm off}$ in km s$^{-1}$,
-      where positive values of $V_{\rm off}$ means the line is blueshifted.
-      Equivalent widths are \AA\.  
-      Shen11 is \citet{Shen2011}. 
-      Ham17 is \citet{Hamann2017}.
-      DR12 SAS is the line measurement information from the SDSS DR12 
-      Science Archive Server (SAS).
+  \end{tabular}
+  \caption{Line Measurement Information from the SDSS DR12 Science Archive Server (SAS). 
+    %dr12.sdss.org/spectrumDetail?plateid=2089\&mjd=53498\&fiber=427 
+    Line $\sigma$ in units of   km s$^{-1}$; 
+    Line flux          in units of  10$^{-17}$ erg/cm$^2$/s; 
+    Continuum      in units of  10$^{-17}$ erg/cm$^2$/s/ \AA; 
     $^{(a)}$Emission lines of a common ``width group'', in this case,
@@
     procedure \citep{Bolton2012}.
-      %$^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
-      Positive values of Voff means the line is blueshifted.
-%      $^{(b)}$Bit 3: FWHM value hits a limit in the fit
-      Notes: QSFit does not fit the \mgii line for J1638+2827 MJD
-      54553 or 55832. QSFit does not fit the \civ line for J2228+2201 MJD 56189.
-      $^{(d)}$Emission line modelled with two components.
-      The different colours of text are merely for readability.
   }
- \label{tab:LineMeasurement}
+ \label{tab:SDSS_line_values}
 \end{table*}
 
-%%
-%% %% \eta_{\rm Edd} = log10((10**LBol)/((1.26e38)*(10**MBH)))
-%%
-%% Using    C IV
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
+sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
 
-%% In [6]: log10((10**47.216)/((1.26e38)*(10**9.49)))                                                                                                                                             
-%%Out[6]: -0.37437054511756207
-%%
-%%In [7]: log10((10**46.166)/((1.26e38)*(10**8.742)))                                                                                                                                            
-%%Out[7]: -0.676370545117567
-%%
-%%In [8]: log10((10**46.721)/((1.26e38)*(10**9.1289)))                                                                                                                                           
-%%Out[8]: -0.5082705451175662
-%%
-%%In [9]: log10((10**46.231)/((1.26e38)*(10**8.733)))                                                                                                                                            
-%%Out[9]: -0.6023705451175618
-\begin{table*}
-  \begin{tabular}{l l  ll ll cc r}
-    \hline
-    \hline
-\multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$} & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref. \\
-                                      &                                   &                                      &                                                 & \mgii                  & \civ                    &  \mgii           &  \civ                       &        \\
-    \hline
-                                     & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen2011\\
- J1205+3422                & 58538                         &                                      &                                                 &                             &                             &                    &                               & \\
-                                     & 58693                         &                                     &                                                  &                             &                             &                    &                               &   \\
-    \hline 
-                                    & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen2011\\
- J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kol017\\
-                                    & 58583                          &                                      &                                                &                               &                            &                   &                                      &  \\
-    \hline 
-                                   & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kol017\\
-J2228+2201               & 56960                          &                                       &                                                &                              &                               &                 &                                        & \\
-                                  & 58693                          &                                       &                                               &                               &                                &                &                   &  \\
-    \hline
-    \hline
-  \end{tabular}
-  \caption{$\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio.
-        Shen11 is \citet{Shen2011}. 
-        Kol17 is \citet{Kozlowski2017}.
-        Measured line values using the methods and catalogue from
-\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
-$K$-corrected to $z = 2$; Bolometric luminosity computed from the
-monochromatic luminosity at 1350\AA\ using the spectral fits and
-bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
-luminosity, FWHM, rest-frame equivalent width, and their errors for
-the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
-continuum fit for \civ; Virial BH masses using calibrations of
-\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
-virial BH mass.}
-\label{tab:Eddington_ratios} 
-\end{table*}
+Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
+pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
+id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
+dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
+euismod. Cras vel auctor neque. Nam quis diam risus.
 
@@
   \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
+  {figures/CIV_CLQs_hexplot_20190925.png}
    \vspace{-12pt}
@@
 
-%{\bf Our Eddington ratios \\
-%Done 1\% \\
-%Coatman, Hewett say \civ\ masses are okay.\\
-%But what are these Eddington ratios? \\
-%Low state BHs vs. High-mass BHs... \\
-%Coatman et al?? Blue-shiftted \\ }
-\section{Discussion}
-\civ\ probes the photoionization environment produced by the innermost
-disk, as indicated by RM time-delay measurements. In standard \citet{SS73}
-thin disk models, large changes in the continuum flux are not
-permitted over short timescales due to the relatively long viscous
-time associated with such disks. Given the observed short timescale
-continuum variations, it is not surprising that the \citet{SS73} disk may fail
-on other fronts. The \civ\ variations observed in our sources... 
-%DO/DO NOT (I can't tell!?! we have to determine this!) fit the Baldwin Effect relationship found by previous authors (cite em again).
-
-%If they DO fit:
-This indicates they may comfortably fit into the sample of CIV
-variable QSOs explored by \citet{Dyer2019}, and similar to those
-authors we suggest slim accretion disk models e.g., 
-\citet[][]{Abramowicz1988} or inhomogeneous disk models
-\citep[e.g.,][]{DexterAgol2011} may provide viable explanations for
-our observations. I want to say a bit more here about the generic
-probe of photoionization vs shielding and conditions in the BL region
-but that will take more time.
-
-%If they DO NOT fit:
-This implies that the variable \civ\ in our sample arises through
-different emission mechanisms than is usual for high-$z$ quasar...
-%% --and I gotta think more/longer about what else to say here.
-
-\subsection{The Baldwin Effect}
+\section{Discussion and Conclusions}
 The variable properties of the rest-frame UV quasar emission lines
@@
 underlying continuum luminosity of single-epoch observations of a
-large number of AGN, first noted in \citet{Baldwin1977}.  More
-recently, the intrinsic Baldwin effect, the same anti-correlation but
-in an individual, variable AGN.  The variable properties of high-$z$
-quasars, however, has been less well studied. Reasons for this include
-more massive systems will tend to have longer timescales e.g. with
-$R_{\rm Sch}= 2GM /c^{2}$ and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$ means
-$t_{\rm dyn} \sim 6 G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2}
-$.
+large number of AGN, first noted in \citet{Baldwin1977}. 
+%%
+More recently, the intrinsic Baldwin effect, the same anti-correlation but in an individual, variable AGN.
+%
+The variable properites of high-$z$ quasars, however, has been less 
+well stuided. Reasons for this include more massive systems will tend to 
+have longer timescales e.g. with $R_{\rm Sch}= 2GM /c^{2}$ and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$
+means   $t_{\rm dyn} \sim 6G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2} $.
 
-The X-ray Baldwin Effect \citep[e.g., ][]{Iwasawa_Taniguchi1993}... 
-\citet{Bachev2004} find a 10-fold decrease in EW \civ\ with Eddington
-ratio (decreasing from $\sim$1 to $\sim$0.01), while \nv shows no
-change. These trends suggest a luminosity-independent ``Baldwin
-effect'' in which the physical driver may be the Eddington ratio.
-\citet{Ge2016} Broad emission lines is a prominent property of type I quasi-stellar objects (QSOs).
+\noindent
+{\bf Our Eddington ratios \\
+Done 1\% \\
+Coatman, Hewett say \civ\ masses are okay.\\
+But what are these Eddington ratios? \\
+Low state BHs vs. High-mass BHs... \\
+Coatman et al?? Blue-shiftted \\
+}
 
-\subsection{Eddington ratios and State Changes} 
-The broad UV and optical lines in quasars are most sensitive to the
-extreme ultraviolet (EUV) part of the spectral energy distribution
-(SED), with \civ\ (and indeed \heii and \nv) being at the higher
-energy end of the EUV distribution.
-
-The soft X-ray excess – the excess of X-rays below 2 keV with respect
-to the extrapo- lation of the hard X-ray spectral continuum model – is
-a very common feature among type 1 active galactic nuclei (AGN). 
-\citet{NodaDone2018} note that
-The soft X-ray excess produces most of the ionizing photons, so its
-dramatic drop leads to the disappearance of the broad-line region,
-driving the ``changing-look'' phenomena.  major difference is that
-radiation pressure should be much more important in AGNs, so that the
-sound speed is much faster than expected from the gas temperature.
-%%
-This spectral hardening appears similar to the soft-to-hard state
-transition in black hole binaries at $L / L_{\rm Edd} \sim 0.02$
-(i.e. $\eta_{\rm Edd} \sim -1.7$, where the inner disc evaporates into
-an advection dominated accretion flow, while the overall drop in
-luminosity appears consistent with the hydrogen ionization disc
-instability.  Crucially \citet{NodaDone2018} make the prediction that
-all changing-look AGNs are similarly associated with the state
-transition at $L / L_{\rm Edd} \sim$a few per cent.
-%%
-\citet{JiangYF2014, JiangYF2016, JiangYF2019}.
-\citet{JiangYF2019arXiv} use global three dimensional radiation
-magneto-hydrodynamic simulations to study the properties of inner
-regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$
-black hole with mass accretion rates reaching 7\% and 20\% of the
-Eddington value.
-
-We investigate this reporting the Eddington ratios of the three
-quasars in Table~\ref{tab:Eddington_ratios}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_LBol_20191015.png}
-   \vspace{-12pt}
-   \caption[]{The Baldwin Plot. The bolometric luminosities are from \citet{Kozlowski2017},
-     while the REW measurements are from \citet{Hamann2017}.}
-  \label{fig:REWvsFWHM}
-\end{figure}
-
-\section{Conclusions}
-In this paper we have reported on three redshift $z>2$ quasars with
-dramatic changes in their \civ\ emission lines, the first
-`Changing-Look'' quasars at high redshift.  This is also the first
-time the changing-look behaviour has been seen in a high-ionization
-emission line.
-
-\begin{itemize}
-  \item SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
-in their observed optical light curves, and subsequent spectroscopy
-shows significant changes in the \civ\ broad emission line, with both
-line collapse and emergence being displayed in rest-frame timescales
-of $\sim$240-1640 days.
-\item Where observed, the profile of the Ly$\alpha$/\nv emission complex
-also changes, and there is tentative evidence for changes in the \mgii
-line.
-\item Although line measurements from the three quasars show large changes
-in the \civ\ line flux-line width plane, the quasars are not seen to
-be outliers when considered against the full $z>2$ quasar population
-in terms of (rest) Equivalent Width and FWHM properties.
-\item 
-We put these observations in context with recent ``state-change''
-models, but note that even in their `low-state', the \civ\ CLQs are
-above $\sim10\%$ in Eddington luminosity.
-\end{itemize}
+Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
+at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
+in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
+nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
+nulla. Nullam eu augue id purus mollis dignissim sed et
+libero. Phasellus eget justo sed neque pellentesque egestas nec id
+arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
+vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
+imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
+neque id mi ultrices tristique. Integer quam libero, ornare vel
+gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
+cursus, dui nisl egestas augue, non fermentum nisl est nec
+nisi. Vestibulum nec mi justo, eget dapibus velit.
 
@@
 id. Ut varius iaculis quam in consequat. Nulla nec orci est, sit amet
+pellentesque nisl. Mauris non cursus lectus. Praesent placerat leo vel
+erat gravida lacinia. Donec vehicula consectetur lectus vitae
+luctus. Praesent nisl justo, laoreet elementum facilisis vel,
+tristique ac enim. Etiam vel quam ut quam eleifend
+tincidunt. Suspendisse sit amet eros vel elit ullamcorper
+laoreet. Etiam venenatis sodales turpis, nec lacinia ligula hendrerit
+nec. Nam eu vulputate purus. Quisque facilisis congue metus, sed
+imperdiet lorem rhoncus sit amet.
+
+In this paper we have... 
+\begin{itemize}
+\item Pellentesque vel elit neque, in interdum lacus. Quisque sodales, nunc et luctus convallis, nisl dui luctus dui, at congue urna velit a; 
+\item At sit amet sapien a risus dapibus sagittis. Cras sed ultricies erat. Donec id metus sed urna lacinia convallis vel sed enim. 
+\item Nisi libero, ornare vel bibendum eu, sollicitudin sed leo. Cras tincidunt aliquet ultricies. Cras pretium velit leo, in malesuada. 
+\item Duis sagittis ultricies interdum. Proin sit amet sem nec metus feugiat pharetra.
+\end{itemize}
+
 Aliquam ac metus nec odio tempus pharetra sed nec diam. Sed eget arcu
@@
 All materials, databases, data tables and code are fully available at: 
-\href{https://github.com/d80b2t/CIV_CLQs}{\tt https://github.com/d80b2t/CIV\_CLQs}.
+\href{https://github.com/d80b2t/VHzQ}{\tt https://github.com/d80b2t/}
 
@@
 %% KESF \& BM thank CalTech/JPL for support during sabbatical.
-\\
 

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190916.tex
CIV tex/ tidy up

\documentclass[a4paper,fleqn,usenatbib]{mnras}

\input{format}

\title[High-redshift CLQs]{The first high-redshift Changing Look Quasars}

\author[Bercow]
{The RH John~S.~Bercow, MP, {\it et al.} 
%Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
%K. E. Saavik Ford$^{2,3,4}$,  Matthew Graham$^{5}$,  Barry McKernan$^{2,3,4}$,  
%\newauthor Daniel Stern$^{6}$, 
%Aaron M. Meisner$^{7,8}$, Roberto J. Assef$^{9}$, Arjun Dey$^{10}$, Andrew J. Drake$^{11}$, \newauthor Hyunsung D. Jun$^{12}$, Dustin Lang$^{13,14,15}
\\
% List of institutions
$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
%$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
%$^{2}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
%$^{3}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
%$^{4}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
%$^{5}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
%$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

\date{Accepted XXX. Received YYY; in original form ZZZ}
\pubyear{2018}

%\hypersetup{draft}
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nunc imperdiet facilisis volutpat. Phasellus ultricies justo a ante bibendum porta. Nulla varius convallis risus in tincidunt. Vivamus sit amet massa non dui volutpat porttitor. Donec imperdiet mauris non risus commodo tempor. Nulla volutpat nulla a lorem lobortis, a luctus nulla rhoncus. Vestibulum vel ante elementum nisl feugiat sollicitudin. Aenean purus sem, mattis vitae odio et, varius vehicula nulla.
%%
Nulla ante mauris, mattis a tristique eu, pharetra eget erat. Cras et ultrices lectus. Praesent augue erat, commodo ac malesuada vel, mattis ac nisi. Quisque eu vehicula urna, in fringilla nunc. Duis faucibus scelerisque felis, sollicitudin luctus tortor pretium dapibus. Sed cursus scelerisque dapibus. Proin a bibendum neque, sit amet aliquet arcu. Vivamus in eros lectus. Nam dui felis, convallis sit amet dolor ut, dignissim posuere nunc. Donec egestas tellus vel urna interdum tincidunt. Sed orci eros, convallis in rhoncus sit amet, tincidunt ac est. Mauris tempus, diam a euismod tempus, est turpis laoreet justo, quis posuere augue ipsum sed nisi. Aliquam non lobortis tellus. Morbi vulputate porta placerat. Quisque dapibus pretium arcu eget tempor. Aenean in tincidunt nisi. Aenean interdum congue enim.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
accretion, accretion discs -- surveys -- quasars: general -- quasars: individual: J1100-0053 
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their energy output on timescales of weeks to months. 
This observational fact, and the subsequent mismatch in the expected timescale, the ``viscous'' timescale, 
which for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was noted over 30 years ago \citep[e.g.][]{Alloin1985}. 
However, with new photometric light-curve and repeat spectroscopic data, the desire for a deeper understanding 
of AGN accretion disk physics  has been re-established \citep[e.g.][]{Lawrence2018, Antonucci2018}.

Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs) have now been 
assembled \citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
terms as a cover for the underlying physics. For sake of argument, ``Changing Look'' quasars can be 
thought of as the extension of ``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas 
the ``Changing State'' quasars (CSQs) have a `state-transition' similar to that in Galactic X-ray binaries
\citep[e.g][]{NodaDone2018, Ruan2019}.

While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
%% 
Here, we report on three objects 
SDSS J120544.7+342252.4  (hereafter J1205+3422), 
SDSS J163852.93+282707.7 (hereafter J1638+2827) and
SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in the \civ broad emission line
properties, as well as in the underlying continuum. We claim these are
the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift and for emission lines with high ionization potentials
(I.P.'s $>$13.6 eV).

For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
standard UV/blue continuum slope increases in flux. 
the UV/blue continuum diminishes and the shape of \lya changes.

\subsection{Literature Search}
\citet{Wilhite2006} examine the variability of the high-ionizaton
C~\textsc{iv}$\lambda{1549}$ line in a sample of 105 quasars observed
at multiple epochs by the Sloan Digital Sky Survey.  We find a strong
correlation between the change in the C~\textsc{iv} line flux and the
change in the line width, but no correlations between the change in
flux and changes in line center and skewness.  The relation between
line flux change and line width change is consistent with a model in
which a broad line base varies with greater amplitude than the line
core. The objects studied here are more luminous and at higher
redshift than those normally studied for variability, ranging in
redshift from 1.65 to 4.00 and in absolute $r$-band magnitude from
roughly $-$24 to $-$28.  Using moment analysis line-fitting
techniques, we measure line fluxes, centers, widths and skewnesses for
the C~\textsc{iv} line at two epochs for each object.  The well-known
Baldwin Effect is seen for these objects, with a slope $\beta =
-0.22$.  The sample has a median intrinsic Baldwin Effect slope of
$\beta_{int} = -0.85$; the C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  Additionally, we find
no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
indicating that this blueshift might be useful as a measure of
orientation.

%% NAZAROVA 2003
%% BROAD EMISSION LINES La, C IV AND Hb IN NGC 5548
%% Astronomical and Astrophysical Transactions
%% Vol. 22, Nos. 4–5, August–October 2003, pp. 681–689

%% Punsly 2010
%% Astrophysical Journal, 713, 232
%% THE REDSHIFTED EXCESS IN QUASAR C iv BROAD EMISSION LINES

Denney, Klly; SDSS-RM Team \\
The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project\\
http://adsabs.harvard.edu/abs/2015AAS...22520403D\\

%% Coatman et al. (2017, AAS; http://adsabs.harvard.edu/abs/2017AAS...22930203C) 
%%Accurate black-hole (BH) mass estimates for high-redshift (z>2) quasars are essential for better understanding the relationship between super-massive BH accretion and star formation. Progress is currently limited by the large systematic errors in virial BH-masses derived from the CIV broad emission line, which is often significantly blueshifted relative to systemic, most likely due to outflowing gas in the quasar broad-line region. We have assembled Balmer-line based BHmasses for a large sample of 230 high-luminosity (1045.5-1048 ergs-1), redshift 1.5<z<4 quasars, which, for the first time, span the entire range of CIV blueshifts seen in the quasar population. We find the CIV-based BH-masses to be larger than the corresponding Balmer line-based masses by almost an order of magnitude at the most extreme blueshifts (˜5000 kms-1). An empirical correction to the CIV BH-masses is derived, which depends only on the properties of the CIV line itself (i.e. blueshift and FWHM). 
%%
\citet{Coatman2017AAS} show that this new correction now enables the derivation of un-biased CIV-based virial BH masses for the majority of high-luminosity, high-redshift quasars.In the same high-luminosity quasar sample, we find the narrow [OIII] emission to be weaker and more asymmetric than is generally found in  lower-luminosity AGN and that a significant fraction of our quasars have exceptionally broad (FWHM $> 3000 km s^{-1}$), blueshifted [OIII] emission. We find a strong correlation between the \civ and [OIII] blueshifts. This correlation holds even for quasars at fixed
luminosity and suggests that broad line region outflows in quasars are
connected to galaxy-scale winds.

%% \citet{Coatman2017} 
The \civ $\lambda \lambda$1498,1501 broad emission line is visible in optical spectra to redshifts exceeding $z\sim5$. \civ has long been known to exhibit significant displacements to the blue and these `blueshifts' almost certainly signal the presence of strong outflows. As a consequence, single-epoch virial black hole (BH) mass estimates derived from \civ velocity widths are known to be systematically biased compared to masses from the hydrogen Balmer lines. 
\citet{Coatman2017} use a large sample of 230 high-luminosity (LBol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with both \civ and Balmer line spectra, we have quantified the bias in \civ BH masses as a function of the \civ blueshift. \civ BH masses are shown to be a factor of 5 larger than the corresponding Balmer-line masses at C IV blueshifts of 3000 km s-1 and are overestimated by almost an order of magnitude at the most extreme blueshifts, $\gtrsim$5000 km s$^{-1}$. Using the monotonically increasing relationship between the \civ blueshift and the mass ratio BH(\civ)/BH(H$\alpha$), we derive an empirical correction to all C IV BH masses. The scatter between the corrected C IV masses and the Balmer masses is 0.24 dex at low C IV blueshifts ($\sim$0 km s-1) and just 0.10 dex at high blueshifts ($\sim$3000 km s$^{-1}$), compared to 0.40 dex before the correction. The correction depends only on the C IV line properties - i.e. full width at half-maximum and blueshift - and can therefore be applied to all quasars where C IV emission line properties have been measured, enabling the derivation of unbiased virial BH-mass estimates for the majority of high-luminosity, high-redshift, spectroscopically confirmed quasars in the literature.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the Sloan Digital Sky Survey Reverberation Mapping project to investigate the dependence of the blueshift of \civ relative to \mgii on quasar properties. We confirm that high-blueshift sources tend to have low \civ equivalent widths (EWs), and that the low-EW sources span a range of blueshift. Other high-ionization lines, such as He II, also show similar blueshift properties. The ratio of the line width (measured as both the full width at half maximum and the velocity dispersion) of \civ to that of \mgii increases with blueshift. Quasar variability enhances the connection between the \civ blueshift and quasar properties (e.g., EW). The variability of the \mgii line center (i.e., the wavelength that bisects the cumulative line flux) increases with blueshift. In contrast, the C IV line center shows weaker variability at the extreme blueshifts. Quasars with the high-blueshift \civ lines tend to have less variable continuum emission, when controlling for EW, luminosity, and redshift. Our results support the scenario that high-blueshift sources tend to have large Eddington ratios.

%% Romain A. Meyer, Sarah E. I. Bosman, Richard S. Ellis  https://arxiv.org/abs/1902.04558v1
\citet{Meyer2019} present the results of a model-independent investigation of the rest-frame UV spectra from a comprehensive sample of 394 quasars in the redshift range $1.5\leq z \leq 7.5$. We fit the main Broad Emission Lines (BELs) in the rest-frame range 1280 \AA $\leq \lambda \leq $3000 \AA (O I, C II, Si IV, C III, C IV and Mg II) with a lightly-supervised spline fitting technique. Redshifts are derived from the peaks of each fitted BEL and used to compute relative velocity shifts. We show that our method gives unbiased velocity shifts and is insensitive to spectral resolution and instrumental parameters. It is found that the average blueshift of the \civ\, line with respect to several low-ionisation lines in luminosity-matched samples does not significantly evolve over $1.5\leq z\leq 6$. However, the average blueshift increases significantly by a factor $\sim$2.5 at $z \geq 6$. We propose that this redshift evolution can be explained by \civ\, winds launched perpendicularly to an accretion disk with increased torus opacity at high-redshift, coupled with a potential orientation-driven selection bias. Our results open new exciting avenues of investigation into young quasars in the reionisation epoch.

\citet{Richards2011} 
use a sample of $\sim$30,000 quasars from the 7th Data Release of the Sloan Digital Sky Survey, and explore the range of properties exhibited by high-ionization, broad emission lines, such as \civ $\lambda$1549. Specifically, we investigate the anti-correlation between continuum luminosity and emission-line equivalent width (the Baldwin Effect (BEff)) and the ``blueshifting''of the high-ionization emission lines with respect to low-ionization emission lines. 
%Employing improved redshift determinations from Hewett \& Wild, the blueshift of the C IV emission line is found to be nearly ubiquitous, with a mean shift of ~810 km s-1 for radio-quiet (RQ) quasars and ~360 km s-1 for radio-loud (RL) quasars. The BEff is present in both RQ and RL samples. We consider these phenomena within the context of an accretion disk-wind model that is modulated by the nonlinear correlation between ultraviolet and X-ray continuum luminosity. Composite spectra are constructed as a function of C IV emission-line properties in an attempt to reveal empirical relationships between different line species and the continuum. Within a two-component disk+wind model of the broad emission-line region (BELR), where the wind filters the continuum seen by the disk component, we find that RL quasars are consistent with being dominated by the disk component, while broad absorption line quasars are consistent with being dominated by the wind component. Some RQ objects have emission-line features similar to RL quasars; they may simply have insufficient black hole (BH) spin to form radio jets. Our results suggest that there could be significant systematic errors in the determination of L bol and BH mass that make it difficult to place these findings in a more physical context. 
It is possible to classify quasars in a paradigm where the diversity of BELR parameters is due to differences in an accretion disk wind between quasars (and over time); these differences are underlain primarily by the spectral energy distribution, which ultimately must be tied to BH mass and accretion rate.

%\includegraphics\includegraphics[]{../../../../../Users/npr1/Downloads/Richards_2011_AJ_141_167.pdf}

%\citet{1994}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___425__622P.pdf}

%\citet{1994}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}

\citet{Denney2016}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Denney_2016_ApJS_224_14.pdf}
investigate the dependence on data quality of quasar properties
measured from the C IV emission line region at high redshifts.  Our
measurements come from 32 epochs of Sloan Digital Sky Survey
Reverberation Mapping Project spectroscopic observations of 482 $z >
1.46$ quasars. We compare the differences between measurements made
from the single-epoch (SE) and coadded spectra, focusing on the \civ
$\lambda$1549 emission line because of its importance for studies of
high-redshift quasar demographics and physical properties, including
black hole masses. In addition to statistical errors increasing (by
factors of $\sim2-4$), we find increasing systematic offsets with
decreasing signal-to-noise ratio (S/N).

\citet{Grier2015}....
%\includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}

\citep{Corbin1991, Dimitrijevic1992, Wills1993, Brotherton1994, Osmer1994} ...

\citep{Nazarova2003} ...

%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J2228+2201.png}
  \vspace{-12pt}
  \caption[]{J222818.7+220102.6. 
% EMERGING., 
The light curve shows it brightening from 20.5 to 19.5 over the 771 days observed-frame between the two SDSS spectra available. 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] emerging on a new blue contiuum slope.}
  \label{fig:disk_suppression}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J1638+2827.png}
  \vspace{-12pt}
  \caption[]{The quasar SDSS J163852.9+282708. 
% Disappearing 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.}
  \label{fig:disk_suppression}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
\subsection{Selection/Identification}

\subsection{SDSS spectra}
\begin{table}
 \centering
 \begin{tabular}{l l l l}
  \hline \hline 
% &&\\
   Quantity \ Object                           & J2228+2201     &  J1638+2827 \\
% &&\\
 \hline 
    &&\\
    R.A. / deg                                        &    337.078194      &  249.720559\\
    Declination / deg                            &    +22.017478      &  +28.452159 \\
    redshift, $z$                                    &   2.222$\pm$0.00038   &  2.185$\pm$0.00043          \\
    &&\\ 
    \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
                                         & 7582, 790, 56960	     & 5201, 178, 55832 \\    
 %   &&\\ 
    %$M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
    %log $(L_{\rm bol} / {\rm erg s}^{-1}) $      &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
    %log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
    %Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
    &&\\
    \hline \hline 
  \end{tabular}
  \caption{Physical properties of J1100-0053, J2317+0005 and J1052+1519 using the
    methods from \citet{Shen2011}. *This spectrum was used to estimate
    the quantities reported.  We use the regular definition of $L_{\rm
      Edd} = 4 \pi G M m_{\rm p} c /\sigma_{T} =
    1.26\times10^{38}\left (M/M_{\odot} \right )$ erg s$^{-1}$.} 
 \label{tab:Shen_props}
\end{table}

Double Spectrograph (DBSP) is a low-to-medium resolution ($R\sim$1,000
to 10,000) grating instrument for the Palomar 200-inch telescope
Cassegrain focus that uses a dichroic (at, e.g., 5200\AA\ ) to split
light into simultaneously observed separate red and blue channels.

The Low Resolution Imaging Spectrometer (LRIS) is a visible-wavelength
imaging and spectroscopy instrument commissioned in 1993 and operating
at the Cassegrain focus of 10-meter Keck I telescope.

\begin{table*}
 \centering
 \begin{tabular}{r  r  r r r   r r r r}
  \hline \hline 
% &&\\
   Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{Mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}   & Exposure    & \multirow{3}{*}{Spectrum} & \multirow{3}{*}{Notes} \\
   R.A. / deg                   &               &               &            &                                &                                                                       &  Time         & & \\
   Decl. / deg                 &               &               &            &                                &                                                                       &  / seconds         & & \\

% &&\\
 \hline 
                                       &                &               &            &                              &                   &                             &  & \\
   J120544.7+342252.4   & 2.071     &   17.99   & 53498 & 2005-May-08   & SDSS             & ?                          & 53498-2089-427  & \\
          181.436164           &                &               & 58538 & 2019-Feb-24     & DBSP            &  2$\times$900    &                               &  Conditions? \\
         +34.381229           &                &               & 58693 & 2019-Jul-29      & DBSP            &  2$\times$1200   &                                &   \\
                                       &                &               &              &                           &                   &                             &  & \\
   J163852.9+282707.7   & 2.182     &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
      249.720558407	       &               &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
       +28.452158884        &               &              & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
                                       &                &               &              &                           &                   &                             &  & \\
    J222818.7+220102.9   & 2.222     & 19.97    & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
        337.078194              &              &              & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
        +22.017478                                &               &             & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
                                       &                &               &            &                             &                   &                              &  & \\
%   J232446.7+140029.5   &  0.916     &  18.83   &  56209 & 2012-Oct-09   & BOSS             & ?                             & 56209-6148-743   & \\
 %                                      &                &               &   58662 & 2019-Jun-28  &   (??)DBSP       & ?                            &  & \\
  %                                     &                &               &              &                           &                   &                              &  & \\
   \hline \hline   
  \end{tabular}
  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
Exposure times are from the {\tt plate.fits} file. 
DBSP on the Palomar 200-inch telescope is the } 
 \label{tab:obs_notes}
\end{table*}

\subsection{J1205+3422 }
SDSS J120544.67+342252.4, observed by SDSS, first reported in \citet{Schneider2007}. 
Redshift of $z=$2.068$\pm$0.00027. 
%% targeting_flags	SERENDIP_BLUE QSO_CAP
plate	2089 
mjd	53498
fiberid	427

\subsection{J1638+2827}
SDSS J163852.93+282707.7       16h38m52.9s +28d27m08s  \\
First reported in \citet{Schneider2010}. 
Selected by {\tt SERENDIP\_BLUE} and {\tt QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
Selected as a $z>2$ known quasar and passed BOSS quasar target selections \citep{Ross2012}.

R.A. (J2000) = 249.72058 degs. \\
Decl. (J2000) = 28.45217 degs. \\
\href{skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232}{SDSS SkyServer} 
All Spectra of this Object:: \\
specObjId	plate	MJD	fiber	ra	dec	redshift \\
5855854441601671168	5201	55832	178	2.186$\pm$0.00073\\
3319321776793610240	2948	54553	614	2.185$\pm$0.00043\\

\subsection{J2228+2201}
SDSS J222818.76+220102.9 (R.A. 337.078194926, Decl. 22.017477924) was first reported in 
\citet{Paris2017}.

%%\href{https://skyserver.sdss.org/dr12/en/tools/chart/navi.aspx?ra=337.077916666667&dec=22.0173888888889&scale=0.2&width=120&height=120&opt=
\href{skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655}{SDSS SkyServer}
All Spectra of this Object:: \\
specObjId	plate	MJD	fiber	ra	dec	redshift \\
8536790363997708288	7582	56960	790	2.222$\pm$0.00038\\
6888453645991387136	6118	56189	720	2.217$\pm$0.00208\\

%Plate: 2948, MJD: 54553, Fiber: 0614
%https://dr12.sdss.org/spectrumDetail?mjd=54553&fiber=614&plateid=2948

\begin{table*}
  \centering
  \begin{tabular}{l  l  l    lll}
    \hline \hline 
    Line 	    &   Rest	      & Line       & Line	       &	Line			                 &   Continuum \\ 
    Name	    &   Wavelength  &  $z$       & $\sigma$ 	&	Flux			                 & \\
                    &    $\AA $        &              & /  km s$-1$	&     10$^{-17}$ erg/cm$2$/s &  10$^{-17}$ erg/cm$^2$/s/\AA  \\
Ly$\alpha$  &	 1215.7	&	2.186      &	1362	&	510.5		                &	7.224 \\
\nv		    &   1240.8	&	2.184     &	 854.6	&	122.4	                    	&	5.546 \\ 
\civ		    &  1549.5	&	2.184    &	1927	&	462.6		                &	2.722 \\ 
\heii	    &	 1640.4	&	2.184    &	1927	&    	  8.067	                   	&	2.447 \\  
\ciii 	    &	 1908.7	&	2.184    &	1927	&	164.6	                   	&	1.966  \\ 
\mgii	    &	 2800.3	&	2.184   & 	1927	&	187.4	                   	&	1.513  \\
   \hline \hline   
  \end{tabular}
  \caption{Line Measurement Information}
 \label{tab:line_values}
\end{table*}

\begin{table*}
  \centering
  \begin{tabular}{l  lll lll  }
    \hline \hline 
                                    &                               &                                           &                                                      &                                  &                         & \\  
                                  \multicolumn{7}{c}{J1638+2827}  \\
                                    &                               &                                           &                                                      &                                  &                         & \\  
   \hline                       
%                                   &                               &                                           &                                                      &                                  &                         & \\  
    Line      	             & Line  $\sigma$     & Line  Flux                           &   Continuum                                 & Line  $\sigma$          & Line  Flux        &   Continuum                                    \\
%    Wavelength	             & /  km s$^{-1}$         &   10$^{-17}$ erg/cm$2$/s  & 10$^{-17}$ erg/cm$^2$/s/\AA      &  /  km s$-1$             & / 10$^{-17}$ erg/cm$2$/s   & /10$^{-17}$ erg/cm$^2$/s/\AA       \\
                                     & \multicolumn{3}{l}{MJD 54553}                                                                                   & \multicolumn{3}{l}{MJD 55832}                                                                                                          \\
    Ly$\alpha$1215.7    &  1362	            &	510.5		                  &	7.224                                           &  1769	                &   633.9	              &  5.376     \\
    \nv1240.8	            &   854.6	            &	122.4	                    	  &	5.546                                           & 1012	                &  107.1		      &  4.645\\ 
    \civ1549.5         	    &	 1927	            &	462.6		                  &	2.722                                           & 2287	                &  125.1		      &  1.256      \\  
    \heii1640.4	            &	 1927    	            &      8.067	                   	  &	2.447                                           & 2287	                &    10.68	      &  1.001\\  
    \ciii1908.7        	    &	 1927	            &	164.6	                   	  &	1.966                                          & 2287	 	                &     29.53	      &  0.6008\\ 
    \mgii2800.3	    &   1927	            &	187.4	                   	  &	1.513                                          & 2287 	 	         &    34.66	      &  0.3461  \\
                                    &                               &                                           &                                                      &                                  &                           &                \\  
   \hline \hline   
  \end{tabular}
  \caption{Line Measurement Information. 
    Line $\sigma$ in units of   km s$-1$; 
    Line flux          in units of  10$^{-17}$ erg/cm$^2$/s; 
    Continuum      in units of  10$^{-17}$ erg/cm$^2$/s/ \AA; 
}
 \label{tab:line_values}
\end{table*}

%Plate: 5201, MJD: 55832, Fiber: 178
%https://dr12.sdss.org/spectrumDetail?mjd=55832&fiber=178&plateid=5201

%Line		Rest		        Line	        Line		        Line			   Continuum
%Name		Wavelength	z	        sigma 		Flux	
%                       [Å]			               [km s-1]  	[10-17erg/cm2/s] 	   [10-17erg/cm2/s/Å]
%Ly_alpha	1215.7		2.186	1769		633.9		   5.376
%N_V		1240.8		2.185	1012		107.1		   4.645
%C_IV		1549.5		2.185	2287		125.1		   1.256
%He_II		1640.4		2.185	2287		 10.68		   1.001
%C_III]		1908.7		2.185	2287	 	 29.53		   0.6008
%Mg_II		2800.3		2.185	2287 	 	 34.66		   0.3461

%So, ratios, MJD 54553 / MJD 55832::
%$Ly_alpha	1215.7		—	0.770		0.805			1.344			
%N_V		1240.8		—	0.844		1.143			1.194
%C_IV		1549.5		—	0.843		3.698			2.167			
%He_II		1640.4		—	0.843		0.755			2.445			
%C_III]		1908.7		—	0.843		5.574			3.27			
%Mg_II		2800.3		—	0.843		5.407			4.37

\subsection{Multi-wavelength properties}
MIR \\
Radio \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{In the context of CLQs at lower-$z$}

\subsection{Balmer CLQs vs. \civ CLQs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}

\bibliographystyle{mnras}
\bibliography{tester_mnras}

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

\end{document}

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190917v1.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190916.tex
@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Nunc imperdiet facilisis volutpat.
-Phasellus ultricies justo a ante bibendum porta.
-Nulla varius convallis risus in tincidunt.
-Vivamus sit amet massa non dui volutpat porttitor.
-Donec imperdiet mauris non risus commodo tempor.
-Nulla volutpat nulla a lorem lobortis, a luctus nulla rhoncus.
-Vestibulum vel ante elementum nisl feugiat sollicitudin.
-Aenean purus sem, mattis vitae odio et, varius vehicula nulla.
-%%
-Nulla ante mauris, mattis a tristique eu, pharetra eget erat.
-Cras et ultrices lectus.
-Praesent augue erat, commodo ac malesuada vel, mattis ac nisi.
-Quisque eu vehicula urna, in fringilla nunc.
-Duis faucibus scelerisque felis, sollicitudin luctus tortor pretium dapibus.
-Sed cursus scelerisque dapibus.
-Proin a bibendum neque, sit amet aliquet arcu.
-Vivamus in eros lectus.
-Nam dui felis, convallis sit amet dolor ut, dignissim posuere nunc.
-Donec egestas tellus vel urna interdum tincidunt.
-Sed orci eros, convallis in rhoncus sit amet, tincidunt ac est.
-Mauris tempus, diam a euismod tempus, est turpis laoreet justo, quis posuere augue ipsum sed nisi.
-Aliquam non lobortis tellus.
-Morbi vulputate porta placerat.
-Quisque dapibus pretium arcu eget tempor.
-Aenean in tincidunt nisi.
-Aenean interdum congue enim.
+This is two hundred words, the suggested maximum for a MNRAS
+Letter. Lorem ipsum dolor sit amet, autem semper eam ei. Eros
+maluisset posidonium eu mea, atqui aperiam nostrum cum ad. Te vocent
+volutpat petentium vix, pro senserit convenire vituperatoribus ex, ad
+his mucius tamquam appetere. An mea omnium voluptaria scribentur, te
+verear iisque vulputate sit. Vim malis omittam probatus cu, vide
+tempor ius ex, vim eu case magna rebum. Vis id clita eruditi, in sea
+evertitur dissentiunt, per eu deseruisse mnesarchum deterruisset. Eu
+tale tempor sea, te mundi congue detracto est. Has ipsum animal timeam
+no. Atqui novum nobis et his, pericula interesset mel ut. Ea pro eros
+everti legendos. Vel iusto legere euismod id, ea erat debitis
+democritum usu. Ut paulo aliquid vix, disputationi delicatissimi
+signiferumque ut eam. Utroque impedit ad his. Ei mea sale tritani, ex
+eum duis epicuri, at per nonumy delectus electram. Dolorem patrioque
+prodesset vis at, sint tritani mel te. Ut nulla solet nonumes has, mel
+diam scripta delectus in, ne duo laudem appetere assueverit. An vim
+reque munere, labores apeirian his cu. Ei clita placerat praesent nam,
+in affert sapientem est. Qui te regione deterruisset. Nam at quodsi
+placerat. Pri no quando placerat.
 \end{abstract}
@@
 \citep[e.g][]{NodaDone2018, Ruan2019}. 
+%
+These CLQs have primarily been defined according to their Balmer emission line properties with 
+particular attention paid to the H$\beta$ emission line, usually observed from optical spectroscopy. 
+As such, current CLQ studies have been at redshifts $z<1$.
 
@@
 %%
+
+I also don’t think this is a recombination (for H, He) vs. collisionally excited lines (MgII, C IV etc.) thing, though I’m not sure.
+
 Here, we report on three objects 
@@
 
+In this paper we use the wavelengths of 1548.2 and 1550.8 \AA for the \civ doublet
+%Example of how to reference these results:
+using the values from the National Institute of Standards and Technology (NIST) Atomic Spectra Database 
+\citep{Kramida2018}. 
+% A., Ralchenko, Yu., Reader, J., and NIST ASD Team (2018).
+NIST Atomic Spectra Database (ver.
+5.6.1), [Online].
+Available: https://physics.nist.gov/asd [2019, September 17].
+National Institute of Standards and Technology, Gaithersburg, MD.
+DOI: https://doi.org/10.18434/T4W30F
+
+%The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.
+%11.3 eV is the energy needed for C I to get rid of one electron, and become singly-ionised C II”
+%“24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
+%% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
+Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form}
+for ionisation energies, we note 47.89 eV  (3.519 Ry) is the energy required to for neutral C to dislodge three electrons and become triply--ionised \civ, 
+and where 64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.
+
 \subsection{Literature Search}
+\citet{Gregory1982} reported time variability in both Lya and \civ 1550 emission lines in the Seyfert galaxy NGC 5548.
+
+From \citet{VandenBerk2001} 
+The rest positions of emission lines in quasar spectra, especially the
+high-ionization broad lines, are known to vary from their nominal
+laboratory wavelengths \citep{Gaskell1982, Wilkes1986,  Espey1989, Espey1990Erratum, 
+ZhengSulentic1990, Corbin1990, Weymann1991, TytlerFan1992, 
+Brotherton1994, Laor1995, McIntosh1999}.
+
 \citet{Wilhite2006} examine the variability of the high-ionizaton
@@
 
-Denney, Klly; SDSS-RM Team \\
-The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project\\
-http://adsabs.harvard.edu/abs/2015AAS...22520403D\\
+\citet{Denney2015}, 
+%Denney, Kelly; SDSS-RM Team, ``The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project'' ; http://adsabs.harvard.edu/abs/2015AAS...22520403D
+The Sloan Digital Sky Survey Reverberation Mapping (SDSS-RM) Project
+spectroscopically monitored $\sim$850 quasars over a seven square
+degree field for approximately six months with the BOSS
+spectrograph. While the time series analysis of the quasar continuum
+and emission-line variability, and thereby the potential to measure
+reverberation time delays from this sample, is still underway, we have
+used the subset (roughly half) of this sample containing the \civ 1549\AA 
+broad emission line to investigate the effects of S/N on measuring
+this broad emission line width. Line width measurements are necessary
+for inferring the broad line region gas velocities used to determine
+the quasar black hole mass. However, literature studies have suggested
+line width measurements, and therefore black hole mass estimates, may
+be biased by the use of relatively low S/N, typical survey-quality,
+data, compared to the high S/N data that calibrate single-epoch black
+hole mass scaling relations. The SDSS-RM data set provides a unique
+opportunity to search for any systematic uncertainties in CIV line
+width measurements through a comparison of line widths measured from
+the single-epoch spectra, which are roughly equivalent to other
+SDSS/BOSS quasar spectra (though still twice the exposure time) to
+those measured from the high-S/N, campaign co-added spectra, which
+contain more than 30 epochs of each source. Here we present results
+from this investigation, which have implications for estimating CIV
+single-epoch black hole masses from the SDSS/BOSS and other surveys.
 
@@
 connected to galaxy-scale winds.
+
+\citet{Coatman2016} show that %%Black hole masses are crucial to understanding the physics of the connection between quasars and their host galaxies and measuring cosmic black hole-growth. 
+at high redshift, $z>2.1$, black hole masses are normally derived using the velocity width of the C IV λλ1548, 1550 broad emission line, based on the assumption that the observed velocity widths arise from virial- induced motions.
+In many quasars, the C IV emission line exhibits significant blue asymmetries (‘blueshifts’) with the line centroid displaced by up to thousands of km s−1 to the blue.
+These blueshifts almost certainly signal the presence of strong outflows, most likely originating in a disc wind.
+We have obtained near-infrared spectra, including the Hα λ6565 emission line, for 19 luminous (LBol = 46.5–47.5 erg s−1) Sloan Digital Sky Survey quasars, at redshifts 2 < z < 2.7, with C IV emission lines spanning the full range of blueshifts present in the population.
+A strong correlation between C IV velocity width and blueshift is found and, at large blueshifts, >2000kms−1, the velocity widths appear to be dominated by non-virial motions.
+Black hole masses, based on the full width at half-maximum of the C IV emission line, can be overestimated by a factor of 5 at large blueshifts.
+A larger sample of quasar spectra with both C IV and H β, or Hα, emission lines will allow quantitative corrections to C IV-based black hole masses as a function of blueshift to be derived.
+We find that quasars with large C IV blueshifts possess high Eddington luminosity ratios and that the fraction of high-blueshift quasars in a flux-limited sample is enhanced by a factor of approximately 4 relative to a sample limited by black hole mass.
 
@@
 
+Also from \citet{Richards2011}, 
+At high redshift, two well-known properties of the Civ emission line are evident in quasar spectra (see Section 4).
+An anti-correlation between luminosity and the equivalent width (EQW) of C iv, generally known as the Baldwin Effect (BEff; Baldwin 1977), was first identified in 20 (mostly radio-loud (RL)) quasars and has been confirmed in much larger samples (e.g., Wu et al.
+2009).
+The other effect is the blueshifting of the C iv with respect to the systemic redshift (Gaskell 1982; Wilkes 1984).
+As with the BEff, these blueshifts have not only been confirmed with larger samples, but appear to be nearly ubiquitous in the quasar population (Sulentic et al.
+2000b; Richards et al.
+2002a).
+
 %\includegraphics\includegraphics[]{../../../../../Users/npr1/Downloads/Richards_2011_AJ_141_167.pdf}
@@
 
+\iffalse
 \begin{figure}
@@
 \end{figure}
+\fi
 
@@
 \section{Data}
-\subsection{Selection/Identification}
+%\subsection{Selection/Identification}
+%\subsection{SDSS spectra}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
+sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
 
-\subsection{SDSS spectra}
+Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
+pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
+id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
+dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
+euismod. Cras vel auctor neque. Nam quis diam risus.
+
 \begin{table}
@@
 \end{table*}
+
+\subsection{Multi-wavelength properties}
+MIR \\
+Radio \\
+
+%%\newpage
+%% For the MNRAS Letter, not sure this can take up a full page...
+\begin{figure}
+  \centering
+  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
+  {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
+% {figures/The_3_CIV_CLQs_20190917.pdf}
+   \vspace{-12pt}
+  \caption[]{The threes high-$z$ CLQ quasars; 
+SDSS J1205+3422 (top), 
+SDSS J1638+2827 (middle), 
+SDSS J2228+2201 (bottom). 
+%A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
+}
+  \label{fig:civ_clqs}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
+%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
+%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+Figure~\ref{fig:civ_clqs} presents the threes high-$z$ CLQ quasars. 
+Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
+at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
+in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
+nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
+nulla. Nullam eu augue id purus mollis dignissim sed et
+libero. Phasellus eget justo sed neque pellentesque egestas nec id
+arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
+vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
+imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
+neque id mi ultrices tristique. Integer quam libero, ornare vel
+gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
+cursus, dui nisl egestas augue, non fermentum nisl est nec
+nisi. Vestibulum nec mi justo, eget dapibus velit.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
+  {../plots/Wilhite/Wilhite_2006_Fig2_redux_20190830.png}
+% {figures/The_3_CIV_CLQs_20190917.pdf}
+   \vspace{-12pt}
+  \caption[]{
+The Change in \civ line width vs. line flux change. 
+Data from \citet{Wilhite2006} with a sample of 105 quasars observed at
+multiple epochs by the Sloan Digital Sky Survey. We find a strong
+correlation between the change in the C iv line flux and the change in
+the line width, but no correlations between the change in flux and
+changes in line center and skewness.}
+  \label{fig:Wilhite2006_comparison}
+\end{figure}
+From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
+strong correlation between the change in the line flux and the change
+in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
+epoch-to-epoch flux ratio versus the ratio of line widths.
+
+In the context of CLQs at lower-$z$...  Sociis natoque penatibus et
+magnis dis parturient montes, nascetur ridiculus mus. Duis tempus,
+lectus nec ultricies mollis, mi orci feugiat nulla, a bibendum velit
+orci nec lacus. Duis a odio in nisi egestas dictum. Nullam vel quam
+mauris, eget consectetur orci. Morbi ac mi sit amet neque consectetur
+tempus ac eget est. Curabitur malesuada arcu sit amet metus dictum at
+dapibus arcu accumsan. Fusce sollicitudin luctus rutrum.  Balmer CLQs
+vs. \civ CLQs...
 
@@
 
-\subsection{Multi-wavelength properties}
-MIR \\
-Radio \\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
-%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
-%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\subsection{In the context of CLQs at lower-$z$}
-
-\subsection{Balmer CLQs vs. \civ CLQs}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Discussion and Conclusions}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
+sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
+
+Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
+pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
+id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
+dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
+euismod. Cras vel auctor neque. Nam quis diam risus.
+
+Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
+at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
+in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
+nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
+nulla. Nullam eu augue id purus mollis dignissim sed et
+libero. Phasellus eget justo sed neque pellentesque egestas nec id
+arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
+vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
+imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
+neque id mi ultrices tristique. Integer quam libero, ornare vel
+gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
+cursus, dui nisl egestas augue, non fermentum nisl est nec
+nisi. Vestibulum nec mi justo, eget dapibus velit.
+
+Cras in laoreet mauris. Vivamus nec nulla a dui commodo
+adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor
+ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus
+et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida
+sagittis quis in sem. Phasellus quis risus bibendum eros luctus
+auctor.
+
+Etiam mollis viverra nisi eget aliquet. Aliquam erat volutpat. Vivamus
+tristique, nisl eu malesuada semper, libero tortor convallis elit, a
+scelerisque orci nisi lacinia turpis. In lacinia ultrices
+volutpat. Proin ultrices luctus tellus, in placerat eros tincidunt
+id. Ut varius iaculis quam in consequat. Nulla nec orci est, sit amet
+pellentesque nisl. Mauris non cursus lectus. Praesent placerat leo vel
+erat gravida lacinia. Donec vehicula consectetur lectus vitae
+luctus. Praesent nisl justo, laoreet elementum facilisis vel,
+tristique ac enim. Etiam vel quam ut quam eleifend
+tincidunt. Suspendisse sit amet eros vel elit ullamcorper
+laoreet. Etiam venenatis sodales turpis, nec lacinia ligula hendrerit
+nec. Nam eu vulputate purus. Quisque facilisis congue metus, sed
+imperdiet lorem rhoncus sit amet.
+
+In this paper we have... 
+\begin{itemize}
+\item Pellentesque vel elit neque, in interdum lacus. Quisque sodales, nunc et luctus convallis, nisl dui luctus dui, at congue urna velit a; 
+\item At sit amet sapien a risus dapibus sagittis. Cras sed ultricies erat. Donec id metus sed urna lacinia convallis vel sed enim. 
+\item Nisi libero, ornare vel bibendum eu, sollicitudin sed leo. Cras tincidunt aliquet ultricies. Cras pretium velit leo, in malesuada. 
+\item Duis sagittis ultricies interdum. Proin sit amet sem nec metus feugiat pharetra.
+\end{itemize}
+
+Aliquam ac metus nec odio tempus pharetra sed nec diam. Sed eget arcu
+nulla. Etiam elementum ultrices ligula, at iaculis libero feugiat
+bibendum. Suspendisse potenti. Nam pharetra adipiscing
+euismod. Quisque imperdiet dignissim odio, sed volutpat justo
+tincidunt eu. Nunc vehicula pharetra suscipit. Integer aliquet pretium
+ipsum vel ultrices. Nam rutrum nibh ac quam pulvinar molestie.
+
+Sed sed ipsum diam. In risus tortor, sagittis eu auctor in, varius in
+dui. Mauris a nunc ut ligula ullamcorper tincidunt. Nunc aliquam eros
+ac risus pellentesque aliquam. Phasellus augue velit, varius at
+porttitor sit amet, pretium eget felis. Ut mollis tellus elementum
+magna porttitor rutrum. Etiam blandit leo eget est consectetur
+imperdiet. Quisque et diam nec orci vulputate varius vitae id sapien.
 

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190917v2.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190917v1.tex
@@
 
-I also don’t think this is a recombination (for H, He) vs. collisionally excited lines (MgII, C IV etc.) thing, though I’m not sure.
+Recombination (e.g. H, He) vs. collisionally excited lines (\mgii, \civ).
 
@@
 
-\citet{Coatman2016} show that %%Black hole masses are crucial to understanding the physics of the connection between quasars and their host galaxies and measuring cosmic black hole-growth. 
-at high redshift, $z>2.1$, black hole masses are normally derived using the velocity width of the C IV λλ1548, 1550 broad emission line, based on the assumption that the observed velocity widths arise from virial- induced motions.
-In many quasars, the C IV emission line exhibits significant blue asymmetries (‘blueshifts’) with the line centroid displaced by up to thousands of km s−1 to the blue.
-These blueshifts almost certainly signal the presence of strong outflows, most likely originating in a disc wind.
-We have obtained near-infrared spectra, including the Hα λ6565 emission line, for 19 luminous (LBol = 46.5–47.5 erg s−1) Sloan Digital Sky Survey quasars, at redshifts 2 < z < 2.7, with C IV emission lines spanning the full range of blueshifts present in the population.
-A strong correlation between C IV velocity width and blueshift is found and, at large blueshifts, >2000kms−1, the velocity widths appear to be dominated by non-virial motions.
-Black hole masses, based on the full width at half-maximum of the C IV emission line, can be overestimated by a factor of 5 at large blueshifts.
-A larger sample of quasar spectra with both C IV and H β, or Hα, emission lines will allow quantitative corrections to C IV-based black hole masses as a function of blueshift to be derived.
-We find that quasars with large C IV blueshifts possess high Eddington luminosity ratios and that the fraction of high-blueshift quasars in a flux-limited sample is enhanced by a factor of approximately 4 relative to a sample limited by black hole mass.
+\citet{Coatman2016} show that at high redshift, $z>2.1$, black hole
+masses are normally derived using the velocity width of the C IV
+$\lambda \lambda$1548, 1550 broad emission line, based on the
+assumption that the observed velocity widths arise from virial-
+induced motions. In many quasars, the \civ emission line exhibits
+significant blue asymmetries  with the line centroid
+displaced by up to thousands of km s$^{-1}$ to the blue. These blueshifts
+almost certainly signal the presence of strong outflows, most likely
+originating in a disc wind. We have obtained near-infrared spectra,
+including the H$\alpha$ $\lambda$6565 emission line, for 19 luminous 
+(L$_{\rm Bol} =46.5–47.5$ erg s$^{-1}$) Sloan Digital Sky Survey quasars, at redshifts $2 <
+z < 2.7$, with \civ emission lines spanning the full range of
+blueshifts present in the population. A strong correlation between C
+IV velocity width and blueshift is found and, at large blueshifts,
+$>$2000 km s$−1$, the velocity widths appear to be dominated by non-virial
+motions. Black hole masses, based on the full width at half-maximum of
+the \civ emission line, can be overestimated by a factor of 5 at large
+blueshifts. A larger sample of quasar spectra with both \civ and H$\beta$, 
+or H$\alpha$, emission lines will allow quantitative corrections to \civ-based black hole masses as a function of blueshift to be
+derived. We find that quasars with large \civ blueshifts possess high
+Eddington luminosity ratios and that the fraction of high-blueshift
+quasars in a flux-limited sample is enhanced by a factor of
+approximately 4 relative to a sample limited by black hole mass.
 
@@
 Our results support the scenario that high-blueshift sources tend to have large Eddington ratios.
-
-%% Romain A. Meyer, Sarah E. I. Bosman, Richard S. Ellis  https://arxiv.org/abs/1902.04558v1
-\citet{Meyer2019} present the results of a model-independent investigation of the rest-frame UV spectra from a comprehensive sample of 394 quasars in the redshift range $1.5\leq z \leq 7.5$.
-We fit the main Broad Emission Lines (BELs) in the rest-frame range 1280 \AA $\leq \lambda \leq $3000 \AA (O I, C II, Si IV, C III, C IV and Mg II) with a lightly-supervised spline fitting technique.
-Redshifts are derived from the peaks of each fitted BEL and used to compute relative velocity shifts.
-We show that our method gives unbiased velocity shifts and is insensitive to spectral resolution and instrumental parameters.
-It is found that the average blueshift of the \civ\, line with respect to several low-ionisation lines in luminosity-matched samples does not significantly evolve over $1.5\leq z\leq 6$.
-However, the average blueshift increases significantly by a factor $\sim$2.5 at $z \geq 6$.
-We propose that this redshift evolution can be explained by \civ\, winds launched perpendicularly to an accretion disk with increased torus opacity at high-redshift, coupled with a potential orientation-driven selection bias.
-Our results open new exciting avenues of investigation into young quasars in the reionisation epoch.
 
@@
 %\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}
+
+Recent investigations also include \citet{Meyer2019}.
 
@@
 Radio \\
+{\bf FROM ROSS ET AL 2018!!!!} 
+While previous efforts have used the 1-year baseline of the WISE mission to identify
+changing-look quasars \citep[e.g.,][]{Assef2018, Stern2018}, our
+investigation is the first to extend this selection to the infrared
+using NEOWISE-R mission data. We have identified a sample of Sloan
+Digital Sky Survey (SDSS) quasars that show significant changes in
+their IR flux over the course of a few years. Importantly, our IR
+light curves enable us to set limits on SED changes due to
+obscuration.
+
+We use data from the
+beginning of the WISE mission \citep[2010 January; ][]{Wright2010}
+through the thrid-year of NEOWISE-R operations \citep[2016 December;
+][]{Mainzer2011}. The WISE scan pattern leads to coverage of the
+full-sky approximately once every six months (a ``sky pass''), but the
+satellite was placed in hibernation in 2011 February and then
+reactivated in 2013 October. Hence, our light curves have a cadence of
+6 months with a 32 month sampling gap.
+
+The W1/W2 light curves for $\sim$200,000 SDSS and BOSS spectroscopic
+quasars were obtained by performing forced photometry at the locations
+of DECam-detected optical sources \citep{Lang2014, Meisner2017a,
+Meisner2017b}. This forced photometry was performed on time-resolved
+coadds \citep{Lang2014}, each of which represents a stack of $\sim$12
+exposures. The coaddition removes the possibility of probing
+variability on $\lesssim$1 day time scales, but pushes $\approx$1.4
+magnitudes deeper than individual exposures while removing virtually
+all single-exposure artifacts (e.g. cosmic rays and satellites).
+
+Approximately $\sim$30,000 of the SDSS/BOSS quasars with W1/W2
+light-curves available are `IR-bright', in that they are above both
+the W1 and W2 single exposure thresholds and therefore detected at
+very high significance in the coadds. For this ensemble of objects,
+the typical variation in each quasar's measured (W1-W2) color is 0.06
+magnitudes.  This includes statistical and systematic errors which are
+expected to contribute variations at the few hundredths of a magnitude
+level. The typical measured single-band scatter is 0.07 magnitudes in
+each of W1 and W2.
 

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190919.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190917v2.tex
@@
 \section{Introduction}
-Luminous AGN, i.e. quasars, are now seen to significantly vary their energy output on timescales of weeks to months. 
-This observational fact, and the subsequent mismatch in the expected timescale, the ``viscous'' timescale, 
-which for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was noted over 30 years ago \citep[e.g.][]{Alloin1985}. 
-However, with new photometric light-curve and repeat spectroscopic data, the desire for a deeper understanding 
-of AGN accretion disk physics  has been re-established \citep[e.g.][]{Lawrence2018, Antonucci2018}.
+Luminous AGN, i.e. quasars, are now seen to significantly vary their
+energy output on timescales of weeks to months.  This observation, and
+the subsequent mismatch in the expected ``viscous'' timescale, which
+for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was
+noted over 30 years ago \citep[e.g.][]{Alloin1985}. However, with new
+photometric light-curve and repeat spectroscopic data, the desire for
+a deeper understanding of AGN accretion disk physics has been recently
+re-invigorated the field \citep[e.g.][]{Lawrence2018, Antonucci2018}.
 
@@
 %
-These CLQs have primarily been defined according to their Balmer emission line properties with 
+These CLQs have primarily been defined according to the (recombination) Balmer emission line properties with 
 particular attention paid to the H$\beta$ emission line, usually observed from optical spectroscopy. 
@@
 
-While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
-\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
-broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
+While there have been a slew of studies on triply ionized carbon, i.e
+\civ, these have tended to focus on broad absorption line quasars
+\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019} or the Baldwin Effect
+\citep[BEff; e.g. ][]{Baldwin1977, Bian2012, Jensen2016,
+Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
+types of Baldwin effect are present in the literature: the {\it
+global} (or {\it ensemble}) Baldwin Effect, which is an anti-correlation
+between the EW of the emission line and the underlying continuum
+luminosity of {\it single-epoch} observations of a {\it large number}
+of AGN and second, the {\it intrinsic} Baldwin effect, the same anti-correlation
+but in an {\it individual, variable} AGN \citep{PoggePeterson1992}.}.
 %%
+Dramatic changes in the collisionally excited  broad {\it emission} line (BEL) 
+of \civ (and indeed \ciii) have not to this point been seen.
 
-Recombination (e.g. H, He) vs. collisionally excited lines (\mgii, \civ).
+Here, we report on three quasars  
+%SDSS J120544.7+342252.4  (hereafter J1205+3422), 
+%SDSS J163852.93+282707.7 (hereafter J1638+2827) and
+%SDSS J222818.76+220102.9 (hereafter J2228+2201)  
+which show dramatic changes in their \civ\ and \ciii broad emission line
+properties as well as in the underlying continuum. We claim these are
+the first examples of ``Changing Look Quasars'' at high ($z>1$)
+redshift. Moreover, these are cases for dramatic changes of 
+ions with high ionization potentials (I.P.'s $>$2 Rydberg).
 
-Here, we report on three objects 
-SDSS J120544.7+342252.4  (hereafter J1205+3422), 
-SDSS J163852.93+282707.7 (hereafter J1638+2827) and
-SDSS J222818.76+220102.9 (hereafter J2228+2201)  
-which show dramatic changes in the \civ broad emission line
-properties, as well as in the underlying continuum. We claim these are
-the first examples of ``Changing Look Quasars'' at high ($z>1$)
-redshift and for emission lines with high ionization potentials
-(I.P.'s $>$13.6 eV).
-
-For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
-For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
-standard UV/blue continuum slope increases in flux. 
-the UV/blue continuum diminishes and the shape of \lya changes.
-
-In this paper we use the wavelengths of 1548.2 and 1550.8 \AA for the \civ doublet
+%%
+In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for the \civ doublet
 %Example of how to reference these results:
@@
 %The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.
-%11.3 eV is the energy needed for C I to get rid of one electron, and become singly-ionised C II”
+
 %“24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
 %% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
+The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$.
 Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form}
-for ionisation energies, we note 47.89 eV  (3.519 Ry) is the energy required to for neutral C to dislodge three electrons and become triply--ionised \civ, 
-and where 64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.
+for ionisation energies, we see 
+11.3 eV is the energy needed for C I to dislodge one electron and become singly-ionised C II; 
+24.4 eV is energy needed for singly-ionised C II to dislodge an additional electron, and become doubly-ionised C III, 
+and 47.89 eV  (3.519 Ry) is required for doubly-ionised C III  become triply--ionised \civ. 
+64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.
+
+The 1548.202 	and 1550.774 \AA\ emission doublet is created by the 
+2$p$ $^{2}P_{0}$ $---$  2$s$ $^{2}S$ transition with 
+energies 64,484 cm$^{-1}$ and 64591 cm$^{-1}$ 
+\citep[e.g.][]{Moore1993}.
+
+Ground  Shells:  1$s^{2}$2$s$. 
+Ground  Level: $^{2}S_{1/2}$. 
+Ionized  Level: 1$s^{2}$ $^{1}S_{0}$.
 
@@
 %\subsection{Selection/Identification}
-%\subsection{SDSS spectra}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
-sodales est, vel cursus risus porta non. Vivamus vel pretium
-velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
-ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
-hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
-conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
-eu blandit. Donec in lacinia libero.
+\subsection{Spectra}
+An overview of our spectroscopic observations is given in Table~\ref{tab:obs_notes}. 
+The spectra are from the SDSS \citep{Stoughton2002, DR7, Schneider2010},  
+the SDSS-III Baryon Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011, Dawson2013, Smee2013, Alam2015, Paris2017} 
+and the SDSS-IV  Extended Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016, Abolfathi2018}. 
+These quasars were targetted via a range of techniques and algorithms \citep[][]{Richards2002, Ross2012, 
+Myers2015}.  
+These data are supplemented by spectra from 
+the Low Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I} telescope \citep{Oke1995}. 
+%% The Keck Low Resolution Imaging Spectrometer", Oke, J.B., et al.. 1995, PASP, 107, 375
+and the Double Spectrograph (DBSP) instrument on the Palomar {\it Hale} 5m telescope.
+
+\subsection{Line Properties}. 
+We use the measured quasar emission line properties from \citet{Shen2011} and \citet{Hamann2017}. 
+\citet{Hamann2017} in particular investigate in robust detail the UV continuum and the \civ (and \nv $\lambda$ $\lambda$1238, 1242) emission lines in 
+over 200,000 quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line catalog 
+can be downloaded from \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
+The quasar redshift are limited to the range 1.53 ≤ ze ≤ 5.0 so that C IV and the adjacent continuum are covered by BOSS. 
+These measurements provide line profile information and N V/C IV flux ratios
 
@@
 \end{table}
-
-Double Spectrograph (DBSP) is a low-to-medium resolution ($R\sim$1,000
-to 10,000) grating instrument for the Palomar 200-inch telescope
-Cassegrain focus that uses a dichroic (at, e.g., 5200\AA\ ) to split
-light into simultaneously observed separate red and blue channels.
-
-The Low Resolution Imaging Spectrometer (LRIS) is a visible-wavelength
-imaging and spectroscopy instrument commissioned in 1993 and operating
-at the Cassegrain focus of 10-meter Keck I telescope.
 
@@
 \end{figure}
+
+\begin{figure*}
+  \centering
+  %% trim=l b r t
+  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
+  % {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
+  {../plots/perObject/J1205+3422_landscape_20190920.png}
+  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
+  {../plots/perObject/J1638+2827_landscape_20190920.png}
+  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
+  {../plots/perObject/J2228+2201_landscape_20190920.png}
+  \vspace{-12pt}
+  \caption[]{The threes high-$z$ CLQ quasars; 
+    SDSS J1205+3422 (top), 
+    SDSS J1638+2827 (middle), 
+    SDSS J2228+2201 (bottom). 
+    % A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
+  }
+  \label{fig:civ_clqs2}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Figure~\ref{fig:civ_clqs} presents the threes high-$z$ CLQ quasars. 
+%%
+%%
+For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
+For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
+standard UV/blue continuum slope increases in flux. 
+the UV/blue continuum diminishes and the shape of \lya changes.
+
 Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190920.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190919.tex
@@
 
-Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs) have now been 
-assembled \citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
-terms as a cover for the underlying physics. For sake of argument, ``Changing Look'' quasars can be 
-thought of as the extension of ``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas 
-the ``Changing State'' quasars (CSQs) have a `state-transition' similar to that in Galactic X-ray binaries
-\citep[e.g][]{NodaDone2018, Ruan2019}. 
-%
-These CLQs have primarily been defined according to the (recombination) Balmer emission line properties with 
-particular attention paid to the H$\beta$ emission line, usually observed from optical spectroscopy. 
-As such, current CLQ studies have been at redshifts $z<1$.
+Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing
+State'' quasars (CSQs) have now been assembled
+\citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
+terms as a cover for the underlying physics. For sake of argument,
+``Changing Look'' quasars can be thought of as the extension of
+``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas the
+``Changing State'' quasars (CSQs) have a `state-transition' similar to
+that in Galactic X-ray binaries \citep[e.g][]{NodaDone2018, Ruan2019}.
+These CLQs have primarily been defined according to the
+(recombination) Balmer emission line properties with particular
+attention paid to the H$\beta$ emission line, usually observed from
+optical spectroscopy.  As such, current CLQ studies have been at
+redshifts $z<1$.
 
@@
 types of Baldwin effect are present in the literature: the {\it
-global} (or {\it ensemble}) Baldwin Effect, which is an anti-correlation
-between the EW of the emission line and the underlying continuum
-luminosity of {\it single-epoch} observations of a {\it large number}
-of AGN and second, the {\it intrinsic} Baldwin effect, the same anti-correlation
-but in an {\it individual, variable} AGN \citep{PoggePeterson1992}.}.
-%%
-Dramatic changes in the collisionally excited  broad {\it emission} line (BEL) 
-of \civ (and indeed \ciii) have not to this point been seen.
+global} (or {\it ensemble}) Baldwin Effect, which is an
+anti-correlation between the EW of the emission line and the
+underlying continuum luminosity of {\it single-epoch} observations of
+a {\it large number} of AGN and second, the {\it intrinsic} Baldwin
+effect, the same anti-correlation but in an {\it individual, variable}
+AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
+collisionally excited broad {\it emission} line (BEL) of \civ (and
+indeed \ciii) have not to this point been seen.
 
@@
 %SDSS J222818.76+220102.9 (hereafter J2228+2201)  
-which show dramatic changes in their \civ\ and \ciii broad emission line
-properties as well as in the underlying continuum. We claim these are
-the first examples of ``Changing Look Quasars'' at high ($z>1$)
-redshift. Moreover, these are cases for dramatic changes of 
-ions with high ionization potentials (I.P.'s $>$2 Rydberg).
+which show dramatic changes in their \civ\ and \ciii broad emission
+line properties as well as in the underlying continuum. We claim these
+are the first examples of ``Changing Look Quasars'' at high ($z>1$)
+redshift. Moreover, these are the first cases for substantial changes
+of ions with high ionization potentials (I.P.'s $>$2 Rydberg), thus
+linking the ionizing photons to the energetic inner accretion disk,
+potentially by inverse Compton scattering lower energy photons to
+higher energies.  Furthermore, the measured rest-wavelengths of
+emission lines in quasar spectra, are known to vary from their nominal
+laboratory especially for the high-ionization broad lines,
+wavelengths, \citep[e.g.][]{VandenBerk2001}.
 
+In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for
+the \civ doublet \citep{Kramida2018}.
+%%  The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.
+%%  “24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
+%%  https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
+The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$.  Using the
+\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
+Atomic Spectra Database Ionization Energies Form} for ionisation
+energies, we see 11.3 eV is the energy needed for C I to dislodge one
+electron and become singly-ionised C II; 24.4 eV is energy needed for
+singly-ionised C II to dislodge an additional electron, and become
+doubly-ionised C III, and 47.89 eV (3.519 Ry) is required for
+doubly-ionised C III become triply--ionised \civ.  64.49 eV (4.74 Ry)
+is the energy needed to ionize \civ itself.
 %%
-In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for the \civ doublet
-%Example of how to reference these results:
-using the values from the National Institute of Standards and Technology (NIST) Atomic Spectra Database 
-\citep{Kramida2018}. 
-% A., Ralchenko, Yu., Reader, J., and NIST ASD Team (2018).
-NIST Atomic Spectra Database (ver.
-5.6.1), [Online].
-Available: https://physics.nist.gov/asd [2019, September 17].
-National Institute of Standards and Technology, Gaithersburg, MD.
-DOI: https://doi.org/10.18434/T4W30F
+The 1548.202 and 1550.774 \AA\ emission doublet is created by the 2$p$
+$^{2}P_{0}$ $---$ 2$s$ $^{2}S$ transition with energies 64,484
+cm$^{-1}$ and 64591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.
+%Ground  Shells:  1$s^{2}$2$s$. 
+%Ground  Level: $^{2}S_{1/2}$. 
+%Ionized  Level: 1$s^{2}$ $^{1}S_{0}$.
 
-%The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.
-
-%“24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
-%% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
-The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$.
-Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form}
-for ionisation energies, we see 
-11.3 eV is the energy needed for C I to dislodge one electron and become singly-ionised C II; 
-24.4 eV is energy needed for singly-ionised C II to dislodge an additional electron, and become doubly-ionised C III, 
-and 47.89 eV  (3.519 Ry) is required for doubly-ionised C III  become triply--ionised \civ. 
-64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.
-
-The 1548.202 	and 1550.774 \AA\ emission doublet is created by the 
-2$p$ $^{2}P_{0}$ $---$  2$s$ $^{2}S$ transition with 
-energies 64,484 cm$^{-1}$ and 64591 cm$^{-1}$ 
-\citep[e.g.][]{Moore1993}.
-
-Ground  Shells:  1$s^{2}$2$s$. 
-Ground  Level: $^{2}S_{1/2}$. 
-Ionized  Level: 1$s^{2}$ $^{1}S_{0}$.
-
-\subsection{Literature Search}
-\citet{Gregory1982} reported time variability in both Lya and \civ 1550 emission lines in the Seyfert galaxy NGC 5548.
-
-From \citet{VandenBerk2001} 
-The rest positions of emission lines in quasar spectra, especially the
-high-ionization broad lines, are known to vary from their nominal
-laboratory wavelengths \citep{Gaskell1982, Wilkes1986,  Espey1989, Espey1990Erratum, 
-ZhengSulentic1990, Corbin1990, Weymann1991, TytlerFan1992, 
-Brotherton1994, Laor1995, McIntosh1999}.
-
-\citet{Wilhite2006} examine the variability of the high-ionizaton
-C~\textsc{iv}$\lambda{1549}$ line in a sample of 105 quasars observed
-at multiple epochs by the Sloan Digital Sky Survey.  We find a strong
-correlation between the change in the C~\textsc{iv} line flux and the
-change in the line width, but no correlations between the change in
-flux and changes in line center and skewness.  The relation between
-line flux change and line width change is consistent with a model in
-which a broad line base varies with greater amplitude than the line
-core. The objects studied here are more luminous and at higher
-redshift than those normally studied for variability, ranging in
-redshift from 1.65 to 4.00 and in absolute $r$-band magnitude from
-roughly $-$24 to $-$28.  Using moment analysis line-fitting
-techniques, we measure line fluxes, centers, widths and skewnesses for
-the C~\textsc{iv} line at two epochs for each object.  The well-known
-Baldwin Effect is seen for these objects, with a slope $\beta =
--0.22$.  The sample has a median intrinsic Baldwin Effect slope of
-$\beta_{int} = -0.85$; the C~\textsc{iv} lines in these
-high-luminosity quasars appear to be less responsive to continuum
-variations than those in lower luminosity AGN.  Additionally, we find
-no evidence for variability of the well known blueshift of the
-C~\textsc{iv} line with respect to the low-ionization
-Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
-indicating that this blueshift might be useful as a measure of
-orientation.
+%%\subsection{Literature Search}
+\civ\ variability has been long studied, \citep[e.g., ][]{Baldwin1977,
+Gaskell1982, Gregory1982, Wilkes1986, Espey1989, Espey1990Erratum,
+ZhengSulentic1990, Corbin1990, Corbin1991, Weymann1991,
+Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
+Laor1995, McIntosh1999}.
+%%
+%\citet{Gregory1982} reported time variability in both Lya and \civ 1550 emission lines in the Seyfert galaxy NGC 5548.
+%
+%\citet{1994}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}
 
@@
 %% Vol. 22, Nos. 4–5, August–October 2003, pp. 681–689
+\citep{Nazarova2003} ...
+
+\citet{Wilhite2006} examine the variability of a C~\textsc{iv} 
+sample of 105 quasars observed at multiple epochs by the SDSS. 
+They find a strong correlation between the change in the C~\textsc{iv} line flux and the
+change in the line width, but no correlations between the change in 
+flux and changes in line center and skewness.  These authors find 
+that the relation between line flux change and line width change is consistent with a model in
+which a broad line base varies with greater amplitude than the line
+core. The C~\textsc{iv} lines in these 
+high-luminosity quasars appear to be less responsive to continuum
+variations than those in lower luminosity AGN.  
+%% Additionally, we find no evidence for variability of the well known
+blueshift of the C~\textsc{iv} line with respect to the low-ionization
+Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
+indicating that this blueshift might be useful as a measure of
+orientation.
 
@@
 
-\citet{Denney2015}, 
-%Denney, Kelly; SDSS-RM Team, ``The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project'' ; http://adsabs.harvard.edu/abs/2015AAS...22520403D
+\citet{Richards2011} explored the BELR in over 30,000 $z > 1.54$ SDSS
+quasars, concentrating on the properties of the \civ\ emission
+line. We consider two well-known effects involving the \civ\ emission
+line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
+the BEff) and the blueshifting of the peak of \civ\ emission with
+respect to the systemic redshift. These authors conclude that these
+two \civ\ parameters (EQW and blueshift) are capturing an important
+trade-off between ``disk'' and ``wind'' components in the disk-wind
+model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000, Proga2000}.  with one dominating over the other depending on the
+shape of the SED \citep[][]{Leighly2004b}.  (strong \civ EQW indicates
+a more ionizing SED and large \civ blueshift indicating a less
+ionizing SED).
+
+%% \citet{Grier2015}....
+%% \includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}
+%% \citet{Denney2015}, 
+%%Denney, Kelly; SDSS-RM Team, ``The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project'' ; http://adsabs.harvard.edu/abs/2015AAS...22520403D
 The Sloan Digital Sky Survey Reverberation Mapping (SDSS-RM) Project 
-spectroscopically monitored $\sim$850 quasars over a seven square
-degree field for approximately six months with the BOSS
-spectrograph. While the time series analysis of the quasar continuum
-and emission-line variability, and thereby the potential to measure
-reverberation time delays from this sample, is still underway, we have
-used the subset (roughly half) of this sample containing the \civ 1549\AA 
-broad emission line to investigate the effects of S/N on measuring
-this broad emission line width. Line width measurements are necessary
-for inferring the broad line region gas velocities used to determine
-the quasar black hole mass. However, literature studies have suggested
-line width measurements, and therefore black hole mass estimates, may
-be biased by the use of relatively low S/N, typical survey-quality,
-data, compared to the high S/N data that calibrate single-epoch black
-hole mass scaling relations. The SDSS-RM data set provides a unique
-opportunity to search for any systematic uncertainties in CIV line
-width measurements through a comparison of line widths measured from
-the single-epoch spectra, which are roughly equivalent to other
-SDSS/BOSS quasar spectra (though still twice the exposure time) to
-those measured from the high-S/N, campaign co-added spectra, which
-contain more than 30 epochs of each source. Here we present results
-from this investigation, which have implications for estimating CIV
-single-epoch black hole masses from the SDSS/BOSS and other surveys.
-
-%% Coatman et al. (2017, AAS; http://adsabs.harvard.edu/abs/2017AAS...22930203C) 
-%%Accurate black-hole (BH) mass estimates for high-redshift (z>2) quasars are essential for better understanding the relationship between super-massive BH accretion and star formation.
-Progress is currently limited by the large systematic errors in virial BH-masses derived from the CIV broad emission line, which is often significantly blueshifted relative to systemic, most likely due to outflowing gas in the quasar broad-line region.
-We have assembled Balmer-line based BHmasses for a large sample of 230 high-luminosity (1045.5-1048 ergs-1), redshift 1.5<z<4 quasars, which, for the first time, span the entire range of CIV blueshifts seen in the quasar population.
-We find the CIV-based BH-masses to be larger than the corresponding Balmer line-based masses by almost an order of magnitude at the most extreme blueshifts (˜5000 kms-1).
-An empirical correction to the CIV BH-masses is derived, which depends only on the properties of the CIV line itself (i.e.
-blueshift and FWHM).
-%%
-\citet{Coatman2017AAS} show that this new correction now enables the derivation of un-biased CIV-based virial BH masses for the majority of high-luminosity, high-redshift quasars.In the same high-luminosity quasar sample, we find the narrow [OIII] emission to be weaker and more asymmetric than is generally found in  lower-luminosity AGN and that a significant fraction of our quasars have exceptionally broad (FWHM $> 3000 km s^{-1}$), blueshifted [OIII] emission.
-We find a strong correlation between the \civ and [OIII] blueshifts.
-This correlation holds even for quasars at fixed
-luminosity and suggests that broad line region outflows in quasars are
-connected to galaxy-scale winds.
-
-\citet{Coatman2016} show that at high redshift, $z>2.1$, black hole
-masses are normally derived using the velocity width of the C IV
-$\lambda \lambda$1548, 1550 broad emission line, based on the
-assumption that the observed velocity widths arise from virial-
-induced motions. In many quasars, the \civ emission line exhibits
-significant blue asymmetries  with the line centroid
-displaced by up to thousands of km s$^{-1}$ to the blue. These blueshifts
-almost certainly signal the presence of strong outflows, most likely
-originating in a disc wind. We have obtained near-infrared spectra,
-including the H$\alpha$ $\lambda$6565 emission line, for 19 luminous 
-(L$_{\rm Bol} =46.5–47.5$ erg s$^{-1}$) Sloan Digital Sky Survey quasars, at redshifts $2 <
-z < 2.7$, with \civ emission lines spanning the full range of
-blueshifts present in the population. A strong correlation between C
-IV velocity width and blueshift is found and, at large blueshifts,
-$>$2000 km s$−1$, the velocity widths appear to be dominated by non-virial
-motions. Black hole masses, based on the full width at half-maximum of
-the \civ emission line, can be overestimated by a factor of 5 at large
-blueshifts. A larger sample of quasar spectra with both \civ and H$\beta$, 
-or H$\alpha$, emission lines will allow quantitative corrections to \civ-based black hole masses as a function of blueshift to be
-derived. We find that quasars with large \civ blueshifts possess high
-Eddington luminosity ratios and that the fraction of high-blueshift
-quasars in a flux-limited sample is enhanced by a factor of
-approximately 4 relative to a sample limited by black hole mass.
+\citep{Shen2015} has a  monitored $\sim$350 quasars with \civ
+Noting the biases associated with \civ Emission Line Properties 
+\citep[e.g. increasing systematic offsets with decreasing signal-to-noise][]{Denney2016}, 
+\citet{Grier2019} report 
+report significant time delays between the continuum and the CIV 1549 emission line in 52 quasars, 
+and investigate the \civ radius-luminosity relationship.
 
 %% \citet{Coatman2017} 
-The \civ $\lambda \lambda$1498,1501 broad emission line is visible in optical spectra to redshifts exceeding $z\sim5$.
+%The \civ $\lambda \lambda$1498,1501 broad emission line is visible in optical spectra to redshifts exceeding $z\sim5$. 
 \civ has long been known to exhibit significant displacements to the blue and these `blueshifts' almost certainly signal the presence of strong outflows.
@@
 \citet{Coatman2017} use a large sample of 230 high-luminosity (LBol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with both \civ and Balmer line spectra, we have quantified the bias in \civ BH masses as a function of the \civ blueshift.
-\civ BH masses are shown to be a factor of 5 larger than the corresponding Balmer-line masses at C IV blueshifts of 3000 km s-1 and are overestimated by almost an order of magnitude at the most extreme blueshifts, $\gtrsim$5000 km s$^{-1}$.
-Using the monotonically increasing relationship between the \civ blueshift and the mass ratio BH(\civ)/BH(H$\alpha$), we derive an empirical correction to all C IV BH masses.
+\civ BH masses are shown to be a factor of 5 larger than the corresponding Balmer-line masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated by almost an order of magnitude at the most extreme blueshifts, $\gtrsim$5000 km s$^{-1}$.
+%Using the monotonically increasing relationship between the \civ blueshift and the mass ratio BH(\civ)/BH(H$\alpha$), we derive an empirical correction to all C IV BH masses.
 The scatter between the corrected C IV masses and the Balmer masses is 0.24 dex at low C IV blueshifts ($\sim$0 km s-1) and just 0.10 dex at high blueshifts ($\sim$3000 km s$^{-1}$), compared to 0.40 dex before the correction.
@@
 Our results support the scenario that high-blueshift sources tend to have large Eddington ratios.
-
-\citet{Richards2011} 
-use a sample of $\sim$30,000 quasars from the 7th Data Release of the Sloan Digital Sky Survey, and explore the range of properties exhibited by high-ionization, broad emission lines, such as \civ $\lambda$1549.
-Specifically, we investigate the anti-correlation between continuum luminosity and emission-line equivalent width (the Baldwin Effect (BEff)) and the ``blueshifting''of the high-ionization emission lines with respect to low-ionization emission lines.
-%Employing improved redshift determinations from Hewett \& Wild, the blueshift of the C IV emission line is found to be nearly ubiquitous, with a mean shift of ~810 km s-1 for radio-quiet (RQ) quasars and ~360 km s-1 for radio-loud (RL) quasars.
-The BEff is present in both RQ and RL samples.
-We consider these phenomena within the context of an accretion disk-wind model that is modulated by the nonlinear correlation between ultraviolet and X-ray continuum luminosity.
-Composite spectra are constructed as a function of C IV emission-line properties in an attempt to reveal empirical relationships between different line species and the continuum.
-Within a two-component disk+wind model of the broad emission-line region (BELR), where the wind filters the continuum seen by the disk component, we find that RL quasars are consistent with being dominated by the disk component, while broad absorption line quasars are consistent with being dominated by the wind component.
-Some RQ objects have emission-line features similar to RL quasars; they may simply have insufficient black hole (BH) spin to form radio jets.
-Our results suggest that there could be significant systematic errors in the determination of L bol and BH mass that make it difficult to place these findings in a more physical context.
-It is possible to classify quasars in a paradigm where the diversity of BELR parameters is due to differences in an accretion disk wind between quasars (and over time); these differences are underlain primarily by the spectral energy distribution, which ultimately must be tied to BH mass and accretion rate.
-
-Also from \citet{Richards2011}, 
-At high redshift, two well-known properties of the Civ emission line are evident in quasar spectra (see Section 4).
-An anti-correlation between luminosity and the equivalent width (EQW) of C iv, generally known as the Baldwin Effect (BEff; Baldwin 1977), was first identified in 20 (mostly radio-loud (RL)) quasars and has been confirmed in much larger samples (e.g., Wu et al.
-2009).
-The other effect is the blueshifting of the C iv with respect to the systemic redshift (Gaskell 1982; Wilkes 1984).
-As with the BEff, these blueshifts have not only been confirmed with larger samples, but appear to be nearly ubiquitous in the quasar population (Sulentic et al.
-2000b; Richards et al.
-2002a).
-
-%\includegraphics\includegraphics[]{../../../../../Users/npr1/Downloads/Richards_2011_AJ_141_167.pdf}
-
-%\citet{1994}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___425__622P.pdf}
-
-%\citet{1994}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}
-
-\citet{Denney2016}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Denney_2016_ApJS_224_14.pdf}
-investigate the dependence on data quality of quasar properties
-measured from the C IV emission line region at high redshifts.  Our
-measurements come from 32 epochs of Sloan Digital Sky Survey
-Reverberation Mapping Project spectroscopic observations of 482 $z >
-1.46$ quasars. We compare the differences between measurements made
-from the single-epoch (SE) and coadded spectra, focusing on the \civ
-$\lambda$1549 emission line because of its importance for studies of
-high-redshift quasar demographics and physical properties, including
-black hole masses. In addition to statistical errors increasing (by
-factors of $\sim2-4$), we find increasing systematic offsets with
-decreasing signal-to-noise ratio (S/N).
-
-\citet{Grier2015}....
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}
-
-\citep{Corbin1991, Dimitrijevic1992, Wills1993, Brotherton1994, Osmer1994} ...
-
-\citep{Nazarova2003} ...
-
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}
-
+%%
+Therefore, the \civ\ or \heii\ EW is not an accurate indicator of the Eddington ratio or quasar SED.
+%%
 Recent investigations also include \citet{Meyer2019}.
 
-\iffalse
-\begin{figure}
-  \centering
-  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {figures/J2228+2201.png}
-  \vspace{-12pt}
-  \caption[]{J222818.7+220102.6. 
-% EMERGING., 
-The light curve shows it brightening from 20.5 to 19.5 over the 771 days observed-frame between the two SDSS spectra available. 
-A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] emerging on a new blue contiuum slope.}
-  \label{fig:disk_suppression}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {figures/J1638+2827.png}
-  \vspace{-12pt}
-  \caption[]{The quasar SDSS J163852.9+282708. 
-% Disappearing 
-A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.}
-  \label{fig:disk_suppression}
-\end{figure}
-\fi
+This paper is organised as follows. In Section 2, we describe our
+sample selection, catalogs and observationa data sets.  In Section 3,
+we present various theoretical models and discuss if and how each
+describes and explains the data.  We conclude in Section 4.  We report
+all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
+Fukugita1996} unless otherwise stated explicitly. For the WISE bands,
+$m_{\rm AB} = m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1
+at 3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively
+\citep{Cutri2011}. We choose the cosmological parameters
+$\Omega_{\Lambda} = 0.7$, $\Omega_{\rm M} = 0.3$, and $h = 0.7$ in
+order to be consistent with \citet{Shen2011}.
 

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190920v2.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190920.tex
@@
 
-In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for
-the \civ doublet \citep{Kramida2018}.
-%%  The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.
-%%  “24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
-%%  https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
-The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$.  Using the
-\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
-Atomic Spectra Database Ionization Energies Form} for ionisation
-energies, we see 11.3 eV is the energy needed for C I to dislodge one
-electron and become singly-ionised C II; 24.4 eV is energy needed for
-singly-ionised C II to dislodge an additional electron, and become
-doubly-ionised C III, and 47.89 eV (3.519 Ry) is required for
-doubly-ionised C III become triply--ionised \civ.  64.49 eV (4.74 Ry)
-is the energy needed to ionize \civ itself.
-%%
-The 1548.202 and 1550.774 \AA\ emission doublet is created by the 2$p$
-$^{2}P_{0}$ $---$ 2$s$ $^{2}S$ transition with energies 64,484
-cm$^{-1}$ and 64591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.
-%Ground  Shells:  1$s^{2}$2$s$. 
-%Ground  Level: $^{2}S_{1/2}$. 
-%Ionized  Level: 1$s^{2}$ $^{1}S_{0}$.
+In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for the \civ doublet \citep{Kramida2018}.
+The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$.
+Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form} for ionisation energies, we see 11.3 eV is the energy needed for C I to dislodge one electron and become singly-ionised C II; 24.4 eV is energy needed for singly-ionised C II to dislodge an additional electron, and become doubly-ionised C III, and 47.89 eV (3.519 Ry) is required for doubly-ionised C III become triply--ionised \civ.
+64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.
+The 1548.202 and 1550.774 \AA\ emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition with energies 64,484 cm$^{-1}$ and 64,591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.
 
@@
 Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
-Laor1995, McIntosh1999}.
+Laor1995, McIntosh1999, Nazarova2003}.
 %%
-%\citet{Gregory1982} reported time variability in both Lya and \civ 1550 emission lines in the Seyfert galaxy NGC 5548.
-%
-%\citet{1994}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}
-
-%% NAZAROVA 2003
-%% BROAD EMISSION LINES La, C IV AND Hb IN NGC 5548
-%% Astronomical and Astrophysical Transactions
-%% Vol. 22, Nos. 4–5, August–October 2003, pp. 681–689
-\citep{Nazarova2003} ...
-
-\citet{Wilhite2006} examine the variability of a C~\textsc{iv} 
-sample of 105 quasars observed at multiple epochs by the SDSS. 
-They find a strong correlation between the change in the C~\textsc{iv} line flux and the
-change in the line width, but no correlations between the change in 
-flux and changes in line center and skewness.  These authors find 
-that the relation between line flux change and line width change is consistent with a model in
-which a broad line base varies with greater amplitude than the line
-core. The C~\textsc{iv} lines in these 
+\citet{Wilhite2006} examine the variability of a C~\textsc{iv} sample
+of 105 quasars observed at multiple epochs by the SDSS.  They find a
+strong correlation between the change in the C~\textsc{iv} line flux
+and the change in the line width, but no correlations between the
+change in flux and changes in line center and skewness.  These authors
+find that the relation between line flux change and line width change
+is consistent with a model in which a broad line base varies with
+greater amplitude than the line core. The C~\textsc{iv} lines in these
 high-luminosity quasars appear to be less responsive to continuum
-variations than those in lower luminosity AGN.  
-%% Additionally, we find no evidence for variability of the well known
-blueshift of the C~\textsc{iv} line with respect to the low-ionization
-Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
-indicating that this blueshift might be useful as a measure of
-orientation.
-
-%% Punsly 2010
-%% Astrophysical Journal, 713, 232
-%% THE REDSHIFTED EXCESS IN QUASAR C iv BROAD EMISSION LINES
+variations than those in lower luminosity AGN.  \citet{Wilhite2006}
+find no evidence for variability of the well known blueshift of the
+C~\textsc{iv} line with respect to the low-ionization
+Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects.
 
@@
 trade-off between ``disk'' and ``wind'' components in the disk-wind
-model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000, Proga2000}.  with one dominating over the other depending on the
-shape of the SED \citep[][]{Leighly2004b}.  (strong \civ EQW indicates
-a more ionizing SED and large \civ blueshift indicating a less
-ionizing SED).
+model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
+Proga2000}.  with one dominating over the other depending on the shape
+of the SED \citep[][strong \civ EQW indicates a
+more ionizing SED and large \civ blueshift indicating a less ionizing
+SED]{Leighly2004b}.
 
-%% \citet{Grier2015}....
-%% \includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}
-%% \citet{Denney2015}, 
-%%Denney, Kelly; SDSS-RM Team, ``The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project'' ; http://adsabs.harvard.edu/abs/2015AAS...22520403D
-The Sloan Digital Sky Survey Reverberation Mapping (SDSS-RM) Project 
-\citep{Shen2015} has a  monitored $\sim$350 quasars with \civ
-Noting the biases associated with \civ Emission Line Properties 
-\citep[e.g. increasing systematic offsets with decreasing signal-to-noise][]{Denney2016}, 
-\citet{Grier2019} report 
-report significant time delays between the continuum and the CIV 1549 emission line in 52 quasars, 
-and investigate the \civ radius-luminosity relationship.
+The Sloan Digital Sky Survey Reverberation Mapping Project
+\cite[(SDSS-RM)][]{Shen2015} has a monitored $\sim$350 quasars with
+\civ Noting the biases associated with \civ Emission Line Properties
+\citep[e.g. increasing systematic offsets with decreasing
+signal-to-noise][]{Denney2016}, \citet{Grier2019} report report
+significant time delays between the continuum and the CIV 1549
+emission line in 52 quasars, and investigate the \civ
+radius-luminosity relationship.
 
@@
 \civ BH masses are shown to be a factor of 5 larger than the corresponding Balmer-line masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated by almost an order of magnitude at the most extreme blueshifts, $\gtrsim$5000 km s$^{-1}$.
-%Using the monotonically increasing relationship between the \civ blueshift and the mass ratio BH(\civ)/BH(H$\alpha$), we derive an empirical correction to all C IV BH masses.
-The scatter between the corrected C IV masses and the Balmer masses is 0.24 dex at low C IV blueshifts ($\sim$0 km s-1) and just 0.10 dex at high blueshifts ($\sim$3000 km s$^{-1}$), compared to 0.40 dex before the correction.
-The correction depends only on the C IV line properties - i.e.
-full width at half-maximum and blueshift - and can therefore be applied to all quasars where C IV emission line properties have been measured, enabling the derivation of unbiased virial BH-mass estimates for the majority of high-luminosity, high-redshift, spectroscopically confirmed quasars in the literature.
 
@@
 We use the measured quasar emission line properties from \citet{Shen2011} and \citet{Hamann2017}.
-\citet{Hamann2017} in particular investigate in robust detail the UV continuum and the \civ (and \nv $\lambda$ $\lambda$1238, 1242) emission lines in 
-over 200,000 quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line catalog 
-can be downloaded from \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
-The quasar redshift are limited to the range 1.53 ≤ ze ≤ 5.0 so that C IV and the adjacent continuum are covered by BOSS. 
-These measurements provide line profile information and N V/C IV flux ratios
-
-Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
-pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
-id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
-dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
-euismod. Cras vel auctor neque. Nam quis diam risus.
+\citet{Hamann2017} in particular investigate in robust detail the UV continuum and the \civ (and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000 quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line catalog can be downloaded from \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.} The quasar redshift are limited to the range 1.53 ≤ ze ≤ 5.0 so that C IV and the adjacent continuum are covered by BOSS.
+These measurements provide line profile information and N V/C IV flux ratios...
 

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190922.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190920v2.tex
@@
 \section{Data}
-%\subsection{Selection/Identification}
+%%\subsection{Selection/Identification}
+{\bf MJG to write a few notes on how the CIV CLQs were identified....}
+ Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam
+porta sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
+
+Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
+pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
+id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
+dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
+euismod. Cras vel auctor neque. Nam quis diam risus.
+
+\begin{table*}
+ \centering
+ \begin{tabular}{r  r  r r r   r r r r}
+  \hline \hline 
+% &&\\
+   Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{$dg$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}   & Exposure    & \multirow{3}{*}{Spectrum} & \multirow{3}{*}{Notes} \\
+   R.A.
+/ deg                   &               &               &            &                                &                                                                       &  Time         & & \\
+   Decl.
+/ deg                 &               &               &            &                                &                                                                       &  / seconds         & & \\
+
+% &&\\
+ \hline 
+                                       &                                   &                        &             &                          &                   &                             &  & \\
+   J120544.7+342252.4   & 2.068$\pm$0.0003   &   18.27            & 53498  &  2005-May-08  & SDSS             & ?                          & 53498-2089-427  & \\
+          181.436164           & 2.071                        & {\bf 17.99??}  & 58538  &  2019-Feb-24   & DBSP            &  2$\times$900    &                               &  Conditions? \\
+         +34.381229           &                                   &                          & 58693  &  2019-Jul-29    & DBSP            &  2$\times$1200   &                                &   \\
+                                       &                                   &               &              &                           &                   &                             &  & \\
+   J163852.9+282707.7   & 2.185$\pm$0.0004   &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
+      249.720558407	       &  2.186$\pm$0.0007   &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
+       +28.452158884        &  2.182             &                & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
+                                       &                                     &                   &              &                           &                   &                             &  & \\
+    J222818.7+220102.9   & 2.217$\pm$0.0021    & 19.97      & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
+        337.078194              & 2.222$\pm$0.0004    &                & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
+        +22.017478              &                                   &                & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
+                                        &                                     &                &            &                            &                   &                              &  & \\
+   \hline \hline   
+  \end{tabular}
+  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
+Exposure times are from the {\tt plate.fits} file. 
+DBSP on the Palomar 200-inch telescope is the } 
+ \label{tab:obs_notes}
+\end{table*}
 \subsection{Spectra}
@@
 
-\subsection{Line Properties}. 
+\subsection{Line Properties}  
 We use the measured quasar emission line properties from \citet{Shen2011} and \citet{Hamann2017}.
@@
 These measurements provide line profile information and N V/C IV flux ratios...
-
-\begin{table}
- \centering
- \begin{tabular}{l l l l}
-  \hline \hline 
-% &&\\
-   Quantity \ Object                           & J2228+2201     &  J1638+2827 \\
-% &&\\
- \hline 
-    &&\\
-    R.A. / deg                                        &    337.078194      &  249.720559\\
-    Declination / deg                            &    +22.017478      &  +28.452159 \\
-    redshift, $z$                                    &   2.222$\pm$0.00038   &  2.185$\pm$0.00043          \\
-    &&\\ 
-    \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
-                                         & 7582, 790, 56960	     & 5201, 178, 55832 \\    
- %   &&\\ 
-    %$M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
-    %log $(L_{\rm bol} / {\rm erg s}^{-1}) $      &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
-    %log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
-    %Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
-    &&\\
-    \hline \hline 
-  \end{tabular}
-  \caption{Physical properties of J1100-0053, J2317+0005 and J1052+1519 using the
-    methods from \citet{Shen2011}. *This spectrum was used to estimate
-    the quantities reported.  We use the regular definition of $L_{\rm
-      Edd} = 4 \pi G M m_{\rm p} c /\sigma_{T} =
-    1.26\times10^{38}\left (M/M_{\odot} \right )$ erg s$^{-1}$.} 
- \label{tab:Shen_props}
-\end{table}
-
-\begin{table*}
- \centering
- \begin{tabular}{r  r  r r r   r r r r}
-  \hline \hline 
-% &&\\
-   Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{Mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}   & Exposure    & \multirow{3}{*}{Spectrum} & \multirow{3}{*}{Notes} \\
-   R.A.
-/ deg                   &               &               &            &                                &                                                                       &  Time         & & \\
-   Decl.
-/ deg                 &               &               &            &                                &                                                                       &  / seconds         & & \\
-
-% &&\\
- \hline 
-                                       &                &               &            &                              &                   &                             &  & \\
-   J120544.7+342252.4   & 2.071     &   17.99   & 53498 & 2005-May-08   & SDSS             & ?                          & 53498-2089-427  & \\
-          181.436164           &                &               & 58538 & 2019-Feb-24     & DBSP            &  2$\times$900    &                               &  Conditions? \\
-         +34.381229           &                &               & 58693 & 2019-Jul-29      & DBSP            &  2$\times$1200   &                                &   \\
-                                       &                &               &              &                           &                   &                             &  & \\
-   J163852.9+282707.7   & 2.182     &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
-      249.720558407	       &               &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
-       +28.452158884        &               &              & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
-                                       &                &               &              &                           &                   &                             &  & \\
-    J222818.7+220102.9   & 2.222     & 19.97    & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
-        337.078194              &              &              & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
-        +22.017478                                &               &             & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
-                                       &                &               &            &                             &                   &                              &  & \\
-%   J232446.7+140029.5   &  0.916     &  18.83   &  56209 & 2012-Oct-09   & BOSS             & ?                             & 56209-6148-743   & \\
- %                                      &                &               &   58662 & 2019-Jun-28  &   (??)DBSP       & ?                            &  & \\
-  %                                     &                &               &              &                           &                   &                              &  & \\
-   \hline \hline   
-  \end{tabular}
-  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
-Exposure times are from the {\tt plate.fits} file. 
-DBSP on the Palomar 200-inch telescope is the } 
- \label{tab:obs_notes}
-\end{table*}
+\input{Ham17_clqs}
 
 \subsection{Multi-wavelength properties}
-MIR \\
-Radio \\
-{\bf FROM ROSS ET AL 2018!!!!} 
-While previous efforts have used the 1-year baseline of the WISE mission to identify
-changing-look quasars \citep[e.g.,][]{Assef2018, Stern2018}, our
-investigation is the first to extend this selection to the infrared
-using NEOWISE-R mission data. We have identified a sample of Sloan
-Digital Sky Survey (SDSS) quasars that show significant changes in
-their IR flux over the course of a few years. Importantly, our IR
-light curves enable us to set limits on SED changes due to
-obscuration.
-
-We use data from the
-beginning of the WISE mission \citep[2010 January; ][]{Wright2010}
-through the thrid-year of NEOWISE-R operations \citep[2016 December;
-][]{Mainzer2011}. The WISE scan pattern leads to coverage of the
-full-sky approximately once every six months (a ``sky pass''), but the
-satellite was placed in hibernation in 2011 February and then
-reactivated in 2013 October. Hence, our light curves have a cadence of
-6 months with a 32 month sampling gap.
-
-The W1/W2 light curves for $\sim$200,000 SDSS and BOSS spectroscopic
-quasars were obtained by performing forced photometry at the locations
-of DECam-detected optical sources \citep{Lang2014, Meisner2017a,
-Meisner2017b}. This forced photometry was performed on time-resolved
-coadds \citep{Lang2014}, each of which represents a stack of $\sim$12
-exposures. The coaddition removes the possibility of probing
-variability on $\lesssim$1 day time scales, but pushes $\approx$1.4
-magnitudes deeper than individual exposures while removing virtually
-all single-exposure artifacts (e.g. cosmic rays and satellites).
-
-Approximately $\sim$30,000 of the SDSS/BOSS quasars with W1/W2
-light-curves available are `IR-bright', in that they are above both
-the W1 and W2 single exposure thresholds and therefore detected at
-very high significance in the coadds. For this ensemble of objects,
-the typical variation in each quasar's measured (W1-W2) color is 0.06
-magnitudes.  This includes statistical and systematic errors which are
-expected to contribute variations at the few hundredths of a magnitude
-level. The typical measured single-band scatter is 0.07 magnitudes in
-each of W1 and W2.
-
-%%\newpage
-%% For the MNRAS Letter, not sure this can take up a full page...
-\begin{figure}
-  \centering
-  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
-% {figures/The_3_CIV_CLQs_20190917.pdf}
-   \vspace{-12pt}
-  \caption[]{The threes high-$z$ CLQ quasars; 
-SDSS J1205+3422 (top), 
-SDSS J1638+2827 (middle), 
-SDSS J2228+2201 (bottom). 
-%A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
-}
-  \label{fig:civ_clqs}
-\end{figure}
+We use data from the beginning of the WISE mission \citep[2010
+January; ][]{Wright2010} through the fifth-year of NEOWISE-R
+operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
+pattern leads to coverage of the full-sky approximately once every six
+months (a ``sky pass''), but the satellite was placed in hibernation
+in 2011 February and then reactivated in 2013 October. Hence, our
+light curves have a cadence of 6 months with a 32 month sampling gap.
+%Radio ??
 
@@
   }
-  \label{fig:civ_clqs2}
+  \label{fig:civ_clqs}
 \end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In the context of CLQs at lower-$z$...  Sociis natoque penatibus et
+In the context of CLQs at lower-$z$...  
+(Balmer CLQs vs. \civ CLQs...) 
+Sociis natoque penatibus et
 magnis dis parturient montes, nascetur ridiculus mus. Duis tempus,
@@
 tempus ac eget est. Curabitur malesuada arcu sit amet metus dictum at
-dapibus arcu accumsan. Fusce sollicitudin luctus rutrum.  Balmer CLQs
-vs. \civ CLQs...
-
-\subsection{J1205+3422 }
-SDSS J120544.67+342252.4, observed by SDSS, first reported in \citet{Schneider2007}. 
-Redshift of $z=$2.068$\pm$0.00027. 
-%% targeting_flags	SERENDIP_BLUE QSO_CAP
-plate	2089 
-mjd	53498
-fiberid	427
-
-\subsection{J1638+2827}
-SDSS J163852.93+282707.7       16h38m52.9s +28d27m08s  \\
-First reported in \citet{Schneider2010}. 
-Selected by {\tt SERENDIP\_BLUE} and {\tt QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
-Selected as a $z>2$ known quasar and passed BOSS quasar target selections \citep{Ross2012}.
-
-R.A. (J2000) = 249.72058 degs. \\
-Decl. (J2000) = 28.45217 degs. \\
-\href{skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232}{SDSS SkyServer} 
-All Spectra of this Object:: \\
-specObjId	plate	MJD	fiber	ra	dec	redshift \\
-5855854441601671168	5201	55832	178	2.186$\pm$0.00073\\
-3319321776793610240	2948	54553	614	2.185$\pm$0.00043\\
-
-\subsection{J2228+2201}
-SDSS J222818.76+220102.9 (R.A. 337.078194926, Decl. 22.017477924) was first reported in 
-\citet{Paris2017}.
-
-%%\href{https://skyserver.sdss.org/dr12/en/tools/chart/navi.aspx?ra=337.077916666667&dec=22.0173888888889&scale=0.2&width=120&height=120&opt=
-\href{skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655}{SDSS SkyServer}
-All Spectra of this Object:: \\
-specObjId	plate	MJD	fiber	ra	dec	redshift \\
-8536790363997708288	7582	56960	790	2.222$\pm$0.00038\\
-6888453645991387136	6118	56189	720	2.217$\pm$0.00208\\
-
-%Plate: 2948, MJD: 54553, Fiber: 0614
-%https://dr12.sdss.org/spectrumDetail?mjd=54553&fiber=614&plateid=2948
+dapibus arcu accumsan. Fusce sollicitudin luctus rutrum.
 

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190923.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190922.tex
@@
 
-%\hypersetup{draft}
+\hypersetup{draft}
 \begin{document}
@@
 
-Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing
-State'' quasars (CSQs) have now been assembled
-\citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
-terms as a cover for the underlying physics. For sake of argument,
-``Changing Look'' quasars can be thought of as the extension of
-``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas the
+The optical continuum variability of quasars has been recognized since
+their first optical identification 
+\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  However, dramatic
+changes in the broad emission lines (BELs) in quasars has only
+recently been identified \citep[e.g.][]{LaMassa2015}.  Samples of over
+100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars
+(CSQs) have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}. 
+The community uses both these terms as a cover for the
+underlying physics. For sake of argument, ``Changing Look'' quasars
+can potentially be thought of as the extension to the BELs of quasar
+continuum variability \citep[e.g.][]{MacLeod2012} whereas the
 ``Changing State'' quasars (CSQs) have a `state-transition' similar to
-that in Galactic X-ray binaries \citep[e.g][]{NodaDone2018, Ruan2019}.
+that in Galactic X-ray binaries \citep[e.g][]{NodaDone2018,
+Ruan2019}. In this paper, we use the term `Changing Look', as we are
+currently agnostic to the underlying physical processes.
+
 These CLQs have primarily been defined according to the
@@
 the Low Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I} telescope \citep{Oke1995}. 
-%% The Keck Low Resolution Imaging Spectrometer", Oke, J.B., et al.. 1995, PASP, 107, 375
 and the Double Spectrograph (DBSP) instrument on the Palomar {\it Hale} 5m telescope.
+
+\begin{table*}
+\begin{tabular}{ l rrrr rrrr rrrr rrrr rrrr rr|}
+\hline
+\hline 
+Object (MJD)               & $f$1450 & $\alpha_{\civ}$    & $\alpha_{\rm allc}$    & REW                       & cREW   &  wREW  & FWHM              & cFWHM  &  wFWHM  & $\sigma$     \\
+\hline 
+J1638+2827 (55832) & 1.4659    & -3.3547             & -4.026$\pm$0.452 & 42.76$\pm$1.96  & 26.72  & 16.03  & 5210$\pm$226 & 4651      & 13444    & 3702          \\
+J2228+2201 (56189) & 0.5101    & -1.5931             & -0.657$\pm$0.004 & 42.18$\pm$5.59  &  6.42   & 35.76  & 2994$\pm$620 & 1458      &   7636    & 3002           \\
+\hline
+\end{tabular}
+ \caption{
+Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
+\noindent {\tt f1450} = flux in the uncorrected BOSS spectrum at 1450 \AA\ rest (10$^{-17}$ ergs s$^{-1}$ cm$^{-2}$ \AA$^{-1}$) used to anchor the power law continuum fits beneath \civ\ and \nv , e.g., $f_{\lambda} = f_{1450}\, (\lambda /1450{\rm \AA})^{\alpha}$.
+\noindent {\tt $alpha_{\civ}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) measured from the BOSS spectrum on either side of \civ .
+\noindent {\tt $alpha_{\rm allc}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) between 1350 \AA\ and 2200 \AA\ in the flux corrected BOSS spectrum, listed only for quasars wit $z_{\rm e} \le 3.4$ (with 1$\sigma$ uncertainty).
+\noindent {\tt REW} = \civ\ REW (\AA ) from the line profile fit (with 1$\sigma$ uncertainty). 
+\noindent {\tt cREW} = \civ\ REW (\AA ) for the core Gaussian component.
+\noindent {\tt wREW} = \civ\ REW (\AA ) for the wing Gaussian component.
+\noindent {\tt FWHM} = \civ\ FWHM (km/s) from the line profile fit (with 1$\sigma$ uncertainty). 
+\noindent {\tt fwhmc} = \civ\ FWHM (km/s) for the core Gaussian only.
+\noindent {\tt fwhmw} = \civ\ FWHM (km/s) for the wing Gaussian only.
+\noindent {\tt $\sigma$} = \civ\ velocity dispersion (km/s) measured from the profile fit \citep{Peterson2004}.
+} 
+ \label{tab:Ham17_lines}
+\end{table*}
 
@@
 These measurements provide line profile information and N V/C IV flux ratios...
-\input{Ham17_clqs}
+%\input{Ham17_clqs}
 

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190924.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190923.tex
@@
 %\newauthor Daniel Stern$^{6}$, 
-%Aaron M. Meisner$^{7,8}$, Roberto J. Assef$^{9}$, Arjun Dey$^{10}$, Andrew J. Drake$^{11}$, \newauthor Hyunsung D. Jun$^{12}$, Dustin Lang$^{13,14,15}
 \\
@@
 (CSQs) have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}.
-The community uses both these terms as a cover for the
-underlying physics. For sake of argument, ``Changing Look'' quasars
-can potentially be thought of as the extension to the BELs of quasar
+The community uses both these terms as a cover for the underlying
+physics. For sake of argument, ``Changing Look'' quasars can
+potentially be thought of as the extension to the BELs of quasar
 continuum variability \citep[e.g.][]{MacLeod2012} whereas the
@@
 Ruan2019}. In this paper, we use the term `Changing Look', as we are
-currently agnostic to the underlying physical processes.
+currently agnostic, and somewhat ignorant, to the underlying physical
+processes.
 
@@
 
-In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for the \civ doublet \citep{Kramida2018}.
-The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$.
-Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form} for ionisation energies, we see 11.3 eV is the energy needed for C I to dislodge one electron and become singly-ionised C II; 24.4 eV is energy needed for singly-ionised C II to dislodge an additional electron, and become doubly-ionised C III, and 47.89 eV (3.519 Ry) is required for doubly-ionised C III become triply--ionised \civ.
-64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.
-The 1548.202 and 1550.774 \AA\ emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition with energies 64,484 cm$^{-1}$ and 64,591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.
+In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for
+the \civ doublet \citep{Kramida2018}. The ground state of carbon is
+1$s^2$ 2$s^2$ 2$p^2$.  Using the
+\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
+Atomic Spectra Database Ionization Energies Form} for ionisation
+energies, we see 11.3 eV is the energy needed for C I to dislodge one
+electron and become singly-ionised C II; 24.4 eV is energy needed for
+singly-ionised C II to dislodge an additional electron, and become
+doubly-ionised C III, and 47.89 eV (3.519 Ry) is required for
+doubly-ionised C III become triply--ionised \civ.  64.49 eV (4.74 Ry)
+is the energy needed to ionize \civ itself. The 1548.202 and 1550.774
+\AA\ emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$
+$^{2}S$ transition with energies 64,484 cm$^{-1}$ and 64,591 cm$^{-1}$
+\citep[e.g.][]{Moore1993}.
 
-%%\subsection{Literature Search}
+%%       B a c k g r o u n d     L i t e r a t u r e    
 \civ\ variability has been long studied, \citep[e.g., ][]{Baldwin1977,
@@
 Proga2000}.  with one dominating over the other depending on the shape
-of the SED \citep[][strong \civ EQW indicates a
-more ionizing SED and large \civ blueshift indicating a less ionizing
-SED]{Leighly2004b}.
+of the SED \citep[][strong \civ EQW indicates a more ionizing SED and
+large \civ blueshift indicating a less ionizing SED]{Leighly2004b}.
 
@@
 
-%% \citet{Coatman2017} 
-%The \civ $\lambda \lambda$1498,1501 broad emission line is visible in optical spectra to redshifts exceeding $z\sim5$. 
-\civ has long been known to exhibit significant displacements to the blue and these `blueshifts' almost certainly signal the presence of strong outflows.
-As a consequence, single-epoch virial black hole (BH) mass estimates derived from \civ velocity widths are known to be systematically biased compared to masses from the hydrogen Balmer lines.
-\citet{Coatman2017} use a large sample of 230 high-luminosity (LBol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with both \civ and Balmer line spectra, we have quantified the bias in \civ BH masses as a function of the \civ blueshift.
-\civ BH masses are shown to be a factor of 5 larger than the corresponding Balmer-line masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated by almost an order of magnitude at the most extreme blueshifts, $\gtrsim$5000 km s$^{-1}$.
+\civ has long been known to exhibit significant displacements to the
+blue and these `blueshifts' almost certainly signal the presence of
+strong outflows. As a consequence, single-epoch virial black hole (BH)
+mass estimates derived from \civ velocity widths are known to be
+systematically biased compared to masses from the hydrogen Balmer
+lines. \citet{Coatman2017} use a large sample of 230 high-luminosity
+(LBol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with
+both \civ and Balmer line spectra, we have quantified the bias in \civ
+BH masses as a function of the \civ blueshift. \civ BH masses are
+shown to be a factor of 5 larger than the corresponding Balmer-line
+masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated
+by almost an order of magnitude at the most extreme blueshifts,
+$\gtrsim$5000 km s$^{-1}$.
 
-\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the Sloan Digital Sky Survey Reverberation Mapping project to investigate the dependence of the blueshift of \civ relative to \mgii on quasar properties.
-We confirm that high-blueshift sources tend to have low \civ equivalent widths (EWs), and that the low-EW sources span a range of blueshift.
-Other high-ionization lines, such as He II, also show similar blueshift properties.
-The ratio of the line width (measured as both the full width at half maximum and the velocity dispersion) of \civ to that of \mgii increases with blueshift.
-Quasar variability enhances the connection between the \civ blueshift and quasar properties (e.g., EW).
-The variability of the \mgii line center (i.e., the wavelength that bisects the cumulative line flux) increases with blueshift.
-In contrast, the C IV line center shows weaker variability at the extreme blueshifts.
-Quasars with the high-blueshift \civ lines tend to have less variable continuum emission, when controlling for EW, luminosity, and redshift.
-Our results support the scenario that high-blueshift sources tend to have large Eddington ratios.
-%%
-Therefore, the \civ\ or \heii\ EW is not an accurate indicator of the Eddington ratio or quasar SED.
+\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
+Sloan Digital Sky Survey Reverberation Mapping project to investigate
+the dependence of the blueshift of \civ relative to \mgii on quasar
+properties. We confirm that high-blueshift sources tend to have low
+\civ equivalent widths (EWs), and that the low-EW sources span a range
+of blueshift. Other high-ionization lines, such as He II, also show
+similar blueshift properties. The ratio of the line width (measured as
+both the full width at half maximum and the velocity dispersion) of
+\civ to that of \mgii increases with blueshift. Quasar variability
+enhances the connection between the \civ blueshift and quasar
+properties (e.g., EW). The variability of the \mgii line center (i.e.,
+the wavelength that bisects the cumulative line flux) increases with
+blueshift. In contrast, the C IV line center shows weaker variability
+at the extreme blueshifts. Quasars with the high-blueshift \civ lines
+tend to have less variable continuum emission, when controlling for
+EW, luminosity, and redshift. Our results support the scenario that
+high-blueshift sources tend to have large Eddington ratios.
+Therefore, according to this study, the \civ\ or \heii\ EW is not an
+accurate indicator of the Eddington ratio or quasar SED.
 %%
@@
 
+The purpose of this paper is, for the first time, to access and 
+report on the ``Changing-Look'' quasar phenomenon at high, 
+$z>2$ redshift. By doing so, we move from the low-ionization 
+energy Balmer emission line series to the high-ionization emission 
+lines, in particular \civ.
+
 This paper is organised as follows. In Section 2, we describe our
 sample selection, catalogs and observationa data sets.  In Section 3,
-we present various theoretical models and discuss if and how each
-describes and explains the data.  We conclude in Section 4.  We report
-all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
+we present the high-$z$ quasars and report the line properties for the
+quasars at the observed epochs.  We give a very brief theoretical
+discussio in Section 4. We present our Conculsions in Seciton 5.  We
+report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
 Fukugita1996} unless otherwise stated explicitly. For the WISE bands,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}
+  \centering
+  \begin{tabular}{r  r  r r r   r r r r}
+  \hline 
+  \hline 
+    Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{$g$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
+    R.A.
+/ deg                   &                                         &                                                          &                                 &                                   &                                               &  Time           & Spectrum                 & \\
+    Decl.
+/ deg                 &                                         &                                                          &                                &                                     &                                              &  / seconds    & Plate-FiberID  & \\
+  \hline 
+                                     &                                          &                        &             &                            &                    &                             &                              & \\
+ J120544.7+342252.4  & 2.068$\pm$0.0003          &   18.27             & 53498  &  2005-May-08   & SDSS             & ?                          & 2089-427             & \\
+        181.436164          & 2.071                               & {\bf 17.99??}   & 58538  &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions? \\
+       +34.381229           &                                        &                          & 58693  &  2019-Jul-29     & DBSP            &  2$\times$1200   &                              &   \\
+                                     &                                        &                          &              &                          &                   &                                &                              & \\
+ J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77               & 54553 & 2008-Mar-28     & SDSS             & ?                          &  2948-614              & \\
+    249.720558	             &  2.186$\pm$0.0007      &                           & 55832  & 2011-Sep-28     & BOSS            &   3603                  &  5201-178            & \\
+     +28.452159             &  2.182                           &                           & 58583 & 2019-Apr-10      & LRIS              &  2$\times$900    &                              & \\
+                                      &                                      &                          &              &                           &                   &                              &                                & \\
+ J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                 & 56189 & 2012-Sep-19      & BOSS             &  2702                 &   6118-720          & \\
+      337.078194             & 2.222$\pm$0.0004      &                          & 56960 & 2014-Oct-30      & BOSS             & ?                         &   7582-790          & QSO1-REOBS \\ 
+      +22.017478            &                                      &                          & 58693 & 2019-Jul-29        & DBSP              & 2$\times$1200  &                           &    \\
+                                      &                                     &                           &            &                             &                   &                              &                            & \\
+   \hline \hline   
+  \end{tabular}
+  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
+Exposure times are from the {\tt plate.fits} file. 
+DBSP on the Palomar 200-inch telescope is the } 
+ \label{tab:obs_notes}
+\end{table*}
 \section{Data}
 %%\subsection{Selection/Identification}
-{\bf MJG to write a few notes on how the CIV CLQs were identified....}
- Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam
+{\bf MJG to write a few notes on how the CIV CLQs were identified} 
+lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam
 porta sodales est, vel cursus risus porta non. Vivamus vel pretium
@@
 
-\begin{table*}
+\begin{figure*}
   \centering
- \begin{tabular}{r  r  r r r   r r r r}
-  \hline \hline 
-% &&\\
-   Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{$dg$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}   & Exposure    & \multirow{3}{*}{Spectrum} & \multirow{3}{*}{Notes} \\
-   R.A.
-/ deg                   &               &               &            &                                &                                                                       &  Time         & & \\
-   Decl.
-/ deg                 &               &               &            &                                &                                                                       &  / seconds         & & \\
-
-% &&\\
- \hline 
-                                       &                                   &                        &             &                          &                   &                             &  & \\
-   J120544.7+342252.4   & 2.068$\pm$0.0003   &   18.27            & 53498  &  2005-May-08  & SDSS             & ?                          & 53498-2089-427  & \\
-          181.436164           & 2.071                        & {\bf 17.99??}  & 58538  &  2019-Feb-24   & DBSP            &  2$\times$900    &                               &  Conditions? \\
-         +34.381229           &                                   &                          & 58693  &  2019-Jul-29    & DBSP            &  2$\times$1200   &                                &   \\
-                                       &                                   &               &              &                           &                   &                             &  & \\
-   J163852.9+282707.7   & 2.185$\pm$0.0004   &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
-      249.720558407	       &  2.186$\pm$0.0007   &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
-       +28.452158884        &  2.182             &                & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
-                                       &                                     &                   &              &                           &                   &                             &  & \\
-    J222818.7+220102.9   & 2.217$\pm$0.0021    & 19.97      & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
-        337.078194              & 2.222$\pm$0.0004    &                & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
-        +22.017478              &                                   &                & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
-                                        &                                     &                &            &                            &                   &                              &  & \\
-   \hline \hline   
-  \end{tabular}
-  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
-Exposure times are from the {\tt plate.fits} file. 
-DBSP on the Palomar 200-inch telescope is the } 
- \label{tab:obs_notes}
-\end{table*}
+  %% trim=l b r t
+  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
+  {figures/J1205+3422_landscape_20190920.png}
+  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
+  {figures/J1638+2827_landscape_20190920.png}
+  \includegraphics[width=16.7cm, trim=0.0cm 0.0cm  0.2cm 0.1cm, clip]
+  {figures/J2228+2201_landscape_20190920.png}
+  \vspace{-12pt}
+  \caption[]{The threes high-$z$ CLQ quasars; 
+    SDSS J1205+3422 (top), 
+    SDSS J1638+2827 (middle), 
+    SDSS J2228+2201 (bottom). 
+The light curve data is present in the panels on the left hand side, with the 
+spectral epoch observational timings given by the vertical lines. 
+The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
+complex, the \civ line and the \mgii line. 
+  }
+  \label{fig:civ_clqs}
+\end{figure*}
 \subsection{Spectra}
-An overview of our spectroscopic observations is given in Table~\ref{tab:obs_notes}. 
-The spectra are from the SDSS \citep{Stoughton2002, DR7, Schneider2010},  
-the SDSS-III Baryon Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011, Dawson2013, Smee2013, Alam2015, Paris2017} 
-and the SDSS-IV  Extended Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016, Abolfathi2018}. 
-These quasars were targetted via a range of techniques and algorithms \citep[][]{Richards2002, Ross2012, 
-Myers2015}.  
-These data are supplemented by spectra from 
-the Low Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I} telescope \citep{Oke1995}. 
-and the Double Spectrograph (DBSP) instrument on the Palomar {\it Hale} 5m telescope.
+An overview of our spectroscopic observations is given in
+Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
+\citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
+Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011,
+Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
+Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
+Abolfathi2018}.  These quasars were targetted via a range of
+techniques and algorithms \citep[][]{Richards2002, Ross2012,
+Myers2015}.  These data are supplemented by spectra from the Low
+Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I}
+telescope \citep{Oke1995}.  and the Double Spectrograph (DBSP)
+instrument on the Palomar {\it Hale} 5m telescope.
 
@@
 \hline 
-Object (MJD)               & $f$1450 & $\alpha_{\civ}$    & $\alpha_{\rm allc}$    & REW                       & cREW   &  wREW  & FWHM              & cFWHM  &  wFWHM  & $\sigma$     \\
+Object (MJD)               & $f$1450 & $\alpha_{\rm C IV}$    & $\alpha$    & REW                       & cREW   &  wREW  & FWHM              & cFWHM  &  wFWHM  & $\sigma$     \\
 \hline 
@@
  \caption{
-Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
-\noindent {\tt f1450} = flux in the uncorrected BOSS spectrum at 1450 \AA\ rest (10$^{-17}$ ergs s$^{-1}$ cm$^{-2}$ \AA$^{-1}$) used to anchor the power law continuum fits beneath \civ\ and \nv , e.g., $f_{\lambda} = f_{1450}\, (\lambda /1450{\rm \AA})^{\alpha}$.
-\noindent {\tt $alpha_{\civ}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) measured from the BOSS spectrum on either side of \civ .
-\noindent {\tt $alpha_{\rm allc}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) between 1350 \AA\ and 2200 \AA\ in the flux corrected BOSS spectrum, listed only for quasars wit $z_{\rm e} \le 3.4$ (with 1$\sigma$ uncertainty).
-\noindent {\tt REW} = \civ\ REW (\AA ) from the line profile fit (with 1$\sigma$ uncertainty). 
-\noindent {\tt cREW} = \civ\ REW (\AA ) for the core Gaussian component.
-\noindent {\tt wREW} = \civ\ REW (\AA ) for the wing Gaussian component.
-\noindent {\tt FWHM} = \civ\ FWHM (km/s) from the line profile fit (with 1$\sigma$ uncertainty). 
+Measured line values using the methods and catalogue from \citet{Hamann2017}. 
+\noindent {\tt f1450} = flux in the uncorrected BOSS spectrum at 1450 \AA\ rest (10$^{-17}$ ergs s$^{-1}$ cm$^{-2}$ \AA$^{-1}$) used to anchor the power law continuum fits beneath \civ\ and \nv , 
+                                     e.g., $f_{\lambda} = f_{1450}\, (\lambda /1450{\rm \AA})^{\alpha}$; 
+\noindent {\tt $\alpha_{\rm C IV}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) measured from the BOSS spectrum on either side of \civ ; 
+\noindent {\tt $\alpha$}                            = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) between 1350 \AA\ and 2200 \AA\ in the flux corrected BOSS spectrum; 
+\noindent {\tt REW} = \civ\ REW (\AA ) from the line profile fit;
+\noindent {\tt cREW} = \civ\ REW (\AA ) for the core Gaussian component;
+\noindent {\tt wREW} = \civ\ REW (\AA ) for the wing Gaussian component; 
+\noindent {\tt FWHM} = \civ\ FWHM (km/s) from the line profile fit; 
 \noindent {\tt fwhmc} = \civ\ FWHM (km/s) for the core Gaussian only.
@@
 \noindent {\tt $\sigma$} = \civ\ velocity dispersion (km/s) measured from the profile fit \citep{Peterson2004}.
+Errors were given are 1$\sigma$ uncertainties. 
 } 
@@
 
+\begin{table*}
+\begin{tabular}{ l rrr rrr rrr rrr}
+\hline
+\hline
+  \multicolumn{1}{c}{Object (MJD)} &
+  \multicolumn{1}{c}{$M_{\rm I}(z=2)$} &
+  \multicolumn{1}{c}{$\log$($L_{\rm Bol} / {\rm erg s}^{-1}$} &
+  \multicolumn{1}{c}{$\log(L_{\rm CIV})$} &
+  \multicolumn{1}{c}{FWHM} &
+  \multicolumn{1}{c}{EW} &
+  \multicolumn{1}{c}{$\alpha$} &
+  \multicolumn{1}{c}{$\log$BH } &
+  \multicolumn{1}{c}{$\log$(Edd ratio)} \\
+\hline
+  J1205+3422 (53498)   & 
+  -27.742                      & 47.22$\pm$0.004    &    %46.37$\pm$0.009    & 46.634$\pm$0.004   & 44.896$\pm$0.013 & 
+44.896$\pm$0.014     &   5230$\pm$219          & 30.1$\pm$1.21        &  -1.467$\pm$0.076    &  % & 27.59                         & 1118$\pm$133.5 & 
+  9.494$\pm$0.036    &  -0.378 \\
+%%
+ J1638+2827 (54553)   & 
+ -26.750                      & 46.17$\pm$0.040    & %45.50$\pm$0.086      & 45.586$\pm$0.040 & 44.449$\pm$0.036   & 
+44.449$\pm$0.036    &  4180$\pm$736          & 100.5$\pm$11.9      & -0.137$\pm$0.677    &   % & 4.630                      & 680$\pm$133.5         & 
+  8.743$\pm$0.154     & -0.677  \\
+\hline
+\hline
+\end{tabular}
+ \caption{
+Measured line values using the methods and catalogue from
+\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
+$K$-corrected to $z = 2$; Bolometric luminosity computed from the
+monochromatic luminosity at 1350\AA\ using the spectral fits and
+bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
+luminosity, FWHM, rest-frame equivalent width, and their errors for
+the whole \civ profile.  Power-law slope $\alpha_{\lambda}$ for the
+continuum fit for \civ; Virial BH masses using calibrations of
+\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
+virial BH mass.
+}
+ \label{tab:Shen11_lines}
+\end{table*}
+
 \subsection{Line Properties}  
-We use the measured quasar emission line properties from \citet{Shen2011} and \citet{Hamann2017}.
-\citet{Hamann2017} in particular investigate in robust detail the UV continuum and the \civ (and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000 quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line catalog can be downloaded from \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.} The quasar redshift are limited to the range 1.53 ≤ ze ≤ 5.0 so that C IV and the adjacent continuum are covered by BOSS.
-These measurements provide line profile information and N V/C IV flux ratios...
-%\input{Ham17_clqs}
+We use the measured quasar emission line properties from
+\citet{Shen2011} and \citet{Hamann2017}. \citet{Hamann2017} in
+particular investigate in robust detail the UV continuum and the \civ
+(and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000
+quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line
+catalog can be downloaded from
+\href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
+The quasar redshift are limited to the range $1.53 \leq z \leq 5.0$ so
+that \civ and the adjacent continuum are covered by BOSS. These
+measurements provide line profile information and N V/C IV flux
+ratios.
 
@@
 
-\begin{figure*}
-  \centering
-  %% trim=l b r t
-  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
-  % {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
-  {../plots/perObject/J1205+3422_landscape_20190920.png}
-  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
-  {../plots/perObject/J1638+2827_landscape_20190920.png}
-  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
-  {../plots/perObject/J2228+2201_landscape_20190920.png}
-  \vspace{-12pt}
-  \caption[]{The threes high-$z$ CLQ quasars; 
-    SDSS J1205+3422 (top), 
-    SDSS J1638+2827 (middle), 
-    SDSS J2228+2201 (bottom). 
-    % A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
-  }
-  \label{fig:civ_clqs}
-\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%
-For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
-For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
-standard UV/blue continuum slope increases in flux. 
-the UV/blue continuum diminishes and the shape of \lya changes.
+For J1638+2827, over the course of 1279 days observed, 400 days in the
+rest-frame, the broad \civ and \ciii BEL start to fade.  For
+J2228+2201, over the course of 771 days observed, 240 days in the
+rest-frame, broad \civ and \ciii BELs both emerge and the standard
+UV/blue continuum slope increases in flux.  the UV/blue continuum
+diminishes and the shape of \lya changes.
 
@@
   \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {../plots/Wilhite/Wilhite_2006_Fig2_redux_20190830.png}
+  {figures/Wilhite_2006_Fig2_redux_20190924.png}
 % {figures/The_3_CIV_CLQs_20190917.pdf}
    \vspace{-12pt}
-  \caption[]{
-The Change in \civ line width vs. line flux change. 
-Data from \citet{Wilhite2006} with a sample of 105 quasars observed at
-multiple epochs by the Sloan Digital Sky Survey. We find a strong
-correlation between the change in the C iv line flux and the change in
-the line width, but no correlations between the change in flux and
-changes in line center and skewness.}
+  \caption[]{The Change in \civ line width vs. line flux change. 
+We compare our object J1638+2827 with the sample 
+from \citet{Wilhite2006} with a sample of 105 quasars observed at
+multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
+in this parameter space.}
   \label{fig:Wilhite2006_comparison}
@@
   \centering
-  \begin{tabular}{l  l  l    lll}
+  \begin{tabular}{l  rrr  }
     \hline \hline 
-    Line 	    &   Rest	      & Line       & Line	       &	Line			                 &   Continuum \\ 
-    Name	    &   Wavelength  &  $z$       & $\sigma$ 	&	Flux			                 & \\
-                    &    $\AA $        &              & /  km s$-1$	&     10$^{-17}$ erg/cm$2$/s &  10$^{-17}$ erg/cm$^2$/s/\AA  \\
-Ly$\alpha$  &	 1215.7	&	2.186      &	1362	&	510.5		                &	7.224 \\
-\nv		    &   1240.8	&	2.184     &	 854.6	&	122.4	                    	&	5.546 \\ 
-\civ		    &  1549.5	&	2.184    &	1927	&	462.6		                &	2.722 \\ 
-\heii	    &	 1640.4	&	2.184    &	1927	&    	  8.067	                   	&	2.447 \\  
-\ciii 	    &	 1908.7	&	2.184    &	1927	&	164.6	                   	&	1.966  \\ 
-\mgii	    &	 2800.3	&	2.184   & 	1927	&	187.4	                   	&	1.513  \\
+    J1205+3422           &                             &                      &  \\
+                                   & \multicolumn{3}{l}{MJD 53498}         \\
+                                  &                              &                    &     \\
+
+    Line                         & Line  $\sigma$   & Line  Flux    &   Cont.  Flux  \\
+   \hline                       
+    Ly$\alpha$1215.7   &   1362	          &	510.5       &  7.224    \\
+    \nv1240.8	            &     855	          &	122.4     	&  5.546   \\
+    \civ1549.5         	    &	 1927	          &	462.6	&  2.722   \\
+    \heii1640.4	            &	 1927    	          &      8.1	&  2.447   \\
+    \ciii1908.7        	    &	 1927	          &	164.6	&  1.966   \\
+    \mgii2800.3	    &   1927	          &	187.4	&  1.513   \\
+%                                  &                             &                   &                \\  
    \hline \hline   
   \end{tabular}
-  \caption{Line Measurement Information}
- \label{tab:line_values}
+  \caption{Line Measurement Information from the DR12 Science Archive Server (SAS). 
+    Line $\sigma$ in units of   km s$^{-1}$; 
+    Line flux          in units of  10$^{-17}$ erg/cm$^2$/s; 
+    Continuum      in units of  10$^{-17}$ erg/cm$^2$/s/ \AA; 
+}
+ \label{tab:J1205_line_values}
 \end{table*}
+Cras in laoreet mauris. Vivamus nec nulla a dui commodo
+adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor
+ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus
+et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida
+sagittis quis in sem. Phasellus quis risus bibendum eros luctus
+auctor.
+
+Cras in laoreet mauris. Vivamus nec nulla a dui commodo
+adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor
+ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus
+et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida
+sagittis quis in sem. Phasellus quis risus bibendum eros luctus
+auctor.
 
@@
     \hline \hline 
-                                    &                               &                                           &                                                      &                                  &                         & \\
-                                  \multicolumn{7}{c}{J1638+2827}  \\
-                                    &                               &                                           &                                                      &                                  &                         & \\
+    J1638+2827              &                               &                  &                       &                           &                   &                      \\  
+                                      & \multicolumn{3}{l}{MJD 54553}                            & \multicolumn{3}{l}{MJD 55832}                        \\
+    Line      	             & Line  $\sigma$     & Line  Flux    &   Cont. Flux   & Line  $\sigma$  & Line  Flux    &   Cont. Flux  \\
    \hline                       
-%                                   &                               &                                           &                                                      &                                  &                         & \\
-    Line      	             & Line  $\sigma$     & Line  Flux                           &   Continuum                                 & Line  $\sigma$          & Line  Flux        &   Continuum                                    \\
-%    Wavelength	             & /  km s$^{-1}$         &   10$^{-17}$ erg/cm$2$/s  & 10$^{-17}$ erg/cm$^2$/s/\AA      &  /  km s$-1$             & / 10$^{-17}$ erg/cm$2$/s   & /10$^{-17}$ erg/cm$^2$/s/\AA       \\
-                                     & \multicolumn{3}{l}{MJD 54553}                                                                                   & \multicolumn{3}{l}{MJD 55832}                                                                                                          \\
     Ly$\alpha$1215.7    &  1362	            &	510.5	    &	7.224            & 1769                &  633.9	              &  5.376     \\
@@
     \civ1549.5         	    &	 1927	            &	462.6	    &	2.722            & 2287	         &  125.1		      &  1.256      \\  
-    \heii1640.4	            &	 1927    	            &      8.067	                   	  &	2.447                                           & 2287	                &    10.68	      &  1.001\\  
-    \ciii1908.7        	    &	 1927	            &	164.6	                   	  &	1.966                                          & 2287	 	                &     29.53	      &  0.6008\\ 
-    \mgii2800.3	    &   1927	            &	187.4	                   	  &	1.513                                          & 2287 	 	         &    34.66	      &  0.3461  \\
-                                    &                               &                                           &                                                      &                                  &                           &                \\
+    \heii1640.4	            &	 1927    	            &      8.067	    &	2.447            & 2287	         &    10.7	      &  1.001\\  
+    \ciii1908.7        	    &	 1927	            &	164.6	    &	1.966            & 2287	 	 &    29.5	      &  0.6008\\ 
+    \mgii2800.3	    &   1927	            &	187.4	    &	1.513            & 2287 	 	 &    34.7	      &  0.3461  \\
+%                                    &                               &                                           &                                                      &                                  &                           &                \\
    \hline \hline   
   \end{tabular}
-  \caption{Line Measurement Information. 
-    Line $\sigma$ in units of   km s$-1$; 
+  \caption{Line Measurement Information from the DR12 Science Archive Server (SAS). 
+    Line $\sigma$ in units of   km s$^{-1}$; 
     Line flux          in units of  10$^{-17}$ erg/cm$^2$/s; 
@@
 }
- \label{tab:line_values}
+ \label{tab:1638_line_values}
 \end{table*}
-
-%Plate: 5201, MJD: 55832, Fiber: 178
-%https://dr12.sdss.org/spectrumDetail?mjd=55832&fiber=178&plateid=5201
-
-%Line		Rest		        Line	        Line		        Line			   Continuum
-%Name		Wavelength	z	        sigma 		Flux	
-%                       [Å]			               [km s-1]  	[10-17erg/cm2/s] 	   [10-17erg/cm2/s/Å]
-%Ly_alpha	1215.7		2.186	1769		633.9		   5.376
-%N_V		1240.8		2.185	1012		107.1		   4.645
-%C_IV		1549.5		2.185	2287		125.1		   1.256
-%He_II		1640.4		2.185	2287		 10.68		   1.001
-%C_III]		1908.7		2.185	2287	 	 29.53		   0.6008
-%Mg_II		2800.3		2.185	2287 	 	 34.66		   0.3461
-
-%So, ratios, MJD 54553 / MJD 55832::
-%$Ly_alpha	1215.7		—	0.770		0.805			1.344			
-%N_V		1240.8		—	0.844		1.143			1.194
-%C_IV		1549.5		—	0.843		3.698			2.167			
-%He_II		1640.4		—	0.843		0.755			2.445			
-%C_III]		1908.7		—	0.843		5.574			3.27			
-%Mg_II		2800.3		—	0.843		5.407			4.37
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
-%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
-%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and Conclusions}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
+%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
+%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+  \centering
+  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
+  {figures/CIV_CLQs_hexplot_20190923.png}
+   \vspace{-12pt}
+  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
+of the \civ emission line in the BOSS DR12 quasar sample using the catalogue 
+of \citet{Hamannn2017}. Note the REW logarithmic scaling.}
+  \label{fig:REWvsFWHM}
+\end{figure}
+
+\section{Discussion and Conclusions}
+The variable properties of the rest-frame UV quasar emission lines
+have been long studied, with the global (or ensemble) Baldwin Effect
+(the anti-correlation between the EW of the emission line and the
+underlying continuum luminosity of single-epoch observations of a
+large number of AGN, first noted in \citet{Baldwin1977}. 
+%%
+More recently, the intrinsic Baldwin effect, the same anti-correlation but in an individual, variable AGN.
+%
+The variable properites of high-$z$ quasars, however, has been less 
+well stuided. Reasons for this include more massive systems will tend to 
+have longer timescales e.g. with $R_{\rm Sch}= 2GM /c^{2}$ and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$
+means   $t_{\rm dyn} \sim 6G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2} $.
+
 Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
@@
 nisi. Vestibulum nec mi justo, eget dapibus velit.
-
-Cras in laoreet mauris. Vivamus nec nulla a dui commodo
-adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor
-ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus
-et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida
-sagittis quis in sem. Phasellus quis risus bibendum eros luctus
-auctor.
 

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190925.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190924.tex
@@
 their first optical identification
-\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  However, dramatic
-changes in the broad emission lines (BELs) in quasars has only
-recently been identified \citep[e.g.][]{LaMassa2015}.  Samples of over
+\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic
+changes in the broad emission lines (BELs) of quasars has only
+recently been identified \citep[e.g., ][]{LaMassa2015}.  Samples of over
 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars
@@
 potentially be thought of as the extension to the BELs of quasar
-continuum variability \citep[e.g.][]{MacLeod2012} whereas the
+continuum variability \citep[e.g., ][]{MacLeod2012} whereas the
 ``Changing State'' quasars (CSQs) have a `state-transition' similar to
-that in Galactic X-ray binaries \citep[e.g][]{NodaDone2018,
+that in Galactic X-ray binaries \citep[][]{NodaDone2018,
 Ruan2019}. In this paper, we use the term `Changing Look', as we are
@@
 \civ, these have tended to focus on broad absorption line quasars
-\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019} or the Baldwin Effect
-\citep[BEff; e.g. ][]{Baldwin1977, Bian2012, Jensen2016,
+\citep[BAL QSOs; see Table 1][]{Hemler2019} or the Baldwin Effect
+\citep[BEff; ][]{Baldwin1977, Bian2012, Jensen2016,
 Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
@@
 AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
-collisionally excited broad {\it emission} line (BEL) of \civ (and
+collisionally excited broad {\it emission} line (BEL) of \civ\ (and
 indeed \ciii) have not to this point been seen.
@@
 Here, we report on three quasars  
-%SDSS J120544.7+342252.4  (hereafter J1205+3422), 
-%SDSS J163852.93+282707.7 (hereafter J1638+2827) and
-%SDSS J222818.76+220102.9 (hereafter J2228+2201)  
 which show dramatic changes in their \civ\ and \ciii broad emission
@@
 linking the ionizing photons to the energetic inner accretion disk,
-potentially by inverse Compton scattering lower energy photons to
+potentially by inverse Compton scattering of lower energy photons to
 higher energies.  Furthermore, the measured rest-wavelengths of
 emission lines in quasar spectra, are known to vary from their nominal
-laboratory especially for the high-ionization broad lines,
-wavelengths, \citep[e.g.][]{VandenBerk2001}.
+laboratory wavelengths especially for the high-ionization broad lines \citep[e.g.][]{VandenBerk2001}.
 
-In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for
-the \civ doublet \citep{Kramida2018}. The ground state of carbon is
+In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
+the \civ\ doublet \citep{Kramida2018}. The ground state of carbon is
 1$s^2$ 2$s^2$ 2$p^2$.  Using the
@@
 Atomic Spectra Database Ionization Energies Form} for ionisation
-energies, we see 11.3 eV is the energy needed for C I to dislodge one
-electron and become singly-ionised C II; 24.4 eV is energy needed for
-singly-ionised C II to dislodge an additional electron, and become
-doubly-ionised C III, and 47.89 eV (3.519 Ry) is required for
-doubly-ionised C III become triply--ionised \civ.  64.49 eV (4.74 Ry)
-is the energy needed to ionize \civ itself. The 1548.202 and 1550.774
-\AA\ emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$
-$^{2}S$ transition with energies 64,484 cm$^{-1}$ and 64,591 cm$^{-1}$
-\citep[e.g.][]{Moore1993}.
+energies, we note 11.3 eV is the energy required for C~I to dislodge
+one electron and become singly-ionised C~II; 24.4 eV is then the
+(`additional') energy needed for singly-ionised C~II to dislodge an
+additional electron, and become doubly-ionised C~III, and 47.89 eV
+(3.519 Ry) is required for doubly-ionised C~III become triply--ionised
+\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
+itself. The 1548.202 and 1550.774 \AA\ emission doublet is created by
+the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition with energies 64,484
+cm$^{-1}$ and 64,591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.
 
 %%       B a c k g r o u n d     L i t e r a t u r e    
-\civ\ variability has been long studied, \citep[e.g., ][]{Baldwin1977,
+\civ\ variability has been long studied, e.g., \citet[][]{Baldwin1977,
 Gaskell1982, Gregory1982, Wilkes1986, Espey1989, Espey1990Erratum,
@@
 Laor1995, McIntosh1999, Nazarova2003}.
-%%
-\citet{Wilhite2006} examine the variability of a C~\textsc{iv} sample
-of 105 quasars observed at multiple epochs by the SDSS.  They find a
-strong correlation between the change in the C~\textsc{iv} line flux
-and the change in the line width, but no correlations between the
-change in flux and changes in line center and skewness.  These authors
-find that the relation between line flux change and line width change
-is consistent with a model in which a broad line base varies with
-greater amplitude than the line core. The C~\textsc{iv} lines in these
-high-luminosity quasars appear to be less responsive to continuum
-variations than those in lower luminosity AGN.  \citet{Wilhite2006}
-find no evidence for variability of the well known blueshift of the
-C~\textsc{iv} line with respect to the low-ionization
-Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects.
 
-\citet{Richards2011} explored the BELR in over 30,000 $z > 1.54$ SDSS
+\citet{Wilhite2006} examine
+the variability of a C~\textsc{iv} sample of 105 quasars observed at
+multiple epochs by the SDSS.  They find a strong correlation between
+the change in the C~\textsc{iv} line flux and the change in the line
+width, but no correlations between the change in flux and changes in
+line center and skewness.  These authors find that the relation
+between line flux change and line width change is consistent with a
+model in which a broad line base varies with greater amplitude than
+the line core. The C~\textsc{iv} lines in these high-luminosity
+quasars appear to be less responsive to continuum variations than
+those in lower luminosity AGN.  \citet{Wilhite2006} find no evidence
+for variability of the well known blueshift of the C~\textsc{iv} line
+with respect to the low-ionization Mg~\textsc{ii}$\lambda$2798 line in
+the highest flux objects.
+
+\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$ SDSS
 quasars, concentrating on the properties of the \civ\ emission
@@
 
-\civ has long been known to exhibit significant displacements to the
+\civ is also known to exhibit significant displacements to the
 blue and these `blueshifts' almost certainly signal the presence of
@@
 %%
-Recent investigations also include \citet{Meyer2019}.
+Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}.
 
 The purpose of this paper is, for the first time, to access and 
-report on the ``Changing-Look'' quasar phenomenon at high, 
+report on the Changing-Look quasar phenomenon at high, 
 $z>2$ redshift. By doing so, we move from the low-ionization 
 energy Balmer emission line series to the high-ionization emission 
-lines, in particular \civ.
+lines, in particular \civ\ $lambda$1549.
 
@@
 
+SDSS J120544.7+342252.4  (hereafter J1205+3422), 
+SDSS J163852.93+282707.7 (hereafter J1638+2827) and
+SDSS J222818.76+220102.9 (hereafter J2228+2201). 
 Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
@@
 
+{\bf Our Eddington ratios \\
+Done 1\% \\
+Coatman, Hewett say \civ masses are okay.\\
+But what are these Eddington ratios? \\
+Low state BHs vs. High-mass BHs... \\
+Coatman et al?? Blue-shiftted \\
+}
+
 Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191001_MJG.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_CLQs_20190926.tex
@@
 redshift.  This is also the first time the changing-look behaviour has
-been seen in a high-ionization emissions line.
+been seen in a high-ionization emission line.
 %%
@@
 Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
+\citet{Dyer2019} provide a detailed analysis of 340 quasars at high-redshift
+($1.62<z<3.30$) from the SDSS-RM project, which we will compare our
+results to.
 
@@
 %% \subsection{Selection/Identification}
-{\bf MJG to write a few notes on how the CIV CLQs were identified} 
-lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam
-porta sodales est, vel cursus risus porta non. Vivamus vel pretium
-velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
-ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
-hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
-conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
-eu blandit. Donec in lacinia libero.
+%{\bf MJG to write a few notes on how the CIV CLQs were identified} 
+Our high-$z$ CLQs were identified as follows. 
+We selected all 64,774 SDSS DR15 sources with $z > 0.35$ classified as
+'QSO', having at least two spectra separated by at least 100 days, and
+with a corresponding CRTS light curve. We fitted a damped random walk
+to the CRTS data via Gaussian process regression and the photometric
+magnitudes at the epochs of the SDSS spectra for a given source are
+predicted. Those where $|\Delta V| > 0.3$ are then selected for visual
+inspection.
 
@@
 
-Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
-pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
-id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
-dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
-euismod. Cras vel auctor neque. Nam quis diam risus.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
-at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
-in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
-nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
-nulla. Nullam eu augue id purus mollis dignissim sed et
-libero. Phasellus eget justo sed neque pellentesque egestas nec id
-arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
-vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
-imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
-neque id mi ultrices tristique. Integer quam libero, ornare vel
-gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
-cursus, dui nisl egestas augue, non fermentum nisl est nec
-nisi. Vestibulum nec mi justo, eget dapibus velit.
+\begin{figure}
+  \centering
+  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
+  {figures/CIV_CLQs_Baldwinn_20191003.png}
+   \vspace{-12pt}
+  \caption[]{The Baldwin Plot.}
+  \label{fig:REWvsFWHM}
+\end{figure}
+
+\civ\ probes the photoionization environment produced by the innermost
+disk, as indicated by RM time-delay measurements. In standard \citet{SS73}
+thin disk models, large changes in the continuum flux are not
+permitted over short timescales due to the relatively long viscous
+time associated with such disks. Given the observed short timescale
+continuum variations, it is not surprising that the \citet{SS73} disk may fail
+on other fronts. The \civ\ variations observed in our sources... 
+%DO/DO NOT (I can't tell!?! we have to determine this!) fit the Baldwin Effect relationship found by previous authors (cite em again).
+
+%If they DO fit:
+This indicates they may comfortably fit into the sample of CIV
+variable QSOs explored by \citet{Dyer2019}, and similar to those
+authors we suggest slim accretion disk models e.g., 
+\citet[][]{Abramowicz1988} or inhomogeneous disk models
+\citep[e.g.,][]{DexterAgol2011} may provide viable explanations for
+our observations. I want to say a bit more here about the generic
+probe of photoionization vs shielding and conditions in the BL region
+but that will take more time.
+
+%If they DO NOT fit:
+This implies that the variable \civ\ in our sample arises through
+different emission mechanisms than is usual for high-$z$ quasar...
+%% --and I gotta think more/longer about what else to say here.
 

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191014.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191001_MJG.tex
@@
     J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             & tbd                          & 2089-427             & \\
-    181.436164          & 2.071                               & {\bf 17.99?}   & 58538  &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions? \\
+    181.436164                  & 2.071                              & {\bf 17.99?}     &  58538   &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions?
+\\
     +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2$\times$1200   &                              &   \\
@@
 \nv	               & 1604	        & 1251        &  853.5               &  \; 854.6	    &	122.4   	    &	5.546                 & 1012                 &  107.1	 &  4.645                 &  5501	        &  611.3	          & -2.58  \\
-$^{(a)}$\civ     & 2174	        & 1254	   &  661.6             &  1927	            &	462.6	    &	2.722         & 2287	               &  125.1	 &  1.256             &  2216	        & \; 48.67          &   0.49  \\
-$^{(a)}$\heii    &  2174    	        & \;\; 33.2  &  620.3             &  1927    	            & \;\;\; 8.067  &	2.447         & 2287	               &  \; 10.7	 &  1.001             &  2216	        &  \;\;\; 0.35      &   0.39  \\
-$^{(a)}$\ciii     & 2174	        & \;  449.4  &  523.6             &  1927    	            & \;\;\; 8.067  &	2.447         & 2287	               &  \; 10.7	 &  1.001             &  2216	        & \; 17.2             &  0.41  \\
-$^{(a)}$\mgii   &  2174	        & \;	405.4  &  334.1             &  1927    	            & \;\;\; 8.067  &	2.447         & 2287	               &  \; 10.7	 &  1.001             &  2216	        & \; 33.6	           &  0.29  \\
+\civ $^{(a)}$     & 2174	        & 1254	   &  661.6                &  1927	            &	462.6	    &	2.722                 & 2287	               &  125.1	 &  1.256                 &  2216	        & \; 48.67          &   0.49  \\
+\heii$^{(a)}$    &  2174            & \;\; 33.2  &  620.3               &  1927    	    & \;\;\; 8.067  &	2.447                 & 2287	               &  \; 10.7	 &  1.001                 &  2216	        &  \;\;\; 0.35      &   0.39  \\
+\ciii$^{(a)}$     & 2174	        & \;  449.4  &  523.6               &  1927    	    & 164.6           &	1.966                 & 2287	               &  \; 29.5	 &  0.601                &  2216	        & \; 17.2             &  0.41  \\
+\mgii $^{(a)}$   &  2174	        & \;	405.4  &  334.1              &  1927    	            & 187.4           &	1.513                 & 2287	               &  \; 34.7	 &  0.346                &  2216	        & \; 33.6	           &  0.29  \\
     \hline   
@@
 eu blandit. Donec in lacinia libero.
+
+\begin{table*}
+  \centering
+  % \begin{tabular}{lll  cccc r }
+  \begin{tabu}{lll  cccc r }
+    \hline 
+    \hline 
+    Object                               &   MJD       & line                        & Line  Lumin.
+&  FWHM                         &  $V_{\rm off}$            & E.W.
+&     Catalog  \\
+    % &                 &                                    &                           &                                   &                                       &          &     \\  
+    \hline
+    \rowfont{\color{blue}}       & 53948            &  \civ                  &    570$\pm$14    &   9003$\pm$261          &  1487$\pm$76      &  18.09$\pm$0.46         &      \\
+    \rowfont{\color{blue}}       &  {\it 53948 }   &  {\it \civ  }         &    ---                   &  {\it  5230$\pm$736}   &    ---                     &   {\it 30.1$\pm$1.21}  & {\it Shen2011}  \\
+    \rowfont{\color{blue}}       &  {\it 53948 }   &  {\it \civ  }         &    {\it 1254}          &  {\it  5119}$^{(a)}$        &    ---                     &   ---                            & {\it SDSS DR12 SAS}  \\
+                                              & 53948            &  \ciii                 &    467$\pm$15    &  13707$\pm$491         &  2983$\pm$223    &  25.90$\pm$0.84         &     \\
+                                              & {\it 53948}     &  {\it \ciii}          &    {\it 449}            &   {\it  5119}$^{(a)}$        &  ---                       &                                    & {\it SDSS DR12 SAS}\\
+    \rowfont{\color{teal}}        & 53948           &  \mgii               &    209$\pm$7       &     5063$\pm$175        &  -227$\pm$77       &  21.43$\pm$0.69      &     \\
+ \multirow{2}{*}{{\bf J1205+3422}}  
+                       &     \textcolor{teal}{53948}      &\textcolor{teal}{\mgii}   & \textcolor{teal}{405$\pm$7} & \textcolor{teal}{5063$\pm$175}   &  \textcolor{teal}{-227$\pm$77}   & \textcolor{teal}{21.43$\pm$0.69}        &     \\
+    \rowfont{\color{teal}}        &  {\it 53948 }    &  {\it \mgii }        &   ---                    &   {\it  5119}$^{(a)}$       &    ---                     &   ---                           & {\it SDSS DR12 SAS }  \\
+                                               \cdashline{2-8} 
+    \rowfont{\color{blue}}       & 58538          &  \civ                    &      90$\pm$2      &   13112$\pm$208          &  1333$\pm$69      &   45.44$\pm$0.86     &     \\  
+                                              & 58538          &  \ciii                    &      83$\pm$1      &   14913$\pm$245          &    942$\pm$93      &   52.99$\pm$0.91     &     \\  
+    \rowfont{\color{teal}}        & 58538          &  \mgii                  &      71$\pm$2      &   14951$\pm$340          &    -63$\pm$129    &   77.08$\pm$1.69    &     \\
+                                               \cdashline{2-8}
+    \rowfont{\color{blue}}        & 58693          &  \civ                    &  1006$\pm$1     &   13685$\pm$127          &   3000                     &   17.19$\pm$0.17    &     \\  
+                                              & 58693          &  \ciii                    &    151$\pm$1     &   15000                          &   3000                      &    39.31$\pm$0.24    &     \\
+    \rowfont{\color{teal}}          & 58693           &  \mgii                  &    180$\pm$1     &   11400$\pm$83           &     -82$\pm$34       &    73.71$\pm$0.50    &     \\  
+\hline
+                                               %& {\it  54553 }  &  {\it Ly$\alpha$}    &  {\it 510.5}          &  {\it  3207}$^{(a)}$        &    ---                        &   ---                             & {\it SDSS DR12 SAS}  \\
+   \rowfont{\color{blue}}          & 54533             & \civ                  & 284$\pm$13       & 4574$\pm$658            &   55$\pm$438.31     &  31.80$\pm$1.51           &     \\
+   \rowfont{\color{blue}}          &  {\it 54533 }    &  {\it \civ  }        &  ---                     &  {\it  4180$\pm$736}   &    ---                        &   {\it 100.5$\pm$11.9}  & {\it Shen2011}   \\
+   \rowfont{\color{blue}}          &  {\it 54553 }    &  {\it \civ  }        &    {\it 462.6}          &  {\it  4537}$^{(a)}$         &    ---                       &   ---                              & {\it SDSS DR12 SAS}  \\
+
+                                                & 54533             & \ciii                  & 105$\pm$7          & 3687$\pm$336            &  -246$\pm$122.7   &  33.29$\pm$2.32         &     \\
+                                                & {\it 54553}     &  {\it \ciii}          &    {\it 164.6}            &   {\it  4537}$^{(a)}$        &  ---                         &  ---                           &  {\it SDSS DR12 SAS}\\
+    \rowfont{\color{teal}}           &  {\it 54533 }  &  {\it \mgii }        &   ---                    &  {\it 4802$\pm$2005}     &    ---                       &  {\it 115$\pm$33}         & {\it Shen2011}  \\
+    \rowfont{\color{teal}}            &  {\it 54533 }  &  {\it \mgii }        &   {\it 187.4}          &  {\it 4537}$^{(a)}$             &    ---                       &  ---                           &  {\it SDSS DR12 SAS }  \\
+                                                 \cdashline{2-8}
+                                                  & 55832         & Ly$\alpha_{\rm na}$  &   27$\pm$4   &  783$\pm$102            & -323$\pm$35            &    9.72$\pm$1.59       &     \\   
+                                                 & 55832          & Ly$\alpha$           & 288$\pm$11      &  4444$\pm$243           & -463$\pm$68           &  103.69$\pm$3.99     &     \\
+                                                & {\it  55832 }  &  {\it Ly$\alpha$}    &  {\it 633.9}          &  {\it  4165.6}$^{(a)}$      &    ---                        &   ---                             & {\it SDSS DR12 SAS}  \\
+\multirow{2}{*}{J1638+2827}
+                & \textcolor{blue}{55832} & \textcolor{blue}{\civ}       &   \textcolor{blue}{73$\pm$3}     &  \textcolor{blue}{6253$\pm$259}   &  \textcolor{blue}{  270$\pm$106}     &  \textcolor{blue}{45.15$\pm$1.90}      &     \\
+    \rowfont{\color{blue}}           &  {\it 55832 }  &  {\it \civ  }        &   -                          &  {\it  5210$\pm$226}   &    ---                       &    {\it 42.76$\pm$1.96 }     & {\it Ham17  }\\
+    \rowfont{\color{blue}}           &  {\it 55832 }  &  {\it \civ  }       &    {\it 125.1}             &  {\it  5385.}$^{(a)}$        &    ---                       &   ---                             & {\it SDSS DR12 SAS}  \\
+                                                 & 55832            & \ciii                &   19$\pm$6            & 14952$\pm$4682        &    3000$\pm$0         &   17.79$\pm$5.49      &     \\
+                                                 & {\it 55832}     &  {\it \ciii}        &    {\it 10.68}            &   {\it  5385.}$^{(a)}$        &  ---                        &                                & {\it SDSS DR12 SAS}\\
+    \rowfont{\color{teal}}           & 55832            & \mgii               &  41$\pm$7             &        0$\pm$0              &    1000$\pm$1108     &    81.76$\pm$13.90    &     \\
+    \rowfont{\color{teal}}           & {\it 55832}     &  {\it \mgii}      &    {\it 34.66}            &   {\it  5385.}$^{(a)}$        &  ---                       &                                & {\it SDSS DR12 SAS}\\
+                                                 \cdashline{2-8}
+      \rowfont{\color{blue}}          & 58583             & \civ                 &  286$\pm$2         & -                                   &                   -                &   20.89$\pm$0.13      &     \\
+                                                & 58583            & \ciii                  &   92$\pm$1          &  6689$\pm$89             &    37$\pm$37.186        &   28.96$\pm$0.35      &     \\
+    \rowfont{\color{teal}}          & 58583            & \mgii               &  116$\pm$1          &  6649$\pm$85             & -422$\pm$34.818       &   67.38$\pm$0.77      &     \\  
+\hline 
+    \rowfont{\color{blue}}         &  {\it 56189 }   &  {\it \civ }           &  {\it --- }               &  {\it 2994$\pm$620}    &     ---                        &  {\it 42.18$\pm$5.59}      &    {\it Ham17 } \\
+    \rowfont{\color{blue}}          &  {\it 56189 }   &  {\it \civ  }         &    {\it 48.67}             &  {\it  5218}$^{(a)}$        &    ---                     &   ---                             & {\it SDSS DR12 SAS}  \\
+                                                & 56189           & \ciii                           &  39$\pm$8      & 14097$\pm$2943        &   2243$\pm$1142    & 66.63$\pm$12.90     &     \\
+                                                 & {\it 56189}     &  {\it \ciii}          &    {\it 17.2}            &   {\it  5218}$^{(a)}$           &  ---                       &                                & {\it SDSS DR12 SAS}\\
+    \rowfont{\color{teal}}           & 56189            & \mgii                         &  23$\pm$6          &   6694$\pm$1765   &   -597$\pm$741      & 41.19$\pm$10.95     &     \\
+    \rowfont{\color{teal}}        & {\it 56189}     &  {\it \mgii}          &    {\it 33.6}            &   {\it  5218}$^{(a)}$           &  ---                       &                                & {\it SDSS DR12 SAS}\\
+                                                   \cdashline{2-8}
+                                               & 56960    & Ly$\alpha_{\rm na}$   &   24$\pm$5         &     642$\pm$92               &    -319$\pm$30        &  2.71 $\pm$0.51      &     \\  
+                                                & 56960    & Ly$\alpha$                & 121$\pm$38        & 3580$\pm$673              &     -16$\pm$171     &  13.52 $\pm$4.21    &     \\  
+\multirow{2}{*}{J2228+2201}
+           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}              & \textcolor{blue}{254$\pm$5}    &  \textcolor{blue}{8731$\pm$172}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{45.35$\pm$0.90}    &     \\
+                                               & 56960    & \ciii                            & 185$\pm$5           &        -                            &  2701$\pm$225         &   47.75$\pm$1.29    &     \\
+    \rowfont{\color{teal}}          & 56960    & \mgii                         &   99$\pm$4           &  7312.6$\pm$340        &   188$\pm$137          &   50.75$\pm$2.21     &     \\
+                                            \cdashline{2-8}
+     \rowfont{\color{blue}}        & 58693    & \civ                            & 54.688$\pm$0.6   &  6000.3$\pm$70           &      33$\pm$28          &   39.28$\pm$0.43     &     \\  
+                                               & 58693    & \ciii                            & 115.08$\pm$1.2   & 15000                            &  2772$\pm$86          &   96.36$\pm$0.97     &     \\
+     \rowfont{\color{teal}}         & 58693    & \mgii                         & 46.361$\pm$1.3   & 8900$\pm$278             &  1000                         &   53.46$\pm$1.54     &     \\  
+                                                %
+\hline
+\hline
+     %    \end{tabular}
+    \end{tabu}
+\caption{Line Measurement Information from QSFIT, unless otherwise stated. 
+      Shen11 is \citet{Shen2011}. 
+      Ham17 is \citet{Hamann2017}.
+      SDSS DR12 SAS is the line measurement information from the SDSS DR12
+      Science Archive Server (SAS).
+      $^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
+    }
+ \label{tab: QSFIT_line_values}
+\end{table*}
+
+\iffalse
+\begin{table*}
+  \centering
+  \begin{tabular}{lll  cccc r }
+    \hline 
+    \hline 
+    Object                                 &   MJD       & line                        & Line  Lumin.
+& FWHM                     &  $V_{\rm off}$            & E.W.
+\\
+    % &                 &                                    &                           &                               &                                  &        \\
+    \hline
+                                               & 53948 &  \civ                            &    570$\pm$14  &     9003$\pm$261    &  1487$\pm$76      &  18.09$\pm$0.46  \\
+                                               & 53948 &  \ciii                            &    467$\pm$15  &   13707$\pm$491    &  2983$\pm$223    &  25.90$\pm$0.84  \\
+                                               & 53948 &  \mgii                          &    209$\pm$7    &     5063$\pm$175    &  -227$\pm$77     &  21.43$\pm$0.69  \\
+                                               & 58538 &  \civ                             &      90$\pm$2    &   13112$\pm$208   &  1333$\pm$69      &   45.44$\pm$0.86   \\
+\multirow{2}{*}{J1205+3422}  & 58538 &  \ciii                             &      83$\pm$1    &   14913$\pm$245   &    942$\pm$93      &   52.99$\pm$0.91  \\
+                                               & 58538 &  \mgii                           &      71$\pm$2    &   14951$\pm$340   &    -63$\pm$129    &   77.08$\pm$1.69  \\
+                                               & 58693 &  \civ                             &  1006$\pm$1    &   13685$\pm$127   &   3000                     &   17.19$\pm$0.17   \\
+                                               & 58693 &  \ciii                             &    151$\pm$1    &   15000                   &   3000                      &    39.31$\pm$0.24  \\
+                                               & 58693 &  \mgii                           &    180$\pm$1    &   11400$\pm$83    &     -82$\pm$34       &    73.71$\pm$0.50  \\
+    \hline
+                                                 & 54533  & \civ                           & 284$\pm$13      & 4574$\pm$658       &      55$\pm$438.31   &  31.80$\pm$1.51    \\
+                                                & 54533  & \ciii                           & 105$\pm$7        & 3687$\pm$336       &  -246$\pm$122.7      &  33.29$\pm$2.32    \\
+                                                & 55832  & Ly$\alpha_{\rm na}$   &   27$\pm$4        &   783$\pm$102       & -323$\pm$35           &    9.72$\pm$1.59     \\ 
+                                               & 55832  & Ly$\alpha$                & 288$\pm$11      &  4444$\pm$243       & -463$\pm$68            &  103.69$\pm$3.99   \\
+\multirow{2}{*}{J1638+2827}   & 55832  & \civ                            &   73$\pm$3       &  6253$\pm$259       &    270$\pm$106         &    45.15$\pm$1.90    \\ 
+                                                & 55832  & \ciii                           &   19$\pm$6        & 14952$\pm$4682    &    3000$\pm$0           &   17.79$\pm$5.49    \\
+                                                 & 55832  & \mgii                         &  41$\pm$7         &        0$\pm$0          &    1000$\pm$1108    &   81.76$\pm$13.90  \\
+                                                & 58583  & \civ                           & 286$\pm$2        & -                               &                   -               &   20.89$\pm$0.13    \\
+                                                & 58583  & \ciii                           &  92$\pm$1         & 6689$\pm$89          &    37$\pm$37.186      &   28.96$\pm$0.35    \\
+                                                & 58583  & \mgii                        & 116$\pm$1        & 6649$\pm$85           & -422$\pm$34.818     &   67.38$\pm$0.77    \\
+\hline 
+                                               & 56189    & \ciii                           &  39$\pm$8          & 14097$\pm$2943     &   2243$\pm$1142    & 66.63$\pm$12.90   \\
+                                               & 56189    & \mgii                         &  23$\pm$6          &   6694$\pm$1765     &   -597$\pm$741      & 41.19$\pm$10.95   \\
+                                               & 56960    & Ly$\alpha_{\rm na}$   &   24$\pm$5         &     642$\pm$92        &    -319$\pm$30        &  2.71 $\pm$0.51    \\
+                                               & 56960    & Ly$\alpha$                & 121$\pm$38        & 3580$\pm$673        &     -16$\pm$171     &  13.52 $\pm$4.21  \\
+ \multirow{2}{*}{J2228+2201}  & 56960   & \civ                            & 254$\pm$5         &  8731$\pm$172       &        92$\pm$68      &   45.35$\pm$0.90  \\ 
+                                               & 56960    & \ciii                           & 185$\pm$5          &        -                        &  2701$\pm$225     &   47.75$\pm$1.29  \\
+                                               & 56960    & \mgii                         &   99$\pm$4          &  7312.6$\pm$340    &   188$\pm$137      &   50.75$\pm$2.21   \\
+                                               & 58693    & \civ                           & 54.688$\pm$0.6   &  6000.3$\pm$70     &      33$\pm$28       &   39.28$\pm$0.43  \\
+                                               & 58693    & \ciii                           & 115.08$\pm$1.2   & 15000                      &  2772$\pm$86       &   96.36$\pm$0.97   \\
+                                               & 58693    & \mgii                         & 46.361$\pm$1.3   & 8900$\pm$278       &  1000                      &   53.46$\pm$1.54   \\
+                                                %
+\hline
+\hline
+  \end{tabular}
+  \caption{Line Measurement Information from QSFIT. }
+ \label{tab: QSFIT_line_values}
+\end{table*}
+\fi
 

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191015.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191001_MJG.tex
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
-sodales est, vel cursus risus porta non. Vivamus vel pretium
-velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
-ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
-hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
-conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
-eu blandit. Donec in lacinia libero.
+\begin{table*}
+  \centering
+  % \begin{tabular}{lll  cccc r }
+  \begin{tabu}{lll  cccc r }
+    \hline 
+    \hline 
+    Object                               &   MJD       & line              & Line  Lumin.
+&  FWHM                      &  $V_{\rm off}$          & E.W.
+&     Catalog  \\
+    % &                 &                                    &                           &                                   &                                       &          &     \\  
+    \hline
+    \rowfont{\color{blue}}       & 53948     &  \civ             &   570$\pm$14      &   9003$\pm$261      &  1487$\pm$76      &  18.09$\pm$0.46         &      \\
+    \rowfont{\color{blue}}       & 53948     &   \civ            &    ---                   &    5230$\pm$736      &    ---                     &    30.1$\pm$1.21        &  Shen2011  \\
+    \rowfont{\color{blue}}        & 53948    &   \civ            &  1254                   &    5119$^{(a)}$          &    ---                     &   ---                            &  SDSS DR12 SAS  \\
+                                              & 53948     &  \ciii            &   467$\pm$15     &  13707$\pm$491      &  2983$\pm$223    &  25.90$\pm$0.84         &     \\
+                                              &  53948    &  \ciii            &   449                    &     5119$^{(a)}$          &  ---                        &    ---                           &  SDSS DR12 SAS \\
+  \rowfont{\color{teal}}         & 53948     &  \mgii         &   209$\pm$7       &     5063$\pm$175     &  $-227\pm77$         &  21.43$\pm$0.69       &     \\
+  \rowfont{\color{teal}}         & 53948     &  \mgii         &   ---                    &     4730$\pm$313     &  ---                         &  32$\pm$3.88            &    Shen2011 \\
+ \multirow{2}{*}{{\bf J1205+3422}}  
+                &     \textcolor{teal}{53948}      & \textcolor{teal}{\mgii}   & \textcolor{teal}{405} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        &   \textcolor{teal}{SDSS DR12 SAS}    \\
+                                               \cdashline{2-8} 
+    \rowfont{\color{blue}}        & 58538      &  \civ             &    90$\pm$2        &   13112$\pm$208          &  1333$\pm$69      &   45.44$\pm$0.86     &     \\  
+                                              & 58538      &  \ciii              &    83$\pm$1       &   14913$\pm$245          &    942$\pm$93      &   52.99$\pm$0.91     &     \\  
+    \rowfont{\color{teal}}         & 58538      &  \mgii           &     71$\pm$2      &   14951$\pm$340          &    -63$\pm$129    &   77.08$\pm$1.69    &     \\
+                                               \cdashline{2-8}
+    \rowfont{\color{blue}}        & 58693          &  \civ          &  1006$\pm$1     &   13685$\pm$127          &   3000                     &   17.19$\pm$0.17    &     \\  
+                                              & 58693          &  \ciii           &    151$\pm$1     &   15000                          &   3000                      &    39.31$\pm$0.24    &     \\  
+    \rowfont{\color{teal}}         & 58693           &  \mgii       &    180$\pm$1     &   11400$\pm$83           &     -82$\pm$34       &    73.71$\pm$0.50    &     \\  
+\hline
+                                               &  54553     &   Ly$\alpha$   &   510.5              &    3207$^{(a)}$          &    ---                        &   ---                             &  SDSS DR12 SAS  \\
+   \rowfont{\color{blue}}          & 54533      & \civ                & 284$\pm$13    & 4574$\pm$658         &   55$\pm$438.31     &  31.80$\pm$1.51         &     \\
+   \rowfont{\color{blue}}          &  54533     &   \civ              &  ---                  &    4180$\pm$736     &    ---                        &    100.5$\pm$11.9       &  Shen2011   \\
+   \rowfont{\color{blue}}          &  54553     &   \civ              & 462.6               &    4537$^{(a)}$           &    ---                       &   ---                              &  SDSS DR12 SAS  \\
+                                                & 54533       & \ciii              & 105$\pm$7        &  3687$\pm$336       &  -246$\pm$122.7   &  33.29$\pm$2.32         &     \\
+                                                &  54553      &  \ciii             &  164.6                &  4537$^{(a)}$             &  ---                         &  ---                           &   SDSS DR12 SAS \\
+    \rowfont{\color{teal}}           &   54533     & \mgii           &   ---                 &  4802$\pm$2005      &    ---                       &   115$\pm$33         &  Shen2011   \\
+    \rowfont{\color{teal}}            &   54533    & \mgii           & 187.4                &  4537$^{(a)}$              &    ---                       &  ---                           &   SDSS DR12 SAS  \\
+                                                 \cdashline{2-8}
+                                                 & 55832     & Ly$\alpha_{\rm na}$                  &   27$\pm$4              &  783$\pm$102        & -323$\pm$35            &    9.72$\pm$1.59       &     \\
+                                                 & 55832      & Ly$\alpha$    & 288$\pm$11   &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99     &     \\
+                                              &   55832     & Ly$\alpha$    &   633.9            &    4165.6$^{(a)}$        &    ---                       &   ---                           &  SDSS DR12 SAS  \\
+\multirow{2}{*}{\bf {J1638+2827}}
+                & \textcolor{blue}{55832} & \textcolor{blue}{\civ}  &   \textcolor{blue}{73$\pm$3}               &  \textcolor{blue}{6253$\pm$259}   &  \textcolor{blue}{270$\pm$106}     &  \textcolor{blue}{45.15$\pm$1.90}      &     \\
+    \rowfont{\color{blue}}           &   55832    &  \civ                &   -                     &    5210$\pm$226    &    ---                       &     42.76$\pm$1.96      &  Ham17  \\
+    \rowfont{\color{blue}}           &   55832    &  \civ                &  125.1               &    5385$^{(a)}$          &    ---                       &   ---                             &  SDSS DR12 SAS  \\
+                                                & 55832      & \ciii                 & 19$\pm$6         &  14952$\pm$4682  &    3000$\pm$0         &   17.79$\pm$5.49      &     \\
+                                                 &  55832     &  \ciii                &  10.68               &     5385$^{(a)}$         &  ---                        &                                &  SDSS DR12 SAS\\
+    \rowfont{\color{teal}}           & 55832       & \mgii               &  41$\pm$7       &        0$\pm$0           &    1000$\pm$1108     &    81.76$\pm$13.90    &     \\
+    \rowfont{\color{teal}}           &  55832      & \mgii               &  34.66               &     5385$^{(a)}$        &  ---                       &                                &  SDSS DR12 SAS\\
+                                                \cdashline{2-8}
+      \rowfont{\color{blue}}        & 58583       & \civ                &  286$\pm$2         & -                                   &                   -                &   20.89$\pm$0.13      &     \\
+                                                & 58583       & \ciii                &   92$\pm$1          &  6689$\pm$89             &    37$\pm$37.186        &   28.96$\pm$0.35      &     \\  
+    \rowfont{\color{teal}}          & 58583        & \mgii             &  116$\pm$1         &  6649$\pm$85             & -422$\pm$34.818       &   67.38$\pm$0.77      &     \\  
+\hline 
+    \rowfont{\color{blue}}         &   56189      &   \civ            &   ---                       &   2994$\pm$620        &     ---                        &   42.18$\pm$5.59        &     Ham17  \\
+    \rowfont{\color{blue}}          &   56189     &   \civ            &  48.67                     &    5218$^{(a)}$             &    ---                        &   ---                             &  SDSS DR12 SAS  \\
+                                               & 56189        & \ciii               &  39$\pm$8            & 14097$\pm$2943      &   2243$\pm$1142    & 66.63$\pm$12.90         &     \\
+                                                 &  56189     &   \ciii             &  17.2                      &     5218$^{(a)}$           &  ---                          &                                      &  SDSS DR12 SAS \\
+    \rowfont{\color{teal}}           & 56189       & \mgii            &  23$\pm$6             &   6694$\pm$1765      &   -597$\pm$741       & 41.19$\pm$10.95        &     \\
+    \rowfont{\color{teal}}        &  56189         &   \mgii          &  33.6                      &     5218$^{(a)}$           &  ---                           &                                     &  SDSS DR12 SAS \\
+                                                   \cdashline{2-8}
+                                               & 56960       & Ly$\alpha_{\rm na}$   &   24$\pm$5    &     642$\pm$92         &    -319$\pm$30       &  2.71 $\pm$0.51          &     \\  
+                                                & 56960      & Ly$\alpha$                & 121$\pm$38   & 3580$\pm$673         &     -16$\pm$171     &  13.52 $\pm$4.21        &     \\  
+\multirow{2}{*}{{\bf J2228+2201}}
+           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}     & \textcolor{blue}{254$\pm$5}    &  \textcolor{blue}{8731$\pm$172}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{45.35$\pm$0.90}    &     \\
+                                               & 56960    & \ciii                   & 185$\pm$5              &        -                            &  2701$\pm$225       &   47.75$\pm$1.29      &     \\
+    \rowfont{\color{teal}}          & 56960    & \mgii                &   99$\pm$4              &  7312.6$\pm$340        &   188$\pm$137         &   50.75$\pm$2.21     &     \\
+                                            \cdashline{2-8}
+     \rowfont{\color{blue}}        & 58693    & \civ                   & 54.688$\pm$0.6    &  6000.3$\pm$70           &      33$\pm$28          &   39.28$\pm$0.43     &     \\  
+                                               & 58693    & \ciii                   & 115.08$\pm$1.2    & 15000                            &  2772$\pm$86          &   96.36$\pm$0.97     &     \\  
+     \rowfont{\color{teal}}         & 58693    & \mgii                & 46.361$\pm$1.3    & 8900$\pm$278             &  1000                         &   53.46$\pm$1.54     &     \\  
+                                                %
+\hline
+\hline
+     %    \end{tabular}
+    \end{tabu}
+\caption{Line Measurement Information from QSFIT, unless otherwise stated. 
+      Shen11 is \citet{Shen2011}. 
+      Ham17 is \citet{Hamann2017}.
+      SDSS DR12 SAS is the line measurement information from the SDSS DR12
+      Science Archive Server (SAS).
+      $^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
+      The different colours of text are merely for readability. 
+    }
+ \label{tab: QSFIT_line_values}
+\end{table*}
+
+\begin{table*}
+  \begin{tabular}{ll l l cc ll}
+    \hline
+    \hline
+    Object        & MJD         & $M_i$   &  $L_{\rm bol}$             & \multicolumn{2}{c}{$M_{\rm BH}$}          & $\eta_{\rm Edd}$  & Ref. \\
+                      &                &              &                                   & \mgii      & \civ                                    &                             &        \\
+    \hline
+                      & 53498    & -27.74   & 47.216$\pm$0.004   &  9.55$\pm$0.05   &   9.49$\pm$0.04   &  -0.3783               & Shen2011\\
+ J1205+3422  & 58538    &               &                              &                             &                                &                              &  \\
+                      & 58693    &               &                              &                            &                                 &                             &  \\
+    \hline 
+                      & 54553    & -26.75   & 46.166$\pm$0.04    &   9.03$\pm$0.366 & 8.742$\pm$0.15   &  -0.6768               & Shen2011\\
+ J1638+2827 & 55832    &  -26.40   & 46.721$\pm$0.073  &   9.338                   &  9.1289                   & -0.717                           & Kol017\\
+                      & 58583    &              &                                   &                              &                                 &                   & \\
+    \hline 
+                      & 56189    &  -25.46  & 46.231$\pm$0.073  &   9.448                 & 8.733                        &  -1.317               & Kol017\\
+J2228+2201  & 56960    &               &                                  &                           &                                    &                 &   \\
+                      & 58693    &              &                                   &                            &                                   &               &  \\
+    \hline
+    \hline
+  \end{tabular}
+  \caption{$\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio.
+        Shen11 is \citet{Shen2011}. 
+      Kol17 is \citet{Kozlowski2017}.}
+\end{table*}
 
@@
   \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwinn_20191003.png}
+  {figures/CIV_CLQs_Baldwin_LBol_20191015.png}
    \vspace{-12pt}
-  \caption[]{The Baldwin Plot.}
+   \caption[]{The Baldwin Plot. The bolometric luminosities are from \citet{Kozlowski2017},
+     while the REW measurements are from \citet{Hamann2017}.}
   \label{fig:REWvsFWHM}

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191016.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191001_MJG.tex
@@
 
-\hypersetup{draft}
+% \hypersetup{draft}
+
 \begin{document}
@@
 \subsection{Line Properties}  
-We use the measured quasar emission line properties from
-\citet{Shen2011} and \citet{Hamann2017}. \citet{Hamann2017} in
+We use the measured quasar emission line properties from several catalogues: 
+\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017} and
+\citet{Calderone2017}.
+
+\citet{Shen2011} present a compilation of properties of the 105,783
+quasars in the SDSS Data Release 7 (DR7) quasar catalog \citep[DR7Q;
+][]{Schneider2007}. \citet{Shen2011} report non-zero \civ\ FWHM and
+EWs for approximately half (51,501) of the full DR7Q, and non-zero
+\mgii FWHM and EWs for 80\% (84,183) of the DR7Q quasars).
+
+\citet{Calderone2017} present the Quasar Spectral Fitting (QSFIT)
+software package which among other quantities provides luminosity
+estimates as well as width, velocity offset and equivalent width of 20
+emission lines, includinng \civ, \ciii and \mgii.  We use the lastest
+version (v1.3.0) of the QSFIT
+\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online calculator}
+and process our spectra with QSFit setting $E(B-V)=0.00$.
+
+\citet{Hamann2017} in
 particular investigate in robust detail the UV continuum and the \civ\
@@
 that \civ\ and the adjacent continuum are covered by BOSS. These
-measurements provide line profile information and N V/C IV flux
-ratios.
+measurements provide line profile information and flux ratios.
+\citet{Hamann2017} was focused on $z\geq2$ quasars and specifcally
+their \civ properties in order to understand the high-$z$ ``Extremely Red Quasar''
+population \citet{Ross2015, Zakamska2016, Perrotta2019, Zakamska2019}. 
+As such, these measurements can be taken as the
+`gold standard' for \civ line measurement, though this is only for 2
+out of our 9 spectra.
+
+%% Notes.
+ When using the \citet{Shen2011} catalogue, we report line luminosity,
+FWHM, rest-frame equivalent width, and their errors for the {\it
+whole} \mgii profile (the \citet{Shen2011} catalogue also quotes values
+for just the broad \mgii compoment, but the differences here in the
+two spectra of ours is negligible). The line luminosites in
+\citet{Calderone2017} are given in units of $10^{42}$ erg s$^{-1}$,
+while the line luminosites in \citet{Shen2011} are in units of
+$\log(L)$.  So comparing the error values for these measurements is
+not straightforward.
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
-sodales est, vel cursus risus porta non. Vivamus vel pretium
-velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
-ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
-hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
-conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
-eu blandit. Donec in lacinia libero.
+\begin{table*}
+  \centering
+  % \begin{tabular}{lll  cccc r }
+  \begin{tabu}{lll  cccc c r }
+    \hline 
+    \hline 
+    Object                               &   MJD      & line      & Line  Lumin.
+&  FWHM                      &  $V_{\rm off}$          & E.W.
+& $\alpha_{\lambda}$   &  Catalogue  \\
+    % &                 &                                    &                           &                                   &                                       &          &     \\  
+    \hline
+    \rowfont{\color{blue}}       & 53948    & \civ      &  523$\pm$14    &   9816$\pm$321       &  1407$\pm$81      &  16.83$\pm$0.43      & $-1.64\pm0.01$      & QSFit    \\
+    \rowfont{\color{blue}}       & 53948    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    &    30.1$\pm$1.21      & $-1.47\pm0.08$      &  Shen2011  \\
+    \rowfont{\color{blue}}       & 53948    & \civ      &                           &   5119$^{(a)}$             &    ---                     &   ---                          &  ---                           & DR12 SAS  \\
+                                             & 53948     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    &  25.10$\pm$0.59      & $-1.65\pm0.01$      & QSFit   \\
+                                             & 53948    & \ciii       &                          &   5119$^{(a)}$             &  ---                       &    ---                         &  ---                          & DR12 SAS \\
+  \rowfont{\color{teal}}         & 53948     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     &  26.66$\pm$1.65     &   $-1.65\pm0.01$     &  QSFit  \\
+  \rowfont{\color{teal}}         & 53948     & \mgii     &  284                  &   4730$\pm$314       &  $-179\pm188$     &  32$\pm$3.88           &  $-1.87\pm0.06$     & Shen2011 \\
+ \multirow{2}{*}{{\bf J1205+3422}}  
+                &     \textcolor{teal}{53948}      & \textcolor{teal}{\mgii}   & \textcolor{teal}{---} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\
+                \cdashline{2-9}
+                                               & 58538     & \lya     & 1393$\pm$11   & $>$15000   &  $-796\pm57$      &  ---     &    &   QSFit  \\
+    \rowfont{\color{blue}}        & 58538     & \civ      &  1037$\pm$5    & $>$15000   &  983$\pm$40        &  ---     &    &   QSFit    \\  
+                                              & 58538      & \ciii     &    677$\pm$4    & $>$15000    & $>$3000              &  ---     &     &  QSFit   \\  
+    \rowfont{\color{teal}}         & 58538     & \mgii    &     755$\pm$4  & $>$15000    & 350$\pm$39        &  ---      &    &   QSFit  \\
+                                          \cdashline{2-9}
+                                              & 58693      & \lya     & 290$\pm$3        & 8803$\pm$52      &  $-1096\pm35$  &  ---                        & $<$-3       &   QSFit  \\
+    \rowfont{\color{blue}}        & 58693     & \civ      &   68$\pm$0.9     & 3743$\pm$26    &   591$\pm$17    &   ---                       & $<$-3     &  QSFit   \\  
+                                              & 58693      & \ciii     &   19$\pm$0.4     & 5625$\pm$         &   $>$3000           &    ---                      & $<$-3    &  QSFit    \\  
+    \rowfont{\color{teal}}         & 58693     & \mgii    &   19$\pm$0.4    & 1530$\pm$22     &  $>$3000          &    ---                          &$<$-3    &  QSFit   \\  
+\hline
+                                                & 54553     & \lya     &   510.5              &  3207          &    ---                        &   ---                             & ---   &   DR12 SAS  \\
+   \rowfont{\color{blue}}          & 54533     & \civ      & 284$\pm$13    & 4574$\pm$658         &   55$\pm$438.31     &  31.80$\pm$1.51         &   &  QSFit  \\
+   \rowfont{\color{blue}}          & 54533     & \civ      &  281                  &    4181$\pm$736     &    680$\pm$133       &    100.5$\pm$11.9       & $-0.14\pm0.68$  &  Shen2011   \\
+   \rowfont{\color{blue}}          & 54553     & \civ      & 462.6                &    4537$^{(a)}$           &    ---                       &   ---                              & ---   &  DR12 SAS  \\
+                                                & 54533     & \ciii     & 105$\pm$7       &  3687$\pm$336       &  $-246\pm122.7$   &  33.29$\pm$2.32         &    &  QSFit  \\
+                                                & 54553     & \ciii     &  164.6                &  4537$^{(a)}$             &  ---                         &  ---                           & ---     &  DR12 SAS \\
+    \rowfont{\color{teal}}          & 54533      & \mgii  &   139                 &  4757$\pm$2224      &  $-944\pm568$        &   119$\pm$40         &  $-1.49\pm0.54$   &  Shen2011   \\
+    \rowfont{\color{teal}}          & 54533      & \mgii  & 187.4                 &  4537$^{(a)}$              &    ---                       &  ---                           & ---    &  DR12 SAS  \\
+                                                \cdashline{2-8}
+                                                & 55832     & \lya     & 288$\pm$11   &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99     &    &   QSFit  \\
+                                                & 55832     & \lya     &   633.9            &    4165.6$^{(a)}$        &    ---                       &   ---                           &   ---   &   DR12 SAS  \\
+\multirow{2}{*}{\bf {J1638+2827}}
+                & \textcolor{blue}{55832} & \textcolor{blue}{\civ}  &   \textcolor{blue}{73$\pm$3}               &  \textcolor{blue}{6253$\pm$259}   &  \textcolor{blue}{270$\pm$106}     &  \textcolor{blue}{45.15$\pm$1.90}      &  &   QSFit    \\
+    \rowfont{\color{blue}}           &  55832   &  \civ     &   -                     &    5210$\pm$226    &    ---                       &     42.76$\pm$1.96      &   &   Ham17  \\
+    \rowfont{\color{blue}}           &  55832   &  \civ     &  125.1               &    5385$^{(a)}$          &    ---                       &   ---                             &   &   DR12 SAS  \\
+                                                 & 55832     & \ciii     & 19$\pm$6         &  14952$\pm$4682  &    3000$\pm$0         &   17.79$\pm$5.49      &  &   QSFit    \\
+                                                 &  55832    &  \ciii    &  10.68               &     5385$^{(a)}$         &  ---                        &                                &   &   DR12 SAS\\
+    \rowfont{\color{teal}}           & 55832      & \mgii   &  41$\pm$7       &        0$\pm$0           &    1000$\pm$1108     &    81.76$\pm$13.90    &    &   QSFit  \\
+    \rowfont{\color{teal}}           &  55832     & \mgii   &  34.66               &     5385$^{(a)}$        &  ---                       &                                &   &   DR12 SAS\\  
+                                               \cdashline{2-9}
+      \rowfont{\color{blue}}        & 58583      & \civ      &  286$\pm$2     & -                                   &                   -                &   20.89$\pm$0.13      &   &   QSFit   \\  
+                                                & 58583      & \ciii      &   92$\pm$1      &  6689$\pm$89             &    37$\pm$37.186        &   28.96$\pm$0.35      &   &   QSFit   \\  
+    \rowfont{\color{teal}}           & 58583      & \mgii   &  116$\pm$1      &  6649$\pm$85             & -422$\pm$34.818       &   67.38$\pm$0.77      &   &   QSFit   \\  
+\hline
+    \rowfont{\color{blue}}         &   56189      & \civ    &   ---                       &   ---                          &     ---                        &    ---                             &     &   QSFit$^{(c)}$  \\
+    \rowfont{\color{blue}}         &   56189      & \civ    &   ---                       &   2994$\pm$620        &     ---                        &   42.18$\pm$5.59        &    &    Ham17  \\
+    \rowfont{\color{blue}}         &   56189      & \civ    &  48.67                     &    5218$^{(a)}$             &    ---                        &   ---                             &   &   DR12 SAS  \\
+                                               & 56189        &  \ciii   &  39$\pm$8            & 14097$\pm$2943      &   2243$\pm$1142    & 66.63$\pm$12.90         &    &   QSFit  \\
+                                               &  56189       & \ciii    &  17.2                      &     5218$^{(a)}$           &  ---                          &                                      &   &   DR12 SAS \\
+    \rowfont{\color{teal}}          & 56189       & \mgii  &  23$\pm$6             &   6694$\pm$1765      &   -597$\pm$741       & 41.19$\pm$10.95        &  &   QSFit   \\
+    \rowfont{\color{teal}}         &  56189       &  \mgii &  33.6                      &     5218$^{(a)}$           &  ---                           &                                     &   &   DR12 SAS \\
+                                                  \cdashline{2-9}
+                                              & 56960         & \lya    & 121$\pm$38   & 3580$\pm$673         &     -16$\pm$171     &  13.52 $\pm$4.21        &  &   QSFit   \\  
+\multirow{2}{*}{{\bf J2228+2201}}
+           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}     & \textcolor{blue}{254$\pm$5}    &  \textcolor{blue}{8731$\pm$172}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{45.35$\pm$0.90}    &    &    \\
+                                               & 56960    & \ciii        & 185$\pm$5              &        -                            &  2701$\pm$225       &   47.75$\pm$1.29      &  &   QSFit    \\
+   \rowfont{\color{teal}}           & 56960    & \mgii     &   99$\pm$4              &  7312.6$\pm$340        &   188$\pm$137         &   50.75$\pm$2.21     &   &   QSFit   \\
+                                            \cdashline{2-8}
+     \rowfont{\color{blue}}        & 58693    & \civ      & 54.688$\pm$0.6    &  6000.3$\pm$70           &      33$\pm$28          &   39.28$\pm$0.43     &   &   QSFit   \\  
+                                               & 58693    & \ciii       & 115.08$\pm$1.2    & 15000                            &  2772$\pm$86          &   96.36$\pm$0.97     &   &   QSFit   \\  
+     \rowfont{\color{teal}}         & 58693    & \mgii    & 46.361$\pm$1.3    & 8900$\pm$278             &  1000                         &   53.46$\pm$1.54     &   &   QSFit   \\  
+\hline
+\hline
+     %    \end{tabular}
+    \end{tabu}
+\caption{Line Measurement Information from   %\href{QSFIT}{https://qsfit.inaf.it/}, unless otherwise stated. 
+      Shen11 is \citet{Shen2011}. 
+      Ham17 is \citet{Hamann2017}.
+      DR12 SAS is the line measurement information from the SDSS DR12 
+      Science Archive Server (SAS).
+      $^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
+      Positive values of Voff means the line is blueshifted.
+      $^{(b)}$Bit 3: FWHM value hits a limit in the fit;
+      $^{(c)}$QSFit does not fit the \civ line. 
+      The different colours of text are merely for readability.
+    }
+ \label{tab: QSFIT_line_values}
+\end{table*}
+
+\begin{table*}
+  \begin{tabular}{ll l l cc ll}
+    \hline
+    \hline
+    Object        & MJD         & $M_i$   &  $L_{\rm bol}$             & \multicolumn{2}{c}{$M_{\rm BH}$}          & $\eta_{\rm Edd}$  & Ref. \\
+                      &                &              &                                   & \mgii      & \civ                                    &                             &        \\
+    \hline
+                      & 53498    & -27.74   & 47.216$\pm$0.004   &  9.55$\pm$0.05   &   9.49$\pm$0.04   &  -0.3783               & Shen2011\\
+ J1205+3422  & 58538    &               &                              &                             &                                &                              &  \\
+                      & 58693    &               &                              &                            &                                 &                             &  \\
+    \hline 
+                      & 54553    & -26.75   & 46.166$\pm$0.04    &   9.03$\pm$0.366 & 8.742$\pm$0.15   &  -0.6768               & Shen2011\\
+ J1638+2827 & 55832    &  -26.40   & 46.721$\pm$0.073  &   9.338                   &  9.1289                   & -0.717                           & Kol017\\
+                      & 58583    &              &                                   &                              &                                 &                   & \\
+    \hline 
+                      & 56189    &  -25.46  & 46.231$\pm$0.073  &   9.448                 & 8.733                        &  -1.317               & Kol017\\
+J2228+2201  & 56960    &               &                                  &                           &                                    &                 &   \\
+                      & 58693    &              &                                   &                            &                                   &               &  \\
+    \hline
+    \hline
+  \end{tabular}
+  \caption{$\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio.
+        Shen11 is \citet{Shen2011}. 
+      Kol17 is \citet{Kozlowski2017}.}
+\end{table*}
 

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191017.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191016.tex
@@
 Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
-Laor1995, McIntosh1999, Nazarova2003}.
-
-\citet{Wilhite2006} examine
+Laor1995, McIntosh1999, Nazarova2003}.  \citet{Wilhite2006} examine
 the variability of a C~\textsc{iv} sample of 105 quasars observed at
@@
 model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
-Proga2000}.  with one dominating over the other depending on the shape
+Proga2000}, with one dominating over the other depending on the shape
 of the SED \citep[][strong \civ\ EQW indicates a more ionizing SED and
-large \civ\ blueshift indicating a less ionizing SED]{Leighly2004b}.
+large \civ\ blueshift indicating a less ionizing SED ]{Leighly2004b}.
 
 The Sloan Digital Sky Survey Reverberation Mapping Project
-\cite[(SDSS-RM)][]{Shen2015} has a monitored $\sim$350 quasars with
+\cite[SDSS-RM; ][]{Shen2015} has a monitored $\sim$350 quasars with
 \civ. Noting the biases associated with \civ Emission Line Properties
@@
 at 3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively
-\citep{Cutri2011}. We choose the cosmological parameters
-$\Omega_{\Lambda} = 0.7$, $\Omega_{\rm M} = 0.3$, and $h = 0.7$ in
-order to be consistent with \citet{Shen2011}.
+\citep{Cutri2011}.
+We adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73$,
+$\Omega_{\rm M} = 0.27$, and $h = 0.71$ in order to be consistent with
+\citet{Hamann2017}. As a guide this cosmology has a $z=2.000$
+comoving radial distance of 5244.3 Mpc, a $\sim$1.25\% difference
+compared to 5179.0 Mpc from $\Omega_{\Lambda} = 0.70$, $\Omega_{\rm M}
+= 0.30$, and $h = 0.70$ that is used in \citet{Shen2011}.
 
@@
     Details of our spectroscopic observations.
-    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and
-    eBOSS spectra have $\mathcal{R}\sim$2,000.  DBSP is the
-    $\mathcal{R}\sim$1,000-10,000 resolution Double Spectrograph for the
-    Palomar 200-inch telescope.  LRIS is the Low Resolution Imaging
-    Spectrometer on the Keck I 10m telescope.} 
+    Redshift and redshift errors from SDSS SkyServer for SDSS, BOSS and eBOSS spectra. 
+    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and  eBOSS spectra have $\mathcal{R}\sim$2,000.
+    DBSP: Double Spectrograph on the Palomar 200-inch telescope.
+    LRIS:  Low Resolution Imaging Spectrometer on Keck I 10m telescope.
+  } 
   \label{tab:obs_notes}
@@
 Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
-Abolfathi2018, Paris2018}.  These quasars were targetted via a range of
-techniques and algorithms \citep[][]{Richards2002, Ross2012,
-Myers2015}.  These data are supplemented by spectra from the Low
-Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I}
-telescope \citep{Oke1995}.  and the Double Spectrograph (DBSP)
-instrument on the Palomar {\it Hale} 5m telescope.
+Abolfathi2018, Paris2018}.  These quasars were targetted via a range
+of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
+Myers2015}. These SDSS, BOSS and eBOSS data are supplemented by
+spectra from the Low Resolution Imaging Spectrometer (LRIS) on the 10m
+Keck {\sc I} telescope \citep{Oke1995}.  and the Double Spectrograph
+(DBSP) instrument on the Palomar {\it Hale} 5m telescope.
 
@@
 
-\subsection{Line Properties}  
+\subsection{Emission Line and Power-law slope measurements}
 We use the measured quasar emission line properties from several catalogues: 
@@
 estimates as well as width, velocity offset and equivalent width of 20
-emission lines, includinng \civ, \ciii and \mgii.  We use the lastest
-version (v1.3.0) of the QSFIT
+emission lines, includinng \civ, \ciii and \mgii.  We attempt to process and fit
+all nine spectra using the lastest version (v1.3.0) of the QSFIT
 \href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online calculator}
-and process our spectra with QSFit setting $E(B-V)=0.00$.
+and setting $E(B-V)=0.00$.
 
-\citet{Hamann2017} in
-particular investigate in robust detail the UV continuum and the \civ\
-(and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000
-quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line
+\citet{Hamann2017} investigate in robust detail the UV continuum and
+the \civ\ (and \nv $\lambda$1238, 1242 \AA\ ) emission lines for over
+200,000 quasars in BOSS DR12Q \citep{Paris2017}.  The quasar redshift
+are limited to the range $1.53 \leq z \leq 5.0$ so that \civ\ and the
+adjacent continuum are covered by BOSS. These measurements provide
+line profile information and flux ratios\footnote{This emission-line
 catalog can be downloaded from
 \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
-The quasar redshift are limited to the range $1.53 \leq z \leq 5.0$ so
-that \civ\ and the adjacent continuum are covered by BOSS. These
-measurements provide line profile information and flux ratios.
 \citet{Hamann2017} was focused on $z\geq2$ quasars and specifcally
-their \civ properties in order to understand the high-$z$ ``Extremely Red Quasar''
-population \citet{Ross2015, Zakamska2016, Perrotta2019, Zakamska2019}. 
-As such, these measurements can be taken as the
-`gold standard' for \civ line measurement, though this is only for 2
-out of our 9 spectra.
+their \civ properties in order to understand the high-$z$ ``Extremely
+Red Quasar'' population \citet{Ross2015, Zakamska2016, Perrotta2019,
+Zakamska2019}.  As such, these measurements can be taken as the `gold
+standard' for \civ line measurement, though this is only for two out of
+our nine spectra.
 
-%% Notes.
  When using the \citet{Shen2011} catalogue, we report line luminosity,
 FWHM, rest-frame equivalent width, and their errors for the {\it
-whole} \mgii profile (the \citet{Shen2011} catalogue also quotes values
-for just the broad \mgii compoment, but the differences here in the
-two spectra of ours is negligible). The line luminosites in
-\citet{Calderone2017} are given in units of $10^{42}$ erg s$^{-1}$,
-while the line luminosites in \citet{Shen2011} are in units of
-$\log(L)$.  So comparing the error values for these measurements is
-not straightforward.
+whole} \mgii profile (this catalogue also quotes values for just the
+broad \mgii compoment, but the differences for our objects is
+negligible). The line luminosites in \citet{Calderone2017} are given
+in units of $10^{42}$ erg s$^{-1}$, while the line luminosites in
+\citet{Shen2011} are in units of $\log(L)$.  We do not report
+the \citet{Shen2011} error on the line luminosity.
+
+Power-law continuum slopes, $\alpha_{\lambda}$ where $f_{\lambda}
+\propto \lambda^{\alpha}$, are also reported in these catalogues and
+from QSFit.  We quote the most appropriate value given the emission
+line wavelength.
 
@@
 %%
-Gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
-cursus, dui nisl egestas augue, non fermentum nisl est nec
-nisi. Vestibulum nec mi justo, eget dapibus velit.
 
@@
 \hline
-                                                & 54553     & \lya     &   510.5              &  3207          &    ---                        &   ---                             & ---   &   DR12 SAS  \\
-   \rowfont{\color{blue}}          & 54533     & \civ      & 284$\pm$13    & 4574$\pm$658         &   55$\pm$438.31     &  31.80$\pm$1.51         &   &  QSFit  \\
+                                                & 54553     & \lya      &  ---                 &  3207                     &    ---                        &   ---                             & ---                        &   DR12 SAS  \\
+   \rowfont{\color{blue}}          & 54533     & \civ      & 257$\pm$13    &  4550$\pm$371     &   55$\pm$450         &  31.80$\pm$1.51         &                               &  QSFit$^{(d)}$  \\
    \rowfont{\color{blue}}          & 54533     & \civ      &  281                  &    4181$\pm$736   &    680$\pm$133       &    100.5$\pm$11.9       & $-0.14\pm0.68$   &  Shen2011   \\
-   \rowfont{\color{blue}}          & 54553     & \civ      & 462.6                &    4537$^{(a)}$           &    ---                       &   ---                              & ---   &  DR12 SAS  \\
-                                                & 54533     & \ciii     & 105$\pm$7       &  3687$\pm$336       &  $-246\pm122.7$   &  33.29$\pm$2.32         &    &  QSFit  \\
-                                                & 54553     & \ciii     &  164.6                &  4537$^{(a)}$             &  ---                         &  ---                           & ---     &  DR12 SAS \\
+   \rowfont{\color{blue}}          & 54553     & \civ      & ---                   &    4537$^{(a)}$        &    ---                       &   ---                              & ---                        &  DR12 SAS  \\
+                                                & 54533     & \ciii     &  130$\pm$10   &  3852$\pm$402    &  $-236\pm565$       &  36.7$\pm$2.8           &  $-1.47\pm0.20$     &  QSFit$^{(d)}$  \\
+                                                & 54553     & \ciii     &  ---                  &  4537$^{(a)}$          &  ---                         &  ---                           & ---                            &  DR12 SAS \\
+                                                &  54553     & \mgii  &   ---                 &   ---                      &     ---                     &    ---                          & ---                            &   QSFit$^{(e)}$  \\
     \rowfont{\color{teal}}          & 54533      & \mgii  &   139                  &  4757$\pm$2224   &  $-944\pm568$        &   119$\pm$40         &  $-1.49\pm0.54$       &  Shen2011   \\
     \rowfont{\color{teal}}          & 54533      & \mgii  & 187.4                 &  4537$^{(a)}$          &    ---                       &  ---                           & ---                             &  DR12 SAS  \\
-                                                \cdashline{2-8}
+                                                \cdashline{2-9}
                                                 & 55832     & \lya     & 288$\pm$11    &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99     &    &   QSFit  \\
-                                                & 55832     & \lya     &   633.9            &    4165.6$^{(a)}$        &    ---                       &   ---                           &   ---   &   DR12 SAS  \\
+                                                & 55832     & \lya     &   ---                 &  4165.6$^{(a)}$         &    ---                       &   ---                           &   ---   &   DR12 SAS  \\
 \multirow{2}{*}{\bf {J1638+2827}}
-                & \textcolor{blue}{55832} & \textcolor{blue}{\civ}  &   \textcolor{blue}{73$\pm$3}               &  \textcolor{blue}{6253$\pm$259}   &  \textcolor{blue}{270$\pm$106}     &  \textcolor{blue}{45.15$\pm$1.90}      &  &   QSFit    \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &   -                     &    5210$\pm$226    &    ---                       &     42.76$\pm$1.96      &   &   Ham17  \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &  125.1               &    5385$^{(a)}$          &    ---                       &   ---                             &   &   DR12 SAS  \\
-                                                 & 55832     & \ciii     & 19$\pm$6         &  14952$\pm$4682  &    3000$\pm$0         &   17.79$\pm$5.49      &  &   QSFit    \\
-                                                 &  55832    &  \ciii    &  10.68               &     5385$^{(a)}$         &  ---                        &                                &   &   DR12 SAS\\
+ & \textcolor{blue}{55832} & \textcolor{blue}{\civ}  & \textcolor{blue}{63$\pm$3}  &   \textcolor{blue}{6052$\pm$250}  &  \textcolor{blue}{-117$\pm$103}  &  \textcolor{blue}{43.2$\pm$1.7}  &  \textcolor{blue}{-2.25$\pm$0.05} & QSFit    \\
+    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---                     &    5210$\pm$226    &    ---                       &     42.8$\pm$2.0      & $-3.35$ &   Ham17  \\
+    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---                 &    5385$^{(a)}$          &    ---                      &   ---                             &---   &   DR12 SAS  \\
+                                                 & 55832     & \ciii     & 19$\pm$6         &  14952$\pm$4682  &    3000$\pm$0        &   17.79$\pm$5.49         &   $-2.25\pm0.05$         &   QSFit    \\
+                                                 &  55832    &  \ciii    &  10.68               &     5385$^{(a)}$         &  ---                          &                                      &  --- &   DR12 SAS\\
     \rowfont{\color{teal}}           & 55832      & \mgii   &  41$\pm$7       &        0$\pm$0          &    1000$\pm$1108    &    81.76$\pm$13.90    &    &   QSFit  \\
-    \rowfont{\color{teal}}           &  55832     & \mgii   &  34.66               &     5385$^{(a)}$        &  ---                       &                                &   &   DR12 SAS\\  
+    \rowfont{\color{teal}}           &  55832     & \mgii   &  34.66               &     5385$^{(a)}$        &  ---                           &                                     &  ---  &   DR12 SAS\\
                                                \cdashline{2-9}
@@
     \rowfont{\color{blue}}         &   56189      & \civ    &   ---                  &   ---                          &     ---                        &    ---                             &              &   QSFit$^{(c)}$  \\
-    \rowfont{\color{blue}}         &   56189      & \civ    &   ---                       &   2994$\pm$620        &     ---                        &   42.18$\pm$5.59        &    &    Ham17  \\
+    \rowfont{\color{blue}}         &   56189      & \civ    &   ---                  &   2994$\pm$620        &     ---                        &   42.2$\pm$5.6            & -1.59   &    Ham17  \\
     \rowfont{\color{blue}}         &   56189      & \civ    &  48.67                 &    5218$^{(a)}$             &    ---                        &   ---                             &               &   DR12 SAS  \\
@@
    \rowfont{\color{teal}}           & 56960    & \mgii     &   99$\pm$4              &  7312.6$\pm$340        &   188$\pm$137         &   50.75$\pm$2.21     &   &   QSFit   \\
-                                            \cdashline{2-8}
+                                            \cdashline{2-9}
      \rowfont{\color{blue}}        & 58693    & \civ      & 54.688$\pm$0.6    &  6000.3$\pm$70           &      33$\pm$28          &   39.28$\pm$0.43     &   &   QSFit   \\  
@@
     \end{tabu}
-\caption{Line Measurement Information from   %\href{QSFIT}{https://qsfit.inaf.it/}, unless otherwise stated. 
+    \caption{Line Measurement information for the nine epochs for the 3 quasars.
+      Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM and $V_{\rm off}$ in km s$^{-1}$,
+      where positive values of $V_{\rm off}$ means the line is blueshifted.
+      Equivalent widths are \AA\.  
       Shen11 is \citet{Shen2011}. 
@@
       Science Archive Server (SAS).
-      $^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
+      %$^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
       Positive values of Voff means the line is blueshifted.
-      $^{(b)}$Bit 3: FWHM value hits a limit in the fit;
-      $^{(c)}$QSFit does not fit the \civ line. 
+%      $^{(b)}$Bit 3: FWHM value hits a limit in the fit
+      Notes: $^{(c)}$QSFit does not fit the \civ line for J2228+2201 MJD 56189. 
+      $^{(d)}$Emission line modelled with two components.
+
       The different colours of text are merely for readability.

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191018.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191017.tex
@@
 the subsequent mismatch in the expected ``viscous'' timescale, which
-for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was
-noted over 30 years ago \citep[e.g.][]{Alloin1985}. However, with new
-photometric light-curve and repeat spectroscopic data, the desire for
-a deeper understanding of AGN accretion disk physics has been recently
-re-invigorated the field \citep[e.g.][]{Lawrence2018, Antonucci2018}.
+for a $\approx$10$^{7}$ M$_{\odot}$ central supermassive black hole
+(SMBH) is $\sim$hundreds of years, was noted over 30 years ago
+\citep[e.g.][]{Alloin1985}. However, with new photometric light-curve
+and repeat spectroscopic data, the desire for a deeper understanding
+of AGN accretion disk physics has been recently re-invigorated the
+field \citep[e.g.][]{Lawrence2018, Antonucci2018}.
 
@@
 
+\begin{table*}
+  \centering
+  \begin{tabular}{r  r  r r r   r r r r}
+    \hline 
+    \hline 
+    Object                           & \multirow{3}{*}{Redshift}  & \multirow{3}{*}{$g$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
+    R.A.
+/ deg                     &                                         &                                                          &                                 &                                   &                                               &  Time           & Spectrum                 & \\
+    Decl.
+/ deg                   &                                         &                                                          &                                &                                     &                                              &  / seconds    & Plate-FiberID  & \\
+    \hline  
+                                         &                                         &                        &               &                            &                    &                             &                              & \\
+    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             & tbd                          & 2089-427             & \\
+    181.436164                  & 2.071                              & {\bf 17.99?}     &  58538   &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions?
+\\
+    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2$\times$1200   &                              &   \\
+                                         &                                       &                          &                &                          &                   &                                &                              & \\
+    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS             & tbd                          &  2948-614              & \\
+    249.720558	                 &  2.186$\pm$0.0007     &                          &  55832    & 2011-Sep-28     & BOSS            &   3603                  &  5201-178            & \\
+    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10      & LRIS              &  2$\times$900    &                              & \\
+                                        &                                      &                          &                &                           &                   &                              &                                & \\
+    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                &  56189    & 2012-Sep-19      & BOSS             &  2702                 &   6118-720          & \\
+    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30      & BOSS             & tbd                         &   7582-790          & QSO1-REOBS \\ 
+    +22.017478                &                                      &                          &  58693    & 2019-Jul-29        & DBSP              & 2$\times$1200  &                           &    \\
+                                       &                                       &                          &               &                             &                   &                              &                            & \\
+    \hline \hline   
+  \end{tabular}
+  \caption{
+    Details of our spectroscopic observations.
+    Redshift and redshift errors from SDSS SkyServer for SDSS, BOSS and eBOSS spectra. 
+    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and  eBOSS spectra have $\mathcal{R}\sim$2,000.
+    DBSP: Double Spectrograph on the Palomar 200-inch telescope.
+    LRIS:  Low Resolution Imaging Spectrometer on Keck I 10m telescope.
+  } 
+  \label{tab:obs_notes}
+\end{table*}
+
 Here, we report on three quasars  
@@
 In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
-the \civ\ doublet \citep{Kramida2018}. The ground state of carbon is
-1$s^2$ 2$s^2$ 2$p^2$.  Using the
+the \civ\ doublet \citep{Kramida2018}.  The 1548.202 and 1550.774 \AA\
+emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
+transition with energies 64,484 cm$^{-1}$ and 64,591 cm$^{-1}$
+\citep[e.g.][]{Moore1993}.  The ground state of carbon is 1$s^2$
+2$s^2$ 2$p^2$.  Using the
 \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
@@
 \civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
-itself. The 1548.202 and 1550.774 \AA\ emission doublet is created by
-the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition with energies 64,484
-cm$^{-1}$ and 64,591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.
+itself. This energy corresponds to a thermal temperature of $T
+\gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
+X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).
 
@@
 accurate indicator of the Eddington ratio or quasar SED.
-%%
 Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}
-  \centering
-  \begin{tabular}{r  r  r r r   r r r r}
-    \hline 
-    \hline 
-    Object                           & \multirow{3}{*}{Redshift}  & \multirow{3}{*}{$g$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
-    R.A.
-/ deg                     &                                         &                                                          &                                 &                                   &                                               &  Time           & Spectrum                 & \\
-    Decl.
-/ deg                   &                                         &                                                          &                                &                                     &                                              &  / seconds    & Plate-FiberID  & \\
-    \hline  
-                                         &                                         &                        &               &                            &                    &                             &                              & \\
-    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             & tbd                          & 2089-427             & \\
-    181.436164                  & 2.071                              & {\bf 17.99?}     &  58538   &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions?
-\\
-    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2$\times$1200   &                              &   \\
-                                         &                                       &                          &                &                          &                   &                                &                              & \\
-    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS             & tbd                          &  2948-614              & \\
-    249.720558	                 &  2.186$\pm$0.0007     &                          &  55832    & 2011-Sep-28     & BOSS            &   3603                  &  5201-178            & \\
-    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10      & LRIS              &  2$\times$900    &                              & \\
-                                        &                                      &                          &                &                           &                   &                              &                                & \\
-    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                &  56189    & 2012-Sep-19      & BOSS             &  2702                 &   6118-720          & \\
-    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30      & BOSS             & tbd                         &   7582-790          & QSO1-REOBS \\ 
-    +22.017478                &                                      &                          &  58693    & 2019-Jul-29        & DBSP              & 2$\times$1200  &                           &    \\
-                                       &                                       &                          &               &                             &                   &                              &                            & \\
-    \hline \hline   
-  \end{tabular}
-  \caption{
-    Details of our spectroscopic observations.
-    Redshift and redshift errors from SDSS SkyServer for SDSS, BOSS and eBOSS spectra. 
-    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and  eBOSS spectra have $\mathcal{R}\sim$2,000.
-    DBSP: Double Spectrograph on the Palomar 200-inch telescope.
-    LRIS:  Low Resolution Imaging Spectrometer on Keck I 10m telescope.
-  } 
-  \label{tab:obs_notes}
-\end{table*}
 \section{Data}
@@
 
-\begin{table*}
-\begin{tabular}{ l rrrr rrrr rrrr rrrr rrrr rr|}
-\hline
-\hline 
-Object (MJD)               & $f$1450 & $\alpha_{\rm C IV}$    & $\alpha$    & REW                       & cREW   &  wREW  & FWHM              & cFWHM  &  wFWHM  & $\sigma$     \\
-\hline 
-J1638+2827 (55832) & 1.4659    & -3.3547             & -4.026$\pm$0.452 & 42.76$\pm$1.96  & 26.72  & 16.03  & 5210$\pm$226 & 4651      & 13444    & 3702          \\
-J2228+2201 (56189) & 0.5101    & -1.5931             & -0.657$\pm$0.004 & 42.18$\pm$5.59  &  6.42   & 35.76  & 2994$\pm$620 & 1458      &   7636    & 3002           \\
-\hline
-\end{tabular}
- \caption{
-Measured line values using the methods and catalogue from \citet{Hamann2017}. 
-\noindent {\tt f1450} = flux in the uncorrected BOSS spectrum at 1450 \AA\ rest (10$^{-17}$ ergs s$^{-1}$ cm$^{-2}$ \AA$^{-1}$) used to anchor the power law continuum fits beneath \civ\ and \nv , 
-                                     e.g., $f_{\lambda} = f_{1450}\, (\lambda /1450{\rm \AA})^{\alpha}$; 
-\noindent {\tt $\alpha_{\rm C IV}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) measured from the BOSS spectrum on either side of \civ ; 
-\noindent {\tt $\alpha$}                            = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) between 1350 \AA\ and 2200 \AA\ in the flux corrected BOSS spectrum; 
-\noindent {\tt REW} = \civ\ REW (\AA ) from the line profile fit;
-\noindent {\tt cREW} = \civ\ REW (\AA ) for the core Gaussian component;
-\noindent {\tt wREW} = \civ\ REW (\AA ) for the wing Gaussian component; 
-\noindent {\tt FWHM} = \civ\ FWHM (km/s) from the line profile fit; 
-\noindent {\tt fwhmc} = \civ\ FWHM (km/s) for the core Gaussian only.
-\noindent {\tt fwhmw} = \civ\ FWHM (km/s) for the wing Gaussian only.
-\noindent {\tt $\sigma$} = \civ\ velocity dispersion (km/s) measured from the profile fit \citep{Peterson2004}.
-Errors were given are 1$\sigma$ uncertainties. 
-} 
- \label{tab:Ham17_lines}
-\end{table*}
+\subsection{Emission Line and Power-law slope measurements}
+We use the measured quasar emission line properties from several catalogues: 
+\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017} and
+\citet{Calderone2017}.
 
-\begin{table*}
-\begin{tabular}{ l rrr rrr rrr rrr}
-\hline
-\hline
-  \multicolumn{1}{c}{Object (MJD)} &
-  \multicolumn{1}{c}{$M_{\rm I}(z=2)$} &
-  \multicolumn{1}{c}{$\log$($L_{\rm Bol} / {\rm erg s}^{-1}$} &
-  \multicolumn{1}{c}{$\log(L_{\rm CIV})$} &
-  \multicolumn{1}{c}{FWHM} &
-  \multicolumn{1}{c}{EW} &
-  \multicolumn{1}{c}{$\alpha$} &
-  \multicolumn{1}{c}{$\log$BH } &
-  \multicolumn{1}{c}{Edd. ratio, \%)} \\
-\hline
-  J1205+3422 (53498)   & 
-  -27.742                      & 47.22$\pm$0.004    &    %46.37$\pm$0.009    & 46.634$\pm$0.004   & 44.896$\pm$0.013 & 
-44.896$\pm$0.014     &   5230$\pm$219          & 30.1$\pm$1.21        &  -1.467$\pm$0.076    &  % & 27.59                         & 1118$\pm$133.5 & 
-  9.494$\pm$0.036    &  42 \\
+\citet{Shen2011} present a compilation of properties of the 105,783
+quasars in the SDSS Data Release 7 (DR7) quasar catalog \citep[DR7Q;
+][]{Schneider2007}. \citet{Shen2011} report non-zero \civ\ FWHM and
+EWs for approximately half (51,501) of the full DR7Q, and non-zero
+\mgii FWHM and EWs for 80\% (84,183) of the DR7Q quasars).
 %%
- J1638+2827 (54553)   & 
- -26.750                      & 46.17$\pm$0.040    & %45.50$\pm$0.086      & 45.586$\pm$0.040 & 44.449$\pm$0.036   & 
-44.449$\pm$0.036    &  4180$\pm$736          & 100.5$\pm$11.9      & -0.137$\pm$0.677    &   % & 4.630                      & 680$\pm$133.5         & 
-  8.743$\pm$0.154     & 21  \\
-\hline
-\hline
-\end{tabular}
- \caption{
 Measured line values using the methods and catalogue from
@@
 virial BH mass.
-}
- \label{tab:Shen11_lines}
-\end{table*}
-
-\subsection{Emission Line and Power-law slope measurements}
-We use the measured quasar emission line properties from several catalogues: 
-\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017} and
-\citet{Calderone2017}.
-
-\citet{Shen2011} present a compilation of properties of the 105,783
-quasars in the SDSS Data Release 7 (DR7) quasar catalog \citep[DR7Q;
-][]{Schneider2007}. \citet{Shen2011} report non-zero \civ\ FWHM and
-EWs for approximately half (51,501) of the full DR7Q, and non-zero
-\mgii FWHM and EWs for 80\% (84,183) of the DR7Q quasars).
 
@@
 \section{Results}
-Figure~\ref{fig:civ_clqs} presents the threes high-$z$ CLQ quasars. 
-%%
-%%
-For J1205+3422, over the course of 5040 days observed, 1640 days in the
-rest-frame. 
-For J1638+2827, over the course of 1279 days observed, 400 days in the
-rest-frame, the broad \civ\ and \ciii BEL start to fade.  For
-J2228+2201, over the course of 771 days observed, 240 days in the
-rest-frame, broad \civ\ and \ciii BELs both emerge and the standard
-UV/blue continuum slope increases in flux.  the UV/blue continuum
-diminishes and the shape of \lya changes.
-%%
+Figure~\ref{fig:civ_clqs} presents the optical and infrared light
+curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
+shows the spectra for each epoch, with the MJD of observation given by
+the dashed vertical lines in the light curves.
+
+For J1205+3422, over the course of 5040 days observed, 1640 days in
+the rest-frame.  For J1638+2827, over the course of 1279 days
+observed, 400 days in the rest-frame, the broad \civ\ and \ciii BEL
+start to fade.  For J2228+2201, over the course of 771 days observed,
+240 days in the rest-frame, broad \civ\ and \ciii BELs both emerge and
+the standard UV/blue continuum slope increases in flux.  the UV/blue
+continuum diminishes and the shape of \lya changes.
 
@@
   \centering
-  \begin{tabular}{l  lll  lll lll lll }
-    \hline 
-    \hline 
-                      & \multicolumn{3}{l}{ {\bf J1205+3422}}          &  \multicolumn{6}{l}{{\bf J1638+2827}}                                                                                             &  \multicolumn{3}{l}{ {\bf J2228+2201}} \\
-Emission         & \multicolumn{3}{l}{MJD 53498}                        & \multicolumn{3}{l}{MJD 54553}                            & \multicolumn{3}{l}{MJD 55832}                          &  \multicolumn{3}{l}{MJD 56189}     \\
-line                 & Line  $\sigma$ & Line  Flux &   Cont.
-Flux   & Line  $\sigma$   & Line  Flux      & Cont.
-Flux      & Line  $\sigma$ & Line  Flux  &   Cont.
-Flux       & Line  $\sigma$ & Line  Flux       &   Cont.
-Flux  \\    \hline
-Ly$\alpha$     &   ---	        &	---      & ---                   &  1362	            &	510.5	    &	7.224                 & 1769                 &  633.9	 &  5.376                 & ---                   &  ---                & ---    \\
-\nv	               & 1604	        & 1251        &  853.5               &  \; 854.6	    &	122.4   	    &	5.546                 & 1012                 &  107.1	 &  4.645                 &  5501	        &  611.3	          & -2.58  \\
-\civ $^{(a)}$     & 2174	        & 1254	   &  661.6                &  1927	            &	462.6	    &	2.722                 & 2287	               &  125.1	 &  1.256                 &  2216	        & \; 48.67          &   0.49  \\
-\heii$^{(a)}$    &  2174            & \;\; 33.2  &  620.3               &  1927    	    & \;\;\; 8.067  &	2.447                 & 2287	               &  \; 10.7	 &  1.001                 &  2216	        &  \;\;\; 0.35      &   0.39  \\
-\ciii$^{(a)}$     & 2174	        & \;  449.4  &  523.6               &  1927    	    & 164.6           &	1.966                 & 2287	               &  \; 29.5	 &  0.601                &  2216	        & \; 17.2             &  0.41  \\
-\mgii $^{(a)}$   &  2174	        & \;	405.4  &  334.1              &  1927    	            & 187.4           &	1.513                 & 2287	               &  \; 34.7	 &  0.346                &  2216	        & \; 33.6	           &  0.29  \\
-    \hline   
-   \hline   
-  \end{tabular}
-  \caption{Line Measurement Information from the SDSS DR12 Science Archive Server (SAS). 
-    %dr12.sdss.org/spectrumDetail?plateid=2089\&mjd=53498\&fiber=427 
-    Line $\sigma$ in units of   km s$^{-1}$; 
-    Line flux          in units of  10$^{-17}$ erg/cm$^2$/s; 
-    Continuum      in units of  10$^{-17}$ erg/cm$^2$/s/ \AA; 
-    $^{(a)}$Emission lines of a common ``width group'', in this case,
-    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
-    the same intrinsic velocity width in the SDSS spectral line fitting
-    procedure \citep{Bolton2012}. 
-  }
- \label{tab:SDSS_line_values}
-\end{table*}
-
-\begin{table*}
-  \centering
   % \begin{tabular}{lll  cccc r }
@@
 & $\alpha_{\lambda}$   &   Catalogue \\
-    % &                 &                                    &                           &                                   &                                       &          &     \\  
     \hline                                     
-    \rowfont{\color{blue}}       & 53948    & \civ      &  523$\pm$14    &   9816$\pm$321       &  1407$\pm$81      &  16.83$\pm$0.43      & $-1.64\pm0.01$      &      QSFit    \\
-    \rowfont{\color{blue}}       & 53948    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    &    30.1$\pm$1.21      & $-1.47\pm0.08$     &  Shen2011 \\
-    \rowfont{\color{blue}}       & 53948    & \civ      &                           &   5119$^{(a)}$             &    ---                     &   ---                          &  ---                        & DR12 SAS  \\
-                                             & 53948     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    &  25.10$\pm$0.59      & $-1.65\pm0.01$     &       QSFit   \\
-                                             & 53948    & \ciii       &                          &   5119$^{(a)}$             &  ---                       &    ---                         &  ---                         & DR12 SAS  \\
-  \rowfont{\color{teal}}         & 53948     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     &  26.66$\pm$1.65     &   $-1.65\pm0.01$    &       QSFit   \\
-  \rowfont{\color{teal}}         & 53948     & \mgii     &  284                  &   4730$\pm$314       &  $-179\pm188$     &  32$\pm$3.88           &  $-1.87\pm0.06$    & Shen2011  \\
+    \rowfont{\color{blue}}       & 53498    & \civ      &  523$\pm$14    &   9816$\pm$321        &  1407$\pm$81      &  16.83$\pm$0.43    & $-1.64\pm0.01$      &           QSFit  \\
+    \rowfont{\color{blue}}       & 53498    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    &    30.1$\pm$1.21    & $-1.47\pm0.08$     &     Shen2011 \\
+    \rowfont{\color{blue}}       & 53498    & \civ      &   ---                  &   5119$^{(a)}$             &    ---                     &   ---                        &  ---                        &     DR12 SAS   \\
+                                             & 53498     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    &  25.10$\pm$0.59    & $-1.65\pm0.01$     &            QSFit  \\
+                                             & 53498    & \ciii       &   ---                 &   5119$^{(a)}$             &  ---                       &    ---                       &  ---                         &       DR12 SAS  \\
+  \rowfont{\color{teal}}         & 53498     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     &  26.66$\pm$1.65    &   $-1.65\pm0.01$    &  $^{(d)}$QSFit \\
+  \rowfont{\color{teal}}         & 53498     & \mgii     &  284                  &   4730$\pm$314       &  $-179\pm188$     &  32$\pm$3.88         &  $-1.87\pm0.06$    &       Shen2011 \\
  \multirow{2}{*}{{\bf J1205+3422}}  
@@
                                  \cdashline{2-9}
-                                               & 58538     & \lya     & 1393$\pm$11   & $>$15000            &  $-796\pm57$             &  ---     &    &   QSFit  \\
-    \rowfont{\color{blue}}        & 58538     & \civ      &  1037$\pm$5    & $>$15000            &  983$\pm$40             &  ---     &    &   QSFit    \\  
-                                              & 58538      & \ciii     &    677$\pm$4    & $>$15000            & $>$3000                    &  ---     &     &  QSFit   \\  
-    \rowfont{\color{teal}}         & 58538     & \mgii    &     755$\pm$4  & $>$15000            & 350$\pm$39               &  ---      &    &   QSFit  \\
+                                              & 58538     & \lya      & 1393$\pm$11   & $>$15000            &  $-796\pm57$           &  ---                         &  ---                        &   QSFit  \\
+    \rowfont{\color{blue}}        & 58538     & \civ      & 1037$\pm$5    & $>$15000            &  983$\pm$40             &  ---                         &  ---                         &   QSFit    \\
+                                              & 58538      & \ciii     &   677$\pm$4    & $>$15000            & $>$3000                     &  ---                         &  ---                         &  QSFit   \\
+    \rowfont{\color{teal}}         & 58538     & \mgii    &  755$\pm$4    & $>$15000            & 350$\pm$39               &  ---                         &  ---                         &   QSFit  \\
                                           \cdashline{2-9}
@@
                                                 & 54553     & \lya      &  ---                 &  3207                     &    ---                        &   ---                         & ---                         &   DR12 SAS  \\
-   \rowfont{\color{blue}}          & 54533     & \civ      & 257$\pm$13    &  4550$\pm$371     &   55$\pm$450         &  31.80$\pm$1.51         &                               &  QSFit$^{(d)}$  \\
-   \rowfont{\color{blue}}          & 54533     & \civ      &  281                  &    4181$\pm$736   &    680$\pm$133       &    100.5$\pm$11.9       & $-0.14\pm0.68$   &  Shen2011   \\
+   \rowfont{\color{blue}}          & 54553     & \civ      & 257$\pm$13    &  4550$\pm$371     &   55$\pm$450         &  31.80$\pm$1.51     &                                &  $^{(d)}$QSFit  \\
+   \rowfont{\color{blue}}          & 54553     & \civ      &  281                  &    4181$\pm$736   &    680$\pm$133       &    100.5$\pm$11.9  & $-0.14\pm0.68$    &  Shen2011   \\
    \rowfont{\color{blue}}          & 54553     & \civ      & ---                   &    4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\
-                                                & 54533     & \ciii     &  130$\pm$10   &  3852$\pm$402    &  $-236\pm565$       &  36.7$\pm$2.8           &  $-1.47\pm0.20$     &  QSFit$^{(d)}$  \\
+                                                & 54553     & \ciii     &  130$\pm$10   &  3852$\pm$402    &  $-236\pm565$       &  36.7$\pm$2.8          &  $-1.47\pm0.20$    &  $^{(d)}$QSFit  \\
                                                 & 54553     & \ciii     &  ---                  &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\
-                                                &  54553     & \mgii  &   ---                 &   ---                      &     ---                     &    ---                          & ---                            &   QSFit$^{(e)}$  \\
-    \rowfont{\color{teal}}          & 54533      & \mgii  &   139                  &  4757$\pm$2224   &  $-944\pm568$        &   119$\pm$40         &  $-1.49\pm0.54$       &  Shen2011   \\
-    \rowfont{\color{teal}}          & 54533      & \mgii  & 187.4                 &  4537$^{(a)}$          &    ---                       &  ---                           & ---                             &  DR12 SAS  \\
+    \rowfont{\color{teal}}          & 54553      & \mgii  &  139                  &  4757$\pm$2224   &  $-944\pm568$        &   119$\pm$40          &  $-1.49\pm0.54$    &  Shen2011   \\
+    \rowfont{\color{teal}}          & 54553      & \mgii  &  ---                 &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\
                                                 \cdashline{2-9}
@@
     \rowfont{\color{blue}}           &  55832   &  \civ     &  ---                 &    5210$\pm$226     &    ---                       &   42.8$\pm$2.0         & $-3.35$                 &     Ham17  \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---                 &    5385$^{(a)}$          &    ---                      &   ---                             &---   &   DR12 SAS  \\
-                                                 & 55832     & \ciii     & 19$\pm$6         &  14952$\pm$4682  &    3000$\pm$0        &   17.79$\pm$5.49         &   $-2.25\pm0.05$         &   QSFit    \\
-                                                 &  55832    &  \ciii    &  10.68               &     5385$^{(a)}$         &  ---                          &                                      &  --- &   DR12 SAS\\
-    \rowfont{\color{teal}}           & 55832      & \mgii   &  41$\pm$7       &        0$\pm$0          &    1000$\pm$1108    &    81.76$\pm$13.90    &    &   QSFit  \\
-    \rowfont{\color{teal}}           &  55832     & \mgii   &  34.66               &     5385$^{(a)}$        &  ---                           &                                     &  ---  &   DR12 SAS\\
+    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\
+                                                 & 55832     & \ciii     & 15$\pm$5       &  11421$\pm$3654   &   $>$3000                &   14.8$\pm$4.5         &  $-2.25\pm0.05$  &        QSFit \\
+                                                 &  55832    &  \ciii    &  ---                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                      &   DR12 SAS \\
+    \rowfont{\color{teal}}           &  55832     & \mgii   & ---                 &     5385$^{(a)}$         &  ---                           &   ---                          &  ---  &   DR12 SAS\\  
                                                \cdashline{2-9}
-      \rowfont{\color{blue}}        & 58583      & \civ      &  286$\pm$2     & -                              &                   -                &   20.89$\pm$0.13      &   &   QSFit   \\  
-                                                & 58583      & \ciii      &   92$\pm$1      &  6689$\pm$89         &    37$\pm$37.186        &   28.96$\pm$0.35      &   &   QSFit   \\  
-    \rowfont{\color{teal}}           & 58583      & \mgii   &  116$\pm$1      &  6649$\pm$85         & -422$\pm$34.818       &   67.38$\pm$0.77      &   &   QSFit   \\  
+      \rowfont{\color{blue}}        & 58583      & \civ      &  659$\pm$5   & $>$15000                &  $-493\pm56$          &   333$\pm$3            & $-0.43\pm0.01$     &   QSFit   \\  
+                                                & 58583      & \ciii      &  239$\pm$4   &  $>$15000               &  1514$\pm$127        &  124$\pm$2             & $-0.43\pm0.01$     &   QSFit   \\
+    \rowfont{\color{teal}}           & 58583      & \mgii   &  129$\pm$3    &  10957$\pm$307    &  138$\pm$128          &   78$\pm$2              &  $-0.43\pm0.01$    &   QSFit   \\  
 \hline
-    \rowfont{\color{blue}}         &   56189      & \civ    &   ---                  &   ---                          &     ---                        &    ---                             &              &   QSFit$^{(c)}$  \\
     \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &   2994$\pm$620       &     ---                       &   42.2$\pm$5.6      & -1.59                       &    Ham17  \\
-    \rowfont{\color{blue}}         &   56189      & \civ    &  48.67                 &    5218$^{(a)}$             &    ---                        &   ---                             &               &   DR12 SAS  \\
-                                               & 56189        &  \ciii   &  39$\pm$8         & 14097$\pm$2943      &   2243$\pm$1142    & 66.63$\pm$12.90         &    &   QSFit  \\
-                                               &  56189       & \ciii    &  17.2                   &     5218$^{(a)}$           &  ---                          &                                      &   &   DR12 SAS \\
-    \rowfont{\color{teal}}          & 56189       & \mgii  &  23$\pm$6          &   6694$\pm$1765      &   -597$\pm$741       & 41.19$\pm$10.95        &  &   QSFit   \\
-    \rowfont{\color{teal}}         &  56189       &  \mgii &  33.6                    &     5218$^{(a)}$           &  ---                           &                                     &   &   DR12 SAS \\
+    \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                         &   DR12 SAS  \\
+                                               &  56189      &  \ciii   &  34$\pm$6       &  13748$\pm$2869    &   1851$\pm$1140    &  63$\pm$12          &  $-0.46\pm0.21$     &   QSFit  \\
+                                               &  56189      & \ciii    &  ---                  &     5218$^{(a)}$          &  ---                         &     ---                     & ---                          &   DR12 SAS \\
+    \rowfont{\color{teal}}          & 56189      & \mgii  &  25$\pm$6       &   7253$\pm$1712     &   $-931\pm708$      &  51$\pm$10.95      &  $-0.46\pm0.21$     &   QSFit   \\
+    \rowfont{\color{teal}}         &  56189      &  \mgii &  ---                  &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                          &   DR12 SAS \\
                                                   \cdashline{2-9}
@@
                                                \cdashline{2-9}
-     \rowfont{\color{blue}}        & 58693    & \civ      & 54.688$\pm$0.6    &  6000.3$\pm$70           &      33$\pm$28          &   39.28$\pm$0.43     &   &   QSFit   \\  
-                                               & 58693    & \ciii       & 115.08$\pm$1.2    & 15000                            &  2772$\pm$86          &   96.36$\pm$0.97     &   &   QSFit   \\  
-     \rowfont{\color{teal}}         & 58693    & \mgii    & 46.361$\pm$1.3    & 8900$\pm$278             &  1000                         &   53.46$\pm$1.54     &   &   QSFit   \\  
+%   
+     \rowfont{\color{blue}}        & 58693    & \civ     &  327$\pm$1          &  $>$15000              &   $-453\pm34$     &   ---                           & ---  &   QSFit   \\  
+                                               & 58693    & \ciii      & 115.08$\pm$1.2  &  $>$15000              &  2422$\pm$67       &   ---                          & ---  &   QSFit   \\  
+     \rowfont{\color{teal}}         & 58693    & \mgii   & 46.361$\pm$1.3   &  $>$15000             &  $>$1000                &   ---                          & ---  &   QSFit   \\  
 \hline
@@
       Science Archive Server (SAS).
+          $^{(a)}$Emission lines of a common ``width group'', in this case,
+    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
+    the same intrinsic velocity width in the SDSS spectral line fitting
+    procedure \citep{Bolton2012}. 
       %$^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
@@
 %      $^{(b)}$Bit 3: FWHM value hits a limit in the fit
-      Notes: $^{(c)}$QSFit does not fit the \civ line for J2228+2201 MJD 56189. 
+      Notes: QSFit does not fit the \mgii line for J1638+2827 MJD
+      54553 or 55832. QSFit does not fit the \civ line for J2228+2201 MJD 56189.
       $^{(d)}$Emission line modelled with two components.
-
       The different colours of text are merely for readability.
@@
         Shen11 is \citet{Shen2011}. 
-      Kol17 is \citet{Kozlowski2017}.}
+        Kol17 is \citet{Kozlowski2017}.
+        Measured line values using the methods and catalogue from
+\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
+$K$-corrected to $z = 2$; Bolometric luminosity computed from the
+monochromatic luminosity at 1350\AA\ using the spectral fits and
+bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
+luminosity, FWHM, rest-frame equivalent width, and their errors for
+the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
+continuum fit for \civ; Virial BH masses using calibrations of
+\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
+virial BH mass.
+      }
 \end{table*}
@@
 
-\section{Discussion and Conclusions}
-The variable properties of the rest-frame UV quasar emission lines
-have been long studied, with the global (or ensemble) Baldwin Effect
-(the anti-correlation between the EW of the emission line and the
-underlying continuum luminosity of single-epoch observations of a
-large number of AGN, first noted in \citet{Baldwin1977}. 
-%%
-More recently, the intrinsic Baldwin effect, the same anti-correlation but in an individual, variable AGN.
-%
-The variable properites of high-$z$ quasars, however, has been less 
-well stuided. Reasons for this include more massive systems will tend to 
-have longer timescales e.g. with $R_{\rm Sch}= 2GM /c^{2}$ and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$
-means   $t_{\rm dyn} \sim 6G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2} $.
-
-\noindent
-{\bf Our Eddington ratios \\
-Done 1\% \\
-Coatman, Hewett say \civ\ masses are okay.\\
-But what are these Eddington ratios? \\
-Low state BHs vs. High-mass BHs... \\
-Coatman et al?? Blue-shiftted \\
-}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_LBol_20191015.png}
-   \vspace{-12pt}
-   \caption[]{The Baldwin Plot. The bolometric luminosities are from \citet{Kozlowski2017},
-     while the REW measurements are from \citet{Hamann2017}.}
-  \label{fig:REWvsFWHM}
-\end{figure}
-
+%{\bf Our Eddington ratios \\
+%Done 1\% \\
+%Coatman, Hewett say \civ\ masses are okay.\\
+%But what are these Eddington ratios? \\
+%Low state BHs vs. High-mass BHs... \\
+%Coatman et al?? Blue-shiftted \\ }
+\section{Discussion}
 \civ\ probes the photoionization environment produced by the innermost
@@
 
+\subsection{The Baldwin Effect}
+The variable properties of the rest-frame UV quasar emission lines
+have been long studied, with the global (or ensemble) Baldwin Effect
+(the anti-correlation between the EW of the emission line and the
+underlying continuum luminosity of single-epoch observations of a
+large number of AGN, first noted in \citet{Baldwin1977}.  More
+recently, the intrinsic Baldwin effect, the same anti-correlation but
+in an individual, variable AGN.  The variable properites of high-$z$
+quasars, however, has been less well stuided. Reasons for this include
+more massive systems will tend to have longer timescales e.g. with
+$R_{\rm Sch}= 2GM /c^{2}$ and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$ means
+$t_{\rm dyn} \sim 6 G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2}
+$.
+
+\subsection{Eddington ratios and State Changes} 
+The broad UV and optical lines in quasars are most sensitive to the extreme ultraviolet (EUV)
+part of the spectral energy distribution (SED), with \civ\ (and indeed \heii and \nv) being at
+the higher eneggy end of the EUV distribution. 
+\citet{NodaDone2018} note that The soft X-ray excess produces most of
+the ionizing photons, so its dramatic drop leads to the disappearance
+of the broad-line region, driving the ``changing-look'' phenomena.
+major difference is that radiation pressure should be much more
+important in AGNs, so that the sound speed is much faster than
+expected from the gas temperature.
+%%
+This spectral hardening appears similar to the soft-to-hard state
+transition in black hole binaries at $L / L_{\rm Edd} \sim 0.02$
+(i.e. $\eta_{\rm Edd} \sim -1.7$, where the inner disc evaporates into
+an advection dominated accretion flow, while the overall drop in
+luminosity appears consistent with the hydrogen ionization disc
+instability.  Crucially \citet{NodaDone2018} make the prediction that
+all changing-look AGNs are similarly associated with the state
+transition at $L / L_{\rm Edd} \sim$a few per cent.
+
+We investigate this...  \citet{JiangYF2014, JiangYF2016, JiangYF2019}.
+\citet{JiangYF2019arXiv} use global three dimensional radiation
+magneto-hydrodynamic simulations to study the properties of inner
+regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$
+black hole with mass accretion rates reaching 7\% and 20\% of the
+Eddington value.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
+  {figures/CIV_CLQs_Baldwin_LBol_20191015.png}
+   \vspace{-12pt}
+   \caption[]{The Baldwin Plot. The bolometric luminosities are from \citet{Kozlowski2017},
+     while the REW measurements are from \citet{Hamann2017}.}
+  \label{fig:REWvsFWHM}
+\end{figure}
+
+\section{Conclusions}
+In this paper we have reported on three redshift $z>2$ quasars with
+dramatic changes in their \civ\ emission lines, the first
+`Changing-Look'' quasars at high redshift.  This is also the first
+time the changing-look behaviour has been seen in a high-ionization
+emission line.
+
+\begin{itemize}
+  \item {SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
+in their observed optical light curves, and subsequent spectroscopy
+shows significant changes in the \civ\ broad emission line, with both
+line collapse and emergence being displayed in rest-frame timescales
+of $\sim$240-1640 days.}
+\item Where observed, the profile of the Ly$\alpha$/\nv emission complex
+also changes, and there is tentative evidence for changes in the \mgii
+line.
+\item Although line measurements from the three quasars show large changes
+in the \civ\ line flux-line width plane, the quasars are not seen to
+be outliers when considered against the full $z>2$ quasar population
+in terms of (rest) Equivalent Width and FWHM properties.
+\item 
+We put these observations in context with recent ``state-change''
+models, but note that even in their `low-state', the \civ\ CLQs are
+above $\sim10\%$ in Eddington luminosity.
+\end{itemize}
+
 Etiam mollis viverra nisi eget aliquet. Aliquam erat volutpat. Vivamus
@@
 imperdiet lorem rhoncus sit amet.
-
-In this paper we have... 
-\begin{itemize}
-\item Pellentesque vel elit neque, in interdum lacus. Quisque sodales, nunc et luctus convallis, nisl dui luctus dui, at congue urna velit a; 
-\item At sit amet sapien a risus dapibus sagittis. Cras sed ultricies erat. Donec id metus sed urna lacinia convallis vel sed enim. 
-\item Nisi libero, ornare vel bibendum eu, sollicitudin sed leo. Cras tincidunt aliquet ultricies. Cras pretium velit leo, in malesuada. 
-\item Duis sagittis ultricies interdum. Proin sit amet sem nec metus feugiat pharetra.
-\end{itemize}
 

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191021.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191018.tex
@@
 estimates as well as width, velocity offset and equivalent width of 20
-emission lines, includinng \civ, \ciii and \mgii.  We attempt to process and fit
+emission lines, including \civ, \ciii and \mgii.  We attempt to process and fit
 all nine spectra using the lastest version (v1.3.0) of the QSFIT
@@
 whole} \mgii profile (this catalogue also quotes values for just the
-broad \mgii compoment, but the differences for our objects is
-negligible). The line luminosites in \citet{Calderone2017} are given
-in units of $10^{42}$ erg s$^{-1}$, while the line luminosites in
+broad \mgii component, but the differences for our objects is
+negligible). The line luminosities in \citet{Calderone2017} are given
+in units of $10^{42}$ erg s$^{-1}$, while the line luminosities in
 \citet{Shen2011} are in units of $\log(L)$.  We do not report
@@
 In the context of CLQs at lower-$z$...  
-(Balmer CLQs vs. \civ CLQs...) 
+(Balmer CLQs vs. \civ\ CLQs...) 
 Sociis natoque penatibus et
@@
 
+%%
+%% %% \eta_{\rm Edd} = log10((10**LBol)/((1.26e38)*(10**MBH)))
+%%
+%% Using    C IV
+
+%% In [6]: log10((10**47.216)/((1.26e38)*(10**9.49)))                                                                                                                                             
+%%Out[6]: -0.37437054511756207
+%%
+%%In [7]: log10((10**46.166)/((1.26e38)*(10**8.742)))                                                                                                                                            
+%%Out[7]: -0.676370545117567
+%%
+%%In [8]: log10((10**46.721)/((1.26e38)*(10**9.1289)))                                                                                                                                           
+%%Out[8]: -0.5082705451175662
+%%
+%%In [9]: log10((10**46.231)/((1.26e38)*(10**8.733)))                                                                                                                                            
+%%Out[9]: -0.6023705451175618
+
 \begin{table*}
-  \begin{tabular}{ll l l cc ll}
+  \begin{tabular}{l l  ll ll cc r}
     \hline
     \hline
-    Object        & MJD         & $M_i$   &  $L_{\rm bol}$             & \multicolumn{2}{c}{$M_{\rm BH}$}          & $\eta_{\rm Edd}$  & Ref. \\
-                      &                &              &                                   & \mgii      & \civ                                    &                             &        \\
+\multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$} & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref. \\
+                                      &                                   &                                      &                                                 & \mgii                  & \civ                    &  \mgii           &  \civ                       &        \\
     \hline
-                      & 53498    & -27.74   & 47.216$\pm$0.004   &  9.55$\pm$0.05   &   9.49$\pm$0.04   &  -0.3783               & Shen2011\\
- J1205+3422  & 58538    &               &                              &                             &                                &                              &  \\
-                      & 58693    &               &                              &                            &                                 &                             &  \\
+                                     & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen2011\\
+ J1205+3422                & 58538                         &                                      &                                                 &                             &                             &                    &                               & \\
+                                     & 58693                         &                                     &                                                  &                             &                             &                    &                               &   \\
     \hline 
-                      & 54553    & -26.75   & 46.166$\pm$0.04    &   9.03$\pm$0.366 & 8.742$\pm$0.15   &  -0.6768               & Shen2011\\
- J1638+2827 & 55832    &  -26.40   & 46.721$\pm$0.073  &   9.338                   &  9.1289                   & -0.717                           & Kol017\\
-                      & 58583    &              &                                   &                              &                                 &                   & \\
+                                    & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen2011\\
+ J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kol017\\
+                                    & 58583                          &                                      &                                                &                               &                            &                   &                                      &  \\
     \hline 
-                      & 56189    &  -25.46  & 46.231$\pm$0.073  &   9.448                 & 8.733                        &  -1.317               & Kol017\\
-J2228+2201  & 56960    &               &                                  &                           &                                    &                 &   \\
-                      & 58693    &              &                                   &                            &                                   &               &  \\
+                                   & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kol017\\
+J2228+2201               & 56960                          &                                       &                                                &                              &                               &                 &                                        & \\
+                                  & 58693                          &                                       &                                               &                               &                                &                &                   &  \\
     \hline
@@
 recently, the intrinsic Baldwin effect, the same anti-correlation but
-in an individual, variable AGN.  The variable properites of high-$z$
-quasars, however, has been less well stuided. Reasons for this include
+in an individual, variable AGN.  The variable properties of high-$z$
+quasars, however, has been less well studied. Reasons for this include
 more massive systems will tend to have longer timescales e.g. with
@@
 part of the spectral energy distribution (SED), with \civ\ (and indeed \heii and \nv) being at
-the higher eneggy end of the EUV distribution. 
+the higher energy end of the EUV distribution. 
 \citet{NodaDone2018} note that The soft X-ray excess produces most of
@@
 id. Ut varius iaculis quam in consequat. Nulla nec orci est, sit amet
-pellentesque nisl. Mauris non cursus lectus. Praesent placerat leo vel
-erat gravida lacinia. Donec vehicula consectetur lectus vitae
-luctus. Praesent nisl justo, laoreet elementum facilisis vel,
-tristique ac enim. Etiam vel quam ut quam eleifend
-tincidunt. Suspendisse sit amet eros vel elit ullamcorper
-laoreet. Etiam venenatis sodales turpis, nec lacinia ligula hendrerit
-nec. Nam eu vulputate purus. Quisque facilisis congue metus, sed
-imperdiet lorem rhoncus sit amet.
-
 Aliquam ac metus nec odio tempus pharetra sed nec diam. Sed eget arcu

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191022.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191021.tex
@@
 in the \civ\ line flux-line width plane, the quasars are not seen to
-be outliers when considered against the full $z>2$ quasar population
+be outliers when considered against the full $z\sim2$ quasar population
 in terms of (rest) Equivalent Width and FWHM properties.
@@
 models, but note that even in their `low-state', the \civ\ CLQs are
-above $\sim10\%$ in Eddington luminosity.
+above $\sim$10\% in Eddington luminosity.
 \end{abstract}
@@
   \centering
-  \begin{tabular}{r  r  r r r   r r r r}
+  \begin{tabular}{r  l  r r r   r r r r}
     \hline 
@@
                                          &                                         &                        &               &                            &                    &                             &                              & \\
-    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             & tbd                          & 2089-427             & \\
+    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             &                            & 2089-427             & \\
     181.436164                  & 2.071                              & {\bf 17.99?}     &  58538   &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions?
@@
                                          &                                       &                          &                &                          &                    &                                &                              & \\
-    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS             & tbd                          &  2948-614              & \\
-    249.720558	                 &  2.186$\pm$0.0007     &                          &  55832    & 2011-Sep-28     & BOSS            &   3603                  &  5201-178            & \\
+    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS           &                               &  2948-614              & \\
+    249.720558	                 &  2.186$\pm$0.0007     &                          &  55832    & 2011-Sep-28     & BOSS            &   3600                  &  5201-178            & \\
     +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10     & LRIS              &  2$\times$900    &                              & \\
                                         &                                      &                          &                &                            &                    &                              &                                & \\
-    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                &  56189    & 2012-Sep-19      & BOSS             &  2702                 &   6118-720          & \\
-    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30      & BOSS             & tbd                         &   7582-790          & QSO1-REOBS \\ 
+    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                &  56189    & 2012-Sep-19     & BOSS             &  2700                 &   6118-720          & \\
+    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30     & BOSS             &                             &   7582-790          & QSO1-REOBS \\ 
     +22.017478                &                                      &                          &  58693    & 2019-Jul-29       & DBSP             & 2$\times$1200  &                           &    \\
@@
     \hline                                     
-    \rowfont{\color{blue}}       & 53498    & \civ      &  523$\pm$14    &   9816$\pm$321        &  1407$\pm$81      &  16.83$\pm$0.43    & $-1.64\pm0.01$      &           QSFit  \\
+    \rowfont{\color{blue}}       & 53498    & \civ      &  511$\pm$13    &   9593$\pm$287        &  1172$\pm$74      & 15.9$\pm$0.4      & $-1.64\pm0.01$      &           QSFit  \\
     \rowfont{\color{blue}}       & 53498    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    & 30.1$\pm$1.21    & $-1.47\pm0.08$     &     Shen2011 \\
@@
                                                 & 54553     & \lya      &  ---                 &  3207                     &    ---                        &   ---                         & ---                         &   DR12 SAS  \\
-   \rowfont{\color{blue}}          & 54553     & \civ      & 257$\pm$13    &  4550$\pm$371     &   55$\pm$450         &  31.80$\pm$1.51     &                                &  $^{(d)}$QSFit  \\
-   \rowfont{\color{blue}}          & 54553     & \civ      &  281                  &    4181$\pm$736   &    680$\pm$133       &    100.5$\pm$11.9  & $-0.14\pm0.68$    &  Shen2011   \\
+   \rowfont{\color{blue}}          & 54553     & \civ      & 257$\pm$13    &  4550$\pm$371     &   55$\pm$450         &   31.8$\pm$1.5     &                                &  $^{(d)}$QSFit  \\
+   \rowfont{\color{blue}}          & 54553     & \civ      &  281                  &    4181$\pm$736   &    680$\pm$133       & 100.5$\pm$12  & $-0.14\pm0.68$    &  Shen2011   \\
    \rowfont{\color{blue}}          & 54553     & \civ      & ---                   &    4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\
@@
                                                   \cdashline{2-9}
-                                              & 56960         & \lya    & 121$\pm$38     & 3580$\pm$673       &     -16$\pm$171     &  13.52 $\pm$4.21    &                                  &   QSFit   \\
+                                              & 56960         & \lya    & 121$\pm$38     & 3580$\pm$673       &     -16$\pm$171     &  13.52 $\pm$4.21    & ---                           &   QSFit   \\
 \multirow{2}{*}{{\bf J2228+2201}}
-           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}     & \textcolor{blue}{254$\pm$5}    &  \textcolor{blue}{8731$\pm$172}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{45.35$\pm$0.90}    &    &    \\
+           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}  & \textcolor{blue}{229$\pm$4}  &  \textcolor{blue}{8911$\pm$169}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{46.8$\pm$0.9}    & ---    & \textcolor{blue}{QSFit}     \\
                                                & 56960    & \ciii      & 185$\pm$5         &        -                       &  2701$\pm$225     &   47.75$\pm$1.29      &  &   QSFit    \\  

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191025.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191022.tex
@@
 
-% \hypersetup{draft}
+\hypersetup{draft}
 
@@
 their first optical identification
-\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic
-changes in the broad emission lines (BELs) of quasars has only
-recently been identified \citep[e.g., ][]{LaMassa2015}.  Samples of over
-100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars
-(CSQs) have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}.
-The community uses both these terms as a cover for the underlying
+\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic changes
+in the broad emission lines (BELs) of quasars has only recently been
+identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
+``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
+have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}. The
+community uses both these terms as a cover for the underlying
 physics. For sake of argument, ``Changing Look'' quasars can
@@
 ``Changing State'' quasars (CSQs) have a `state-transition' similar to
-that in Galactic X-ray binaries \citep[][]{NodaDone2018,
-Ruan2019}. In this paper, we use the term `Changing Look', as we are
-currently agnostic, and somewhat ignorant, to the underlying physical
-processes.
+that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019}. In
+this paper, we use the term `Changing Look', as we are currently
+agnostic, and somewhat ignorant, to the underlying physical processes.
 
@@
   \centering
-  \begin{tabular}{r  l  r r r   r r r r}
+  \begin{tabular}{r l   r ll   r r r r}
     \hline 
     \hline 
-    Object                           & \multirow{3}{*}{Redshift}  & \multirow{3}{*}{$g$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
+    Object                           & \multirow{3}{*}{Redshift}  &                       & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date} & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
     R.A.
-/ deg                     &                                         &                                                          &                                 &                                   &                                               &  Time           & Spectrum                 & \\
+/ deg                     &                                         &   {$g$-band}   &                                 &                                  &                                               &  Time           & Spectrum                 & \\
     Decl.
-/ deg                   &                                         &                                                          &                                &                                     &                                              &  / seconds    & Plate-FiberID  & \\
+/ deg                   &                                         &    magnitude   &                                &                                   &                                              &  / seconds    & Plate-FiberID  & \\
     \hline  
                                          &                                         &                        &                &                            &                    &                              &                              & \\
-    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             &                            & 2089-427             & \\
-    181.436164                  & 2.071                              & {\bf 17.99?}     &  58538   &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions?
-\\
-    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2$\times$1200   &                              &   \\
+    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             &  8057                  & 2089-427             & \\
+    181.436164                  & 2.071                              & {\bf 17.99?}     &  58538   &  2019-Feb-24    & DBSP            &  1800                  &  ---                      &  Average conditions \\
+    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2400                   &  ---                      &   \\
                                          &                                       &                          &                &                          &                    &                               &                              & \\
-    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS           &                               &  2948-614              & \\
+    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS           &   4801                    &  2948-614              & \\
     249.720558	                 &  2.186$\pm$0.0007     &                          &  55832    & 2011-Sep-28     & BOSS            &   3600                   &  5201-178            & \\
-    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10     & LRIS              &  2$\times$900    &                              & \\
+    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10     & LRIS              &  1800                   &  ---                             & \\
                                         &                                      &                          &                &                            &                    &                              &                                & \\
     J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                &  56189    & 2012-Sep-19     & BOSS             &  2700                 &   6118-720          & \\
-    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30     & BOSS             &                             &   7582-790          & QSO1-REOBS \\ 
-    +22.017478                &                                      &                          &  58693    & 2019-Jul-29       & DBSP             & 2$\times$1200  &                           &    \\
+    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30     & BOSS             &  4500                  &   7582-790          & eBOSS reobservation \\
+    +22.017478                &                                      &                          &  58693    & 2019-Jul-29       & DBSP             & 2400                   &    ---                        &    \\
                                        &                                       &                          &               &                            &                   &                              &                            & \\
@@
     LRIS:  Low Resolution Imaging Spectrometer on Keck I 10m telescope.
+    %  2019-Feb-24    & DBSP            &  2$\times$900 f
+    %  2019-Jul-29     & DBSP            &  2$\times$1200
+    %  2019-Apr-10     & LRIS              &  2$\times$900
+    %& 2019-Jul-29       & DBSP             & 2$\times$1200
   } 
@@
 Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
-Laor1995, McIntosh1999, Nazarova2003}.  \citet{Wilhite2006} examine
-the variability of a C~\textsc{iv} sample of 105 quasars observed at
-multiple epochs by the SDSS.  They find a strong correlation between
-the change in the C~\textsc{iv} line flux and the change in the line
-width, but no correlations between the change in flux and changes in
-line center and skewness.  These authors find that the relation
-between line flux change and line width change is consistent with a
-model in which a broad line base varies with greater amplitude than
-the line core. The C~\textsc{iv} lines in these high-luminosity
-quasars appear to be less responsive to continuum variations than
-those in lower luminosity AGN.  \citet{Wilhite2006} find no evidence
-for variability of the well known blueshift of the C~\textsc{iv} line
-with respect to the low-ionization Mg~\textsc{ii}$\lambda$2798 line in
-the highest flux objects.
+Laor1995, McIntosh1999, Nazarova2003}.
+
+\citet{Wilhite2006} examine the variability of a C~\textsc{iv} sample
+of 105 quasars observed at multiple epochs by the Sloan Digital Sky
+Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
+find a strong correlation between the change in the C~\textsc{iv} line
+flux and the change in the line width, but no correlations between the
+change in flux and changes in line center and skewness.  These authors
+find that the relation between line flux change and line width change
+is consistent with a model in which a broad line base varies with
+greater amplitude than the line core. The C~\textsc{iv} lines in these
+high-luminosity quasars appear to be less responsive to continuum
+variations than those in lower luminosity AGN.  \citet{Wilhite2006}
+find no evidence for variability of the well known blueshift of the
+C~\textsc{iv} line with respect to the low-ionization
+Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects.
 
@@
   %% trim=l b r t
-  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
-  {figures/J1205+3422_landscape_20190920.png}
-  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
-  {figures/J1638+2827_landscape_20190920.png}
-  \includegraphics[width=16.7cm, trim=0.0cm 0.0cm  0.2cm 0.1cm, clip]
-  {figures/J2228+2201_landscape_20190920.png}
+  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
+  {figures/J1205+3422_landscape_20191024.png}
+  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
+  {figures/J1638+2827_landscape_20191024.png}
+  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
+  {figures/J2228+2201_landscape_20191024.png}
   \vspace{-12pt}
@@
 of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
-Myers2015}. These SDSS, BOSS and eBOSS data are supplemented by
+Myers2015}. The SDSS, BOSS and eBOSS data are supplemented by
 spectra from the Low Resolution Imaging Spectrometer (LRIS) on the 10m
@@
 When using the \citet{Shen2011} catalogue, we report line luminosity,
-FWHM, rest-frame equivalent width, and their errors for the {\it
-whole} \mgii profile (this catalogue also quotes values for just the
-broad \mgii component, but the differences for our objects is
+FWHM, rest-frame equivalent width, and their errors for the whole
+\mgii profile (this catalogue also quotes values for just the broad
+\mgii component, but the differences for our objects is
 negligible). The line luminosities in \citet{Calderone2017} are given
 in units of $10^{42}$ erg s$^{-1}$, while the line luminosities in
-\citet{Shen2011} are in units of $\log(L)$.  We do not report
-the \citet{Shen2011} error on the line luminosity.
+\citet{Shen2011} are in units of $\log(L)$.  We do not report the
+\citet{Shen2011} error on the line luminosity.
 
-Power-law continuum slopes, $\alpha_{\lambda}$ where $f_{\lambda}
-\propto \lambda^{\alpha}$, are also reported in these catalogues and
-from QSFit.  We quote the most appropriate value given the emission
-line wavelength.
+Power-law continuum slopes, $\alpha$, where $f_{\lambda} \propto
+\lambda^{\alpha}$, are also reported in these catalogues and from
+QSFit.  We quote the most appropriate value given the emission line
+wavelength.
 
 \subsection{Multi-wavelength properties}
-We use data from the beginning of the WISE mission \citep[2010
+Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning of the
+Wide-field Infrared Survey Explorer (WISE) mission \citep[2010
 January; ][]{Wright2010} through the fifth-year of NEOWISE-R
@@
 
-For J1205+3422, over the course of 5040 days observed, 1640 days in
-the rest-frame.  For J1638+2827, over the course of 1279 days
-observed, 400 days in the rest-frame, the broad \civ\ and \ciii BEL
-start to fade.  For J2228+2201, over the course of 771 days observed,
-240 days in the rest-frame, broad \civ\ and \ciii BELs both emerge and
-the standard UV/blue continuum slope increases in flux.  the UV/blue
-continuum diminishes and the shape of \lya changes.
+For J1205+3422, our spectral observations cover 5195 days observed, 1691 days
+in the rest-frame. For J1205+3422 is identified in SDSS as a bright
+$g\approx18.0$, blue-sloped quasar with broad \siiv, \civ, \ciii and
+\mgii observed in the initial spectrum (MJD 53498; 2005-May-08). \ciii
+and \civ\ are seen to have large blueshifts of $\approx$2600$\pm$150
+and $\approx$1150$\pm$100 km s$^{-1}$, respectively.  By the time the
+2019 spectra were taken (MJD 58538, 2019-Feb-24 and MJD 58693
+2019-Jul-29), however, the light curve has dropped by $\sim$1.5
+magnitudes and the spectra are significantly less steep.  While \lya
+and \nv are detectable in both the MJD 58538 and MJD 58693 DBSP
+spectra, \civ\ has all but disappeared in the MJD 58693 spectrum.  The
+broad \ciii emission has disappeared between the 2005 and 2019
+spectra. {\it The changes in \civ\ and \ciii going from broad emission to
+barely detectable have on the timescales of $\approx$50 days in the rest-frame.}
+
+For J1638+2827, our spectral observations cover 4030 days observed, 1265 days
+in the rest-frame. Here, in the initial epoch spectrum, \civ\ is broad
+and bright, as is \ciii. However, just over 400 days in the rest-frame
+later, the broad \civ\ and \ciii BEL have to faded, the continuum
+slope around 1400\AA\ has changed from $\approx$-1.48 to
+$\approx$-2.25, but the \lya/\nv emission complex is very similar in
+shape and line flux intensity. Around 870 days in the rest-frame after
+the second spectral epoch, \lya, \nv, \civ, \ciii and \mgii are all
+apparent and broad, with \mgii being seen for the first time at high
+signal-to-noise. The light curve is consistent with this spectral
+brightening, increasing from around $\sim$19.5-20.5th magnitude to
+$\sim$18.5 in the optical band. An absorption feature between  \lya and \nv
+is seen in all three spectral epochs.
+
+For J2228+2201, our spectral observations cover 2504 days observed,
+778 days in the rest-frame. Over the course of 240 days in the rest-frame, \civ\ and \ciii both {\it emerge} as BELs and
+the standard UV/blue continuum slope increases in flux.
+Then, over the course of 538 days in the rest-frame, the broadline emission, while still
+very present, reduces in line flux the UV/blue continuum diminishes,
+though is still more luminous than the initial BOSS spectrum.
 
@@
                                  \cdashline{2-9}
-                                              & 58538     & \lya      & 1393$\pm$11   & $>$15000            &  $-796\pm57$           &  ---                         &  ---                        &   QSFit  \\
-    \rowfont{\color{blue}}        & 58538     & \civ      & 1037$\pm$5    & $>$15000            &  983$\pm$40             &  ---                         &  ---                         &   QSFit    \\
-                                              & 58538      & \ciii     &   677$\pm$4    & $>$15000            & $>$3000                     &  ---                         &  ---                         &  QSFit   \\
-    \rowfont{\color{teal}}         & 58538     & \mgii    &  755$\pm$4    & $>$15000            & 350$\pm$39               &  ---                         &  ---                         &   QSFit  \\
+                                            & 58538     & \lya      & 1393$\pm$11   & $>$15000            &  $-796\pm57$          &  ---                        &  ---                       &   QSFit (NPR) \\
+                                            & 58538     & \lya      & 952$\pm$1.1    & 12242$\pm$15    &  $-1679\pm6$          &  165$\pm$0.2        &  ---                       &   QSFit (MJG) \\
+   \rowfont{\color{blue}}       & 58538     & \civ      & 1037$\pm$5    & $>$15000             &  983$\pm$40            &  ---                        &  ---                       &   QSFit (NPR)   \\
+    \rowfont{\color{blue}}      & 58538     & \civ      &       0$\pm$-    & 14995$\pm$0       & $>$3000$\pm$         &  ---                       &  ---                       &   QSFit (MJG)    \\  
+                                            & 58538      & \ciii     &  677$\pm$4     & $>$15000             & $>$3000                    &  5770$\pm$34       &  ---                       &  QSFit  (NPR) \\
+                                            & 58538      & \ciii     &  167$\pm$0.9  & $>$15000            &  2734$\pm$46            &     45$\pm$0.2       &  ---                       &  QSFit (MJG)  \\
+    \rowfont{\color{teal}}      & 58538     & \mgii    &  755$\pm$4     & $>$15000            & 350$\pm$39               &  7571$\pm$37       &  ---                       &   QSFit (NPR) \\
+    \rowfont{\color{teal}}      & 58538     & \mgii    &  216$\pm$1.4  & 13940$\pm$94    & $-465.2\pm38$         &  88$\pm$0.6	    &  ---                       &   QSFit (MJG) \\
                                           \cdashline{2-9}
-                                              & 58693      & \lya     &  290$\pm$3        & 8803$\pm$52     &  $-1096\pm35$        &  ---                        & $<$-3                      &   QSFit  \\
-    \rowfont{\color{blue}}        & 58693     & \civ      &   68$\pm$0.9     & 3743$\pm$26     &   591$\pm$17           &   ---                       & $<$-3                       &  QSFit   \\  
-                                              & 58693      & \ciii     &   19$\pm$0.4     & 5625$\pm$         &   $>$3000                  &    ---                      & $<$-3                      &  QSFit    \\
-    \rowfont{\color{teal}}         & 58693     & \mgii    &   19$\pm$0.4    & 1530$\pm$22     &  $>$3000                   &    ---                        &$<$-3                      &  QSFit   \\  
+                                           & 58693     & \lya     &  290$\pm$3       & 8803$\pm$52     &  $-1096\pm35$        &  ---                           & $<$-3                   &   QSFit  (NPR)\\
+                                           & 58693     & \lya     &  271$\pm$0.9    & 9637$\pm$52     &  $-447\pm13$          &  85.1$\pm$0.3          & ---                        &   QSFit  (MJG) \\ 
+    \rowfont{\color{blue}}    & 58693     & \civ      &   68$\pm$0.9    & 3743$\pm$26     &   591$\pm$17           &   ---                           & $<$-3                   &  QSFit   (NPR)\\  
+    \rowfont{\color{blue}}    & 58693     & \civ      &   52$\pm$0.9    & 5046$\pm$26     &   1053$\pm$17         &   24.0$\pm$0.2          & ---                        &  QSFit  (MJG)  \\  
+                                           & 58693     & \ciii     &   19$\pm$0.4    & 5625$\pm$          &   $>$3000                 &  988$\pm$20             & $<$-3                   &  QSFit   (NPR) \\
+                                           & 58693     & \ciii     &   59$\pm$0.9    & 10751$\pm$        &  1097$\pm$77         &   36$\pm$0.6             & ---                        &  QSFit   (MJG)  \\
+   \rowfont{\color{teal}}      & 58693     & \mgii    &  19$\pm$0.4    & 1530$\pm$22      &  $>$3000                  &    499$\pm$9             &$<$-3                    &  QSFit (NPR)  \\
+   \rowfont{\color{teal}}      & 58693     & \mgii    &  69$\pm$1.5    & 14983$\pm$346   &  $-190\pm134$       &    72$\pm$1.6           & ---                        &  QSFit  (MJG)  \\  
 \hline
@@
                                                \cdashline{2-9}
-      \rowfont{\color{blue}}        & 58583      & \civ      &  659$\pm$5   & $>$15000                &  $-493\pm56$          &   333$\pm$3            & $-0.43\pm0.01$     &   QSFit   \\  
-                                                & 58583      & \ciii      &  239$\pm$4   &  $>$15000               &  1514$\pm$127        &  124$\pm$2             & $-0.43\pm0.01$     &   QSFit   \\
-    \rowfont{\color{teal}}           & 58583      & \mgii   &  129$\pm$3    &  10957$\pm$307    &  138$\pm$128          &   78$\pm$2              &  $-0.43\pm0.01$    &   QSFit   \\  
+                                               & 58583       & \lya    &  1086$\pm$14  & $>$15000     	&   $-1047\pm88$        &  500$\pm$6   	  & $-0.443\pm0.01$   & QSFit  (NPR)\\ 
+                                               & 58583       & \lya    &  785$\pm$1      & 4956$\pm$4    	&   $-641\pm2$            &   90$\pm$0.1   	  &  ---                          & QSFit  (MJG) \\
+   \rowfont{\color{blue}}         & 58583      & \civ      &  659$\pm$5     & $>$15000                &  $-493\pm56$          &   333$\pm$3           & $-0.43\pm0.01$     &   QSFit (NPR)  \\
+   \rowfont{\color{blue}}         & 58583      & \civ      &  311$\pm$1     & 5739$\pm$14	 &  $-167\pm6$             &   58$\pm$0.1          & ---                          &   QSFit (MJG)  \\  
+                                               & 58583      & \ciii      &  239$\pm$4    &  $>$15000               &  1514$\pm$127        &  124$\pm$2            & $-0.43\pm0.01$     &   QSFit  (NPR) \\
+                                               & 58583      & \ciii      &  52$\pm$0.8   &  3917.4	68.837      &  1514$\pm$127        &  124$\pm$2             & ---                          &   QSFit   (MJG) \\
+   \rowfont{\color{teal}}           & 58583      & \mgii   &  129$\pm$3    &  10957$\pm$307    &  138$\pm$128          &   78$\pm$2              & $-0.43\pm0.01$     &   QSFit  (NPR) \\
+   \rowfont{\color{teal}}           & 58583      & \mgii   &  157$\pm$2    &  10565$\pm$129    &  $-450\pm52$          &   92$\pm$1              & ---                          &   QSFit    (MJG) \\  
 \hline
@@
            & \textcolor{blue}{56960} & \textcolor{blue}{\civ}  & \textcolor{blue}{229$\pm$4}      &  \textcolor{blue}{8911$\pm$169}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{46.8$\pm$0.9}    & ---    & \textcolor{blue}{QSFit}     \\
-                                               & 56960    & \ciii      & 185$\pm$5         &        -                       &  2701$\pm$225     &   47.75$\pm$1.29      &  &   QSFit    \\  
-   \rowfont{\color{teal}}           & 56960    & \mgii   &   99$\pm$4        &  7312.6$\pm$340     &   188$\pm$137      &   50.75$\pm$2.21     &   &   QSFit   \\
+                                               & 56960    & \ciii      & 185$\pm$5        &        -                      &  2701$\pm$225      &   47.75$\pm$1.29     & ---                      &   QSFit    \\
+   \rowfont{\color{teal}}           & 56960    & \mgii   &   99$\pm$4        &  7312.6$\pm$340   &   188$\pm$137      &   50.75$\pm$2.21     & ---                      &   QSFit   \\
                                                \cdashline{2-9}
-%   
-     \rowfont{\color{blue}}        & 58693    & \civ     &  327$\pm$1          &  $>$15000              &   $-453\pm34$     &   ---                           & ---  &   QSFit   \\  
-                                               & 58693    & \ciii      & 115.08$\pm$1.2  &  $>$15000              &  2422$\pm$67       &   ---                          & ---  &   QSFit   \\  
-     \rowfont{\color{teal}}         & 58693    & \mgii   & 46.361$\pm$1.3   &  $>$15000             &  $>$1000                &   ---                          & ---  &   QSFit   \\  
+                                               & 58693     & \lya      &  228$\pm$3       & 4279$\pm$32       &   $-1000\pm29$     &  91976$\pm$1311  &  ---                       & QSFit  (NPR)\\ 
+                                               & 58693     & \lya      &  447$\pm$5       & 8133$\pm$93       &   613$\pm$130       &        56$\pm$0.6     &  ---                    	 &    QSFit  (MJG) \\
+     \rowfont{\color{blue}}        & 58693     & \civ      &  327$\pm$1      &  $>$15000             &   $-453\pm34$       &  20298$\pm$106    & ---                        & QSFit   (NPR)\\  
+     \rowfont{\color{blue}}        & 58693     & \civ      &  41$\pm$1        &  4914$\pm>$65    &   160$\pm$27         &   25$\pm$0.3          & ---                         & QSFit (MJG)  \\  
+                                               & 58693     & \ciii      & 269$\pm$1.5    &  $>$15000             &  2302$\pm$42.6     &   3776$\pm$21      & ---                          &  QSFit  (NPR) \\
+                                               & 58693     & \ciii      & 107$\pm$1.2    &  $>$15000             &  2422$\pm$67        &   ---                       & ---                          &  QSFit (MJG)   \\
+     \rowfont{\color{teal}}        & 58693     & \mgii    & 177$\pm$1.1    &  $>$15000             &  1000$\pm$2617    &   16$\pm$36         & ---                           &   QSFit (NPR) \\
+     \rowfont{\color{teal}}        & 58693     & \mgii    &  89$\pm$1.4     &  $>$15000             &  $>$1000                &   1230$\pm$1.9    & ---                            &   QSFit  (MJG) \\  
 \hline
@@
 \begin{itemize}
-  \item {SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
+  \item SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
 in their observed optical light curves, and subsequent spectroscopy
@@
 line collapse and emergence being displayed in rest-frame timescales
-of $\sim$240-1640 days.}
+of $\sim$240-1640 days.
 \item Where observed, the profile of the Ly$\alpha$/\nv emission complex

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191029v1.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191025.tex
@@
 (recombination) Balmer emission line properties with particular
-attention paid to the H$\beta$ emission line, usually observed from
-optical spectroscopy.  As such, current CLQ studies have been at
+attention paid to the H$\beta$ emission line, observed from optical
+spectroscopy. Recent work \citep{Guo2019, Homan2019} report on discoveries
+of \mgii Changing-look AGN. However, current CLQ studies have been at
 redshifts $z<1$.
@@
 emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
-transition with energies 64,484 cm$^{-1}$ and 64,591 cm$^{-1}$
-\citep[e.g.][]{Moore1993}.  The ground state of carbon is 1$s^2$
-2$s^2$ 2$p^2$.  Using the
+transition, split by total angular momentum $J= 3/2$ and $1/2$,
+resulting in energies 64,591 cm$^{-1}$ and 64,484 cm$^{-1}$,
+respectively \citep[e.g.][]{Moore1993}. The transition probabilities
+of the the 1548 and 1550\AA\ lines are $A_{ki}= 2.65\times10^{8}$ and
+2.64$\times10^{8}$.
+
+The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. Using the
 \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
@@
 \gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
-X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).
+X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).  \ciii is the
+1$s2$2$s$2$p$ $^{3}$P$^{\circ}$ to 1$s^{2}$2$s^{2}$ $^{1}$S transition
+(with $J=1\rightarrow0$) resulting in an energy of 52,390.75 cm$^{-1}$ and
+a transition probability of $A_{ki} = 1.14\times^{2}$.
 
@@
 
+%%   P a p e r    O v e r v i e w
 The purpose of this paper is, for the first time, to access and 
@@
 %% \subsection{Selection/Identification}
-%{\bf MJG to write a few notes on how the CIV CLQs were identified} 
 Our high-$z$ CLQs were identified as follows. 
@@
 \section{Results}
+\subsection{Overall Spectral Evolution}
 Figure~\ref{fig:civ_clqs} presents the optical and infrared light
@@
 \end{figure}
+\subsection{Overall Spectral Evolution}
+
 From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
@@
 
-In the context of CLQs at lower-$z$...  
-(Balmer CLQs vs. \civ\ CLQs...) 
-Sociis natoque penatibus et
-magnis dis parturient montes, nascetur ridiculus mus. Duis tempus,
-lectus nec ultricies mollis, mi orci feugiat nulla, a bibendum velit
-orci nec lacus. Duis a odio in nisi egestas dictum. Nullam vel quam
-mauris, eget consectetur orci. Morbi ac mi sit amet neque consectetur
-tempus ac eget est. Curabitur malesuada arcu sit amet metus dictum at
-dapibus arcu accumsan. Fusce sollicitudin luctus rutrum.
+The Balmer series in hydrogen is due to the recombination cascade
+between different principal quantum numbers $n$, and
+the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
+%(and assuming an equilibrium distribution between the angular momentum levels $l$ corresponding to a given $n$).
+%%
+Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
+H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
+Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$. 
+%%
+\civ\ is one of the strongest collisionally excited lines in quasar
+spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
+at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
+canonical BELR parameters deduced over from early analysis of the
+\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
+ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
+speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
+H$^{+}$).
 
@@
     }
- \label{tab: QSFIT_line_values}
+ \label{tab:LineMeasurement}
 \end{table*}

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191029v2.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191029v1.tex
@@
 \section{Data}
-%% \subsection{Selection/Identification}
-Our high-$z$ CLQs were identified as follows. 
-We selected all 64,774 SDSS DR15 sources with $z > 0.35$ classified as
-'QSO', having at least two spectra separated by at least 100 days, and
-with a corresponding CRTS light curve. We fitted a damped random walk
-to the CRTS data via Gaussian process regression and the photometric
-magnitudes at the epochs of the SDSS spectra for a given source are
-predicted. Those where $|\Delta V| > 0.3$ are then selected for visual
-inspection.
-
-SDSS J120544.7+342252.4  (hereafter J1205+3422), 
-SDSS J163852.93+282707.7 (hereafter J1638+2827) and
-SDSS J222818.76+220102.9 (hereafter J2228+2201). 
-Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
-pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
-id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
-dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
-euismod. Cras vel auctor neque. Nam quis diam risus.
+Our high-$z$ CLQs were identified as follows.  We selected all 64,774
+SDSS DR15 sources with $z > 0.35$ classified as `QSO', having at least
+two spectra separated by at least 100 days, and with a corresponding
+CRTS light curve. We fitted a damped random walk to the CRTS data via
+Gaussian process regression and the photometric magnitudes at the
+epochs of the SDSS spectra for a given source are predicted. Those
+where $|\Delta V| > 0.3$ are then selected for visual
+inspection. Three quasars SDSS J120544.7+342252.4 (hereafter
+J1205+3422), SDSS J163852.93+282707.7 (hereafter J1638+2827) and SDSS
+J222818.76+220102.9 (hereafter J2228+2201), satisfied these selection
+criteria and showed interesting or dramatic emission line behaviour.
 
@@
 \subsection{Overall Spectral Evolution}
-
+Emission line measurements from the catalogues of  \citet{Shen2011}.
+\citet{Hamann2017}, \citet{Kozłowski2017} or the QSFit routine of \citet{Calderone2017}
+are presented in Table~\ref{tab:LineMeasurement}.
+%%
 From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
@@
   % \begin{tabular}{lll  cccc r }
-  \begin{tabu}{lll  cccc c r }
+  \begin{tabu}{l ll  lccc c r }
     \hline 
@@
     \rowfont{\color{blue}}       & 53498    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    & 30.1$\pm$1.21    & $-1.47\pm0.08$     &     Shen2011 \\
-    \rowfont{\color{blue}}       & 53498    & \civ      &   ---                  &   5119$^{(a)}$             &    ---                     &  ---                        &  ---                        &     DR12 SAS   \\
+    \rowfont{\color{blue}}       & 53498    & \civ      &   403                  &   5119$^{(a)}$             &    ---                     &  ---                        &  ---                        &     DR12 SAS   \\
                                              & 53498     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    & 25.10$\pm$0.59    & $-1.65\pm0.01$     &     QSFit   \\
-                                             & 53498    & \ciii       &   ---                 &   5119$^{(a)}$             &  ---                       &   ---                       &  ---                         &       DR12 SAS  \\
+                                             & 53498    & \ciii       &   144                 &   5119$^{(a)}$             &  ---                       &   ---                       &  ---                         &       DR12 SAS  \\
   \rowfont{\color{teal}}         & 53498     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     & 26.66$\pm$1.65    &   $-1.65\pm0.01$    &  $^{(d)}$QSFit  \\
@@
  \multirow{2}{*}{{\bf J1205+3422}}  
-                &     \textcolor{teal}{53948}     & \textcolor{teal}{\mgii}   & \textcolor{teal}{---} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\
+                &     \textcolor{teal}{53948}     & \textcolor{teal}{\mgii}   & \textcolor{teal}{130} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\
                                  \cdashline{2-9}
@@
 \hline
-                                                & 54553     & \lya      &  ---                 &  3207                     &    ---                        &   ---                         & ---                         &   DR12 SAS  \\
+                                                & 54553     & \lya      & 188                 &  3207                     &    ---                        &   ---                         & ---                    &   DR12 SAS  \\
    \rowfont{\color{blue}}          & 54553     & \civ      & 257$\pm$13   &  4550$\pm$371     &   55$\pm$450         &   31.8$\pm$1.5     &                                &  $^{(d)}$QSFit  \\
    \rowfont{\color{blue}}          & 54553     & \civ      & 281                  &    4181$\pm$736   &    680$\pm$133       & 100.5$\pm$12  & $-0.14\pm0.68$    &  Shen2011   \\
-   \rowfont{\color{blue}}          & 54553     & \civ      & ---                   &    4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\
+   \rowfont{\color{blue}}          & 54553     & \civ      & 170                  &   4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\
                                                 & 54553     & \ciii     &  130$\pm$10   &  3852$\pm$402    &  $-236\pm565$       &  36.7$\pm$2.8          &  $-1.47\pm0.20$    &  $^{(d)}$QSFit  \\
-                                                & 54553     & \ciii     &  ---                  &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\
+                                                & 54553     & \ciii     &  61                    &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\
     \rowfont{\color{teal}}          & 54553      & \mgii  &  139                  &  4757$\pm$2224   &  $-944\pm568$        &   119$\pm$40          &  $-1.49\pm0.54$    &  Shen2011   \\
-    \rowfont{\color{teal}}          & 54553      & \mgii  &  ---                 &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\
+    \rowfont{\color{teal}}          & 54553      & \mgii  &  69                    &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\
                                                 \cdashline{2-9}
                                                 & 55832     & \lya     & 288$\pm$11    &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99   &                               &   QSFit  \\
-                                                & 55832     & \lya     &   ---                 &  4165.6$^{(a)}$         &    ---                       &   ---                         & ---                         &   DR12 SAS  \\
+                                                & 55832     & \lya     & 234                  &  4165.6$^{(a)}$         &    ---                       &   ---                         & ---                         &   DR12 SAS  \\
 \multirow{2}{*}{\bf {J1638+2827}}
@@
     \rowfont{\color{blue}}           &  55832   &  \civ     &  ---               &    5210$\pm$226     &    ---                       &   42.8$\pm$2.0         & $-3.35$                 &     Ham17  \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\
+    \rowfont{\color{blue}}           &  55832   &  \civ     &  46                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\
                                                  & 55832     & \ciii     & 15$\pm$5     &  11421$\pm$3654   &   $>$3000                &   14.8$\pm$4.5         &  $-2.25\pm0.05$   &        QSFit \\
-                                                 &  55832    &  \ciii    &  ---                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                      &   DR12 SAS \\
-    \rowfont{\color{teal}}           &  55832     & \mgii   & ---                 &     5385$^{(a)}$         &  ---                           &   ---                          &  ---  &   DR12 SAS\\  
+                                                 &  55832    &  \ciii    &  11                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                       &   DR12 SAS \\
+    \rowfont{\color{teal}}           &  55832     & \mgii   &  13                &     5385$^{(a)}$         &  ---                           &   ---                          &  ---                       &   DR12 SAS\\
                                                \cdashline{2-9}
@@
     \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &   2994$\pm$620       &     ---                       &   42.2$\pm$5.6      & -1.59                      &    Ham17  \\
-    \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                        &   DR12 SAS  \\
+    \rowfont{\color{blue}}         &  56189     & \civ    &   19                  &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                        &   DR12 SAS  \\
                                                &  56189      &  \ciii   &  34$\pm$6       &  13748$\pm$2869    &   1851$\pm$1140    &  63$\pm$12          &  $-0.46\pm0.21$    &   QSFit  \\
-                                               &  56189      & \ciii    &  ---                  &     5218$^{(a)}$          &  ---                         &     ---                     & ---                         &   DR12 SAS \\
+                                               &  56189      & \ciii    &  7                     &     5218$^{(a)}$          &  ---                         &     ---                     & ---                         &   DR12 SAS \\
     \rowfont{\color{teal}}          & 56189      & \mgii  &  25$\pm$6       &   7253$\pm$1712     &   $-931\pm708$      &  51$\pm$10.95      &  $-0.46\pm0.21$   &   QSFit   \\
-    \rowfont{\color{teal}}         &  56189      &  \mgii &  ---                  &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                       &   DR12 SAS \\
+    \rowfont{\color{teal}}         &  56189      &  \mgii &  13                   &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                       &   DR12 SAS \\
                                                   \cdashline{2-9}
@@
 %%Out[9]: -0.6023705451175618
-
 \begin{table*}
@@
 \citet{VestergaardPeterson2006}.  Eddington ratio computed using the
-virial BH mass.
-      }
+virial BH mass.}
+\label{tab:Eddington_ratios} 
 \end{table*}
@@
   \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {figures/CIV_CLQs_hexplot_20190925.png}
+  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
    \vspace{-12pt}
@@
 \subsection{Eddington ratios and State Changes} 
-The broad UV and optical lines in quasars are most sensitive to the extreme ultraviolet (EUV)
-part of the spectral energy distribution (SED), with \civ\ (and indeed \heii and \nv) being at
-the higher energy end of the EUV distribution. 
-\citet{NodaDone2018} note that The soft X-ray excess produces most of
-the ionizing photons, so its dramatic drop leads to the disappearance
-of the broad-line region, driving the ``changing-look'' phenomena.
-major difference is that radiation pressure should be much more
-important in AGNs, so that the sound speed is much faster than
-expected from the gas temperature.
+The broad UV and optical lines in quasars are most sensitive to the
+extreme ultraviolet (EUV) part of the spectral energy distribution
+(SED), with \civ\ (and indeed \heii and \nv) being at the higher
+energy end of the EUV distribution.
+
+The soft X-ray excess – the excess of X-rays below 2 keV with respect
+to the extrapo- lation of the hard X-ray spectral continuum model – is
+a very common feature among type 1 active galactic nuclei (AGN). 
+\citet{NodaDone2018} note that
+The soft X-ray excess produces most of the ionizing photons, so its
+dramatic drop leads to the disappearance of the broad-line region,
+driving the ``changing-look'' phenomena.  major difference is that
+radiation pressure should be much more important in AGNs, so that the
+sound speed is much faster than expected from the gas temperature.
 %%
@@
 transition at $L / L_{\rm Edd} \sim$a few per cent.
-
-We investigate this...  \citet{JiangYF2014, JiangYF2016, JiangYF2019}.
+%%
+\citet{JiangYF2014, JiangYF2016, JiangYF2019}.
 \citet{JiangYF2019arXiv} use global three dimensional radiation
@@
 Eddington value.
+
+We investigate this reporting the Eddington ratios of the three
+quasars in Table~\ref{tab:Eddington_ratios}.
 

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191030.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191029v2.tex
@@
 {The RH John~S.~Bercow, MP, {\it et al.} 
-%Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
-%K. E. Saavik Ford$^{2,3,4}$,  Matthew Graham$^{5}$,  Barry McKernan$^{2,3,4}$,  
+  % Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
+  %Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,    Barry McKernan$^{3,4,5}$,  
 %\newauthor Daniel Stern$^{6}$, 
@@
 %$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
-%$^{2}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
-%$^{3}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
-%$^{4}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
-%$^{5}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
+%$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
+%$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
+%$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
+%$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
 %$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
@@
 Emission line measurements from the catalogues of  \citet{Shen2011}.
-\citet{Hamann2017}, \citet{Kozłowski2017} or the QSFit routine of \citet{Calderone2017}
+\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of \citet{Calderone2017}
 are presented in Table~\ref{tab:LineMeasurement}.
@@
 
+The X-ray Baldwin Effect \citet[e.g., ][]{Iwasawa_Taniguchi1993}
+\citet{Bachev2004} find a 10-fold decrease in EW C IV λ1549 with
+Eddington ratio (decreasing from ~1 to ~0.01), while N V λ1240 shows
+no change. These trends suggest a luminosity-independent ``Baldwin
+effect'' in which the physical driver may be the Eddington ratio.
+\citet{Ge2016} Broad emission lines is a prominent property of type I quasi-stellar objects (QSOs).
+
 \subsection{Eddington ratios and State Changes} 

### 2019-11-07 tex/other_tex/201911/CIV_CLQs_20191105v1.tex
CIV tex/ tidy up

--- 2019-11-04 tex/CIV_CLQs.tex
@@
 
-\author[Bercow]
+\author[Ross {\it et al.}]
 {%The RH John~S.~Bercow, MP, {\it et al.} 
@@
 the subsequent mismatch in the expected ``viscous'' timescale, which
-for a $\approx$10$^{7}$ M$_{\odot}$ central supermassive black hole
+for a 10$^{7}$ M$_{\odot}$ central supermassive black hole
 (SMBH) is $\sim$hundreds of years, was noted over 30 years ago
@@
 
-\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$ SDSS
-quasars, concentrating on the properties of the \civ\ emission
-line. We consider two well-known effects involving the \civ\ emission
-line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
-the BEff) and the blueshifting of the peak of \civ\ emission with
-respect to the systemic redshift. These authors conclude that these
-two \civ\ parameters (EQW and blueshift) are capturing an important
-trade-off between ``disk'' and ``wind'' components in the disk-wind
-model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
-Proga2000}, with one dominating over the other depending on the shape
-of the SED \citep[][strong \civ\ EQW indicates a more ionizing SED and
-large \civ\ blueshift indicating a less ionizing SED ]{Leighly2004b}.
+\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$
+SDSS quasars, concentrating on the properties of the \civ\ emission
+line. These authors consider two well-known effects involving the
+\civ\ emission line: {\it (i)} the anti-correlation between the \civ\
+equivalent widths (EWs) and luminosity (i.e., the Baldwin Effect;
+BEff) and {\it (ii)} the blueshifting of the peak of \civ\ emission
+with respect to the systemic redshift. \citet{Richards2011} conclude
+that these two \civ\ parameters (EQW and blueshift) are capturing an
+important trade-off between ``disk'' and ``wind'' components in the
+disk-wind model of accretion disks \citep[e.g.,][]{Murray1995,
+Elvis2000, Proga2000}, with one dominating over the other depending on
+the shape of the SED \citep[][strong \civ\ EQW indicates a more
+ionizing SED and large \civ\ blueshift indicating a less ionizing SED
+]{Leighly2004b}.
 
@@
 \cite[SDSS-RM; ][]{Shen2015} has a monitored $\sim$350 quasars with
-\civ. Noting the biases associated with \civ Emission Line Properties
-\citep[e.g. increasing systematic offsets with decreasing
-signal-to-noise][]{Denney2016}, \citet{Grier2019} report report
+\civ. Noting the biases associated with \civ\ emission line properties
+\citep[such as increasing systematic offsets with decreasing
+signal-to-noise; ][]{Denney2016}, \citet{Grier2019} report report
 significant time delays between the continuum and the CIV 1549
-emission line in 52 quasars, and investigate the \civ
+emission line in 52 quasars, and investigate the \civ\ 
 radius-luminosity relationship.
 
-\civ\ is also known to exhibit significant displacements to the
-blue and these `blueshifts' almost certainly signal the presence of
-strong outflows. As a consequence, single-epoch virial black hole (BH)
-mass estimates derived from \civ\ velocity widths are known to be
+\civ\ is also known to exhibit significant displacements to the blue
+and these `blueshifts' almost certainly signal the presence of strong
+outflows. As a consequence, single-epoch virial black hole (BH) mass
+estimates derived from \civ\ velocity widths are known to be
 systematically biased compared to masses from the hydrogen Balmer
 lines. \citet{Coatman2017} use a large sample of 230 high-luminosity
-($L$Bol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with
-both \civ\ and Balmer line spectra, we have quantified the bias in \civ
-BH masses as a function of the \civ\ blueshift. \civ\ BH masses are
-shown to be a factor of 5 larger than the corresponding Balmer-line
-masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated
-by almost an order of magnitude at the most extreme blueshifts,
-$\gtrsim$5000 km s$^{-1}$.
+($L_{\rm Bol} = 10^{45.5 - 48}$ erg s$^{-1}$), redshift $1.5 < z <
+4.0$ quasars with both \civ\ and Balmer line spectra, we have
+quantified the bias in \civ BH masses as a function of the \civ\
+blueshift. \civ\ BH masses are shown to be a factor of 5 larger than
+the corresponding Balmer-line masses at C IV blueshifts of 3000 km
+s$^{-1}1$ and are overestimated by almost an order of magnitude at the
+most extreme blueshifts, $\gtrsim$5000 km s$^{-1}$.
 
@@
 properties. We confirm that high-blueshift sources tend to have low
-\civ\ equivalent widths (EWs), and that the low-EW sources span a range
+\civ\ EWs, and that the low-EW sources span a range
 of blueshift. Other high-ionization lines, such as He II, also show
@@
 and setting $E(B-V)=0.00$.
+%%
+The host galaxy and blended iron emission at rest-frame optical wavelengths components
+are automatically disabled when they can not be constrained by the available data,
+such as the case for all our objects (we do not have infrared spectral data).
+%%
 
@@
 Red Quasar'' population \citet{Ross2015, Zakamska2016, Perrotta2019,
-Zakamska2019}.  As such, these measurements can be taken as the `gold
-standard' for \civ line measurement, though this is only for two out of
-our nine spectra.
+  Zakamska2019}.  As such, we prefer the \citet{Hamann2017} emission line
+values where available, though this is only for two out of our nine spectra.
 
@@
 Emission line measurements from the catalogues of \citet{Shen2011}.
-\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of \citet{Calderone2017}
-are presented in Table~\ref{tab:LineMeasurement}.
-%%
+\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of
+\citet{Calderone2017} are presented in Table~\ref{tab:
+LineMeasurements}.
+
 From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
@@
 
-The Balmer series in hydrogen is due to the recombination cascade
-between different principal quantum numbers $n$, and
-the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
-%(and assuming an equilibrium distribution between the angular momentum levels $l$ corresponding to a given $n$).
-%%
-Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
-H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
-Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$. 
-%%
-\civ\ is one of the strongest collisionally excited lines in quasar
-spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
-at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
-canonical BELR parameters deduced over from early analysis of the
-\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
-ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
-speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
-H$^{+}$).
+For the BOSS spectrum of J2228+2201 on MJD 56189, some of the data are
+``masked'' (i.e. they have {\tt and\_mask} != 0) in the FITS file at
+wavelengths $\lesssim$1600\AA\ (rest-frame).  This typically means
+there is some potential problem in using those data. However, visual
+inspection shows strong broad \civ\ emission, so we disable the check on the mask,
+and report the line fits in Table~\ref{tab:LineMeasurement}
 
@@
 \hline
+    \rowfont{\color{blue}}         &  56189     & \civ    &   32$\pm$3.5   &   7663$\pm$881       &    538$\pm$352       &   50.2$\pm$5.6      & ---                        &    QSFit  \\
     \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &   2994$\pm$620       &     ---                       &   42.2$\pm$5.6      & -1.59                      &    Ham17  \\
@@
     }
- \label{tab:LineMeasurement}
+ \label{tab:LineMeasurements}
 \end{table*}
@@
 %% Using    C IV
-
+%%
 %% In [6]: log10((10**47.216)/((1.26e38)*(10**9.49)))                                                                                                                                             
@@
     \hline
-\multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$} & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref. \\
+    \multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$} & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref.
+\\
                               &                                   &                                      &                                                 & \mgii                  & \civ                    &  \mgii           &  \civ                       &        \\
     \hline
-                                     & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen2011\\
+                              & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen11\\
     J1205+3422      & 58538                         &                                      &                                                 &                             &                             &                    &                               & \\
@@
     \hline 
-                                    & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen2011\\
- J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kol017\\
+                              & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen11\\
+    J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kozl17\\
                               & 58583                          &                                      &                                                &                               &                            &                   &                                      &  \\
     \hline 
-                                   & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kol017\\
+                              & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kozl17\\
     J2228+2201       & 56960                          &                                       &                                                &                              &                               &                 &                                        & \\
@@
     \hline
+                              &                                     &                                       &                                               &                             &                                &                  &                  & \\
+    M87$^{*}$          &  57854	                     & ---                                &   43.187	                               & \multicolumn{2}{c}{9.812$\pm$0.044}    & 	\multicolumn{2}{c}{-4.699}   & EHT \\
+                                  &                                     &                                       &                                               &                             &                                &                  &                  & \\
+     \hline
     \hline
   \end{tabular}
-  \caption{$\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio.
+  \caption{Physical properties of the \civ\ CLQs and M87.
+     $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude $K$-corrected to $z = 2$; Bolometric luminosity computed from the
+        monochromatic luminosity at 1350\AA\ using the spectral fits and
+        bolometric corrections (BC = 3.81) in \citet{Richards2006b}.
+        Virial BH masses using calibrations of \citet{VestergaardPeterson2006}.
+         $\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio computed using the virial BH mass.
         Shen11 is \citet{Shen2011}. 
-        Kol17 is \citet{Kozlowski2017}.
-        Measured line values using the methods and catalogue from
-\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
-$K$-corrected to $z = 2$; Bolometric luminosity computed from the
-monochromatic luminosity at 1350\AA\ using the spectral fits and
-bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
-luminosity, FWHM, rest-frame equivalent width, and their errors for
-the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
-continuum fit for \civ; Virial BH masses using calibrations of
-\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
-virial BH mass.}
+        Kozl17 is \citet{Kozlowski2017}.
+        EHT is \citet{EHT2019_PaperV}.      }
 \label{tab:Eddington_ratios} 
@@
 see Figure~\ref{fig:CIV_Baldwin}
+Our Figure~\ref{fig:CIV_Baldwin} is a reproduction of Figure~15 from \citet{Calderone2017}.
+
+The plotted values are \verb|CONT1450\_\_LUM| and \verb|BR\_CIV\_1549\_\_\EW|.
+\verb|CONT1\_\_LUM| is the $\nu L_{\nu}$ luminosity at wavelength
+%{\tt CONT1\_\_WAVE}, and the latter is always within the observed wavelength range, hence it is always present.
+We use the v1.2.4 of the QSFIT catalogue, applying the cuts: {\tt BR\_CIV\_1549\_\_LUM} $>0$ \&\& {\tt BR\_CIV\_1549\_\_EW} $>0$.
+This selects 20,374 quasars.
+%On the other hand, CONT1450__LUM is estimated at 1450AA (rest frame), hence it is available only if 1450AA is within the available
+%wavelength range.  For SDSS data, CONT1450__LUM is available only if $z> 1.83$.
+
 The slope $\beta$ is $-0.1997$. 
@@
 \section{Discussion}
+The variable properties of high-$z$
+quasars, however, has been less well studied. Reasons for this include
+more massive systems will tend to have longer timescales with e.g.
+$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.
+
+The Balmer series in hydrogen is due to the recombination cascade
+between different principal quantum numbers $n$, and
+the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
+Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
+H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
+Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$.
+
+\civ\ is one of the strongest collisionally excited lines in quasar
+spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
+at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
+canonical BELR parameters deduced over from early analysis of the
+\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
+ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
+speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
+H$^{+}$).
+
 \civ\ probes the photoionization environment produced by the innermost
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
+  {figures/CIV_CLQs_Baldwin_20191104v3.png}
+   \vspace{-12pt}
+   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
+     commonly referred to as The Baldwin Plot. The continuum luminosities are
+     from \citet{Kozlowski2017},
+     the REW measurements are Table~\ref{tab:Baldwin}.}
+  \label{fig:CIV_Baldwin}
+\end{figure}
 \subsection{The Baldwin Effect}
@@
 recently, the intrinsic Baldwin effect, the same anti-correlation but
-in an individual, variable AGN.  The variable properties of high-$z$
-quasars, however, has been less well studied. Reasons for this include
-more massive systems will tend to have longer timescales with e.g.
-$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.
+in an individual, variable AGN.
 
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
+  {figures/MJD_vs_Eddington_20191104_v0pnt9.png}
+  \vspace{-12pt}
+  \caption[]{Eddington Ratios of the three \civ\ CLQs and M87.}
+  \label{fig:Eddington_ratios}
+\end{figure*}
 \subsection{Eddington ratios and State Changes} 
@@
 
-The soft X-ray excess – the excess of X-rays below 2 keV with respect
-to the extrapo- lation of the hard X-ray spectral continuum model – is
+The soft X-ray excess -- the excess of X-rays below 2 keV with respect
+to the extrapolation of the hard X-ray spectral continuum model -- is
 a very common feature among type 1 active galactic nuclei (AGN). 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_20191104v3.png}
-   \vspace{-12pt}
-   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
-     commonly referred to as The Baldwin Plot. The continuum luminosities are
-     from \citet{Kozlowski2017},
-     the REW measurements are Table~\ref{tab:Baldwin}.}
-  \label{fig:CIV_Baldwin}
-\end{figure}
-
-\subsection{Variability around billion solar mass black holes} 
+%\subsection{Variability around billion solar mass black holes} 
 The Event Horizon Telescope (EHT) mapped the central compact radio
-source of the elliptical galaxy M87 at 1.3 mm \citep{EHT2019_PaperI, EHT2019_PaperII, EHT2019_PaperIII, EHT2019_PaperIV, EHT2019_PaperV, EHT2019_PaperVI} .
+source of the elliptical galaxy M87 at 1.3 mm \citep{EHT2019_PaperI,
+EHT2019_PaperII, EHT2019_PaperIII, EHT2019_PaperIV, EHT2019_PaperV,
+EHT2019_PaperVI} .
 
@@
 \end{equation}
-giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c = 32 015 {\rm secs}$ (0.37 days).
-%\begin{equation}
-%t_{\rm lt} = R_{s} / c = 32015 {\rm secs}$
-%\end{equation}
-%and a {\it dynamical timescale}, $t_{\rm dyn}$
-%\begin{equation}
-%$t_{\rm dyn}  =  sqrt{ R_{s}^{3}/G M}
-% \end{equation}
-%also (!!!!!) of $t_{\rm dyn}  =  \sqrt{ R_{s}^{3}/G M}$ = 32015 seconds.
+giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c =$
+32,015 secs (0.37 days).
 
-$\log_{10} (M_{M87^{*}} / M_{\odot} ) = 9.813$. 
-which is only about double that of J1205+3422 and J2228+2201,
-and a factor of $\sim$6 that of J1638+2827.
-However, M87
+$\log_{10} (M_{\rm M87^{*}} / M_{\odot} ) = 9.813$.  which is only
+about double that of J1205+3422 or J2228+2201, and a factor of $\sim$6
+that of J1638+2827.  However, M87 has an Eddington accretion rate of
+$\approx$140 $M_{\odot}$ yr$^{-1}$, and thus an Eddington ratio of
+$\dot{M} / \dot{M}_{\rm Edd} \sim 2 \times 10^{-5}$, i.e. $\eta_{\rm
+Edd} = -4.699$.  \citep[assuming the canonical accretion radiative
+efficiency of 10\%; ][]{DiMatteo2003a, EHT2019_PaperV}.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%     S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5   
+%%     S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5   
+%%     S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5   
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}

### 2019-11-07 tex/other_tex/Ham17_clqs.tex
CIV tex/ tidy up

\begin{table*}
\begin{tabular}{ l rrrr rrrr rrrr rrrr rrrr rr|}
\hline
%  \multicolumn{1}{|c|}{sdss\_name} &
 % \multicolumn{1}{c|}{f1450} &
 % \multicolumn{1}{c|}{$alpha\_civ$} &
 % \multicolumn{1}{c|}{$alpha\_nv$} &
 % \multicolumn{1}{c|}{$alpha\_all$} &
 % \multicolumn{1}{c|}{$alpha\_allc$} &
 % \multicolumn{1}{c|}{rew} &
 % \multicolumn{1}{c|}{rewc} &
 % \multicolumn{1}{c|}{reww} &
 % \multicolumn{1}{c|}{fwhm} &
 % \multicolumn{1}{c|}{fwhme} &
 % \multicolumn{1}{c|}{fwhmc} &
 % \multicolumn{1}{c|}{fwhmw} &
 % \multicolumn{1}{c|}{$\sigma$} &
 % \multicolumn{1}{c|}{peak} &
 % \multicolumn{1}{c|}{peaksnr} &
 % \multicolumn{1}{c|}{rat} &
 % \multicolumn{1}{c|}{asy} &
 % \multicolumn{1}{c|}{kt75} &
 % \multicolumn{1}{c|}{kt80} &
 % \multicolumn{1}{c|}{rew\_di} &
 % \multicolumn{1}{c|}{rewe\_di} &
 % \multicolumn{1}{c|}{fwhm\_di} &
\hline 
  Plate-Fiber-MJD & $f$1450 & $\alpha_{\civ}$ & $\alpha_{\rm all}$      & $\alpha_{\rm allc}$     & rew                       & rewc   &  reww  & fwhm                 & fwhmc  &  fwhmw  & $\sigma$  & asy       & kt75  & kt80   & rew\_di               & fwhm\_di                     \\
\hline 
  5201-178-55832 & 1.4659    & -3.3547              & -4.95$\pm$0.46 & -4.026$\pm$0.452 & 42.76$\pm$1.96  & 26.72  & 16.03  & 5210$\pm$226 & 4651   & 13444    & 3702          &   0.059  & 0.415 & 0.325 & 41.41$\pm$1.6 & 5372  \\
  6118-720-56189 & 0.5101    & -1.5931              & -1.47$\pm$0.04 & -0.657$\pm$0.004 & 42.18$\pm$5.59  &  6.42   & 35.76  & 2994$\pm$620 & 1458   &   7636    & 3002          & -0.150  & 0.183 & 0.138 & 44.15$\pm$4.2 & 3867  \\
\hline
\end{tabular}
  \caption{
Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
\noindent {\tt f1450} = flux in the uncorrected BOSS spectrum at 1450
\AA\ rest (10$^{-17}$ ergs s$^{-1}$ cm$^{-2}$ \AA$^{-1}$) used to
anchor the power law continuum fits beneath \civ\ and \nv , e.g.,
$f_{\lambda} = f_{1450}\, (\lambda /1450{\rm \AA})^{\alpha}$.
\noindent {\tt alpha\_civ} = power law continuum slope
($f_{\lambda}\propto \lambda^{\alpha}$) measured from the BOSS
spectrum on either side of \civ .
\noindent {\tt alpha\_nv} = as above but for \nv .
\noindent {\tt alpha\_all} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) between 1350 \AA\ and 2200 \AA\ in the uncorrected BOSS spectrum (with 1$\sigma$ uncertainty). 
\noindent {\tt alpha\_allc} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) between 1350 \AA\ and 2200 \AA\ in the flux corrected BOSS spectrum, listed only for quasars with $z_{\rm e} \le 3.4$ (with 1$\sigma$ uncertainty). 
\noindent {\tt rew} = \civ\ REW (\AA ) from the line profile fit (with 1$\sigma$ uncertainty). 
\noindent {\tt rewc} = \civ\ REW (\AA ) for the core Gaussian component.
\noindent {\tt reww} = \civ\ REW (\AA ) for the wing Gaussian component.
\noindent {\tt fhwm} = \civ\ FWHM (km/s) from the line profile fit (with 1$\sigma$ uncertainty). 
\noindent {\tt fwhmc} = \civ\ FWHM (km/s) for the core Gaussian only.
\noindent {\tt fwhmw} = \civ\ FWHM (km/s) for the wing Gaussian only.
\noindent {\tt sigma} = \civ\ velocity dispersion (km/s) measured from the profile fit \citep{Peterson2004}.
\noindent {\tt asy} = \civ\ profile asymmetry index \citep{Marziani1996}.
\noindent {\tt kt75} = \civ\ profile kurtosis 75 index \citep{Marziani1996}.
} 
 \label{tab:Ham17_lines}
\end{table*}

### 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190322.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/201909/CIV_notes_20190916.tex
@@
 \section{Introduction}
-Luminous AGN, i.e. quasars, are now seen to significantly vary their energy output on timescales of weeks to months. 
-This observational fact, and the subsequent mismatch in the expected timescale, the ``viscous'' timescale, 
-which for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was noted over 30 years ago \citep[e.g.][]{Alloin1985}. 
-However, with new photometric light-curve and repeat spectroscopic data, the desire for a deeper understanding 
-of AGN accretion disk physics  has been re-established \citep[e.g.][]{Lawrence2018, Antonucci2018}.
+While there have been a slew of studies on carbon IV (\civ) broad absorption line quasars
+\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}. However, dramatic changes in the 
+broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
+Here, we report on two objects SDSS J222818.76+220102.9 (hereafter J2228+2201) and 
+SDSS J163852.93+282707.7 (hereafter J1638+2827).
 
-Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs) have now been 
-assembled \citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
-terms as a cover for the underlying physics. For sake of argument, ``Changing Look'' quasars can be 
-thought of as the extension of ``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas 
-the ``Changing State'' quasars (CSQs) have a `state-transition' similar to that in Galactic X-ray binaries
-\citep[e.g][]{NodaDone2018, Ruan2019}.
-
-While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
-\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
-broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
-%% 
-Here, we report on three objects 
-SDSS J120544.7+342252.4  (hereafter J1205+3422), 
-SDSS J163852.93+282707.7 (hereafter J1638+2827) and
-SDSS J222818.76+220102.9 (hereafter J2228+2201)  
-which show dramatic changes in the \civ broad emission line
-properties, as well as in the underlying continuum. We claim these are
-the first examples of ``Changing Look Quasars'' at high ($z>1$)
-redshift and for emission lines with high ionization potentials
-(I.P.'s $>$13.6 eV).
-
-For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
 For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the
-standard UV/blue continuum slope increases in flux. 
-the UV/blue continuum diminishes and the shape of \lya changes.
+standard UV/blue continnum slope increases in flux. 
+For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, 
+the UV/blue continuum diminshes and the shape of \lya changes.
 
 \subsection{Literature Search}
-\citet{Wilhite2006} examine the variability of the high-ionizaton
-C~\textsc{iv}$\lambda{1549}$ line in a sample of 105 quasars observed
-at multiple epochs by the Sloan Digital Sky Survey.  We find a strong
-correlation between the change in the C~\textsc{iv} line flux and the
-change in the line width, but no correlations between the change in
-flux and changes in line center and skewness.  The relation between
-line flux change and line width change is consistent with a model in
-which a broad line base varies with greater amplitude than the line
-core. The objects studied here are more luminous and at higher
-redshift than those normally studied for variability, ranging in
-redshift from 1.65 to 4.00 and in absolute $r$-band magnitude from
-roughly $-$24 to $-$28.  Using moment analysis line-fitting
-techniques, we measure line fluxes, centers, widths and skewnesses for
-the C~\textsc{iv} line at two epochs for each object.  The well-known
-Baldwin Effect is seen for these objects, with a slope $\beta =
--0.22$.  The sample has a median intrinsic Baldwin Effect slope of
-$\beta_{int} = -0.85$; the C~\textsc{iv} lines in these
-high-luminosity quasars appear to be less responsive to continuum
-variations than those in lower luminosity AGN.  Additionally, we find
-no evidence for variability of the well known blueshift of the
-C~\textsc{iv} line with respect to the low-ionization
-Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
-indicating that this blueshift might be useful as a measure of
-orientation.
 
@@
 
-\citet{Grier2015}....
+%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}
+
+\citet{Grier2015}
 %\includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}
 
-\citep{Corbin1991, Dimitrijevic1992, Wills1993, Brotherton1994, Osmer1994} ...
+%\includegraphics[]{../../../../../Users/npr1/Downloads/mnras0409-0591.pdf}
+%%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/681-689.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___423__131B.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1992A+AS___96__613D.pdf}
+%%\includegraphics[]{../../../../../Users/npr1/Downloads/1993IAUS__155___94D.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1991ApJ___371L__51C.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
+%[]{../../../../../Users/npr1/Downloads/1993ApJ___415__563W.pdf}
 
-\citep{Nazarova2003} ...
+\subsection{Carbon IV}
+Table~\ref{tab:civ_configs} from 
+Atomic Line List version: 2.05b21  
+%%Version 2.05b21 of the line list was created: Nov 7, 2017.
+\citep{Tunklev1997} \\
 
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}
+\citep[NIST; ][]{Reader2012AAS, Kramida2018}\\
+
+%Wavelength range: 0 - inf   Unit: Angstrom   Type: Vacuum \\
+%Radial velocity: 0 km/s\\
+%Element/Spectrum: C  IV  \\
+%
+%-LAB-WAVL-ANG-VAC-|-SPC-|TT|-TERM--|-J\_i-J\_k-|-LVL-EN--CM-1--|-REF---| \\
+ % 1548.203         C IV E1  2S-2Po 1/2 - 3/2 0.00 - 64591.00 045 \\
+ % 1550.777         C IV E1  2S-2Po 1/2 - 1/2 0.00 - 64483.80 045 \\
+%
+%  gk*Aki weighted average wavelength:    1549.06    \\
+%
+
+\href{https://physics.nist.gov/cgi-bin/ASD/lines1.pl?spectra=C+IV&limits_type=0&low_w=&upp_w=&unit=1&submit=Retrieve+Data&de=0&format=0&line_out=0&en_unit=0&output=0&bibrefs=1&page_size=15&show_obs_wl=1&show_calc_wl=1&unc_out=1&order_out=0&max_low_enrg=&show_av=2&max_upp_enrg=&tsb_value=0&min_str=&A_out=0&intens_out=on&max_str=&allowed_out=1&forbid_out=1&min_accur=&min_intens=&conf_out=on&term_out=on&enrg_out=on&J_out=on}{NIST Atomic Spectra Database Lines Data; C IV: 228 Lines of Data Found}.
+\\
+
+\href{https://physics.nist.gov/cgi-bin/ASD/energy1.pl?encodedlist=XXT2&de=0&spectrum=C+IV&submit=Retrieve+Data&units=0&format=0&output=0&page_size=15&multiplet_ordered=0&conf_out=on&term_out=on&level_out=on&unc_out=1&j_out=on&lande_out=on&perc_out=on&biblio=on&temp=}{C IV   91 Levels Found
+Z = 6, Li isoelectronic sequence}. \\
+
+%%
+Kramida, A., Ralchenko, Yu., Reader, J., and NIST ASD Team (2018).
+NIST Atomic Spectra Database (ver.
+5.6.1), [Online].
+Available: https://physics.nist.gov/asd [2019, March 22].
+National Institute of Standards and Technology, Gaithersburg, MD.
+DOI: https://doi.org/10.18434/T4W30F
+
+%% 
+%% http://www-personal.umich.edu/~cowley/ionen.htm
+%% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
+
+%%\newpage
+%%\input{CIV_AtomicLineList_full}
+%%\newpage
+
+%%\newpage
+%%\input{CIV_AtomicLineList_mid}
+%%\newpage
+
+%%\newpage
+%%\input{CIV_AtomicLineList}
+%\newpage
+
+\begin{table*}
+\begin{tabular}{rrr@{ -- }lr@{ -- }lr@{ -- }llrrr@{ -- }rl}
+\hline
+\multicolumn{1}{c}{$\lambda_{\rm lab}^{\rm obs}$} & \multicolumn{1}{c}{$\Delta\lambda_{\rm lab}^{\rm obs}$} & \multicolumn{2}{c}{Configurations} & \multicolumn{2}{c}{Terms} & $J_i$ & $J_k$ & \multicolumn{1}{c}{$A_{\rm ki}$} & \multicolumn{1}{c}{$\log(gf)$} & TP flags & \multicolumn{2}{c}{Levels}  \\
+\multicolumn{1}{c}{\AA } & \multicolumn{1}{c}{\AA} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{1}{c}{s$^{-1}$} & & & \multicolumn{2}{c}{cm$^{-1}$} & \\
+\hline
+   1548.203  & $2.7-2$ &  $1s^{2}2s$ & $1s^{2}2p$  &       $^{2}{\rm S}$ & $^{2}{\rm P}^\circ$ &  $\frac{1}{2}$ & $\frac{3}{2}$  & $2.65+8$ & $ -0.4198$ &     8 &      $0.00$ &  $64591.00$  \\
+   1550.777  & $2.7-2$ &  $1s^{2}2s$ & $1s^{2}2p$  &       $^{2}{\rm S}$ & $^{2}{\rm P}^\circ$ &  $\frac{1}{2}$ & $\frac{1}{2}$  & $2.63+8$ & $ -0.7217$ &     8 &      $0.00$ &  $64483.80$  \\
+\hline
+\end{tabular}
+\label{tab:civ_configs}
+\end{table*}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
-%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
-%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Data}
-\subsection{Selection/Identification}
-
-\subsection{SDSS spectra}
 \begin{table}
@@
     \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
-                                         & 7582, 790, 56960	     & 5201, 178, 55832 \\    
+    &                                                   & 7582, 790, 56960	     & 5201, 178, 55832 \\    
+    &                                                   &                                         & \\
  %   &&\\ 
-    %$M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
-    %log $(L_{\rm bol} / {\rm erg s}^{-1}) $      &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
-    %log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
-    %Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
+    $M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
+    log $(L_{\rm bol} / {\rm erg s}^{-1}) $  &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
+    log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
+    Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
     &&\\
@@
 
-Double Spectrograph (DBSP) is a low-to-medium resolution ($R\sim$1,000
-to 10,000) grating instrument for the Palomar 200-inch telescope
-Cassegrain focus that uses a dichroic (at, e.g., 5200\AA\ ) to split
-light into simultaneously observed separate red and blue channels.
+\subsection{J2228+2201}
+SDSS J222818.76+220102.9 (R.A. 337.078194926, 22.017477924was observed
 
-The Low Resolution Imaging Spectrometer (LRIS) is a visible-wavelength
-imaging and spectroscopy instrument commissioned in 1993 and operating
-at the Cassegrain focus of 10-meter Keck I telescope.
-
-\begin{table*}
- \centering
- \begin{tabular}{r  r  r r r   r r r r}
-  \hline \hline 
-% &&\\
-   Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{Mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}   & Exposure    & \multirow{3}{*}{Spectrum} & \multirow{3}{*}{Notes} \\
-   R.A.
-/ deg                   &               &               &            &                                &                                                                       &  Time         & & \\
-   Decl.
-/ deg                 &               &               &            &                                &                                                                       &  / seconds         & & \\
-
-% &&\\
- \hline 
-                                       &                &               &            &                              &                   &                             &  & \\
-   J120544.7+342252.4   & 2.071     &   17.99   & 53498 & 2005-May-08   & SDSS             & ?                          & 53498-2089-427  & \\
-          181.436164           &                &               & 58538 & 2019-Feb-24     & DBSP            &  2$\times$900    &                               &  Conditions? \\
-         +34.381229           &                &               & 58693 & 2019-Jul-29      & DBSP            &  2$\times$1200   &                                &   \\
-                                       &                &               &              &                           &                   &                             &  & \\
-   J163852.9+282707.7   & 2.182     &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
-      249.720558407	       &               &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
-       +28.452158884        &               &              & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
-                                       &                &               &              &                           &                   &                             &  & \\
-    J222818.7+220102.9   & 2.222     & 19.97    & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
-        337.078194              &              &              & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
-        +22.017478                                &               &             & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
-                                       &                &               &            &                             &                   &                              &  & \\
-%   J232446.7+140029.5   &  0.916     &  18.83   &  56209 & 2012-Oct-09   & BOSS             & ?                             & 56209-6148-743   & \\
- %                                      &                &               &   58662 & 2019-Jun-28  &   (??)DBSP       & ?                            &  & \\
-  %                                     &                &               &              &                           &                   &                              &  & \\
-   \hline \hline   
-  \end{tabular}
-  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
-Exposure times are from the {\tt plate.fits} file. 
-DBSP on the Palomar 200-inch telescope is the } 
- \label{tab:obs_notes}
-\end{table*}
-
-\subsection{J1205+3422 }
-SDSS J120544.67+342252.4, observed by SDSS, first reported in \citet{Schneider2007}. 
-Redshift of $z=$2.068$\pm$0.00027. 
-%% targeting_flags	SERENDIP_BLUE QSO_CAP
-plate	2089 
-mjd	53498
-fiberid	427
+%%\href{https://skyserver.sdss.org/dr12/en/tools/chart/navi.aspx?ra=337.077916666667&dec=22.0173888888889&scale=0.2&width=120&height=120&opt=
+skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655
+All Spectra of this Object:: \\
+specObjId	plate	MJD	fiber	ra	dec	redshift \\
+8536790363997708288	7582	56960	790	2.222$\pm$0.00038\\
+6888453645991387136	6118	56189	720	2.217$\pm$0.00208\\
 
@@
 SDSS J163852.93+282707.7       16h38m52.9s +28d27m08s  \\
-First reported in \citet{Schneider2010}. 
-Selected by {\tt SERENDIP\_BLUE} and {\tt QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
+Selected by {\tt SERENDIP\_BLUE} and {\it QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
 Selected as a $z>2$ known quasar and passed BOSS quasar target selections \citep{Ross2012}.
@@
 Decl. (J2000) = 28.45217 degs. \\
-\href{skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232}{SDSS SkyServer} 
+skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232
 All Spectra of this Object:: \\
@@
 
-\subsection{J2228+2201}
-SDSS J222818.76+220102.9 (R.A. 337.078194926, Decl. 22.017477924) was first reported in 
-\citet{Paris2017}.
+\section{Results}
 
-%%\href{https://skyserver.sdss.org/dr12/en/tools/chart/navi.aspx?ra=337.077916666667&dec=22.0173888888889&scale=0.2&width=120&height=120&opt=
-\href{skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655}{SDSS SkyServer}
-All Spectra of this Object:: \\
-specObjId	plate	MJD	fiber	ra	dec	redshift \\
-8536790363997708288	7582	56960	790	2.222$\pm$0.00038\\
-6888453645991387136	6118	56189	720	2.217$\pm$0.00208\\
-
-%Plate: 2948, MJD: 54553, Fiber: 0614
-%https://dr12.sdss.org/spectrumDetail?mjd=54553&fiber=614&plateid=2948
-
-\begin{table*}
-  \centering
-  \begin{tabular}{l  l  l    lll}
-    \hline \hline 
-    Line 	    &   Rest	      & Line       & Line	       &	Line			                 &   Continuum \\ 
-    Name	    &   Wavelength  &  $z$       & $\sigma$ 	&	Flux			                 & \\
-                    &    $\AA $        &              & /  km s$-1$	&     10$^{-17}$ erg/cm$2$/s &  10$^{-17}$ erg/cm$^2$/s/\AA  \\
-Ly$\alpha$  &	 1215.7	&	2.186      &	1362	&	510.5		                &	7.224 \\
-\nv		    &   1240.8	&	2.184     &	 854.6	&	122.4	                    	&	5.546 \\ 
-\civ		    &  1549.5	&	2.184    &	1927	&	462.6		                &	2.722 \\ 
-\heii	    &	 1640.4	&	2.184    &	1927	&    	  8.067	                   	&	2.447 \\  
-\ciii 	    &	 1908.7	&	2.184    &	1927	&	164.6	                   	&	1.966  \\ 
-\mgii	    &	 2800.3	&	2.184   & 	1927	&	187.4	                   	&	1.513  \\
-   \hline \hline   
-  \end{tabular}
-  \caption{Line Measurement Information}
- \label{tab:line_values}
-\end{table*}
-
-\begin{table*}
-  \centering
-  \begin{tabular}{l  lll lll  }
-    \hline \hline 
-                                    &                               &                                           &                                                      &                                  &                         & \\
-                                  \multicolumn{7}{c}{J1638+2827}  \\
-                                    &                               &                                           &                                                      &                                  &                         & \\
-   \hline                       
-%                                   &                               &                                           &                                                      &                                  &                         & \\
-    Line      	             & Line  $\sigma$     & Line  Flux                           &   Continuum                                 & Line  $\sigma$          & Line  Flux        &   Continuum                                    \\
-%    Wavelength	             & /  km s$^{-1}$         &   10$^{-17}$ erg/cm$2$/s  & 10$^{-17}$ erg/cm$^2$/s/\AA      &  /  km s$-1$             & / 10$^{-17}$ erg/cm$2$/s   & /10$^{-17}$ erg/cm$^2$/s/\AA       \\
-                                     & \multicolumn{3}{l}{MJD 54553}                                                                                   & \multicolumn{3}{l}{MJD 55832}                                                                                                          \\
-    Ly$\alpha$1215.7    &  1362	            &	510.5		                  &	7.224                                           &  1769	                &   633.9	              &  5.376     \\
-    \nv1240.8	            &   854.6	            &	122.4	                    	  &	5.546                                           & 1012	                &  107.1		      &  4.645\\ 
-    \civ1549.5         	    &	 1927	            &	462.6		                  &	2.722                                           & 2287	                &  125.1		      &  1.256      \\  
-    \heii1640.4	            &	 1927    	            &      8.067	                   	  &	2.447                                           & 2287	                &    10.68	      &  1.001\\  
-    \ciii1908.7        	    &	 1927	            &	164.6	                   	  &	1.966                                          & 2287	 	                &     29.53	      &  0.6008\\ 
-    \mgii2800.3	    &   1927	            &	187.4	                   	  &	1.513                                          & 2287 	 	         &    34.66	      &  0.3461  \\
-                                    &                               &                                           &                                                      &                                  &                           &                \\
-   \hline \hline   
-  \end{tabular}
-  \caption{Line Measurement Information. 
-    Line $\sigma$ in units of   km s$-1$; 
-    Line flux          in units of  10$^{-17}$ erg/cm$^2$/s; 
-    Continuum      in units of  10$^{-17}$ erg/cm$^2$/s/ \AA; 
-}
- \label{tab:line_values}
-\end{table*}
-
-%Plate: 5201, MJD: 55832, Fiber: 178
-%https://dr12.sdss.org/spectrumDetail?mjd=55832&fiber=178&plateid=5201
-
-%Line		Rest		        Line	        Line		        Line			   Continuum
-%Name		Wavelength	z	        sigma 		Flux	
-%                       [Å]			               [km s-1]  	[10-17erg/cm2/s] 	   [10-17erg/cm2/s/Å]
-%Ly_alpha	1215.7		2.186	1769		633.9		   5.376
-%N_V		1240.8		2.185	1012		107.1		   4.645
-%C_IV		1549.5		2.185	2287		125.1		   1.256
-%He_II		1640.4		2.185	2287		 10.68		   1.001
-%C_III]		1908.7		2.185	2287	 	 29.53		   0.6008
-%Mg_II		2800.3		2.185	2287 	 	 34.66		   0.3461
-
-%So, ratios, MJD 54553 / MJD 55832::
-%$Ly_alpha	1215.7		—	0.770		0.805			1.344			
-%N_V		1240.8		—	0.844		1.143			1.194
-%C_IV		1549.5		—	0.843		3.698			2.167			
-%He_II		1640.4		—	0.843		0.755			2.445			
-%C_III]		1908.7		—	0.843		5.574			3.27			
-%Mg_II		2800.3		—	0.843		5.407			4.37
-
-\subsection{Multi-wavelength properties}
-MIR \\
-Radio \\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
-%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
-%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\subsection{In the context of CLQs at lower-$z$}
-
-\subsection{Balmer CLQs vs. \civ CLQs}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
-%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
-%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion and Conclusions}
@@
 \bibliographystyle{mnras}
-\bibliography{tester_mnras}
+\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}
 

### 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190329.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190322.tex
@@
 \section{Introduction}
-While there have been a slew of studies on carbon IV (\civ) broad absorption line quasars
-\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}. However, dramatic changes in the 
+While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
+\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
 broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
 Here, we report on two objects SDSS J222818.76+220102.9 (hereafter J2228+2201) and 
-SDSS J163852.93+282707.7 (hereafter J1638+2827).
+SDSS J163852.93+282707.7 (hereafter J1638+2827) which show dramatic changes in the \civ broad emission line properties, as well as in the underlying continuum.
+We claim these are the first examples of ``Changing Look Quasars'' at high ($z>1$) redshift and for emission lines with high ionization potentials (I.P.'s
+$>$13.6 eV).
 
@@
 \subsection{Literature Search}
+\citet{Baldwin1977}...
+Since the discovery of an anticorrelation between the equivalent width $W_{\lambda}$ of the \civ $\lambda$1549 emission line and the continuum luminosity $L$ by Baldwin (1977),
+
+%\includegraphics[]{../../../../../Users/npr1/Downloads/mnras0409-0591.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/681-689.pdf}
+
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1991ApJ___371L__51C.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1992A+AS___96__613D.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1993IAUS__155___94D.pdf}
+%[]{../../../../../Users/npr1/Downloads/1993ApJ___415__563W.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___425__622P.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___423__131B.pdf}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}
+
+See e.g., \citet{HamannFerland1999} and \citet{Sulentic2000_ARAA} for reviews of 
+elemental abundances and phenomenology of broad emission lines in 
+AGN.
+
+\citet{Dietrich2002}
+
+\citet{Croom2002}
+
+\citet{Hamann2002}
 
@@
 
+%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
+
+%%\citet{Punsly2010}
 %% Punsly 2010
@@
 %% THE REDSHIFTED EXCESS IN QUASAR C iv BROAD EMISSION LINES
+%%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
+
+\citet{Richards2011} 
+use a sample of $\sim$30,000 quasars from the 7th Data Release of the Sloan Digital Sky Survey, and explore the range of properties exhibited by high-ionization, broad emission lines, such as \civ $\lambda$1549.
+Specifically, we investigate the anti-correlation between continuum luminosity and emission-line equivalent width (the Baldwin Effect (BEff)) and the ``blueshifting''of the high-ionization emission lines with respect to low-ionization emission lines.
+%Employing improved redshift determinations from Hewett \& Wild, the blueshift of the C IV emission line is found to be nearly ubiquitous, with a mean shift of ~810 km s-1 for radio-quiet (RQ) quasars and ~360 km s-1 for radio-loud (RL) quasars.
+The BEff is present in both RQ and RL samples.
+We consider these phenomena within the context of an accretion disk-wind model that is modulated by the nonlinear correlation between ultraviolet and X-ray continuum luminosity.
+Composite spectra are constructed as a function of C IV emission-line properties in an attempt to reveal empirical relationships between different line species and the continuum.
+Within a two-component disk+wind model of the broad emission-line region (BELR), where the wind filters the continuum seen by the disk component, we find that RL quasars are consistent with being dominated by the disk component, while broad absorption line quasars are consistent with being dominated by the wind component.
+Some RQ objects have emission-line features similar to RL quasars; they may simply have insufficient black hole (BH) spin to form radio jets.
+Our results suggest that there could be significant systematic errors in the determination of L bol and BH mass that make it difficult to place these findings in a more physical context.
+It is possible to classify quasars in a paradigm where the diversity of BELR parameters is due to differences in an accretion disk wind between quasars (and over time); these differences are underlain primarily by the spectral energy distribution, which ultimately must be tied to BH mass and accretion rate.
+
+\citet{Bian2012}
+
+\citet{Sun2015} , ApJ, 811, 42
+%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}
+
+\citet{Grier2015}
+%\includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}
 
@@
 http://adsabs.harvard.edu/abs/2015AAS...22520403D\\
+
+\citet{Denney2016} investigate the dependence on data quality of quasar properties
+measured from the C IV emission line region at high redshifts.  Our
+measurements come from 32 epochs of Sloan Digital Sky Survey
+Reverberation Mapping Project spectroscopic observations of 482 $z >
+1.46$ quasars. We compare the differences between measurements made
+from the single-epoch (SE) and coadded spectra, focusing on the \civ
+$\lambda$1549 emission line because of its importance for studies of
+high-redshift quasar demographics and physical properties, including
+black hole masses. In addition to statistical errors increasing (by
+factors of $\sim2-4$), we find increasing systematic offsets with
+decreasing signal-to-noise ratio (S/N).
+
+%%\citet{Cracco2016}
+
+\citet{Ge2016}
+
+\citep{Tammour2016} use the K-means unsupervised clustering algorithm 
+to study a sample of quasar UV spectra from the 10th Data Release of the Sloan Digital Sky Survey
+\citep[SDSS-DR10Q; ][]{Paris2014}.
 
@@
 
-\citet{Richards2011} 
-use a sample of $\sim$30,000 quasars from the 7th Data Release of the Sloan Digital Sky Survey, and explore the range of properties exhibited by high-ionization, broad emission lines, such as \civ $\lambda$1549.
-Specifically, we investigate the anti-correlation between continuum luminosity and emission-line equivalent width (the Baldwin Effect (BEff)) and the ``blueshifting''of the high-ionization emission lines with respect to low-ionization emission lines.
-%Employing improved redshift determinations from Hewett \& Wild, the blueshift of the C IV emission line is found to be nearly ubiquitous, with a mean shift of ~810 km s-1 for radio-quiet (RQ) quasars and ~360 km s-1 for radio-loud (RL) quasars.
-The BEff is present in both RQ and RL samples.
-We consider these phenomena within the context of an accretion disk-wind model that is modulated by the nonlinear correlation between ultraviolet and X-ray continuum luminosity.
-Composite spectra are constructed as a function of C IV emission-line properties in an attempt to reveal empirical relationships between different line species and the continuum.
-Within a two-component disk+wind model of the broad emission-line region (BELR), where the wind filters the continuum seen by the disk component, we find that RL quasars are consistent with being dominated by the disk component, while broad absorption line quasars are consistent with being dominated by the wind component.
-Some RQ objects have emission-line features similar to RL quasars; they may simply have insufficient black hole (BH) spin to form radio jets.
-Our results suggest that there could be significant systematic errors in the determination of L bol and BH mass that make it difficult to place these findings in a more physical context.
-It is possible to classify quasars in a paradigm where the diversity of BELR parameters is due to differences in an accretion disk wind between quasars (and over time); these differences are underlain primarily by the spectral energy distribution, which ultimately must be tied to BH mass and accretion rate.
+%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}
 
-%\includegraphics\includegraphics[]{../../../../../Users/npr1/Downloads/Richards_2011_AJ_141_167.pdf}
+\citet{Sulentic2017} find that:
 
-%\citet{1994}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___425__622P.pdf}
+{\it (i):} \civ outflows become stronger and more frequent at higher-$z$ in sources with 2-4 dex higher luminosity than low-$z$ quasars.
+The emission component associated with the outflow becomes a dominant source of line broadening, and confirms that the full \civ profile is not a useful virial estimator of black hole mass for most sources.
+{\it (ii):} We show evidence that the Civ outflows are driven by $L/LEdd$ rather than source luminosity.
+A clear dependence of \civ blueshifts on Eddington ratio is observed while a weaker trend is observed with source luminosity that becomes appreciable only over a wide luminosity range (4–5 dex).
+Large shifts ($c(\frac{1}{2}) \lesssim -1000 km s^{-1}$) are apparently possible above a threshold $L/L_{\rm Edd} \approx 0.2\pm0.1$.
+{\it (iii):} The relations between $c(\frac{1}{2})$ and $L/L_{\rm Edd}$ and $L$ are consistent with a radiation-driven outflow, and the largest shifts may support the existence of an optically thick ADAF in at least some of the Pop.
+A sources.
 
-%\citet{1994}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ASPC___69____1P.pdf}
+\citet{Martinez-Aldama2018} 
+present a sample of 19 quasar satisfying the 
+4D eigenvector 1 \citep[4DE1; ][]{Sulentic2000, Marziani2001} 
+selection criteria for finding high redshift highly accretors xA sources. 
+and show that this sample is likely radiating close to the Eddington limit 
+$(L/L_{\rm Edd} \geq 0.2)$. 
+FWHM, centroid at half intensity $c(\frac{1}{2})$
 
-\citet{Denney2016}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Denney_2016_ApJS_224_14.pdf}
-investigate the dependence on data quality of quasar properties
-measured from the C IV emission line region at high redshifts.  Our
-measurements come from 32 epochs of Sloan Digital Sky Survey
-Reverberation Mapping Project spectroscopic observations of 482 $z >
-1.46$ quasars. We compare the differences between measurements made
-from the single-epoch (SE) and coadded spectra, focusing on the \civ
-$\lambda$1549 emission line because of its importance for studies of
-high-redshift quasar demographics and physical properties, including
-black hole masses. In addition to statistical errors increasing (by
-factors of $\sim2-4$), we find increasing systematic offsets with
-decreasing signal-to-noise ratio (S/N).
-
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}
-
-\citet{Grier2015}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}
-
-%\includegraphics[]{../../../../../Users/npr1/Downloads/mnras0409-0591.pdf}
-%%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/681-689.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___423__131B.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/1992A+AS___96__613D.pdf}
-%%\includegraphics[]{../../../../../Users/npr1/Downloads/1993IAUS__155___94D.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/1991ApJ___371L__51C.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}
-%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
-%[]{../../../../../Users/npr1/Downloads/1993ApJ___415__563W.pdf}
+\subsection{The Baldwin Effect}
+\input{Beff}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
+%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
+%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Data}
+\subsection{Selection/Identification}
+
+\subsection{SDSS spectra}
 \begin{table}
@@
     \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
-    &                                                   & 7582, 790, 56960	     & 5201, 178, 55832 \\    
-    &                                                   &                                         & \\
+                                                          & 7582, 790, 56960	     & 5201, 178, 55832 \\    
  %   &&\\ 
-    $M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
-    log $(L_{\rm bol} / {\rm erg s}^{-1}) $  &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
-    log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
-    Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
+    %$M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
+    %log $(L_{\rm bol} / {\rm erg s}^{-1}) $      &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
+    %log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
+    %Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
     &&\\
@@
 
+\subsection{Check Hamann 2017}
+\citet{Hamann2017} carry out a deep investigation into Extremely Red Quasars \citep[ERQs;][]{Ross2015, Zakamska2016} using the SDSS-III BOSS dataset.
+One product of that investigation is a new catalogue of \civ and \nv emission-line data for 216 188 BOSS quasars.
+%% to characterize the ERQ line properties further.
+
+\input{Ham17_clqs}
+
+\subsection{J1638+2827}
+SDSS J163852.93+282707.7       16h38m52.9s +28d27m08s  \\
+Selected by {\tt SERENDIP\_BLUE} and {\tt QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
+Selected as a $z>2$ known quasar and passed BOSS quasar target selections \citep{Ross2012}.
+
+R.A. (J2000) = 249.72058 degs. \\
+Decl. (J2000) = 28.45217 degs. \\
+\href{skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232}{SDSS SkyServer} 
+All Spectra of this Object:: \\
+specObjId	plate	MJD	fiber	ra	dec	redshift \\
+5855854441601671168	5201	55832	178	2.186$\pm$0.00073\\
+3319321776793610240	2948	54553	614	2.185$\pm$0.00043\\
+
 \subsection{J2228+2201}
-SDSS J222818.76+220102.9 (R.A. 337.078194926, 22.017477924was observed
+SDSS J222818.76+220102.9 (R.A. 337.078194926, Decl. 22.017477924) was observed...
 
 %%\href{https://skyserver.sdss.org/dr12/en/tools/chart/navi.aspx?ra=337.077916666667&dec=22.0173888888889&scale=0.2&width=120&height=120&opt=
-skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655
+\href{skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655}{SDSS SkyServer}
 All Spectra of this Object:: \\
@@
 
-\subsection{J1638+2827}
-SDSS J163852.93+282707.7       16h38m52.9s +28d27m08s  \\
-Selected by {\tt SERENDIP\_BLUE} and {\it QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
-Selected as a $z>2$ known quasar and passed BOSS quasar target selections \citep{Ross2012}.
+%\subsection{J1504+1029}
+%SDSS J150425.0+102939.2
 
-R.A. (J2000) = 249.72058 degs. \\
-Decl. (J2000) = 28.45217 degs. \\
-skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232
-All Spectra of this Object:: \\
-specObjId	plate	MJD	fiber	ra	dec	redshift \\
-5855854441601671168	5201	55832	178	2.186$\pm$0.00073\\
-3319321776793610240	2948	54553	614	2.185$\pm$0.00043\\
+\subsection{J2344-0039}
+SDSS J234423.8-003950.2
 
+\subsection{Richards et al. (2011)}
+98,715 objects in %actual input (public.gtr.DR7qsosHW10pub2) and output tables 
+public.gtr.dr7qsos\_c4b\_HW10pub2n\_big from SDSS CasJobs.
+
+588018055127629913
+
+\subsubsection{Lines from SDSS database}
+\civ  $\lambda$1549.479 \\
+2799 $\lambda$2799.116  \\
+1909 $\lambda$1908.734 \\
+
+\subsection{Multi-wavelength properties}
+MIR \\
+
+Radio. \\ 
+J2228+2201 is not in the area currently covered by the FIRST catalog.
+
+Searching the FIRST catalog for sources within 10.0000 arcsec of 16 38 52.930 +28 27 07.70 (J2000). 
+Map RMS at search position is 0.133 mJy/beam. 
+Catalog detection limit (including CLEAN bias) at source position is 0.91 mJy/beam
+No sources found within 10.0000 arcsec
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
+%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
+%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
+\subsection{In the context of CLQs at lower-$z$}
 
+\subsection{Balmer CLQs vs. \civ CLQs}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
+%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
+%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion and Conclusions}

### 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190611.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190322.tex
@@
 %Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
-%K. E. Saavik Ford$^{2,3,4}$,  Matthew Graham$^{5}$,  Barry McKernan$^{2,3,4}$,  
+% Matthew Graham$^{5}$
+% K. E. Saavik Ford$^{2,3,4}$, 
+% Barry McKernan$^{2,3,4}$,  
 %\newauthor Daniel Stern$^{6}$, 
-%Aaron M. Meisner$^{7,8}$, Roberto J. Assef$^{9}$, Arjun Dey$^{10}$, Andrew J. Drake$^{11}$, \newauthor Hyunsung D. Jun$^{12}$, Dustin Lang$^{13,14,15}
 \\
-% List of institutions
+%% List of institutions
 $^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
@@
 \date{Accepted XXX. Received YYY; in original form ZZZ}
-\pubyear{2018}
+\pubyear{2019}
 
@@
 \begin{abstract}
+%% 190 words of 'lorem ipsum' (200 words Abstract total for MNRAS Letters)
 Lorem ipsum dolor sit amet, consectetur adipiscing elit.
@@
 \section{Introduction}
-While there have been a slew of studies on carbon IV (\civ) broad absorption line quasars
-\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}. However, dramatic changes in the 
-broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
-Here, we report on two objects SDSS J222818.76+220102.9 (hereafter J2228+2201) and 
-SDSS J163852.93+282707.7 (hereafter J1638+2827).
+While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars \citep[BAL QSOs; see e.g.
+Table 1][]{Hemler2019}, dramatic changes in the broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen.
+Here, we report on two objects SDSS J222818.76+220102.9 (hereafter J2228+2201) and SDSS J163852.93+282707.7 (hereafter J1638+2827) which show dramatic changes in the \civ broad emission line properties, as well as in the underlying continuum.
+We claim these are the first examples of ``Changing Look Quasars'' at high ($z>1$) redshift and for emission lines with high ionization potentials (I.P.'s $>$13.6 eV).
 
-For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the
-standard UV/blue continnum slope increases in flux. 
-For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, 
-the UV/blue continuum diminshes and the shape of \lya changes.
+For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the standard UV/blue continuum slope increases in flux.
+For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, the UV/blue continuum diminishes and the shape of \lya changes.
 
-\subsection{Literature Search}
+%% \subsection{Literature Search}
 
@@
 %% THE REDSHIFTED EXCESS IN QUASAR C iv BROAD EMISSION LINES
+
+\citet{Wilhite2005} and especially \citet{Wilhite2006}
+
+\citet{Wilhite2008} also...
 
@@
 
-\subsection{Carbon IV}
+%%\subsection{Carbon IV}
 Table~\ref{tab:civ_configs} from 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
+%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
+%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
+\section{Data}
+\subsection{Selection/Identification}
 
-\section{Data}
+\subsection{SDSS spectra}
 \begin{table}
@@
     \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
-    &                                                   & 7582, 790, 56960	     & 5201, 178, 55832 \\    
-    &                                                   &                                         & \\
+                                         & 7582, 790, 56960	     & 5201, 178, 55832 \\    
  %   &&\\ 
-    $M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
-    log $(L_{\rm bol} / {\rm erg s}^{-1}) $  &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
-    log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
-    Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
+    %$M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
+    %log $(L_{\rm bol} / {\rm erg s}^{-1}) $      &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
+    %log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
+    %Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
     &&\\
@@
 \subsection{J2228+2201}
-SDSS J222818.76+220102.9 (R.A. 337.078194926, 22.017477924was observed
+SDSS J222818.76+220102.9 (R.A. 337.078194926, Decl. 22.017477924) was observed...
 
 %%\href{https://skyserver.sdss.org/dr12/en/tools/chart/navi.aspx?ra=337.077916666667&dec=22.0173888888889&scale=0.2&width=120&height=120&opt=
-skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655
+\href{skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655}{SDSS SkyServer}
 All Spectra of this Object:: \\
@@
 SDSS J163852.93+282707.7       16h38m52.9s +28d27m08s  \\
-Selected by {\tt SERENDIP\_BLUE} and {\it QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
+Selected by {\tt SERENDIP\_BLUE} and {\tt QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
 Selected as a $z>2$ known quasar and passed BOSS quasar target selections \citep{Ross2012}.
@@
 Decl. (J2000) = 28.45217 degs. \\
-skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232
+\href{skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232}{SDSS SkyServer} 
 All Spectra of this Object:: \\
@@
 
+\subsection{Multi-wavelength properties}
+MIR \\
+Radio \\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
+%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
+%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
+Even with nearly a change of a decade in the continuum flux, no 
+no change is seen in the flux of the \civ line flux \citet[e.g. Figure 6 in ][]{Hawkins2011}.
 
+\citep{Wilhite2006} for SDSS...
+
+\subsection{In the context of CLQs at lower-$z$}
+
+\subsection{Balmer CLQs vs. \civ CLQs}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
+%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
+%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion and Conclusions}
@@
 \bibliographystyle{mnras}
-\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}
+\bibliography{tester_mnras}
 

### 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190820.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190611.tex
@@
 %Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
-% Matthew Graham$^{5}$
-% K. E. Saavik Ford$^{2,3,4}$, 
-% Barry McKernan$^{2,3,4}$,  
+%K. E. Saavik Ford$^{2,3,4}$,  Matthew Graham$^{5}$,  Barry McKernan$^{2,3,4}$,  
 %\newauthor Daniel Stern$^{6}$, 
+%Aaron M. Meisner$^{7,8}$, Roberto J. Assef$^{9}$, Arjun Dey$^{10}$, Andrew J. Drake$^{11}$, \newauthor Hyunsung D. Jun$^{12}$, Dustin Lang$^{13,14,15}
 \\
-%% List of institutions
+% List of institutions
 $^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
@@
 \date{Accepted XXX. Received YYY; in original form ZZZ}
-\pubyear{2019}
+\pubyear{2018}
 
@@
 \begin{abstract}
-%% 190 words of 'lorem ipsum' (200 words Abstract total for MNRAS Letters)
 Lorem ipsum dolor sit amet, consectetur adipiscing elit.
@@
 \section{Introduction}
-While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars \citep[BAL QSOs; see e.g.
-Table 1][]{Hemler2019}, dramatic changes in the broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen.
-Here, we report on two objects SDSS J222818.76+220102.9 (hereafter J2228+2201) and SDSS J163852.93+282707.7 (hereafter J1638+2827) which show dramatic changes in the \civ broad emission line properties, as well as in the underlying continuum.
-We claim these are the first examples of ``Changing Look Quasars'' at high ($z>1$) redshift and for emission lines with high ionization potentials (I.P.'s $>$13.6 eV).
+While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
+\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
+broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
+Here, we report on two objects SDSS J222818.76+220102.9 (hereafter J2228+2201) and 
+SDSS J163852.93+282707.7 (hereafter J1638+2827) which show dramatic changes in the \civ broad emission line properties, as well as in the underlying continuum.
+We claim these are the first examples of ``Changing Look Quasars'' at high ($z>1$) redshift and for emission lines with high ionization potentials (I.P.'s
+$>$13.6 eV).
 
-For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the standard UV/blue continuum slope increases in flux.
-For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, the UV/blue continuum diminishes and the shape of \lya changes.
+For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the
+standard UV/blue continuum slope increases in flux. 
+For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, 
+the UV/blue continuum diminishes and the shape of \lya changes.
 
-%% \subsection{Literature Search}
+\subsection{Literature Search}
 
@@
 %% THE REDSHIFTED EXCESS IN QUASAR C iv BROAD EMISSION LINES
-
-\citet{Wilhite2005} and especially \citet{Wilhite2006}
-
-\citet{Wilhite2008} also...
 
@@
 
-%%\subsection{Carbon IV}
+\subsection{Carbon IV}
 Table~\ref{tab:civ_configs} from 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
-%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
-%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
+%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
+%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Data}
@@
 \section{Results}
-Even with nearly a change of a decade in the continuum flux, no 
-no change is seen in the flux of the \civ line flux \citet[e.g. Figure 6 in ][]{Hawkins2011}.
-
-\citep{Wilhite2006} for SDSS...
-
 \subsection{In the context of CLQs at lower-$z$}

### 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190829.tex
CIV tex/ tidy up

--- 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190820.tex
@@
 broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
-Here, we report on two objects SDSS J222818.76+220102.9 (hereafter J2228+2201) and 
-SDSS J163852.93+282707.7 (hereafter J1638+2827) which show dramatic changes in the \civ broad emission line properties, as well as in the underlying continuum.
-We claim these are the first examples of ``Changing Look Quasars'' at high ($z>1$) redshift and for emission lines with high ionization potentials (I.P.'s
-$>$13.6 eV).
+%% 
+Here, we report on three objects 
+SDSS J120544.7+342252.4  (hereafter J1205+3422), 
+SDSS J163852.93+282707.7 (hereafter J1638+2827) and
+SDSS J222818.76+220102.9 (hereafter J2228+2201)  
+which show dramatic changes in the \civ broad emission line
+properties, as well as in the underlying continuum. We claim these are
+the first examples of ``Changing Look Quasars'' at high ($z>1$)
+redshift and for emission lines with high ionization potentials
+(I.P.'s $>$13.6 eV).
 
+For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
 For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
 standard UV/blue continuum slope increases in flux. 
-For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, 
 the UV/blue continuum diminishes and the shape of \lya changes.
@@
 \subsection{Literature Search}
+\citet{Wilhite2006} examine the variability of the high-ionizaton
+C~\textsc{iv}$\lambda{1549}$ line in a sample of 105 quasars observed
+at multiple epochs by the Sloan Digital Sky Survey.  We find a strong
+correlation between the change in the C~\textsc{iv} line flux and the
+change in the line width, but no correlations between the change in
+flux and changes in line center and skewness.  The relation between
+line flux change and line width change is consistent with a model in
+which a broad line base varies with greater amplitude than the line
+core. The objects studied here are more luminous and at higher
+redshift than those normally studied for variability, ranging in
+redshift from 1.65 to 4.00 and in absolute $r$-band magnitude from
+roughly $-$24 to $-$28.  Using moment analysis line-fitting
+techniques, we measure line fluxes, centers, widths and skewnesses for
+the C~\textsc{iv} line at two epochs for each object.  The well-known
+Baldwin Effect is seen for these objects, with a slope $\beta =
+-0.22$.  The sample has a median intrinsic Baldwin Effect slope of
+$\beta_{int} = -0.85$; the C~\textsc{iv} lines in these
+high-luminosity quasars appear to be less responsive to continuum
+variations than those in lower luminosity AGN.  Additionally, we find
+no evidence for variability of the well known blueshift of the
+C~\textsc{iv} line with respect to the low-ionization
+Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
+indicating that this blueshift might be useful as a measure of
+orientation.
 
@@
 
+Double Spectrograph (DBSP) is a low-to-medium resolution ($R\sim$1,000
+to 10,000) grating instrument for the Palomar 200-inch telescope
+Cassegrain focus that uses a dichroic (at, e.g., 5200\AA\ ) to split
+light into simultaneously observed separate red and blue channels.
+
+The Low Resolution Imaging Spectrometer (LRIS) is a visible-wavelength
+imaging and spectroscopy instrument commissioned in 1993 and operating
+at the Cassegrain focus of 10-meter Keck I telescope.
+
+\begin{table*}
+ \centering
+ \begin{tabular}{r  r  r r    r r r r}
+  \hline \hline 
+% &&\\
+   Object                          & Redshift  & Mag       & Date                               & Instrument    & Exp. Time            & Spectrum & Notes \\
+% &&\\
+ \hline 
+                                       &                &               &                                         &                   &                             &  & \\
+   J120544.7+342252.4   & 2.071     &   17.99   & 53498  (2005-May-08)   & SDSS             & ?                          & 53498-2089-427  & \\
+                                       &                &               & 58538 (2019-Feb-24)     & DBSP            &  2$\times$900    &                               &  Conditions? \\
+                                       &                &               & 58693 (2019-Jul-29)      & DBSP            &  2$\times$1200   &                                &   \\
+                                       &                &               &                                         &                   &                             &  & \\
+   J163852.9+282707.7   & 2.182     &   19.77    & 54553 (2008-Mar-28)    & SDSS             & ?                          & 54553-2948-614  & \\
+                                        &               &              & 55832  (2011-Sep-28)     & BOSS            &   3603                  & 55832-5201-178  & \\
+                                        &               &              & 58583 (2019-Apr-10)        & LRIS              &  2$\times$900    &   & \\
+                                       &                &               &                                         &                   &                             &  & \\
+    J222818.7+220102.9   & 2.222     & 19.97    & 56189  (2012-Sept-19)     & BOSS             &  2702               & 56189-6118-720   & \\
+                                         &              &              & 56960   (2014-Oct-30)    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
+                                         &               &             & 58693 (2019-Jul-29)      & DBSP              & 2$\times$1200  &       &    \\
+                                       &                &               &                                         &                   &                             &  & \\
+   \hline \hline   
+  \end{tabular}
+  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
+Exposure times are from the {\tt plate.fits} file. 
+DBSP on the Palomar 200-inch telescope is the } 
+ \label{tab:obs_notes}
+\end{table*}
+
 \subsection{J2228+2201}

### 2019-11-07 plots/spectral/CIV_fits.py
BIG plots/spectral/CIV_fits update

@@ -47,7 +47,7 @@ J12_third_flux  = J12_third['flux']
 sdssname   = 'spec-2948-54553-0614.fits'
 J16_first  = fits.open(path+sdssname)
 bossname   = 'spec-5201-55832-0178_v5_10_0.fits'
-J16_second = fits.open(path+sdssname)
+J16_second = fits.open(path+bossname)
 J16_third  = ascii.read(path+'J1638p2827_58583.dat')
 
 J16_redshift    = 2.182
@@ -63,7 +63,7 @@ J16_third_flux  = J16_third['flux']
 sdssname   = 'spec-6118-56189-0720.fits'
 J22_first  = fits.open(path+sdssname)
 bossname   = 'spec-7582-56960-0790.fits'
-J22_second = fits.open(path+sdssname)
+J22_second = fits.open(path+bossname)
 J22_third  = ascii.read(path+'J2228p2201_58693.dat')
 
 J22_redshift    = 2.222
@@ -78,10 +78,6 @@ J22_third_flux  = J22_third['flux']
 ##  R E A D I N G    I N    T H E   L I N E   F I T S    F R O M    Q S F I T
 infile = 'QSFIT_CIV_line_params.dat'
 qsfit = ascii.read(path+infile)
-
-## c in km/s; nominal wavelength in Ang
-qsfit_fwhm_wave  = (qsfit['FWHM']  /3e5) * 1548.
-qsfit_sigma      = qsfit_fwhm_wave / 2.*np.sqrt(2*np.log(2)) 
 
 
 ##  S E T T I N G   U P   T H E   P L O T
@@ -136,65 +132,296 @@ ax1.set_ylim([ymin_J12, ymax_J12])
 ax2.set_ylim([ymin_J12, ymax_J12])
 ax3.set_ylim([ymin_J12, ymax_J12])
 
-ymin_J16 = -2.9; ymax_J16 = 21.9   
-ax4.set_ylim([ymin_J16, ymax_J16])
-ax5.set_ylim([ymin_J16, ymax_J16])
-ax6.set_ylim([ymin_J16, ymax_J16])
+ymin_J16 = -2.9; ymax_J16 = 31.9     ## 21.9 in the 'main' figure; larger here to accomodate legend
+ax4.set_ylim([ymin_J16,  ymax_J16/1.2])
+ax5.set_ylim([ymin_J16,  ymax_J16/2.4])
[…]

### 2019-11-07 plots/spectral/CIV_fits_20191107.py

@@ -1,0 +1,224 @@
+'''
+
+Plotting the observed CIV emission lines from the z~2 CLQs and
+comparing those to the e.g. QSFIT model parameters
+
+'''
+
+import math
+import numpy as np
+import scipy.stats as stats
+
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+from astropy.io          import ascii
+from astropy.io          import fits
+from astropy.convolution import convolve, Box1DKernel
+
+
+##
+## R E A D I N G   I N   T H E    D A T A 
+##
+path = '../../data/QSFIT/'
+
+
+##  J 1 2 0 5 +  3 4 2 2 
+sdssname   = 'spec-2089-53498-0427.fits'
+J12_first  = fits.open(path+sdssname)
+J12_second = ascii.read(path+'J1205p3422_58538.dat')
+J12_third  = ascii.read(path+'J1205p3422_58693.dat')
+
+J12_redshift    = 2.071
+J12_first_flux  =       J12_first[1].data.flux
+J12_first_wave  = (10**(J12_first[1].data.loglam)) / (1 + J12_redshift)
+J12_second_wave = J12_second['wavelength'] / (1 + J12_redshift)
+J12_second_flux = J12_second['flux'] 
+J12_third_wave  = J12_third['wavelength']  / (1 + J12_redshift)
+J12_third_flux  = J12_third['flux']    
+
+
+##  J 1 6 3 8 +  2 8 2 7
+sdssname   = 'spec-2948-54553-0614.fits'
+J16_first  = fits.open(path+sdssname)
+bossname   = 'spec-5201-55832-0178_v5_10_0.fits'
+J16_second = fits.open(path+sdssname)
+J16_third  = ascii.read(path+'J1638p2827_58583.dat')
+
+J16_redshift    = 2.182
+J16_first_flux  =        J16_first[1].data.flux
+J16_first_wave  = (10**( J16_first[1].data.loglam))  / (1 + J16_redshift)
+J16_second_flux =       J16_second[1].data.flux
[…]

### 2019-11-08 data/QSFIT/prep_DBSP_LRIS_spectra.py
data/QSFIT/prep_DBSP_LRIS_spectra.py tiny, tiny modification

@@ -28,18 +28,18 @@ path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/'
 #red    = ascii.read(path+object_name+infile)
 ##
 ##  J1638+2827
-#object_name = 'J1638+2827/'
-#infile = 'LRIS_J1638p2827_b_58583.dat'
-#blue   = ascii.read(path+object_name+infile)
-#infile = 'LRIS_J1638p2827_r_58583.dat'
-#red    = ascii.read(path+object_name+infile)
-##
-##  J2228+3422
-object_name = 'J2228+2201/'
-infile = 'DBSP_J2228p2201_b_58693.dat'
+object_name = 'J1638+2827/'
+infile = 'LRIS_J1638p2827_b_58583.dat'
 blue   = ascii.read(path+object_name+infile)
-infile = 'DBSP_J2228p2201_r_58693.dat'
+infile = 'LRIS_J1638p2827_r_58583.dat'
 red    = ascii.read(path+object_name+infile)
+
+##  J2228+3422
+#object_name = 'J2228+2201/'
+#infile = 'DBSP_J2228p2201_b_58693.dat'
+#blue   = ascii.read(path+object_name+infile)
+#infile = 'DBSP_J2228p2201_r_58693.dat'
+#red    = ascii.read(path+object_name+infile)
 
 
 print()
@@ -60,6 +60,10 @@ wavelength_red  =  red['wavelength']
 flux_blue = (2.99792458E+21 * (blue['flux_density'] / 1000.)) / (blue['wavelength']**2) / 1e-17
 flux_red  = (2.99792458E+21 * ( red['flux_density'] / 1000.)) / ( red['wavelength']**2) / 1e-17
 
+## Trying to 'join' up the Blue and Red arm data more smoothly. 
+#if object_name == 'J1638+2827/':
+#    boost_one = (flux_red[np.where((wavelength_red > 5600) & (wavelength_red < 5680))])*2.]
+    
 
 ## We don’t have flux uncertainties but the SNR
 ## is typically between 10 - 30.

### 2019-11-08 tex/other_tex/201911/CIV_CLQs_20191107.tex
other wee .tex updates

--- 2019-11-07 tex/other_tex/201911/CIV_CLQs_20191105v1.tex
@@
 
+\begin{table*}
+  \begin{centering}
+    \begin{tabular}{l r  r r   lll lll  r r}
+      \hline  \hline 
+      Line                 & $\lambda$ &  Transition  & Ionization  &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
+%                              &    / \AA\    &      / eV             &  / eV            &   Lower                  & Conf.
+&  $J$       & Upper                      &  Conf.
+& $J$       & / cm$^{-1}$    &  / s$^{-1}$                \\      \hline
+                              &  / \AA\     &  energy  / eV &  energy  / eV   &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    &  / s$^{-1}$                \\      \hline
+      H LyLim           &   912.324   & 13.5984           & 13.5984      & 1$s$                      & $^2$S     & 1/2        & $\infty$                  &                                 &             & 109 678.7       & 1.23$\times10^{2}$  \\
+      H Ly$\alpha$  &  1215.670  & 10.1988          & 13.5984      & 1$s$                       & $^2$S      & 1/2        & 2                             &                                 &             &  82 259.2       &  4.67$\times10^{8}$  \\
+      \nv                  &  1238.821  & 10.0082          &  97.8901     &  1$s^{2}$2$s$        &  $^{2}$S   &  1/2       & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2    &  80 721.9        & 3.40$\times10^{8}$   \\
+      \nv                  &  1242.804  &  9.9762            &  97.8901     &  1$s^{2}$2$s$       &  $^{2}$S   &  1/2       &  1$s^{2}$2$p$         &  $^{2}$P$^{{\rm o}}$ &  1/2     &  80 463.2        & 3.37$\times10^{8}$  \\
+      \civ                 &  1548.187  &  8.0083            &  64.4935     &  1$s^{2}$2$s$       &   $^{2}$S  & 1/2        & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  3/2     &  64 591.7        & 2.65$\times10^{8}$  \\
+      \civ                 &  1550.772  &  7.9950          &  64.4935     & 1$s^{2}$2$s$          &  $^{2}$S   & 1/2        & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  1/2     &   64 484.0       & 2.64$\times10^{8}$  \\
+      \ciii                 &  1906.683  &  6.5026    & 47.8878      & 1$s^{2}$2$s^{2}$         &   $^{1}$S   & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &   2        &   52 447.1       & 5.19$\times10^{-3}$ \\
+      \ciii                 &  1908.734  &  6.4956    & 47.8878      & 1$s^{2}$2$s^{2}$         &  $^{1}$S    & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &  1         &  52 390.8        & 1.14$\times10^{2}$  \\
+       \mgii              &  2795.528  &  4.4338    & 15.0353       & 2$p^{6}$3$s$             &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2     &  35 760.9       & 2.60$\times10^{8}$  \\
+      \mgii               &  2802.705  &  4.4224    & 15.0353        & 2$p^{6}$3$s$            &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   1/2     &  35 669.3       & 2.57 $\times10^{8}$ \\
+      H Ba $\beta$   &  4861.333  &  2.5497    & 13.5984       & 2                                 &                 &               & 4                             &                                 &              &  20 564.8       & 8.42$\times10^{6}$  \\
+      \hline   
+      \hline
+    \end{tabular}
+    \caption{Strong UV/optical spectral emission lines in quasars, and their atomic data.
+      Data from the NIST Atomic Spectra Database       \citep{Kramida2018, Kramida2019}.
+      The Transition Energies are $E=hc/\lambda$ for the given wavelength. The Ionization Energy is the
+      energy required to ionize the given species, e.g. 64.49 eV are needed to create a \cv\ ion.
+      Transitions Level configurations are given in standard spectroscopic notation
+      %($N^{2s+1}$ $L_{j}$. 
+      $A_{i,j}$ are transition probabilities.
+%      $A_{i,j}$ are \href{https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-6}{transition probabilities}.} 
+%      such that the radiative lifetime $\tau_{k}$ of an atomic level $k$ is related to the sum of transition probabilities to all levels $i$ lower in energy than $k$
+%      The 1548.202 and 1550.774 \AA\ emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition, split by total angular momentum $J= 3/2$ and $1/2$. 
+      Data from the NIST Atomic Spectra Database       \citep{Kramida2018, Kramida2019}.}
+    %% 
+    %%  Mg II Z = 12, Na isoelectronic sequence  
+  \label{tab:atomic_lines}
+  \end{centering}
+\end{table*}
+
 These CLQs have primarily been defined according to the
@@
 
+Details of the atomic transitions that produce strong rest-frame
+UV/optical lines in quasars are given in Table~\ref{tab:atomic_lines}.
 In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
-the \civ\ doublet \citep{Kramida2018}.  The 1548.202 and 1550.774 \AA\
-emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
-transition, split by total angular momentum $J= 3/2$ and $1/2$,
-resulting in energies 64,591 cm$^{-1}$ and 64,484 cm$^{-1}$,
-respectively \citep[e.g.][]{Moore1993}. The transition probabilities
-of the the 1548 and 1550\AA\ lines are $A_{ki}= 2.65\times10^{8}$ and
-2.64$\times10^{8}$ s$^{-1}$.
-
-The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. Using the
-\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
-Atomic Spectra Database Ionization Energies Form} for ionisation
-energies, we note 11.3 eV is the energy required for C~I to dislodge
+the \civ\ doublet \citep{Kramida2018}.
+%% The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. \
+%% Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form}
+For ionisation energies, 11.3 eV is the energy required for C~I to dislodge
 one electron and become singly-ionised C~II; 24.4 eV is then the
@@
 \gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
-X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).  \ciii is the
-1$s2$2$s$2$p$ $^{3}$P$^{\circ}$ to 1$s^{2}$2$s^{2}$ $^{1}$S transition
-(with $J=1\rightarrow0$) resulting in an energy of 52,390.75 cm$^{-1}$ and
-a transition probability of $A_{ki} = 1.14\times10^{2}$ s$^{-1}$ \citep{Wiese1996}.
+X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).
 
@@
   \centering
-  % \begin{tabular}{lll  cccc r }
-  \begin{tabu}{l ll  ll cc c r }
-    \hline 
-    \hline 
-    Object                               &   MJD      & line      & Line  Lumin.
-&   FWHM                       &  $V_{\rm off}$         & E.W.
-& $\alpha_{\lambda}$  &   Catalogue \\
-    \hline                                     
-    \rowfont{\color{blue}}       & 53498    & \civ      &  511$\pm$13    &   9593$\pm$287        &  1172$\pm$74      & 15.9$\pm$0.4      & $-1.64\pm0.01$       &  QSFit         \\    %% (NPR) 
-    \rowfont{\color{blue}}       & 53498    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    & 30.1$\pm$1.21    & $-1.47\pm0.08$       &  Shen2011 \\
-    \rowfont{\color{blue}}       & 53498    & \civ      &   403                  &   5119$^{(a)}$             &    ---                     &  ---                        &  ---                         &  DR12 SAS   \\
-                                             & 53498     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    & 25.10$\pm$0.59    & $-1.65\pm0.01$      &  QSFit          \\  %% (NPR) 
-                                             & 53498    & \ciii       &   144                 &   5119$^{(a)}$             &  ---                       &   ---                       &  ---                          &  DR12 SAS  \\
-  \rowfont{\color{teal}}         & 53498     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     & 26.66$\pm$1.65    &   $-1.65\pm0.01$    &  $^{(d)}$QSFit  \\  %% (NPR) 
-  \rowfont{\color{teal}}         & 53498     & \mgii     &  284                  &   4730$\pm$314       &  $-179\pm188$     & 32$\pm$3.88         &  $-1.87\pm0.06$     &  Shen2011 \\
- \multirow{2}{*}{{\bf J1205+3422}}  
-                &     \textcolor{teal}{53948}     & \textcolor{teal}{\mgii}   & \textcolor{teal}{130} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\
-                                 \cdashline{2-9}
-                                            & 58538     & \lya      & 952$\pm$1.1    & 12242$\pm$15    &  $-1679\pm6$          &  165$\pm$0.2        &  ---                       &   QSFit  \\    %% (MJG)
-   \rowfont{\color{blue}}       & 58538     & \civ      & 1037$\pm$5    & $>$15000             &  983$\pm$40            &  ---                        &  ---                       &   QSFit  \\   %% (NPR)
-                                            & 58538      & \ciii     &  167$\pm$0.9  & $>$15000            &  2734$\pm$46            &     45$\pm$0.2       &  ---                       &  QSFit  \\    %% (MJG)
-    \rowfont{\color{teal}}      & 58538     & \mgii    &  216$\pm$1.4  & 13940$\pm$94    & $-465.2\pm38$         &  88$\pm$0.6	    &  ---                       &   QSFit  \\    %% (MJG)
-                                          \cdashline{2-9}
-                                           & 58693     & \lya     &  271$\pm$0.9    & 9637$\pm$52     &  $-447\pm13$          &  85.1$\pm$0.3          & ---                        &   QSFit  \\    %% (MJG)
-    \rowfont{\color{blue}}    & 58693     & \civ      &   52$\pm$0.9    & 5046$\pm$26     &   1053$\pm$17         &   24.0$\pm$0.2          & ---                        &  QSFit \\     %% (MJG)
-                                           & 58693     & \ciii     &   59$\pm$0.9    & 10751$\pm$        &  1097$\pm$77         &   36$\pm$0.6             & ---                        &  QSFit   \\    %% (MJG)
-   \rowfont{\color{teal}}      & 58693     & \mgii    &  69$\pm$1.5    & 14983$\pm$346   &  $-190\pm134$       &    72$\pm$1.6           & ---                        &  QSFit   \\    %% (MJG)
-\hline
-                                                & 54553     & \lya      & 188                 &  3207                     &    ---                        &   ---                         & ---                    &   DR12 SAS  \\
-   \rowfont{\color{blue}}          & 54553     & \civ      & 257$\pm$13   &  4550$\pm$371     &   55$\pm$450         &   31.8$\pm$1.5     &                                &  $^{(d)}$QSFit  \\   %% (NPR)
-   \rowfont{\color{blue}}          & 54553     & \civ      & 281                  &    4181$\pm$736   &    680$\pm$133       & 100.5$\pm$12  & $-0.14\pm0.68$        &  Shen2011   \\
-   \rowfont{\color{blue}}          & 54553     & \civ      & 170                  &   4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\    %% (NPR)
-                                                & 54553     & \ciii     &  130$\pm$10   &  3852$\pm$402    &  $-236\pm565$       &  36.7$\pm$2.8          &  $-1.47\pm0.20$    &  $^{(d)}$QSFit  \\
-                                                & 54553     & \ciii     &  61                    &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\    %% (NPR)
-    \rowfont{\color{teal}}          & 54553      & \mgii  &  139                  &  4757$\pm$2224   &  $-944\pm568$        &   119$\pm$40          &  $-1.49\pm0.54$    &  Shen2011   \\
-    \rowfont{\color{teal}}          & 54553      & \mgii  &  69                    &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\   %% (NPR)
-                                                \cdashline{2-9}
-                                                & 55832     & \lya     & 288$\pm$11    &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99   &                               &   QSFit  \\
-                                                & 55832     & \lya     & 234                  &  4165.6$^{(a)}$         &    ---                       &   ---                         & ---                         &   DR12 SAS  \\    %% (NPR)
-\multirow{2}{*}{\bf {J1638+2827}}
- & \textcolor{blue}{55832} & \textcolor{blue}{\civ}    & \textcolor{blue}{63$\pm$3}  &   \textcolor{blue}{6052$\pm$250}  &  \textcolor{blue}{-117$\pm$103}  &  \textcolor{blue}{43.2$\pm$1.7}  &  \textcolor{blue}{-2.25$\pm$0.05} & QSFit    \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---               &    5210$\pm$226     &    ---                       &   42.8$\pm$2.0         & $-3.35$                 &     Ham17  \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &  46                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\
-                                                 & 55832     & \ciii     & 15$\pm$5     &  11421$\pm$3654   &   $>$3000                &   14.8$\pm$4.5         &  $-2.25\pm0.05$   &        QSFit \\
-                                                 &  55832    &  \ciii    &  11                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                       &   DR12 SAS \\
-    \rowfont{\color{teal}}           &  55832     & \mgii   &  13                &     5385$^{(a)}$         &  ---                           &   ---                          &  ---                       &   DR12 SAS\\
-                                               \cdashline{2-9}
-                                               & 58583       & \lya    &  785$\pm$1      & 4956$\pm$4    	&   $-641\pm2$            &   90$\pm$0.1   	  &  ---                          &  QSFit  \\ %% (MJG)
-   \rowfont{\color{blue}}         & 58583      & \civ      &  311$\pm$1     & 5739$\pm$14	 &  $-167\pm6$             &   58$\pm$0.1          & ---                          &   QSFit  \\  %% (MJG)
-                                               & 58583      & \ciii      &  52$\pm$0.8   &  3917.4	68.837      &  1514$\pm$127        &  124$\pm$2             & ---                          &   QSFit \\   %% (MJG)
-   \rowfont{\color{teal}}           & 58583      & \mgii   &  157$\pm$2    &  10565$\pm$129    &  $-450\pm52$          &   92$\pm$1              & ---                          &   QSFit  \\  %% (MJG)
-\hline
-    \rowfont{\color{blue}}         &  56189     & \civ    &   32$\pm$3.5   &   7663$\pm$881       &    538$\pm$352       &   50.2$\pm$5.6      & ---                        &    QSFit  \\
-    \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &   2994$\pm$620       &     ---                       &   42.2$\pm$5.6      & -1.59                      &    Ham17  \\
-    \rowfont{\color{blue}}         &  56189     & \civ    &   19                  &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                        &   DR12 SAS  \\
-                                               &  56189      &  \ciii   &  34$\pm$6       &  13748$\pm$2869    &   1851$\pm$1140    &  63$\pm$12          &  $-0.46\pm0.21$    &   QSFit  \\
-                                               &  56189      & \ciii    &  7                     &     5218$^{(a)}$          &  ---                         &     ---                     & ---                         &   DR12 SAS \\
-    \rowfont{\color{teal}}          & 56189      & \mgii  &  25$\pm$6       &   7253$\pm$1712     &   $-931\pm708$      &  51$\pm$10.95      &  $-0.46\pm0.21$   &   QSFit   \\
-    \rowfont{\color{teal}}         &  56189      &  \mgii &  13                   &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                       &   DR12 SAS \\
-                                                  \cdashline{2-9}
-                                              & 56960         & \lya    & 121$\pm$38     & 3580$\pm$673       &     -16$\pm$171     &  13.52 $\pm$4.21    & ---                        &   QSFit   \\  
-\multirow{2}{*}{{\bf J2228+2201}}
-           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}  & \textcolor{blue}{229$\pm$4}      &  \textcolor{blue}{8911$\pm$169}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{46.8$\pm$0.9}    & ---    & \textcolor{blue}{QSFit}     \\
-                                               & 56960    & \ciii      & 185$\pm$5        &        -                      &  2701$\pm$225      &   47.75$\pm$1.29     & ---                      &   QSFit    \\
-   \rowfont{\color{teal}}           & 56960    & \mgii   &   99$\pm$4        &  7312.6$\pm$340   &   188$\pm$137      &   50.75$\pm$2.21     & ---                      &   QSFit   \\
-                                               \cdashline{2-9}
-                                               & 58693     & \lya      &  447$\pm$5       & 8133$\pm$93       &   613$\pm$130       &        56$\pm$0.6     &  ---                    	 &   QSFit  \\%% (MJG)
-     \rowfont{\color{blue}}        & 58693     & \civ      &  41$\pm$1        &  4914$\pm>$65    &   160$\pm$27         &   25$\pm$0.3          & ---                         & QSFit   \\  %% (MJG)
-                                               & 58693     & \ciii      & 107$\pm$1.2    &  $>$15000             &  2422$\pm$67        &   ---                       & ---                          &  QSFit    \\  %% (MJG)
-     \rowfont{\color{teal}}        & 58693     & \mgii    & 177$\pm$1.1    &  $>$15000             &  1000$\pm$2617    &   16$\pm$36         & ---                           &   QSFit  \\  %% (NPR) 
-\hline
-\hline
-     %    \end{tabular}
-    \end{tabu}
+  \input{emission_line_comparison_tab}
+
   \caption{Line Measurement information for the nine epochs for the 3 quasars.
@@
     procedure \citep{Bolton2012}. 
-      %$^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
+    % $^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
     Positive values of Voff means the line is blueshifted.

### 2019-11-10 plots/spectra_schematic/spectra_schematic.py
Sometimes you have to work on the weekend ;-)

@@ -1,119 +1,0 @@
-'''
-A plot with an e.g. the UV/blue/red quasar spectrum (straight from
-Vanden Berk et al. (2001) with the given emission lines, and their
-Ionization Energies.
-'''
-
-import numpy as np
-from astropy.io          import ascii
-
-import matplotlib.lines    as mlines
-import matplotlib.pyplot   as plt
-import matplotlib.gridspec as gridspec
-
-from matplotlib          import colors as mcolors
-from matplotlib.gridspec import GridSpec
-from matplotlib.patches  import Rectangle
-
-
-
-path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/plots/spectra_schematic/'
-
-##
-## Vanden_Berk composite spectrum
-##
-spectrum_file = 'Vanden_Berk01_Table1.dat'
-spectrum = ascii.read(path+spectrum_file)
-
-wave    = spectrum['Wave']
-flux    = spectrum['FluxD']
-fluxerr = spectrum['e_FluxD']
-
-##
-## Emission Line list
-## "EMISSION-LINE VELOCITY SHIFTS RELATIVE TO [O III] 5007"
-##
-linelist_file = 'Vanden_Berk01_Table4.dat'
-linelist = ascii.read(path+linelist_file)
-
-
-##  S E T T I N G    U P   T H E    P L O T 
-fig, ax = plt.subplots(figsize=(14, 8), dpi=200, facecolor='w', edgecolor='k')
-
-##  Dark background :-) 
-plt.style.use('dark_background')
-
-##  Get things looking "tex-y"
-plt.rcParams['text.usetex'] = True
-
-## Adjusting the Whitespace for the plots
-left   = 0.10   # the left side of the subplots of the figure
-right  = 0.98   # the right side of the subplots of the figure
-bottom = 0.18   # the bottom of the subplots of the figure
-top    = 0.96   # the top of the subplots of the figure
-wspace = 0.26   # the amount of width reserved for blank space between subplots
-hspace = 0.06   # the amount of height reserved for white space between subplots
-plt.subplots_adjust(left=left, bottom=bottom, right=right, top=top, wspace=wspace, hspace=hspace)
- 
-## Some NPR defaults
-alpha           = 1.0
-fontsize        = 16
[…]

### 2019-11-10 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py
big update for plots/schematic/*

@@ -20,7 +20,6 @@ import matplotlib.lines  as mlines
 
 ## Setting up the cosmology
 cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                         
-
 ## Reading in the data
 path      = '../../../data/CLQ_line_measurements/'
 filename  = 'Baldwin_CIV.dat'
@@ -31,7 +30,12 @@ CLQs_FWHM       = CLQs['FWHM']    / 1000.
 CLQs_errFWHM    = CLQs['errFWHM'] / 1000.
 CLQs_logREW     = np.log10(CLQs['REW'])
 CLQs_logerrREW  = np.log10(CLQs['errREW'])
-CLQs_loglineLum = np.log10(CLQs['lineLum']*1e42)   
+CLQs_loglineLum = np.log10(CLQs['lineLum']*1e42)
+CLQs_logContLum = np.log10(CLQs['contLum']*1e42)
+
+## To ``normalize'' to 10^42 erg s^-1
+CLQs_loglineLum = CLQs_loglineLum - 42.
+CLQs_logContLum = CLQs_logContLum - 42.
     
 
 ##  Hamann et al. (2017) and Kozłowski (2017) merged BOSS DR12 catalog
@@ -190,11 +194,9 @@ R_sq          = str(np.around((r_value**2), decimals=3))
         
 
 ## AXES LIMITS 
-#xmin =  44.8   ##                   - ( log_LBol.max()-log_L1350.max())
-#xmax =  log_LCont_QSFit.max() ## log_LBol.max()   ## can be e.g. 48.4 for log_LBol
-xmin =  1.67   ##                   - ( log_LBol.max()-log_L1350.max())
-xmax =  5.2   ## log_LCont_QSFit.max() ## log_LBol.max()   ## can be e.g. 48.4 for log_LBol
-ymin =  0.5
+xmin =  2.30   
+xmax =  5.55    ## log_LCont_QSFit.max() ## log_LBol.max()   ## can be e.g. 48.4 for log_LBol
+ymin =  0.4
 ymax =  2.9    ## when in '000 km s^-1;  3.4 when the Legend handles has the # and slope line
 ax.axis([xmin, xmax, ymin, ymax])
 
@@ -213,8 +215,6 @@ ax.tick_params(axis='both', which='minor', labelsize=labelsize)
 ##
 ##
 ##
[…]

### 2019-11-10 plots/schematic/spectra_schematic.py

@@ -1,0 +1,119 @@
+'''
+A plot with an e.g. the UV/blue/red quasar spectrum (straight from
+Vanden Berk et al. (2001) with the given emission lines, and their
+Ionization Energies.
+'''
+
+import numpy as np
+from astropy.io          import ascii
+
+import matplotlib.lines    as mlines
+import matplotlib.pyplot   as plt
+import matplotlib.gridspec as gridspec
+
+from matplotlib          import colors as mcolors
+from matplotlib.gridspec import GridSpec
+from matplotlib.patches  import Rectangle
+
+
+
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/plots/spectra_schematic/'
+
+##
+## Vanden_Berk composite spectrum
+##
+spectrum_file = 'Vanden_Berk01_Table1.dat'
+spectrum = ascii.read(path+spectrum_file)
+
+wave    = spectrum['Wave']
+flux    = spectrum['FluxD']
+fluxerr = spectrum['e_FluxD']
+
+##
+## Emission Line list
+## "EMISSION-LINE VELOCITY SHIFTS RELATIVE TO [O III] 5007"
+##
+linelist_file = 'Vanden_Berk01_Table4.dat'
+linelist = ascii.read(path+linelist_file)
+
+
+##  S E T T I N G    U P   T H E    P L O T 
+fig, ax = plt.subplots(figsize=(14, 8), dpi=200, facecolor='w', edgecolor='k')
+
+##  Dark background :-) 
+plt.style.use('dark_background')
+
+##  Get things looking "tex-y"
+plt.rcParams['text.usetex'] = True
+
+## Adjusting the Whitespace for the plots
+left   = 0.10   # the left side of the subplots of the figure
+right  = 0.98   # the right side of the subplots of the figure
+bottom = 0.18   # the bottom of the subplots of the figure
+top    = 0.96   # the top of the subplots of the figure
+wspace = 0.26   # the amount of width reserved for blank space between subplots
+hspace = 0.06   # the amount of height reserved for white space between subplots
+plt.subplots_adjust(left=left, bottom=bottom, right=right, top=top, wspace=wspace, hspace=hspace)
+ 
+## Some NPR defaults
+alpha           = 1.0
+fontsize        = 16
[…]

### 2019-11-10 plots/spectral/CIV_fits.py

@@ -101,7 +101,8 @@ alpha           = 1.0
 fontsize        = 16
 labelsize       = fontsize
 tickwidth       = 2.0
-linewidth       = 1.4
+linewidth       = 1.0 ## 1.4
+beefup          = 2.2
 tickwidth       = 2.0
 ticklength      = 6.0
 ticklabelsize   = labelsize
@@ -156,7 +157,7 @@ center     = 1549.48                         ## line center for CIV, Angstrom
 print()
 print("qsfit['FILENAME'][ii], '     ',  qsfit['LUM'][ii], qsfit['FWHM'][ii], qsfit['VOFF'][ii]")
 for ii in range(len(qsfit)):
-    print(qsfit['FILENAME'][ii], '       ', qsfit['NCOMP'][ii],  qsfit['LUM'][ii], qsfit['FWHM'][ii], qsfit['VOFF'][ii])
+    print(ii, qsfit['FILENAME'][ii], '       ', qsfit['NCOMP'][ii],  qsfit['LUM'][ii], qsfit['FWHM'][ii], qsfit['VOFF'][ii])
     if ii == 0:
         #j=0; k=0
         norm       = qsfit['LUM'][ii]                ## 10^42 erg s^-1
@@ -171,7 +172,7 @@ for ii in range(len(qsfit)):
         line_profile = (peak_value * (np.exp( -((J12_first_wave - x0) / sigma)**2 / 2.)))+cont_off
 
         ax1.plot(J12_first_wave,  J12_first_flux, '-b', lw=linewidth)
-        ax1.plot(J12_first_wave,  line_profile,   '-b', lw=linewidth)
+        ax1.plot(J12_first_wave,  line_profile,   '-b', lw=beefup)
 
         norm_str = str(np.around(norm, decimals=3))
         fwhm_str = str(np.around(fwhm, decimals=3))
@@ -198,7 +199,7 @@ for ii in range(len(qsfit)):
         line_profile = (peak_value * (np.exp( -((J12_second_wave - x0) / sigma)**2 / 2.)))+cont_off
 
         ax2.plot(J12_second_wave, J12_second_flux, '-r', lw=linewidth)
-        ax2.plot(J12_second_wave, line_profile,    '-r', lw=linewidth)
+        ax2.plot(J12_second_wave, line_profile,    '-r', lw=beefup)
 
         norm_str = str(np.around(norm, decimals=3))
[…]

### 2019-11-10 tex/other_tex/CIV_CLQs_20191108.tex
Big, BIG tex/ update

--- 2019-11-08 tex/other_tex/201911/CIV_CLQs_20191107.tex
@@
 inspection shows strong broad \civ\ emission, so we disable the check on the mask,
-and report the line fits in Table~\ref{tab:LineMeasurement}
+and report the line fits in Table~\ref{tab:LineMeasurements} and show the \civ\ line 
+fits in~\ref{fig:CIV_LineFits}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=8.5cm, trim=0.4cm 0.4cm 0.2cm 0.4cm, clip]
+  {figures/CIV_fits_20191108.png}
+   \vspace{-12pt}
+   \caption[]{The \civ\ emission line and the subsequent QSFit model and
+     parameters.}
+\end{figure}
 
@@
   \centering
-  \input{emission_line_comparison_tab}
-
-  \caption{Line Measurement information for the nine epochs for the 3 quasars.
-    Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM and $V_{\rm off}$ in km s$^{-1}$,
-    where positive values of $V_{\rm off}$ means the line is blueshifted.
-    Equivalent widths are \AA\.  
-    Shen11 is \citet{Shen2011}. 
-    Ham17 is \citet{Hamann2017}.
-    DR12 SAS is the line measurement information from the SDSS DR12 
-    Science Archive Server (SAS).
-    $^{(a)}$Emission lines of a common ``width group'', in this case,
-    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
-    the same intrinsic velocity width in the SDSS spectral line fitting
-    procedure \citep{Bolton2012}. 
-    % $^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
-    Positive values of Voff means the line is blueshifted.
-    % $^{(b)}$Bit 3: FWHM value hits a limit in the fit
-    Notes: QSFit does not fit the \mgii line for J1638+2827 MJD
-    54553 or 55832. QSFit does not fit the \civ line for J2228+2201 MJD 56189.
-    $^{(d)}$Emission line modelled with two components.
-    The different colours of text are merely for readability.
-    }
+  % \input{emission_line_comparison_tab}
+  \input{emission_line_tab}
+  \caption{Line Measurement information for the nine epochs for the 3
+    quasars.  Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM
+    and $V_{\rm off}$ in km s$^{-1}$, where positive values of $V_{\rm
+      off}$ means the line is blueshifted.  Equivalent widths are in units
+    of \AA\ .  Positive values of V$_{\rm off}$ means the line is
+    blueshifted.  All measuremennts are from QSFIT, except for J1638+2827
+    (MJD 54553) which are from \citet{Shen2011}.  $^{(d)}$Emission line
+    modelled with two components.}
  \label{tab:LineMeasurements}
@@
     \hline
-                              &                                     &                                       &                                               &                             &                                &                  &                  & \\
-    M87$^{*}$          &  57854	                     & ---                                &   43.187	                               & \multicolumn{2}{c}{9.812$\pm$0.044}    & 	\multicolumn{2}{c}{-4.699}   & EHT \\
-                                  &                                     &                                       &                                               &                             &                                &                  &                  & \\
+%                              &                                     &                                       &                                               &                             &                                &                  &                  & \\
+ %   M87$^{*}$          &  57854	                     & ---                                &   43.187	                               & \multicolumn{2}{c}{9.812$\pm$0.044}    & 	\multicolumn{2}{c}{-4.699}   & EHT \\
+  %                                &                                     &                                       &                                               &                             &                                &                  &                  & \\
      \hline
@@
         Shen11 is \citet{Shen2011}. 
-        Kozl17 is \citet{Kozlowski2017}.
-        EHT is \citet{EHT2019_PaperV}.      }
+        Kozl17 is \citet{Kozlowski2017}. }
 \label{tab:Eddington_ratios} 
@@
 %%
-There is an anti-correlation between the emission-line REWs and e.g. 1450\AA\ rest continuum luminosity,
-so that as the underlying UV continuum luminosity increases, the EW decreses,
-see Figure~\ref{fig:CIV_Baldwin}
-Our Figure~\ref{fig:CIV_Baldwin} is a reproduction of Figure~15 from \citet{Calderone2017}.
+There is an anti-correlation between the emission-line REWs and
+e.g. 1450\AA\ rest continuum luminosity, so that as the underlying UV
+continuum luminosity increases, the EW decreses, see
+Figure~\ref{fig:CIV_Baldwin} Our Figure~\ref{fig:CIV_Baldwin} is a
+reproduction of Figure~15 from \citet{Calderone2017}.
 
-The plotted values are \verb|CONT1450\_\_LUM| and \verb|BR\_CIV\_1549\_\_\EW|.
-\verb|CONT1\_\_LUM| is the $\nu L_{\nu}$ luminosity at wavelength
-%{\tt CONT1\_\_WAVE}, and the latter is always within the observed wavelength range, hence it is always present.
-We use the v1.2.4 of the QSFIT catalogue, applying the cuts: {\tt BR\_CIV\_1549\_\_LUM} $>0$ \&\& {\tt BR\_CIV\_1549\_\_EW} $>0$.
-This selects 20,374 quasars.
-%On the other hand, CONT1450__LUM is estimated at 1450AA (rest frame), hence it is available only if 1450AA is within the available
-%wavelength range.  For SDSS data, CONT1450__LUM is available only if $z> 1.83$.
+The plotted values are \verb|CONT1450__LUM| and
+\verb|BR_CIV_1549__EW|.  \verb|CONT1__LUM| is the $\nu L_{\nu}$
+luminosity at wavelength. This selects 20,374 quasars.  The slope
+$\beta$ is $-0.1997$.  Checking with \citet{Kozlowski2017}, using
+their bolometric luminosity gives a slope of $\beta=-0.251$, in line
+with that from \citet{Hamann2017} ($\beta=-0.23$).
+%%
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
+sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
 
-The slope $\beta$ is $-0.1997$. 
-Checking with \citet{Kozlowski2017}, using their bolometric luminosity gives a slope of $\beta=-0.251$,
-in line with that from \citet{Hamann2017} ($\beta=-0.23$.
+Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
+at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
+in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
+nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
+nulla. Nullam eu augue id purus mollis dignissim sed et
+libero. Phasellus eget justo sed neque pellentesque egestas nec id
+arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
+vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
+imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
+neque id mi ultrices tristique. Integer quam libero, ornare vel
+gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
+cursus, dui nisl egestas augue, non fermentum nisl est nec
+nisi. Vestibulum nec mi justo, eget dapibus velit.
 
@@
 \end{figure}
-
-%{\bf Our Eddington ratios \\
-%Done 1\% \\
-%Coatman, Hewett say \civ\ masses are okay.\\
-%But what are these Eddington ratios? \\
-%Low state BHs vs. High-mass BHs... \\
-%Coatman et al?? Blue-shiftted \\ }
 \section{Discussion}
@@
   \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_20191104v3.png}
+  {figures/CIV_CLQs_Baldwin_20191108.png}
    \vspace{-12pt}
    \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
-     commonly referred to as The Baldwin Plot. The continuum luminosities are
-     from \citet{Kozlowski2017},
+     commonly referred to as The Baldwin Plot.
+     The continuum luminosities are  from \citet{Calderone2017},
      the REW measurements are Table~\ref{tab:Baldwin}.}
@@
 quasars in Table~\ref{tab:Eddington_ratios}.
+%%
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
+sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
 
-%\subsection{Variability around billion solar mass black holes} 
-The Event Horizon Telescope (EHT) mapped the central compact radio
-source of the elliptical galaxy M87 at 1.3 mm \citep{EHT2019_PaperI,
-EHT2019_PaperII, EHT2019_PaperIII, EHT2019_PaperIV, EHT2019_PaperV,
-EHT2019_PaperVI} .
+Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
+pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
+id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
+dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
+euismod. Cras vel auctor neque. Nam quis diam risus.
 
-The EHT observsations confirm the observed 1.3mm asymmetric ring
-emission is consistent with predictions of strong
-gravitational lensing of synchrotron emission from a hot plasma
-orbiting near the black hole event horizon \citep{EHT2019_PaperV}.
-
-EHT2017 data includes tracks from four separate
-days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{EHT2019_PaperIV} timescale is short
-compared to the decorrelation timescale of simulated images, which is
-$\sim$50 $r_{g}$ $c^{-1}$, and smaller than the light-crossing time of the source
-plasma.
-
-From \citet{EHT2019_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
-\begin{equation}
-R_{s} = 2 r_{g} =  2 GM/c^{2}  = 9.598 \times10^{12} {\rm m}.
-\end{equation}
-giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c =$
-32,015 secs (0.37 days).
-
-$\log_{10} (M_{\rm M87^{*}} / M_{\odot} ) = 9.813$.  which is only
-about double that of J1205+3422 or J2228+2201, and a factor of $\sim$6
-that of J1638+2827.  However, M87 has an Eddington accretion rate of
-$\approx$140 $M_{\odot}$ yr$^{-1}$, and thus an Eddington ratio of
-$\dot{M} / \dot{M}_{\rm Edd} \sim 2 \times 10^{-5}$, i.e. $\eta_{\rm
-Edd} = -4.699$.  \citep[assuming the canonical accretion radiative
-efficiency of 10\%; ][]{DiMatteo2003a, EHT2019_PaperV}.
+Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
+at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
+in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
+nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
+nulla. Nullam eu augue id purus mollis dignissim sed et
+libero. Phasellus eget justo sed neque pellentesque egestas nec id
+arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
+vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
+imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
+neque id mi ultrices tristique. Integer quam libero, ornare vel
+gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
+cursus, dui nisl egestas augue, non fermentum nisl est nec
+nisi. Vestibulum nec mi justo, eget dapibus velit.
 

### 2019-11-11 plots/perObject/J1638p2827_landscape_v1pnt0.py
polish up updated

@@ -52,6 +52,25 @@ NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
 
 
 ##    S P E C T R A 
+##    SDSS
+sdssname        = 'spec-2948-54553-0614.fits'
+sdss_data       = fits.open(path+sdssname)
+sdss_spectrum   = sdss_data[1].data
+sdss_flux       = sdss_spectrum.flux
+sdss_loglam     = sdss_spectrum.loglam
+sdss_wavelength = 10**(sdss_loglam)
+sdss_mjd        = sdss_data[2].data['MJD'][0]
+
+bossname        = 'spec-5201-55832-0178.fits'
+#bossname        = 'spec-5201-55832-0178_v5_10_0.fits'
+boss_data       = fits.open(path+bossname)
+boss_spectrum   = boss_data[1].data
+boss_flux       = boss_spectrum.flux
+boss_loglam     = boss_spectrum.loglam
+boss_wavelength = 10**(boss_loglam)
+boss_mjd        = boss_data[2].data['MJD'][0]
+
+##  L R I S    data
 infile   = 'LRIS_J1638p2827_b_58583.dat'
 LRIS_b  = ascii.read(path+infile)
 infile   = 'LRIS_J1638p2827_r_58583.dat'
@@ -73,22 +92,6 @@ LRIS_r_wavelength = LRIS_r['wavelength']
 LRIS_b_flux   = (2.99792458E+21 * (LRIS_b['flux_density'] / 1000.)) / (LRIS_b['wavelength']**2)  / 1e-17
 LRIS_r_flux   = (2.99792458E+21 * (LRIS_r['flux_density'] / 1000.)) / (LRIS_r['wavelength']**2)  / 1e-17
 
-##    SDSS
-sdssname        = 'spec-2948-54553-0614.fits'
-sdss_data       = fits.open(path+sdssname)
-sdss_spectrum   = sdss_data[1].data
-sdss_flux       = sdss_spectrum.flux
-sdss_loglam     = sdss_spectrum.loglam
-sdss_wavelength = 10**(sdss_loglam)
-sdss_mjd        = sdss_data[2].data['MJD'][0]
-
-bossname        = 'spec-5201-55832-0178_v5_10_0.fits'
-boss_data       = fits.open(path+bossname)
-boss_spectrum   = boss_data[1].data
-boss_flux       = boss_spectrum.flux
[…]

### 2019-11-11 plots/perObject/J2228p2201_landscape_v1pnt0.py

@@ -52,6 +52,25 @@ NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
 
 
 ##    S P E C T R A 
+##  It's actaully a BOSS spectrum, but let's just call it SDSS for
+##  ease of variable...
+sdssname        = 'spec-6118-56189-0720.fits'
+sdss_data       = fits.open(path+sdssname)
+sdss_spectrum   = sdss_data[1].data
+sdss_flux       = sdss_spectrum.flux
+sdss_loglam     = sdss_spectrum.loglam
+sdss_wavelength = 10**(sdss_loglam)
+sdss_mjd        = sdss_data[2].data['MJD'][0]
+
+bossname        = 'spec-7582-56960-0790.fits'
+boss_data       = fits.open(path+bossname)
+boss_spectrum   = boss_data[1].data
+boss_flux       = boss_spectrum.flux
+boss_loglam     = boss_spectrum.loglam
+boss_wavelength = 10**(boss_loglam)
+boss_mjd        = boss_data[2].data['MJD'][0]
+
+##  DBSP spectrum
 infile   = 'DBSP_J2228p2201_b_58693.dat'
 DBSP_b  = ascii.read(path+infile)
 infile   = 'DBSP_J2228p2201_r_58693.dat'
@@ -73,23 +92,6 @@ DBSP_r_wavelength = DBSP_r['wavelength']
 DBSP_b_flux   = (2.99792458E+21 * (DBSP_b['flux_density'] / 1000.)) / (DBSP_b['wavelength']**2)  / 1e-17
 DBSP_r_flux   = (2.99792458E+21 * (DBSP_r['flux_density'] / 1000.)) / (DBSP_r['wavelength']**2)  / 1e-17
 
-##  It's actaully a BOSS spectrum, but let's just call it SDSS for
-##  ease of variable...
-sdssname        = 'spec-6118-56189-0720.fits'
-sdss_data       = fits.open(path+sdssname)
-sdss_spectrum   = sdss_data[1].data
-sdss_flux       = sdss_spectrum.flux
-sdss_loglam     = sdss_spectrum.loglam
-sdss_wavelength = 10**(sdss_loglam)
-sdss_mjd        = sdss_data[2].data['MJD'][0]
-
-bossname        = 'spec-7582-56960-0790.fits'
[…]

### 2019-11-12 tex/CIV_CLQs.tex
Inntroduction BIG update

@@
  Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
-\newauthor and Daniel Stern$^{6}$ 
+\newauthor Daniel Stern$^{6}$ and Giorgio Calderone$^{7}$
 \\
@@
 $^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
+$^{7}$INAF -- Osservatorio Astronomico di Trieste, Via Tiepolo 11, I-34143 Trieste, Italy \\
 }
@@
 We report on three redshift $z>2$ quasars with dramatic changes in
-their \civ\ emission lines, the first `Changing-Look'' quasars at high
+their \civ\ emission lines, the first ``Changing-Look'' quasars at high
 redshift.  This is also the first time the changing-look behaviour has
@@
 Although line measurements from the three quasars show large changes
-in the \civ\ line flux-line width plane, the quasars are not seen to
+in the \civ\ flux-line width plane, the quasars are not seen to
 be outliers when considered against the full $z\sim2$ quasar population
@@
 Luminous AGN, i.e. quasars, are now seen to significantly vary their
-energy output on timescales of weeks to months.  This observation, and
-the subsequent mismatch in the expected ``viscous'' timescale, which
-for a $\approx$10$^{7}$ M$_{\odot}$ central supermassive black hole
-(SMBH) is $\sim$hundreds of years, was noted over 30 years ago
+energy output on timescales as short as weeks to months.  This
+observation, and the subsequent mismatch in the expected ``viscous''
+timescale, which for a 10$^{7}$ M$_{\odot}$ central supermassive black
+hole (SMBH) is $\sim$hundreds of years, was noted over 30 years ago
 \citep[e.g.][]{Alloin1985}. However, with new photometric light-curve
 and repeat spectroscopic data, the desire for a deeper understanding
-of AGN accretion disk physics has been recently re-invigorated the
-field \citep[e.g.][]{Lawrence2018, Antonucci2018}.
+of AGN accretion disk physics has recently re-invigorated the field
+\citep[e.g.][]{Antonucci2018, Lawrence2018, Ross2018, Stern2018}.
 
@@
 community uses both these terms as a cover for the underlying
-physics. For sake of argument, ``Changing Look'' quasars can
-potentially be thought of as the extension to the BELs of quasar
-continuum variability \citep[e.g., ][]{MacLeod2012} whereas the
-``Changing State'' quasars (CSQs) have a `state-transition' similar to
+physics. For sake of argument, CLQs can potentially be thought of as
+the extension to the BELs of quasar continuum variability \citep[e.g.,
+][]{MacLeod2012} whereas the CSQs have a `state-transition' similar to
 that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019}. In
 this paper, we use the term `Changing Look', as we are currently
-agnostic, and somewhat ignorant, to the underlying physical processes.
+agnostic, and confessedly ignorant, to the underlying physical
+processes.
 
-These CLQs have primarily been defined according to the
+\begin{table*}
+  \begin{centering}
+    \begin{tabular}{l r  r r   lll lll  r r}
+      \hline  \hline 
+      Line                 & $\lambda$ &  Transition  & Ionization   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
+%                              &    / \AA\    &      / eV             &  / eV            &   Lower                  & Conf.
+&  $J$       & Upper                      &  Conf.
+& $J$       & / cm$^{-1}$    &  / s$^{-1}$                \\      \hline
+                              &  / \AA\    & energy / eV &  energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & ($\times10^{8}$  / s$^{-1}$)               \\      \hline
+      H LyLim           &   912.324   & 13.5984    & 13.5984        & 1$s$                    & $^2$S     & 1/2          & $\infty$                  &                                 &             & 109 678.7       & 1.23$\times10^{-6}$  \\
+      H Ly$\alpha$  &  1215.670  & 10.1988    & 13.5984       & 1$s$                     & $^2$S      & 1/2          & 2                             &                                 &             &  82 259.2       &  4.67  \\
+      \nv                  &  1238.821  & 10.0082    &  97.8901      &  1$s^{2}$2$s$      &  $^{2}$S   &  1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2    &  80 721.9        & 3.40   \\
+      \nv                  &  1242.804  &  9.9762     &  97.8901      &  1$s^{2}$2$s$       &  $^{2}$S   &  1/2        &  1$s^{2}$2$p$         &  $^{2}$P$^{{\rm o}}$ &  1/2     &  80 463.2        & 3.37 \\
+      \civ                 &  1548.187  &  8.0083     &  64.4935      &  1$s^{2}$2$s$       &   $^{2}$S  & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  3/2     &  64 591.7        & 2.65  \\
+      \civ                 &  1550.772  &  7.9950     &  64.4935      & 1$s^{2}$2$s$        &  $^{2}$S   & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  1/2     &   64 484.0       & 2.64  \\
+      \heii               &   1640.474  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  5/2        &  60 958.0       & 10.35 \\
+      \heii               &   1640.490  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  3/2        &  60 958.0       & 1.73 \\
+      \ciii                 &  1906.683  &  6.5026     & 47.8878       & 1$s^{2}$2$s^{2}$   &   $^{1}$S   & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &   2        &   52 447.1       & 5.19$\times10^{-11}$ \\
+      \ciii                 &  1908.734  &  6.4956     & 47.8878       & 1$s^{2}$2$s^{2}$   &  $^{1}$S    & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &  1         &  52 390.8        & 1.14$\times10^{-6}$  \\
+       \mgii              &  2795.528  &  4.4338     & 15.0353       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2     &  35 760.9       & 2.60  \\
+      \mgii               &  2802.705  &  4.4224     & 15.0353       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   1/2     &  35 669.3       & 2.57 \\
+      H Ba $\beta$   &  4861.333  &  2.5497     & 13.5984       & 2                              &                 &               & 4                             &                                 &              &  20 564.8       & 0.0842  \\
+      \hline   
+      \hline
+    \end{tabular}
+    \caption{Strong UV/optical spectral emission lines in quasars, and their atomic data.
+      Data from the NIST Atomic Spectra Database       \citep{Kramida2018, Kramida2019}.
+      The Transition Energies are $E=hc/\lambda$ for the given wavelength. The Ionization Energy is the
+      energy required to ionize the given species, e.g. 64.49 eV are needed to create a \cv\ ion.
+      Transitions Level configurations are given in standard spectroscopic notation
+      %($N^{2s+1}$ $L_{j}$. 
+      $A_{i,j}$ are transition probabilities.
+%      $A_{i,j}$ are \href{https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-6}{transition probabilities}.} 
+%      such that the radiative lifetime $\tau_{k}$ of an atomic level $k$ is related to the sum of transition probabilities to all levels $i$ lower in energy than $k$
+%      The 1548.202 and 1550.774 \AA\ emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition, split by total angular momentum $J= 3/2$ and $1/2$. 
+      Data from the NIST Atomic Spectra Database       \citep{Kramida2018, Kramida2019}.}
+    %% 
+    %%  Mg II Z = 12, Na isoelectronic sequence  
+  \label{tab:atomic_lines}
+  \end{centering}
+\end{table*}
+
+CLQs to date have primarily been defined according to the
 (recombination) Balmer emission line properties with particular
 attention paid to the H$\beta$ emission line, observed from optical
-spectroscopy. Recent work \citep{Guo2019, Homan2019} report on discoveries
-of \mgii Changing-look AGN. However, current CLQ studies have been at
-redshifts $z<1$.
+spectroscopy. Recent work report on discoveries of \mgii Changing-look
+AGN \citep{Guo2019, Homan2019}. However, current CLQ studies have
+primarily been at redshifts $z<1$.
 
-While there have been a slew of studies on triply ionized carbon, i.e
+While there have been many studies on triply ionized carbon, i.e
 \civ, these have tended to focus on broad absorption line quasars
-\citep[BAL QSOs; see Table 1][]{Hemler2019} or the Baldwin Effect
+\citep[BAL QSOs; see Table 1 of][]{Hemler2019} or the Baldwin Effect
 \citep[BEff; ][]{Baldwin1977, Bian2012, Jensen2016,
@@
 global} (or {\it ensemble}) Baldwin Effect, which is an
-anti-correlation between the EW of the emission line and the
+anti-correlation between the Equivalent Width (EW) of the emission line and the
 underlying continuum luminosity of {\it single-epoch} observations of
@@
 AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
-collisionally excited broad {\it emission} line (BEL) of \civ\ (and
-indeed \ciii) have not to this point been seen.
+collisionally excited broad {\it emission} line (BEL) of \civ\ and
+indeed \ciii have not to this point been reported.
 
@@
 
-Here, we report on three quasars  
-which show dramatic changes in their \civ\ and \ciii broad emission
-line properties as well as in the underlying continuum. We claim these
-are the first examples of ``Changing Look Quasars'' at high ($z>1$)
+Here, we present new results for three quasars which show dramatic
+changes in their \civ\ and \ciii broad emission line properties as
+well as in their underlying continuum. These are some of the first
+examples of ``Changing Look Quasars'' at high ($z>1$)
 redshift. Moreover, these are the first cases for substantial changes
@@
 potentially by inverse Compton scattering of lower energy photons to
-higher energies.  Furthermore, the measured rest-wavelengths of
-emission lines in quasar spectra, are known to vary from their nominal
-laboratory wavelengths especially for the high-ionization broad lines \citep[e.g.][]{VandenBerk2001}.
+higher energies.
 
-In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
-the \civ\ doublet \citep{Kramida2018}.  The 1548.202 and 1550.774 \AA\
-emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
-transition, split by total angular momentum $J= 3/2$ and $1/2$,
-resulting in energies 64,591 cm$^{-1}$ and 64,484 cm$^{-1}$,
-respectively \citep[e.g.][]{Moore1993}. The transition probabilities
-of the the 1548 and 1550\AA\ lines are $A_{ki}= 2.65\times10^{8}$ and
-2.64$\times10^{8}$ s$^{-1}$.
+Details of the atomic transitions that produce strong rest-frame
+UV/optical lines in quasars are given in
+Table~\ref{tab:atomic_lines}. In this paper we use the wavelengths of
+1548.202 and 1550.774~\AA\ for the \civ\ doublet
+\citep{Kramida2018}. For ionisation energies, 47.89 eV (3.519 Ry) is
+required for doubly-ionised C~III to become triply-ionised \civ.
+64.49 eV (4.74 Ry) is the energy needed to ionize \civ\ itself. This
+energy corresponds to a thermal temperature of $T \gtrsim$
+4$\times10^{5}$, implying a heating energy source of (soft) X-ray
+photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).
 
-The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. Using the
-\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
-Atomic Spectra Database Ionization Energies Form} for ionisation
-energies, we note 11.3 eV is the energy required for C~I to dislodge
-one electron and become singly-ionised C~II; 24.4 eV is then the
-(`additional') energy needed for singly-ionised C~II to dislodge an
-additional electron, and become doubly-ionised C~III, and 47.89 eV
-(3.519 Ry) is required for doubly-ionised C~III become triply-ionised
-\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
-itself. This energy corresponds to a thermal temperature of $T
-\gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
-X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).  \ciii is the
-1$s2$2$s$2$p$ $^{3}$P$^{\circ}$ to 1$s^{2}$2$s^{2}$ $^{1}$S transition
-(with $J=1\rightarrow0$) resulting in an energy of 52,390.75 cm$^{-1}$ and
-a transition probability of $A_{ki} = 1.14\times10^{2}$ s$^{-1}$ \citep{Wiese1996}.
-
-%%   B a c k g r o u n d     L i t e r a t u r e    
-\civ\ variability has been long studied, e.g., \citet[][]{Baldwin1977,
-Gaskell1982, Gregory1982, Wilkes1986, Espey1989, Espey1990Erratum,
-ZhengSulentic1990, Corbin1990, Corbin1991, Weymann1991,
-Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
-Laor1995, McIntosh1999, Nazarova2003}.
-
-\citet{Wilhite2006} examine the variability of a C~\textsc{iv} sample
+\citet{Wilhite2006} examine \civ\ variability in a sample
 of 105 quasars observed at multiple epochs by the Sloan Digital Sky
 Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
-find a strong correlation between the change in the C~\textsc{iv} line
+find a strong correlation between the change in the \civ\ line
 flux and the change in the line width, but no correlations between the
@@
 is consistent with a model in which a broad line base varies with
-greater amplitude than the line core. The C~\textsc{iv} lines in these
+greater amplitude than the line core. The \civ\ lines in these
 high-luminosity quasars appear to be less responsive to continuum
-variations than those in lower luminosity AGN.  \citet{Wilhite2006}
-find no evidence for variability of the well known blueshift of the
-C~\textsc{iv} line with respect to the low-ionization
-Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects.
+variations than those in lower luminosity AGN.
 
-\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$ SDSS
-quasars, concentrating on the properties of the \civ\ emission
-line. We consider two well-known effects involving the \civ\ emission
-line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
-the BEff) and the blueshifting of the peak of \civ\ emission with
-respect to the systemic redshift. These authors conclude that these
-two \civ\ parameters (EQW and blueshift) are capturing an important
-trade-off between ``disk'' and ``wind'' components in the disk-wind
-model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
-Proga2000}, with one dominating over the other depending on the shape
-of the SED \citep[][strong \civ\ EQW indicates a more ionizing SED and
-large \civ\ blueshift indicating a less ionizing SED ]{Leighly2004b}.
+\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$
+SDSS quasars, concentrating on the properties of the \civ\ emission
+line. These authors consider two well-known effects involving the
+\civ\ emission line: {\it (i)} the anti-correlation between the \civ\
+equivalent widths (EWs) and luminosity (i.e., the Baldwin Effect;
+BEff) and {\it (ii)} the blueshifting of the peak of \civ\ emission
+with respect to the systemic redshift.  We denote the velocity offset
+of emission lines as $V_{\rm off}$ and use the convention that a
+positive $V_{\rm off}$ value means the line is blueshifted while a
+negative $V_{\rm off}$ value means the line is redshifted.
+\citet{Richards2011} find the blueshift of the \civ\ emission line, is
+found to be nearly ubiquitous, with a mean shift of $V_{\rm off}
+\sim$810 km s$^{-1}$ for radio-quiet (RQ) quasars and $V_{\rm off}
+\sim$360 km s$^{-1}$ for radio-loud (RL) objects. \citet{Richards2011}
+also find the BEff is present in both the RQ and RL studied samples.
+%%
+These author conclude
+that these two \civ\ parameters (EQW and blueshift) are capturing an
+important trade-off between ``disk'' and ``wind'' components in the
+disk-wind model of accretion disks \citep[e.g.,][]{Murray1995,
+Elvis2000, Proga2000, Leighly2004b}, with one dominating over the other depending on
+the shape of the SED.
 
-The Sloan Digital Sky Survey Reverberation Mapping Project
-\cite[SDSS-RM; ][]{Shen2015} has a monitored $\sim$350 quasars with
-\civ. Noting the biases associated with \civ Emission Line Properties
-\citep[e.g. increasing systematic offsets with decreasing
-signal-to-noise][]{Denney2016}, \citet{Grier2019} report report
-significant time delays between the continuum and the CIV 1549
-emission line in 52 quasars, and investigate the \civ
-radius-luminosity relationship.
-
-\civ\ is also known to exhibit significant displacements to the
-blue and these `blueshifts' almost certainly signal the presence of
-strong outflows. As a consequence, single-epoch virial black hole (BH)
-mass estimates derived from \civ\ velocity widths are known to be
-systematically biased compared to masses from the hydrogen Balmer
-lines. \citet{Coatman2017} use a large sample of 230 high-luminosity
-($L$Bol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with
-both \civ\ and Balmer line spectra, we have quantified the bias in \civ
-BH masses as a function of the \civ\ blueshift. \civ\ BH masses are
-shown to be a factor of 5 larger than the corresponding Balmer-line
-masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated
-by almost an order of magnitude at the most extreme blueshifts,
-$\gtrsim$5000 km s$^{-1}$.
-
-\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
-Sloan Digital Sky Survey Reverberation Mapping project to investigate
-the dependence of the blueshift of \civ\ relative to \mgii on quasar
-properties. We confirm that high-blueshift sources tend to have low
-\civ\ equivalent widths (EWs), and that the low-EW sources span a range
-of blueshift. Other high-ionization lines, such as He II, also show
-similar blueshift properties. The ratio of the line width (measured as
-both the full width at half maximum and the velocity dispersion) of
-\civ\ to that of \mgii increases with blueshift. Quasar variability
-enhances the connection between the \civ\ blueshift and quasar
-properties (e.g., EW). The variability of the \mgii line center (i.e.,
-the wavelength that bisects the cumulative line flux) increases with
-blueshift. In contrast, the C IV line center shows weaker variability
-at the extreme blueshifts. Quasars with the high-blueshift \civ\ lines
-tend to have less variable continuum emission, when controlling for
-EW, luminosity, and redshift. Our results support the scenario that
-high-blueshift sources tend to have large Eddington ratios.
-Therefore, according to this study, the \civ\ or \heii\ EW is not an
-accurate indicator of the Eddington ratio or quasar SED.
+Using the multi-epoch spectra of 362 quasars from the Sloan Digital
+Sky Survey Reverberation Mapping \citep[SDSS-RM; ][]{Shen2015,
+Shen2019} project, \citet{Sun2018} investigate the blueshift of \civ\
+emission relative to \mgii emission, and its dependence on quasar
+properties.  These authors confirm that high-blueshift sources tend to
+have low \civ\ EWs, and that the low-EW sources span a range of
+blueshift. Other high-ionization lines, such as \heii, also show
+similar blueshift properties. The ratio of the line width of \civ\ to
+that of \mgii increases with blueshift.  \citet{Sun2018} also find
+that quasar variability might slightly enhance the connection between
+the \civ\ blueshift and EW, though further investigation here is
+warranted.  There is also the finding that the objects with that
+largest blueshifts are less variable and tend to have higher Eddington
+ratios.  \citet{Sun2018} explain their results these by suggesting
+that quasar SEDs become {\it softer} with {\it increasing Eddington
+ratio} along with the presence of X-ray shielding by the inner
+accretion disk.  However, a high Eddington ratio alone might be an
+insufficient condition for the \civ\ blueshift.
+%%
 Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
@@
 %%    P a p e r    O v e r v i e w
-The purpose of this paper is, for the first time, to access and 
-report on the Changing-Look quasar phenomenon at high, 
-$z>2$ redshift. By doing so, we move from the low-ionization 
+The purpose of this paper is, for the first time, to systematically access and 
+report on the CLQ phenomenon at high ($z>2$) redshift. By doing so, we move from the low-ionization 
 energy Balmer emission line series to the high-ionization emission 
@@
 This paper is organised as follows. In Section 2, we describe our
-sample selection, catalogs and observational data sets.  In Section 3,
-we present the high-$z$ quasars and report the line properties for the
+sample selection, catalogues, and observational data sets.  In Section 3,
+we show the high-$z$ quasars and report the line properties for the
 quasars at the observed epochs.  We give a very brief theoretical
-discussion in Section 4. We present our Conclusions in Section 5.  We
+discussion in Section 4. We present our conclusions in Section 5.  We
 report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
-Fukugita1996} unless otherwise stated explicitly. For the WISE bands,
+Fukugita1996} unless otherwise stated. For the WISE bands,
 $m_{\rm AB} = m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1
@@
 
-The Balmer series in hydrogen is due to the recombination cascade
-between different principal quantum numbers $n$, and
-the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
-%(and assuming an equilibrium distribution between the angular momentum levels $l$ corresponding to a given $n$).
-%%
-Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
-H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
-Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$. 
-%%
-\civ\ is one of the strongest collisionally excited lines in quasar
-spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
-at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
-canonical BELR parameters deduced over from early analysis of the
-\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
-ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
-speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
-H$^{+}$).
+For the BOSS spectrum of J2228+2201 on MJD 56189, some of the data are
+``masked'' (i.e. they have {\tt and\_mask} != 0) in the FITS file at
+wavelengths $\lesssim$1600\AA\ (rest-frame).  This typically means
+there is some potential problem in using those data. However, visual
+inspection shows strong broad \civ\ emission, so we disable the check on the mask,
+and report the line fits in Table~\ref{tab:LineMeasurements} and show the \civ\ line 
+fits in~\ref{fig:CIV_LineFits}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=8.5cm, trim=0.4cm 0.4cm 0.2cm 0.4cm, clip]
+  {figures/CIV_fits_20191108.png}
+   \vspace{-12pt}
+   \caption[]{The \civ\ emission line and the subsequent QSFit model and
+     parameters.}
+\end{figure}
 
@@
   \centering
-  % \begin{tabular}{lll  cccc r }
-  \begin{tabu}{l ll  ll cc c r }
-    \hline 
-    \hline 
-    Object                               &   MJD      & line      & Line  Lumin.
-&   FWHM                       &  $V_{\rm off}$         & E.W.
-& $\alpha_{\lambda}$  &   Catalogue \\
-    \hline                                     
-    \rowfont{\color{blue}}       & 53498    & \civ      &  511$\pm$13    &   9593$\pm$287        &  1172$\pm$74      & 15.9$\pm$0.4      & $-1.64\pm0.01$       &  QSFit         \\    %% (NPR) 
-    \rowfont{\color{blue}}       & 53498    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    & 30.1$\pm$1.21    & $-1.47\pm0.08$       &  Shen2011 \\
-    \rowfont{\color{blue}}       & 53498    & \civ      &   403                  &   5119$^{(a)}$             &    ---                     &  ---                        &  ---                         &  DR12 SAS   \\
-                                             & 53498     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    & 25.10$\pm$0.59    & $-1.65\pm0.01$      &  QSFit          \\  %% (NPR) 
-                                             & 53498    & \ciii       &   144                 &   5119$^{(a)}$             &  ---                       &   ---                       &  ---                          &  DR12 SAS  \\
-  \rowfont{\color{teal}}         & 53498     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     & 26.66$\pm$1.65    &   $-1.65\pm0.01$    &  $^{(d)}$QSFit  \\  %% (NPR) 
-  \rowfont{\color{teal}}         & 53498     & \mgii     &  284                  &   4730$\pm$314       &  $-179\pm188$     & 32$\pm$3.88         &  $-1.87\pm0.06$     &  Shen2011 \\
- \multirow{2}{*}{{\bf J1205+3422}}  
-                &     \textcolor{teal}{53948}     & \textcolor{teal}{\mgii}   & \textcolor{teal}{130} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\
-                                 \cdashline{2-9}
-                                            & 58538     & \lya      & 952$\pm$1.1    & 12242$\pm$15    &  $-1679\pm6$          &  165$\pm$0.2        &  ---                       &   QSFit  \\    %% (MJG)
-   \rowfont{\color{blue}}       & 58538     & \civ      & 1037$\pm$5    & $>$15000             &  983$\pm$40            &  ---                        &  ---                       &   QSFit  \\   %% (NPR)
-                                            & 58538      & \ciii     &  167$\pm$0.9  & $>$15000            &  2734$\pm$46            &     45$\pm$0.2       &  ---                       &  QSFit  \\    %% (MJG)
-    \rowfont{\color{teal}}      & 58538     & \mgii    &  216$\pm$1.4  & 13940$\pm$94    & $-465.2\pm38$         &  88$\pm$0.6	    &  ---                       &   QSFit  \\    %% (MJG)
-                                          \cdashline{2-9}
-                                           & 58693     & \lya     &  271$\pm$0.9    & 9637$\pm$52     &  $-447\pm13$          &  85.1$\pm$0.3          & ---                        &   QSFit  \\    %% (MJG)
-    \rowfont{\color{blue}}    & 58693     & \civ      &   52$\pm$0.9    & 5046$\pm$26     &   1053$\pm$17         &   24.0$\pm$0.2          & ---                        &  QSFit \\     %% (MJG)
-                                           & 58693     & \ciii     &   59$\pm$0.9    & 10751$\pm$        &  1097$\pm$77         &   36$\pm$0.6             & ---                        &  QSFit   \\    %% (MJG)
-   \rowfont{\color{teal}}      & 58693     & \mgii    &  69$\pm$1.5    & 14983$\pm$346   &  $-190\pm134$       &    72$\pm$1.6           & ---                        &  QSFit   \\    %% (MJG)
-\hline
-                                                & 54553     & \lya      & 188                 &  3207                     &    ---                        &   ---                         & ---                    &   DR12 SAS  \\
-   \rowfont{\color{blue}}          & 54553     & \civ      & 257$\pm$13   &  4550$\pm$371     &   55$\pm$450         &   31.8$\pm$1.5     &                                &  $^{(d)}$QSFit  \\   %% (NPR)
-   \rowfont{\color{blue}}          & 54553     & \civ      & 281                  &    4181$\pm$736   &    680$\pm$133       & 100.5$\pm$12  & $-0.14\pm0.68$        &  Shen2011   \\
-   \rowfont{\color{blue}}          & 54553     & \civ      & 170                  &   4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\    %% (NPR)
-                                                & 54553     & \ciii     &  130$\pm$10   &  3852$\pm$402    &  $-236\pm565$       &  36.7$\pm$2.8          &  $-1.47\pm0.20$    &  $^{(d)}$QSFit  \\
-                                                & 54553     & \ciii     &  61                    &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\    %% (NPR)
-    \rowfont{\color{teal}}          & 54553      & \mgii  &  139                  &  4757$\pm$2224   &  $-944\pm568$        &   119$\pm$40          &  $-1.49\pm0.54$    &  Shen2011   \\
-    \rowfont{\color{teal}}          & 54553      & \mgii  &  69                    &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\   %% (NPR)
-                                                \cdashline{2-9}
-                                                & 55832     & \lya     & 288$\pm$11    &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99   &                               &   QSFit  \\
-                                                & 55832     & \lya     & 234                  &  4165.6$^{(a)}$         &    ---                       &   ---                         & ---                         &   DR12 SAS  \\    %% (NPR)
-\multirow{2}{*}{\bf {J1638+2827}}
- & \textcolor{blue}{55832} & \textcolor{blue}{\civ}    & \textcolor{blue}{63$\pm$3}  &   \textcolor{blue}{6052$\pm$250}  &  \textcolor{blue}{-117$\pm$103}  &  \textcolor{blue}{43.2$\pm$1.7}  &  \textcolor{blue}{-2.25$\pm$0.05} & QSFit    \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---               &    5210$\pm$226     &    ---                       &   42.8$\pm$2.0         & $-3.35$                 &     Ham17  \\
-    \rowfont{\color{blue}}           &  55832   &  \civ     &  46                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\
-                                                 & 55832     & \ciii     & 15$\pm$5     &  11421$\pm$3654   &   $>$3000                &   14.8$\pm$4.5         &  $-2.25\pm0.05$   &        QSFit \\
-                                                 &  55832    &  \ciii    &  11                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                       &   DR12 SAS \\
-    \rowfont{\color{teal}}           &  55832     & \mgii   &  13                &     5385$^{(a)}$         &  ---                           &   ---                          &  ---                       &   DR12 SAS\\
-                                               \cdashline{2-9}
-                                               & 58583       & \lya    &  785$\pm$1      & 4956$\pm$4    	&   $-641\pm2$            &   90$\pm$0.1   	  &  ---                          &  QSFit  \\ %% (MJG)
-   \rowfont{\color{blue}}         & 58583      & \civ      &  311$\pm$1     & 5739$\pm$14	 &  $-167\pm6$             &   58$\pm$0.1          & ---                          &   QSFit  \\  %% (MJG)
-                                               & 58583      & \ciii      &  52$\pm$0.8   &  3917.4	68.837      &  1514$\pm$127        &  124$\pm$2             & ---                          &   QSFit \\   %% (MJG)
-   \rowfont{\color{teal}}           & 58583      & \mgii   &  157$\pm$2    &  10565$\pm$129    &  $-450\pm52$          &   92$\pm$1              & ---                          &   QSFit  \\  %% (MJG)
-\hline
-    \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &   2994$\pm$620       &     ---                       &   42.2$\pm$5.6      & -1.59                      &    Ham17  \\
-    \rowfont{\color{blue}}         &  56189     & \civ    &   19                  &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                        &   DR12 SAS  \\
-                                               &  56189      &  \ciii   &  34$\pm$6       &  13748$\pm$2869    &   1851$\pm$1140    &  63$\pm$12          &  $-0.46\pm0.21$    &   QSFit  \\
-                                               &  56189      & \ciii    &  7                     &     5218$^{(a)}$          &  ---                         &     ---                     & ---                         &   DR12 SAS \\
-    \rowfont{\color{teal}}          & 56189      & \mgii  &  25$\pm$6       &   7253$\pm$1712     &   $-931\pm708$      &  51$\pm$10.95      &  $-0.46\pm0.21$   &   QSFit   \\
-    \rowfont{\color{teal}}         &  56189      &  \mgii &  13                   &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                       &   DR12 SAS \\
-                                                  \cdashline{2-9}
-                                              & 56960         & \lya    & 121$\pm$38     & 3580$\pm$673       &     -16$\pm$171     &  13.52 $\pm$4.21    & ---                        &   QSFit   \\  
-\multirow{2}{*}{{\bf J2228+2201}}
-           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}  & \textcolor{blue}{229$\pm$4}      &  \textcolor{blue}{8911$\pm$169}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{46.8$\pm$0.9}    & ---    & \textcolor{blue}{QSFit}     \\
-                                               & 56960    & \ciii      & 185$\pm$5        &        -                      &  2701$\pm$225      &   47.75$\pm$1.29     & ---                      &   QSFit    \\
-   \rowfont{\color{teal}}           & 56960    & \mgii   &   99$\pm$4        &  7312.6$\pm$340   &   188$\pm$137      &   50.75$\pm$2.21     & ---                      &   QSFit   \\
-                                               \cdashline{2-9}
-                                               & 58693     & \lya      &  447$\pm$5       & 8133$\pm$93       &   613$\pm$130       &        56$\pm$0.6     &  ---                    	 &   QSFit  \\%% (MJG)
-     \rowfont{\color{blue}}        & 58693     & \civ      &  41$\pm$1        &  4914$\pm>$65    &   160$\pm$27         &   25$\pm$0.3          & ---                         & QSFit   \\  %% (MJG)
-                                               & 58693     & \ciii      & 107$\pm$1.2    &  $>$15000             &  2422$\pm$67        &   ---                       & ---                          &  QSFit    \\  %% (MJG)
-     \rowfont{\color{teal}}        & 58693     & \mgii    & 177$\pm$1.1    &  $>$15000             &  1000$\pm$2617    &   16$\pm$36         & ---                           &   QSFit  \\  %% (NPR) 
-\hline
-\hline
-     %    \end{tabular}
-    \end{tabu}
-    \caption{Line Measurement information for the nine epochs for the 3 quasars.
-      Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM and $V_{\rm off}$ in km s$^{-1}$,
-      where positive values of $V_{\rm off}$ means the line is blueshifted.
-      Equivalent widths are \AA\.  
-      Shen11 is \citet{Shen2011}. 
-      Ham17 is \citet{Hamann2017}.
-      DR12 SAS is the line measurement information from the SDSS DR12 
-      Science Archive Server (SAS).
-          $^{(a)}$Emission lines of a common ``width group'', in this case,
-    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
-    the same intrinsic velocity width in the SDSS spectral line fitting
-    procedure \citep{Bolton2012}. 
-      %$^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
-      Positive values of Voff means the line is blueshifted.
-%      $^{(b)}$Bit 3: FWHM value hits a limit in the fit
-      Notes: QSFit does not fit the \mgii line for J1638+2827 MJD
-      54553 or 55832. QSFit does not fit the \civ line for J2228+2201 MJD 56189.
-      $^{(d)}$Emission line modelled with two components.
-      The different colours of text are merely for readability.
-    }
- \label{tab:LineMeasurement}
+  % \input{emission_line_comparison_tab}
+  \input{emission_line_tab}
+  \caption{Line Measurement information for the nine epochs for the 3
+    quasars.  Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM
+    and $V_{\rm off}$ in km s$^{-1}$, where positive values of $V_{\rm
+      off}$ means the line is blueshifted.  Equivalent widths are in units
+    of \AA\ .  Positive values of V$_{\rm off}$ means the line is
+    blueshifted.  All measuremennts are from QSFIT, except for J1638+2827
+    (MJD 54553) which are from \citet{Shen2011}.  $^{(d)}$Emission line
+    modelled with two components.}
+ \label{tab:LineMeasurements}
 \end{table*}
@@
     \hline
-\multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$} & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref. \\
+    \multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$}  & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref.
+\\
                               &                                   &                                      &                                                              & \mgii                  & \civ                    &  \mgii           &  \civ                       &        \\
     \hline
-                                     & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen2011\\
+                              & 53498                         & -27.74                          & 47.216$\pm$0.004                            &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen11\\
     J1205+3422      & 58538                         &                                      &                                                            &                             &                             &                    &                               & \\
@@
     \hline
+%                              &                                     &                                       &                                               &                             &                                &                  &                  & \\
+ %   M87$^{*}$          &  57854	                     & ---                                &   43.187	                               & \multicolumn{2}{c}{9.812$\pm$0.044}    & 	\multicolumn{2}{c}{-4.699}   & EHT \\
+  %                                &                                     &                                       &                                               &                             &                                &                  &                  & \\
+     \hline
     \hline
   \end{tabular}
-  \caption{$\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio.
+  \caption{Physical properties of the \civ\ CLQs and M87.
+     $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude $K$-corrected to $z = 2$; Bolometric luminosity computed from the
+        monochromatic luminosity at 1350\AA\ using the spectral fits and
+        bolometric corrections (BC = 3.81) in \citet{Richards2006b}.
+        Virial BH masses using calibrations of \citet{VestergaardPeterson2006}.
+         $\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio computed using the virial BH mass.
         Shen11 is \citet{Shen2011}. 
-        Kol17 is \citet{Kozlowski2017}.
-        Measured line values using the methods and catalogue from
-\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
-$K$-corrected to $z = 2$; Bolometric luminosity computed from the
-monochromatic luminosity at 1350\AA\ using the spectral fits and
-bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
-luminosity, FWHM, rest-frame equivalent width, and their errors for
-the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
-continuum fit for \civ; Virial BH masses using calibrations of
-\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
-virial BH mass.}
+        Kozl17 is \citet{Kozlowski2017}. }
 \label{tab:Eddington_ratios} 
@@
 %%
-There is an anti-correlation between the emission-line REWs and e.g. 1450\AA\ rest continuum luminosity,
-so that as the underlying UV continuum luminosity increases, the EW decreses,
-see Figure~\ref{fig:CIV_Baldwin}
-The slope $\beta$ is $-0.1997$. 
-Checking with \citet{Kozlowski2017}, using their bolometric luminosity gives a slope of $\beta=-0.251$,
-in line with that from \citet{Hamann2017} ($\beta=-0.23$.
+There is an anti-correlation between the emission-line REWs and
+e.g. 1450\AA\ rest continuum luminosity, so that as the underlying UV
+continuum luminosity increases, the EW decreses, see
+Figure~\ref{fig:CIV_Baldwin} Our Figure~\ref{fig:CIV_Baldwin} is a
+reproduction of Figure~15 from \citet{Calderone2017}.
+
+The plotted values are \verb|CONT1450__LUM| and
+\verb|BR_CIV_1549__EW|.  \verb|CONT1__LUM| is the $\nu L_{\nu}$
+luminosity at wavelength. This selects 20,374 quasars.  The slope
+$\beta$ is $-0.1997$.  Checking with \citet{Kozlowski2017}, using
+their bolometric luminosity gives a slope of $\beta=-0.251$, in line
+with that from \citet{Hamann2017} ($\beta=-0.23$).
+%%
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
+sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
+
+Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
+at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
+in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
+nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
+nulla. Nullam eu augue id purus mollis dignissim sed et
+libero. Phasellus eget justo sed neque pellentesque egestas nec id
+arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
+vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
+imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
+neque id mi ultrices tristique. Integer quam libero, ornare vel
+gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
+cursus, dui nisl egestas augue, non fermentum nisl est nec
+nisi. Vestibulum nec mi justo, eget dapibus velit.
 
@@
 \end{figure}
+\section{Discussion}
+The variable properties of high-$z$
+quasars, however, has been less well studied. Reasons for this include
+more massive systems will tend to have longer timescales with e.g.
+$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.
 
-%{\bf Our Eddington ratios \\
-%Done 1\% \\
-%Coatman, Hewett say \civ\ masses are okay.\\
-%But what are these Eddington ratios? \\
-%Low state BHs vs. High-mass BHs... \\
-%Coatman et al?? Blue-shiftted \\ }
-\section{Discussion}
+The Balmer series in hydrogen is due to the recombination cascade
+between different principal quantum numbers $n$, and
+the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
+Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
+H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
+Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$.
+
+\civ\ is one of the strongest collisionally excited lines in quasar
+spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
+at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
+canonical BELR parameters deduced over from early analysis of the
+\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
+ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
+speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
+H$^{+}$).
+
 \civ\ probes the photoionization environment produced by the innermost
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
+  {figures/CIV_CLQs_Baldwin_20191108.png}
+   \vspace{-12pt}
+   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
+     commonly referred to as The Baldwin Plot.
+     The continuum luminosities are  from \citet{Calderone2017},
+     the REW measurements are Table~\ref{tab:Baldwin}.}
+  \label{fig:CIV_Baldwin}
+\end{figure}
 \subsection{The Baldwin Effect}
@@
 quasars in Table~\ref{tab:Eddington_ratios}.
+%%
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
+sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_20191104v3.png}
-   \vspace{-12pt}
-   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
-     commonly referred to as The Baldwin Plot. The continuum luminosities are
-     from \citet{Kozlowski2017},
-     the REW measurements are Table~\ref{tab:Baldwin}.}
-  \label{fig:CIV_Baldwin}
-\end{figure}
+Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
+pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
+id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
+dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
+euismod. Cras vel auctor neque. Nam quis diam risus.
 
-\subsection{Variability around billion solar mass black holes} 
-The Event Horizon Telescope (EHT) mapped the central compact radio
-source of the elliptical galaxy M87 at 1.3 mm \citep{EHT2019_PaperI, EHT2019_PaperII, EHT2019_PaperIII, EHT2019_PaperIV, EHT2019_PaperV, EHT2019_PaperVI} .
+Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
+at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
+in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
+nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
+nulla. Nullam eu augue id purus mollis dignissim sed et
+libero. Phasellus eget justo sed neque pellentesque egestas nec id
+arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
+vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
+imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
+neque id mi ultrices tristique. Integer quam libero, ornare vel
+gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
+cursus, dui nisl egestas augue, non fermentum nisl est nec
+nisi. Vestibulum nec mi justo, eget dapibus velit.
 
-The EHT observsations confirm the observed 1.3mm asymmetric ring
-emission is consistent with predictions of strong
-gravitational lensing of synchrotron emission from a hot plasma
-orbiting near the black hole event horizon \citep{EHT2019_PaperV}.
-
-EHT2017 data includes tracks from four separate
-days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{EHT2019_PaperIV} timescale is short
-compared to the decorrelation timescale of simulated images, which is
-$\sim$50 $r_{g}$ $c^{-1}$, and smaller than the light-crossing time of the source
-plasma.
-
-From \citet{EHT2019_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
-\begin{equation}
-R_{s} = 2 r_{g} =  2 GM/c^{2}  = 9.598 \times10^{12} {\rm m}.
-\end{equation}
-giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c = 32 015 {\rm secs}$ (0.37 days).
-%\begin{equation}
-%t_{\rm lt} = R_{s} / c = 32015 {\rm secs}$
-%\end{equation}
-%and a {\it dynamical timescale}, $t_{\rm dyn}$
-%\begin{equation}
-%$t_{\rm dyn}  =  sqrt{ R_{s}^{3}/G M}
-% \end{equation}
-%also (!!!!!) of $t_{\rm dyn}  =  \sqrt{ R_{s}^{3}/G M}$ = 32015 seconds.
-
-$\log_{10} (M_{M87^{*}} / M_{\odot} ) = 9.813$. 
-which is only about double that of J1205+3422 and J2228+2201,
-and a factor of $\sim$6 that of J1638+2827.
-However, M87
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%     S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5   
+%%     S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5   
+%%     S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5    S E C T I O N     5   
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}

### 2019-11-12 plots/perObject/J1205p3422_portrait_v1pnt0.py
big tidy up in plots/perObject/

@@ -1,349 +1,0 @@
-'''
-12h05m44.7s +34d22m52.4s
-'''
-
-import numpy as np
-import seaborn as sns
-import matplotlib.lines    as mlines
-import matplotlib.pyplot   as plt
-import matplotlib.gridspec as gridspec
-
-from matplotlib          import colors as mcolors
-from matplotlib.gridspec import GridSpec
-from matplotlib.patches  import Rectangle
-
-
-from astropy.io          import ascii
-from astropy.io          import fits
-from astropy.convolution import convolve, Box1DKernel
-
-#import pylustrator
-#pylustrator.start()
-
-
-##
-## R E A D I N G   I N   T H E    D A T A 
-##
-path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
-
-##    L I G H T    C U R V E
-## CRTS
-infile = 'J120544.67+342252.4_CRTS.dat'
-CRTS   = ascii.read(path+infile)
-## CRTS MJD offset
-CRTS_MJD_offset = 53500
-CRTS_MJD = CRTS['mjd'] + CRTS_MJD_offset
-
-infile = 'J120544.67+342252_ztf_g.dat'
-ZTF_g  = ascii.read(path+infile)
-
-infile = 'J120544.67+342252_ztf_r.dat'
-ZTF_r  = ascii.read(path+infile)
-
-
-infile = 'NEOWISER-L1b_J1205p3422.dat'
-NEOWISER = ascii.read(path+infile)
-NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
-NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
-infile = 'NEOWISER-L1b_J1205p3422_averaged.dat'
-NEOWISER_aver = ascii.read(path+infile)
-NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
-NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
-
-##    S P E C T R A 
-infile   = 'DBSP_J1205p3422_b_58538.dat'
-DBSP_b1  = ascii.read(path+infile)
-infile   = 'DBSP_J1205p3422_r_58538.dat'
-DBSP_r1  = ascii.read(path+infile)
-infile   = 'DBSP_J1205p3422_b_58693.dat'
-DBSP_b2  = ascii.read(path+infile)
[…]

### 2019-11-12 plots/perObject/J1205p3422_landscape_v1pnt0.py
plots/perObject/ BIG UPDATE

@@ -1,5 +1,8 @@
 '''
+      J 1 2 0 5 + 3 4 2 2  
+
 12h05m44.7s +34d22m52.4s
+181.436164  +34.381229
 '''
 
 import numpy as np
@@ -20,26 +23,34 @@ from astropy.convolution import convolve, Box1DKernel
 #import pylustrator
 #pylustrator.start()
 
-
 ##
 ## R E A D I N G   I N   T H E    D A T A 
 ##
 path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
 
-##    L I G H T    C U R V E
-## CRTS
+##     L I G H T    C U R V E
+##  CRTS
 infile = 'J120544.67+342252.4_CRTS.dat'
 CRTS   = ascii.read(path+infile)
-## CRTS MJD offset
+##  CRTS MJD offset
 CRTS_MJD_offset = 53500
 CRTS_MJD = CRTS['mjd'] + CRTS_MJD_offset
-
+##  ZTF
 infile = 'J120544.67+342252_ztf_g.dat'
 ZTF_g  = ascii.read(path+infile)
-
 infile = 'J120544.67+342252_ztf_r.dat'
 ZTF_r  = ascii.read(path+infile)
 
+## Pan-STARRS
+infile    = 'PanSTARRS_DR2_detections.dat'
+PanSTARRS = ascii.read(path+infile)
+##  g=1, r=2, i=3, z=4, y=5 
+PS_gband   = PanSTARRS[np.where(PanSTARRS['filterID'] == 1)]
+PS_rband   = PanSTARRS[np.where(PanSTARRS['filterID'] == 2)]
+PS_gPSFmag = -2.5*(np.log10(PS_gband['psfFlux']/3631.))
+PS_rPSFmag = -2.5*(np.log10(PS_rband['psfFlux']/3631.))
+
+##  NEOWISE
 infile = 'NEOWISER-L1b_J1205p3422.dat'
 NEOWISER = ascii.read(path+infile)
 NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
@@ -48,7 +59,6 @@ infile = 'NEOWISER-L1b_J1205p3422_averaged.dat'
 NEOWISER_aver = ascii.read(path+infile)
 NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
[…]

### 2019-11-12 plots/perObject/J1638p2827_landscape_v1pnt0.py

@@ -40,6 +40,15 @@ ZTF_g  = ascii.read(path+infile)
 infile = 'J163852.9+282708_ztf_r.dat'
 ZTF_r  = ascii.read(path+infile)
 
+## Pan-STARRS
+infile    = 'PanSTARRS_DR2_detections.dat'
+PanSTARRS = ascii.read(path+infile)
+##  g=1, r=2, i=3, z=4, y=5 
+PS_gband   = PanSTARRS[np.where(PanSTARRS['filterID'] ==1)]
+PS_rband   = PanSTARRS[np.where(PanSTARRS['filterID'] ==2)]
+PS_gPSFmag = -2.5*(np.log10(PS_gband['psfFlux']/3631.))
+PS_rPSFmag = -2.5*(np.log10(PS_rband['psfFlux']/3631.))
+
 ## NEOWISE-R
 infile = 'NEOWISER-L1b_J1638+2827.dat'
 NEOWISER = ascii.read(path+infile)
@@ -172,9 +181,9 @@ ax1.axvline(x=58583, linewidth=lw, linestyle='dashed', color='k')
 
 ## CRTS data
 lw = 1
-ax1.scatter( CRTS_MJD, CRTS['magnitude'], color='k',       alpha=alpha, s=ms*1.8)
-ax1.scatter( CRTS_MJD, CRTS['magnitude'], color='dimgray', alpha=alpha, s=ms, label='CRTS')
-ax1.errorbar(CRTS_MJD, CRTS['magnitude'], color='k', yerr=CRTS['magnitude_err'], fmt='o', linewidth=lw, ms=ms)
+ax1.scatter( CRTS_MJD, CRTS['magnitude'], color='k',       alpha=alpha, s=ms*1.8, zorder=0)
+ax1.scatter( CRTS_MJD, CRTS['magnitude'], color='dimgray', alpha=alpha, s=ms, label='CRTS', zorder=0)
+ax1.errorbar(CRTS_MJD, CRTS['magnitude'], color='k', yerr=CRTS['magnitude_err'], fmt='o', linewidth=lw, ms=ms, zorder=0)
 ## ZTF data
 ax1.scatter( ZTF_g['mjd'], ZTF_g['mag'], color='k',         alpha=alpha, s=ms*1.8)
 ax1.scatter( ZTF_g['mjd'], ZTF_g['mag'], color='olivedrab', alpha=alpha, s=ms, label='ZTF g-band')
[…]

### 2019-11-12 plots/perObject/older_py/J1205p3422_portrait_v1pnt0.py

@@ -1,8 +1,5 @@
 '''
-      J 2 2 2 8  +  2 2 0 1
-   
-22h28m18.7s +22d01m02.9s
-337.078194  +22.017478 
+12h05m44.7s +34d22m52.4s
 '''
 
 import numpy as np
@@ -15,6 +12,7 @@ from matplotlib          import colors as mcolors
 from matplotlib.gridspec import GridSpec
 from matplotlib.patches  import Rectangle
 
+
 from astropy.io          import ascii
 from astropy.io          import fits
 from astropy.convolution import convolve, Box1DKernel
@@ -22,48 +20,65 @@ from astropy.convolution import convolve, Box1DKernel
 #import pylustrator
 #pylustrator.start()
 
+
 ##
 ## R E A D I N G   I N   T H E    D A T A 
 ##
-path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J2228+2201/'
+path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
 
 ##    L I G H T    C U R V E
 ## CRTS
-infile = 'J222818.77+220102.6_CRTS.dat'
+infile = 'J120544.67+342252.4_CRTS.dat'
 CRTS   = ascii.read(path+infile)
 ## CRTS MJD offset
 CRTS_MJD_offset = 53500
 CRTS_MJD = CRTS['mjd'] + CRTS_MJD_offset
-## ZTF
-infile = 'J222818+220102_ztf_g.dat'
+
+infile = 'J120544.67+342252_ztf_g.dat'
 ZTF_g  = ascii.read(path+infile)
-infile = 'J222818+220102_ztf_r.dat'
+
+infile = 'J120544.67+342252_ztf_r.dat'
 ZTF_r  = ascii.read(path+infile)
 
-##  Pan-STARRS 
-infile    = 'PanSTARRS_DR2_detections.dat'
-PanSTARRS = ascii.read(path+infile)
-##  g=1, r=2, i=3, z=4, y=5 
-PS_gband   = PanSTARRS[np.where(PanSTARRS['filterID'] == 1)]
-PS_rband   = PanSTARRS[np.where(PanSTARRS['filterID'] == 2)]
-PS_gPSFmag = -2.5*(np.log10(PS_gband['psfFlux']/3631.))
[…]

### 2019-11-12 tex/CIV_CLQs.tex
Contnunning to update the .tex ...

@@
 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
-have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}. The
+have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019b}. The
 community uses both these terms as a cover for the underlying
@@
       \heii               &   1640.474  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  5/2        &  60 958.0       & 10.35 \\
-      \heii               &   1640.490  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  3/2        &  60 958.0       & 1.73 \\
+      \heii               &   1640.490  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  3/2        &  60 957.4       & 1.73 \\
       \ciii                 &  1906.683  &  6.5026     & 47.8878       & 1$s^{2}$2$s^{2}$   &   $^{1}$S   & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &   2        &   52 447.1       & 5.19$\times10^{-11}$ \\
@@
   \centering
-  \begin{tabular}{r l   r ll   r r r r}
+  \begin{tabular}{l l   r ll   r r r l}
     \hline 
     \hline 
-    Object                           & \multirow{3}{*}{Redshift}  &                       & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date} & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
-    R.A.
-/ deg                     &                                         &   {$g$-band}   &                                 &                                  &                                               &  Time           & Spectrum                 & \\
-    Decl.
-/ deg                   &                                         &    magnitude   &                                &                                   &                                              &  / seconds    & Plate-FiberID  & \\
+    \multirow{3}{*}{Object} & \multirow{3}{*}{Redshift} &                        & \multirow{3}{*}{MJD} &  \multirow{3}{*}{Instrument}  & Exposure      &                   & \multirow{3}{*}{Notes} \\
+                            &                                                     &   {$g$-band}   &                                 &                                              &  Time           &    SDSS             & \\
+                                       &                                          &    (mag)           &                                 &                                              & (seconds)    & Plate-FiberID  & \\
     \hline  
+%                                         &                                         &                        &                                &                    &                              &                              & \\
+    J120544.7+342252.4   & 2.068                               &   18.27             &  53498                   & SDSS             &  8057                  & 2089-427             & \\
+                                        & 2.071                                &                        &  58538                   & DBSP            &  1800                  &  ---                      &  Average conditions \\
+                                         & 2.071                               &                         &  58693                  & DBSP            &  2400                   &  ---                      &   \\
                                          &                                       &                          &                                &                          &                     &                               &                              & \\
-    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             &  8057                  & 2089-427             & \\
-    181.436164                  & 2.071                              &                         &  58538   &  2019-Feb-24    & DBSP            &  1800                  &  ---                      &  Average conditions \\
-    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2400                   &  ---                      &   \\
+    J163852.9+282707.7   & 2.185                            &   19.77               &  54553                   & SDSS           &   4801                    &  2948-614              & \\
+    	                                 &  2.186                            &                          &  55832                  & BOSS            &   3600                   &  5201-178            & \\
+                                         &  2.182                           &                          &  58583                     & LRIS              &  1800                   &  ---                             & \\
                                         &                                      &                          &                                 &                            &                    &                              &                                & \\
-    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS           &   4801                    &  2948-614              & \\
-    249.720558	                 &  2.186$\pm$0.0007     &                          &  55832    & 2011-Sep-28     & BOSS            &   3600                   &  5201-178            & \\
-    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10     & LRIS              &  1800                   &  ---                             & \\
-                                        &                                      &                          &                &                            &                    &                              &                                & \\
-    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                &  56189    & 2012-Sep-19     & BOSS             &  2700                 &   6118-720          & \\
-    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30     & BOSS             &  4500                  &   7582-790          & eBOSS reobservation \\
-    +22.017478                &                                      &                          &  58693    & 2019-Jul-29       & DBSP             & 2400                   &    ---                        &    \\
-                                       &                                       &                          &               &                            &                   &                              &                            & \\
+    J222818.7+220102.9   & 2.217                           & 19.97                &  56189                  &  BOSS             &  2700                 &   6118-720          & \\
+                                          & 2.222                         &                          &  56960                    & BOSS             &  4500                  &   7582-790          & eBOSS reobservation \\
+                                         &  2.222                         &                          &  58693                  &  DBSP             & 2400                   &    ---                        &    \\
+  %                                     &                                       &                          &               &                            &                   &                              &                            & \\
     \hline \hline   
@@
     Details of our spectroscopic observations.
-    Redshift and redshift errors from SDSS SkyServer for SDSS, BOSS and eBOSS spectra. 
+%    Redshift and redshift errors from SDSS SkyServer for SDSS, BOSS and eBOSS spectra.
+    Redshift errors are typically  $\pm$0.002. 
     Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and  eBOSS spectra have $\mathcal{R}\sim$2,000.
@@
 also find the BEff is present in both the RQ and RL studied samples.
-%%
-These author conclude
-that these two \civ\ parameters (EQW and blueshift) are capturing an
-important trade-off between ``disk'' and ``wind'' components in the
-disk-wind model of accretion disks \citep[e.g.,][]{Murray1995,
-Elvis2000, Proga2000, Leighly2004b}, with one dominating over the other depending on
-the shape of the SED.
+These author conclude that these two \civ\ parameters (EQW and
+blueshift) are capturing an important trade-off between ``disk'' and
+``wind'' components in the disk-wind model of accretion disks
+\citep[e.g.,][]{Murray1995, Elvis2000, Proga2000, Leighly2004b}, with
+one dominating over the other depending on the shape of the SED.
 
@@
 %%    P a p e r    O v e r v i e w
-The purpose of this paper is, for the first time, to systematically access and 
-report on the CLQ phenomenon at high ($z>2$) redshift. By doing so, we move from the low-ionization 
-energy Balmer emission line series to the high-ionization emission 
-lines, in particular \civ\ $\lambda$1549.
+The purpose of this paper is, for the first time, to systematically
+access and report on the CLQ phenomenon at high ($z>2$)
+redshift. While accessing this phenomenon at an earlier cosmic epoch
+is somewhat interesting, the main value of this study is we move from
+the low-ionization energy Balmer emission line series to the
+high-ionization emission lines, in particular \civ\ $\lambda$1549.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data}
+\section{Data, CLQ Selection and Line measurements}
+In this section we present the photometric data used to select the CLQs, and then
+give details to the multiwavelength data where we have it, obtained spectroscopy and
+emission lines measurements.
+
+\subsection{Photometry}
+\subsubsection{Optical Photometry}
+We use optical data from the Catalina Real-time Transient Survey
+\citep[CRTS;][]{Drake2009, Mahabal2011}, the Panoramic Survey
+Telescope and Rapid Response System \citep[PanSTARRS;][]{Kaiser2010,
+Stubbs2010, Tonry2012, Magnier2013} and the Zwicky Transient Facility
+\citep[ZTF;][]{Bellm2019_ZTFOverview}.
+
+The CRTS archive\footnote{http://catalinadata.org} contains the
+Catalina Sky Survey data streams from three telescopes -- the 0.7 m
+Catalina Sky Survey (CSS) Schmidt and 1.5 m Mount Lemmon Survey (MLS)
+telescopes in Arizona and the 0.5 m Siding Springs Survey (SSS)
+Schmidt in Australia. 
+CRTS covers up to $\sim$2500 deg$^2$ per night, with 4 exposures per visit, separated
+by 10 min. The survey observes over 21 nights per lunation. The data
+are broadly calibrated to Johnson $V$ \citep[see ][for details]{Drake2013}
+and the current CRTS data set contains time series for
+approximately 400 million sources to $V \sim 20$ above Dec $> -30$
+from 2003 to 2016 May (observed with CSS and MLS) and 100 million
+sources to $V \sim 19$ in the southern sky from 2005 to 2013 (from
+SSS). CRTS has been used to study distant quasars previously
+\citep{Graham2014, Graham2015, Graham2015Nature, Graham2017, Graham2019b}.
+
+PanSTARRS data is obtained via the Pan-STARRS Catalog Search
+interface\footnote{https://catalogs.mast.stsci.edu/panstarrs/}.
+We query the PS1 DR2 Detection catalog.
+
+The ZTF is a new robotic time-domain sky survey capable of visiting
+the entire visible sky north of -30 deg. declination every night. ZTF
+observes the sky in the $g$, $r$, and $i$-bands at different cadences
+depending on the scientific program and sky region
+\citep{Bellm2019_ZTFSurveys, Graham2019_ZTF}. The ZTF 576 megapixel
+camera with a 47 deg$^{2}$ field of view, installed on the Samuel
+Oschin 48-inch Schmidt Telescope, can scan more than 3750 deg$^{2}$
+per hour, to a 5$\sigma$ detection limit of 20.7 mag in the $r$-band
+with a 30sec exposure during new moon \citep{Masci2019}.
+
+\subsection{CLQ Selection}
 Our high-$z$ CLQs were identified as follows.  We selected all 64,774
@@
 where $|\Delta V| > 0.3$ are then selected for visual
-inspection. Three quasars SDSS J120544.7+342252.4 (hereafter
+inspection. Only three quasars SDSS J120544.7+342252.4 (hereafter
 J1205+3422), SDSS J163852.93+282707.7 (hereafter J1638+2827) and SDSS
@@
   \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
-  {figures/J1205+3422_landscape_20191024.png}
+  {figures/J1205+3422_landscape_20191112.png}
   \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
-  {figures/J1638+2827_landscape_20191024.png}
+  {figures/J1638+2827_landscape_20191112.png}
   \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
-  {figures/J2228+2201_landscape_20191024.png}
+  {figures/J2228+2201_landscape_20191112.png}
   \vspace{-12pt}

### 2019-11-13 correspondence/J1205p3422_v1pnt0.py
Removed correspondence/ folder

@@ -1,280 +1,0 @@
-'''
-12h05m44.7s +34d22m52.4s
-'''
-
-import numpy as np
-import seaborn as sns
-import matplotlib.lines    as mlines
-import matplotlib.pyplot   as plt
-import matplotlib.gridspec as gridspec
-
-from matplotlib          import colors as mcolors
-from matplotlib.gridspec import GridSpec
-from matplotlib.patches  import Rectangle
-
-
-from astropy.io          import ascii
-from astropy.io          import fits
-from astropy.convolution import convolve, Box1DKernel
-
-#import pylustrator
-#pylustrator.start()
-
-##
-## R E A D I N G   I N   T H E    D A T A 
-##
-path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1205+3422/'
-
-##  Light Curve
-infile = 'NEOWISER-L1b_J1205p3422.dat'
-NEOWISER = ascii.read(path+infile)
-NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
-NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
-infile = 'NEOWISER-L1b_J1205p3422_averaged.dat'
-NEOWISER_aver = ascii.read(path+infile)
-NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
-NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
-
-##  Spectra
-infile   = 'DBSP_J1205p3422_b_58538.dat'
-DBSP_b1  = ascii.read(path+infile)
-infile   = 'DBSP_J1205p3422_r_58538.dat'
-DBSP_r1  = ascii.read(path+infile)
-infile   = 'DBSP_J1205p3422_b_58693.dat'
-DBSP_b2  = ascii.read(path+infile)
-infile   = 'DBSP_J1205p3422_r_58693.dat'
-DBSP_r2  = ascii.read(path+infile)
-
-DBSP_b1_wavelength = DBSP_b1['wavelength']
-DBSP_r1_wavelength = DBSP_r1['wavelength']
-DBSP_b2_wavelength = DBSP_b2['wavelength']
-DBSP_r2_wavelength = DBSP_r2['wavelength']
-
-
-## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
[…]

### 2019-11-13 correspondence/J1638p2827_v1pnt0.py

@@ -1,264 +1,0 @@
-'''
-12h05m44.7s +34d22m52.4s
-'''
-
-import numpy as np
-import seaborn as sns
-import matplotlib.lines    as mlines
-import matplotlib.pyplot   as plt
-import matplotlib.gridspec as gridspec
-
-from matplotlib          import colors as mcolors
-from matplotlib.gridspec import GridSpec
-from matplotlib.patches  import Rectangle
-
-
-from astropy.io          import ascii
-from astropy.io          import fits
-from astropy.convolution import convolve, Box1DKernel
-
-#import pylustrator
-#pylustrator.start()
-
-##
-## R E A D I N G   I N   T H E    D A T A 
-##
-path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J1638+2827/'
-
-##  Light Curve
-infile = 'NEOWISER-L1b_J1638+2827.dat'
-NEOWISER = ascii.read(path+infile)
-NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
-NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
-infile = 'NEOWISER-L1b_J1638+2827_averaged.dat'
-NEOWISER_aver = ascii.read(path+infile)
-NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
-NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
-
-##  Spectra
-infile   = 'LRIS_J1638p2827_b_58583.dat'
-LRIS_b  = ascii.read(path+infile)
-infile   = 'LRIS_J1638p2827_r_58583.dat'
-LRIS_r  = ascii.read(path+infile)
-
-LRIS_b_wavelength = LRIS_b['wavelength']
-LRIS_r_wavelength = LRIS_r['wavelength']
-
-## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
-## http://www.stsci.edu/~strolger/docs/UNITS.txt
-## 
-## [Y erg/cm^2/s/Hz]            = 1000 * [X W/m^2/Hz]
-## [Y erg/cm^2/s/A]             = 2.99792458E+21 * [X1 W/m^2/Hz] / [X2 A]^2
-## / 1e-17 to put into 'regular' SDSS flux units 
[…]

### 2019-11-13 correspondence/J2228p2201_v1pnt0.py

@@ -1,265 +1,0 @@
-'''
-12h05m44.7s +34d22m52.4s
-'''
-
-import numpy as np
-import seaborn as sns
-import matplotlib.lines    as mlines
-import matplotlib.pyplot   as plt
-import matplotlib.gridspec as gridspec
-
-from matplotlib          import colors as mcolors
-from matplotlib.gridspec import GridSpec
-from matplotlib.patches  import Rectangle
-
-
-from astropy.io          import ascii
-from astropy.io          import fits
-from astropy.convolution import convolve, Box1DKernel
-
-#import pylustrator
-#pylustrator.start()
-
-##
-## R E A D I N G   I N   T H E    D A T A 
-##
-path = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/J2228+2201/'
-
-##  Light Curve
-infile = 'NEOWISER-L1b_J2228+2201.dat'
-NEOWISER = ascii.read(path+infile)
-NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.673
-NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.313
-infile = 'NEOWISER-L1b_J2228+2201_averaged.dat'
-NEOWISER_aver = ascii.read(path+infile)
-NEOWISER_aver_W1_AB = NEOWISER_aver['w1mpro_wgt'] + 2.673
-NEOWISER_aver_W2_AB = NEOWISER_aver['w2mpro_wgt'] + 3.313
-
-##  Spectra
-infile   = 'DBSP_J2228p2201_b_56893.dat'
-DBSP_b  = ascii.read(path+infile)
-infile   = 'DBSP_J2228p2201_r_56893.dat'
-DBSP_r  = ascii.read(path+infile)
-
-DBSP_b_wavelength = DBSP_b['wavelength']
-DBSP_r_wavelength = DBSP_r['wavelength']
-
-## Need to convert BUNIT   = 'erg/cm2/s/Hz'  to  'erg/cm2/s/A'
-## http://www.stsci.edu/~strolger/docs/UNITS.txt
-## 
-## [Y erg/cm^2/s/Hz]            = 1000 * [X W/m^2/Hz]
-## [Y erg/cm^2/s/A]             = 2.99792458E+21 * [X1 W/m^2/Hz] / [X2 A]^2
-## / 1e-17 to put into 'regular' SDSS flux units 
[…]

### 2019-11-13 data/QSFIT/prep_DBSP_LRIS_spectra.py
../data/QSFIT/prep_DBSP_LRIS_spectra.py modified

@@ -85,3 +85,8 @@ output = Table( [wavelength,flux,err_flux], names=['wavelength', 'flux', 'err_fl
 
 ascii.write(output, 'spec_output_temp.dat',  overwrite=True) # names=['wavelength', 'flux', 'err_flux'])
 
+
+print()
+print('You probably want to see:: ')
+pritn('https://stackoverflow.com/questions/58411437/simple-formatting-of-astropy-tables-ascii-output/58419100#58419100')
+print()

### 2019-11-13 tex/CIV_CLQs.tex
continuing to update CIV_CLQs.tex

@@
 
+\subsubsection{Mid-infrared Photometry}
+Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning
+of the Wide-field Infrared Survey Explorer (WISE) mission \citep[2010
+January; ][]{Wright2010} through the fifth-year of NEOWISE-R
+operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
+pattern leads to coverage of the full-sky approximately once every six
+months (a ``sky pass''), albeit with a gap from 2011 February to 2013
+October when the satellite was placed in hibernation.  Hence, our
+light curves have a cadence of 6 months with a 32 month sampling
+gap. \\
+{\bf DS to check for any X-ray, radio etc.}
+
 \subsection{CLQ Selection}
+{\bf MJG to finalise this::} \\
 Our high-$z$ CLQs were identified as follows.  We selected all 64,774
@@
   \vspace{-12pt}
-  \caption[]{The threes high-$z$ CLQ quasars; 
-    SDSS J1205+3422 (top), 
-    SDSS J1638+2827 (middle), 
-    SDSS J2228+2201 (bottom). 
+  \caption[]{The three high-$z$ CLQ quasars; 
+    J1205+3422 (top), 
+    J1638+2827 (middle) and  
+    J2228+2201 (bottom). 
 The light curve data is present in the panels on the left hand side, with the 
-spectral epoch observational timings given by the vertical lines. 
+spectral epoch observational timings indicated by vertical lines. 
 The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
-complex, the \civ\ line and the \mgii line. 
+complex, the \civ\ line, and the \mgii line. 
   }
@@
 \end{figure*}
-\subsection{Spectra}
+\subsection{Spectroscopy}
 An overview of our spectroscopic observations is given in
@@
 \citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
-Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011,
+Oscillation Spectroscopic Survey \citep[BOSS; ][]{Eisenstein2011,
 Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
@@
 of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
-Myers2015}. The SDSS, BOSS and eBOSS data are supplemented by
-spectra from the Low Resolution Imaging Spectrometer (LRIS) on the 10m
-Keck {\sc I} telescope \citep{Oke1995}.  and the Double Spectrograph
-(DBSP) instrument on the Palomar {\it Hale} 5m telescope.
+Myers2015}. The SDSS, BOSS, and eBOSS data are supplemented by
+spectra from the Low Resolution Imaging Spectrometer \citep[LRIS; ][]{Oke1995} on the 10m
+Keck {\sc I} telescope.  and the Double Spectrograph
+(DBSP) instrument on the 200'' Palomar telescope.
 
-\subsection{Emission Line and Power-law slope measurements}
+\subsubsection{Spectrophotometry}
+{\bf MJG to finish this::} \\
+We want all our spectra to have reliable flux calibrations.  SDSS
+spectra ae spectrophotometrically calibrated.  BOSS and eBOSS spectra
+have spectrophotometric corrections applied in the latest data release
+\citep{Hutchinson2016, Jensen2016, Margala2016}.  Due to the high-$z$
+of our objects, \oiii is not available to us to use as a calibrating
+flux line. Instead we use photometric data from the ZTF since all our
+non-SDSS/BOSS/eBOSS data are taken after MJD 57500.
+
+\subsection{Emission Line and Power-law Slope Measurements}
 We use the measured quasar emission line properties from several catalogues: 
-\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017} and
+\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017}, and
 \citet{Calderone2017}.
 
-\citet{Shen2011} present a compilation of properties of the 105,783
-quasars in the SDSS Data Release 7 (DR7) quasar catalog \citep[DR7Q;
-][]{Schneider2007}. \citet{Shen2011} report non-zero \civ\ FWHM and
-EWs for approximately half (51,501) of the full DR7Q, and non-zero
-\mgii FWHM and EWs for 80\% (84,183) of the DR7Q quasars).
+In particular we use the Quasar Spectral Fitting (QSFIT) software
+package presented in \citet{Calderone2017}. This provides luminosity
+estimates as well as width, velocity offset and equivalent width of 20
+emission lines, including \civ, \ciii and \mgii.  We process and fit
+all nine spectra using the lastest version (v1.3.0) of the QSFIT
+\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
+calculator}.
+% and setting $E(B-V)=0.00$.
 %%
-Measured line values using the methods and catalogue from
-\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
-$K$-corrected to $z = 2$; Bolometric luminosity computed from the
-monochromatic luminosity at 1350\AA\ using the spectral fits and
-bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
-luminosity, FWHM, rest-frame equivalent width, and their errors for
-the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
-continuum fit for \civ; Virial BH masses using calibrations of
-\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
-virial BH mass.
-
-\citet{Calderone2017} present the Quasar Spectral Fitting (QSFIT)
-software package which among other quantities provides luminosity
-estimates as well as width, velocity offset and equivalent width of 20
-emission lines, including \civ, \ciii and \mgii.  We attempt to process and fit
-all nine spectra using the lastest version (v1.3.0) of the QSFIT
-\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online calculator}
-and setting $E(B-V)=0.00$.
+The host galaxy and blended iron emission at rest-frame optical
+wavelengths components are automatically disabled when they can not be
+constrained by the available data, such as the case for all our
+objects (we do not have infrared spectral data).
 %%
-The host galaxy and blended iron emission at rest-frame optical wavelengths components
-are automatically disabled when they can not be constrained by the available data,
-such as the case for all our objects (we do not have infrared spectral data).
-%%
-
-\citet{Hamann2017} investigate in robust detail the UV continuum and
-the \civ\ (and \nv $\lambda$1238, 1242 \AA\ ) emission lines for over
-200,000 quasars in BOSS DR12Q \citep{Paris2017}.  The quasar redshift
-are limited to the range $1.53 \leq z \leq 5.0$ so that \civ\ and the
-adjacent continuum are covered by BOSS. These measurements provide
-line profile information and flux ratios\footnote{This emission-line
-catalog can be downloaded from
-\href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
-\citet{Hamann2017} was focused on $z\geq2$ quasars and specifcally
-their \civ properties in order to understand the high-$z$ ``Extremely
-Red Quasar'' population \citet{Ross2015, Zakamska2016, Perrotta2019,
-  Zakamska2019}.  As such, we prefer the \citet{Hamann2017} emission line
-values where available, though this is only for two out of our nine spectra.
-
-When using the \citet{Shen2011} catalogue, we report line luminosity,
-FWHM, rest-frame equivalent width, and their errors for the whole
-\mgii profile (this catalogue also quotes values for just the broad
-\mgii component, but the differences for our objects is
-negligible). The line luminosities in \citet{Calderone2017} are given
-in units of $10^{42}$ erg s$^{-1}$, while the line luminosities in
-\citet{Shen2011} are in units of $\log(L)$.  We do not report the
-\citet{Shen2011} error on the line luminosity.
-
 Power-law continuum slopes, $\alpha$, where $f_{\lambda} \propto
@@
 wavelength.
-
-\subsection{Multi-wavelength properties}
-Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning of the
-Wide-field Infrared Survey Explorer (WISE) mission \citep[2010
-January; ][]{Wright2010} through the fifth-year of NEOWISE-R
-operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
-pattern leads to coverage of the full-sky approximately once every six
-months (a ``sky pass''), but the satellite was placed in hibernation
-in 2011 February and then reactivated in 2013 October. Hence, our
-light curves have a cadence of 6 months with a 32 month sampling gap.
-%Radio ??
 
@@
 \section{Results}
-\subsection{Overall Spectral Evolution}
-Figure~\ref{fig:civ_clqs} presents the optical and infrared light
+\subsection{Photometric and Spectral Evolution}
+Figure~\ref{fig:civ_clqs} presents the optical and mid-IR light
 curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also

### 2019-11-14 plots/perObject/J1205p3422_landscape_v1pnt0.py
plots/perObject/ .py updated

@@ -15,7 +15,6 @@ from matplotlib          import colors as mcolors
 from matplotlib.gridspec import GridSpec
 from matplotlib.patches  import Rectangle
 
-
 from astropy.io          import ascii
 from astropy.io          import fits
 from astropy.convolution import convolve, Box1DKernel
@@ -34,7 +33,7 @@ infile = 'J120544.67+342252.4_CRTS.dat'
 CRTS   = ascii.read(path+infile)
 ##  CRTS MJD offset
 CRTS_MJD_offset = 53500
-CRTS_MJD = CRTS['mjd'] + CRTS_MJD_offset
+CRTS_MJD        = CRTS['mjd'] + CRTS_MJD_offset
 ##  ZTF
 infile = 'J120544.67+342252_ztf_g.dat'
 ZTF_g  = ascii.read(path+infile)
@@ -49,6 +48,12 @@ PS_gband   = PanSTARRS[np.where(PanSTARRS['filterID'] == 1)]
 PS_rband   = PanSTARRS[np.where(PanSTARRS['filterID'] == 2)]
 PS_gPSFmag = -2.5*(np.log10(PS_gband['psfFlux']/3631.))
 PS_rPSFmag = -2.5*(np.log10(PS_rband['psfFlux']/3631.))
+
+##  ALLWISE
+infile  = 'ALLWISE_catalog.dat'
+ALLWISE = ascii.read(path+infile)
+ALLWISE_W1_AB = ALLWISE['w1mpro'] + 2.673
+ALLWISE_W2_AB = ALLWISE['w2mpro'] + 3.313
 
 ##  NEOWISE
 infile = 'NEOWISER-L1b_J1205p3422.dat'
@@ -169,7 +174,7 @@ minorticklength = 6
 ##  T H E    L I G H T     C U R V E S
 xmin = 53400; xmax = 59000
 #ymin = 20.49; ymax = 16.501
-ymin = 21.20; ymax = 16.70   
+ymin = 21.20; ymax = 16.20   
 ax1.set_xlim([xmin,xmax])
 ax1.set_ylim([ymin, ymax])
 
@@ -204,19 +209,23 @@ ax1.scatter(PS_rband['obsTime'], PS_rPSFmag, color='deeppink', alpha=alpha, s=ms
 ## indigo and brown were used in Ross et al. (2018)
 ms              = 10.
 ms_big          = ms*6.
[…]

### 2019-11-14 plots/perObject/J1638p2827_landscape_v1pnt0.py

@@ -49,6 +49,12 @@ PS_rband   = PanSTARRS[np.where(PanSTARRS['filterID'] ==2)]
 PS_gPSFmag = -2.5*(np.log10(PS_gband['psfFlux']/3631.))
 PS_rPSFmag = -2.5*(np.log10(PS_rband['psfFlux']/3631.))
 
+##  ALLWISE
+infile  = 'ALLWISE_catalog.dat'
+ALLWISE = ascii.read(path+infile)
+ALLWISE_W1_AB = ALLWISE['w1mpro'] + 2.673
+ALLWISE_W2_AB = ALLWISE['w2mpro'] + 3.313
+
 ## NEOWISE-R
 infile = 'NEOWISER-L1b_J1638+2827.dat'
 NEOWISER = ascii.read(path+infile)
@@ -135,7 +141,6 @@ ax3 = fig.add_subplot(gs[-1, 2])
 ax4 = fig.add_subplot(gs[-1, 3])
 ax5 = fig.add_subplot(gs[-1, -1])
 
-
 ## Adjusting the Whitespace for the plots
 left   = 0.06   # the left side of the subplots of the figure
 right  = 0.97   # the right side of the subplots of the figure
@@ -169,7 +174,7 @@ minorticklength = 6
 ##  T H E    L I G H T     C U R V E S 
 xmin = 53400; xmax = 59000
 #ymin = 21.29; ymax = 17.01
-ymin = 21.20; ymax = 16.70   
+ymin = 21.20; ymax = 16.20   
 ax1.set_xlim([xmin,xmax])
 ax1.set_ylim([ymin, ymax])
 
@@ -200,19 +205,22 @@ ax1.scatter(PS_gband['obsTime'], PS_gPSFmag, color='lime',     alpha=alpha, s=ms
 ax1.scatter(PS_rband['obsTime'], PS_rPSFmag, color='k',        alpha=alpha, s=ms_big)
 ax1.scatter(PS_rband['obsTime'], PS_rPSFmag, color='deeppink', alpha=alpha, s=ms, label='Pan-STARRS r-band')
 
-
 ## NEOWISER W1/2 (AB)
 ms              = 10.
 ms_big          = ms*6.
-ax1.scatter(NEOWISER['mjd'],  NEOWISER_W1_AB, color='k', alpha=alpha, s=ms*1.8)
[…]

### 2019-11-14 plots/perObject/J2228p2201_landscape_v1pnt0.py

@@ -49,6 +49,12 @@ PS_rband   = PanSTARRS[np.where(PanSTARRS['filterID'] == 2)]
 PS_gPSFmag = -2.5*(np.log10(PS_gband['psfFlux']/3631.))
 PS_rPSFmag = -2.5*(np.log10(PS_rband['psfFlux']/3631.))
 
+##  ALLWISE
+infile  = 'ALLWISE_catalog.dat'
+ALLWISE = ascii.read(path+infile)
+ALLWISE_W1_AB = ALLWISE['w1mpro'] + 2.673
+ALLWISE_W2_AB = ALLWISE['w2mpro'] + 3.313
+
 ## NEOWISE-R
 infile = 'NEOWISER-L1b_J2228+2201.dat'
 NEOWISER = ascii.read(path+infile)
@@ -170,7 +176,7 @@ plt.rcParams['text.usetex'] = True
 
 ##  T H E    L I G H T     C U R V E S 
 xmin = 53400; xmax = 59000
-ymin = 21.20; ymax = 16.70   
+ymin = 21.20; ymax = 16.20   
 ax1.set_xlim([xmin,xmax])
 ax1.set_ylim([ymin, ymax])
 
@@ -204,14 +210,19 @@ ax1.scatter(PS_rband['obsTime'], PS_rPSFmag, color='deeppink', alpha=alpha, s=ms
 ## NEOWISER W1/2 (AB)
 ms     = 10.
 ms_big = ms*6.
-ax1.scatter(NEOWISER['mjd'],  NEOWISER_W1_AB, color='k', alpha=alpha, s=ms*1.8)
-ax1.scatter(NEOWISER['mjd'],  NEOWISER_W1_AB, color='r', alpha=alpha, s=ms, label='NEOWISE W1')
-ax1.scatter(NEOWISER['mjd'],  NEOWISER_W2_AB, color='k', alpha=alpha, s=ms*1.8)
-ax1.scatter(NEOWISER['mjd'],  NEOWISER_W2_AB, color='c', alpha=alpha, s=ms, label='NEOWISE W2')
-ax1.scatter(NEOWISER_aver['mean_mjd'],  NEOWISER_aver_W1_AB, color='k', alpha=alpha, s=ms_big*1.8)
-ax1.scatter(NEOWISER_aver['mean_mjd'],  NEOWISER_aver_W1_AB, color='r', alpha=alpha, s=ms_big)
[…]

### 2019-11-14 tex/CIV_CLQs.tex
ALLWISE_catalog.dat data added x3

@@
 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
-have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019b}. The
+have now been assembled \citep[e.g.][]{MacLeod2019, Graham2019b}. The
 community uses both these terms as a cover for the underlying

### 2019-11-14 tex/CIV_CLQs.tex
plots/spectral/CIV_fits_1comp.png and CIV_fits_2comp.png added

@@
 
-For J1205+3422, our spectral observations cover 5195 days observed, 1691 days
-in the rest-frame. For J1205+3422 is identified in SDSS as a bright
-$g\approx18.0$, blue-sloped quasar with broad \siiv, \civ, \ciii and
-\mgii observed in the initial spectrum (MJD 53498; 2005-May-08). \ciii
-and \civ\ are seen to have large blueshifts of $\approx$2600$\pm$150
-and $\approx$1150$\pm$100 km s$^{-1}$, respectively.  By the time the
-2019 spectra were taken (MJD 58538, 2019-Feb-24 and MJD 58693
-2019-Jul-29), however, the light curve has dropped by $\sim$1.5
-magnitudes and the spectra are significantly less steep.  While \lya
-and \nv are detectable in both the MJD 58538 and MJD 58693 DBSP
-spectra, \civ\ has all but disappeared in the MJD 58693 spectrum.  The
-broad \ciii emission has disappeared between the 2005 and 2019
-spectra. {\it The changes in \civ\ and \ciii going from broad emission to
-barely detectable have on the timescales of $\approx$50 days in the rest-frame.}
+For J1205+3422, our spectral observations cover 5195 days observed,
+1691 days in the rest-frame. This quasar was initially identified in
+SDSS in 2005 May, as a bright, $g\approx18.0$, blue-sloped quasar with
+broad \siiv, \civ, \ciii and \mgii. \ciii and \civ\ have large
+blueshifts of $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km
+s$^{-1}$, respectively.  By 2019, however, the opitical brightness
+dropped by $\sim$1.5 magnitudes and the spectra are significantly less
+blue.  While \lya and \nv are detectable in both 2019 spectra, \civ\
+has all but disappeared in the 2019 June spectrum.  The broad \ciii
+emission has disappeared between the 2005 and 2019 spectra. The
+changes in \civ\ and \ciii going from broad emission to barely
+detectable have on the timescales of $\approx$50 days in the
+rest-frame.
 

### 2019-11-14 plots/spectral/CIV_fits.py

@@ -78,7 +78,8 @@ J22_third_flux  = J22_third['flux']
 ##  R E A D I N G    I N    T H E   L I N E   F I T S    F R O M    Q S F I T
 infile = 'QSFIT_CIV_line_params.dat'
 qsfit = ascii.read(path+infile)
-
+ncomp = input("Number of CIV line components?")  # Python 3
+ncomp = np.int64(ncomp)
 
 ##  S E T T I N G   U P   T H E   P L O T
 ##
@@ -160,6 +161,8 @@ for ii in range(len(qsfit)):
     print(ii, qsfit['FILENAME'][ii], '       ', qsfit['NCOMP'][ii],  qsfit['LUM'][ii], qsfit['FWHM'][ii], qsfit['VOFF'][ii])
     if ii == 0:
         #j=0; k=0
+        ax1.plot(J12_first_wave,  J12_first_flux, '-b', lw=linewidth)
+        
         norm       = qsfit['LUM'][ii]                ## 10^42 erg s^-1
         fwhm       = qsfit['FWHM'][ii]               ## km/s
         v_off      = qsfit['VOFF'][ii]               ## km/s
@@ -171,8 +174,8 @@ for ii in range(len(qsfit)):
     
         line_profile = (peak_value * (np.exp( -((J12_first_wave - x0) / sigma)**2 / 2.)))+cont_off
 
-        ax1.plot(J12_first_wave,  J12_first_flux, '-b', lw=linewidth)
-        ax1.plot(J12_first_wave,  line_profile,   '-b', lw=beefup)
+        if qsfit['NCOMP'][ii] == ncomp:
+            ax1.plot(J12_first_wave,  line_profile,   '-b', lw=beefup)
 
         norm_str = str(np.around(norm, decimals=3))
         fwhm_str = str(np.around(fwhm, decimals=3))
@@ -199,7 +202,8 @@ for ii in range(len(qsfit)):
         line_profile = (peak_value * (np.exp( -((J12_second_wave - x0) / sigma)**2 / 2.)))+cont_off
 
         ax2.plot(J12_second_wave, J12_second_flux, '-r', lw=linewidth)
-        ax2.plot(J12_second_wave, line_profile,    '-r', lw=beefup)
+        if qsfit['NCOMP'][ii] == ncomp:
+            ax2.plot(J12_second_wave, line_profile,    '-r', lw=beefup)
 
         norm_str = str(np.around(norm, decimals=3))
[…]

### 2019-11-14 tex/CIV_CLQs.tex
CIV_CLQs.tex update

@@
 
-For J1638+2827, our spectral observations cover 4030 days observed, 1265 days
-in the rest-frame. Here, in the initial epoch spectrum, \civ\ is broad
-and bright, as is \ciii. However, just over 400 days in the rest-frame
-later, the broad \civ\ and \ciii BEL have to faded, the continuum
-slope around 1400\AA\ has changed from $\approx$-1.48 to
-$\approx$-2.25, but the \lya/\nv emission complex is very similar in
+For J1638+2827, our spectral observations cover 4030 days observed,
+1265 days in the rest-frame. Here, in the initial epoch spectrum,
+\civ\ is broad and bright, as is C\,{\sc iii}. However, $\approx$400
+rest-frame days later, the broad \civ\ and \ciii BEL have faded, the
+continuum slope around 1400\AA\ has changed from $\approx-1.48$ to
+$\approx-2.25$, but the \lya/\nv emission complex is very similar in
 shape and line flux intensity. Around 870 days in the rest-frame after
@@
 signal-to-noise. The light curve is consistent with this spectral
-brightening, increasing from around $\sim$19.5-20.5th magnitude to
-$\sim$18.5 in the optical band. An absorption feature between  \lya and \nv
-is seen in all three spectral epochs.
+brightening, increasing from $\sim$20th magnitude to $\sim$18.5
+magnitude at optical wavelengths. An absorption feature between \lya
+and \nv is seen in all three spectral epochs.
 
 For J2228+2201, our spectral observations cover 2504 days observed,
-778 days in the rest-frame. Over the course of 240 days in the rest-frame, \civ\ and \ciii both {\it emerge} as BELs and
-the standard UV/blue continuum slope increases in flux.
-Then, over the course of 538 days in the rest-frame, the broadline emission, while still
-very present, reduces in line flux the UV/blue continuum diminishes,
-though is still more luminous than the initial BOSS spectrum.
+778 days in the rest-frame. Over the course of 240 rest-frame days,
+\civ\ and \ciii both {\it emerge} as BELs and the standard UV/blue
+continuum slope increases in flux.  Then, over the course of 538 days
+in the rest-frame, the broadline emission, while still very present,
+reduces in line flux the UV/blue continuum diminishes, though is still
+more luminous than the initial BOSS spectrum.
 
@@
 \end{figure}
-\subsection{Emission line evolution}
+\subsection{Emission Line Evolution}
 Emission line measurements from the catalogues of \citet{Shen2011}.
 \citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of
-\citet{Calderone2017} are presented in Table~\ref{tab:
-LineMeasurements}.
+\citet{Calderone2017} are presented in Table~\ref{tab:LineMeasurements}.
 
@@
      parameters.}
+   \label{fig:CIV_LineFits}
 \end{figure}
@@
 \section{Discussion}
-The variable properties of high-$z$
-quasars, however, has been less well studied. Reasons for this include
-more massive systems will tend to have longer timescales with e.g.
-$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.
+With $t_{\rm dyn} \propto M^{2}$, the variable properties of high-$z$
+quasars, generally with more massive SMBHs, has been less well
+studied.
 
+%Reasons for this include more massive systems will tend to have longer timescales with e.g. if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.
+%%
 The Balmer series in hydrogen is due to the recombination cascade

### 2019-11-15 tex/CIV_CLQs.tex
tex/CIV_CLQs.tex QSFIT to QSFit update

@@
 
-In particular we use the Quasar Spectral Fitting (QSFIT) software
+In particular we use the Quasar Spectral Fitting (QSFit) software
 package presented in \citet{Calderone2017}. This provides luminosity
@@
 emission lines, including \civ, \ciii and \mgii.  We process and fit
-all nine spectra using the lastest version (v1.3.0) of the QSFIT
+all nine spectra using the lastest version (v1.3.0) of the QSFit 
 \href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
@@
     of \AA\ .  Positive values of V$_{\rm off}$ means the line is
-    blueshifted.  All measuremennts are from QSFIT, except for J1638+2827
+    blueshifted.  All measuremennts are from QSFit, except for J1638+2827
     (MJD 54553) which are from \citet{Shen2011}.  $^{(d)}$Emission line
@@
   \caption{Quasar continuum $\nu L_{\nu}$ luminosities and slopes, at
-the fixed rest-frame wavelengths 1450\AA\ from QSFIT.  The
+the fixed rest-frame wavelengths 1450\AA\ from QSFit.  The
 luminosities are in units of 10$^{42}$~erg~s$^{-1}$.}

### 2019-11-15 tex/CIV_CLQs.tex
tex/CIV_CLQs.tex 3000Ang values added to Table 4
Big update in .tex for Discussion

@@
   \centering
-  \begin{tabular}{l l   r ll   r r r l}
+  \begin{tabular}{l l   r ll  r r l}
     \hline 
     \hline 
-    \multirow{3}{*}{Object} & \multirow{3}{*}{Redshift} &                        & \multirow{3}{*}{MJD} &  \multirow{3}{*}{Instrument}  & Exposure      &                   & \multirow{3}{*}{Notes} \\
-                            &                                                     &   {$g$-band}   &                                 &                                              &  Time           &    SDSS             & \\
-                                       &                                          &    (mag)           &                                 &                                              & (seconds)    & Plate-FiberID  & \\
+    \multirow{2}{*}{Object} & \multirow{2}{*}{Redshift} &  $g$-band     & \multirow{2}{*}{MJD} &  \multirow{3}{*}{Instrument}  & Exposure     &   SDSS               & \multirow{2}{*}{Notes} \\
+                            &                                                     &   (mag)           &                                 &                                               &  Time (secs) &   Plate-FiberID  & \\
     \hline  
-%                                         &                                         &                        &                                &                    &                              &                              & \\
     J120544.7+342252.4   & 2.068                               &   18.27             &  53498                   & SDSS                                    &  8057            & 2089-427             & \\
@@
                                          & 2.071                               &                         &  58693                  & DBSP                                     &  2400            &  ---                      &          \\
-                                         &                                       &                          &                                &                          &                     &                               &                              & \\
+                                         &                                       &                          &                               &                                              &                      &                               &                               \\
     J163852.9+282707.7   & 2.185                            &   19.77               &  54553                   & SDSS                                      &   4801            &  2948-614              & \\
@@
                                          &  2.182                           &                          &  58583                     & LRIS                                     &  1800              &  ---                      & \\
-                                        &                                      &                          &                                 &                            &                    &                              &                                & \\
+                                        &                                      &                          &                                 &                                              &                      &                              &                                 \\
     J222818.7+220102.9   & 2.217                           & 19.97                &  56189                  &  BOSS                                       &  2700            &   6118-720          & \\
@@
                                          &  2.222                         &                          &  58693                  &  DBSP                                         & 2400             &    ---                        &    \\
-  %                                     &                                       &                          &               &                            &                   &                              &                            & \\
     \hline \hline   
@@
 4$\times10^{5}$, implying a heating energy source of (soft) X-ray
-photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).
+photons.
 
@@
 We adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73$,
-$\Omega_{\rm M} = 0.27$, and $h = 0.71$ in order to be consistent with
-\citet{Hamann2017}. As a guide this cosmology has a $z=2.000$
-comoving radial distance of 5244.3 Mpc, a $\sim$1.25\% difference
-compared to 5179.0 Mpc from $\Omega_{\Lambda} = 0.70$, $\Omega_{\rm M}
-= 0.30$, and $h = 0.70$ that is used in \citet{Shen2011}.
+$\Omega_{\rm M} = 0.27$, and $h = 0.71$.
+% in order to be consistent with \citet{Hamann2017}.
+As a guide this cosmology has a $z=2.000$ comoving radial distance of 5244.3 Mpc, a $\sim$1.25\% difference compared to 5179.0 Mpc from $\Omega_{\Lambda} = 0.70$, $\Omega_{\rm M} = 0.30$, and $h = 0.70$ that is used in \citet{Shen2011}.
 
@@
 \section{Data, CLQ Selection and Line measurements}
-In this section we present the photometric data used to select the CLQs, and then
-give details to the multiwavelength data where we have it, obtained spectroscopy and
-emission lines measurements.
+In this section we present the photometric data used to select the
+CLQs, and then give details to the multiwavelength data where we have
+it. We then give details of the spectroscopic data including emission
+lines measurements.
 
@@
 \subsection{CLQ Selection}
-{\bf MJG to finalise this::} \\
+{\bf MJG to finalise this} \\
 Our high-$z$ CLQs were identified as follows.  We selected all 64,774
@@
 \subsubsection{Spectrophotometry}
-{\bf MJG to finish this::} \\
+{\bf MJG to finish this} \\
 We want all our spectra to have reliable flux calibrations.  SDSS
@@
    \vspace{-12pt}
-  \caption[]{The Change in \civ\ line width vs. line flux change. 
+   \caption[]{ {\bf NPR to update this}. 
+     The change in \civ\ line width vs. line flux change. 
 We compare our object J1638+2827 with the sample 
@@
 \end{figure}
-\subsection{Emission Line Evolution}
-Emission line measurements from the catalogues of \citet{Shen2011}.
-\citet{Hamann2017}, \citet{Kozlowski2017} or the QSFit routine of
+%\subsection{Emission Line Evolution}
+Emission line measurements from the QSFit routine of
 \citet{Calderone2017} are presented in Table~\ref{tab:LineMeasurements}. 
+and fits for the \civ\ line are given in~\ref{fig:CIV_LineFits}.
 
@@
 epoch-to-epoch flux ratio versus the ratio of line widths.
-
-For the BOSS spectrum of J2228+2201 on MJD 56189, some of the data are
-``masked'' (i.e. they have {\tt and\_mask} != 0) in the FITS file at
-wavelengths $\lesssim$1600\AA\ (rest-frame).  This typically means
-there is some potential problem in using those data. However, visual
-inspection shows strong broad \civ\ emission, so we disable the check on the mask,
-and report the line fits in Table~\ref{tab:LineMeasurements} and show the \civ\ line 
-fits in~\ref{fig:CIV_LineFits}.
 
@@
   \begin{centering}
-    \begin{tabular}{c c l l}
+    \begin{tabular}{l c l l  ll}
       \hline
       \hline
-      Object             & MJD      & Cont. Lumin        &  Cont. slope \\
+        Object       &  MJD     & \multicolumn{2}{c}{1450\AA\ Cont. }     & \multicolumn{2}{c}{3000\AA\  Cont.}  \\
+                         &             &  Lumin.          &  slope                              &  Lumin.  &    slope      \\
       \hline
-                             & 53498   &  40040$\pm$34  & -1.656$\pm$ 0.006 \\
-      J1205+3422    & 58538   &   ---                   &  ---     \\
-                             & 58693   &   ---                    &  ---     \\
-                             &              &                             & \\
-                             & 54553   &  3774$\pm$111   &  -1.472$\pm$0.197   \\
-      J1638+2827    & 55832  &  2433$\pm$14     &  -2.316$\pm$0.051  \\  
-                             & 58583   &  3292$\pm$9       &    -0.541$\pm$0.010 \\
-                             &              &                             &\\
-                            & 56189    &  ---                      &  ---     \\
-    J2228+2201     & 56960   &  7889$\pm$14      &  -1.729$\pm$0.015     \\
-                            & 58693   &  ---                       &  ---     \\
+                         & 53498   &  40040$\pm$34    & -1.66$\pm$0.01    & ---        & ---  \\
+ J1205               & 58538   &   ---                     &  ---                         & ---        & ---   \\
+                         & 58693   &   ---                     &  ---                         & ---        & --- \\
+                         &              &                              &                                  &       & \\
+                         & 54553   &  3774$\pm$111   &   -1.47$\pm$0.20    & ---                      & --- \\
+ J1638              & 55832    &  2433$\pm$14     &  -2.32$\pm$0.05    & 958$\pm$29        & -2.27$\pm$0.05 \\  
+                         & 58583   &  3292$\pm$9       &    -0.54$\pm$0.01  & 4595$\pm$18      &  -0.54$\pm$0.01 \\
+                         &              &                              &                                 &       &     \\ 
+                         & 56189    &  ---                     &  ---                         & 1114$\pm$107    & -0.46$\pm$0.21     \\
+J2228                & 56960   &  7889$\pm$14     &  -1.73$\pm$0.02   &  4634.1$\pm$28  &  -1.72$\pm$0.02      \\
+                         & 58693   &  ---                      &  ---                         &  ---                       &  ---  \\
       \hline
@@
     \caption{Quasar continuum $\nu L_{\nu}$ luminosities and slopes, at
-the fixed rest-frame wavelengths 1450\AA\ from QSFit.  The
+      the fixed rest-frame wavelengths 1450\AA\ and 3000\AA\ from QSFit.  The
       luminosities are in units of 10$^{42}$~erg~s$^{-1}$.}
@@
 \subsection{The \civ\ Baldwin Effect}
-The Baldwin Effect (Baldwin 1977) is an empirical %inverse
+The Baldwin Effect \citep[Beff; ][]{Baldwin1977} is an empirical 
 relation between emission-line REWs and continuum luminosity in
-quasars \citep[][]{Shields2007, Hamann2017, Calderone2017}
-%%
+quasars \citep[][]{Shields2007, Hamann2017, Calderone2017}.
+\citet{Hamann2017} and \citet{Calderone2017} present recent
+measurements of the Beff for large quasar samples.
+
 There is an anti-correlation between the emission-line REWs and
@@
 continuum luminosity increases, the EW decreses, see
-Figure~\ref{fig:CIV_Baldwin} Our Figure~\ref{fig:CIV_Baldwin} is a
-reproduction of Figure~15 from \citet{Calderone2017}.
+Figure~\ref{fig:CIV_Baldwin}. This figure, reproduces that of
+Figure~15 from \citet{Calderone2017}, but where we know
+add the measurements from the 3 \civ\ CLQ quasars at each epoch.
 
@@
 their bolometric luminosity gives a slope of $\beta=-0.251$, in line
-with that from \citet{Hamann2017} ($\beta=-0.23$).
-%%
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
-sodales est, vel cursus risus porta non. Vivamus vel pretium
-velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
-ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
-hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
-conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
-eu blandit. Donec in lacinia libero.
-
-Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
-at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
-in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
-nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
-nulla. Nullam eu augue id purus mollis dignissim sed et
-libero. Phasellus eget justo sed neque pellentesque egestas nec id
-arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
-vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
-imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
-neque id mi ultrices tristique. Integer quam libero, ornare vel
-gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
-cursus, dui nisl egestas augue, non fermentum nisl est nec
-nisi. Vestibulum nec mi justo, eget dapibus velit.
+with that from \citet[][ $\beta=-0.23$]{Hamann2017}.
 
@@
 \section{Discussion}
-With $t_{\rm dyn} \propto M^{2}$, the variable properties of high-$z$
-quasars, generally with more massive SMBHs, has been less well
-studied.
+\subsection{Continuum and Line Changes}
+\citet{Trakhtenbrot2019} report on the quasar 1ES 1927+654 which was
+initially seenn to lack broad emission lines and line-of-sight
+obscuration, i.e, a ``Type 2'' quasar at redshift $z=0.02$. This
+object is then seen to spectroscopically change with the appearance of
+a blue, featureless continuum, followed by the emergence of broad
+Balmer emission lines.  i.e. this quasar changes into a broad-line
+Type 1 after a raise in the continuum luminosity.  This suggests that
+there is (at least in some cases) a relationship between the continuum
+and broad emission lines in CLQs.  A similar scenario may have occured
+for the 3 high-$z$ quasars presented here, although we lack the
+high-cadence multiwavelength, multi-epoch coverage that
+\citet{Trakhtenbrot2019} present.  The multiwavelength data that
+\citet{Trakhtenbrot2019} have includes a UV spectrum of 1ES 1927+654.
+However, there is no evidence for broad UV emission lines, including
+\civ\ , \ciii\ , or \mgii.  The authors attribute the lack of broad UV
+emission lines to dust within the BLR, noting that to dust in the
+broadline emission region, noting that the continuum emission does not
+show any signs of dust extinction.
 
-%Reasons for this include more massive systems will tend to have longer timescales with e.g. if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.
-%%
-The Balmer series in hydrogen is due to the recombination cascade
-between different principal quantum numbers $n$, and
-the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
-Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
-H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
+\citet{MacLeod2019} present a sample of CLQs where the primary
+selection requires large-amplitude ($∣\Delta g∣ > 1 mag, ∣\Delta r∣ >
+0.5 mag$) variability over any of the available time baselines probed
+by the SDSS and Pan-STARRS1 surveys.  For our adopted signal-to-noise
+ratio threshold on variability of broad H$\beta$ emission, they find
+17 new CLQs (which is $\sim20$ of the observerd sample). These
+candidates are at lower Eddington ratio relative to the overall quasar
+population, while the CLQ fraction increases from 10\% to roughly
+half, as the continuum flux ratio between repeat spectra at 3420 \AA\
+(rest-frame) increases from 1.5 to 6.
+
+\citet{Homan2019} investigate the responsiveness of the \mgii broad
+emission line doublet in AGN on timescales of several years.  This
+study is based on a the same extremely variable quasar sample as was
+used for \citet{MacLeod2019}.  By again focussing on quasars that show
+large changes in their optical light-curves, \citet{Homan2019} find
+that \mgii clearly does respond to the continuum.  However, a key
+finding from \citet{Homan2019} is that the degree of responsivity
+varies strikingly from one object to another.  There are cases of
+\mgii changing by as much as the continuum, more than the continuum,
+or very little at all.  In the majority (72\%) of this highly variable
+sample, the behaviour of \mgii corresponds with that of H$\beta$.
+However, there are also examples of \mgii showing variation, but
+H$\beta$ does not, and vice versa.
+
+%Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the  H$\beta$ emission line.
+H$\beta$ emission is associated with a 2.55 eV energy difference.
 Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$.
 
-\civ\ is one of the strongest collisionally excited lines in quasar
-spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
-at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
-canonical BELR parameters deduced over from early analysis of the
-\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
-ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
-speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
-H$^{+}$).
-
-\civ\ probes the photoionization environment produced by the innermost
-disk, as indicated by RM time-delay measurements. In standard \citet{SS73}
+The \civ\ line is one of the strongest collisionally excited lines in quasar
+spectra \citet[e.g.][]{HamannFerland1999}, and 
+\civ\ emission probes the photoionization environment produced by the innermost
+disk, as indicated by RM time-delay measurements.
+%%
+In standard \citet{SS73}
 thin disk models, large changes in the continuum flux are not
@@
 \end{figure}
-\subsection{The Baldwin Effect}
+%\subsection{The Baldwin Effect}
 The variable properties of the rest-frame UV quasar emission lines
@@
 effect'' in which the physical driver may be the Eddington ratio.
-\citet{Ge2016} Broad emission lines is a prominent property of type I quasi-stellar objects (QSOs).
+\citet{Ge2016} Broad emission lines is a prominent property of Type 1 quasars.
 
@@
 \end{figure*}
-\subsection{Eddington ratios and State Changes} 
+\subsection{Eddington Ratios and State Changes} 
 The broad UV and optical lines in quasars are most sensitive to the
@@
 euismod. Cras vel auctor neque. Nam quis diam risus.
-
-Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
-at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
-in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
-nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
-nulla. Nullam eu augue id purus mollis dignissim sed et
-libero. Phasellus eget justo sed neque pellentesque egestas nec id
-arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
-vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
-imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
-neque id mi ultrices tristique. Integer quam libero, ornare vel
-gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
-cursus, dui nisl egestas augue, non fermentum nisl est nec
-nisi. Vestibulum nec mi justo, eget dapibus velit.
 

### 2019-11-15 plots/MJD_Eddington/mjd_vs_Eddington.py
plots/MJD_Eddington/MJD_vs_Eddington update

@@ -15,32 +15,46 @@ from matplotlib import colors as mcolors
 from astropy.io import ascii
 from astropy.io import fits
 
-##
-##  S h e n   et al.  (2 0 1 1)   D R 7 Q  
-##
-path = '../../data/QSO_CIV_catalogs/'
-filename ='Shen_dr7_bh_May_2010.fits'
-infile = path+filename
 
-## Okay, what we really want to do ;-)
-#data_table = pyfits.getdata(infile)
-data_in    = fits.open(infile)
-data_table = data_in[1].data
+##
+##  S h e n   et al.  (2 0 1 1)
+##  D R 7 Q  
+##
+path       = '../../data/QSO_CIV_catalogs/'
+filename   = 'Shen_dr7_bh_May_2010.fits'
+dr7q_in    = fits.open(path+filename)
+dr7q_table = dr7q_in[1].data
 
 ## Quick check on the format/dimensions of the FITS table file...
-print(type(data_table), '\n')
-print('The number of rows of is.... ',     data_table.shape,  '\n')
-print('The number of columns is...  ', len(data_table.names), '\n\n')
-
+print(type(dr7q_table), '\n')
+print('The number of rows of is.... ',     dr7q_table.shape,  '\n')
+print('The number of columns is...  ', len(dr7q_table.names), '\n\n')
 
 ## Making some senible selections and cuts 
-mjd_full    = data_table.field('MJD')
-logtau_full = data_table.field('LOGEDD_RATIO')
+mjd_full    = dr7q_table.field('MJD')
+logtau_full = dr7q_table.field('LOGEDD_RATIO')
 
-dr7q        = data_table[np.where(data_table['LOGEDD_RATIO'] > -9.0)]
+dr7q        = dr7q_table[np.where(dr7q_table['LOGEDD_RATIO'] > -9.0)]
 dr7q_mjd    = dr7q['MJD']
 dr7q_logtau = dr7q['LOGEDD_RATIO']
 dr7q_tau    = (10**dr7q['LOGEDD_RATIO'])*100
+
+
+## Kozlowski (2017)  and  Hamann et al. (2017)
+##  D R 1 2 Q 
+filename   = 'BOSS_Ham17Koz17_DR12Q.fits'
+dr12q_in    = fits.open(path+filename)
+dr12q_table = dr12q_in[1].data
+
+## Quick check on the format/dimensions of the FITS table file...
+print(type(dr12q_table), '\n')
[…]

### 2019-11-15 tex/CIV_CLQs.tex
big tex/CIV_CLQs.tex update

@@
 
-\subsubsection{Mid-infrared Photometry}
+\subsection{Multi-Wavelength Properties}
 Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning
-of the Wide-field Infrared Survey Explorer (WISE) mission \citep[2010
-January; ][]{Wright2010} through the fifth-year of NEOWISE-R
-operations \citep[2018 December; ][]{Mainzer2011}. The WISE scan
-pattern leads to coverage of the full-sky approximately once every six
-months (a ``sky pass''), albeit with a gap from 2011 February to 2013
-October when the satellite was placed in hibernation.  Hence, our
-light curves have a cadence of 6 months with a 32 month sampling
-gap. \\
-{\bf DS to check for any X-ray, radio etc.}
+of the {\it Wide-field Infrared Survey Explorer} ({\it WISE}) mission
+\citep[2010 January; ][]{Wright2010} through the fifth-year of {\it
+NEOWISE-R} operations \citep[2018 December; ][]{Mainzer2011}. The {\it
+WISE}WISE scan pattern leads to coverage of the full-sky approximately
+once every six months (a ``sky pass''), but the satellite was placed
+in hibernation in 2011 February and then reactivated in 2013
+October. Hence, our light curves have a cadence of 6 months with a
+32-month sampling gap. [{\it DANIEL to write something on FIRST
+non-detections; possibly check the X-rays too?}]
 
@@
   \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/MJD_vs_Eddington_20191104_v0pnt9.png}
+  {figures/MJD_vs_Eddington_20191115.png}
   \vspace{-12pt}

### 2019-11-29 data/QSFit/GC_20191125/GC.tex
major, major update

\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}

\begin{document}

\begin{table*}
  \small
  \begin{centering}
    \begin{tabular}{l | l | c c | c c c | c}
      \hline
      \hline
        Object         &  MJD         &  \multicolumn{2}{c}{Cont. @ 1450\AA }                        &   \multicolumn{3}{c}{CIV 1549\AA}                                   & Virial product \\
                       &              &       $\nu L_{\nu}$    &         Slope                       &   Luminosity             &     FWHM           &    V$_{\rm off}$    & log($\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$)\\
                       &              & $10^{42}$ erg s$^{-1}$ & (F$_\lambda \propto \lambda^\alpha$)  & $10^{42}$ erg s$^{-1}$ &     km s$^{-1}$    &    km s$^{-1}$      &  $\log(M)$ \\
      \hline                        
                       &  53498       &  38129   $\pm$ 39      &  -1.57 $\pm$ 0.01                   &  898    $\pm$ 15         &   6024 $\pm$  120  &     944 $\pm$  33   &   9.85 $\pm$ 0.02\\
          J1205+3422   &  58538       &   8550   $\pm$ 11      &  -1.41 $\pm$ 0.01                   &  385.2  $\pm$  3.9       &   7109 $\pm$   91  &    1085 $\pm$  29   &   9.67 $\pm$ 0.01\\  
                       &  58693$^*$   &   2725   $\pm$ 40      &  -1.27 $\pm$ 0.05                   &  161    $\pm$ 22         &  14997 $\pm$ 2500  &     922 $\pm$ 690   &  10.07 $\pm$ 0.13\\  
                                      &                        &                                     &                          &                    &                     &                  \\
                       &  54553       &   3579   $\pm$ 49      &  -1.16 $\pm$ 0.07                   &  293.6  $\pm$  8.8       &   4630 $\pm$  180  &     183 $\pm$  57   &   9.11 $\pm$ 0.04\\  
          J1638+2827   &  55832       &   2340   $\pm$ 15      &  -2.17 $\pm$ 0.05                   &   84.6  $\pm$  4.2       &   4733 $\pm$  290  &     172 $\pm$  89   &   9.04 $\pm$ 0.05\\  
                       &  58583       &   7793   $\pm$ 19      &  -2.02 $\pm$ 0.01                   &  367.5  $\pm$  4.3       &   4511 $\pm$   71  &      94 $\pm$  24   &   9.25 $\pm$ 0.01\\  
                                      &                        &                                     &                          &                    &                     &                  \\
                       &  56189$^*$   &    607   $\pm$ 49      &  -0.00 $\pm$ 0.16                   &   72.8  $\pm$ 11.3       &  14993 $\pm$ 2400  &     828 $\pm$ 691   &   9.74 $\pm$ 0.14\\  
          J2228+2201   &  56960       &   7842   $\pm$ 25      &  -1.72 $\pm$ 0.02                   &  301.0  $\pm$  7.2       &   7136 $\pm$  210  &    -276 $\pm$  64   &   9.65 $\pm$ 0.03\\ 
                       &  58693       &   2388.4 $\pm$  6.8    &  -1.22 $\pm$ 0.01                   &  145.4  $\pm$  1.5       &   6084 $\pm$   83  &     168 $\pm$  28   &   9.26 $\pm$ 0.01\\  
      \hline
      \hline
    \end{tabular}
    \caption{Continuum (at 1450\AA) and CIV spectral measurements for the three QSO considered in this work, at all observation epochs, as calculated by QSFit.  The last column shows the virial product calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$.  $^*$: The CIV line is very faint (with respect to the continuum), and the associated estimates are likely biased.}
    \label{tab:QSFit-results}
  \end{centering}
\end{table*}

We analyzed the spectra of the three QSO considered in this work, at all observation epochs, using the QSFit spectral fitting package \citep{Calderone2017}.  In this case the main advantage of using QSFit is that it allows to constrain the slope and luminosity of the broad band continuum of the source, using data at all available wavelengths. The relevant estimated quantities are shown in Tab.~\ref{tab:QSFit-results}, and the plot of the best fit model in the region of the CIV emission line are shon in Fig.~\ref{fig:QSFit-CIV}.  We used the standard settings in all analysis, except for the CIV emission line profile for which we used a Lorentzian profile (rather than a Gaussian one).  The latter allows to account for the rather narrow peak of the CIV line without adding a further, and typically highly degenerate, ``narrow'' line component to the model.  Only in two cases where the CIV line became barely distinguishable (marked with a $^*$ in Tab.~\ref{tab:QSFit-results}) a narrow component appeared in the spectra.  The latter is however much fainter than the main broad components detected at other epochs, hence we neglect it.

The QSO continuum (here evaluated at 1450\AA) and the CIV line luminosities follow a similar evolution, with a ratio of $\sim$~20--30, confirming that the main driver for emission line variability is likely the broad band continuum itself.  Also, for all sources except J1638+2827, the slope of the continuum changes with luminosity following a bluer-when-brighter pattern, suggesting that a distinct emerging component is responsible or both the slope and luminosity variations.  In J1638+2827 the opposite beahviour is observed, especially in the first observation epoch.  However, this may be a bias due to the limited wavelength range available which extends to $\lambda \sim 1240\AA$ for the first epoch, while it extend to shorter wavelengths for the other epochs (respectively 1140\AA and 1010\AA).  The latter suggests that the ``emerging'' component is more prominent at UV wavelengths, and a sufficent wavelength coverage is required to detect it.

In all cases where the CIV line profile is reliably constrained its FWHM is rather constant, with maximum variations $\lesssim$~1000 km s$^{-1}$, despite the significantly larger variations in the line luminosities.  The FWHM of broad lines is likely related to the mass of the supermassive black hole powering the QSO phenomenon, which is supposed to be constant on any human timescale.  Hence it is instructive to check whether the virial product, which is the basic quantity used to calculate the single epoch mass estimate, show any variation.  The virial product, calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$, is reported in the last column of Tab.~\ref{tab:QSFit-results}.  The uncertainty typically associated to the single epoch mass estimate is $\sim$~0.5 dex, hence the virial product at all epochs are remarkably constant and compatible with a single value of black hole mass for each source, even in those cases where the CIV estimates are possibly unreliable.  The object showing larger variation is J2228+2201, although the extreme values span a range of 0.48 dex.

Finally, also the velocity offsets of the CIV line are rather constant, and compatible with a single value (within 3$\sigma$).  The only exception is J2228+2201, where a significant change ($\sim 7 \sigma$) is observed between the second and third observation epochs.

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{QSFit-results}
   \vspace{-12pt}
   \caption{Temporal evolution of the Spectral properties of the three QSO considered in this work (Tab.~\ref{tab:QSFit-results})}.
     \label{fig:QSFit-results}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=.3\textwidth]{spec-2089-53498-0427}
  \includegraphics[width=.3\textwidth]{J1205p3422_58538}
  \includegraphics[width=.3\textwidth]{J1205p3422_58693}\\
  \includegraphics[width=.3\textwidth]{spec-2948-54553-0614}
  \includegraphics[width=.3\textwidth]{spec-5201-55832-0178_v5_10_0}
  \includegraphics[width=.3\textwidth]{J1638p2827_58583}\\
  \includegraphics[width=.3\textwidth]{spec-6118-56189-0720}
  \includegraphics[width=.3\textwidth]{spec-7582-56960-0790}
  \includegraphics[width=.3\textwidth]{J2228p2201_58693}
  \caption{Observed spectra and best fit model in the region relevant to CIV emission line for all QSO considered in this work}.
  \label{fig:QSFit-CIV}
\end{figure*}
\end{document}

\end{document}

### 2019-11-29 data/QSFit/GC_20191128/GC.tex
major, major update

--- 2019-11-29 data/QSFit/GC_20191125/GC.tex
@@
 \begin{table*}
-  \small
+  \scriptsize
   \begin{centering}
-    \begin{tabular}{l | l | c c | c c c | c}
+    \begin{tabular}{l | l | c c | c c c c | c}
       \hline
       \hline
-        Object         &  MJD         &  \multicolumn{2}{c}{Cont. @ 1450\AA }                        &   \multicolumn{3}{c}{CIV 1549\AA}                                   & Virial product \\
-                       &              &       $\nu L_{\nu}$    &         Slope                       &   Luminosity             &     FWHM           &    V$_{\rm off}$    & log($\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$)\\
-                       &              & $10^{42}$ erg s$^{-1}$ & (F$_\lambda \propto \lambda^\alpha$)  & $10^{42}$ erg s$^{-1}$ &     km s$^{-1}$    &    km s$^{-1}$      &  $\log(M)$ \\
+        Object         &  MJD         &  \multicolumn{2}{c}{Cont.
+@ 1450\AA }                        &   \multicolumn{4}{c}{CIV 1549\AA}                                                          &  Virial product \\
+                       &              &       $\nu L_{\nu}$    &         Slope                       &   Luminosity             &     FWHM           &    V$_{\rm off}$    &          EW          &  log($\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$)\\
+                       &              & $10^{42}$ erg s$^{-1}$ & (F$_\lambda \propto \lambda^\alpha$)  & $10^{42}$ erg s$^{-1}$ &     km s$^{-1}$    &    km s$^{-1}$      &          \AA         &  $\log(M)$ \\
       \hline                        
-                       &  53498       &  38129   $\pm$ 39      &  -1.57 $\pm$ 0.01                   &  898    $\pm$ 15         &   6024 $\pm$  120  &     944 $\pm$  33   &   9.85 $\pm$ 0.02\\
-          J1205+3422   &  58538       &   8550   $\pm$ 11      &  -1.41 $\pm$ 0.01                   &  385.2  $\pm$  3.9       &   7109 $\pm$   91  &    1085 $\pm$  29   &   9.67 $\pm$ 0.01\\  
-                       &  58693$^*$   &   2725   $\pm$ 40      &  -1.27 $\pm$ 0.05                   &  161    $\pm$ 22         &  14997 $\pm$ 2500  &     922 $\pm$ 690   &  10.07 $\pm$ 0.13\\  
-                                      &                        &                                     &                          &                    &                     &                  \\
-                       &  54553       &   3579   $\pm$ 49      &  -1.16 $\pm$ 0.07                   &  293.6  $\pm$  8.8       &   4630 $\pm$  180  &     183 $\pm$  57   &   9.11 $\pm$ 0.04\\  
-          J1638+2827   &  55832       &   2340   $\pm$ 15      &  -2.17 $\pm$ 0.05                   &   84.6  $\pm$  4.2       &   4733 $\pm$  290  &     172 $\pm$  89   &   9.04 $\pm$ 0.05\\  
-                       &  58583       &   7793   $\pm$ 19      &  -2.02 $\pm$ 0.01                   &  367.5  $\pm$  4.3       &   4511 $\pm$   71  &      94 $\pm$  24   &   9.25 $\pm$ 0.01\\  
-                                      &                        &                                     &                          &                    &                     &                  \\
-                       &  56189$^*$   &    607   $\pm$ 49      &  -0.00 $\pm$ 0.16                   &   72.8  $\pm$ 11.3       &  14993 $\pm$ 2400  &     828 $\pm$ 691   &   9.74 $\pm$ 0.14\\  
-          J2228+2201   &  56960       &   7842   $\pm$ 25      &  -1.72 $\pm$ 0.02                   &  301.0  $\pm$  7.2       &   7136 $\pm$  210  &    -276 $\pm$  64   &   9.65 $\pm$ 0.03\\ 
-                       &  58693       &   2388.4 $\pm$  6.8    &  -1.22 $\pm$ 0.01                   &  145.4  $\pm$  1.5       &   6084 $\pm$   83  &     168 $\pm$  28   &   9.26 $\pm$ 0.01\\  
+                       &  53498       &  38129   $\pm$ 39      &  -1.57 $\pm$ 0.01                   &  898    $\pm$ 15         &   6024 $\pm$  120  &     944 $\pm$  33   &   37.78 $\pm$  0.62  &   9.85 $\pm$ 0.02\\
+          J1205+3422   &  58538       &   8550   $\pm$ 11      &  -1.41 $\pm$ 0.01                   &  385.2  $\pm$  3.9       &   7109 $\pm$   91  &    1085 $\pm$  29   &   71.32 $\pm$  0.71  &   9.67 $\pm$ 0.01\\
+                       &  58693$^*$   &   2725   $\pm$ 40      &  -1.27 $\pm$ 0.05                   &  161    $\pm$ 22         &  14997 $\pm$ 2500  &     922 $\pm$ 690   &   91.68 $\pm$ 12.73  &  10.07 $\pm$ 0.13\\
+                                      &                        &                                     &                          &                    &                     &                      &                  \\
+                       &  54553       &   3579   $\pm$ 49      &  -1.16 $\pm$ 0.07                   &  293.6  $\pm$  8.8       &   4630 $\pm$  180  &     183 $\pm$  57   &  127.67 $\pm$  3.80  &   9.11 $\pm$ 0.04\\
+          J1638+2827   &  55832       &   2340   $\pm$ 15      &  -2.17 $\pm$ 0.05                   &   84.6  $\pm$  4.2       &   4733 $\pm$  290  &     172 $\pm$  89   &   59.61 $\pm$  2.98  &   9.04 $\pm$ 0.05\\
+                       &  58583       &   7793   $\pm$ 19      &  -2.02 $\pm$ 0.01                   &  367.5  $\pm$  4.3       &   4511 $\pm$   71  &      94 $\pm$  24   &   77.89 $\pm$  0.91  &   9.25 $\pm$ 0.01\\
+                                      &                        &                                     &                          &                    &                     &                      &                  \\
+                       &  56189$^*$   &    607   $\pm$ 49      &  -0.00 $\pm$ 0.16                   &   72.8  $\pm$ 11.3       &  14993 $\pm$ 2400  &     828 $\pm$ 691   &  162.89 $\pm$ 25.37  &   9.74 $\pm$ 0.14\\
+          J2228+2201   &  56960       &   7842   $\pm$ 25      &  -1.72 $\pm$ 0.02                   &  301.0  $\pm$  7.2       &   7136 $\pm$  210  &    -276 $\pm$  64   &   61.99 $\pm$  1.48  &   9.65 $\pm$ 0.03\\
+                       &  58693       &   2388.4 $\pm$  6.8    &  -1.22 $\pm$ 0.01                   &  145.4  $\pm$  1.5       &   6084 $\pm$   83  &     168 $\pm$  28   &   94.77 $\pm$  0.99  &   9.26 $\pm$ 0.01\\
       \hline

### 2019-11-29 tex/CIV_CLQs.tex
major, major update

@@
 \date{Accepted XXX. Received YYY; in original form ZZZ}
-\pubyear{2018}
 
@@
 We report on three redshift $z>2$ quasars with dramatic changes in
-their \civ\ emission lines, the first ``Changing-Look'' quasars at high
-redshift.  This is also the first time the changing-look behaviour has
-been seen in a high-ionization emission line.
-%%
-SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
-in their observed optical light curves, and subsequent spectroscopy
-shows significant changes in the \civ\ broad emission line, with both
-line collapse and emergence being displayed in rest-frame timescales
-of $\sim$240-1640 days.
-%%
-Where observed, the profile of the Ly$\alpha$/\nv emission complex
-also changes, and there is tentative evidence for changes in the \mgii
-line.
-%%
-Although line measurements from the three quasars show large changes
-in the \civ\ flux-line width plane, the quasars are not seen to
-be outliers when considered against the full $z\sim2$ quasar population
-in terms of (rest) Equivalent Width and FWHM properties.
-%%
-We put these observations in context with recent ``state-change''
-models, but note that even in their `low-state', the \civ\ CLQs are
-above $\sim$10\% in Eddington luminosity.
+their \civ\ emission lines, the first ``Changing-Look'' quasars at
+high redshift.  This is also the first time the changing-look
+behaviour has been seen in a high-ionization emission line.  SDSS
+J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour in
+their observed optical light curves, and subsequent spectroscopy shows
+significant changes in the \civ\ broad emission line, with both line
+collapse and emergence being displayed in rest-frame timescales of
+$\sim$240-1640 days.  Where observed, the profile of the
+Ly$\alpha$/\nv emission complex also changes, and there is tentative
+evidence for changes in the \mgii line.  Although line measurements
+from the three quasars show large changes in the \civ\ flux-line width
+plane, the quasars are not seen to be outliers when considered against
+the full $z\sim2$ quasar population in terms of (rest) Equivalent
+Width and FWHM properties.  We put these observations in context with
+recent ``state-change'' models, but note that even in their
+`low-state', the \civ\ CLQs are above $\sim$10\% in Eddington
+luminosity.
 \end{abstract}
 
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
 \begin{keywords}
-accretion, accretion discs -- surveys -- quasars: general -- quasars: individual: J1100-0053 
+accretion, accretion discs -- surveys -- quasars: general -- quasars: time-domain: 
 \end{keywords}
@@
 ][]{MacLeod2012} whereas the CSQs have a `state-transition' similar to
-that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019}. In
+that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019a}. In
 this paper, we use the term `Changing Look', as we are currently
@@
       Line                 & $\lambda$ &  Transition  & Ionization   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
-%                              &    / \AA\    &      / eV             &  / eV            &   Lower                  & Conf.
-&  $J$       & Upper                      &  Conf.
-& $J$       & / cm$^{-1}$    &  / s$^{-1}$                \\      \hline
                               &  / \AA\    & energy / eV &  energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & ($\times10^{8}$  / s$^{-1}$)               \\      \hline
@@
     \end{tabular}
-    \caption{Strong UV/optical spectral emission lines in quasars, and their atomic data.
-      Data from the NIST Atomic Spectra Database       \citep{Kramida2018, Kramida2019}.
-      The Transition Energies are $E=hc/\lambda$ for the given wavelength. The Ionization Energy is the
-      energy required to ionize the given species, e.g. 64.49 eV are needed to create a \cv\ ion.
-      Transitions Level configurations are given in standard spectroscopic notation
-      %($N^{2s+1}$ $L_{j}$. 
-      $A_{i,j}$ are transition probabilities.
-%      $A_{i,j}$ are \href{https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-6}{transition probabilities}.} 
-%      such that the radiative lifetime $\tau_{k}$ of an atomic level $k$ is related to the sum of transition probabilities to all levels $i$ lower in energy than $k$
-%      The 1548.202 and 1550.774 \AA\ emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition, split by total angular momentum $J= 3/2$ and $1/2$. 
-      Data from the NIST Atomic Spectra Database       \citep{Kramida2018, Kramida2019}.}
-    %% 
-    %%  Mg II Z = 12, Na isoelectronic sequence  
+    \caption{
+      Strong UV/optical spectral emission lines in quasars, and their
+      atomic data.  Data from the NIST Atomic Spectra Database
+      \citep{Kramida2018, Kramida2019}.  The Transition Energies are
+      $E=hc/\lambda$ for the given wavelength. The Ionization Energy is the
+      energy required to ionize the given species, e.g. 64.49 eV are needed
+      to create a \cv\ ion.  Transitions Level configurations are given in
+      standard spectroscopic notation $A_{i,j}$ are transition
+      probabilities.  Data from the NIST Atomic Spectra Database
+      \citep{Kramida2018, Kramida2019}.}
     \label{tab:atomic_lines}
@@
 \civ, these have tended to focus on broad absorption line quasars
-\citep[BAL QSOs; see Table 1 of][]{Hemler2019} or the Baldwin Effect
+\citep[BAL quasars; see Table 1 of][]{Hemler2019} or the Baldwin Effect
 \citep[BEff; ][]{Baldwin1977, Bian2012, Jensen2016,
@@
     \hline  
-    J120544.7+342252.4   & 2.068                               &   18.27             &  53498                   & SDSS                                    &  8057            & 2089-427             & \\
-                                        & 2.071                                &                        &  58538                   & DBSP                                     &  1800            &  ---                      &  Average conditions \\
+                                       & 2.068                              & 18.27          &  53498                   & SDSS                                     &  8057            & 2089-427             & \\
+ J120544.7+342252.4     & 2.071                             &                    &  58538                   & DBSP                                     &  1800            &  ---                      &  Average conditions \\
                                        & 2.071                             &                     &  58693                  & DBSP                                      &  2400            &  ---                      &          \\
                                        &                                       &                     &                               &                                              &                      &                               &                               \\
-    J163852.9+282707.7   & 2.185                            &   19.77               &  54553                   & SDSS                                      &   4801            &  2948-614              & \\
-    	                                 &  2.186                            &                          &  55832                  & BOSS                                      &   3600            &  5201-178            & \\
+                                      & 2.185                              & 19.77           &  54553                   & SDSS                                     &   4801            &  2948-614              & \\
+J163852.9+282707.7     & 2.186                              &                    &  55832                     & BOSS                                    &   3600            &  5201-178            & \\
                                       & 2.182                              &                     &  58583                     & LRIS                                    &  1800              &  ---                      & \\
                                       &                                         &                    &                                 &                                            &                      &                              &                                 \\
-    J222818.7+220102.9   & 2.217                           & 19.97                &  56189                  &  BOSS                                       &  2700            &   6118-720          & \\
-                                          & 2.222                         &                          &  56960                    & BOSS                                       &  4500            &   7582-790          & eBOSS reobservation \\
+                                      & 2.217                               & 19.97          &  56189                    &  BOSS                                    &  2700            &   6118-720          & \\
+ J222818.7+220102.9   & 2.222                               &                    &  56960                     & BOSS                                    &  4500            &   7582-790          & eBOSS reobservation \\
                                      &  2.222                               &                    &  58693                    &  DBSP                                    & 2400             &    ---                        &    \\
@@
   \end{tabular}
-  \caption{
-    Details of our spectroscopic observations.
-%    Redshift and redshift errors from SDSS SkyServer for SDSS, BOSS and eBOSS spectra.
-    Redshift errors are typically  $\pm$0.002. 
-    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and  eBOSS spectra have $\mathcal{R}\sim$2,000.
-    DBSP: Double Spectrograph on the Palomar 200-inch telescope.
-    LRIS:  Low Resolution Imaging Spectrometer on Keck I 10m telescope.
-    %  2019-Feb-24    & DBSP            &  2$\times$900 f
-    %  2019-Jul-29     & DBSP            &  2$\times$1200
-    %  2019-Apr-10     & LRIS              &  2$\times$900
-    %& 2019-Jul-29       & DBSP             & 2$\times$1200
-  } 
+  \caption{Details of our spectroscopic observations.  Redshift errors are
+    typically $\pm$0.002.  SDSS, BOSS and eBOSS spectra have
+    $\mathcal{R}\sim$2,000.  DBSP: Double Spectrograph on the Palomar
+    200-inch telescope.  LRIS: Low Resolution Imaging Spectrometer on Keck
+    I 10m telescope.} 
   \label{tab:obs_notes}
@@
 This paper is organised as follows. In Section 2, we describe our
-sample selection, catalogues, and observational data sets.  In Section 3,
-we show the high-$z$ quasars and report the line properties for the
+sample selection, catalogues, and observational data sets.  In Section
+3, we show the high-$z$ quasars and report the line properties for the
 quasars at the observed epochs.  We give a very brief theoretical
@@
 report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
-Fukugita1996} unless otherwise stated. For the WISE bands,
-$m_{\rm AB} = m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1
-at 3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively
-\citep{Cutri2011}.
-We adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73$,
-$\Omega_{\rm M} = 0.27$, and $h = 0.71$.
-% in order to be consistent with \citet{Hamann2017}.
-As a guide this cosmology has a $z=2.000$ comoving radial distance of 5244.3 Mpc, a $\sim$1.25\% difference compared to 5179.0 Mpc from $\Omega_{\Lambda} = 0.70$, $\Omega_{\rm M} = 0.30$, and $h = 0.70$ that is used in \citet{Shen2011}.
+Fukugita1996} unless otherwise stated. For the WISE bands, $m_{\rm AB}
+= m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1 at
+3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011}. We
+adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73 $,
+$\Omega_{\rm M} = 0.27$, and $h = 0.71$. All logarithms are to the base 10.
 
@@
 \subsection{Multi-Wavelength Properties}
+{\bf DS to write something on FIRST non-detections; possibly check the X-rays too?} \\
 Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning
@@
 October. Hence, our light curves have a cadence of 6 months with a
-32-month sampling gap. [{\it DANIEL to write something on FIRST
-non-detections; possibly check the X-rays too?}]
+32-month sampling gap.
 
@@
 Our high-$z$ CLQs were identified as follows.  We selected all 64,774
-SDSS DR15 sources with $z > 0.35$ classified as `QSO', having at least
+SDSS DR15 sources with $z > 0.35$ classified as `quasar', having at least
 two spectra separated by at least 100 days, and with a corresponding
@@
 \subsubsection{Spectrophotometry}
-{\bf MJG to finish this} \\
+{\bf MJG to check/finalise} \\
 We want all our spectra to have reliable flux calibrations.  SDSS
@@
 \href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
-calculator}.
-% and setting $E(B-V)=0.00$.
-%%
-The host galaxy and blended iron emission at rest-frame optical
-wavelengths components are automatically disabled when they can not be
-constrained by the available data, such as the case for all our
-objects (we do not have infrared spectral data).
-%%
-Power-law continuum slopes, $\alpha$, where $f_{\lambda} \propto
+calculator}. The host galaxy and blended iron emission at rest-frame
+optical wavelengths components are automatically disabled when they
+can not be constrained by the available data, such as the case for all
+our objects (we do not have infrared spectral data).  Power-law
+continuum slopes, $\alpha$, where $f_{\lambda} \propto
 \lambda^{\alpha}$, are also reported in these catalogues and from
@@
 
+\begin{table*}
+  \small
+  \begin{centering}
+    \begin{tabular}{l  l | c c | c c c c | c}
+      \hline
+      \hline
+              &          &  \multicolumn{2}{c}{Cont.
+@ 1450\AA }                  &   \multicolumn{4}{c}{CIV 1549\AA}                                                                                & Virial product \\
+Object    & MJD  &      $\nu L_{\nu}$    &         Slope                             &   Luminosity         &     FWHM                 &    V$_{\rm off}$    & EW                                 & log($\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$) \\
+ & & $10^{42}$ erg s$^{-1}$ & (F$_\lambda \propto \lambda^\alpha$)  & $10^{42}$ erg s$^{-1}$ &  km s$^{-1}$   &     km s$^{-1}$   &  \AA                              &  $\log(M/M_{\odot})$ \\
+      \hline
+                     & 53498   &  38129  $\pm$ 39  &  -1.57 $\pm$ 0.01 &   898 $\pm$ 15    &   6024 $\pm$  120  &  944 $\pm$  33  & 37.78 $\pm$  0.62  &   9.85 $\pm$ 0.02\\
+ J1205+3422 & 58538    &  8550 $\pm$ 11    &  -1.41 $\pm$ 0.01 &  385.2 $\pm$ 3.9 &   7109 $\pm$   91   & 1085 $\pm$  29  &   71.32 $\pm$  0.71  &   9.67 $\pm$ 0.01\\  
+                     & 58693$^*$ & 2725 $\pm$ 40 &  -1.27 $\pm$ 0.05 &  161 $\pm$ 22    &  14997 $\pm$ 2500 &  922 $\pm$ 690  & 91.68 $\pm$ 12.73  &  10.07 $\pm$ 0.13\\  
+                      &              &                               &                               &                              &                                 &                             &                                   &                              \\
+                      & 54553   & 3579 $\pm$ 49    &  -1.16 $\pm$ 0.07  & 293.6  $\pm$ 8.8 &  4630 $\pm$  180   & 183 $\pm$  57   & 127.67 $\pm$  3.80  &    9.11 $\pm$ 0.04\\  
+ J1638+2827 & 55832   & 2340 $\pm$ 15    &  -2.17 $\pm$ 0.05  &  84.6  $\pm$ 4.2  &  4733 $\pm$  290   & 172 $\pm$  89   &  59.61 $\pm$  2.98  &    9.04 $\pm$ 0.05\\  
+                      & 58583  & 7793 $\pm$ 19     &  -2.02 $\pm$ 0.01  & 367.5  $\pm$ 4.3 &  4511 $\pm$   71    &  94 $\pm$  24   &  77.89 $\pm$  0.91  &  9.25 $\pm$ 0.01\\  
+                      &             &                               &                                &                              &                                 &                            &                                   &                            \\
+                     & 56189$^*$ & 607 $\pm$ 49  &  -0.00 $\pm$ 0.16 &  72.8  $\pm$ 11.3 & 14993 $\pm$ 2400 &  828 $\pm$ 691   & 162.89 $\pm$ 25.37  &  9.74 $\pm$ 0.14\\  
+ J2228+2201 & 56960   & 7842 $\pm$ 25     &  -1.72 $\pm$ 0.02 & 301.0  $\pm$ 7.2  &  7136 $\pm$  210   & -276 $\pm$  64   &  61.99 $\pm$  1.48  &    9.65 $\pm$ 0.03\\ 
+              & 58693   & 2388.4 $\pm$ 6.8 &  -1.22 $\pm$ 0.01 & 145.4  $\pm$ 1.5  &  6084 $\pm$   83    &   168 $\pm$  28   &  94.77 $\pm$  0.99  &    9.26 $\pm$ 0.01\\
+      \hline
+      \hline
+    \end{tabular}
+    \caption{Continuum at 1450\AA\ and \civ\ spectral measurements for the
+      three quasar considered in this work, at all observation epochs, as
+      calculated by QSFit.  The last column shows the virial product
+      calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$.  $^{*}$The
+      \civ\ line is very faint (with respect to the continuum), and the
+      associated estimates are likely unreliable.}
+    \label{tab:QSFit-results}
+  \end{centering}
+\end{table*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Results}
-\subsection{Photometric and Spectral Evolution}
+\subsection{Photometric and Overal Spectral Evolution}
 Figure~\ref{fig:civ_clqs} presents the optical and mid-IR light
@@
 
-\begin{figure}
+\subsection{\civ\ Emission Line Evolution}
+We analyzed the spectra of the three quasars, at all observational
+epochs, using the QSFit spectral fitting package
+\citep{Calderone2017}.  One advantage of using QSFit is that it allows
+constraints on the slope and luminosity of the broad band continuum of
+the source. The relevant estimated quantities, including continuum
+luminosity and slope at rest-frame 1450\AA, \civ\ line luminosity,
+FWHM and EW are given in Tab.~\ref{tab:QSFit-results}. All fits are
+performed with $E(B-V) = 0$ and the best fit model in the region of
+the \civ\ emission line are shown in Figure~\ref{fig:QSFit-CIV}.
+
+All \civ\ lines are fitted with a single, broad, Lorentzian profile.
+This allows us to account for the narrow peak of the \civ\ line. 
+No narrow components are considered for several reasons: in the epochs
+of highest brightness the ``narrow'' component would have FWHM
+$\sim2-3 \times 10^{3}$ km s$^{-1}$, i.e. values exceeding the usual
+widths of genuine narrow lines ($\lesssim 10^3$ km s$^{-1}$); by
+allowing a second component, to have such large widths their
+parameters would become highly degenerate with the ``broad''
+components, and the latter would also have much larger FWHM
+($\sim10^{4}$ km s$^{-1}$); and by neglecting the narrow components we
+have a consistent fit across all epochs.
+
+The quasar continuum, evaluated at 1450\AA\ , and the \civ\ line
+luminosities follow a similar evolution, with a ratio of $\sim$20-30,
+confirming that the main driver for emission line variability is
+likely the broad band continuum itself.  For all sources except
+J1638+2827, the slope of the continuum changes with luminosity
+following a ``bluer-when-brighter'' pattern, suggesting that a
+distinct emerging component is responsible or both the slope and
+luminosity variations.  In J1638+2827 the opposite behaviour is
+observed, especially in the first observation epoch.  However, this
+may be a bias due to the limited wavelength range available which
+extends to $\lambda \sim 1240\AA$ for the first epoch, while it extend
+to shorter wavelengths for the other epochs (respectively 1140\AA\ and
+1010\AA).  The latter suggests that the ``emerging'' component is more
+prominent at UV wavelengths, and a sufficient wavelength coverage is
+required to detect it. We find there is no need for a narrow component
+in J2228+2201 MJD 56189.  This is because the data resemble a P-Cygni
+profile, with blueshifted absorption. This feature is very narrow, and
+the uncertainties large, such that the overall $\chi^{2}$ is only
+marginally affected by the addition of a further component. We
+therefore avoid using a narrow component for this spectrum only, since
+that would be inconsistent with the other analyses.
+
+In all cases where the \civ\ line profile is reliably constrained the
+\civ\ FWHM is approximately constant, with maximum variations
+$\lesssim$~1000 km s$^{-1}$, despite the significantly larger
+variations in the line luminosities.  The FWHM of broad lines is
+likely related to the mass of the supermassive black hole powering the
+quasar phenomenon, which is supposed to be constant on any human
+timescale.  Hence it is instructive to check whether the virial
+product, which is the basic quantity used to calculate the single
+epoch mass estimate, show any variation.  The virial product,
+calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$, is reported in
+the last column of Tab.~\ref{tab:QSFit-results}.  The uncertainty
+typically associated to the single epoch mass estimate is $\sim$0.5
+dex, hence the virial product at all epochs are remarkably constant
+and compatible with a single value of black hole mass for each source,
+even in those cases where the \civ\ estimates are possibly
+unreliable. The object showing larger variation is J2228+2201,
+although the extreme values span a range of 0.48 dex.
+
+Finally, also the velocity offsets of the \civ\ line are also
+approximately constant, and compatible with a single value (within
+3$\sigma$).  The exception is J2228+2201, where a significant change
+($\sim$7$\sigma$) is observed between the second and third observation
+epochs.
+
+The temporal evolution of the velocity offsets, along with the
+1450\AA\ continuum luminosity and slope, the \civ\ line FWHM
+and virial black hole mass are given in Figure~\ref{fig:QSFit-results}.
+
+%% trim={<left> <lower> <right> <upper>}
+\begin{figure*}
   \centering
-  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
-  {figures/Wilhite_2006_Fig2_redux_20190926.png}
+ \includegraphics[width=\textwidth, trim={0cm 0 0 0},clip]{figures/CIVregions.png}
+%  \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-2089-53498-0427.png}
+ % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J1205p3422_58538.png}
+ % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J1205p3422_58693.png}\\
+ % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-2948-54553-0614.png}
+ % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-5201-55832-0178_v5_10_0.png}
+ % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J1638p2827_58583.png}\\
+ % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-6118-56189-0720.png}
+ % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-7582-56960-0790.png}
+ % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J2228p2201_58693.png}
+  \caption{Observed spectra and best fit model in the region relevant
+    to \civ\ emission line for the quasars considered here.}
+  \label{fig:QSFit-CIV}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{figures/QSFit-results}
   \vspace{-12pt}
-   \caption[]{ {\bf NPR to update this}. 
-     The change in \civ\ line width vs. line flux change. 
-We compare our object J1638+2827 with the sample 
-from \citet{Wilhite2006} with a sample of 105 quasars observed at
-multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
-in this parameter space.}
-  \label{fig:Wilhite2006_comparison}
-\end{figure}
-%\subsection{Emission Line Evolution}
-Emission line measurements from the QSFit routine of
-\citet{Calderone2017} are presented in Table~\ref{tab:LineMeasurements}. 
-and fits for the \civ\ line are given in~\ref{fig:CIV_LineFits}.
+  \caption{Temporal evolution of the spectral properties of the three
+    quasar considered in this work.}
+  \label{fig:QSFit-results}
+\end{figure*}
 
-From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
-strong correlation between the change in the line flux and the change
-in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
-epoch-to-epoch flux ratio versus the ratio of line widths.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=8.5cm, trim=0.4cm 0.4cm 0.2cm 0.4cm, clip]
-  {figures/CIV_fits_20191108.png}
-   \vspace{-12pt}
-   \caption[]{The \civ\ emission line and the subsequent QSFit model and
-     parameters.}
-   \label{fig:CIV_LineFits}
-\end{figure}
-
-\begin{table*}
-  \centering
-  % \input{emission_line_comparison_tab}
-  \input{emission_line_tab}
-  \caption{Line Measurement information for the nine epochs for the 3
-    quasars.  Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM
-    and $V_{\rm off}$ in km s$^{-1}$, where positive values of $V_{\rm
-      off}$ means the line is blueshifted.  Equivalent widths are in units
-    of \AA\ .  Positive values of V$_{\rm off}$ means the line is
-    blueshifted.  All measuremennts are from QSFit, except for J1638+2827
-    (MJD 54553) which are from \citet{Shen2011}.  $^{(d)}$Emission line
-    modelled with two components.}
- \label{tab:LineMeasurements}
-\end{table*}
-
-\begin{table}
-  \begin{centering}
-    \begin{tabular}{l c l l  ll}
-      \hline
-      \hline
-        Object       &  MJD     & \multicolumn{2}{c}{1450\AA\ Cont. }     & \multicolumn{2}{c}{3000\AA\  Cont.}  \\
-                         &             &  Lumin.          &  slope                              &  Lumin.  &    slope      \\
-      \hline
-                         & 53498   &  40040$\pm$34    & -1.66$\pm$0.01    & ---        & ---  \\
- J1205               & 58538   &   ---                     &  ---                         & ---        & ---   \\
-                         & 58693   &   ---                     &  ---                         & ---        & --- \\
-                         &              &                              &                                  &       & \\
-                         & 54553   &  3774$\pm$111   &   -1.47$\pm$0.20    & ---                      & --- \\
- J1638              & 55832    &  2433$\pm$14     &  -2.32$\pm$0.05    & 958$\pm$29        & -2.27$\pm$0.05 \\  
-                         & 58583   &  3292$\pm$9       &    -0.54$\pm$0.01  & 4595$\pm$18      &  -0.54$\pm$0.01 \\
-                         &              &                              &                                 &       &     \\ 
-                         & 56189    &  ---                     &  ---                         & 1114$\pm$107    & -0.46$\pm$0.21     \\
-J2228                & 56960   &  7889$\pm$14     &  -1.73$\pm$0.02   &  4634.1$\pm$28  &  -1.72$\pm$0.02      \\
-                         & 58693   &  ---                      &  ---                         &  ---                       &  ---  \\
-      \hline
-      \hline
-    \end{tabular}
-    \caption{Quasar continuum $\nu L_{\nu}$ luminosities and slopes, at
-      the fixed rest-frame wavelengths 1450\AA\ and 3000\AA\ from QSFit.  The
-      luminosities are in units of 10$^{42}$~erg~s$^{-1}$.}
-    \label{tab:Baldwin}
-  \end{centering}
-\end{table}
-
-%%
-%% %% \eta_{\rm Edd} = log10((10**LBol)/((1.26e38)*(10**MBH)))
-%%
-%% Using    C IV
-%%
-%% In [6]: log10((10**47.216)/((1.26e38)*(10**9.49)))                                                                                                                                             
-%%Out[6]: -0.37437054511756207
-%%
-%%In [7]: log10((10**46.166)/((1.26e38)*(10**8.742)))                                                                                                                                            
-%%Out[7]: -0.676370545117567
-%%
-%%In [8]: log10((10**46.721)/((1.26e38)*(10**9.1289)))                                                                                                                                           
-%%Out[8]: -0.5082705451175662
-%%
-%%In [9]: log10((10**46.231)/((1.26e38)*(10**8.733)))                                                                                                                                            
-%%Out[9]: -0.6023705451175618
 \begin{table*}
@@
      \hline
-%                              &                                     &                                       &                                               &                             &                                &                  &                  & \\
- %   M87$^{*}$          &  57854	                     & ---                                &   43.187	                               & \multicolumn{2}{c}{9.812$\pm$0.044}    & 	\multicolumn{2}{c}{-4.699}   & EHT \\
-  %                                &                                     &                                       &                                               &                             &                                &                  &                  & \\
-     \hline
     \hline
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
+  {figures/CIV_CLQs_Baldwin_20191129.png}
+   \vspace{-12pt}
+   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
+     commonly referred to as The Baldwin Plot.
+     The continuum luminosities are  from \citet{Calderone2017},
+     the REW measurements are Table~\ref{tab:Baldwin}.}
+  \label{fig:CIV_Baldwin}
+\end{figure}
 \subsection{The \civ\ Baldwin Effect}
@@
 continuum luminosity increases, the EW decreses, see
-Figure~\ref{fig:CIV_Baldwin}. This figure, reproduces that of
-Figure~15 from \citet{Calderone2017}, but where we know
+Figure~\ref{fig:CIV_Baldwin}. This figure effectively reproduces Figure~15 from \citet{Calderone2017}, but where we now
 add the measurements from the 3 \civ\ CLQ quasars at each epoch.
@@
   \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
+  {figures/CIV_CLQs_REWvsFWHM_20191128.png}
    \vspace{-12pt}
@@
 \citet{MacLeod2019} present a sample of CLQs where the primary
-selection requires large-amplitude ($∣\Delta g∣ > 1 mag, ∣\Delta r∣ >
-0.5 mag$) variability over any of the available time baselines probed
-by the SDSS and Pan-STARRS1 surveys.  For our adopted signal-to-noise
-ratio threshold on variability of broad H$\beta$ emission, they find
-17 new CLQs (which is $\sim20$ of the observerd sample). These
-candidates are at lower Eddington ratio relative to the overall quasar
-population, while the CLQ fraction increases from 10\% to roughly
-half, as the continuum flux ratio between repeat spectra at 3420 \AA\
-(rest-frame) increases from 1.5 to 6.
-
-\citet{Homan2019} investigate the responsiveness of the \mgii broad
-emission line doublet in AGN on timescales of several years.  This
-study is based on a the same extremely variable quasar sample as was
-used for \citet{MacLeod2019}.  By again focussing on quasars that show
-large changes in their optical light-curves, \citet{Homan2019} find
-that \mgii clearly does respond to the continuum.  However, a key
-finding from \citet{Homan2019} is that the degree of responsivity
-varies strikingly from one object to another.  There are cases of
-\mgii changing by as much as the continuum, more than the continuum,
-or very little at all.  In the majority (72\%) of this highly variable
-sample, the behaviour of \mgii corresponds with that of H$\beta$.
-However, there are also examples of \mgii showing variation, but
-H$\beta$ does not, and vice versa.
+selection requires large-amplitude ($| \Delta g | > 1$ mag, $| \Delta
+r | > 0.5$ mag) variability over any of the available time baselines
+probed by the SDSS and Pan-STARRS1 surveys.  For our adopted
+signal-to-noise ratio threshold on variability of broad H$\beta$
+emission, they find 17 new CLQs (which is $\sim20$ of the observerd
+sample). These candidates are at lower Eddington ratio relative to the
+overall quasar population, while the CLQ fraction increases from 10\%
+to roughly half, as the continuum flux ratio between repeat spectra at
+3420 \AA\ (rest-frame) increases from 1.5 to 6.  \citet{Homan2019}
+investigate the responsiveness of the \mgii broad emission line
+doublet in AGN on timescales of several years.  This study is based on
+a the same extremely variable quasar sample as was used for
+\citet{MacLeod2019}.  By again focussing on quasars that show large
+changes in their optical light-curves, \citet{Homan2019} find that
+\mgii clearly does respond to the continuum.  However, a key finding
+from \citet{Homan2019} is that the degree of responsivity varies
+strikingly from one object to another.  There are cases of \mgii
+changing by as much as the continuum, more than the continuum, or very
+little at all.  In the majority (72\%) of this highly variable sample,
+the behaviour of \mgii corresponds with that of H$\beta$.  However,
+there are also examples of \mgii showing variation, but H$\beta$ does
+not, and vice versa.
 
@@
 The \civ\ line is one of the strongest collisionally excited lines in quasar
-spectra \citet[e.g.][]{HamannFerland1999}, and 
+spectra \citep[e.g.][]{HamannFerland1999}, and 
 \civ\ emission probes the photoionization environment produced by the innermost
@@
 This indicates they may comfortably fit into the sample of CIV
-variable QSOs explored by \citet{Dyer2019}, and similar to those
+variable quasars explored by \citet{Dyer2019}, and similar to those
 authors we suggest slim accretion disk models e.g., 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_20191108.png}
-   \vspace{-12pt}
-   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
-     commonly referred to as The Baldwin Plot.
-     The continuum luminosities are  from \citet{Calderone2017},
-     the REW measurements are Table~\ref{tab:Baldwin}.}
-  \label{fig:CIV_Baldwin}
-\end{figure}
 %\subsection{The Baldwin Effect}
@@
 The X-ray Baldwin Effect \citep[e.g., ][]{Iwasawa_Taniguchi1993}...
-\citet{Bachev2004} find a 10-fold decrease in EW \civ\ with Eddington
-ratio (decreasing from $\sim$1 to $\sim$0.01), while \nv shows no
-change. These trends suggest a luminosity-independent ``Baldwin
-effect'' in which the physical driver may be the Eddington ratio.
+\citet{Bachev2004} find a 10-fold decrease in EW \civ\ with Eddington ratio (decreasing from $\sim$1 to $\sim$0.01), while \nv shows no change.
+These trends suggest a luminosity-independent ``Baldwin effect'' in which the physical driver may be the Eddington ratio.
 \citet{Ge2016} Broad emission lines is a prominent property of Type 1 quasars.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
+  {figures/CIV_CLQs_MBHvsREW_QSFit20K.png}
+   \vspace{-12pt}
+   \caption[]{The    \civ\ Equivalent width and the virial black hole masses.}
+  \label{fig:CIV_MBHvsREW}
+\end{figure}
+
+Figure~\ref{fig:CIV_MBHvsREW} shows the  \civ\ Equivalent width and the virial black hole masses.
 
@@
   \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/MJD_vs_Eddington_20191115.png}
+  {figures/MJD_vs_Eddington_20191129.png}
   \vspace{-12pt}
@@
 transition in black hole binaries at $L / L_{\rm Edd} \sim 0.02$
-(i.e. $\eta_{\rm Edd} \sim -1.7$, where the inner disc evaporates into
+(i.e. $\eta_{\rm Edd} \sim -1.7$), where the inner disc evaporates into
 an advection dominated accretion flow, while the overall drop in
@@
 transition at $L / L_{\rm Edd} \sim$a few per cent.
+
+By comparing the observed correlations between the UV-to-X-ray
+spectral index ($\alpha_{\rm OX}$) and Eddington ratio in AGN to those
+predicted from observations of X-ray binary outbursts,
+\citet{Ruan2019a} find %that the observed correlations between the
+($\alpha_{\rm OX}$ and Eddington ratio of that AGN display a
+remarkable similarity to accretion state transitions in prototypical
+X-ray binary outbursts, including an inversion of this correlation at
+a critical Eddington ratio of $\sim$10$^{-2}$ (i.e. at the same ratio
+as motivated by \citet{NodaDone2018}).  These results suggest that the
+structures of black hole accretion flows directly scale across a
+factor of $\sim10^{8}$ in black hole mass and across different
+accretion states. Using \citet{Ruan2019a} as a guide, there are potentially three accretion regimes: 
+(1) a ``High/Soft State'' with $\eta_{\rm Edd} \gtrsim -1$; 
+(1) a ``Low/Hard State'' with $-2 \lesssim \eta_{\rm Edd} \lesssim  -1$;
+(1) a ``High/Soft State'' with $\eta_{\rm Edd} \lesssim -2$.
+These are given as shaded regions in Figure~\ref{fig:Eddington_ratios}.
+
 %%
@@
 
-We investigate this reporting the Eddington ratios of the three
-quasars in Table~\ref{tab:Eddington_ratios}.
-%%
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
-sodales est, vel cursus risus porta non. Vivamus vel pretium
-velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
-ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
-hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
-conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
-eu blandit. Donec in lacinia libero.
+%% We investigate this reporting the Eddington ratios of the three quasars in Table~\ref{tab:Eddington_ratios}.
 
-Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
-pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
-id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
-dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
-euismod. Cras vel auctor neque. Nam quis diam risus.
+{\bf Must say something about these objects all being $>10^{9}$ but having
+the quick \civ\ line changes.}
 
@@
 \end{itemize}
-
-Etiam mollis viverra nisi eget aliquet. Aliquam erat volutpat. Vivamus
-tristique, nisl eu malesuada semper, libero tortor convallis elit, a
-scelerisque orci nisi lacinia turpis. In lacinia ultrices
-volutpat. Proin ultrices luctus tellus, in placerat eros tincidunt
-id. Ut varius iaculis quam in consequat. Nulla nec orci est, sit amet
-Aliquam ac metus nec odio tempus pharetra sed nec diam. Sed eget arcu
-nulla. Etiam elementum ultrices ligula, at iaculis libero feugiat
-bibendum. Suspendisse potenti. Nam pharetra adipiscing
-euismod. Quisque imperdiet dignissim odio, sed volutpat justo
-tincidunt eu. Nunc vehicula pharetra suscipit. Integer aliquet pretium
-ipsum vel ultrices. Nam rutrum nibh ac quam pulvinar molestie.
 

### 2019-11-29 plots/MJD_Eddington/mjd_vs_Eddington.py

@@ -15,10 +15,14 @@ from matplotlib import colors as mcolors
 from astropy.io import ascii
 from astropy.io import fits
 
+## Reading in the data
+##     C I V     C  L Q s
+path   = '../../data/CLQ_line_measurements/'
+infile = 'MJD_Eddington.dat'
+CLQs   = ascii.read(path+infile)
 
 ##
-##  S h e n   et al.  (2 0 1 1)
-##  D R 7 Q  
+##  D R 7 Q    S h e n   et al.  (2011)     
 ##
 path       = '../../data/QSO_CIV_catalogs/'
 filename   = 'Shen_dr7_bh_May_2010.fits'
@@ -33,15 +37,14 @@ print('The number of columns is...  ', len(dr7q_table.names), '\n\n')
 ## Making some senible selections and cuts 
 mjd_full    = dr7q_table.field('MJD')
 logtau_full = dr7q_table.field('LOGEDD_RATIO')
-
 dr7q        = dr7q_table[np.where(dr7q_table['LOGEDD_RATIO'] > -9.0)]
 dr7q_mjd    = dr7q['MJD']
 dr7q_logtau = dr7q['LOGEDD_RATIO']
 dr7q_tau    = (10**dr7q['LOGEDD_RATIO'])*100
 
-
-## Kozlowski (2017)  and  Hamann et al. (2017)
-##  D R 1 2 Q 
+##
+##  D R 1 2 Q    Kozlowski (2017)  and  Hamann et al. (2017)
+##
 filename   = 'BOSS_Ham17Koz17_DR12Q.fits'
 dr12q_in    = fits.open(path+filename)
 dr12q_table = dr12q_in[1].data
@@ -57,10 +60,6 @@ dr12q_mjd    = dr12q['MJD_x']
 dr12q_etaEdd = dr12q['nEdd']
 
     
-## The data for our CIV CLQs
-path   = '../../data/CLQ_line_measurements/'
-infile = 'MJD_Eddington.dat'
-CLQs   = ascii.read(path+infile)
 
 
 ## Setting up the plot
@@ -102,7 +101,6 @@ mincnt    = .1
 ##  T H E     D R 7 Q     q u a s a r s 
 ax.hexbin( dr7q_mjd,  dr7q_logtau, bins='log',  gridsize=gridsize, cmap=color_map, mincnt=mincnt)
[…]

### 2019-11-29 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py

@@ -22,24 +22,22 @@ import matplotlib.lines  as mlines
 cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                         
 ## Reading in the data
 path      = '../../../data/CLQ_line_measurements/'
-filename  = 'Baldwin_CIV.dat'
+filename  = 'QSFIT_CIV_line_params.dat'
 CLQs      = ascii.read(path+filename)
 
-
 CLQs_FWHM       = CLQs['FWHM']    / 1000.
-CLQs_errFWHM    = CLQs['errFWHM'] / 1000.
-CLQs_logREW     = np.log10(CLQs['REW'])
-CLQs_logerrREW  = np.log10(CLQs['errREW'])
-CLQs_loglineLum = np.log10(CLQs['lineLum']*1e42)
-CLQs_logContLum = np.log10(CLQs['contLum']*1e42)
+CLQs_FWHMerr    = CLQs['FWHM_err'] / 1000.
+CLQs_logREW     = np.log10(CLQs['EW'])
+CLQs_logREWerr  = np.log10(CLQs['EW_err'])
+CLQs_logContLum = np.log10(CLQs['ContLum']*1e42)
+CLQs_logLineLum = np.log10(CLQs['LineLum_err']*1e42)
+CLQs_logContLum = CLQs_logContLum - 42.   ## To ``normalize'' to 10^42 erg s^-1
+CLQs_logLineLum = CLQs_logLineLum - 42.   ## To ``normalize'' to 10^42 erg s^-1
 
-## To ``normalize'' to 10^42 erg s^-1
-CLQs_loglineLum = CLQs_loglineLum - 42.
-CLQs_logContLum = CLQs_logContLum - 42.
-    
+
 
 ##  Hamann et al. (2017) and Kozłowski (2017) merged BOSS DR12 catalog
-path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/QSO_CIV_catalogs/'
+path      = '../../../data/QSO_CIV_catalogs/'
 filename  = 'BOSS_Ham17Koz17_DR12Q.fits'
 infile    = path+filename
 data_full = fits.open(infile)
@@ -185,8 +183,11 @@ print("R-squared       : %f" % r_value**2)
 print("p-value         : %f" % p_value)
 print("Standard errro  : %f" % std_err)
 print()
-plt.plot(x, (slope*x + intercept), 'r')
[…]

### 2019-11-29 plots/hexbin_plots/Baldwin/Baldwin_triptych.py

@@ -1,0 +1,370 @@
+'''
+A ``hexbin'' plot for the SDSS-III BOSS data from the Hamann et
+al. (2017) catalog and analysis.  This initially concentrated on
+'just' f1450 converted into Lum_1450.  However, matching with the
+Kozłowski (2017) catalog means we can do the Baldwin plot with LBol
+directly.
+'''
+
+import numpy as np
+from scipy             import stats
+from astropy.io        import fits
+from astropy.io        import ascii
+from astropy.cosmology import FlatLambdaCDM
+
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.mlab   as mlab
+import matplotlib.lines  as mlines
+
+
+## Setting up the cosmology
+cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                         
+## Reading in the data
+##
+##  T H E   C L Qs   
+##
+path      = '../../../data/CLQ_line_measurements/'
+#filename  = 'Baldwin_CIV.dat'
+filename  = 'QSFIT_CIV_line_params.dat'
+CLQs      = ascii.read(path+filename)
+
+CLQs_FWHM       = CLQs['FWHM']     / 1000.
+CLQs_errFWHM    = CLQs['FWHM_err'] / 1000.
+CLQs_logREW     = np.log10(CLQs['EW'])
+CLQs_logerrREW  = np.log10(CLQs['EW_err'])
+CLQs_loglineLum = np.log10(CLQs['LineLum']*1e42)
+CLQs_logContLum = np.log10(CLQs['ContLum']*1e42)
+CLQs_MBH        = CLQs['MBH']
+CLQs_MBHerr     = CLQs['MBH_err']
+CLQs_eta        = CLQs['eta']  
+#CLQs_MBH        = CLQs['MBH_CIV']  ## MBH_CIV from Kozłowski (2017)
+#CLQs_eta        = CLQs['eta_CIV']  ## MBH_CIV from Kozłowski (2017)
+CLQs_loglineLum = CLQs_loglineLum - 42.  ## To ``normalize'' to 10^42 erg s^-1
+CLQs_logContLum = CLQs_logContLum - 42.  ## To ``normalize'' to 10^42 erg s^-1
+
+##
+##     Q S F I T 
+## CONT*__LUM::  1450, 2245, 3000, 4210 or 5100:
[…]

### 2019-11-29 plots/hexbin_plots/MBH_REW/MBH_REW_hexbin.py

@@ -1,0 +1,254 @@
+'''
+A ``hexbin'' plot for the SDSS-III BOSS data from the Hamann et
+al. (2017) catalog and analysis.  This initially concentrated on
+'just' f1450 converted into Lum_1450.  However, matching with the
+Kozłowski (2017) catalog means we can do the Baldwin plot with LBol
+directly.
+'''
+
+import numpy as np
+from scipy             import stats
+from astropy.io        import fits
+from astropy.io        import ascii
+from astropy.cosmology import FlatLambdaCDM
+
+import matplotlib
+import matplotlib.pyplot as plt
+import matplotlib.mlab   as mlab
+import matplotlib.lines  as mlines
+
+
+## Setting up the cosmology
+cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                          
+## Reading in the data
+##  
+##  T H E    C L Q s
+##
+path      = '../../../data/CLQ_line_measurements/'
+filename  = 'QSFIT_CIV_line_params.dat'
+CLQs      = ascii.read(path+filename)
+
+CLQs_logREW     = np.log10(CLQs['EW'])
+CLQs_logREWerr  = np.log10(CLQs['EW_err'])
+CLQs_MBH        = CLQs['MBH']
+
+
+##
+##    Q S F I T
+##
+## CONT*__LUM::  1450, 2245, 3000, 4210 or 5100:
+## AGN continuum (Section 2.2) νLν luminosities and their uncertainties, in units of 1042 erg s−1
+## 
+path        = '../../../data/QSO_CIV_catalogs/'
+filename    = 'qsfit_1.2.4.fits'
+infile      = path+filename
+sdata_full  = fits.open(infile)
+sdata       = sdata_full[1].data
+
+data_qsofit = sdata[np.where((sdata['BR_CIV_1549__LUM']  > 0.) &
+                             (sdata['BR_CIV_1549__FWHM'] > 0.) &
+                             (sdata['BR_CIV_1549__EW']   > 0.))] 
+
+EW_QSFit        =           data_qsofit['BR_CIV_1549__EW']
+log_EW_QSFit    = np.log10(data_qsofit['BR_CIV_1549__EW'])
+## Virial BH estimate:: "just"  (nu.L_nu)^0.5  *  FWHM^2 
[…]

### 2019-11-29 plots/hexbin_plots/REW_FWHM/REW_FWHM_hexplot.py

@@ -16,14 +16,13 @@ import matplotlib.lines  as mlines
 ## READING IN THE DATA
 ##
 ##  F U L L    B O S S    D R 1 2    catalog
-path      = '/cos_pc19a_npr/data/ERQs/Hamann2017_CIVcatalog/'
-filename  = 'C4N5REWs_DR12v11_MNRAS.fits'
+path      = '../../../data/QSO_CIV_catalogs/'
+filename  = 'BOSS_Ham17Koz17_DR12Q.fits'
 infile    = path+filename
 data_full = fits.open(infile)
 tdata     = data_full[1].data
-## knocking out a couple of objects with bad REW values 
+## Knocking out a couple of objects with bad REW values
 data = tdata[np.where( (tdata['rew'] >0.) & (tdata['rew'] < 10000.)  )]
-
 ## Setting up variable names
 REW  = data['rew']        
 FWHM = data['fwhm']
@@ -34,24 +33,25 @@ log_REW = np.log10(REW)
 FWHM    = FWHM/1000.
 
 
+
 ##  T H E    C I V    C L Q    S A M P L E 
-path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/CLQ_line_measurements/'
-filename  = 'REW_FWHM_CIV.dat'
+path      = '../../../data/CLQ_line_measurements/'
+#filename  = 'REW_FWHM_CIV.dat'
+filename  = 'QSFIT_CIV_line_params.dat'
 CLQs      = ascii.read(path+filename)
 
 CLQ_FWHM    = CLQs['FWHM']    / 1000.
-CLQ_errFWHM = CLQs['errFWHM'] / 1000.
-CLQ_REW     = CLQs['REW']
-CLQ_errREW  = CLQs['errREW'] 
-
-CLQ_logREW = np.log10(CLQs['REW'])
+CLQ_errFWHM = CLQs['FWHM_err'] / 1000.
+CLQ_REW     = CLQs['EW']
+CLQ_errREW  = CLQs['EW_err'] 
+CLQ_logREW  = np.log10(CLQs['EW'])
 
 ## have to put the x-errors into log-space
 #log_REW_hi = np.log10(CLQs['REW'] np.log10(CLQs['errREW']))
 #log_REW_lo = np.log10(CLQs['REW']-CLQs['errREW'])
 ## and then have them as
 #CLQ_asym_xerr = [log_REW_lo, log_REW_hi] 
[…]

### 2019-12-02 tex/CIV_CLQs.tex
Massive general update

@@
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib]{mnras}
 
@@
 \author[Ross {\it et al.}]
-{%The RH John~S.~Bercow, MP, {\it et al.} 
-Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
+{Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
  Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
@@
 \\
-% List of institutions
-%$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
+%%  List of institutions
 $^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
@@
 \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-\hypersetup{draft}
 
@@
 collapse and emergence being displayed in rest-frame timescales of
-$\sim$240-1640 days.  Where observed, the profile of the
-Ly$\alpha$/\nv emission complex also changes, and there is tentative
-evidence for changes in the \mgii line.  Although line measurements
-from the three quasars show large changes in the \civ\ flux-line width
-plane, the quasars are not seen to be outliers when considered against
-the full $z\sim2$ quasar population in terms of (rest) Equivalent
-Width and FWHM properties.  We put these observations in context with
+$\sim$240-1640 days.  These are very quick changes, especially when
+considering virial black hole mass estimates have all three quasars
+with $M_{\rm BH} > 10^{9} M_{\odot}$.  Continuum and emission line
+measurements from the three quasars show changes in the
+continuum-equivalent width plane with the CLQs seen to be on the edge
+of the full population distribution, and showing indications of an
+intrinsic Baldwin Effect. We put these observations in context with
 recent ``state-change'' models, but note that even in their
@@
 similar blueshift properties. The ratio of the line width of \civ\ to
-that of \mgii increases with blueshift.  \citet{Sun2018} also find
-that quasar variability might slightly enhance the connection between
-the \civ\ blueshift and EW, though further investigation here is
+that of \mgii increases with blueshift. \citet{Sun2018} also find that
+quasar variability might slightly enhance the connection between the
+\civ\ blueshift and EW, though further investigation here is
 warranted. There is also the finding that the objects with that
 largest blueshifts are less variable and tend to have higher Eddington
-ratios.  \citet{Sun2018} explain their results these by suggesting
-that quasar SEDs become {\it softer} with {\it increasing Eddington
-ratio} along with the presence of X-ray shielding by the inner
-accretion disk.  However, a high Eddington ratio alone might be an
-insufficient condition for the \civ\ blueshift.
-%%
-Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
-\citet{Dyer2019} provide a detailed analysis of 340 quasars at high-redshift
-($1.62<z<3.30$) from the SDSS-RM project, which we will compare our
-results to.
+ratios. \citet{Sun2018} explain their results these by suggesting that
+quasar SEDs have weaker X-ray emission (or at least a larger UV/optical-to-Xray
+spectral index, $\alpha_{\rm ox}$) and thus become {\it
+softer} with {\it increasing Eddington ratio} along with the presence
+of X-ray shielding by the inner accretion disk. However, a high
+Eddington ratio alone might be an insufficient condition for the \civ\
+blueshift. Recent investigations also include \citet{Meyer2019} and
+\citet{Doan2019}. \citet{Dyer2019} provide a detailed analysis of 340
+quasars at high-redshift ($1.62<z<3.30$) from the SDSS-RM project,
+which we will compare our results to.
 
@@
 = m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1 at
-3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011}. We
+3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011, Cutri2013}. We
 adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73 $,
@@
 with a 30sec exposure during new moon \citep{Masci2019}.
+\begin{figure*}
+  \centering
+  %% trim=l b r t
+  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
+  {figures/J1205+3422_landscape_20191112.png}
+  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
+  {figures/J1638+2827_landscape_20191112.png}
+  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
+  {figures/J2228+2201_landscape_20191112.png}
+  \vspace{-12pt}
+  \caption[]{The three high-$z$ CLQ quasars; 
+    J1205+3422 (top), 
+    J1638+2827 (middle) and  
+    J2228+2201 (bottom). 
+The light curve data is present in the panels on the left hand side, with the 
+spectral epoch observational timings indicated by vertical lines. 
+The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
+complex, the \civ\ line, and the \mgii line. 
+  }
+  \label{fig:civ_clqs}
+\end{figure*}
 
@@
 
-\begin{figure*}
-  \centering
-  %% trim=l b r t
-  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
-  {figures/J1205+3422_landscape_20191112.png}
-  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
-  {figures/J1638+2827_landscape_20191112.png}
-  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
-  {figures/J2228+2201_landscape_20191112.png}
-  \vspace{-12pt}
-  \caption[]{The three high-$z$ CLQ quasars; 
-    J1205+3422 (top), 
-    J1638+2827 (middle) and  
-    J2228+2201 (bottom). 
-The light curve data is present in the panels on the left hand side, with the 
-spectral epoch observational timings indicated by vertical lines. 
-The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
-complex, the \civ\ line, and the \mgii line. 
-  }
-  \label{fig:civ_clqs}
-\end{figure*}
+%% From Section 3.1; Place here to help with overall formatting of
+%% the paper
+\input{QSFit-results}
+
 \subsection{Spectroscopy}
@@
 
-\begin{table*}
-  \small
-  \begin{centering}
-    \begin{tabular}{l  l | c c | c c c c | c}
-      \hline
-      \hline
-              &          &  \multicolumn{2}{c}{Cont.
-@ 1450\AA }                  &   \multicolumn{4}{c}{CIV 1549\AA}                                                                                & Virial product \\
-Object    & MJD  &      $\nu L_{\nu}$    &         Slope                             &   Luminosity         &     FWHM                 &    V$_{\rm off}$    & EW                                 & log($\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$) \\
- & & $10^{42}$ erg s$^{-1}$ & (F$_\lambda \propto \lambda^\alpha$)  & $10^{42}$ erg s$^{-1}$ &  km s$^{-1}$   &     km s$^{-1}$   &  \AA                              &  $\log(M/M_{\odot})$ \\
-      \hline
-                     & 53498   &  38129  $\pm$ 39  &  -1.57 $\pm$ 0.01 &   898 $\pm$ 15    &   6024 $\pm$  120  &  944 $\pm$  33  & 37.78 $\pm$  0.62  &   9.85 $\pm$ 0.02\\
- J1205+3422 & 58538    &  8550 $\pm$ 11    &  -1.41 $\pm$ 0.01 &  385.2 $\pm$ 3.9 &   7109 $\pm$   91   & 1085 $\pm$  29  &   71.32 $\pm$  0.71  &   9.67 $\pm$ 0.01\\  
-                     & 58693$^*$ & 2725 $\pm$ 40 &  -1.27 $\pm$ 0.05 &  161 $\pm$ 22    &  14997 $\pm$ 2500 &  922 $\pm$ 690  & 91.68 $\pm$ 12.73  &  10.07 $\pm$ 0.13\\  
-                      &              &                               &                               &                              &                                 &                             &                                   &                              \\
-                      & 54553   & 3579 $\pm$ 49    &  -1.16 $\pm$ 0.07  & 293.6  $\pm$ 8.8 &  4630 $\pm$  180   & 183 $\pm$  57   & 127.67 $\pm$  3.80  &    9.11 $\pm$ 0.04\\  
- J1638+2827 & 55832   & 2340 $\pm$ 15    &  -2.17 $\pm$ 0.05  &  84.6  $\pm$ 4.2  &  4733 $\pm$  290   & 172 $\pm$  89   &  59.61 $\pm$  2.98  &    9.04 $\pm$ 0.05\\  
-                      & 58583  & 7793 $\pm$ 19     &  -2.02 $\pm$ 0.01  & 367.5  $\pm$ 4.3 &  4511 $\pm$   71    &  94 $\pm$  24   &  77.89 $\pm$  0.91  &  9.25 $\pm$ 0.01\\  
-                      &             &                               &                                &                              &                                 &                            &                                   &                            \\
-                     & 56189$^*$ & 607 $\pm$ 49  &  -0.00 $\pm$ 0.16 &  72.8  $\pm$ 11.3 & 14993 $\pm$ 2400 &  828 $\pm$ 691   & 162.89 $\pm$ 25.37  &  9.74 $\pm$ 0.14\\  
- J2228+2201 & 56960   & 7842 $\pm$ 25     &  -1.72 $\pm$ 0.02 & 301.0  $\pm$ 7.2  &  7136 $\pm$  210   & -276 $\pm$  64   &  61.99 $\pm$  1.48  &    9.65 $\pm$ 0.03\\ 
-              & 58693   & 2388.4 $\pm$ 6.8 &  -1.22 $\pm$ 0.01 & 145.4  $\pm$ 1.5  &  6084 $\pm$   83    &   168 $\pm$  28   &  94.77 $\pm$  0.99  &    9.26 $\pm$ 0.01\\
-      \hline
-      \hline
-    \end{tabular}
-    \caption{Continuum at 1450\AA\ and \civ\ spectral measurements for the
-      three quasar considered in this work, at all observation epochs, as
-      calculated by QSFit.  The last column shows the virial product
-      calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$.  $^{*}$The
-      \civ\ line is very faint (with respect to the continuum), and the
-      associated estimates are likely unreliable.}
-    \label{tab:QSFit-results}
-  \end{centering}
-\end{table*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 blueshifts of $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km
-s$^{-1}$, respectively.  By 2019, however, the opitical brightness
+s$^{-1}$, respectively.  By 2019, however, the optical brightness
 dropped by $\sim$1.5 magnitudes and the spectra are significantly less
@@
 
+%% trim={<left> <lower> <right> <upper>}
+\begin{figure}
+  \centering
+  \includegraphics[width=8.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
+    \vspace{-18pt}
+  \caption{Observed spectra and best fit model in the region relevant
+    to \civ\ emission line for the quasars considered here.}
+  \label{fig:QSFit-CIV}
+\end{figure}
 \subsection{\civ\ Emission Line Evolution}
@@
 luminosity and slope at rest-frame 1450\AA, \civ\ line luminosity,
-FWHM and EW are given in Tab.~\ref{tab:QSFit-results}. All fits are
+FWHM and EW are given in Tabl;e~\ref{tab:QSFit-results}. All fits are
 performed with $E(B-V) = 0$ and the best fit model in the region of
@@
 All \civ\ lines are fitted with a single, broad, Lorentzian profile.
-This allows us to account for the narrow peak of the \civ\ line. 
-No narrow components are considered for several reasons: in the epochs
-of highest brightness the ``narrow'' component would have FWHM
-$\sim2-3 \times 10^{3}$ km s$^{-1}$, i.e. values exceeding the usual
-widths of genuine narrow lines ($\lesssim 10^3$ km s$^{-1}$); by
-allowing a second component, to have such large widths their
-parameters would become highly degenerate with the ``broad''
-components, and the latter would also have much larger FWHM
-($\sim10^{4}$ km s$^{-1}$); and by neglecting the narrow components we
-have a consistent fit across all epochs.
+This allows us to account for the narrow peak of the \civ\ line.  No
+narrow components are considered for several reasons: in the epochs of
+highest brightness the ``narrow'' component would have FWHM~$\sim2-3
+\times 10^{3}$~km~s$^{-1}$, i.e. values exceeding the usual widths of
+genuine narrow lines ($\lesssim$ $10^3$ km s$^{-1}$); by allowing a
+second component, to have such large widths their parameters would
+become highly degenerate with the ``broad'' components, and the latter
+would also have much larger FWHM ($\sim$$10^{4}$ km s$^{-1}$); and by
+neglecting the narrow components we have a consistent fit across all
+epochs.
 
@@
 may be a bias due to the limited wavelength range available which
-extends to $\lambda \sim 1240\AA$ for the first epoch, while it extend
+extends to $\lambda \sim 1240$\AA\ for the first epoch, while it extend
 to shorter wavelengths for the other epochs (respectively 1140\AA\ and
@@
 that would be inconsistent with the other analyses.
-
 In all cases where the \civ\ line profile is reliably constrained the
@@
 $\lesssim$~1000 km s$^{-1}$, despite the significantly larger
-variations in the line luminosities.  The FWHM of broad lines is
-likely related to the mass of the supermassive black hole powering the
-quasar phenomenon, which is supposed to be constant on any human
-timescale.  Hence it is instructive to check whether the virial
-product, which is the basic quantity used to calculate the single
-epoch mass estimate, show any variation.  The virial product,
-calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$, is reported in
-the last column of Tab.~\ref{tab:QSFit-results}.  The uncertainty
-typically associated to the single epoch mass estimate is $\sim$0.5
-dex, hence the virial product at all epochs are remarkably constant
-and compatible with a single value of black hole mass for each source,
-even in those cases where the \civ\ estimates are possibly
-unreliable. The object showing larger variation is J2228+2201,
-although the extreme values span a range of 0.48 dex.
+variations in the line luminosities.
 
-Finally, also the velocity offsets of the \civ\ line are also
+\begin{figure}
+  \centering
+  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
+  {figures/CIV_CLQs_MBHvsREW_QSFit20K.png}
+   \vspace{-12pt}
+   \caption[]{The virial black hole masses of $\approx$20,000 $z>1.5$ quasars
+     from QSFit catalogue \citep{Calderone2017} and the \civ\ Equivalent widths.
+     Different quasars are given different colours: J1205+3422 purple; J1638+2827 green; J2228+2201 is blue.
+     Different epochs different symbols: first epoch circles; second epoch squares; third epoch diamonds. 
+   }
+  \label{fig:CIV_MBHvsREW}
+\end{figure}
+\subsection{Virial Black Hole Masses}
+The FWHM of broad lines is likely related to the mass of the
+supermassive black hole powering the quasar phenomenon, which is
+assumed to be constant on any human timescale.  Hence it is
+instructive to check whether the virial product, which is the basic
+quantity used to calculate the single epoch black hole mass estimate,
+show any variation.
+
+Using the estimates for the continuum luminosity and FWHW from the
+single-epoch spectra, one can estimate the central black hole mass
+\citep[e.g.][]{Shen2011, Calderone2017}.  This approach assumes that
+the broad-line region (BLR) is virialized, the continuum luminosity is
+used as a proxy for the BLR radius, and the broad line width (FWHM) is
+used as a proxy for the virial velocity.  This ``virial mass''
+estimate can then be expressed as:
+\begin{equation}
+  \log(M_{\rm BH}) = (\nu L_{\nu})^{\gamma} \times ({\rm FWHM})^{\delta}
+\end{equation}
+where $\gamma=0.5$ and $\delta=2$.  The virial product for the \civ\
+CLQs is reported in the last column of Tab.~\ref{tab:QSFit-results}. 
+The uncertainty typically associated to the single epoch mass estimate
+is $\sim$0.5 dex, hence the virial product at all epochs are
+remarkably constant and compatible with a single value of black hole
+mass for each source, even in those cases where the \civ\ estimates
+are possibly unreliable. The object showing larger variation is
+J2228+2201, although the extreme values span a range of 0.48 dex.
+
+From the virial mass estimates, all our objects have SMBH masses $M >10^{9} M_{\odot}$.
+This is at the upper end of SMBH masses at all epochs, and towards the
+extreme of the mass distribution for $z\sim2$ objects.  
+Figure~\ref{fig:CIV_MBHvsREW} shows the \civ\ Equivalent width and the
+virial black hole masses for a sample of $\approx$20,000 $z>1.5$ SDSS
+quasars from the QSFit catalog as well as the estimates for the three
+\civ\ CLQs.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
+  {figures/CIV_CLQs_REWvsFWHM_20191128.png}
+  \vspace{-12pt}
+  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
+    of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
+    of \citet{Hamann2017}.
+   Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.}
+  \label{fig:REWvsFWHM}
+\end{figure}
+\subsection{Quantified Temporal Evolution of \civ\ Emission}
+Figure~\ref{fig:REWvsFWHM} shows the rest Equivalent Width (REW)
+versus the Full Width Half Maximum (FWHM) of the \civ\ emission line
+in the BOSS DR12 quasar sample using the catalogue of
+\citet{Hamann2017}.
+
+The velocity offsets of the \civ\ line are also
 approximately constant, and compatible with a single value (within
@@
 epochs.
-
-The temporal evolution of the velocity offsets, along with the
-1450\AA\ continuum luminosity and slope, the \civ\ line FWHM
-and virial black hole mass are given in Figure~\ref{fig:QSFit-results}.
-
-%% trim={<left> <lower> <right> <upper>}
-\begin{figure*}
-  \centering
- \includegraphics[width=\textwidth, trim={0cm 0 0 0},clip]{figures/CIVregions.png}
-%  \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-2089-53498-0427.png}
- % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J1205p3422_58538.png}
- % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J1205p3422_58693.png}\\
- % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-2948-54553-0614.png}
- % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-5201-55832-0178_v5_10_0.png}
- % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J1638p2827_58583.png}\\
- % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-6118-56189-0720.png}
- % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-7582-56960-0790.png}
- % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J2228p2201_58693.png}
-  \caption{Observed spectra and best fit model in the region relevant
-    to \civ\ emission line for the quasars considered here.}
-  \label{fig:QSFit-CIV}
-\end{figure*}
 
@@
 \end{figure*}
+The temporal evolution of the velocity offsets, along with the
+1450\AA\ continuum luminosity and slope, the \civ\ line FWHM
+and virial black hole mass are given in Figure~\ref{fig:QSFit-results}.
 
@@
   \end{tabular}
-  \caption{Physical properties of the \civ\ CLQs and M87.
+  \caption{Physical properties of the \civ\ CLQs. 
      $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude $K$-corrected to $z = 2$; Bolometric luminosity computed from the
@@
   \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_20191129.png}
+  {figures/CIV_CLQs_Baldwin_20191130.png}
    \vspace{-12pt}
@@
      The continuum luminosities are  from \citet{Calderone2017},
-     the REW measurements are Table~\ref{tab:Baldwin}.}
+     the REW measurements are Table~\ref{tab:QSFit-results}.
+     Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.
+     The dashed red line has slope $\beta=-0.38$.}
   \label{fig:CIV_Baldwin}
@@
 e.g. 1450\AA\ rest continuum luminosity, so that as the underlying UV
-continuum luminosity increases, the EW decreses, see
-Figure~\ref{fig:CIV_Baldwin}. This figure effectively reproduces Figure~15 from \citet{Calderone2017}, but where we now
-add the measurements from the 3 \civ\ CLQ quasars at each epoch.
+continuum luminosity increases, the EW decreses. 
+Figure~\ref{fig:CIV_Baldwin} shows this for a sample (from the QSFit catalogue)
+for 20,374 quasars.  The slope (not shown) is $\beta$ is $-0.1997$.
+This is consistent with \citet{Kozlowski2017}, using their bolometric
+luminosity gives a slope of $\beta=-0.251$ and in line with that from
+\citet[][ $\beta=-0.23$]{Hamann2017}.
 
-The plotted values are \verb|CONT1450__LUM| and
-\verb|BR_CIV_1549__EW|.  \verb|CONT1__LUM| is the $\nu L_{\nu}$
-luminosity at wavelength. This selects 20,374 quasars.  The slope
-$\beta$ is $-0.1997$.  Checking with \citet{Kozlowski2017}, using
-their bolometric luminosity gives a slope of $\beta=-0.251$, in line
-with that from \citet[][ $\beta=-0.23$]{Hamann2017}.
+We add the measurements from the three \civ\ CLQ quasars at each epoch
+to Figure~\ref{fig:CIV_Baldwin}. We see first that all three quasars
+at all three epochs lie on the edge of the $\nu L_{\nu}$-EW
+distribution.  Second, with the exception of J1638+2827 on MJD 55832,
+all the measurements show an {\it intrinsic Baldwin Effect}
+\citep[e.g.][]{Goad2004, Rakic2017}.  The slope of the CLQs intrinsic
+BEff is $\approx-0.38$, as shown by the dashed red line in
+Fig.~\ref{fig:CIV_Baldwin}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-  \centering
-  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_REWvsFWHM_20191128.png}
-   \vspace{-12pt}
-  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
-of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
-of \citet{Hamann2017}. %Note the REW logarithmic scaling.
-}
-  \label{fig:REWvsFWHM}
-\end{figure}
 \section{Discussion}
-\subsection{Continuum and Line Changes}
+\subsection{Continuum and Line Changes: Comparisons to recent Observations}
+The top row of Figure~\ref{fig:QSFit-results} demonstrates that
+both the 1450\AA\ continuum and the \civ\ emission lines can
+exhibit large, $>$$\times$10, changes in luminosity, {\it and}
+that these continuum-line changes track each other.
+
 \citet{Trakhtenbrot2019} report on the quasar 1ES 1927+654 which was
@@
 Type 1 after a raise in the continuum luminosity.  This suggests that
-there is (at least in some cases) a relationship between the continuum
+there is (at least in some cases) a direct relationship between the continuum
 and broad emission lines in CLQs.  A similar scenario may have occured
@@
 \citet{Trakhtenbrot2019} have includes a UV spectrum of 1ES 1927+654.
-However, there is no evidence for broad UV emission lines, including
-\civ\ , \ciii\ , or \mgii.  The authors attribute the lack of broad UV
+Interestingly, however, there is no evidence for broad UV emission lines, including
+\civ, C\,{\sc iii}, or Mg\,{\sc ii}.  The authors attribute the lack of broad UV
 emission lines to dust within the BLR, noting that to dust in the
@@
 r | > 0.5$ mag) variability over any of the available time baselines
-probed by the SDSS and Pan-STARRS1 surveys.  For our adopted
-signal-to-noise ratio threshold on variability of broad H$\beta$
-emission, they find 17 new CLQs (which is $\sim20$ of the observerd
-sample). These candidates are at lower Eddington ratio relative to the
-overall quasar population, while the CLQ fraction increases from 10\%
-to roughly half, as the continuum flux ratio between repeat spectra at
-3420 \AA\ (rest-frame) increases from 1.5 to 6.  \citet{Homan2019}
+probed by the SDSS and Pan-STARRS1 surveys. They find 17 new CLQs
+which is $\sim$20\% of the observerd sample. This CLQ fraction
+increases from 10\% to roughly half, as the continuum flux ratio
+between repeat spectra at 3420 \AA\ (rest-frame) increases from 1.5 to
+6. \citet{MacLeod2019} note that these candidates are at lower Eddington
+ratio relative to the overall quasar population.
+
+Using the same dataset as and extremely variable quasar sample
+as \citet{MacLeod2019}, \citet{Homan2019}
 investigate the responsiveness of the \mgii broad emission line
-doublet in AGN on timescales of several years.  This study is based on
-a the same extremely variable quasar sample as was used for
-\citet{MacLeod2019}.  By again focussing on quasars that show large
+doublet in AGN on timescales of several years.  By again focussing on quasars that show large
 changes in their optical light-curves, \citet{Homan2019} find that
@@
 
-%Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the  H$\beta$ emission line.
-H$\beta$ emission is associated with a 2.55 eV energy difference.
-Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$.
+\subsection{Continuum and Line Changes: Comparisons to theoretical expectaions}
+{\bf SF and BM to add a little more here}\\
+The \civ\ line is one of the strongest collisionally excited lines in quasar spectra \citep[e.g.][]{HamannFerland1999}, and \civ\ emission probes the photoionization environment produced by the innermost disk, as indicated by RM time-delay measurements.
 
-The \civ\ line is one of the strongest collisionally excited lines in quasar
-spectra \citep[e.g.][]{HamannFerland1999}, and 
-\civ\ emission probes the photoionization environment produced by the innermost
-disk, as indicated by RM time-delay measurements.
-%%
-In standard \citet{SS73} 
-thin disk models, large changes in the continuum flux are not
-permitted over short timescales due to the relatively long viscous
-time associated with such disks. Given the observed short timescale
-continuum variations, it is not surprising that the \citet{SS73} disk may fail
-on other fronts. The \civ\ variations observed in our sources... 
-%DO/DO NOT (I can't tell!?! we have to determine this!) fit the Baldwin Effect relationship found by previous authors (cite em again).
+In standard \citet{SS73} thin disk models, large changes in the continuum flux are not permitted over short timescales due to the relatively long viscous time associated with such disks.
+Given the observed short timescale continuum variations, it is not surprising that the \citet{SS73} disk may fail on other fronts.
+%The \civ\ variations observed in our sources...
 
-%If they DO fit:
-This indicates they may comfortably fit into the sample of CIV
-variable quasars explored by \citet{Dyer2019}, and similar to those
-authors we suggest slim accretion disk models e.g., 
-\citet[][]{Abramowicz1988} or inhomogeneous disk models
-\citep[e.g.,][]{DexterAgol2011} may provide viable explanations for
-our observations. I want to say a bit more here about the generic
-probe of photoionization vs shielding and conditions in the BL region
-but that will take more time.
+This indicates they may comfortably fit into the sample of \civ\ variable quasars explored by \citet{Dyer2019}, and similar to those authors we suggest slim accretion disk models e.g., \citet[][]{Abramowicz1988} or inhomogeneous disk models
+\citep[e.g.,][]{DexterAgol2011} may provide viable explanations for our observations.
+%% I want to say a bit more here about the generic probe of photoionization vs shielding and conditions in the BL region but that will take more time.
 
-%If they DO NOT fit:
-This implies that the variable \civ\ in our sample arises through
-different emission mechanisms than is usual for high-$z$ quasar...
-%% --and I gotta think more/longer about what else to say here.
-
-%\subsection{The Baldwin Effect}
-The variable properties of the rest-frame UV quasar emission lines
-have been long studied, with the global (or ensemble) Baldwin Effect
-(the anti-correlation between the EW of the emission line and the
-underlying continuum luminosity of single-epoch observations of a
-large number of AGN, first noted in \citet{Baldwin1977}.  More
-recently, the intrinsic Baldwin effect, the same anti-correlation but
-in an individual, variable AGN.
+\subsection{Implications for The Baldwin Effect}
+The variable properties of the rest-frame UV quasar emission lines have been long studied, with the global (or ensemble) Baldwin Effect (the anti-correlation between the EW of the emission line and the underlying continuum luminosity of single-epoch observations of a large number of AGN, first noted in \citet{Baldwin1977}.
+More recently, the intrinsic Baldwin effect, the same anti-correlation but in an individual, variable AGN.
 
@@
 \citet{Ge2016} Broad emission lines is a prominent property of Type 1 quasars.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_MBHvsREW_QSFit20K.png}
-   \vspace{-12pt}
-   \caption[]{The    \civ\ Equivalent width and the virial black hole masses.}
-  \label{fig:CIV_MBHvsREW}
-\end{figure}
-
-Figure~\ref{fig:CIV_MBHvsREW} shows the  \civ\ Equivalent width and the virial black hole masses.
 
@@
 
-By comparing the observed correlations between the UV-to-X-ray
-spectral index ($\alpha_{\rm OX}$) and Eddington ratio in AGN to those
+By comparing the observed correlations between the UV/optical-to-X-ray
+spectral index ($\alpha_{\rm ox}$) and Eddington ratio in AGN to those
 predicted from observations of X-ray binary outbursts,
-\citet{Ruan2019a} find %that the observed correlations between the
-($\alpha_{\rm OX}$ and Eddington ratio of that AGN display a
-remarkable similarity to accretion state transitions in prototypical
+\citet{Ruan2019a} find a remarkable similarity to accretion state transitions in prototypical
 X-ray binary outbursts, including an inversion of this correlation at
@@
 
-%%
-\citet{JiangYF2014, JiangYF2016, JiangYF2019}.
-\citet{JiangYF2019arXiv} use global three dimensional radiation
-magneto-hydrodynamic simulations to study the properties of inner
-regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$
-black hole with mass accretion rates reaching 7\% and 20\% of the
-Eddington value.
-
-%% We investigate this reporting the Eddington ratios of the three quasars in Table~\ref{tab:Eddington_ratios}.
-
-{\bf Must say something about these objects all being $>10^{9}$ but having
-the quick \civ\ line changes.}
+Building on a previous work \citep[e.g.,][]{JiangYF2014, JiangYF2016, JiangYF2019}, \citet{JiangYF2019arXiv} use global three dimensional radiation magneto-hydrodynamic simulations to study the properties of inner regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$ black hole with mass accretion rates reaching 7\% and 20\% of the Eddington value.
 
@@
 \begin{list}{$\circ$}{}
-  \item  Dr. Giorgio Calderone for discussions to the utility of the QSFit routine and line measurements. 
   \item Andy Lawrence, Mike Hawkins and David Homan for useful discussion.

### 2019-12-02 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py

@@ -186,7 +186,7 @@ print()
 
 #plt.plot(x, (slope*x + intercept), 'r')
 ## "Fitting", by eye, the the CLQs points
-#plt.plot(x, ((-.38*x) + (intercept+1.1)), 'r', linestyle=':')
+plt.plot(x, ((-.38*x) + (intercept+1.1)), 'r', linestyle=':', zorder=0)
 
 ## for the label...
 slope_str     = str(np.around(slope, decimals=3))

### 2019-12-02 plots/hexbin_plots/REW_FWHM/REW_FWHM_hexplot.py

@@ -124,7 +124,7 @@ for ii in range(len(CLQs)):
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='k',       alpha=alpha, marker='D', s=ms*ms_back)
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='fuchsia', alpha=alpha, marker='D', s=ms)
             J12_58693 = mlines.Line2D([], [], label='J1205+3422 (58693)', color='fuchsia',
-                       marker="s", markeredgecolor='k', markeredgewidth=1.4, markersize=7,  linestyle='None')
+                       marker="D", markeredgecolor='k', markeredgewidth=1.4, markersize=7,  linestyle='None')
             
             
     if str(CLQs['Object'][ii]) == 'J1638p2827':
@@ -196,7 +196,7 @@ handles=[boss, J12_53498, J12_58538, J12_58693,
                J16_54553, J16_55832, J16_58583, 
                J22_56189, J22_56960, J22_58693]
 leg = ax.legend(loc='upper right',
-                fontsize=fontsize/1.6, handles=handles, 
+                fontsize=fontsize/1.75, handles=handles, 
                 frameon=True, framealpha=1.0, fancybox=True)
 
 

### 2019-12-02 tex/CIV_CLQs.tex
another major update; manuscript looking good :-)

@@
 = m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1 at
-3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011, Cutri2013}. We
-adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73 $,
-$\Omega_{\rm M} = 0.27$, and $h = 0.71$. All logarithms are to the base 10.
+3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011,
+Cutri2013}. We adopt a flat $\Lambda$CDM cosmology with
+$\Omega_{\Lambda} = 0.73 $, $\Omega_{\rm M} = 0.27$, and $h =
+0.71$. All logarithms are to the base 10.
 
@@
 telescopes in Arizona and the 0.5 m Siding Springs Survey (SSS)
-Schmidt in Australia. 
-CRTS covers up to $\sim$2500 deg$^2$ per night, with 4 exposures per visit, separated
-by 10 min. The survey observes over 21 nights per lunation. The data
-are broadly calibrated to Johnson $V$ \citep[see ][for details]{Drake2013}
-and the current CRTS data set contains time series for
-approximately 400 million sources to $V \sim 20$ above Dec $> -30$
-from 2003 to 2016 May (observed with CSS and MLS) and 100 million
-sources to $V \sim 19$ in the southern sky from 2005 to 2013 (from
-SSS). CRTS has been used to study distant quasars previously
-\citep{Graham2014, Graham2015, Graham2015Nature, Graham2017, Graham2019b}.
+Schmidt in Australia. CRTS covers up to $\sim$2500 deg$^2$ per night,
+with 4 exposures per visit, separated by 10 min. The survey observes
+over 21 nights per lunation. The data are broadly calibrated to
+Johnson $V$ \citep[see ][for details]{Drake2013} and the current CRTS
+data set contains time series for approximately 400 million sources to
+$V \sim 20$ above Dec $> -30$ from 2003 to 2016 May (observed with CSS
+and MLS) and 100 million sources to $V \sim 19$ in the southern sky
+from 2005 to 2013 (from SSS). CRTS has been used to study distant
+quasars previously \citep{Graham2014, Graham2015, Graham2015Nature,
+Graham2017, Graham2019b}.
 
 PanSTARRS data is obtained via the Pan-STARRS Catalog Search
-interface\footnote{https://catalogs.mast.stsci.edu/panstarrs/}.
-We query the PS1 DR2 Detection catalog.
+interface\footnote{https://catalogs.mast.stsci.edu/panstarrs/}.  We
+query the PS1 DR2 Detection catalog.
 
@@
     The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
-complex, the \civ\ line, and the \mgii line. 
-  }
+    complex, the \civ\ line, and the \mgii line.}
   \label{fig:civ_clqs}
@@
 
-%% From Section 3.1; Place here to help with overall formatting of
-%% the paper
+%% From Section 3.1; Placed here to help with overall formatting of the paper
 \input{QSFit-results}
@@
 of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
-Myers2015}. The SDSS, BOSS, and eBOSS data are supplemented by
-spectra from the Low Resolution Imaging Spectrometer \citep[LRIS; ][]{Oke1995} on the 10m
-Keck {\sc I} telescope.  and the Double Spectrograph
-(DBSP) instrument on the 200'' Palomar telescope.
+Myers2015}. The SDSS, BOSS, and eBOSS data are supplemented by spectra
+from the Low Resolution Imaging Spectrometer \citep[LRIS; ][]{Oke1995}
+on the 10m Keck {\sc I} telescope.  and the Double Spectrograph (DBSP)
+instrument on the 200'' Palomar telescope.
 
@@
 \lambda^{\alpha}$, are also reported in these catalogues and from
-QSFit.  We quote the most appropriate value given the emission line
-wavelength.
+QSFit.
 
@@
   \caption{Observed spectra and best fit model in the region relevant
-    to \civ\ emission line for the quasars considered here.}
+    to \civ\ emission line for the quasars considered here.
+    The solid blue line is the Lorentzian profile fit the to the \civ\ emission line.
+    The long-dashed red line is the continuum fit, with the solid orange
+    line giving the overall fit. The short-dashed vertical lines gives the
+    rest wavelengths of the \civ\ doublet. }
   \label{fig:QSFit-CIV}
@@
 \end{figure}
-\subsection{Virial Black Hole Masses}
+\subsection{Virial Black Hole Masses}\label{sec:BH_masses} 
 The FWHM of broad lines is likely related to the mass of the
@@
 
-From the virial mass estimates, all our objects have SMBH masses $M >10^{9} M_{\odot}$.
-This is at the upper end of SMBH masses at all epochs, and towards the
-extreme of the mass distribution for $z\sim2$ objects.  
-Figure~\ref{fig:CIV_MBHvsREW} shows the \civ\ Equivalent width and the
-virial black hole masses for a sample of $\approx$20,000 $z>1.5$ SDSS
-quasars from the QSFit catalog as well as the estimates for the three
-\civ\ CLQs.
+\citet{Shen2011} reports Virial BH mass based on \mgii and \civ\ as
+$\log (M/M_{\rm BH}) = 9.55\pm0.05$ and $\log(M/M_{\rm BH}) =
+9.49\pm0.04$, respectively. We thus use the mean of these five values
+(three from our three epochs and the two \citet{Shen2011} values) to
+establish a working mean SMBH mass of $\log (M_{\rm BM, vir}/M_{\odot})
+= 9.726$ for J1205+3422.  J1638+2827 also has two virial mass
+measurments from Shen2011, but also has two measurements from
+\citet{Kozlowski2017} (again using \civ and \mgii). The mean mass
+measurement for J1638+2827 here is $\log(M_{\rm BM, vir}/M_{\odot} =
+9.091$. For J2228+2201 there are two \citet{Kozlowski2017}, leading to
+a mean mass of $\log(M_{\rm BM, vir}/M_{\odot} = 9.366$. We use these
+mean SMBH masses when calculating the Eddington ratios.
+
+From the virial mass estimates, all our objects have SMBH masses $M
+>10^{9} M_{\odot}$.  This is at the upper end of SMBH masses at all
+epochs, and towards the extreme of the mass distribution for $z\sim2$
+objects.  Figure~\ref{fig:CIV_MBHvsREW} shows the \civ\ Equivalent
+width and the virial black hole masses for a sample of $\approx$20,000
+$z>1.5$ SDSS quasars from the QSFit catalog as well as the estimates
+for the three \civ\ CLQs.
 
@@
 \subsection{Quantified Temporal Evolution of \civ\ Emission}
-Figure~\ref{fig:REWvsFWHM} shows the rest Equivalent Width (REW)
-versus the Full Width Half Maximum (FWHM) of the \civ\ emission line
-in the BOSS DR12 quasar sample using the catalogue of
-\citet{Hamann2017}.
+Quasars with interesting physical properties, such as extreme
+outflows, can be selected using EW and FWHM measurements, \citep[e.g.,
+the ``Extremely Red Quasars'' (ERQs)][]{Ross2015, Zakamska2016,
+Hamann2017, Zakamska2019}. Figure~\ref{fig:REWvsFWHM} shows the rest
+Equivalent Width (REW) versus the Full Width Half Maximum (FWHM) of
+the \civ\ emission line in the BOSS DR12 quasar sample using the
+catalogue of \citet{Hamann2017}.
 
@@
 
-\begin{table*}
-  \begin{tabular}{l l  ll ll cc r}
+\begin{table}
+  \centering
+  \begin{tabular}{l l l r}
     \hline
     \hline
-    \multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$}  & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref.
-\\
-                              &                                   &                                      &                                                              & \mgii                  & \civ                    &  \mgii           &  \civ                       &        \\
+    Object           & MJD      & $L_{\rm bol}$    &  $\eta_{\rm Edd}$  \\
     \hline
-                              & 53498                         & -27.74                          & 47.216$\pm$0.004                            &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen11\\
-    J1205+3422      & 58538                         &                                      &                                                            &                             &                             &                    &                               & \\
-                              & 58693                         &                                     &                                                  &                             &                             &                    &                               &   \\
+                         & 53498    & 47.216           &  -0.610                  \\
+    J1205+3422 & 58538    &  46.567          &  -1.259  \\                        %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
+                         & 58693     &  46.070         &  -1.756 \\
     \hline 
-                              & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen11\\
-    J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kozl17\\
-                              & 58583                          &                                      &                                                &                               &                            &                   &                                      &  \\
+                          & 54553   & 46.166    & -1.025 \\
+    J1638+2827  & 55832   & 45.981    & -1.210  \\                                            %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
+                          & 58583   & 46.504   & -0.687       \\
     \hline 
-                              & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kozl17\\
-    J2228+2201       & 56960                          &                                       &                                                &                              &                               &                 &                                        & \\
-                              & 58693                          &                                       &                                               &                               &                                &                &                   &  \\
+                          & 56189   & 46.231   &  -1.235 \\
+    J2228+2201   & 56960    & 47.342   & -0.124 \\                                             %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
+                          & 58693   & 46.826     &  -0.640 \\
     \hline
@@
   \end{tabular}
-  \caption{Physical properties of the \civ\ CLQs. 
-     $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude $K$-corrected to $z = 2$; Bolometric luminosity computed from the
-        monochromatic luminosity at 1350\AA\ using the spectral fits and
-        bolometric corrections (BC = 3.81) in \citet{Richards2006b}.
-        Virial BH masses using calibrations of \citet{VestergaardPeterson2006}.
-         $\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio computed using the virial BH mass.
-        Shen11 is \citet{Shen2011}. 
-        Kozl17 is \citet{Kozlowski2017}. }
+  \caption{
+    Bolometric luminosities are given in either \citet{Shen2011} or 
+    \citet{Kozlowski2017} for the three CLQs. We scale these 
+    values using our measured $\nu L_{\nu}$ continuum luminosity values.
+    From Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BM, vir}/M_{\odot}) = 9.726$ for J1205+3422,
+    $\log(M_{\rm BM, vir}/M_{\odot} = 9.091$ for  J1638+2827 
+    and $\log(M_{\rm BM, vir}/M_{\odot} = 9.366$ for J2228+2201. 
+    The Eddington Luminosity is 
+    $L_{\rm Edd} = 1.26\times10^{38} (M/M_{\odot})$ erg s$^{-1}$ and
+    %%  6.70456406676162      e+47  for J12
+    %%  1.5537120898684228  e+47  for J16
+    %%  2.9266483634099527  e+47 for J22
+   $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
 \label{tab:Eddington_ratios} 
-\end{table*}
+\end{table}
 
@@
 e.g. 1450\AA\ rest continuum luminosity, so that as the underlying UV
-continuum luminosity increases, the EW decreses. 
+continuum luminosity increases, the EW decreases. 
 Figure~\ref{fig:CIV_Baldwin} shows this for a sample (from the QSFit catalogue)
@@
 
+\citet{Graham2019} report the largest number of H$\beta$ CSQs with 111
+sources being identified. \citet{Graham2019} find that this population
+of extreme varying quasars is associated with {\it changes} in the
+Eddington ratio, (rather than just the magnitude of the Eddington
+ratio itself) and the timescales imply cooling/heating fronts
+propagating through the disk.\\
+{\bf NPR to finish this off} \\
+
 \subsection{Continuum and Line Changes: Comparisons to theoretical expectaions}
@@
   \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/MJD_vs_Eddington_20191129.png}
+  {figures/MJD_vs_Eddington_20191202.png}
   \vspace{-12pt}
-  \caption[]{Eddington Ratios of the three \civ\ CLQs and M87.}
+  \caption[]{Eddington Ratios of the three \civ\ CLQs.
+    Grayscale gives the Eddington Ratio ranges for the SDSS
+    \citep[from ][]{Shen2011} and the BOSS \citep[from ][]{Kozlowski2017)} 
+    catalogues.
+    Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.
+    The red region ($L / L_{\rm Edd} \approx 0.02\pm0.01$;  $\eta =-1.7\pm0.13$) is
+    the transition accretion rate suggested by \citet{NodaDone2018}.
+    A ``High/Soft State'' with $\eta_{\rm Edd} \geq -1$ and a
+    a ``Low/Hard State'' with $\eta_{\rm Edd} \leq -2$ are indicated 
+    with dahsed lines and arrows. 
+  }
   \label{fig:Eddington_ratios}
@@
 (1) a ``Low/Hard State'' with $-2 \lesssim \eta_{\rm Edd} \lesssim  -1$;
-(1) a ``High/Soft State'' with $\eta_{\rm Edd} \lesssim -2$.
+(1) a ``Low/Hard State'' with $\eta_{\rm Edd} \lesssim -2$.
 These are given as shaded regions in Figure~\ref{fig:Eddington_ratios}.

### 2019-12-02 plots/MJD_Eddington/mjd_vs_Eddington.py

@@ -17,9 +17,12 @@ from astropy.io import fits
 
 ## Reading in the data
 ##     C I V     C  L Q s
-path   = '../../data/CLQ_line_measurements/'
-infile = 'MJD_Eddington.dat'
-CLQs   = ascii.read(path+infile)
+path     = '../../data/CLQ_line_measurements/'
+infile   = 'MJD_Eddington.dat'
+CLQs     = ascii.read(path+infile)
+CLQs_MJD = CLQs['MJD']
+CLQs_MBH = CLQs['MBH']
+CLQs_eta = CLQs['eta']
 
 ##
 ##  D R 7 Q    S h e n   et al.  (2011)     
@@ -107,58 +110,55 @@ ax.hexbin(dr12q_mjd, dr12q_etaEdd, bins='log',  gridsize=gridsize, cmap=color_ma
 for ii in range(len(CLQs)):
     
     if str(CLQs['Object'][ii]) == 'J1205+3422':
-        if (CLQs['MJD'][ii] ==  53498):
-            ax.scatter(CLQs['MJD'][ii], CLQs['eta_MgII'][ii], color='k',       alpha=alpha, marker='o', s=ms_large*1.6)
-            ax.scatter(CLQs['MJD'][ii], CLQs['eta_MgII'][ii], color='fuchsia', alpha=alpha, marker='o', s=ms_large)
+        if (CLQs_MJD[ii] ==  53498):
+            ax.scatter(CLQs_MJD[ii], CLQs_eta[ii], color='k',       alpha=alpha, marker='o', s=ms_large*1.6)
+            ax.scatter(CLQs_MJD[ii], CLQs_eta[ii], color='fuchsia', alpha=alpha, marker='o', s=ms_large)
             J12_53498  = mlines.Line2D([], [], label='J1205+3422 (53498)', color='fuchsia',
                        marker="o", markeredgecolor='k', markeredgewidth=1.4, markersize=7,  linestyle='None')
-            
-        if (CLQs['MJD'][ii] ==  58693):
-            ax.scatter(CLQs['MJD'][ii], CLQs['eta_MgII'][ii], color='k',       alpha=alpha, marker='s', s=ms_large*1.6)
-            ax.scatter(CLQs['MJD'][ii], CLQs['eta_MgII'][ii], color='fuchsia', alpha=alpha, marker='s', s=ms_large)
-            J12_58693 = mlines.Line2D([], [], label='J1205+3422 (58693)', color='fuchsia',
+        if (CLQs_MJD[ii] ==  58538):
[…]

### 2019-12-04 tex/CIV_CLQs.tex
quite a bit update on the plot/hexbin_plots/MBH_REW/ figures and code

@@
 {Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
- Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
-\newauthor Daniel Stern$^{6}$ and Giorgio Calderone$^{7}$
+Matthew Graham$^{2}$,
+Giorgio Calderone$^{3}$, 
+K. E. Saavik Ford$^{4,5,6}$,  
+\newauthor Barry McKernan$^{4,5,6}$  and Daniel Stern$^{7}$  
 \\
@@
 $^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
-$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
-$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
-$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
-$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
-$^{7}$INAF -- Osservatorio Astronomico di Trieste, Via Tiepolo 11, I-34143 Trieste, Italy \\
+$^{3}$INAF -- Osservatorio Astronomico di Trieste, Via Tiepolo 11, I-34143 Trieste, Italy \\
+$^{4}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
+$^{5}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
+$^{6}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
+$^{7}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
 }
@@
 SDSS in 2005 May, as a bright, $g\approx18.0$, blue-sloped quasar with
-broad \siiv, \civ, \ciii and \mgii. \ciii and \civ\ have large
+broad Si\,{\sc iv}, \civ, \ciii and Mg\,{\sc ii}. \ciii and \civ\ have large
 blueshifts of $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km
@@
 shape and line flux intensity. Around 870 days in the rest-frame after
-the second spectral epoch, \lya, \nv, \civ, \ciii and \mgii are all
+the second spectral epoch, Ly$\alpha$, N\,{\sc v}, \civ, C\,{\sc iii}] and \mgii are all
 apparent and broad, with \mgii being seen for the first time at high
 signal-to-noise. The light curve is consistent with this spectral
-brightening, increasing from $\sim$20th magnitude to $\sim$18.5
+brightening, increasing from $\sim$20th magnitude to $\sim$18.5th 
 magnitude at optical wavelengths. An absorption feature between \lya
@@
 luminosity and slope at rest-frame 1450\AA, \civ\ line luminosity,
-FWHM and EW are given in Tabl;e~\ref{tab:QSFit-results}. All fits are
+FWHM and EW are given in Table~\ref{tab:QSFit-results}. All fits are
 performed with $E(B-V) = 0$ and the best fit model in the region of
@@
 \times 10^{3}$~km~s$^{-1}$, i.e. values exceeding the usual widths of
-genuine narrow lines ($\lesssim$ $10^3$ km s$^{-1}$); by allowing a
+genuine narrow lines ($\lesssim$10$^{3}$ km s$^{-1}$); by allowing a
 second component, to have such large widths their parameters would
@@
    \caption[]{The virial black hole masses of $\approx$20,000 $z>1.5$ quasars
-     from QSFit catalogue \citep{Calderone2017} and the \civ\ Equivalent widths.
-     Different quasars are given different colours: J1205+3422 purple; J1638+2827 green; J2228+2201 is blue.
-     Different epochs different symbols: first epoch circles; second epoch squares; third epoch diamonds. 
-   }
+     from QSFit catalogue \citep{Calderone2017} and the \civ\
+     Equivalent widths.  Different quasars are given different colours:
+     J1205+3422 purple; J1638+2827 green; J2228+2201 is blue.  Different
+     epochs different symbols: first epoch circles; second epoch squares;
+     third epoch diamonds.  As noted in Table~\ref{tab:QSFit-results},
+     $^{*}$ signifies the \civ\ line is very weak and the associated
+     estimates are likely unreliable.}
    \label{fig:CIV_MBHvsREW}
@@
 \citet{Shen2011} reports Virial BH mass based on \mgii and \civ\ as
-$\log (M/M_{\rm BH}) = 9.55\pm0.05$ and $\log(M/M_{\rm BH}) =
+$\log (M_{\rm BH, Vir}/M_{\odot}) = 9.55\pm0.05$ and $\log(M_{\rm BH, Vir}/M_{\odot}) =
 9.49\pm0.04$, respectively. We thus use the mean of these five values
@@
 ($\sim$7$\sigma$) is observed between the second and third observation
-epochs.
+epochs. The magnitude of the velocity blueshifts ($\sim200-1100$ km s$^{-1}$)
+are consistent with recent results into the properties of 
+rest-frame UV spectra over the redshift range $1.5 \leq z \leq 7.5$
+\citep{Meyer2019}.
 
@@
     values using our measured $\nu L_{\nu}$ continuum luminosity values.
-    From Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BM, vir}/M_{\odot}) = 9.726$ for J1205+3422,
-    $\log(M_{\rm BM, vir}/M_{\odot} = 9.091$ for  J1638+2827 
+    From Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BM, vir}/M_{\odot}) = 9.726$ for J1205+3422; 
+    $\log(M_{\rm BM, vir}/M_{\odot} = 9.091$ for  J1638+2827, 
     and $\log(M_{\rm BM, vir}/M_{\odot} = 9.366$ for J2228+2201. 
@@
 
-\citet{Graham2019} report the largest number of H$\beta$ CSQs with 111
-sources being identified. \citet{Graham2019} find that this population
+\citet{Graham2019b} report the largest number of H$\beta$ CSQs with 111
+sources being identified. \citet{Graham2019b} find that this population
 of extreme varying quasars is associated with {\it changes} in the
@@
     Grayscale gives the Eddington Ratio ranges for the SDSS
-    \citep[from ][]{Shen2011} and the BOSS \citep[from ][]{Kozlowski2017)} 
+    \citep[from ][]{Shen2011} and the BOSS \citep[from ][]{Kozlowski2017} 
     catalogues.

### 2019-12-04 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py

@@ -230,55 +230,55 @@ for ii in range(len(CLQs)):
             #ax.errorbar(CLQs_logContLum[ii], CLQs_logREW[ii], color='fuchsia',xerr=CLQs_logREWerr[ii], yerr=CLQs_FWHMerr[ii], fmt='o', linewidth=lw)
             ax.scatter(CLQs_logContLum[ii], CLQs_logREW[ii], color='k',       alpha=alpha, marker='o', s=ms_back)
             ax.scatter(CLQs_logContLum[ii], CLQs_logREW[ii], color='fuchsia', alpha=alpha, marker='o', s=ms)
-            J12_53498 = mlines.Line2D([], [], label='J1205+3422 (53498)', color='fuchsia',
+            J12_53498 = mlines.Line2D([], [], label=r'J1205+3422 (53498)', color='fuchsia',
                         marker="o", markeredgecolor='k', markeredgewidth=mrkedwd, markersize=markersize,  linestyle='None')
         if (CLQs['MJD'][ii] ==  58538):
             #ax.errorbar(CLQs_logContLum[ii], CLQs_logREW[ii], color='k',      xerr=CLQs_logREWerr[ii], yerr=CLQs_FWHMerr[ii], fmt='s', linewidth=lw*l_back)
             #ax.errorbar(CLQs_logContLum[ii], CLQs_logREW[ii], color='fuchsia',xerr=CLQs_logREWerr[ii], yerr=CLQs_FWHMerr[ii], fmt='s', linewidth=lw)
             ax.scatter (CLQs_logContLum[ii], CLQs_logREW[ii], color='k',       alpha=alpha, marker='s', s=ms_back)
             ax.scatter (CLQs_logContLum[ii], CLQs_logREW[ii], color='fuchsia', alpha=alpha, marker='s', s=ms)
-            J12_58538 = mlines.Line2D([], [], label='J1205+3422 (58538)', color='fuchsia',
+            J12_58538 = mlines.Line2D([], [], label=r'J1205+3422 (58538)', color='fuchsia',
                         marker="s", markeredgecolor='k', markeredgewidth=mrkedwd, markersize=markersize,  linestyle='None')
         if (CLQs['MJD'][ii] ==  58693):
             #ax.errorbar(CLQs_logContLum[ii], CLQs_logREW[ii], color='k',      xerr=CLQs_logREWerr[ii], yerr=CLQs_FWHMerr[ii], fmt='D', linewidth=lw*l_back)
[…]

### 2019-12-04 plots/hexbin_plots/Baldwin/Lum_vs_Lum_hexbin.py

@@ -20,7 +20,7 @@ cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)
 
 
 ## Reading in the data
-path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/CLQ_line_measurements/'
+path      = '../../../data/CLQ_line_measurements/'
 filename  = 'REW_FWHM.dat'
 CLQs      = ascii.read(path+filename)
 
@@ -36,7 +36,7 @@ log_errREW = np.log10(CLQs['errREW'])
 
 
 ##  Hamann et al. (2017) and Kozłowski (2017) merged BOSS DR12 catalog
-path      = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/QSO_CIV_catalogs/'
+path      = '../../../data/QSO_CIV_catalogs/'
 filename  = 'BOSS_Ham17Koz17_DR12Q.fits'
 infile    = path+filename
 data_full = fits.open(infile)

### 2019-12-04 plots/hexbin_plots/MBH_REW/MBH_REW_hexbin.py

@@ -17,7 +17,6 @@ import matplotlib.pyplot as plt
 import matplotlib.mlab   as mlab
 import matplotlib.lines  as mlines
 
-
 ## Setting up the cosmology
 cosmo = FlatLambdaCDM(H0=71, Om0=0.27, Tcmb0=2.725)                                                                                                                          
 ## Reading in the data
@@ -109,12 +108,15 @@ gridsize  = 200
 color_map = plt.cm.Spectral_r
 
 ##
-## Setting things all up... :-)
+## Setting things all up... 
+## Comment in/out which values you’d like
 ##
-#x = logBH_virial
-#y = log_EW_QSFit
-x = log_tMBH
-y = log_tREW
+## 20K objects::
+x = logBH_virial
+y = log_EW_QSFit
+## 200K objects::
+#x = log_tMBH
+#y = log_tREW
 
 ##
 ##  P L O T T I N G    T H E    D A T A
@@ -170,17 +172,17 @@ for ii in range(len(CLQs)):
         if (CLQs['MJD'][ii] ==  53498):
             ax.scatter(CLQs_MBH[ii], CLQs_logREW[ii], color='k',       alpha=alpha, marker='o', s=ms_back)
             ax.scatter(CLQs_MBH[ii], CLQs_logREW[ii], color='fuchsia', alpha=alpha, marker='o', s=ms)
-            J12_53498 = mlines.Line2D([], [], label='J1205+3422 (53498)', color='fuchsia',
+            J12_53498 = mlines.Line2D([], [], label=r'J1205+3422 (53498)', color='fuchsia',
                         marker="o", markeredgecolor='k', markeredgewidth=mrkedwd, markersize=markersize,  linestyle='None')
         if (CLQs['MJD'][ii] ==  58538):
             ax.scatter (CLQs_MBH[ii], CLQs_logREW[ii], color='k',       alpha=alpha, marker='s', s=ms_back)
             ax.scatter (CLQs_MBH[ii], CLQs_logREW[ii], color='fuchsia', alpha=alpha, marker='s', s=ms)
-            J12_58538 = mlines.Line2D([], [], label='J1205+3422 (58538)', color='fuchsia',
+            J12_58538 = mlines.Line2D([], [], label=r'J1205+3422 (58538)', color='fuchsia',
                         marker="s", markeredgecolor='k', markeredgewidth=mrkedwd, markersize=markersize,  linestyle='None')
[…]

### 2019-12-04 plots/hexbin_plots/REW_FWHM/REW_FWHM_hexplot.py

@@ -109,21 +109,21 @@ for ii in range(len(CLQs)):
             ax.errorbar(CLQ_REW[ii], CLQ_FWHM[ii], color='fuchsia', xerr=CLQ_errREW[ii], yerr=CLQ_errFWHM[ii], fmt='o', linewidth=lw)
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='k',       alpha=alpha, marker='o', s=ms*ms_back)
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='fuchsia', alpha=alpha, marker='o', s=ms)
-            J12_53498  = mlines.Line2D([], [], label='J1205+3422 (53498)', color='fuchsia',
+            J12_53498  = mlines.Line2D([], [], label=r'J1205+3422 (53498)', color='fuchsia',
                        marker="o", markeredgecolor='k', markeredgewidth=1.4, markersize=7,  linestyle='None')
         if (CLQs['MJD'][ii] ==  58538):
             ax.errorbar(CLQ_REW[ii], CLQ_FWHM[ii], color='k',       xerr=CLQ_errREW[ii], yerr=CLQ_errFWHM[ii], fmt='s', linewidth=lw*l_back)
             ax.errorbar(CLQ_REW[ii], CLQ_FWHM[ii], color='fuchsia', xerr=CLQ_errREW[ii], yerr=CLQ_errFWHM[ii], fmt='s', linewidth=lw)
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='k',       alpha=alpha, marker='s', s=ms*ms_back)
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='fuchsia', alpha=alpha, marker='s', s=ms)
-            J12_58538 = mlines.Line2D([], [], label='J1205+3422 (58538)', color='fuchsia',
+            J12_58538 = mlines.Line2D([], [], label=r'J1205+3422 (58538)', color='fuchsia',
                        marker="s", markeredgecolor='k', markeredgewidth=1.4, markersize=7,  linestyle='None')
         if (CLQs['MJD'][ii] ==  58693):
             ax.errorbar(CLQ_REW[ii], CLQ_FWHM[ii], color='k',       xerr=CLQ_errREW[ii], yerr=CLQ_errFWHM[ii], fmt='D', linewidth=lw*l_back)
[…]

### 2019-12-10 tex/CIV_CLQs_20191210.tex
submitting tomorrow...

--- 2019-12-04 tex/CIV_CLQs.tex
@@
 
-\title[High-redshift CLQs]{The first high-redshift Changing Look Quasars}
+\title[High-redshift CLQs]{The first high-redshift changing-look quasars}
 
@@
 {Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
-Matthew Graham$^{2}$,
+Matthew J. Graham$^{2}$,
 Giorgio Calderone$^{3}$, 
@@
 We report on three redshift $z>2$ quasars with dramatic changes in
-their \civ\ emission lines, the first ``Changing-Look'' quasars at
+their \civ\ emission lines, the first sample of changing-look quasars (CLQs) at
 high redshift.  This is also the first time the changing-look
-behaviour has been seen in a high-ionization emission line.  SDSS
-J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour in
+behaviour has been seen in a high-ionisation emission line.  SDSS
+J1205+3422, J1638+2827, and J2228+2201 show interesting behaviour in
 their observed optical light curves, and subsequent spectroscopy shows
@@
 collapse and emergence being displayed in rest-frame timescales of
-$\sim$240-1640 days.  These are very quick changes, especially when
+$\sim$240-1640 days.  These are rapid changes, especially when
 considering virial black hole mass estimates have all three quasars
@@
 of the full population distribution, and showing indications of an
-intrinsic Baldwin Effect. We put these observations in context with
-recent ``state-change'' models, but note that even in their
-`low-state', the \civ\ CLQs are above $\sim$10\% in Eddington
+intrinsic Baldwin effect. We put these observations in context with
+recent state-change models, but note that even in their
+low-state, the \civ\ CLQs are above $\sim$10\% in Eddington
 luminosity.
@@
 their first optical identification
-\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic changes
+\citep[e.g.,][]{MatthewsSandage1963}.
+Dramatic changes
 in the broad emission lines (BELs) of quasars has only recently been
 identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
-``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
-have now been assembled \citep[e.g.][]{MacLeod2019, Graham2019b}. The
+``changing-look'' quasars (CLQs) or ``changing-state'' quasars (CSQs)
+have now been assembled \citep[e.g.,][]{MacLeod2019, Graham2019b}. The
 community uses both these terms as a cover for the underlying
@@
 the extension to the BELs of quasar continuum variability \citep[e.g.,
-][]{MacLeod2012} whereas the CSQs have a `state-transition' similar to
+][]{MacLeod2012} whereas the CSQs have a state-transition similar to
 that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019a}. In
-this paper, we use the term `Changing Look', as we are currently
+this paper, we use the term ``changing-look'', as we are currently
 agnostic, and confessedly ignorant, to the underlying physical
@@
       \hline  \hline 
-      Line                 & $\lambda$ &  Transition  & Ionization   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
-                              &  / \AA\    & energy / eV &  energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & ($\times10^{8}$  / s$^{-1}$)               \\      \hline
+      Line                 & $\lambda$ &  Transition  & Ionisation   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
+
+                              &  / \AA\    & Energy / eV &  Energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & / $10^{8}$ s$^{-1}$               \\      \hline
       H LyLim           &   912.324   & 13.5984    & 13.5984        & 1$s$                    & $^2$S     & 1/2          & $\infty$                  &                                 &             & 109 678.7       & 1.23$\times10^{-6}$  \\
@@
       atomic data.  Data from the NIST Atomic Spectra Database
-      \citep{Kramida2018, Kramida2019}.  The Transition Energies are
-      $E=hc/\lambda$ for the given wavelength. The Ionization Energy is the
-      energy required to ionize the given species, e.g. 64.49 eV are needed
-      to create a \cv\ ion.  Transitions Level configurations are given in
-      standard spectroscopic notation $A_{i,j}$ are transition
-      probabilities.  Data from the NIST Atomic Spectra Database
-      \citep{Kramida2018, Kramida2019}.}
+      \citep{Kramida2018, Kramida2019}.  The transition energies are
+      $E=hc/\lambda$ for the given wavelength. The ionisation energy is the
+      energy required to ionise the given species, e.g., 64.49 eV is needed
+      to create a \cv\ ion.  Transitions level configurations are given in
+      standard spectroscopic notation, with $A_{i,j}$ denoting the transition
+      probabilities.}
     \label{tab:atomic_lines}
@@
 attention paid to the H$\beta$ emission line, observed from optical
-spectroscopy. Recent work report on discoveries of \mgii Changing-look
+spectroscopy. Recent works report on discoveries of \mgii changing-look
 AGN \citep{Guo2019, Homan2019}. However, current CLQ studies have
@@
 
-While there have been many studies on triply ionized carbon, i.e
+While there have been many studies on triply ionised carbon, i.e.,
 \civ, these have tended to focus on broad absorption line quasars
-\citep[BAL quasars; see Table 1 of][]{Hemler2019} or the Baldwin Effect
-\citep[BEff; ][]{Baldwin1977, Bian2012, Jensen2016,
+\citep[e.g., Table 1 of][]{Hemler2019} or the Baldwin effect
+\citep{Baldwin1977, Bian2012, Jensen2016,
 Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
-types of Baldwin effect are present in the literature: the {\it
-global} (or {\it ensemble}) Baldwin Effect, which is an
-anti-correlation between the Equivalent Width (EW) of the emission line and the
+types of Baldwin effect are present in the literature: {\it (i)} the {\it
+global} (or {\it ensemble}) Baldwin effect, which is an
+anti-correlation between the equivalent width of the emission line and the
 underlying continuum luminosity of {\it single-epoch} observations of
-a {\it large number} of AGN and second, the {\it intrinsic} Baldwin
+a {\it large number} of AGN, and {\it (ii)} the {\it intrinsic} Baldwin
 effect, the same anti-correlation but in an {\it individual, variable}
@@
     \multirow{2}{*}{Object} & \multirow{2}{*}{Redshift} & $g$-band & \multirow{2}{*}{MJD} & \multirow{3}{*}{Instrument} & Exposure      &   SDSS               & \multirow{2}{*}{Notes} \\
-                                         &                                        &   (mag)      &                                 &                                             &  Time (secs) &   Plate-FiberID  & \\
+                                         &                                        &   / mag      &                                 &                                             &  time / sec &   Plate-FiberID  & \\
     \hline  
@@
 redshift. Moreover, these are the first cases for substantial changes
-of ions with high ionization potentials (I.P.'s $>$2 Rydberg), thus
+of ions with high ionisation potentials (I.P.'s $>$2 Rydberg), thus
 linking the ionizing photons to the energetic inner accretion disk,
@@
 energy corresponds to a thermal temperature of $T \gtrsim$
-4$\times10^{5}$, implying a heating energy source of (soft) X-ray
+4$\times10^{5}$ K, implying a heating energy source of (soft) X-ray
 photons.
@@
 flux and the change in the line width, but no correlations between the
-change in flux and changes in line center and skewness.  These authors
+change in flux and changes in line center or skewness.  These authors
 find that the relation between line flux change and line width change
@@
 
-\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$
+\citet{Richards2011} explored the broad emission line region in over 30,000 $z > 1.54$
 SDSS quasars, concentrating on the properties of the \civ\ emission
@@
 have low \civ\ EWs, and that the low-EW sources span a range of
-blueshift. Other high-ionization lines, such as \heii, also show
+blueshift. Other high-ionisation lines, such as \heii, also show
 similar blueshift properties. The ratio of the line width of \civ\ to
@@
 is somewhat interesting, the main value of this study is we move from
-the low-ionization energy Balmer emission line series to the
-high-ionization emission lines, in particular \civ\ $\lambda$1549.
+the low-ionisation energy Balmer emission line series to the
+high-ionisation emission lines, in particular \civ\ $\lambda$1549.
 
@@
 
-\subsection{Multi-Wavelength Properties}
+\subsubsection{Multi-Wavelength Properties}
 {\bf DS to write something on FIRST non-detections; possibly check the X-rays too?} \\
@@
 \section{Results}
-\subsection{Photometric and Overal Spectral Evolution}
+\subsection{Photometric and Overall Spectral Evolution}
 Figure~\ref{fig:civ_clqs} presents the optical and mid-IR light
@@
 become highly degenerate with the ``broad'' components, and the latter
-would also have much larger FWHM ($\sim$$10^{4}$ km s$^{-1}$); and by
-neglecting the narrow components we have a consistent fit across all
+would also have much larger FWHM ($\sim$$10^{4}$ km s$^{-1}$); moreover, by
+neglecting the narrow components, we have a consistent model across all
 epochs.
 
-The quasar continuum, evaluated at 1450\AA\ , and the \civ\ line
+Both the quasar continuum (evaluated at 1450\AA), and the \civ\ line
 luminosities follow a similar evolution, with a ratio of $\sim$20-30,
@@
 following a ``bluer-when-brighter'' pattern, suggesting that a
-distinct emerging component is responsible or both the slope and
+distinct emerging component is responsible for both the slope and
 luminosity variations.  In J1638+2827 the opposite behaviour is
@@
 that would be inconsistent with the other analyses.
-In all cases where the \civ\ line profile is reliably constrained the
+In all cases where the \civ\ line profile is reliably constrained and the
 \civ\ FWHM is approximately constant, with maximum variations
@@
 1450\AA\ continuum luminosity and slope, the \civ\ line FWHM
-and virial black hole mass are given in Figure~\ref{fig:QSFit-results}.
+and virial black hole mass are shown in Figure~\ref{fig:QSFit-results}.
 
@@
 \subsection{The \civ\ Baldwin Effect}
-The Baldwin Effect \citep[Beff; ][]{Baldwin1977} is an empirical 
+The Baldwin effect \citep{Baldwin1977} is an empirical 
 relation between emission-line REWs and continuum luminosity in
@@
 \citet{Hamann2017} and \citet{Calderone2017} present recent
-measurements of the Beff for large quasar samples.
+measurements of the Baldwin effect for large quasar samples.
 
@@
 \citep[e.g.][]{Goad2004, Rakic2017}.  The slope of the CLQs intrinsic
-BEff is $\approx-0.38$, as shown by the dashed red line in
+Baldwin effect is $\approx-0.38$, as shown by the dashed red line in
 Fig.~\ref{fig:CIV_Baldwin}.
@@
 \citet{Trakhtenbrot2019} report on the quasar 1ES 1927+654 which was
-initially seenn to lack broad emission lines and line-of-sight
+initially seen to lack broad emission lines and line-of-sight
 obscuration, i.e, a ``Type 2'' quasar at redshift $z=0.02$. This
@@
 \citet{Trakhtenbrot2019} present.  The multiwavelength data that
-\citet{Trakhtenbrot2019} have includes a UV spectrum of 1ES 1927+654.
+\citet{Trakhtenbrot2019} includes a UV spectrum of 1ES 1927+654.
 Interestingly, however, there is no evidence for broad UV emission lines, including
@@
 probed by the SDSS and Pan-STARRS1 surveys. They find 17 new CLQs
-which is $\sim$20\% of the observerd sample. This CLQ fraction
+which is $\sim$20\% of the observed sample. This CLQ fraction
 increases from 10\% to roughly half, as the continuum flux ratio
@@
 {\bf SF and BM to add a little more here}\\
-The \civ\ line is one of the strongest collisionally excited lines in quasar spectra \citep[e.g.][]{HamannFerland1999}, and \civ\ emission probes the photoionization environment produced by the innermost disk, as indicated by RM time-delay measurements.
+The \civ\ line is one of the strongest collisionally excited lines in quasar spectra \citep[e.g.][]{HamannFerland1999}, and \civ\ emission probes the photoionisation environment produced by the innermost disk, as indicated by RM time-delay measurements.
 
@@
 \citep[e.g.,][]{DexterAgol2011} may provide viable explanations for our observations.
-%% I want to say a bit more here about the generic probe of photoionization vs shielding and conditions in the BL region but that will take more time.
+%% I want to say a bit more here about the generic probe of photoionisation vs shielding and conditions in the BL region but that will take more time.
 
@@
 an advection dominated accretion flow, while the overall drop in
-luminosity appears consistent with the hydrogen ionization disc
+luminosity appears consistent with the hydrogen ionisation disc
 instability.  Crucially \citet{NodaDone2018} make the prediction that
@@
 `Changing-Look'' quasars at high redshift.  This is also the first
-time the changing-look behaviour has been seen in a high-ionization
+time the changing-look behaviour has been seen in a high-ionisation
 emission line.
@@
 %% KESF \& BM thank CalTech/JPL for support during sabbatical.  
+MJG is supported in part by the NSF grants AST-1815034, and the NASA grant 16-ADAP16-0232. 
 \\

### 2019-12-10 tex/CIV_CLQs_DS.tex
submitting tomorrow...

--- 2019-12-10 tex/CIV_CLQs_20191210.tex
@@
 their first optical identification
-\citep[e.g.,][]{MatthewsSandage1963}.
+\citep[e.g.,][]{MatthewsSandage1963}. %MacLeod2012}.
 Dramatic changes
@@
       Line                 & $\lambda$ &  Transition  & Ionisation   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
-
                               &  / \AA\    & Energy / eV &  Energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & / $10^{8}$ s$^{-1}$               \\      \hline
@@
 AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
-collisionally excited broad {\it emission} line (BEL) of \civ\ and
-indeed \ciii have not to this point been reported.
+collisionally excited broad {\it emission} line of \civ\ --- and
+indeed \ciii --- have not to this point been reported.
 
@@
 Here, we present new results for three quasars which show dramatic
-changes in their \civ\ and \ciii broad emission line properties as
-well as in their underlying continuum. These are some of the first
-examples of ``Changing Look Quasars'' at high ($z>1$)
+changes in their \civ\ and \ciii broad emission line properties and underlying continuum. These are some of the first
+examples of CLQs at high ($z>1$)
 redshift. Moreover, these are the first cases for substantial changes
 of ions with high ionisation potentials (I.P.'s $>$2 Rydberg), thus
-linking the ionizing photons to the energetic inner accretion disk,
-potentially by inverse Compton scattering of lower energy photons to
-higher energies.
+linking the ionizing photons to the energetic inner accretion disk.
+% potentially by inverse Compton scattering of lower energy photons to higher energies.
 
@@
 \citep{Kramida2018}. For ionisation energies, 47.89 eV (3.519 Ry) is
-required for doubly-ionised C~III to become triply-ionised \civ.
-64.49 eV (4.74 Ry) is the energy needed to ionize \civ\ itself. This
+required for doubly-ionised C\,{\sc iii} to become triply-ionised \civ, and
+64.49 eV (4.74 Ry) is needed to ionise \civ\ itself. This
 energy corresponds to a thermal temperature of $T \gtrsim$
@@
 \civ\ emission line: {\it (i)} the anti-correlation between the \civ\
-equivalent widths (EWs) and luminosity (i.e., the Baldwin Effect;
-BEff) and {\it (ii)} the blueshifting of the peak of \civ\ emission
+equivalent widths (EWs) and luminosity (i.e., the Baldwin effect)
+and {\it (ii)} the blueshifting of the peak of \civ\ emission
 with respect to the systemic redshift.  We denote the velocity offset
@@
 negative $V_{\rm off}$ value means the line is redshifted.
-\citet{Richards2011} find the blueshift of the \civ\ emission line, is
-found to be nearly ubiquitous, with a mean shift of $V_{\rm off}
+\citet{Richards2011} find a blueshift of the \civ\ emission line is
+nearly ubiquitous, with a mean shift of $V_{\rm off}
 \sim$810 km s$^{-1}$ for radio-quiet (RQ) quasars and $V_{\rm off}
 \sim$360 km s$^{-1}$ for radio-loud (RL) objects. \citet{Richards2011}
-also find the BEff is present in both the RQ and RL studied samples.
-These author conclude that these two \civ\ parameters (EQW and
+also find the Baldwin effect is present in both the RQ and RL studied samples.
+These author conclude that these two \civ\ parameters (EW and
 blueshift) are capturing an important trade-off between ``disk'' and
@@
 \citep[e.g.,][]{Murray1995, Elvis2000, Proga2000, Leighly2004b}, with
-one dominating over the other depending on the shape of the SED.
+one dominating over the other depending on the shape of the quasar spectral energy distribution (SED).
 
-Using the multi-epoch spectra of 362 quasars from the Sloan Digital
-Sky Survey Reverberation Mapping \citep[SDSS-RM; ][]{Shen2015,
-Shen2019} project, \citet{Sun2018} investigate the blueshift of \civ\
+Using the multi-epoch spectra of 362 quasars from the SDSS Reverberation Mapping project \citep[SDSS-RM; ][]{Shen2015,
+Shen2019}, \citet{Sun2018} investigate the blueshift of \civ\
 emission relative to \mgii emission, and its dependence on quasar
@@
 \civ\ blueshift and EW, though further investigation here is
-warranted. There is also the finding that the objects with that
+warranted. They also find that quasars with the
 largest blueshifts are less variable and tend to have higher Eddington
-ratios. \citet{Sun2018} explain their results these by suggesting that
-quasar SEDs have weaker X-ray emission (or at least a larger UV/optical-to-Xray
-spectral index, $\alpha_{\rm ox}$) and thus become {\it
-softer} with {\it increasing Eddington ratio} along with the presence
-of X-ray shielding by the inner accretion disk. However, a high
+ratios. 
+% \citet{Sun2018} explain their results these by suggesting that
+% quasar SEDs have weaker X-ray emission (or at least a larger UV/optical-to-Xray
+% spectral index, $\alpha_{\rm ox}$) and thus become {\it
+% softer} with {\it increasing Eddington ratio} along with the presence
+% of X-ray shielding by the inner accretion disk. However, a high
 Eddington ratio alone might be an insufficient condition for the \civ\
@@
 \citet{Doan2019}. \citet{Dyer2019} provide a detailed analysis of 340
-quasars at high-redshift ($1.62<z<3.30$) from the SDSS-RM project,
-which we will compare our results to.
+quasars at high redshift ($1.62<z<3.30$) from the SDSS-RM project,
+which we  compare our results to in \S~XXX.
 
@@
 This paper is organised as follows. In Section 2, we describe our
-sample selection, catalogues, and observational data sets.  In Section
-3, we show the high-$z$ quasars and report the line properties for the
-quasars at the observed epochs.  We give a very brief theoretical
-discussion in Section 4. We present our conclusions in Section 5.  We
+sample selection, catalogues, and observational data sets.  Section
+3 presents the high-redshift quasars and reports their time-variable line properties.  We provide a brief theoretical
+discussion in Section 4, and Section~5 presents our conclusions.  We
 report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
 Fukugita1996} unless otherwise stated. For the WISE bands, $m_{\rm AB}
-= m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1 at
-3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011,
+= m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for {\it WISE} W1 
+(3.4$\mu$m) and W2 (4.6$\mu$m), respectively \citep{Cutri2011,
 Cutri2013}. We adopt a flat $\Lambda$CDM cosmology with
@@
 In standard \citet{SS73} thin disk models, large changes in the continuum flux are not permitted over short timescales due to the relatively long viscous time associated with such disks.
-Given the observed short timescale continuum variations, it is not surprising that the \citet{SS73} disk may fail on other fronts.
-%The \civ\ variations observed in our sources...
+Given the observed short timescale continuum variations, we must consider more complex models.
+We note that two of our sources (J1205+3422 and J2228+2201) have \civ\ REW and continuum luminosity changes which fall comfortably along a line, implying their variation is consistent with an intrinsic Baldwin Effect (see Fig.
+\ref{fig:CIV_Baldwin}).
+That is, the excitation of the \civ\ line is driven by the changes in the continuum; however the excited gas cannot reach an equilibrium excitation state as quickly as the continuum changes, thus the slope of the intrinsic Baldwin Effect line is greater than that of the overall (ensemble) slope, which is derived from many single-epoch observations, the majority of which are assumed to be in equilibrium.
+The presence of an intrinsic Baldwin Effect implies those sources may comfortably fit into the sample of \civ\ variable quasars explored by \citet{Dyer2019}.
+Similar to those authors, we consider slim accretion disk models e.g., \citet[][]{Abramowicz1988} which may explain the observed variability.
+In particular, we note the summary timescales for disk variation in \citet{Stern2018}, which are shorter for taller disks, permitting changes similar to those observed if they are caused by heating or cooling fronts propagating on the disk sound crossing time.
+\citet{Dyer2019} also consider inhomogeneous disk models
+\citep[e.g.][]{DexterAgol2011} where flux variations are driven by azimuthal inhomogeneities in the temperature of the disk.
+Such inhomogeneities could arise from disk instabilities \citep[e.g.][]{LightmanEardley1974} or interactions of embedded objects \citep[e.g.][]{McKernanetal2014,McKernanetal2018}.
+If an inhomogeneous disk is responsible for the continuum variations, which then drive \civ\ variations, it implies that our objects are simply the extreme outliers produced by a process which rarely but occasionally produces very large hot or cool spots.
+The frequency of such occurrences can be used to constrain the slope and normalization of the power law distribution of spot size.
+Finally, we must also consider the disk/wind model which has successfully reproduced many features of quasar \civ\ observations, notably the common blueshifted offset \citep[see e.g.,][]{Murrayetal1995}.
+In this model \civ is very optically thick at low velocities, but optically thin at high velocity, with $\tau \sim 1$ at $\sim 5000{\rm km/s}$.
+In a disk wind model, the broad line region is very small, implying short-timescales of variability in the lines.
+Also in this model, there should be associated strong absorption in the soft X-ray band, which can be tested with follow-up observations with Chandra.
 
-This indicates they may comfortably fit into the sample of \civ\ variable quasars explored by \citet{Dyer2019}, and similar to those authors we suggest slim accretion disk models e.g., \citet[][]{Abramowicz1988} or inhomogeneous disk models
-\citep[e.g.,][]{DexterAgol2011} may provide viable explanations for our observations.
-%% I want to say a bit more here about the generic probe of photoionisation vs shielding and conditions in the BL region but that will take more time.
+The foregoing discussion directly applies to the two objects which maintain an intrinsic Baldwin Effect relationship between \civ\ REW and continuum luminosity.
+However, J1638+2827 clearly does not maintain such a relationship--indeed the continuum and \civ\ REW are at least somewhat correlated, rather than anti-correlated in this source.
+This implies that the illumination of the \civ\ emitting region by a variable ionizing continuum and the corresponding change in the photoionisation state alone cannot explain the collapse and recovery of the line.
 
@@
 
-The X-ray Baldwin Effect \citep[e.g., ][]{Iwasawa_Taniguchi1993}...
+The X-ray Baldwin effect \citep[e.g., ][]{Iwasawa_Taniguchi1993}...
 \citet{Bachev2004} find a 10-fold decrease in EW \civ\ with Eddington ratio (decreasing from $\sim$1 to $\sim$0.01), while \nv shows no change.

### 2019-12-11 tex/CIV_CLQs.tex
arXiv SUBMITTEDclear

@@
 We report on three redshift $z>2$ quasars with dramatic changes in
-their \civ\ emission lines, the first ``Changing-Look'' quasars at
-high redshift.  This is also the first time the changing-look
-behaviour has been seen in a high-ionization emission line.  SDSS
-J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour in
-their observed optical light curves, and subsequent spectroscopy shows
-significant changes in the \civ\ broad emission line, with both line
-collapse and emergence being displayed in rest-frame timescales of
-$\sim$240-1640 days.  These are very quick changes, especially when
-considering virial black hole mass estimates have all three quasars
-with $M_{\rm BH} > 10^{9} M_{\odot}$.  Continuum and emission line
-measurements from the three quasars show changes in the
-continuum-equivalent width plane with the CLQs seen to be on the edge
-of the full population distribution, and showing indications of an
-intrinsic Baldwin Effect. We put these observations in context with
-recent ``state-change'' models, but note that even in their
-`low-state', the \civ\ CLQs are above $\sim$10\% in Eddington
+their \civ\ emission lines, the first sample of changing-look quasars
+(CLQs) at high redshift.  This is also the first time the
+changing-look behaviour has been seen in a high-ionisation emission
+line.  SDSS J1205+3422, J1638+2827, and J2228+2201 show interesting
+behaviour in their observed optical light curves, and subsequent
+spectroscopy shows significant changes in the \civ\ broad emission
+line, with both line collapse and emergence being displayed on
+rest-frame timescales of $\sim$240-1640 days.  These are rapid
+changes, especially when considering virial black hole mass estimates
+of $M_{\rm BH} > 10^{9} M_{\odot}$ for all three quasars.  Continuum
+and emission line measurements from the three quasars show changes in
+the continuum-equivalent width plane with the CLQs seen to be on the
+edge of the full population distribution, and showing indications of
+an intrinsic Baldwin effect. We put these observations in context with
+recent state-change models, and note that even in their observed
+low-state, the \civ\ CLQs are generally above $\sim$5\% in Eddington
 luminosity. 
@@
 \begin{keywords}
-accretion, accretion discs -- surveys -- quasars: general -- quasars: time-domain: 
+accretion, accretion discs -- surveys -- quasars: general -- quasars:
+time-domain -- quasars: individual (SDSS~J120544.7+342252.4,
+SDSS~J163852.9+28270.7.7, SDSS~J222818.7+220102.9)
 \end{keywords}
@@
 energy output on timescales as short as weeks to months.  This
-observation, and the subsequent mismatch in the expected ``viscous''
-timescale, which for a 10$^{7}$ M$_{\odot}$ central supermassive black
+observation, and the subsequent mismatch in the expected viscous
+timescale, which for a $10^{7} M_{\odot}$ central supermassive black
 hole (SMBH) is $\sim$hundreds of years, was noted over 30 years ago
@@
 of AGN accretion disk physics has recently re-invigorated the field
-\citep[e.g.][]{Antonucci2018, Lawrence2018, Ross2018, Stern2018}.
+\citep[e.g.,][]{Antonucci2018, Lawrence2018, Ross2018, Stern2018}.
 
-The optical continuum variability of quasars has been recognized since
-their first optical identification
-\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic changes
-in the broad emission lines (BELs) of quasars has only recently been
-identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
-``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
-have now been assembled \citep[e.g.][]{MacLeod2019, Graham2019b}. The
-community uses both these terms as a cover for the underlying
-physics. For sake of argument, CLQs can potentially be thought of as
-the extension to the BELs of quasar continuum variability \citep[e.g.,
-][]{MacLeod2012} whereas the CSQs have a `state-transition' similar to
-that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019a}. In
-this paper, we use the term `Changing Look', as we are currently
+The optical continuum variability of quasars was recognised since
+their first optical identifications
+\citep{MatthewsSandage1963}. %MacLeod2012}.  However, dramatic changes
+in the broad emission lines (BELs) of quasars was only recently first
+identified \citep{LaMassa2015}.  Samples of over 100 ``changing-look''
+quasars (CLQs) or ``changing-state'' quasars (CSQs) have now been
+assembled \citep[e.g.,][]{MacLeod2019, Graham2019b}. The community
+uses both these terms as a cover for the underlying physics. For sake
+of argument, CLQs can potentially be thought of as the extension to
+the BELs of quasar continuum variability \citep[e.g., ][]{MacLeod2012}
+whereas the CSQs have a state-transition, perhaps similar to that seen
+in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019a}. In
+this paper, we use the term ``changing-look'', as we are currently
 agnostic, and confessedly ignorant, to the underlying physical
@@
       \hline  \hline 
-      Line                 & $\lambda$ &  Transition  & Ionization   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
-                              &  / \AA\    & energy / eV &  energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & ($\times10^{8}$  / s$^{-1}$)               \\      \hline
+      Line                 & $\lambda$ &  Transition  & Ionisation   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
+                              &  / \AA\    & Energy / eV &  Energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & / $10^{8}$ s$^{-1}$               \\      \hline
       H LyLim           &   912.324   & 13.5984    & 13.5984        & 1$s$                    & $^2$S     & 1/2          & $\infty$                  &                                 &             & 109 678.7       & 1.23$\times10^{-6}$  \\
@@
       Strong UV/optical spectral emission lines in quasars, and their
-      atomic data.  Data from the NIST Atomic Spectra Database
-      \citep{Kramida2018, Kramida2019}.  The Transition Energies are
-      $E=hc/\lambda$ for the given wavelength. The Ionization Energy is the
-      energy required to ionize the given species, e.g. 64.49 eV are needed
-      to create a \cv\ ion.  Transitions Level configurations are given in
-      standard spectroscopic notation $A_{i,j}$ are transition
-      probabilities.  Data from the NIST Atomic Spectra Database
-      \citep{Kramida2018, Kramida2019}.}
+      atomic data from the NIST Atomic Spectra Database
+      \citep{Kramida2018, Kramida2019}.  The transition energies are
+      $E=hc/\lambda$ for the given wavelength. The ionisation energy is the
+      energy required to ionise the given species, e.g., 64.49 eV is needed
+      to create a \cv\ ion.  Transition level configurations are given in
+      standard spectroscopic notation, with $A_{i,j}$ denoting the transition
+      probabilities.}
     \label{tab:atomic_lines}
@@
 attention paid to the H$\beta$ emission line, observed from optical
-spectroscopy. Recent work report on discoveries of \mgii Changing-look
+spectroscopy. Recent works report on discoveries of \mgii\ changing-look
 AGN \citep{Guo2019, Homan2019}. However, current CLQ studies have
@@
 
-While there have been many studies on triply ionized carbon, i.e
+While there have been many studies on triply ionised carbon, i.e.,
 \civ, these have tended to focus on broad absorption line quasars
-\citep[BAL quasars; see Table 1 of][]{Hemler2019} or the Baldwin Effect
-\citep[BEff; ][]{Baldwin1977, Bian2012, Jensen2016,
+\citep[e.g., Table 1 of][]{Hemler2019} or the Baldwin effect
+\citep{Baldwin1977, Bian2012, Jensen2016,
 Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
-types of Baldwin effect are present in the literature: the {\it
-global} (or {\it ensemble}) Baldwin Effect, which is an
-anti-correlation between the Equivalent Width (EW) of the emission line and the
+types of Baldwin effect are present in the literature: {\it (i)} the {\it
+global} (or {\it ensemble}) Baldwin effect, which is an
+anti-correlation between the emission line equivalent width and the
 underlying continuum luminosity of {\it single-epoch} observations of
-a {\it large number} of AGN and second, the {\it intrinsic} Baldwin
+a {\it large number} of AGN, and {\it (ii)} the {\it intrinsic} Baldwin
 effect, the same anti-correlation but in an {\it individual, variable}
 AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
-collisionally excited broad {\it emission} line (BEL) of \civ\ and
-indeed \ciii have not to this point been reported.
+collisionally excited broad {\it emission} line of \civ\ --- and
+indeed \ciii\ --- have not to this point been reported.
 
@@
     \multirow{2}{*}{Object} & \multirow{2}{*}{Redshift} & $g$-band & \multirow{2}{*}{MJD} & \multirow{3}{*}{Instrument} & Exposure      &   SDSS               & \multirow{2}{*}{Notes} \\
-                                         &                                        &   (mag)      &                                 &                                             &  Time (secs) &   Plate-FiberID  & \\
+                                         &                                        &   / mag      &                                 &                                             &  time / sec &   Plate-FiberID  & \\
     \hline  
-                                       & 2.068                              & 18.27          &  53498                   & SDSS                                     &  8057            & 2089-427             & \\
- J120544.7+342252.4     & 2.071                             &                    &  58538                   & DBSP                                     &  1800            &  ---                      &  Average conditions \\
-                                       & 2.071                             &                     &  58693                  & DBSP                                      &  2400            &  ---                      &          \\
+                                       & 2.068                              & 18.27          &  53498                   & SDSS                                     &  8057            & 2089-427             & Plate quality marginal \\
+ J120544.7+342252.4     & 2.071                             &                    &  58538                   & DBSP                                     &  1800            &  ---                      &  Poor conditions \\
+                                       & 2.071                             &                     &  58693                  & DBSP                                      &  2400            &  ---                      &  Good conditions        \\
                                        &                                       &                     &                               &                                              &                      &                               &                               \\
-                                      & 2.185                              & 19.77           &  54553                   & SDSS                                     &   4801            &  2948-614              & \\
-J163852.9+282707.7     & 2.186                              &                    &  55832                     & BOSS                                    &   3600            &  5201-178            & \\
+                                      & 2.185                              & 19.77           &  54553                   & SDSS                                     &   4801            &  2948-614              & Plate quality good \\
+J163852.9+282707.7     & 2.186                              &                    &  55832                     & BOSS                                    &   3600            &  5201-178            & Plate quality good \\
                                       & 2.182                              &                     &  58583                     & LRIS                                    &  1800              &  ---                      & \\
                                       &                                         &                    &                                 &                                            &                      &                              &                                 \\
-                                      & 2.217                               & 19.97          &  56189                    &  BOSS                                    &  2700            &   6118-720          & \\
- J222818.7+220102.9   & 2.222                               &                    &  56960                     & BOSS                                    &  4500            &   7582-790          & eBOSS reobservation \\
+                                      & 2.217                               & 19.97          &  56189                    &  BOSS                                    &  2700            &   6118-720          & Plate quality good \\
+ J222818.7+220102.9   & 2.222                               &                    &  56960                     & eBOSS                                    &  4500            &   7582-790          & Plate quality good \\
                                      &  2.222                               &                    &  58693                    &  DBSP                                    & 2400             &    ---                        &    \\
@@
   \caption{Details of our spectroscopic observations.  Redshift errors are
-    typically $\pm$0.002.  SDSS, BOSS and eBOSS spectra have
-    $\mathcal{R}\sim$2,000.  DBSP: Double Spectrograph on the Palomar
-    200-inch telescope.  LRIS: Low Resolution Imaging Spectrometer on Keck
-    I 10m telescope.} 
+    typically $\pm 0.002$.  SDSS, BOSS, and eBOSS spectra have
+    resolving power $\mathcal{R} \equiv \lambda / \Delta \lambda \sim 2000$.  DBSP: Double Spectrograph on the Palomar
+    200-inch Hale telescope.  LRIS: Low Resolution Imaging Spectrometer on Keck
+    I 10-m telescope.} 
   \label{tab:obs_notes}
@@
 Here, we present new results for three quasars which show dramatic
-changes in their \civ\ and \ciii broad emission line properties as
-well as in their underlying continuum. These are some of the first
-examples of ``Changing Look Quasars'' at high ($z>1$)
-redshift. Moreover, these are the first cases for substantial changes
-of ions with high ionization potentials (I.P.'s $>$2 Rydberg), thus
-linking the ionizing photons to the energetic inner accretion disk,
-potentially by inverse Compton scattering of lower energy photons to
-higher energies.
+changes in their \civ\ and \ciii\ broad emission line properties and
+underlying continuum. These are some of the first examples of CLQs at
+high ($z>1$) redshift. Moreover, these are the first cases for
+substantial changes of ions with high ionisation potentials (I.P.'s
+$>$2 Rydberg), thus linking the ionizing photons to the energetic
+inner accretion disk.
 
@@
 \citep{Kramida2018}. For ionisation energies, 47.89 eV (3.519 Ry) is
-required for doubly-ionised C~III to become triply-ionised \civ.
-64.49 eV (4.74 Ry) is the energy needed to ionize \civ\ itself. This
+required for doubly-ionised C\,{\sc iii} to become triply-ionised
+\civ, and 64.49 eV (4.74 Ry) is needed to ionise \civ\ itself. This
 energy corresponds to a thermal temperature of $T \gtrsim$
-4$\times10^{5}$, implying a heating energy source of (soft) X-ray
+4$\times10^{5}$ K, implying a heating energy source of (soft) X-ray
 photons.
 
-\citet{Wilhite2006} examine \civ\ variability in a sample
-of 105 quasars observed at multiple epochs by the Sloan Digital Sky
-Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
-find a strong correlation between the change in the \civ\ line
-flux and the change in the line width, but no correlations between the
-change in flux and changes in line center and skewness.  These authors
-find that the relation between line flux change and line width change
-is consistent with a model in which a broad line base varies with
-greater amplitude than the line core. The \civ\ lines in these
-high-luminosity quasars appear to be less responsive to continuum
-variations than those in lower luminosity AGN.
+\citet{Wilhite2006} examine \civ\ variability in a sample of 105
+quasars observed at multiple epochs by the Sloan Digital Sky Survey
+\citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They find a
+strong correlation between the change in the \civ\ line flux and the
+change in the line width, but no correlations between the change in
+flux and changes in line center or skewness.  These authors find that
+the relation between line flux change and line width change is
+consistent with a model in which a broad line base varies with greater
+amplitude than the line core. The \civ\ lines in these high-luminosity
+quasars appear to be less responsive to continuum variations than
+those in lower luminosity AGN.
 
-\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$
-SDSS quasars, concentrating on the properties of the \civ\ emission
-line. These authors consider two well-known effects involving the
-\civ\ emission line: {\it (i)} the anti-correlation between the \civ\
-equivalent widths (EWs) and luminosity (i.e., the Baldwin Effect;
-BEff) and {\it (ii)} the blueshifting of the peak of \civ\ emission
-with respect to the systemic redshift.  We denote the velocity offset
-of emission lines as $V_{\rm off}$ and use the convention that a
-positive $V_{\rm off}$ value means the line is blueshifted while a
-negative $V_{\rm off}$ value means the line is redshifted.
-\citet{Richards2011} find the blueshift of the \civ\ emission line, is
-found to be nearly ubiquitous, with a mean shift of $V_{\rm off}
-\sim$810 km s$^{-1}$ for radio-quiet (RQ) quasars and $V_{\rm off}
-\sim$360 km s$^{-1}$ for radio-loud (RL) objects. \citet{Richards2011}
-also find the BEff is present in both the RQ and RL studied samples.
-These author conclude that these two \civ\ parameters (EQW and
-blueshift) are capturing an important trade-off between ``disk'' and
-``wind'' components in the disk-wind model of accretion disks
-\citep[e.g.,][]{Murray1995, Elvis2000, Proga2000, Leighly2004b}, with
-one dominating over the other depending on the shape of the SED.
+\citet{Richards2011} explored the broad emission line region in over
+30,000 $z > 1.54$ SDSS quasars, concentrating on the properties of the
+\civ\ emission line. These authors consider two well-known effects
+involving the \civ\ emission line: {\it (i)} the anti-correlation
+between the \civ\ equivalent width (EW) and luminosity (i.e., the
+Baldwin effect) and {\it (ii)} the blueshifting of the peak of \civ\
+emission with respect to the systemic redshift.  We denote the
+velocity offset of emission lines as $V_{\rm off}$ and use the
+convention that a positive $V_{\rm off}$ value means the line is
+blueshifted while a negative $V_{\rm off}$ value means the line is
+redshifted.  \citet{Richards2011} find a blueshift of the \civ\
+emission line is nearly ubiquitous, with a mean shift of $\langle
+V_{\rm off}\rangle_{\rm RQ} \sim$810 km s$^{-1}$ for radio-quiet (RQ)
+quasars and $\langle V_{\rm off}\rangle_{\rm RL} \sim$360 km s$^{-1}$
+for radio-loud (RL) objects. \citet{Richards2011} also find the
+Baldwin effect is present in both their RQ sample and their RL sample.
+They conclude that these two \civ\ parameters (EW and blueshift) are
+capturing an important trade-off between disk and wind components in
+the disk-wind model of accretion disks \citep[e.g.,][]{Murray1995,
+Elvis2000, Proga2000, Leighly2004b}, with one dominating over the
+other depending on the shape of the quasar spectral energy
+distribution (SED).
 
-Using the multi-epoch spectra of 362 quasars from the Sloan Digital
-Sky Survey Reverberation Mapping \citep[SDSS-RM; ][]{Shen2015,
-Shen2019} project, \citet{Sun2018} investigate the blueshift of \civ\
-emission relative to \mgii emission, and its dependence on quasar
-properties. These authors confirm that high-blueshift sources tend to
-have low \civ\ EWs, and that the low-EW sources span a range of
-blueshift. Other high-ionization lines, such as \heii, also show
-similar blueshift properties. The ratio of the line width of \civ\ to
-that of \mgii increases with blueshift. \citet{Sun2018} also find that
-quasar variability might slightly enhance the connection between the
-\civ\ blueshift and EW, though further investigation here is
-warranted. There is also the finding that the objects with that
-largest blueshifts are less variable and tend to have higher Eddington
-ratios. \citet{Sun2018} explain their results these by suggesting that
-quasar SEDs have weaker X-ray emission (or at least a larger UV/optical-to-Xray
-spectral index, $\alpha_{\rm ox}$) and thus become {\it
-softer} with {\it increasing Eddington ratio} along with the presence
-of X-ray shielding by the inner accretion disk. However, a high
-Eddington ratio alone might be an insufficient condition for the \civ\
-blueshift. Recent investigations also include \citet{Meyer2019} and
+Using the multi-epoch spectra of 362 quasars from the SDSS
+Reverberation Mapping project \citep[SDSS-RM; ][]{Shen2015, Shen2019},
+\citet{Sun2018} investigate the blueshift of \civ\ emission relative
+to \mgii\ emission, and its dependence on quasar properties. They
+confirm that high-blueshift sources tend to have low \civ\ EWs, and
+that the low-EW sources span a range of blueshift. Other
+high-ionisation lines, such as \heii, also show similar blueshift
+properties. The ratio of the line width of \civ\ to that of \mgii\
+increases with blueshift. \citet{Sun2018} also find that quasar
+variability might slightly enhance the connection between the \civ\
+blueshift and EW, though further investigation here is warranted. They
+also find that quasars with the largest blueshifts are less variable
+and tend to have higher Eddington ratios, though Eddington ratio alone
+might be an insufficient condition for the \civ\ blueshift. Recent
+investigations also include \citet{Meyer2019} and
 \citet{Doan2019}. \citet{Dyer2019} provide a detailed analysis of 340
-quasars at high-redshift ($1.62<z<3.30$) from the SDSS-RM project,
-which we will compare our results to.
+quasars at high redshift ($1.62<z<3.30$) from the SDSS-RM project,
+which we compare with our results in Section~\ref{sec:theory}.
 
@@
 redshift. While accessing this phenomenon at an earlier cosmic epoch
-is somewhat interesting, the main value of this study is we move from
-the low-ionization energy Balmer emission line series to the
-high-ionization emission lines, in particular \civ\ $\lambda$1549.
+is somewhat interesting, the main value of this study is to move from
+the low-ionisation energy Balmer emission line series at rest-frame
+optical wavelengths to the high-ionisation emission lines, in
+particular \civ\ $\lambda$1549, at rest-frame UV wavelengths.
 
 This paper is organised as follows. In Section 2, we describe our
-sample selection, catalogues, and observational data sets.  In Section
-3, we show the high-$z$ quasars and report the line properties for the
-quasars at the observed epochs.  We give a very brief theoretical
-discussion in Section 4. We present our conclusions in Section 5.  We
-report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
-Fukugita1996} unless otherwise stated. For the WISE bands, $m_{\rm AB}
-= m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1 at
-3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011,
-Cutri2013}. We adopt a flat $\Lambda$CDM cosmology with
-$\Omega_{\Lambda} = 0.73 $, $\Omega_{\rm M} = 0.27$, and $h =
-0.71$. All logarithms are to the base 10.
+sample selection, catalogues, and observational data sets.  Section 3
+presents the high-redshift quasars and reports their time-variable
+line properties.  We provide a brief theoretical discussion in Section
+4, and Section~5 presents our conclusions.  We report all magnitudes
+on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996} unless
+otherwise stated. For the {\it WISE} bands, $m_{\rm AB} = m_{\rm Vega}
++ m$ where $m = 2.699$ and 3.339 for {\it WISE} W1 (3.4$\mu$m) and W2
+(4.6$\mu$m), respectively \citep{Cutri2011, Cutri2013}. We adopt a
+flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73 $,
+$\Omega_{\rm M} = 0.27$, and $h = 0.71$. All logarithms are to the
+base 10.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data, CLQ Selection and Line measurements}
+\section{CLQ Selection and Line Measurements}
 In this section we present the photometric data used to select the
@@
 Telescope and Rapid Response System \citep[PanSTARRS;][]{Kaiser2010,
-Stubbs2010, Tonry2012, Magnier2013} and the Zwicky Transient Facility
+Stubbs2010, Tonry2012, Magnier2013}, and the Zwicky Transient Facility
 \citep[ZTF;][]{Bellm2019_ZTFOverview}.
@@
 The CRTS archive\footnote{http://catalinadata.org} contains the
-Catalina Sky Survey data streams from three telescopes -- the 0.7 m
-Catalina Sky Survey (CSS) Schmidt and 1.5 m Mount Lemmon Survey (MLS)
-telescopes in Arizona and the 0.5 m Siding Springs Survey (SSS)
+Catalina Sky Survey data streams from three telescopes -- the 0.7-m
+Catalina Sky Survey (CSS) Schmidt and 1.5-m Mount Lemmon Survey (MLS)
+telescopes in Arizona, and the 0.5-m Siding Springs Survey (SSS)
 Schmidt in Australia. CRTS covers up to $\sim$2500 deg$^2$ per night,
-with 4 exposures per visit, separated by 10 min. The survey observes
+with four exposures per visit, separated by 10 min. The survey observes
 over 21 nights per lunation. The data are broadly calibrated to
-Johnson $V$ \citep[see ][for details]{Drake2013} and the current CRTS
+Johnson $V$ \citep[for details, see][]{Drake2013} and the current CRTS
 data set contains time series for approximately 400 million sources to
@@
 and MLS) and 100 million sources to $V \sim 19$ in the southern sky
-from 2005 to 2013 (from SSS). CRTS has been used to study distant
-quasars previously \citep{Graham2014, Graham2015, Graham2015Nature,
-Graham2017, Graham2019b}.
+from 2005 to 2013 (from SSS). CRTS has been extensively used to study 
+quasar variability \citep[e.g.,][]{Graham2014, Graham2015, Graham2015Nature,
+Graham2017, Graham2019b, Stern2017, Stern2018, Ross2018}.
 
@@
 
-The ZTF is a new robotic time-domain sky survey capable of visiting
-the entire visible sky north of -30 deg. declination every night. ZTF
-observes the sky in the $g$, $r$, and $i$-bands at different cadences
-depending on the scientific program and sky region
-\citep{Bellm2019_ZTFSurveys, Graham2019_ZTF}. The ZTF 576 megapixel
-camera with a 47 deg$^{2}$ field of view, installed on the Samuel
-Oschin 48-inch Schmidt Telescope, can scan more than 3750 deg$^{2}$
+The Zwicky Transient Facility (ZTF; http://ztf.caltech.edu) is a new
+robotic time-domain sky survey capable of visiting the entire visible
+sky north of $-$30 declination every night. ZTF observes the sky in
+the $g$, $r$, and $i$-bands at different cadences depending on the
+scientific program and sky region \citep{Bellm2019_ZTFSurveys,
+Graham2019_ZTF}. The ZTF 576 megapixel camera with a 47 deg$^{2}$
+field of view, installed on the Samuel Oschin 48-inch Schmidt
+telescope at Palomar observatory, can scan more than 3750 deg$^{2}$
 per hour, to a 5$\sigma$ detection limit of 20.7 mag in the $r$-band
-with a 30sec exposure during new moon \citep{Masci2019}.
+with a 30-sec exposure during new moon \citep{Masci2019}.
 \begin{figure*}
@@
   \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
-  {figures/J1205+3422_landscape_20191112.png}
+  {figures/J1205+3422_landscape_20191211.png}
   \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
@@
   \vspace{-12pt}
-  \caption[]{The three high-$z$ CLQ quasars; 
+  \caption[]{The three high-redshift CLQ quasars; 
     J1205+3422 (top), 
@@
     J2228+2201 (bottom). 
-    The light curve data is present in the panels on the left hand side, with the 
-    spectral epoch observational timings indicated by vertical lines. 
+    The light curve data are presented in the panels on the left hand side, with the timing of the
+    spectral observations indicated with vertical dashed lines. 
     The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
-    complex, the \civ\ line, and the \mgii line.}
+    complex, the \civ\ line, and the \mgii\ line.}
   \label{fig:civ_clqs}
@@
 
-\subsection{Multi-Wavelength Properties}
-{\bf DS to write something on FIRST non-detections; possibly check the X-rays too?} \\
+\subsubsection{Mid-Infrared Photometry}
 Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning
-of the {\it Wide-field Infrared Survey Explorer} ({\it WISE}) mission
-\citep[2010 January; ][]{Wright2010} through the fifth-year of {\it
-NEOWISE-R} operations \citep[2018 December; ][]{Mainzer2011}. The {\it
-WISE}WISE scan pattern leads to coverage of the full-sky approximately
-once every six months (a ``sky pass''), but the satellite was placed
-in hibernation in 2011 February and then reactivated in 2013
-October. Hence, our light curves have a cadence of 6 months with a
-32-month sampling gap.
+of the {\it WISE} mission \citep[2010 January; ][]{Wright2010} through
+the fifth-year of {\it NEOWISE-R} operations \citep[2018 December;
+][]{Mainzer2011}. The {\it WISE} scan pattern leads to coverage of the
+full-sky approximately once every six months (a ``sky pass''), albeit
+it with a gab between 2011 February and 2013 October when the
+satellite was placed in hibernation. Hence, our light curves have a
+cadence of 6 months with a 32-month sampling gap.
 
 \subsection{CLQ Selection}
-{\bf MJG to finalise this} \\
-Our high-$z$ CLQs were identified as follows.  We selected all 64,774
-SDSS DR15 sources with $z > 0.35$ classified as `quasar', having at least
-two spectra separated by at least 100 days, and with a corresponding
-CRTS light curve. We fitted a damped random walk to the CRTS data via
-Gaussian process regression and the photometric magnitudes at the
-epochs of the SDSS spectra for a given source are predicted. Those
-where $|\Delta V| > 0.3$ are then selected for visual
-inspection. Only three quasars SDSS J120544.7+342252.4 (hereafter
-J1205+3422), SDSS J163852.93+282707.7 (hereafter J1638+2827) and SDSS
-J222818.76+220102.9 (hereafter J2228+2201), satisfied these selection
-criteria and showed interesting or dramatic emission line behaviour.
+Our high-redshift CLQs were identified as follows.  We selected all
+64,774 SDSS DR15 sources with $z > 0.35$ classified as `quasar', that
+had at least two spectra separated by $\geq 100$ days, and that had a
+corresponding CRTS light curve. We fitted a damped random walk to the
+CRTS data via Gaussian process regression (using the
+\href{https://gpy.readthedocs.io/en/deploy/}{GPy Python} library).
+This allowed us to predict the photometric magnitudes at the epochs of
+the SDSS spectra for each source.  Those with $|\Delta V| > 0.3$ were
+then selected for visual inspection, looking for at least a 50\%
+change in magnitude between the two epochs.  Only three quasars, SDSS
+J120544.7+342252.4 (hereafter J1205+3422), SDSS J163852.93+282707.7
+(hereafter J1638+2827) and SDSS J222818.76+220102.9 (hereafter
+J2228+2201), satisfied these selection criteria and showed interesting
+or dramatic emission line behaviour.
 
-%% From Section 3.1; Placed here to help with overall formatting of the paper
+%% From Section 3.1.
+%% Placed here to help with overall formatting of the paper
 \input{QSFit-results}
@@
 An overview of our spectroscopic observations is given in
-Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
+Table~\ref{tab:obs_notes}.  The archival spectra are from the SDSS
 \citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
@@
 Abolfathi2018, Paris2018}.  These quasars were targetted via a range
-of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
+of techniques and algorithms \citep[see][]{Richards2002, Ross2012,
 Myers2015}. The SDSS, BOSS, and eBOSS data are supplemented by spectra
 from the Low Resolution Imaging Spectrometer \citep[LRIS; ][]{Oke1995}
-on the 10m Keck {\sc I} telescope.  and the Double Spectrograph (DBSP)
-instrument on the 200'' Palomar telescope.
+on the 10-m Keck {\sc I} telescope and the Double Spectrograph (DBSP)
+instrument on the 200-inch Palomar Hale telescope.
 
-\subsubsection{Spectrophotometry}
-{\bf MJG to check/finalise} \\
-We want all our spectra to have reliable flux calibrations.  SDSS
-spectra ae spectrophotometrically calibrated.  BOSS and eBOSS spectra
-have spectrophotometric corrections applied in the latest data release
-\citep{Hutchinson2016, Jensen2016, Margala2016}.  Due to the high-$z$
-of our objects, \oiii is not available to us to use as a calibrating
-flux line. Instead we use photometric data from the ZTF since all our
-non-SDSS/BOSS/eBOSS data are taken after MJD 57500.
+Proper comparison of the spectra requires reliable flux calibrations,
+which is a challenge since not all data were taken in photometric
+conditions.  SDSS spectra are spectrophotometrically calibrated.  BOSS
+and eBOSS spectra have spectrophotometric corrections applied in the
+latest data release \citep{Hutchinson2016, Jensen2016, Margala2016}.
+However, some of the Palomar and Keck data suffered from variable
+conditions and clouds.  For lower redshift AGN, the narrow \oiii
+emission line is typically used to align spectrophotometry since it is
+spatially extended and not expected to change significantly on human
+timescales \citep[e.g.,][]{Barth2011}. However, due to the
+high-redshift of our quasars, \oiii is not available to us to use for
+scaling the spectra.  Instead, we use photometric data from ZTF since
+our Palomar and Keck data were all taken after MJD 57500.  This
+provides broad-band photometry at the time of the spectroscopy, which
+we use to scale the spectra whose initial calibration is based on
+spectrophotometric standards observed on the same nights.
 
@@
 
-In particular we use the Quasar Spectral Fitting (QSFit) software
+In particular, we use the Quasar Spectral Fitting (QSFit) software
 package presented in \citet{Calderone2017}. This provides luminosity
-estimates as well as width, velocity offset and equivalent width of 20
-emission lines, including \civ, \ciii and \mgii.  We process and fit
-all nine spectra using the lastest version (v1.3.0) of the QSFit
+estimates as well as width, velocity offset and EW of 20 emission
+lines, including \civ, \ciii, and \mgii.  We process and fit all nine
+spectra using the lastest version (v1.3.0) of the QSFit
 \href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
@@
 optical wavelengths components are automatically disabled when they
-can not be constrained by the available data, such as the case for all
-our objects (we do not have infrared spectral data).  Power-law
-continuum slopes, $\alpha$, where $f_{\lambda} \propto
-\lambda^{\alpha}$, are also reported in these catalogues and from
-QSFit.
+can not be constrained by the available data, as is the case for all
+our quasars.  Power-law continuum slopes, $\alpha$, where $f_{\lambda}
+\propto \lambda^{\alpha}$, are also reported in these catalogues and
+from QSFit.
 
@@
 \section{Results}
-\subsection{Photometric and Overal Spectral Evolution}
-Figure~\ref{fig:civ_clqs} presents the optical and mid-IR light
-curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
-shows the spectra for each epoch, with the MJD of observation given by
-the dashed vertical lines in the light curves.
+\subsection{Photometric and Overall Spectral Evolution}
+Figure~\ref{fig:civ_clqs} presents the optical and mid-infrared light
+curves for three high-redshift CLQ quasars.  Figure~\ref{fig:civ_clqs}
+also indicates the spectra for each epoch with vertical dashed lines
+in the light curves.
 
-For J1205+3422, our spectral observations cover 5195 days observed,
-1691 days in the rest-frame. This quasar was initially identified in
-SDSS in 2005 May, as a bright, $g\approx18.0$, blue-sloped quasar with
-broad Si\,{\sc iv}, \civ, \ciii and Mg\,{\sc ii}. \ciii and \civ\ have large
-blueshifts of $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km
-s$^{-1}$, respectively.  By 2019, however, the optical brightness
-dropped by $\sim$1.5 magnitudes and the spectra are significantly less
-blue.  While \lya and \nv are detectable in both 2019 spectra, \civ\
-has all but disappeared in the 2019 June spectrum.  The broad \ciii
-emission has disappeared between the 2005 and 2019 spectra. The
-changes in \civ\ and \ciii going from broad emission to barely
-detectable have on the timescales of $\approx$50 days in the
-rest-frame.
+For J1205+3422, our spectral observations cover 5195 observed days,
+corresponding to 1691 days in the rest-frame. This quasar was
+initially identified in SDSS in 2005 May as a bright, $g \approx
+18.0$, blue-sloped quasar with broad Si\,{\sc iv}/O\,{\sc iv}, \civ,
+\ciii, and \mgii. \ciii\ and \civ\ have large blueshifts,
+$\approx$2600$\pm$150 and $\approx$1150$\pm$100 km s$^{-1}$,
+respectively.  By 2019, however, the optical brightness dropped by
+nearly 2 magnitudes and the spectra are significantly less blue.  \lya
+and \nv are detectable in both 2019 spectra, but is just blueward of
+the wavelength range covered by the original SDSS spectrum. The \civ\
+and \ciii\ lines have faded significantly between the SDSS observation
+in 2005 and the Palomar observations in 2019.  Note that \civ\ is
+extremely faint in the 2019 February spectrum, but that night suffered
+from poor conditions.
 
-For J1638+2827, our spectral observations cover 4030 days observed,
-1265 days in the rest-frame. Here, in the initial epoch spectrum,
-\civ\ is broad and bright, as is C\,{\sc iii}. However, $\approx$400
-rest-frame days later, the broad \civ\ and \ciii BEL have faded, the
-continuum slope around 1400\AA\ has changed from $\approx-1.48$ to
-$\approx-2.25$, but the \lya/\nv emission complex is very similar in
-shape and line flux intensity. Around 870 days in the rest-frame after
-the second spectral epoch, Ly$\alpha$, N\,{\sc v}, \civ, C\,{\sc iii}] and \mgii are all
-apparent and broad, with \mgii being seen for the first time at high
-signal-to-noise. The light curve is consistent with this spectral
-brightening, increasing from $\sim$20th magnitude to $\sim$18.5th 
-magnitude at optical wavelengths. An absorption feature between \lya
-and \nv is seen in all three spectral epochs.
+For J1638+2827, our spectral observations cover 4030 observed days,
+corresponding to 1265 days in the rest-frame. Here, in the initial
+epoch spectrum, \civ\ is broad and bright, as is \ciii. However,
+$\approx$400 rest-frame days later, the broad \civ\ and \ciii\
+emission lines have faded, the continuum slope around 1400\AA\ has
+changed from $\approx-1.48$ to $\approx-2.25$, but the \lya/\nv
+emission complex is very similar in shape and line flux
+intensity. Around 870 days in the rest-frame after the second spectral
+epoch, at the time of the third spectral epoch, the source has
+brightened from optical magnitudes of $\sim 20$ mag to $\sim 18.5$
+mag. Ly$\alpha$, N\,{\sc v}, \civ, \ciii, and \mgii\ are all apparent
+and broad, with \mgii\ being seen for the first time at high
+signal-to-noise. An absorption feature between \lya and \nv is seen in
+all three spectral epochs.
 
-For J2228+2201, our spectral observations cover 2504 days observed,
-778 days in the rest-frame. Over the course of 240 rest-frame days,
-\civ\ and \ciii both {\it emerge} as BELs and the standard UV/blue
-continuum slope increases in flux.  Then, over the course of 538 days
-in the rest-frame, the broadline emission, while still very present,
-reduces in line flux the UV/blue continuum diminishes, though is still
-more luminous than the initial BOSS spectrum.
+For J2228+2201, our spectral observations cover 2504 observed days,
+corresponding to 778 days in the rest-frame. Over the course of 240
+rest-frame days, \civ\ and \ciii\ both {\it emerge} as BELs and the
+standard UV/blue continuum slope increases in flux.  Then, over the
+course of 538 days in the rest-frame, the broad emission, while still
+very present, reduces in line flux the UV/blue continuum diminishes.
+However, the third epoch still corresponds to a source more luminous
+than the initial BOSS spectrum.
 
-%% trim={<left> <lower> <right> <upper>}
 \begin{figure}
@@
     \vspace{-18pt}
-  \caption{Observed spectra and best fit model in the region relevant
-    to \civ\ emission line for the quasars considered here.
-    The solid blue line is the Lorentzian profile fit the to the \civ\ emission line.
+  \caption{Observed spectra and best fit models of the \civ\ spectral region.
+    The solid blue line is the Lorentzian profile fit to the \civ\ emission line.
     The long-dashed red line is the continuum fit, with the solid orange
@@
 \end{figure}
+
 \subsection{\civ\ Emission Line Evolution}
-We analyzed the spectra of the three quasars, at all observational
-epochs, using the QSFit spectral fitting package
-\citep{Calderone2017}.  One advantage of using QSFit is that it allows
-constraints on the slope and luminosity of the broad band continuum of
-the source. The relevant estimated quantities, including continuum
-luminosity and slope at rest-frame 1450\AA, \civ\ line luminosity,
-FWHM and EW are given in Table~\ref{tab:QSFit-results}. All fits are
-performed with $E(B-V) = 0$ and the best fit model in the region of
-the \civ\ emission line are shown in Figure~\ref{fig:QSFit-CIV}.
+We analyzed the multi-epoch spectra of the three quasars using the
+QSFit spectral fitting package \citep{Calderone2017}.  One advantage
+of using QSFit is that it allows constraints on the slope and
+luminosity of the broad band continuum of the source. The relevant
+estimated quantities, including continuum luminosity and slope at
+rest-frame 1450\AA, \civ\ line luminosity, FWHM, and EW are given in
+Table~\ref{tab:QSFit-results}. All fits are performed with $E(B-V) =
+0$ and the best fit models in the region of the \civ\ emission line
+are shown in Figure~\ref{fig:QSFit-CIV}.
 
 All \civ\ lines are fitted with a single, broad, Lorentzian profile.
-This allows us to account for the narrow peak of the \civ\ line.  No
-narrow components are considered for several reasons: in the epochs of
-highest brightness the ``narrow'' component would have FWHM~$\sim2-3
-\times 10^{3}$~km~s$^{-1}$, i.e. values exceeding the usual widths of
-genuine narrow lines ($\lesssim$10$^{3}$ km s$^{-1}$); by allowing a
-second component, to have such large widths their parameters would
-become highly degenerate with the ``broad'' components, and the latter
-would also have much larger FWHM ($\sim$$10^{4}$ km s$^{-1}$); and by
-neglecting the narrow components we have a consistent fit across all
-epochs.
+This allows us to account for the central peak of the \civ\ line.  No
+additional narrow components are considered for several reasons.
+First, in the epochs of highest brightness, such a ``narrow''
+component would have FWHM $\sim$ 2000-3000~km~s$^{-1}$, i.e. values
+exceeding the usual widths of genuine narrow lines ($\lesssim
+1000$~km~s$^{-1}$). Second, allowing a second component to have such
+large widths would make that component highly degenerate with the
+``broad'' components, causing the latter to have much larger widths,
+$\sim 10,000$~km~s$^{-1}$.  Finally, neglecting such a narrow
+component ensures a consistent model across all epochs.
 
-The quasar continuum, evaluated at 1450\AA\ , and the \civ\ line
+Both the quasar continuum (evaluated at 1450\AA), and the \civ\ line
 luminosities follow a similar evolution, with a ratio of $\sim$20-30,
@@
 may be a bias due to the limited wavelength range available which
-extends to $\lambda \sim 1240$\AA\ for the first epoch, while it extend
-to shorter wavelengths for the other epochs (respectively 1140\AA\ and
-1010\AA).  The latter suggests that the ``emerging'' component is more
-prominent at UV wavelengths, and a sufficient wavelength coverage is
-required to detect it. We find there is no need for a narrow component
-in J2228+2201 MJD 56189.  This is because the data resemble a P-Cygni
-profile, with blueshifted absorption. This feature is very narrow, and
-the uncertainties large, such that the overall $\chi^{2}$ is only
-marginally affected by the addition of a further component. We
-therefore avoid using a narrow component for this spectrum only, since
-that would be inconsistent with the other analyses.
-In all cases where the \civ\ line profile is reliably constrained the
-\civ\ FWHM is approximately constant, with maximum variations
-$\lesssim$~1000 km s$^{-1}$, despite the significantly larger
-variations in the line luminosities.
+extends to rest-frame $\lambda \sim 1240$~\AA\ for the first epoch,
+while it extend to shorter wavelengths for the other epochs
+(respectively ~\AA\ and 1010~\AA).  This suggests that the emerging
+component is more prominent at UV wavelengths, and a sufficient
+wavelength coverage is required to detect it. In all cases where the
+\civ\ line profile is reliably constrained, we find that the \civ\
+FWHM is approximately constant with maximum variations $\lesssim 1000$
+km s$^{-1}$, despite significantly larger line luminosity variations.
 
@@
   \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_MBHvsREW_QSFit20K.png}
+  {figures/CIV_CLQs_MBHvsREW_20191211.png}
    \vspace{-12pt}
-   \caption[]{The virial black hole masses of $\approx$20,000 $z>1.5$ quasars
-     from QSFit catalogue \citep{Calderone2017} and the \civ\
-     Equivalent widths.  Different quasars are given different colours:
-     J1205+3422 purple; J1638+2827 green; J2228+2201 is blue.  Different
-     epochs different symbols: first epoch circles; second epoch squares;
-     third epoch diamonds.  As noted in Table~\ref{tab:QSFit-results},
-     $^{*}$ signifies the \civ\ line is very weak and the associated
-     estimates are likely unreliable.}
+   \caption[]{
+     Colored density cloud shows virial black hole masses of
+     $\approx$20,000 $z>1.5$ quasars from QSFit catalogue
+     \citep{Calderone2017} compared to their \civ\ rest-frame equivalent
+     widths (REWs).  Overplotted are the three high-redshift CLQs
+     considered here: J1205+3422 (magenta), J1638+2827 (green), and
+     J2228+2201 (cyan).  The symbol shapes indicate the observation epoch,
+     with the first, second, and third epochs denoted by circles, squares,
+     and diamonds, respectively. As per Table~\ref{tab:QSFit-results}, an
+     asterisk in the inset box signifies that the \civ\ line for that
+     quasar observation is very weak, likely making the associated
+     estimates unreliable.}
    \label{fig:CIV_MBHvsREW}
 \end{figure}
-\subsection{Virial Black Hole Masses}\label{sec:BH_masses} 
-The FWHM of broad lines is likely related to the mass of the
-supermassive black hole powering the quasar phenomenon, which is
-assumed to be constant on any human timescale.  Hence it is
-instructive to check whether the virial product, which is the basic
-quantity used to calculate the single epoch black hole mass estimate,
-show any variation.
 
-Using the estimates for the continuum luminosity and FWHW from the
-single-epoch spectra, one can estimate the central black hole mass
-\citep[e.g.][]{Shen2011, Calderone2017}.  This approach assumes that
-the broad-line region (BLR) is virialized, the continuum luminosity is
-used as a proxy for the BLR radius, and the broad line width (FWHM) is
-used as a proxy for the virial velocity.  This ``virial mass''
-estimate can then be expressed as:
+\subsection{Virial Black Hole Masses}
+\label{sec:BH_masses} 
+The FWHMs of quasar broad lines are related to the mass of the SMBH
+powering the quasar phenomenon, and that mass is assumed to be
+constant on any human timescale.  Hence it is instructive to check
+whether the virial products, which are the basic quantity used to
+calculate single-epoch black hole mass estimates, show any
+variation. This approach assumes that the broad-line region (BLR) is
+virialized \citep[e.g.][]{Shen2011, Calderone2017}. The continuum
+luminosity provides a proxy for the BLR radius, and the broad-line
+width (FWHM) provides a proxy for the virial velocity.  This ``virial
+mass'' estimate is then expressed as:
 \begin{equation}
@@
 where $\gamma=0.5$ and $\delta=2$.  The virial product for the \civ\
-CLQs is reported in the last column of Tab.~\ref{tab:QSFit-results}. 
-The uncertainty typically associated to the single epoch mass estimate
-is $\sim$0.5 dex, hence the virial product at all epochs are
-remarkably constant and compatible with a single value of black hole
-mass for each source, even in those cases where the \civ\ estimates
-are possibly unreliable. The object showing larger variation is
-J2228+2201, although the extreme values span a range of 0.48 dex.
+CLQs is reported in the last column of Table~\ref{tab:QSFit-results}.
+The uncertainty typically associated with single-epoch mass estimates
+is $\sim 0.5$~dex, implying that the virial products for our three
+high-redshift CLQs are all remarkably constant and compatible with
+single black hole masses per source, even in those cases where the
+\civ\ estimates were deemed potentially unreliable. The object showing
+the largest variation is J2228+2201, though even that source only
+spans a range of 0.48~dex.
 
-\citet{Shen2011} reports Virial BH mass based on \mgii and \civ\ as
-$\log (M_{\rm BH, Vir}/M_{\odot}) = 9.55\pm0.05$ and $\log(M_{\rm BH, Vir}/M_{\odot}) =
-9.49\pm0.04$, respectively. We thus use the mean of these five values
-(three from our three epochs and the two \citet{Shen2011} values) to
-establish a working mean SMBH mass of $\log (M_{\rm BM, vir}/M_{\odot})
-= 9.726$ for J1205+3422.  J1638+2827 also has two virial mass
-measurments from Shen2011, but also has two measurements from
-\citet{Kozlowski2017} (again using \civ and \mgii). The mean mass
-measurement for J1638+2827 here is $\log(M_{\rm BM, vir}/M_{\odot} =
-9.091$. For J2228+2201 there are two \citet{Kozlowski2017}, leading to
-a mean mass of $\log(M_{\rm BM, vir}/M_{\odot} = 9.366$. We use these
+\citet{Shen2011} and \citet{Kozlowski2017} report virial black hole
+masses based on \mgii\ and \civ\ for the SDSS/BOSS observations of our
+targets. For J1205+3422, \citet{Shen2011} report $\log (M_{\rm BH,
+MgII}/M_{\odot}) = 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot})
+= 9.49 \pm 0.04$. We use the mean of five values --- three from our
+three epochs and two from \citet{Shen2011} --- to calculate an adopted
+SMBH mass of $\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.
+J1638+2827 also has two virial mass measurements from
+\citet{Shen2011}, as well as two measurements from
+\citet{Kozlowski2017}. The mean mass measurement adopted for
+J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot} = 9.09$. For J2228+2201,
+there are two \citet{Kozlowski2017} measurements, leading to a mean
+adopted mass of $\log(M_{\rm BH, vir}/M_{\odot} = 9.37$. We use these
 mean SMBH masses when calculating the Eddington ratios.
 
-From the virial mass estimates, all our objects have SMBH masses $M
->10^{9} M_{\odot}$.  This is at the upper end of SMBH masses at all
-epochs, and towards the extreme of the mass distribution for $z\sim2$
-objects.  Figure~\ref{fig:CIV_MBHvsREW} shows the \civ\ Equivalent
-width and the virial black hole masses for a sample of $\approx$20,000
-$z>1.5$ SDSS quasars from the QSFit catalog as well as the estimates
-for the three \civ\ CLQs.
+From the virial mass estimates, all our objects have SMBH masses
+$M_{\rm BH} >10^{9} M_{\odot}$.  This is at the upper end of SMBH
+masses at all epochs, and towards the extreme of the mass distribution
+for $z\sim2$ quasars.  Figure~\ref{fig:CIV_MBHvsREW} compares the
+\civ\ EW versus the virial SMBH masses for our multi-epoch
+observations to a sample of $\approx 20,000 z>1.5$ SDSS quasars from
+the QSFit catalog \citep{Calderone2017}.
 
@@
   \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_REWvsFWHM_20191128.png}
+  {figures/CIV_CLQs_REWvsFWHM_20191211.png}
   \vspace{-12pt}
-  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
-    of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
-    of \citet{Hamann2017}.
-   Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.}
+  \caption[]{Rest-frame EW vs. FWHM of \civ\
+    for BOSS DR12 quasar sample \citep{Hamann2017}.
+   Symbols as in Figure~\ref{fig:CIV_MBHvsREW}.}
   \label{fig:REWvsFWHM}
 \end{figure}
+
 \subsection{Quantified Temporal Evolution of \civ\ Emission}
 Quasars with interesting physical properties, such as extreme
-outflows, can be selected using EW and FWHM measurements, \citep[e.g.,
-the ``Extremely Red Quasars'' (ERQs)][]{Ross2015, Zakamska2016,
-Hamann2017, Zakamska2019}. Figure~\ref{fig:REWvsFWHM} shows the rest
-Equivalent Width (REW) versus the Full Width Half Maximum (FWHM) of
-the \civ\ emission line in the BOSS DR12 quasar sample using the
-catalogue of \citet{Hamann2017}.
+outflows, can be selected using EW and FWHM measurements \citep[e.g.,
+``Extremely Red Quasars'' ---][]{Ross2015, Zakamska2016, Zakamska2019,
+Hamann2017}. Figure~\ref{fig:REWvsFWHM} shows the rest-frame EW versus
+the FWHM of the \civ\ emission line in the BOSS DR12 quasar sample
+from the catalogue of \citet{Hamann2017}.  Other than the two low
+quality, suspect observations, the multi-epoch observations of our
+high-redshift CLQs are all consistent with the bulk of the BOSS DR12
+sample.
 
-The velocity offsets of the \civ\ line are also
-approximately constant, and compatible with a single value (within
-3$\sigma$).  The exception is J2228+2201, where a significant change
-($\sim$7$\sigma$) is observed between the second and third observation
-epochs. The magnitude of the velocity blueshifts ($\sim200-1100$ km s$^{-1}$)
-are consistent with recent results into the properties of 
-rest-frame UV spectra over the redshift range $1.5 \leq z \leq 7.5$
-\citep{Meyer2019}.
+The temporal evolution of the velocity offsets, 1450~\AA\ continuum
+luminosity, continuum slope, \civ\ line width (FWHM), and virial black
+hole mass estimates are shown in Figure~\ref{fig:QSFit-results}.  The
+\civ\ velocity offsets are approximately constant, and generally
+compatible with a single value (within 3$\sigma$).  The exception is
+J2228+2201, where a significant change ($\sim$7$\sigma$) is observed
+between the second and third epochs. The velocity blueshifts ($\sim
+200-1100$ km s$^{-1}$) are consistent with rest-frame UV spectra of
+quasars over the redshift range $1.5 \leq z \leq 7.5$
+\citep[e.g.,][]{Meyer2019}.
 
@@
   \caption{Temporal evolution of the spectral properties of the three
-    quasar considered in this work.}
+    quasars considered in this work.}
   \label{fig:QSFit-results}
 \end{figure*}
-The temporal evolution of the velocity offsets, along with the
-1450\AA\ continuum luminosity and slope, the \civ\ line FWHM
-and virial black hole mass are given in Figure~\ref{fig:QSFit-results}.
 
@@
     \hline
-    Object           & MJD      & $L_{\rm bol}$    &  $\eta_{\rm Edd}$  \\
+    Object       & MJD & $L_{\rm bol}$&  $\eta_{\rm Edd}$  \\
     \hline
-                     & 53498    & 47.216           &  -0.610                  \\
-J1205+3422 & 58538    &  46.567          &  -1.259  \\                        %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
-                     & 58693     &  46.070         &  -1.756 \\
+                     & 53498 & 47.216     &  $-$0.610   \\
+ J1205+3422 & 58538 &  46.070    &   $-$1.756  \\   %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
+                     & 58693 &  46.567    &  $-$1.259  \\                    
     \hline 
-                     & 54553   & 46.166    & -1.025 \\
-J1638+2827  & 55832   & 45.981    & -1.210  \\                                            %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
-                     & 58583   & 46.504   & -0.687       \\
+                     & 54553 & 46.166   & $-$1.025  \\
+J1638+2827  & 55832 & 45.981   & $-$1.210  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
+                     & 58583 & 46.504   & $-$0.687   \\
     \hline 
-                      & 56189   & 46.231   &  -1.235 \\
-J2228+2201   & 56960    & 47.342   & -0.124 \\                                             %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
-                       & 58693   & 46.826     &  -0.640 \\
+                     & 56189  & 46.231  &  $-$1.235 \\
+J2228+2201  & 56960 & 47.342  & $-$0.124  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
+                     & 58693 & 46.826   &  $-$0.640 \\
     \hline
@@
   \end{tabular}
-  \caption{
-    Bolometric luminosities are given in either \citet{Shen2011} or 
-    \citet{Kozlowski2017} for the three CLQs. We scale these 
-    values using our measured $\nu L_{\nu}$ continuum luminosity values.
-    From Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BM, vir}/M_{\odot}) = 9.726$ for J1205+3422; 
-    $\log(M_{\rm BM, vir}/M_{\odot} = 9.091$ for  J1638+2827, 
-    and $\log(M_{\rm BM, vir}/M_{\odot} = 9.366$ for J2228+2201. 
-    The Eddington Luminosity is 
-    $L_{\rm Edd} = 1.26\times10^{38} (M/M_{\odot})$ erg s$^{-1}$ and
-    %%  6.70456406676162      e+47  for J12
-    %%  1.5537120898684228  e+47  for J16
-    %%  2.9266483634099527  e+47 for J22
-   $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
+  \caption{Bolometric luminosities are given in either \citet{Shen2011} or
+    \citet{Kozlowski2017} for the three CLQs. We scale these values using
+    our measured $\nu L_{\nu}$ continuum luminosity values.  From
+    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
+      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
+      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
+      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
+    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
+    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
 \label{tab:Eddington_ratios} 
@@
   \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_20191130.png}
+  {figures/CIV_CLQs_Baldwin_20191211.png}
    \vspace{-12pt}
-   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
-     commonly referred to as The Baldwin Plot.
-     The continuum luminosities are  from \citet{Calderone2017},
-     the REW measurements are Table~\ref{tab:QSFit-results}.
-     Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.
-     The dashed red line has slope $\beta=-0.38$.}
+   \caption[]{\civ\ equivalent width versus underlying continuum luminosity,
+     commonly referred to as the Baldwin plot.  The continuum luminosities
+     are from \citet{Calderone2017}.  The rest-frame EW (REW) measurements
+     are from Table~\ref{tab:QSFit-results}.  Symbols as in
+     Figure~\ref{fig:CIV_MBHvsREW}.  The dashed red line has slope
+     $\beta=-0.38$.}
   \label{fig:CIV_Baldwin}
 \end{figure}
+
 \subsection{The \civ\ Baldwin Effect}
-The Baldwin Effect \citep[Beff; ][]{Baldwin1977} is an empirical 
-relation between emission-line REWs and continuum luminosity in
-quasars \citep[][]{Shields2007, Hamann2017, Calderone2017}.
+The Baldwin effect \citep{Baldwin1977} is an empirical relation
+between quasar emission line rest-frame EWs and continuum luminosity
+\citep[e.g.,][]{Shields2007, Hamann2017, Calderone2017}.
 \citet{Hamann2017} and \citet{Calderone2017} present recent
-measurements of the Beff for large quasar samples.
+measurements of the Baldwin effect for large quasar samples.
 
-There is an anti-correlation between the emission-line REWs and
-e.g. 1450\AA\ rest continuum luminosity, so that as the underlying UV
-continuum luminosity increases, the EW decreases. 
-Figure~\ref{fig:CIV_Baldwin} shows this for a sample (from the QSFit catalogue)
-for 20,374 quasars.  The slope (not shown) is $\beta$ is $-0.1997$.
-This is consistent with \citet{Kozlowski2017}, using their bolometric
-luminosity gives a slope of $\beta=-0.251$ and in line with that from
-\citet[][ $\beta=-0.23$]{Hamann2017}.
+There is an anti-correlation between the rest-frame EWs and, e.g.,
+1450~\AA\ rest-frame continuum luminosity, so that as the underlying
+UV continuum luminosity increases, the EW decreases.
+Figure~\ref{fig:CIV_Baldwin} shows this for a sample of 20,374 quasars
+from the QSFit catalogue \citep{Calderone2017}.  The slope is $\beta$
+is $-0.20$, consistent with \citet[][ $\beta=-0.25$, but for
+bolometric luminosity rather than rest-frame UV continuum luminosity]
+{Kozlowski2017} and with \citet[][ $\beta=-0.23$]{Hamann2017}.
 
 We add the measurements from the three \civ\ CLQ quasars at each epoch
-to Figure~\ref{fig:CIV_Baldwin}. We see first that all three quasars
-at all three epochs lie on the edge of the $\nu L_{\nu}$-EW
-distribution.  Second, with the exception of J1638+2827 on MJD 55832,
-all the measurements show an {\it intrinsic Baldwin Effect}
-\citep[e.g.][]{Goad2004, Rakic2017}.  The slope of the CLQs intrinsic
-BEff is $\approx-0.38$, as shown by the dashed red line in
-Fig.~\ref{fig:CIV_Baldwin}.
+to Figure~\ref{fig:CIV_Baldwin}. All three quasars at all three epochs
+lie on the edge of the $\nu L_{\nu}$-EW distribution.  Also, with the
+exception of J1638+2827 on MJD 55832, all the measurements show an
+{\it intrinsic} Baldwin effect \citep[e.g.,][]{Goad2004, Rakic2017}.
+Subject to small number statistics, the slope of the intrinsic Baldwin
+effect for these three high-redshift \civ\ CLQs is somewhat steeper
+than the population trends, with $\beta \approx-0.38$, shown by the
+dashed red line in Figure~\ref{fig:CIV_Baldwin}.
 
@@
 \subsection{Continuum and Line Changes: Comparisons to recent Observations}
-The top row of Figure~\ref{fig:QSFit-results} demonstrates that
-both the 1450\AA\ continuum and the \civ\ emission lines can
-exhibit large, $>$$\times$10, changes in luminosity, {\it and}
-that these continuum-line changes track each other.
+The top row of Figure~\ref{fig:QSFit-results} demonstrates that both
+the 1450~\AA\ continuum and the \civ\ emission lines can exhibit
+large, greater than an order-of-magnitude, changes in luminosity, {\it
+and} that these continuum-line changes track each other.
 
-\citet{Trakhtenbrot2019} report on the quasar 1ES 1927+654 which was
-initially seenn to lack broad emission lines and line-of-sight
-obscuration, i.e, a ``Type 2'' quasar at redshift $z=0.02$. This
-object is then seen to spectroscopically change with the appearance of
-a blue, featureless continuum, followed by the emergence of broad
-Balmer emission lines.  i.e. this quasar changes into a broad-line
-Type 1 after a raise in the continuum luminosity.  This suggests that
-there is (at least in some cases) a direct relationship between the continuum
-and broad emission lines in CLQs.  A similar scenario may have occured
-for the 3 high-$z$ quasars presented here, although we lack the
-high-cadence multiwavelength, multi-epoch coverage that
-\citet{Trakhtenbrot2019} present.  The multiwavelength data that
-\citet{Trakhtenbrot2019} have includes a UV spectrum of 1ES 1927+654.
-Interestingly, however, there is no evidence for broad UV emission lines, including
-\civ, C\,{\sc iii}, or Mg\,{\sc ii}.  The authors attribute the lack of broad UV
-emission lines to dust within the BLR, noting that to dust in the
-broadline emission region, noting that the continuum emission does not
-show any signs of dust extinction.
+\citet{Trakhtenbrot2019} report on the quasar 1ES~1927+654 at
+$z=0.02$, which was initially seen to lack broad emission lines and
+line-of-sight obscuration, i.e, it was a ``type 2'' quasar. This
+object was then seen to spectroscopically change with the appearance
+of a blue, featureless continuum, followed by the emergence of broad
+Balmer emission lines --- i.e., this quasar changed into a broad-line,
+or ``type 1'' quasar, after the continuum luminosity brightened.  This
+implies that there is (at least in some cases) a direct relationship
+between the continuum and broad emission lines in CLQs.  Many other
+examples of a similar phenomenon have been reported, albeit not with
+the dense spectral cadencing of 1ES~1927+654.  A similar scenario may
+have occurred for the three high-redshift CLQs presented here,
+although we lack the high-cadence, multiwavelength, multi-epoch
+coverage that \citet{Trakhtenbrot2019} present.  Interestingly,
+\citet{Trakhtenbrot2019} find no evidence for broad UV emission lines
+in their source, including neither \civ, \ciii, nor \mgii.  The
+authors attribute the lack of broad UV emission lines to dust within
+the BLR.
 
 \citet{MacLeod2019} present a sample of CLQs where the primary
-selection requires large-amplitude ($| \Delta g | > 1$ mag, $| \Delta
+selection requires large amplitude ($| \Delta g | > 1$ mag, $| \Delta
 r | > 0.5$ mag) variability over any of the available time baselines
-probed by the SDSS and Pan-STARRS1 surveys. They find 17 new CLQs
-which is $\sim$20\% of the observerd sample. This CLQ fraction
-increases from 10\% to roughly half, as the continuum flux ratio
-between repeat spectra at 3420 \AA\ (rest-frame) increases from 1.5 to
-6. \citet{MacLeod2019} note that these candidates are at lower Eddington
-ratio relative to the overall quasar population.
+probed by the SDSS and Pan-STARRS1 surveys. They find 17 new CLQs,
+corresponding to $\sim 20$\% of their observed sample. This CLQ
+fraction increases from 10\% to roughly half, as the rest-frame
+3420~\AA\ continuum flux ratio between repeat spectra increases from
+1.5 to 6 --- i.e., more variable quasars are more likely to exhibit
+large changes in their broad emission lines. \citet{MacLeod2019} note
+that their CLQs have lower Eddington ratios relative to the overall
+quasar population.
 
-Using the same dataset as and extremely variable quasar sample
-as \citet{MacLeod2019}, \citet{Homan2019}
-investigate the responsiveness of the \mgii broad emission line
-doublet in AGN on timescales of several years.  By again focussing on quasars that show large
-changes in their optical light-curves, \citet{Homan2019} find that
-\mgii clearly does respond to the continuum.  However, a key finding
-from \citet{Homan2019} is that the degree of responsivity varies
-strikingly from one object to another.  There are cases of \mgii
-changing by as much as the continuum, more than the continuum, or very
-little at all.  In the majority (72\%) of this highly variable sample,
-the behaviour of \mgii corresponds with that of H$\beta$.  However,
-there are also examples of \mgii showing variation, but H$\beta$ does
-not, and vice versa.
+Using the same dataset as \citet{MacLeod2019}, \citet{Homan2019}
+investigate the responsiveness of the \mgii\ broad emission line
+doublet in AGN on timescales of several years.  Again focussing on
+quasars that show large changes in their optical light-curves,
+\citet{Homan2019} find that \mgii\ clearly does respond to the
+continuum.  However, a key finding from \citet{Homan2019} is that the
+degree of responsivity varies strikingly from one object to another.
+There are cases of \mgii\ changing by as much as the continuum, more
+than the continuum, or very little at all.  In the majority (72\%) of
+this highly variable sample, the behaviour of \mgii\ corresponds with
+that of H$\beta$.  However, there are also examples of \mgii\ showing
+variations while but H$\beta$ does not, and vice versa.
 
-\citet{Graham2019b} report the largest number of H$\beta$ CSQs with 111
-sources being identified. \citet{Graham2019b} find that this population
-of extreme varying quasars is associated with {\it changes} in the
-Eddington ratio, (rather than just the magnitude of the Eddington
-ratio itself) and the timescales imply cooling/heating fronts
-propagating through the disk.\\
-{\bf NPR to finish this off} \\
+\citet{Graham2019b} report the largest number of H$\beta$ CLQs to
+date, with a sample of 111 sources identified. \citet{Graham2019b}
+find that this population of extreme varying quasars, referred to as
+CSQs in their paper, is associated with {\it changes} in the Eddington
+ratio rather than simply the magnitude of the Eddington ratio itself.
+They also find that the timescales imply cooling/heating fronts
+propagating through the disk.
 
-\subsection{Continuum and Line Changes: Comparisons to theoretical expectaions}
-{\bf SF and BM to add a little more here}\\
-The \civ\ line is one of the strongest collisionally excited lines in quasar spectra \citep[e.g.][]{HamannFerland1999}, and \civ\ emission probes the photoionization environment produced by the innermost disk, as indicated by RM time-delay measurements.
+\subsection{Continuum and Line Changes: Comparisons to Theoretical Expectations}\label{sec:theory}
+The \civ\ line is one of the strongest collisionally excited lines in
+quasar spectra \citep[e.g.,][]{HamannFerland1999}, and \civ\ emission
+probes the photoionisation environment produced by the innermost disk,
+as indicated by reverberation mapping time-delay measurements.
 
-In standard \citet{SS73} thin disk models, large changes in the continuum flux are not permitted over short timescales due to the relatively long viscous time associated with such disks.
-Given the observed short timescale continuum variations, it is not surprising that the \citet{SS73} disk may fail on other fronts.
-%The \civ\ variations observed in our sources...
+In standard \citet{SS73} thin disk models, large changes in the
+continuum flux are not permitted over short timescales due to the
+relatively long viscous time associated with such disks. Given the
+observed short timescale continuum variations, we must consider more
+complex models. We note that two of our sources (J1205+3422 and
+J2228+2201) have \civ\ EW and continuum luminosity changes which fall
+comfortably along a line, implying their variation is consistent with
+an intrinsic Baldwin effect (see Figure~\ref{fig:CIV_Baldwin}). That
+is, the excitation of the \civ\ line is driven by the changes in the
+continuum; however, the excited gas cannot reach an equilibrium
+excitation state as quickly as the continuum changes, making the slope
+of the intrinsic Baldwin effect greater than that of the overall
+ensemble slope, which is derived from many single-epoch observations,
+the majority of which are assumed to be in equilibrium.
 
-This indicates they may comfortably fit into the sample of \civ\ variable quasars explored by \citet{Dyer2019}, and similar to those authors we suggest slim accretion disk models e.g., \citet[][]{Abramowicz1988} or inhomogeneous disk models
-\citep[e.g.,][]{DexterAgol2011} may provide viable explanations for our observations.
-%% I want to say a bit more here about the generic probe of photoionization vs shielding and conditions in the BL region but that will take more time.
+The presence of an intrinsic Baldwin effect implies those sources may
+comfortably fit into the sample of \civ\ variable quasars explored by
+\citet{Dyer2019}. Similar to those authors, we consider slim accretion
+disk models \citep[e.g.,][]{Abramowicz1988}, which may explain the
+observed variability. In particular, the summary of disk variation
+timescales presented in \citet{Stern2018} shows that timescales are
+shorter for taller disks, permitting changes similar to those observed
+if they are caused by heating or cooling fronts propagating on the
+disk sound crossing time. \citet{Dyer2019} also consider inhomogeneous
+disk models \citep[e.g.,][]{DexterAgol2011} where flux variations are
+driven by azimuthal inhomogeneities in the temperature of the
+disk. Such inhomogeneities could arise from disk instabilities
+\citep[e.g.,][]{LightmanEardley1974} or interactions of embedded
+objects \citep[e.g.,][]{McKernan2014, McKernan2018}. If an
+inhomogeneous disk is responsible for the continuum variations, which
+then drive \civ\ variations, it implies that our objects are simply
+the extreme outliers produced by a process which occasionally, but
+rarely, produces very large hot or cool spots. The frequency of such
+occurrences can be used to constrain the slope and normalization of
+the power law distribution of spot size.
 
-\subsection{Implications for The Baldwin Effect}
-The variable properties of the rest-frame UV quasar emission lines have been long studied, with the global (or ensemble) Baldwin Effect (the anti-correlation between the EW of the emission line and the underlying continuum luminosity of single-epoch observations of a large number of AGN, first noted in \citet{Baldwin1977}.
-More recently, the intrinsic Baldwin effect, the same anti-correlation but in an individual, variable AGN.
+Finally, we must also consider the disk/wind model which has
+successfully reproduced many features of quasar \civ\ observations,
+notably the common blueshifted offset \citep[e.g.,][]{Murray1995}. In
+this model, \civ\ is optically thick at low velocities, but optically
+thin at high velocities, with $\tau \sim 1$ at $\sim$5000 km
+s$^{-1}$. In a disk/wind model, the BLR is very small, implying short
+timescales of emission line variability. Also in this model, there
+should be associated strong absorption in the soft X-ray band, which
+could be tested with follow-up observations.
 
-The X-ray Baldwin Effect \citep[e.g., ][]{Iwasawa_Taniguchi1993}...
-\citet{Bachev2004} find a 10-fold decrease in EW \civ\ with Eddington ratio (decreasing from $\sim$1 to $\sim$0.01), while \nv shows no change.
-These trends suggest a luminosity-independent ``Baldwin effect'' in which the physical driver may be the Eddington ratio.
-\citet{Ge2016} Broad emission lines is a prominent property of Type 1 quasars.
+The foregoing discussion directly applies to the two objects which
+maintain an intrinsic Baldwin effect relationship between \civ\ EW and
+continuum luminosity. However, J1638+2827 clearly does not maintain
+such a relationship --- indeed, the continuum and \civ\ EW appear
+somewhat correlated, rather than anti-correlated, in this source. This
+implies that the illumination of the \civ\ emitting region by a
+variable ionising continuum and the corresponding change in the
+photoionisation state alone cannot explain the collapse and recovery
+of the line.
 
@@
   \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/MJD_vs_Eddington_20191202.png}
+  {figures/MJD_vs_Eddington_20191211.png}
   \vspace{-12pt}
-  \caption[]{Eddington Ratios of the three \civ\ CLQs.
-    Grayscale gives the Eddington Ratio ranges for the SDSS
-    \citep[from ][]{Shen2011} and the BOSS \citep[from ][]{Kozlowski2017} 
-    catalogues.
-    Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.
-    The red region ($L / L_{\rm Edd} \approx 0.02\pm0.01$;  $\eta =-1.7\pm0.13$) is
-    the transition accretion rate suggested by \citet{NodaDone2018}.
-    A ``High/Soft State'' with $\eta_{\rm Edd} \geq -1$ and a
-    a ``Low/Hard State'' with $\eta_{\rm Edd} \leq -2$ are indicated 
-    with dahsed lines and arrows. 
-  }
+  \caption[]{Eddington ratios of the three \civ\ CLQs.  Grayscale gives the
+    Eddington ratio ranges for quasars from SDSS \citet[][]{Shen2011} and
+    BOSS \citep[][]{Kozlowski2017}.  Symbols as in
+    Figure~\ref{fig:CIV_MBHvsREW}.  The red region ($L / L_{\rm Edd}
+    \approx 0.02 \pm 0.01$; $\eta_{\rm Edd} = -1.7 \pm 0.13$) is the
+    transition accretion rate suggested by \citet{NodaDone2018}.  A
+    ``High/Soft State'' with $\eta_{\rm Edd} \geq -1$ and a a ``Low/Hard
+    State'' with $\eta_{\rm Edd} \leq -2$ are indicated with dashed lines
+    and arrows.}
   \label{fig:Eddington_ratios}
 \end{figure*}
+
 \subsection{Eddington Ratios and State Changes} 
 The broad UV and optical lines in quasars are most sensitive to the
-extreme ultraviolet (EUV) part of the spectral energy distribution
-(SED), with \civ\ (and indeed \heii and \nv) being at the higher
-energy end of the EUV distribution.
+extreme ultraviolet (EUV) part of the SED, with \civ\ (and indeed
+\heii\ and N\,{\sc v}) being at the higher energy end of the EUV
+distribution.
 
-The soft X-ray excess -- the excess of X-rays below 2 keV with respect
-to the extrapolation of the hard X-ray spectral continuum model -- is
-a very common feature among type 1 active galactic nuclei (AGN). 
-\citet{NodaDone2018} note that
-The soft X-ray excess produces most of the ionizing photons, so its
-dramatic drop leads to the disappearance of the broad-line region,
-driving the ``changing-look'' phenomena.  major difference is that
-radiation pressure should be much more important in AGNs, so that the
-sound speed is much faster than expected from the gas temperature.
-%%
-This spectral hardening appears similar to the soft-to-hard state
-transition in black hole binaries at $L / L_{\rm Edd} \sim 0.02$
-(i.e. $\eta_{\rm Edd} \sim -1.7$), where the inner disc evaporates into
-an advection dominated accretion flow, while the overall drop in
-luminosity appears consistent with the hydrogen ionization disc
-instability.  Crucially \citet{NodaDone2018} make the prediction that
-all changing-look AGNs are similarly associated with the state
-transition at $L / L_{\rm Edd} \sim$a few per cent.
+\citet{NodaDone2018} note that the soft X-ray excess -- the excess of
+X-rays below 2 keV with respect to the extrapolation of the hard X-ray
+spectral continuum model, and a common feature among Type~1 AGN --
+produces most of the ionizing photons, so its dramatic drop can lead
+to the disappearance of the broad-line region, driving the
+changing-look phenomena. \citet{NodaDone2018} go on to make a
+connection between state changes in Galactic binaries and CLQs.
+However, one thing to note is that radiation pressure should be much
+more important in AGNs than in stellar mass black hole systems,
+implying that sound speed is much faster than expected from the gas
+temperature alone.  In Galactic binaries spectral hardening
+corresponds to the soft-to-hard state transition in black hole
+binaries, which occurs at $L / L_{\rm Edd} \sim 0.02$ (i.e.,
+$\eta_{\rm Edd} \sim -1.7$).  During this state transition, the inner
+disc evaporates into an advection-dominated accretion flow, while the
+overall drop in luminosity appears consistent with the hydrogen
+ionisation disc instability.  \citet{NodaDone2018} predict that
+changing-look AGNs are similarly associated with state transitions at
+$L / L_{\rm Edd}$ of a few percent.
 
-By comparing the observed correlations between the UV/optical-to-X-ray
-spectral index ($\alpha_{\rm ox}$) and Eddington ratio in AGN to those
+Comparing observed correlations between the optical-to-X-ray spectral
+index (i.e., $\alpha_{\rm ox}$) and Eddington ratio in AGN to those
 predicted from observations of X-ray binary outbursts,
-\citet{Ruan2019a} find a remarkable similarity to accretion state transitions in prototypical
-X-ray binary outbursts, including an inversion of this correlation at
-a critical Eddington ratio of $\sim$10$^{-2}$ (i.e. at the same ratio
-as motivated by \citet{NodaDone2018}).  These results suggest that the
-structures of black hole accretion flows directly scale across a
-factor of $\sim10^{8}$ in black hole mass and across different
-accretion states. Using \citet{Ruan2019a} as a guide, there are potentially three accretion regimes: 
-(1) a ``High/Soft State'' with $\eta_{\rm Edd} \gtrsim -1$; 
-(1) a ``Low/Hard State'' with $-2 \lesssim \eta_{\rm Edd} \lesssim  -1$;
-(1) a ``Low/Hard State'' with $\eta_{\rm Edd} \lesssim -2$.
-These are given as shaded regions in Figure~\ref{fig:Eddington_ratios}.
+\citet{Ruan2019a} find a remarkable similarity to accretion state
+transitions in prototypical X-ray binary outbursts, including an
+inversion of this correlation at a critical Eddington ratio of
+$\sim$10$^{-2}$, i.e., at the same ratio motivated by
+\citet{NodaDone2018}.  These results suggest that the structures of
+black hole accretion flows directly scale across a factor of
+$\sim10^{8}$ in black hole mass and across different accretion
+states. Using \citet{Ruan2019a} as a guide, there are potentially
+three accretion regimes: {\it (i)} a ``High/Soft State'' with
+$\eta_{\rm Edd} \gtrsim -1$; {\it (ii)} a ``Low/Hard State'' with $-2
+\lesssim \eta_{\rm Edd} \lesssim -1$; and {\it (iii)} a ``Low/Hard
+State'' with $\eta_{\rm Edd} \lesssim -2$.  These are given as shaded
+regions in Figure~\ref{fig:Eddington_ratios}.
 
-Building on a previous work \citep[e.g.,][]{JiangYF2014, JiangYF2016, JiangYF2019}, \citet{JiangYF2019arXiv} use global three dimensional radiation magneto-hydrodynamic simulations to study the properties of inner regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$ black hole with mass accretion rates reaching 7\% and 20\% of the Eddington value.
+Apart from J1205+3422 on MJD 58538, we see all the \civ\ CLQ epochs
+are above $L / L_{\rm Edd} \sim 5$\%. As we have noted throughout, the
+spectrum for J1205+3422 on MJD 58538 has low SNR, so while this object
+could well have entered a `low-state', this is difficult to
+conclusively confirm.  Nevertheless, and taking the J1205+3422
+spectrum at face-value, we note that all the \civ\ CLQs are well above
+$\sim1\%$ in Eddington luminosity and thus the suggested ``Low/Hard
+State'' boundary.
+
+While we note there is interest in plotting these accretion rates, and
+motivation from \citet{NodaDone2018} and \citet{Ruan2019a}, we very
+much caution on over-interpretation at this juncture. The point of
+this paper was to report on three very interesting CLQs.  Our object
+definitions are based on empirical, observed properties.  The
+potential for physical connections of accretion physics across the
+large-range of mass-scales is tantalising, but is left to future
+investigations.
 
@@
 In this paper we have reported on three redshift $z>2$ quasars with
-dramatic changes in their \civ\ emission lines, the first
-`Changing-Look'' quasars at high redshift.  This is also the first
-time the changing-look behaviour has been seen in a high-ionization
+dramatic changes in their \civ\ emission lines, the first sample of
+changing-look quasars at high redshift.  This is also the first time
+the changing-look behaviour has been seen in a high-ionisation
 emission line.
@@
 \begin{itemize}
-\item SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
-  in their observed optical light curves, and subsequent spectroscopy
-  shows significant changes in the \civ\ broad emission line, with both
-  line collapse and emergence being displayed in rest-frame timescales
-  of $\sim$240-1640 days.
+\item SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting
+  behaviour in their observed optical light curves, and subsequent
+  spectroscopy shows significant changes in the \civ\ broad emission
+  line, with both line collapse and emergence being displayed on
+  rest-frame timescales of $\sim 240-1640$~days.
 \item Where observed, the profile of the Ly$\alpha$/\nv emission complex
-  also changes, and there is tentative evidence for changes in the \mgii
+  also changes, and there is tentative evidence for changes in the \mgii\
   line.
@@
   in the \civ\ line flux-line width plane, the quasars are not seen to
-  be outliers when considered against the full $z>2$ quasar population
-  in terms of (rest) Equivalent Width and FWHM properties.
+  be outliers when considered against the full quasar population
+  in terms of (rest-frame) EW and FWHM properties.
 \item 
   We put these observations in context with recent ``state-change''
-  models, but note that even in their `low-state', the \civ\ CLQs are
-  above $\sim10\%$ in Eddington luminosity.
+  models, and note that with the exception of the low SNR spectrum of
+  J1205+3422 on MJD 58538, even in their low state, 
+  the \civ\ CLQs are above $\sim5$\% in Eddington luminosity. 
 \end{itemize}
+
+There are now more observed examples of dramatic, dynamic changes in
+supermassive black hole systems e.g. CLQs/CSQs than Galactic X-ray
+Binaries.  While the timescales are expected to scale with black hole
+mass, whether the full physical system at large does, including the
+associated atomic physics, remains an open question.
 
@@
 \section*{Acknowledgements}
+We thank Andy Lawrence, Mike Hawkins and David Homan for useful discussion.
 NPR acknowledges support from the STFC and the Ernest Rutherford Fellowship scheme. 
 %% KESF \& BM are supported by NSF PAARE AST-1153335. 
-%% KESF \& BM thank CalTech/JPL for support during sabbatical.  
+%% KESF \& BM thank Caltech/JPL for support during sabbatical.
+MJG is supported in part by the NSF grants AST-1815034, and the NASA grant 16-ADAP16-0232.
 \\
-
-\noindent
-We thank:
-\begin{list}{$\circ$}{}
-  \item Andy Lawrence, Mike Hawkins and David Homan for useful discussion.
-\end{list}
 
@@
 
-This publication makes use of data products from the Wide-field
-Infrared Survey Explorer, which is a joint project of the University
+This publication makes use of data products from the {\it Wide-field
+Infrared Survey Explorer}, which is a joint project of the University
 of California, Los Angeles, and the Jet Propulsion
-Laboratory/California Institute of Technology, and NEOWISE, which is a
+Laboratory/California Institute of Technology, and {\it NEOWISE}, which is a
 project of the Jet Propulsion Laboratory/California Institute of
-Technology. WISE and NEOWISE are funded by the National Aeronautics
-and Space Administration. No animals were harmed in the production of
-this paper, but there was a large spider in NPRs apartment that
-``vanished''.
+Technology. {\it WISE} and {\it NEOWISE} are funded by the National Aeronautics
+and Space Administration.
+
+Based on observations obtained with the Samuel Oschin 48-inch Telescope at the Palomar Observatory as part of the Zwicky Transient Facility project.
+ZTF is supported by the National Science Foundation under Grant No.
+AST-1440341 and a collaboration including Caltech, IPAC, the Weizmann Institute for Science, the Oskar Klein Center at Stockholm University, the University of Maryland, the University of Washington, Deutsches Elektronen-Synchrotron and Humboldt University, Los Alamos National Laboratories, the TANGO Consortium of Taiwan, the University of Wisconsin at Milwaukee, and Lawrence Berkeley National Laboratories.
+Operations are conducted by COO, IPAC, and UW.
+%% No animals were harmed in the production of this paper, but there
+%% was a large spider in NPRs apartment that ``vanished''.
 

### 2019-12-11 plots/MJD_Eddington/mjd_vs_Eddington.py

@@ -116,8 +116,8 @@ for ii in range(len(CLQs)):
             J12_53498  = mlines.Line2D([], [], label='J1205+3422 (53498)', color='fuchsia',
                        marker="o", markeredgecolor='k', markeredgewidth=1.4, markersize=7,  linestyle='None')
         if (CLQs_MJD[ii] ==  58538):
-            ax.scatter(CLQs_MJD[ii], CLQs_eta[ii], color='k',       alpha=alpha, marker='s', s=ms_large*1.6)
-            ax.scatter(CLQs_MJD[ii], CLQs_eta[ii], color='fuchsia', alpha=alpha, marker='s', s=ms_large)
+            ax.scatter(CLQs_MJD[ii], CLQs_eta[ii], color='k',       alpha=alpha, marker='s', s=ms_large*1.6, zorder=10)
+            ax.scatter(CLQs_MJD[ii], CLQs_eta[ii], color='fuchsia', alpha=alpha, marker='s', s=ms_large, zorder=10)
             J12_58538  = mlines.Line2D([], [], label='J1205+3422 (58538)', color='fuchsia',
                        marker="s", markeredgecolor='k', markeredgewidth=1.4, markersize=7,  linestyle='None')
         if (CLQs_MJD[ii] ==  58693):

### 2019-12-11 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py

@@ -237,14 +237,14 @@ for ii in range(len(CLQs)):
             #ax.errorbar(CLQs_logContLum[ii], CLQs_logREW[ii], color='fuchsia',xerr=CLQs_logREWerr[ii], yerr=CLQs_FWHMerr[ii], fmt='s', linewidth=lw)
             ax.scatter (CLQs_logContLum[ii], CLQs_logREW[ii], color='k',       alpha=alpha, marker='s', s=ms_back)
             ax.scatter (CLQs_logContLum[ii], CLQs_logREW[ii], color='fuchsia', alpha=alpha, marker='s', s=ms)
-            J12_58538 = mlines.Line2D([], [], label=r'J1205+3422 (58538)', color='fuchsia',
+            J12_58538 = mlines.Line2D([], [], label=r'J1205+3422 (58538)$^{*}$', color='fuchsia',
                         marker="s", markeredgecolor='k', markeredgewidth=mrkedwd, markersize=markersize,  linestyle='None')
         if (CLQs['MJD'][ii] ==  58693):
             #ax.errorbar(CLQs_logContLum[ii], CLQs_logREW[ii], color='k',      xerr=CLQs_logREWerr[ii], yerr=CLQs_FWHMerr[ii], fmt='D', linewidth=lw*l_back)
             #ax.errorbar(CLQs_logContLum[ii], CLQs_logREW[ii], color='fuchsia',xerr=CLQs_logREWerr[ii], yerr=CLQs_FWHMerr[ii], fmt='D', linewidth=lw)
             ax.scatter (CLQs_logContLum[ii], CLQs_logREW[ii], color='k',       alpha=alpha, marker='D', s=ms_back)
             ax.scatter (CLQs_logContLum[ii], CLQs_logREW[ii], color='fuchsia', alpha=alpha, marker='D', s=ms)
-            J12_58693 = mlines.Line2D([], [], label=r'J1205+3422 (58693)$^{*}$', color='fuchsia',
+            J12_58693 = mlines.Line2D([], [], label=r'J1205+3422 (58693)', color='fuchsia',
                         marker="D", markeredgecolor='k', markeredgewidth=mrkedwd, markersize=markersize,  linestyle='None')
             
     if str(CLQs['Object'][ii]) == 'J1638p2827':

### 2019-12-11 plots/hexbin_plots/MBH_REW/MBH_REW_hexbin.py

@@ -151,7 +151,7 @@ ymax =  2.95
 ax.axis([xmin, xmax, ymin, ymax])
 
 ## AXES LABELS
-ax.set_xlabel(r"log$_{10}$(M$_{\rm BH}$)",         fontsize=fontsize)
+ax.set_xlabel(r"log$_{10}$(M$_{\rm BH}$/M$_{\odot}$)",         fontsize=fontsize)
 ax.set_ylabel(r"log$_{10}$(REW CIV / {\rm \AA })", fontsize=fontsize)
 ## AXES TICK FORMAT
 ax.tick_params(axis='both', which='major', labelsize=labelsize)
@@ -177,12 +177,12 @@ for ii in range(len(CLQs)):
         if (CLQs['MJD'][ii] ==  58538):
             ax.scatter (CLQs_MBH[ii], CLQs_logREW[ii], color='k',       alpha=alpha, marker='s', s=ms_back)
             ax.scatter (CLQs_MBH[ii], CLQs_logREW[ii], color='fuchsia', alpha=alpha, marker='s', s=ms)
-            J12_58538 = mlines.Line2D([], [], label=r'J1205+3422 (58538)', color='fuchsia',
+            J12_58538 = mlines.Line2D([], [], label=r'J1205+3422 (58538)$^{*}$', color='fuchsia',
                         marker="s", markeredgecolor='k', markeredgewidth=mrkedwd, markersize=markersize,  linestyle='None')
         if (CLQs['MJD'][ii] ==  58693):
             ax.scatter (CLQs_MBH[ii], CLQs_logREW[ii], color='k',       alpha=alpha, marker='D', s=ms_back)
             ax.scatter (CLQs_MBH[ii], CLQs_logREW[ii], color='fuchsia', alpha=alpha, marker='D', s=ms)
-            J12_58693 = mlines.Line2D([], [], label=r'J1205+3422 (58693)$^{*}$', color='fuchsia',
+            J12_58693 = mlines.Line2D([], [], label=r'J1205+3422 (58693)', color='fuchsia',
                         marker="D", markeredgecolor='k', markeredgewidth=mrkedwd, markersize=markersize,  linestyle='None')
             
     if str(CLQs['Object'][ii]) == 'J1638p2827':

### 2019-12-11 plots/hexbin_plots/REW_FWHM/REW_FWHM_hexplot.py

@@ -116,14 +116,14 @@ for ii in range(len(CLQs)):
             ax.errorbar(CLQ_REW[ii], CLQ_FWHM[ii], color='fuchsia', xerr=CLQ_errREW[ii], yerr=CLQ_errFWHM[ii], fmt='s', linewidth=lw)
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='k',       alpha=alpha, marker='s', s=ms*ms_back)
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='fuchsia', alpha=alpha, marker='s', s=ms)
-            J12_58538 = mlines.Line2D([], [], label=r'J1205+3422 (58538)', color='fuchsia',
+            J12_58538 = mlines.Line2D([], [], label=r'J1205+3422 (58538)$^{*}$', color='fuchsia',
                        marker="s", markeredgecolor='k', markeredgewidth=1.4, markersize=7,  linestyle='None')
         if (CLQs['MJD'][ii] ==  58693):
             ax.errorbar(CLQ_REW[ii], CLQ_FWHM[ii], color='k',       xerr=CLQ_errREW[ii], yerr=CLQ_errFWHM[ii], fmt='D', linewidth=lw*l_back)
             ax.errorbar(CLQ_REW[ii], CLQ_FWHM[ii], color='fuchsia', xerr=CLQ_errREW[ii], yerr=CLQ_errFWHM[ii], fmt='D', linewidth=lw)
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='k',       alpha=alpha, marker='D', s=ms*ms_back)
             ax.scatter( CLQ_REW[ii], CLQ_FWHM[ii], color='fuchsia', alpha=alpha, marker='D', s=ms)
-            J12_58693 = mlines.Line2D([], [], label=r'J1205+3422 (58693)$^{*}$', color='fuchsia',
+            J12_58693 = mlines.Line2D([], [], label=r'J1205+3422 (58693)', color='fuchsia',
                        marker="D", markeredgecolor='k', markeredgewidth=1.4, markersize=7,  linestyle='None')
             
             

### 2019-12-11 plots/perObject/J1205p3422_landscape_v1pnt0.py

@@ -70,9 +70,9 @@ infile   = 'DBSP_J1205p3422_b_58538.dat'
 DBSP_b1  = ascii.read(path+infile)
 infile   = 'DBSP_J1205p3422_r_58538.dat'
 DBSP_r1  = ascii.read(path+infile)
-infile   = 'DBSP_J1205p3422_b_58693.dat'
+infile   = 'DBSP_J1205p3422_b_58694.dat'
 DBSP_b2  = ascii.read(path+infile)
-infile   = 'DBSP_J1205p3422_r_58693.dat'
+infile   = 'DBSP_J1205p3422_r_58694.dat'
 DBSP_r2  = ascii.read(path+infile)
 
 ## The Blue and Red arms overlap in wavelength; Blue has better SNR than RED
@@ -260,13 +260,17 @@ ax5.set_xlim([xmin_ax5, xmax_ax5])
 ax5.set_ylim([ymin_ax5, ymax_ax5])
 
 
-## The Spectra curves on the RHS
-ax2.plot(   sdss_wavelength/(1+redshift), sdss_flux,           '-b', lw=linewidth/4.0,  label='SDSS MJD 53498')
-ax2.plot(DBSP_b1_wavelength/(1+redshift), DBSP_b1_flux,        '-r', lw=linewidth/4.0,  label='DBSP MJD 58538')
-ax2.plot(DBSP_r1_wavelength/(1+redshift), DBSP_r1_flux,        '-r', lw=linewidth/4.0)
 ## Smoothing:: https://joseph-long.com/writing/AstroPy-boxcar/
+DBSP_b1_flux_smoothed = convolve(DBSP_b1_flux, Box1DKernel(5))
+DBSP_r1_flux_smoothed = convolve(DBSP_r1_flux, Box1DKernel(5))
 DBSP_b2_flux_smoothed = convolve(DBSP_b2_flux, Box1DKernel(5))
 DBSP_r2_flux_smoothed = convolve(DBSP_r2_flux, Box1DKernel(5))
+
+
+## The Spectra curves on the RHS
+ax2.plot(   sdss_wavelength/(1+redshift), sdss_flux,           '-b', lw=linewidth/4.0,  label='SDSS MJD 53498')
+ax2.plot(DBSP_b1_wavelength/(1+redshift), DBSP_b1_flux_smoothed, '-r', lw=linewidth/4.0,  label='DBSP MJD 58538')
[…]

### 2020-06-09 tex/MNRAS_submission/rv1/reply2referee.txt
Big update for the rv1 MNRAS submission

		We thank the Review and Scientific Editor for their
		comments and suggestions.  In particular we thank the
		Reviewer for a deep reading and thoughtful digestion
		of the manuscript, which has improved the paper.

		We have addressed every point in the Reviewer's report
		and given our replies as indented text below and changes
		as bold text in the new paper draft.

Scientific Editor's Comments:
Dear Authors
Your paper has a high score for plagiarism, contributed largely from
self plagiarism in subsections of Section 2 of the manuscript
(particularly from recent Ross et al al and Graham et al MNRAS papers
in your bibliography).  Please refer to the plagiarism section in the
'MNRAS instructions to authors' and correct this before re-submission.
Regards
Scientific Editor

	   We have changed the Section 2 text.

Reviewer's Comments:
This manuscript presents a search for high-redshift changing-look quasars (CLQs) and the discovery of three such objects. These examples extend the luminosity range of CLQs substantially and they also illustrate the behavior of the near-UV portion of the spectrum, which was not possible with lower-redshift examples. The data analysis appears to be fine and the level of the discussion is appropriate for this type of "discovery" paper. Because of the new and interesting results, I believe that this manuscript will warrant publication, eventually. However, I cannot recommend publication just yet because (a) the overall presentation of the results can and should be improved and (b) more attention to detail is needed.

Below I give extensive and detailed comments and recommendations regarding revisions. A relatively small fraction of my comments concern scientific issues that I recommend be clarified in the manuscript. Other comments concern the presentation of the results, the level of detail included in various sections of the manuscript, citations to the literature, the format and quality of the figures, etc. The comments follow the order of the manuscript.

1. Introduction

(a) In the 2nd paragraph the beginning of the second sentence seems to be cut off.

       	  This has been corrected.

(b) In the 6th paragraph (starting with "Details of the atomic transitions...") the authors note some of the lines present in the near-UV spectra of quasars and the ionization energies of the corresponding ions. I am concerned that, as written, this paragraph may be misleading to the non-expert reader and may propagate misconceptions. Most of the strong lines in the near-UV spectrum are collisionally excited (e.g., the C IV 1550 doublet; the He II 1640 recombination line is among the exceptions). Therefore the ionization potential of the C IV ion discussed in this paragraph is much less interesting/relevant than the ionization potential of the C III ion (i.e., the photon energy needed to CREATE the C IV ion). Considering the ions producing strong lines in this spectral region, I would argue that the most noteworthy ionization potential is that of the N IV ion, ~78 eV, since it represents the highest photon energy needed to produce the ions that emit the observed emission lines in the spectral range of interest. Therefore, I would strongly recommend that the authors revise this paragraph to explain the physical significance of the ionization potentials in this particular context more clearly and to simplify the argument they make.

       	  We thank the referee for their very thoughtful notes on this
	  point. We have changed and updated the text with the comments above
	  taken into account.

(c) Table 1: This table is rather long-winded and includes a lot of atomic data that do not seem to be used anywhere in the paper, save for some of the ionization potentials mentioned in the 6th paragraph of section 1 (see my previous comment). I would recommend that this table be removed and any information from this table that is useful be included in the main text. In my opinion, as I argue above, the ionization energy of the N IV ion is the main number of interest to the discussion.

      	  We agree with this comment and to help the reader, we have
	  removed the (confusing) ``Ionization Potential'' column,
	  while adding a column to the table noting the "Production
	  Mechanism'' of each emission line. We have a (strong)
	  preference to retain this table, but leave it as a decision
	  to the Editor whether to do so.

2. CLQ Selection and Line Measurements

(a) In section 2.2, the authors describe how they selected the initial candidates using the CRTS light curves. I would recommend some additional explanations and clarifications of the selection process, as follows.

(i) I recommend expanding on the the sentence "This allowed us to predict the photometric magnitudes at the epochs of the SDSS spectra for each source." I presume that the damped random walk model was used to INTERPOLATE between adjacent points in the light cure. If so, it would be useful to state that explicitly. It would also be useful to note the uncertainty in this interpolation scheme; this uncertainty is important in developing a criterion for what is an outlier, as the authors do. I would recommend elaborating on this matter by explaining why the specific criterion of |DV| > 0.3 was adopted (by the way, what are the units? magnitudes?).

       We have added text here for clarification.

(ii) In the next sentence, what does "looking for at least a 50% change in magnitude between the two epochs" mean? I presume the authors looked for a fractional difference in FLUX, not MAGNITUDE (a 50% difference in magnitude is not a well-defined measure of variability).

     	Fixed.

(iii) Finally, I would suggest noting how many quasars were selected for visual inspection by the automatic algorithm before the three final candidates were identified.

        Text has been added here for additional explanation.

(b) Figure 1. -- I found this figure to be rather busy, packed with information, and difficult to read. I would recommend breaking it up into two separate figures, one including the light curves and one including the spectra. In the process of doing so, I would recommend that the authors write the names of the quasars in the corresponding panels and make the fonts considerably larger so that the labels are easier to read (especially the fonts in the sub-panels that zoom in on specific emission lines).

	  We have split the light curve and spectral figures up, have
	  increased the size of the fonts, and have writen the names
	  of the quasars in the approriate panels.

(c) At the very end of section 2.3 the authors note that they use photometric measurements to set the absolute scale of the non-SDSS spectra. It would be useful to note here the resulting uncertainty in flux calibration and whether this uncertainty was propagated into measurements of the continuum and emission lines from these spectra.

           A sentence has been added here.

(d) Table 3. -- This is an important table because it includes a great deal of useful information for the three high-z CLQs but it can be presented much better. I give here detailed recommendations about this table which are connected to and may duplicate comments I make in other parts of this report.
- I would recommend including in the text (perhaps in section 2.4) a brief discussion of how the uncertainties in the measured quantities were determined. If these uncertainties are estimated by QSfit, it would suffice to explain very briefly how that is done and refer the reader to the paper that described that code.

	 We have added a paragraph at the end of Section 2.4
      	 detailing how the uncertainties in the spectral line quantities
    	 are determined.

- Most of the measurements included in this table have too many significant figures. An example (albeit somewhat extreme) are the   properties of the C IV line measured from the MJD 56189 spectrum   (72.8+/-11.3, 14993+/-2400, 828+/-691, 162.89+/-25.37). The uncertainties in these numbers include 3-4 significant figures, which does not seem to be warranted. I would strongly recommend that the authors reconsider this issue very carefully, reduce the number of significant figures in the error bars, and truncate the significant figures in the measurements accordingly.

       	  We have rounded to the appropriate number of significant
       	  figures and decimal places in Table 3.

- It is not clear what is included in the the last column, entitled "virial product." According to the title it could be either the log of the luminosity and FWHM combination or the log of the black hole mass (but these are not the same thing). Incidentally, the term in \nu L_\nu should be written as (\nu L_\nu)^{0.5} (with parentheses). I recommend that the authors clarify what is going on and revise the   heading of this column, after reading my comment 3(c), where I elaborate further on this issue.

        The final column is in arbitrary units (not solar masses as
        originally written), with the purpose to check if this value
        varies significantly across epochs.

- The uncertainties in the virial product may have to be reconsidered or, at least, explained better. Please see my comment 3(d).

       We now note in the text that QSFit takes into account, and
       propagates accordingly, the uncertainties in the spectrum.

(e) The fonts in Figure 2 are very small and difficult to read. I recommend just scaling up the figure and making it occupy the full width of the page; the details and labels will be much easier to see and read that way.

    	      We've increased the font size for this figure.

3. Results

(a) In the 3rd and 4th paragraphs of section 3.1 I found a couple of sentences that are difficult to understand because they use terms that are either redundant or incompatible with each other. In the 3rd paragraph there is the phrase "... is very similar in shape and line flux intensity." I recommend changing this to "... is very similar in shape and intensity." In the 4th paragraph there is the phrase "...and the standard UV/blue continuum slope increases in flux." I recommend changing it to "...and the standard UV/blue continuum becomes stronger."

       	   These changes have been made.

(b) In the first paragraph of section 3.2 the authors note that they set E(B-V)=0 in the fitting process. Is this the reddening intrinsic to the quasar or does it also include the reddening in the Milky Way? I presume the latter is known and could (and should) be corrected.

       We have updated the results (Table 3) and figures (Figs 5, 6
       and 7) obtained by taking the Milky way extinction values for
       the three objects into account.

(c) Equation (1) in section 3.3. -- This equation, as written, appears to be wrong because the LHS is a log while the RHS is not and there should be constants or calibration factors to connect the black hole mass to the luminosity and FWHM combination. Moreover, the exponent of the luminosity is not exactly 0.5 according to empirical determinations. I would very strongly recommend that the authors correct this equation and revise the relevant discussion. Section 3.7 of the paper by Shen et al. (2011, cited just before equation 1) includes a detailed discussion of the calibration of this relation and several references to the original papers that report the calibration factors. I recommend that the authors begin by consulting that paper and then tracking down the most up-to-date calibration of equation (1), which should be the most appropriate calibration to use here (section 4 of Grier et al. 2019, ApJ, 887, 38 would be a good place to start in order to find the most up-to-date calibrations). The revised text should include appropriate references to the original papers reporting the calibration adopted by the authors.

   	We have added key additional text and references here.

(d) Related to the previous point, there is the issue of uncertainties. The authors note that typical uncertainties in the black hole mass are "~0.5 dex." Is this the uncertainty that applies to the virial product in the last column of Table 3?  Or is this the uncertainty in the mass based on the scatter of the M-sigma relation? I recommend that the authors clarify this issue by writing a footnote in Table 3 and giving appropriate references to the literature therein.

     	We have added the key additional text here.

(e) Table 4. -- The results reported in this table seem to have too many significant figures. Please see my comments related to Table 3 (item 2d, above).

    	  Fixed.

(f) The label on the y-axis of Figure 4 has a typographical error (apostrophe instead of "1").

    	  Fixed.

(g) There are out of place words in a couple of places in section 3.5 "The slope is \beta is −0.20,..." (the second "is" is superfluous) and "...from the three C iv CLQ quasars at each epoch..." (the word "quasars" is superfluous).

           Fixed and fixed.

4. Discussion

(a) I would recommend citing some representative papers to support the statement made in the first sentence of section 4.2 about the lag of the C IV line. The most appropriate papers are those dealing with quasars of comparable luminosity (and probably comparable redshift) as the quasars studied here. I am somewhat skeptical of this statement because the papers that I consulted (e.g., Grier et al. 2019 ApJ, 887, 38 and references therein) suggest that the lag between the C IV line and the continuum are of order 1-2 years, which places the C IV emitting region pretty far from the inner accretion disk.

      	    This text has been (significantly) updated.

(b) In the 2nd paragraph of section 4.2 the authors note "That is, the excitation of the C iv line is driven by the changes in the continuum; however, the excited gas cannot reach an equilibrium excitation state as quickly as the continuum changes,..." It took me a while to understand what the authors meant here. In the end I THINK they mean that the light-crossing time of the region that produces the C IV line is substantial, which translates into a delay between the variations of the continuum and the C IV line (and a smoothing of the light curve of the latter). I would strongly recommend that the authors expand this paragraph to make their point clear. I would also recommend citing relevant papers to support their statements (for example, Grier et al. 2019, ApJ, 887, 38 is recent, relevant paper but the authors should look for others too).

      	    This text has also been updated.

(c) In the second paragraph of section 4.3 the authors note that "However, one thing to note is that radiation pressure should be much more important in AGNs than in stellar mass black hole systems, implying that sound speed is much faster than expected from the gas temperature alone." (I presume this refers to the interior of the disk.) It is not obvious (at least not to me) that this statement is true. The importance of radiation pressure would, presumably, depend on the Eddington ratio and the ionization state of the disk. Perhaps at the temperatures of AGN disks a substantial fraction of metals retain their inner shell electrons, which increases the force multiplier because of bound-bound transitions hence the overall radiation pressure. But this consideration does not preclude a high radiation pressure in the disks of stellar-mass black holes because of other opacity sources.

At any rate, I would strongly recommend that the authors reconsider if this statement is essential to their argument. If it is, I would strongly recommend that they elaborate and clarify what they mean (after checking what is going on in the disks). If it is not, perhaps it can be deleted without affecting the argument.

       	     This statement is not required for our argument and
       	     discussion here, and as such has been deleted.

### 2020-06-09 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
Big update for the rv1 MNRAS submission

--- 2019-12-11 tex/CIV_CLQs.tex
@@
 The optical continuum variability of quasars was recognised since
-their first optical identifications
-\citep{MatthewsSandage1963}. %MacLeod2012}.  However, dramatic changes
-in the broad emission lines (BELs) of quasars was only recently first
-identified \citep{LaMassa2015}.  Samples of over 100 ``changing-look''
-quasars (CLQs) or ``changing-state'' quasars (CSQs) have now been
-assembled \citep[e.g.,][]{MacLeod2019, Graham2019b}. The community
-uses both these terms as a cover for the underlying physics. For sake
-of argument, CLQs can potentially be thought of as the extension to
-the BELs of quasar continuum variability \citep[e.g., ][]{MacLeod2012}
+their first optical identifications \citep{MatthewsSandage1963}. {\bf
+However, dramatic changes} in the broad emission lines (BELs) of
+quasars was only recently first identified \citep{LaMassa2015}.
+Samples of over 100 ``changing-look'' quasars (CLQs) or
+``changing-state'' quasars (CSQs) have now been assembled
+\citep[e.g.,][]{MacLeod2019, Graham2020}. The community uses both
+these terms as a cover for the underlying physics. For sake of
+argument, CLQs can potentially be thought of as the extension to the
+BELs of quasar continuum variability \citep[e.g., ][]{MacLeod2012}
 whereas the CSQs have a state-transition, perhaps similar to that seen
@@
   \begin{centering}
-    \begin{tabular}{l r  r r   lll lll  r r}
+    \begin{tabular}{l r  r    lll lll  r r r}
       \hline  \hline 
-      Line                 & $\lambda$ &  Transition  & Ionisation   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
-                              &  / \AA\    & Energy / eV &  Energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & / $10^{8}$ s$^{-1}$               \\      \hline
-      H LyLim           &   912.324   & 13.5984    & 13.5984        & 1$s$                    & $^2$S     & 1/2          & $\infty$                  &                                 &             & 109 678.7       & 1.23$\times10^{-6}$  \\
-      H Ly$\alpha$  &  1215.670  & 10.1988    & 13.5984       & 1$s$                     & $^2$S      & 1/2          & 2                             &                                 &             &  82 259.2       &  4.67  \\
-      \nv                  &  1238.821  & 10.0082    &  97.8901      &  1$s^{2}$2$s$      &  $^{2}$S   &  1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2    &  80 721.9        & 3.40   \\
-      \nv                  &  1242.804  &  9.9762     &  97.8901      &  1$s^{2}$2$s$       &  $^{2}$S   &  1/2        &  1$s^{2}$2$p$         &  $^{2}$P$^{{\rm o}}$ &  1/2     &  80 463.2        & 3.37 \\
-      \civ                 &  1548.187  &  8.0083     &  64.4935      &  1$s^{2}$2$s$       &   $^{2}$S  & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  3/2     &  64 591.7        & 2.65  \\
-      \civ                 &  1550.772  &  7.9950     &  64.4935      & 1$s^{2}$2$s$        &  $^{2}$S   & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  1/2     &   64 484.0       & 2.64  \\
-      \heii               &   1640.474  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  5/2        &  60 958.0       & 10.35 \\
-      \heii               &   1640.490  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  3/2        &  60 957.4       & 1.73 \\
-      \ciii                 &  1906.683  &  6.5026     & 47.8878       & 1$s^{2}$2$s^{2}$   &   $^{1}$S   & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &   2        &   52 447.1       & 5.19$\times10^{-11}$ \\
-      \ciii                 &  1908.734  &  6.4956     & 47.8878       & 1$s^{2}$2$s^{2}$   &  $^{1}$S    & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &  1         &  52 390.8        & 1.14$\times10^{-6}$  \\
-       \mgii              &  2795.528  &  4.4338     & 15.0353       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2     &  35 760.9       & 2.60  \\
-      \mgii               &  2802.705  &  4.4224     & 15.0353       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   1/2     &  35 669.3       & 2.57 \\
-      H Ba $\beta$   &  4861.333  &  2.5497     & 13.5984       & 2                              &                 &               & 4                             &                                 &              &  20 564.8       & 0.0842  \\
+      Line                 & $\lambda$ &  Transition   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                             & Physical             \\
+                              &  / \AA\    & Energy / eV    &    \multicolumn{3}{l}{Lower; Conf., Term, J }    &  \multicolumn{3}{l}{Upper; Conf., Term, J}                                                         & / cm$^{-1}$    & / $10^{8}$ s$^{-1}$           &  Mechanism  \\      \hline
+      H LyLim           &   912.324   & 13.5984       & 1$s$                    & $^2$S     & 1/2          & $\infty$                  &                                 &             & 109 678.7       & 1.23$\times10^{-6}$   & Ionisation \\
+      H Ly$\alpha$  &  1215.670  & 10.1988       & 1$s$                     & $^2$S      & 1/2          & 2                             &                                 &             &  82 259.2       &  4.67  & Recombination \\
+      \nv                  &  1238.821  & 10.0082       &  1$s^{2}$2$s$      &  $^{2}$S   &  1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2    &  80 721.9        & 3.40  & Collisional Ex.
+\\
+      \nv                  &  1242.804  &  9.9762       &  1$s^{2}$2$s$       &  $^{2}$S   &  1/2        &  1$s^{2}$2$p$         &  $^{2}$P$^{{\rm o}}$ &  1/2     &  80 463.2        & 3.37 & Collisional Ex.
+\\
+      \civ                 &  1548.187  &  8.0083       &  1$s^{2}$2$s$       &   $^{2}$S  & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  3/2     &  64 591.7        & 2.65  &Collisional Ex.
+\\
+      \civ                 &  1550.772  &  7.9950       & 1$s^{2}$2$s$        &  $^{2}$S   & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  1/2     &   64 484.0       & 2.64  &Collisional Ex.
+\\
+      \heii               &   1640.474  &  7.5578        & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  5/2        &  60 958.0       & 10.35& Recombination \\
+      \heii               &   1640.490  &  7.5578        & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  3/2        &  60 957.4       & 1.73 &  Recombination \\
+      \heii               &   1640.533  &  7.5576        & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$s$ 	                 & $^2$S                  &  1/2        &  60 957.4       & 0.68 &  Recombination \\
+      \ciii                 &  1906.683  &  6.5026       & 1$s^{2}$2$s^{2}$   &   $^{1}$S   & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &   2        &   52 447.1       & 5.19$\times10^{-11}$ &Collisional  Ex.
+\\
+      \ciii                 &  1908.734  &  6.4956       & 1$s^{2}$2$s^{2}$   &  $^{1}$S    & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &  1         &  52 390.8        & 1.14$\times10^{-6}$  &Collisional Ex.
+\\
+       \mgii              &  2795.528  &  4.4338       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2     &  35 760.9       & 2.60  &Collisional Ex.\\
+      \mgii               &  2802.705  &  4.4224       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   1/2     &  35 669.3       & 2.57 & Collisional Ex.\\
+      H Ba $\beta$   &  4861.333  &  2.5497       & 2                              &                 &               & 4                             &                                 &              &  20 564.8       & 0.0842 &  Recombination\\
       \hline   
@@
       Strong UV/optical spectral emission lines in quasars, and their
-      atomic data from the NIST Atomic Spectra Database
+      atomic data from the \href{https://physics.nist.gov/PhysRefData/ASD/lines_form.html}{NIST Atomic Spectra Database} 
       \citep{Kramida2018, Kramida2019}.  The transition energies are
-      $E=hc/\lambda$ for the given wavelength. The ionisation energy is the
-      energy required to ionise the given species, e.g., 64.49 eV is needed
-      to create a \cv\ ion.  Transition level configurations are given in
-      standard spectroscopic notation, with $A_{i,j}$ denoting the transition
-      probabilities.}
+      $E=hc/\lambda$ for the given wavelength. Transition level configurations are given in
+      standard spectroscopic notation (as Configuration, Term and quantum J number) with $A_{i,j}$ denoting the transition
+      probabilities.
+      {\bf The physical mechanism for the generation of the emission lines
+        e.g., full ionization, collisionally excitation (``Collisional Ex.'' in the rable) or recombination are also given in
+      the last column.}
+    }
     \label{tab:atomic_lines}
@@
 \end{table*}
+
+\iffalse
+\begin{table}
+  \begin{centering}
+    \begin{tabular}{l r}
+      \hline
+      \hline
+      Transition & Energy Required \\
+                      &   / eV (Ryd)\\
+     \hline
+     \ciii $\rightarrow $ \civ  & 47.89     (3.52) \\
+      \civ   $\rightarrow $ \cv &  64.49   (4.74) \\
+      \cv  $ \rightarrow $ \cvi & 392.09   (28.8) \\
+      \niii $\rightarrow $ \niv  & 47.44  (3.49) \\
+	\niv $\rightarrow $ \nv &  77.47  (5.69)  \\
+      \nv $\rightarrow $ \nvi  &  97.89   (7.19) \\
+            \hline
+      \hline
+    \end{tabular}
+    \caption{Ionisation Energies for Carbon and Nitrogen.
+	These are the energies that are needed to go 
+	from the species on the left and create the ion on the right. }
+  \end{centering}
+\end{table}
+\fi
 
@@
 spectroscopy. Recent works report on discoveries of \mgii\ changing-look
-AGN \citep{Guo2019, Homan2019}. However, current CLQ studies have
+AGN \citep{Guo2019, Homan2020}. However, current CLQ studies have
 primarily been at redshifts $z<1$.
@@
 \citep{Baldwin1977, Bian2012, Jensen2016,
-Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
+Hamann2017}. As noted in \citet{Rakic2017}, two different
 types of Baldwin effect are present in the literature: {\it (i)} the {\it
@@
 anti-correlation between the emission line equivalent width and the
-underlying continuum luminosity of {\it single-epoch} observations of
-a {\it large number} of AGN, and {\it (ii)} the {\it intrinsic} Baldwin
-effect, the same anti-correlation but in an {\it individual, variable}
-AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
+underlying continuum luminosity of single-epoch observations of
+a large number of AGN, and {\it (ii)} the {\it intrinsic} Baldwin
+effect, the same anti-correlation but in an individual, variable 
+AGN \citep{PoggePeterson1992}. The ensemble and intrinsic Baldwin effect 
+has been observed in the \civ\ broad absorption line quasar population,
+However, dramatic changes in the 
 collisionally excited broad {\it emission} line of \civ\ --- and
@@
 
-Details of the atomic transitions that produce strong rest-frame
-UV/optical lines in quasars are given in
-Table~\ref{tab:atomic_lines}. In this paper we use the wavelengths of
-1548.202 and 1550.774~\AA\ for the \civ\ doublet
-\citep{Kramida2018}. For ionisation energies, 47.89 eV (3.519 Ry) is
-required for doubly-ionised C\,{\sc iii} to become triply-ionised
-\civ, and 64.49 eV (4.74 Ry) is needed to ionise \civ\ itself. This
-energy corresponds to a thermal temperature of $T \gtrsim$
-4$\times10^{5}$ K, implying a heating energy source of (soft) X-ray
-photons.
+{\bf 
+ Most of the strong lines in the rest-frame near-UV spectrum of quasars are
+collisionally excited, including C\,{\sc iii}, C\,{\sc iv} and N\,{\sc
+v}.  The \heii~$\lambda$1640 recombination line is among the exceptions.
+
+Photoionization followed by recombination determines the ionization
+level of carbon, and collisional excitation from the ground level of
+\civ\ determines the line intensity. Other processes do happen,
+(including radiative and three body recombination to the upper level
+of the transition), but they are much slower unless the density is
+extremely high \citep[e.g., ][and H. Netzer,
+priv. comm.]{Dopita_Sutherland2003book}. The ionization potential of C\,{\sc
+iii} ion is 47.89 eV (3.519 Ry) and thus a photon with this energy
+($k_{\rm B} T \sim 5 \times10^{5}$ K) can create the triply ionised,
+\civ\ ion. Once the \civ\ ion is formed, collisional excitation leads to
+the production of the 1548.202 and 1550.774~\AA\ \civ\ doublet.
+}
+%%
+Details of the atomic transitions and physical mechanisms that produce
+strong rest-frame UV/optical lines in quasars are given in
+Table~\ref{tab:atomic_lines}.
 
@@
 involving the \civ\ emission line: {\it (i)} the anti-correlation
-between the \civ\ equivalent width (EW) and luminosity (i.e., the
+between the \civ\ equivalent width (EW) and luminosity (i.e., the global 
 Baldwin effect) and {\it (ii)} the blueshifting of the peak of \civ\
@@
 emission line is nearly ubiquitous, with a mean shift of $\langle
-V_{\rm off}\rangle_{\rm RQ} \sim$810 km s$^{-1}$ for radio-quiet (RQ)
-quasars and $\langle V_{\rm off}\rangle_{\rm RL} \sim$360 km s$^{-1}$
+V_{\rm off}\rangle \sim$810 km s$^{-1}$ for radio-quiet (RQ)
+quasars and $\langle V_{\rm off}\rangle \sim$360 km s$^{-1}$
 for radio-loud (RL) objects. \citet{Richards2011} also find the
@@
 redshift. While accessing this phenomenon at an earlier cosmic epoch
-is somewhat interesting, the main value of this study is to move from
+is interesting, the main value of this study is to move from
 the low-ionisation energy Balmer emission line series at rest-frame
@@
 \section{CLQ Selection and Line Measurements}
+{\bf A statistical search using optical light curves to initiate spectroscopic follow-up
+  observations is proving an efficient CLQ finder, and by design
+our data sources and overall methodology, are in common to the recent
+\citet{Ross2018}, \citet{Stern2018} and \citet{Graham2020} papers.
+}
+%
 In this section we present the photometric data used to select the
-CLQs, and then give details to the multiwavelength data where we have
-it. We then give details of the spectroscopic data including emission
+CLQs and give details of the multiwavelength data where we have it.
+{\bf We use data from the Catalina Real-time Transient Survey, PanSTARRS,
+  the Zwicky Transient Facility, the WISE mission and SDSS.}
+We then give details of the spectroscopic data including emission
 lines measurements.
@@
 data set contains time series for approximately 400 million sources to
-$V \sim 20$ above Dec $> -30$ from 2003 to 2016 May (observed with CSS
-and MLS) and 100 million sources to $V \sim 19$ in the southern sky
+$V \sim 20$ above Declination $\delta > -30$deg from 2003 to 2016 May (observed with CSS
+and MLS) and 100 million sources to $V \sim 19$ in the Southern sky
 from 2005 to 2013 (from SSS). CRTS has been extensively used to study 
 quasar variability \citep[e.g.,][]{Graham2014, Graham2015, Graham2015Nature,
-Graham2017, Graham2019b, Stern2017, Stern2018, Ross2018}.
+Graham2017, Graham2020, Stern2017, Stern2018, Ross2018}.
 
 PanSTARRS data is obtained via the Pan-STARRS Catalog Search
-interface\footnote{https://catalogs.mast.stsci.edu/panstarrs/}.  We
-query the PS1 DR2 Detection catalog.
+interface\footnote{https://catalogs.mast.stsci.edu/panstarrs/}.
+Specifically, we query the PS1 DR2 Detection catalog.
 
@@
 robotic time-domain sky survey capable of visiting the entire visible
-sky north of $-$30 declination every night. ZTF observes the sky in
+sky north of $-$30 deg declination every night. ZTF observes the sky in
 the $g$, $r$, and $i$-bands at different cadences depending on the
@@
   %% trim=l b r t
-  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
-  {figures/J1205+3422_landscape_20191211.png}
-  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
-  {figures/J1638+2827_landscape_20191112.png}
-  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
-  {figures/J2228+2201_landscape_20191112.png}
-  \vspace{-12pt}
-  \caption[]{The three high-redshift CLQ quasars; 
+  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.20cm 0.1cm, clip]
+  {figures/J1205+3422_landscape_LC.png}
+  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.20cm 0.1cm, clip]
+  {figures/J1638+2827_landscape_LC.png}
+  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.20cm 0.1cm, clip]
+  {figures/J2228+2201_landscape_LC.png}
+  \vspace{-6pt}
+  \caption[]{The light curves for the three high-redshift CLQ quasars; 
     J1205+3422 (top), 
@@
     J2228+2201 (bottom). 
-    The light curve data are presented in the panels on the left hand side, with the timing of the
-    spectral observations indicated with vertical dashed lines. 
-    The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
-    complex, the \civ\ line, and the \mgii\ line.}
-  \label{fig:civ_clqs}
+    The timing of the spectral observations are indicated with vertical dashed lines.}
+  \label{fig:civ_clqs_LCs}
 \end{figure*}
@@
 
+\begin{figure*}
+  \centering
+  %% trim=l b r t
+  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.30cm 0.1cm, clip]
+  {figures/J1205+3422_landscape_spectra.png}
+  \vspace{-12pt}
+  \caption[]{The three epochs of spectra for SDSS  J1205+3422.
+    The full wavelength spectrum is presented in the top panel, 
+    with zoom-in's on the Ly$\alpha$-\nv 
+    complex, the \civ\ line, and the \mgii\ line in the lower panels}
+  \label{fig:civ_clqs_J12_spec}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  %% trim=l b r t
+  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.30cm 0.1cm, clip]
+  {figures/J1638+2827_landscape_spectra.png}
+  \vspace{-12pt}
+  \caption[]{As Figure~\ref{fig:civ_clqs_J12_spec} but for  J1638+2827.}
+  \label{fig:civ_clqs_J16_spec}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  %% trim=l b r t
+  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.30cm 0.1cm, clip]
+  {figures/J2228+2201_landscape_spectra.png}
+  \vspace{-12pt}
+  \caption[]{As Figure~\ref{fig:civ_clqs_J12_spec} but for   J2228+2201.}
+  \label{fig:civ_clqs_J22_spec}
+\end{figure*}
+
 \subsection{CLQ Selection}
+{\bf As this is the first time high-redshift CLQs have been studied,
+defining a formal and automatic process is not an trivial task.  Hence
+we focused on a method and threshold which selects the most promising
+candidates, with no claim of completeness, in a number suitable to be
+inspected visually.}
+
 Our high-redshift CLQs were identified as follows.  We selected all
@@
 \href{https://gpy.readthedocs.io/en/deploy/}{GPy Python} library).
-This allowed us to predict the photometric magnitudes at the epochs of
-the SDSS spectra for each source.  Those with $|\Delta V| > 0.3$ were
-then selected for visual inspection, looking for at least a 50\%
-change in magnitude between the two epochs.  Only three quasars, SDSS
+{\bf This allowed us to predict the photometric magnitudes and their
+uncertainties at the epochs of the SDSS spectra for each source
+\citep[see][]{Rasmussen_Williams2006}.}
+%%
+Candidate objects with $|\Delta V| > 0.3$ magnitude were then selected
+for visual inspection, {\bf looking for at least a 33\% change in flux
+between the two epochs. Approximately 1\% of quasars should show this
+level of significant variability over the timescales considered
+\citep{Graham2017}.}
+
+Only three quasars, SDSS
 J120544.7+342252.4 (hereafter J1205+3422), SDSS J163852.93+282707.7
@@
 spectrophotometric standards observed on the same nights.
+{\bf We note the resulting uncertainty in flux calibration is 2-5\%.
+  This uncertainty is not propagated into measurements. 
+}
 
@@
 
+{\bf As described in detail in \citet{Calderone2017}, the
+uncertainties in the measured quantities are determined by two
+methods; a Fisher matrix method and a Monte Carlo resampling method.
+Due to correlations among model parameters, e.g. emission-line
+luminosities and widths, the Fisher matrix method likely
+underestimates the errors.  However, upon investigation, the
+parameters of the involved model components (a power-law for the
+continuum, and a single Lorentzian profile for the emission lines)
+show negligible correlations, hence we use the Fisher matrix method
+to estimate the uncertainties on the model parameters.  Section 2.8.3
+and Appendix B4 of \citet{Calderone2017} gives further details and
+compares the Fisher matrix and Monte Carlo resampling uncertainties
+and distributions.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Photometric and Overall Spectral Evolution}
-Figure~\ref{fig:civ_clqs} presents the optical and mid-infrared light
-curves for three high-redshift CLQ quasars.  Figure~\ref{fig:civ_clqs}
+Figure~\ref{fig:civ_clqs_LCs} presents the optical and mid-infrared light
+curves for three high-redshift CLQ quasars.  Figure~\ref{fig:civ_clqs_LCs}
 also indicates the spectra for each epoch with vertical dashed lines
@@
 
+Figure~\ref{fig:civ_clqs_J12_spec} shows the rest-frame spectra for SDSS J1205+3422.
 For J1205+3422, our spectral observations cover 5195 observed days,
@@
 18.0$, blue-sloped quasar with broad Si\,{\sc iv}/O\,{\sc iv}, \civ,
-\ciii, and \mgii. \ciii\ and \civ\ have large blueshifts,
-$\approx$2600$\pm$150 and $\approx$1150$\pm$100 km s$^{-1}$,
+C\,{\sc iii}, and Mg\,{\sc ii}. \ciii\ and \civ\ have large
+blueshifts, $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km s$^{-1}$,
 respectively.  By 2019, however, the optical brightness dropped by
@@
 
+Figure~\ref{fig:civ_clqs_J16_spec} shows the rest-frame spectra for SDSS J1638+2827.
 For J1638+2827, our spectral observations cover 4030 observed days,
 corresponding to 1265 days in the rest-frame. Here, in the initial
-epoch spectrum, \civ\ is broad and bright, as is \ciii. However,
-$\approx$400 rest-frame days later, the broad \civ\ and \ciii\
-emission lines have faded, the continuum slope around 1400\AA\ has
-changed from $\approx-1.48$ to $\approx-2.25$, but the \lya/\nv
-emission complex is very similar in shape and line flux
-intensity. Around 870 days in the rest-frame after the second spectral
-epoch, at the time of the third spectral epoch, the source has
-brightened from optical magnitudes of $\sim 20$ mag to $\sim 18.5$
-mag. Ly$\alpha$, N\,{\sc v}, \civ, \ciii, and \mgii\ are all apparent
-and broad, with \mgii\ being seen for the first time at high
-signal-to-noise. An absorption feature between \lya and \nv is seen in
-all three spectral epochs.
-
+epoch spectrum, \civ\ is broad and bright, as is C\,{\sc
+iii}. However, $\approx$400 rest-frame days later, the broad \civ\ and
+\ciii\ emission lines have faded, the continuum slope around 1400\AA\
+has changed from $\approx-1.48$ to $\approx-2.25$, but the \lya/\nv
+emission complex is very similar in shape {\bf and intensity}. Around
+870 days in the rest-frame after the second spectral epoch, at the
+time of the third spectral epoch, the source has brightened from
+optical magnitudes of $\sim 20$ mag to $\sim 18.5$ mag. Ly$\alpha$,
+N\,{\sc v}, \civ, \ciii, and \mgii\ are all apparent and broad, with
+\mgii\ being seen for the first time at high signal-to-noise. An
+absorption feature between \lya and \nv is seen in all three spectral
+epochs.
+
+Figure~\ref{fig:civ_clqs_J22_spec} shows the rest-frame spectra for SDSS J2228+2201.
 For J2228+2201, our spectral observations cover 2504 observed days,
 corresponding to 778 days in the rest-frame. Over the course of 240
-rest-frame days, \civ\ and \ciii\ both {\it emerge} as BELs and the
-standard UV/blue continuum slope increases in flux.  Then, over the
+rest-frame days, \civ\ and \ciii\ both {\it emerge} as BELs and {\bf the
+standard UV/blue continuum becomes stronger.}  Then, over the
 course of 538 days in the rest-frame, the broad emission, while still
@@
 rest-frame 1450\AA, \civ\ line luminosity, FWHM, and EW are given in
-Table~\ref{tab:QSFit-results}. All fits are performed with $E(B-V) =
-0$ and the best fit models in the region of the \civ\ emission line
-are shown in Figure~\ref{fig:QSFit-CIV}.
+Table~\ref{tab:QSFit-results}.
+{\bf 
+All fits are obtained by taking the Milky Way extinction
+\citep{Schlafly2011} into account.  The extinction values are: $E(B-V)
+=0.013$ for J1205+3422; $E(B-V) =0.034$ for J1638+2827 and $E(B-V)
+=0.041$ for J2228+2201.  as taken from NED (e.g. for
+\href{http://ned.ipac.caltech.edu/cgi-bin/objsearch?search_type=Near+Position+Search&in_csys=Equatorial&in_equinox=J2000.0&lon=12%3A05%3A44.7&lat=%2B34%3A22%3A52.4&radius=0.1&hconst=73&omegam=0.27&omegav=0.73&corr_z=1&z_constraint=Unconstrained&z_value1=&z_value2=&z_unit=z&ot_include=ANY&nmp_op=ANY&out_csys=Equatorial&out_equinox=J2000.0&obj_sort=Distance+to+search+center&of=pre_text&zv_breaker=30000.0&list_limit=5&img_stamp=YES#GalacticExtinction_0}{J1205+3422}).
+}
+The best fit models
+in the region of the \civ\ emission line are shown in
+Figure~\ref{fig:QSFit-CIV}.
 
@@
   \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_MBHvsREW_20191211.png}
+  {figures/CIV_CLQs_MBHvsREW_20200519.png}
    \vspace{-12pt}
@@
 mass'' estimate is then expressed as:
+{\bf
 \begin{equation}
-  \log(M_{\rm BH}) = (\nu L_{\nu})^{\gamma} \times ({\rm FWHM})^{\delta}
+    \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}. 
 \end{equation}
-where $\gamma=0.5$ and $\delta=2$.  The virial product for the \civ\
+\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as 0.660, 
+which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
+\citet{Kozlowski2017} calculate $\gamma=0.53$ and the offset as 0.64. 
+\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
+$z>1.3$ quasars that show significant lag measurements,
+and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
+their highest-confidence objects. }
+
+The virial product for the \civ\
 CLQs is reported in the last column of Table~\ref{tab:QSFit-results}.
-The uncertainty typically associated with single-epoch mass estimates
-is $\sim 0.5$~dex, implying that the virial products for our three
+{\bf Here, since our purpose is to check if this measurement varies significantly
+across epochs, we use $\gamma=0.5$ as the power-law slope and
+are not directly concerned with the offset.
+%%
+ The quoted uncertainties account only for the propagation of uncertainties in the continuum luminosities and line widths.
+However, typical uncertainties associated to single epoch virial mass are $\sim$~0.5 dex, hence} implying that the virial products for our three
 high-redshift CLQs are all remarkably constant and compatible with
@@
 \civ\ EW versus the virial SMBH masses for our multi-epoch
-observations to a sample of $\approx 20,000 z>1.5$ SDSS quasars from
+observations to a sample of $\approx$20,000 $z>1.5$ SDSS quasars from
 the QSFit catalog \citep{Calderone2017}.
@@
   \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_REWvsFWHM_20191211.png}
+  {figures/CIV_CLQs_REWvsFWHM_20200519.png}
   \vspace{-12pt}
@@
   \vspace{-12pt}
-  \caption{Temporal evolution of the spectral properties of the three
-    quasars considered in this work.}
+  \caption{
+    Temporal evolution of the spectral properties of the three quasars
+    considered in this work (see Table 3).  The third row show the
+    logarithmic virial product with two error bars: the propagated
+    uncertainties for the $(\nu L_{\nu})^{0.5} \times {\rm FWHM}^2$
+    estimates (red) and the typical uncertainty associated to single epoch
+    virial masses (0.5 dex, black).}
   \label{fig:QSFit-results}
@@
     \hline
-                     & 53498 & 47.216     &  $-$0.610   \\
- J1205+3422 & 58538 &  46.070    &   $-$1.756  \\   %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
-                     & 58693 &  46.567    &  $-$1.259  \\                    
-    \hline 
-                     & 54553 & 46.166   & $-$1.025  \\
-J1638+2827  & 55832 & 45.981   & $-$1.210  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
-                     & 58583 & 46.504   & $-$0.687   \\
-    \hline 
-                     & 56189  & 46.231  &  $-$1.235 \\
-J2228+2201  & 56960 & 47.342  & $-$0.124  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
-                     & 58693 & 46.826   &  $-$0.640 \\
+                     & 53498 & 47.22     &  $-$0.61   \\
+ J1205+3422 & 58538 &  46.07    &   $-$1.76  \\   %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
+                     & 58693 &  46.57    &  $-$1.26  \\                    
+    \hline 
+                     & 54553 & 46.17   & $-$1.03  \\
+J1638+2827  & 55832 & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
+                     & 58583 & 46.50   & $-$0.69   \\
+    \hline 
+                     & 56189  & 46.23  &  $-$1.24 \\
+J2228+2201  & 56960 & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
+                     & 58693 & 46.83   &  $-$0.64 \\
     \hline
@@
   \centering
-  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_Baldwin_20191211.png}
+  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]{figures/CIV_CLQs_Baldwin_20200519.png}
    \vspace{-12pt}
@@
      are from Table~\ref{tab:QSFit-results}.  Symbols as in
-     Figure~\ref{fig:CIV_MBHvsREW}.  The dashed red line has slope
-     $\beta=-0.38$.}
+     Figure~\ref{fig:CIV_MBHvsREW}.
+     % The dashed red line has slope     $\beta=-0.38$.
+   }
   \label{fig:CIV_Baldwin}
@@
 Figure~\ref{fig:CIV_Baldwin} shows this for a sample of 20,374 quasars
-from the QSFit catalogue \citep{Calderone2017}.  The slope is $\beta$
-is $-0.20$, consistent with \citet[][ $\beta=-0.25$, but for
-bolometric luminosity rather than rest-frame UV continuum luminosity]
+from the QSFit catalogue \citep{Calderone2017}.  The slope is $\beta=
+-0.20$, consistent with \citet[][ $\beta=-0.25$, but for bolometric
+luminosity rather than rest-frame UV continuum luminosity]
 {Kozlowski2017} and with \citet[][ $\beta=-0.23$]{Hamann2017}.
 
-We add the measurements from the three \civ\ CLQ quasars at each epoch
+We add the measurements from the three \civ\ CLQ at each epoch
 to Figure~\ref{fig:CIV_Baldwin}. All three quasars at all three epochs
@@
 {\it intrinsic} Baldwin effect \citep[e.g.,][]{Goad2004, Rakic2017}.
-Subject to small number statistics, the slope of the intrinsic Baldwin
-effect for these three high-redshift \civ\ CLQs is somewhat steeper
-than the population trends, with $\beta \approx-0.38$, shown by the
-dashed red line in Figure~\ref{fig:CIV_Baldwin}.
+%% Subject to small number statistics, the slope of the intrinsic Baldwin effect for these three high-redshift \civ\ CLQs is somewhat steeper than the population trends, with $\beta \approx-0.38$, shown by the dashed red line in Figure~\ref{fig:CIV_Baldwin}.
 
@@
 
-Using the same dataset as \citet{MacLeod2019}, \citet{Homan2019}
+Using the same dataset as \citet{MacLeod2019}, \citet{Homan2020}
 investigate the responsiveness of the \mgii\ broad emission line
@@
 quasars that show large changes in their optical light-curves,
-\citet{Homan2019} find that \mgii\ clearly does respond to the
-continuum.  However, a key finding from \citet{Homan2019} is that the
+\citet{Homan2020} find that \mgii\ clearly does respond to the
+continuum.  However, a key finding from \citet{Homan2020} is that the
 degree of responsivity varies strikingly from one object to another.
@@
 
-\citet{Graham2019b} report the largest number of H$\beta$ CLQs to
-date, with a sample of 111 sources identified. \citet{Graham2019b}
+\citet{Graham2020} report the largest number of H$\beta$ CLQs to
+date, with a sample of 111 sources identified. \citet{Graham2020}
 find that this population of extreme varying quasars, referred to as
@@
 The \civ\ line is one of the strongest collisionally excited lines in
-quasar spectra \citep[e.g.,][]{HamannFerland1999}, and \civ\ emission
-probes the photoionisation environment produced by the innermost disk,
+quasar spectra \citep[e.g.,][]{HamannFerland1999}.
+{\bf Early measurements from e.g., 
+  \citet{PoggePeterson1992} and \citet{Peterson1997book}, 
+  using the well-studied Seyfert galaxy NGC 5548,
+  suggested the location of \civ\ emission was 
+%  probes the photoionisation environment
+  produced by the innermost disk, with the line emission
+  responding to the underlying continuum emission in only
+  a matter of $\sim$ 8 days. 
 as indicated by reverberation mapping time-delay measurements.
+%{\bf (a) I would recommend citing some representative papers to support the statement made in the first sentence of section 4.2 about the lag of the C IV line.
+The most appropriate papers are those dealing with quasars of comparable luminosity (and probably comparable redshift) as the quasars studied here.
+I am somewhat skeptical of this statement because the papers that I consulted.}
+However, more recent measurements from e.g. \citet[][and references therein]{Grier2019},
+suggest that the lag between the \civ\ line and the continuum are of order $>100$ observed-frame days. 
+which would place the \civ emitting region far from the inner accretion disk.
+Importantly, many quasars in the \citet{Grier2019} sample are of
+comparable redshift and luminosity to SDSS J1205+3422, J1638+2827, and J2228+2201.}
 
@@
 comfortably along a line, implying their variation is consistent with
-an intrinsic Baldwin effect (see Figure~\ref{fig:CIV_Baldwin}). That
-is, the excitation of the \civ\ line is driven by the changes in the
-continuum; however, the excited gas cannot reach an equilibrium
-excitation state as quickly as the continuum changes, making the slope
-of the intrinsic Baldwin effect greater than that of the overall
-ensemble slope, which is derived from many single-epoch observations,
-the majority of which are assumed to be in equilibrium.
+an intrinsic Baldwin effect (see Figure~\ref{fig:CIV_Baldwin}).
+%%
+{\bf The light-crossing time of the region that produces the \civ\ line is substantial,
+which translates into a delay between the variations of the continuum and
+the \civ\ line, and a smoothing of the light curve of the latter.
+%%
+Thus, if the excitation of the \civ\ line is driven by the changes in the
+continuum, the excited gas cannot reach an equilibrium
+excitation state as quickly as the continuum changes.}
+This makes the slope of the intrinsic Baldwin effect greater than that
+of the overall ensemble slope, which is derived from many single-epoch
+observations, the majority of which are assumed to be in equilibrium.
+{\bf \citet{Grier2019}, }
 
@@
   \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/MJD_vs_Eddington_20191211.png}
+  {figures/MJD_vs_Eddington_20191211}
   \vspace{-12pt}
@@
 connection between state changes in Galactic binaries and CLQs.
-However, one thing to note is that radiation pressure should be much
-more important in AGNs than in stellar mass black hole systems,
-implying that sound speed is much faster than expected from the gas
-temperature alone.  In Galactic binaries spectral hardening
+%
+In Galactic binaries spectral hardening
 corresponds to the soft-to-hard state transition in black hole
@@
 \section*{Acknowledgements}
-We thank Andy Lawrence, Mike Hawkins and David Homan for useful discussion.
+We thank: \\
+\begin{itemize}
+\item Andy Lawrence, Mike Hawkins and David Homan for useful discussion;
+\item the referee for a very constructive report that improved the paper;
+\end{itemize}
 NPR acknowledges support from the STFC and the Ernest Rutherford Fellowship scheme.
-%% KESF \& BM are supported by NSF PAARE AST-1153335. 
-%% KESF \& BM thank Caltech/JPL for support during sabbatical.
+% KESF \& BM are supported by NSF PAARE AST-1153335. 
+% KESF \& BM thank Caltech/JPL for support during sabbatical.
 MJG is supported in part by the NSF grants AST-1815034, and the NASA grant 16-ADAP16-0232.
-\\
 
@@
 \citep{AstropyCollaboration2013, AstropyCollaboration2018}.
+\href{https://pylustrator.readthedocs.io/en/latest/}{\tt pylustrator} \citep{Gerum2019} was also used.
 
@@
 
+%NPR dedicates this work, and indeed his previous research to his father.
+Dad had a deep love for science, mathematics and questioning the conventional wisdom.
+His support allowed me to become an astrophysicist and to have the adventures and discoveries we did.
+He is sorely missed.
+
 \bibliographystyle{mnras}

### 2020-06-12 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
updating CIV_CLQs_rv1

@@
 high-redshift of our quasars, \oiii is not available to us to use for
-scaling the spectra.  Instead, we use photometric data from ZTF since
-our Palomar and Keck data were all taken after MJD 57500.  This
+scaling the spectra.  Instead, we use photometric data from the ZTF
+since our Palomar and Keck data were all taken after MJD 57500.  This
 provides broad-band photometry at the time of the spectroscopy, which
 we use to scale the spectra whose initial calibration is based on
-spectrophotometric standards observed on the same nights.
-{\bf We note the resulting uncertainty in flux calibration is 2-5\%.
-  This uncertainty is not propagated into measurements. 
-}
+spectrophotometric standards observed on the same nights.  {\bf We
+note the resulting uncertainty in flux calibration is 2-5\%.  This
+uncertainty is not propagated into measurements.}
 
 \subsection{Emission Line and Power-law Slope Measurements}
-We use the measured quasar emission line properties from several catalogues: 
-\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017}, and
-\citet{Calderone2017}.
+We use the measured quasar emission line properties from several
+catalogues: \citet{Shen2011}, \citet{Hamann2017},
+\citet{Kozlowski2017}, and \citet{Calderone2017}.
 
@@
 package presented in \citet{Calderone2017}. This provides luminosity
-estimates as well as width, velocity offset and EW of 20 emission
-lines, including \civ, \ciii, and \mgii.  We process and fit all nine
-spectra using the lastest version (v1.3.0) of the QSFit
+estimates as well as width, velocity offset and EWs of 20 emission
+lines, including \civ, \ciii, and {Mg\,{\sc ii}}. We process and fit
+all nine spectra (3 quasars with 3 epochs) using the lastest version
+(v1.3.0) of the QSFit
 \href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
@@
 
-{\bf As described in detail in \citet{Calderone2017}, the
-uncertainties in the measured quantities are determined by two
-methods; a Fisher matrix method and a Monte Carlo resampling method.
-Due to correlations among model parameters, e.g. emission-line
-luminosities and widths, the Fisher matrix method likely
-underestimates the errors.  However, upon investigation, the
-parameters of the involved model components (a power-law for the
-continuum, and a single Lorentzian profile for the emission lines)
-show negligible correlations, hence we use the Fisher matrix method
-to estimate the uncertainties on the model parameters.  Section 2.8.3
-and Appendix B4 of \citet{Calderone2017} gives further details and
-compares the Fisher matrix and Monte Carlo resampling uncertainties
-and distributions.}
+{\bf As described in \citet{Calderone2017}, the uncertainties in the
+measured quantities are determined by two methods; a Fisher matrix
+method and a Monte Carlo resampling method.  One might expect
+correlations among model parameters, e.g. emission-line luminosities
+and widths, and thus the Fisher matrix method to underestimates the
+errors.  However, upon investigation, the parameters of the involved
+model components (a power-law for the continuum, and a single
+Lorentzian profile for the emission lines) show negligible
+correlations, hence we use the Fisher matrix method to estimate the
+uncertainties on the model parameters.  Section 2.8.3 and Appendix B4
+of \citet{Calderone2017} gives further details and compares the Fisher
+matrix and Monte Carlo resampling uncertainties and distributions.}
 
@@
 Figure~\ref{fig:civ_clqs_LCs} presents the optical and mid-infrared light
-curves for three high-redshift CLQ quasars.  Figure~\ref{fig:civ_clqs_LCs}
-also indicates the spectra for each epoch with vertical dashed lines
-in the light curves.
-
-Figure~\ref{fig:civ_clqs_J12_spec} shows the rest-frame spectra for SDSS J1205+3422.
-For J1205+3422, our spectral observations cover 5195 observed days,
-corresponding to 1691 days in the rest-frame. This quasar was
-initially identified in SDSS in 2005 May as a bright, $g \approx
-18.0$, blue-sloped quasar with broad Si\,{\sc iv}/O\,{\sc iv}, \civ,
-C\,{\sc iii}, and Mg\,{\sc ii}. \ciii\ and \civ\ have large
-blueshifts, $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km s$^{-1}$,
-respectively.  By 2019, however, the optical brightness dropped by
-nearly 2 magnitudes and the spectra are significantly less blue.  \lya
-and \nv are detectable in both 2019 spectra, but is just blueward of
-the wavelength range covered by the original SDSS spectrum. The \civ\
-and \ciii\ lines have faded significantly between the SDSS observation
-in 2005 and the Palomar observations in 2019.  Note that \civ\ is
-extremely faint in the 2019 February spectrum, but that night suffered
-from poor conditions.
-
-Figure~\ref{fig:civ_clqs_J16_spec} shows the rest-frame spectra for SDSS J1638+2827.
-For J1638+2827, our spectral observations cover 4030 observed days,
-corresponding to 1265 days in the rest-frame. Here, in the initial
-epoch spectrum, \civ\ is broad and bright, as is C\,{\sc
+curves for three high-redshift CLQ quasars.
+
+Figure~\ref{fig:civ_clqs_J12_spec} shows the rest-frame spectra for
+SDSS J1205+3422.  For J1205+3422, our spectral observations cover 5195
+observed days, corresponding to 1691 days in the rest-frame. This
+quasar was initially identified in SDSS in 2005 May as a bright, $g
+\approx 18.0$, blue-sloped quasar with broad Si\,{\sc iv}/O\,{\sc iv},
+\civ, C\,{\sc iii}, and Mg\,{\sc ii}.  \civ\ has a blueshift of
+$\approx$580$\pm$80 km s$^{-1}$.  By 2019, however, the optical
+brightness dropped by nearly 2 magnitudes and the spectra are
+significantly less blue.  \lya and \nv are detectable in both 2019
+spectra, but is just blueward of the wavelength range covered by the
+original SDSS spectrum. The \civ\ and \ciii\ lines have faded
+significantly between the SDSS observation in 2005 and the Palomar
+observations in 2019.  Note that \civ\ is extremely faint in the 2019
+February spectrum, but that night suffered from poor conditions.
+
+Figure~\ref{fig:civ_clqs_J16_spec} shows the rest-frame spectra for
+SDSS J1638+2827.  For J1638+2827, our spectral observations cover 4030
+observed days, corresponding to 1265 days in the rest-frame. Here, in
+the initial epoch spectrum, \civ\ is broad and bright, as is C\,{\sc
 iii}. However, $\approx$400 rest-frame days later, the broad \civ\ and
 \ciii\ emission lines have faded, the continuum slope around 1400\AA\
-has changed from $\approx-1.48$ to $\approx-2.25$, but the \lya/\nv
+has changed from $\approx-1.16$ to $\approx-2.17$, but the \lya/\nv
 emission complex is very similar in shape {\bf and intensity}. Around
@@
 time of the third spectral epoch, the source has brightened from
-optical magnitudes of $\sim 20$ mag to $\sim 18.5$ mag. Ly$\alpha$,
+optical magnitudes of $\sim$20 mag to $\sim$18.5 mag. Ly$\alpha$,
 N\,{\sc v}, \civ, \ciii, and \mgii\ are all apparent and broad, with
@@
 
-Figure~\ref{fig:civ_clqs_J22_spec} shows the rest-frame spectra for SDSS J2228+2201.
-For J2228+2201, our spectral observations cover 2504 observed days,
-corresponding to 778 days in the rest-frame. Over the course of 240
-rest-frame days, \civ\ and \ciii\ both {\it emerge} as BELs and {\bf the
-standard UV/blue continuum becomes stronger.}  Then, over the
-course of 538 days in the rest-frame, the broad emission, while still
-very present, reduces in line flux the UV/blue continuum diminishes.
-However, the third epoch still corresponds to a source more luminous
-than the initial BOSS spectrum.
-
-\begin{figure}
+Figure~\ref{fig:civ_clqs_J22_spec} shows the rest-frame spectra for
+SDSS J2228+2201.  For J2228+2201, our spectral observations cover 2504
+observed days, corresponding to 778 days in the rest-frame. Over the
+course of 240 rest-frame days, \civ\ and \ciii\ both {\it emerge} as
+BELs and {\bf the standard UV/blue continuum becomes stronger.}  Then,
+over the course of 538 days in the rest-frame, the broad emission,
+while still very present, reduces in line flux the UV/blue continuum
+diminishes.  However, the third epoch still corresponds to a source
+more luminous than the initial BOSS spectrum.
+
+\begin{figure*}
   \centering
-  \includegraphics[width=8.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
+  \includegraphics[width=18.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
     \vspace{-18pt}
@@
   \label{fig:QSFit-CIV}
-\end{figure}
+\end{figure*}
 
 \subsection{\civ\ Emission Line Evolution}
-We analyzed the multi-epoch spectra of the three quasars using the
+We analyse the multi-epoch spectra of the three quasars using the
 QSFit spectral fitting package \citep{Calderone2017}.  One advantage
@@
 rest-frame 1450\AA, \civ\ line luminosity, FWHM, and EW are given in
-Table~\ref{tab:QSFit-results}.
-{\bf 
-All fits are obtained by taking the Milky Way extinction
-\citep{Schlafly2011} into account.  The extinction values are: $E(B-V)
-=0.013$ for J1205+3422; $E(B-V) =0.034$ for J1638+2827 and $E(B-V)
-=0.041$ for J2228+2201.  as taken from NED (e.g. for
-\href{http://ned.ipac.caltech.edu/cgi-bin/objsearch?search_type=Near+Position+Search&in_csys=Equatorial&in_equinox=J2000.0&lon=12%3A05%3A44.7&lat=%2B34%3A22%3A52.4&radius=0.1&hconst=73&omegam=0.27&omegav=0.73&corr_z=1&z_constraint=Unconstrained&z_value1=&z_value2=&z_unit=z&ot_include=ANY&nmp_op=ANY&out_csys=Equatorial&out_equinox=J2000.0&obj_sort=Distance+to+search+center&of=pre_text&zv_breaker=30000.0&list_limit=5&img_stamp=YES#GalacticExtinction_0}{J1205+3422}).
-}
-The best fit models
-in the region of the \civ\ emission line are shown in
-Figure~\ref{fig:QSFit-CIV}.
+Table~\ref{tab:QSFit-results}.  {\bf All fits are obtained by taking
+the Milky Way extinction \citep{Schlafly2011} into account.  The
+extinction values are: $E(B-V) =0.013$ for J1205+3422; $E(B-V) =0.034$
+for J1638+2827 and $E(B-V) =0.041$ for J2228+2201.  as taken from the
+\href{http://ned.ipac.caltech.edu/}{NASA/IPAC Extragalactic Database} 
+}. The best fit models in the region of the \civ\ emission line are
+shown in Figure~\ref{fig:QSFit-CIV}.
 
@@
 
+{\bf The values in Table~\ref{tab:QSFit-results} are
+$\approx$0.27-0.30 dex higher than the estimates in
+Table~\label{tab:Eddington_ratios}, which is to be expected given the
+difference of calibrations factors. In fact, the virial products are
+all remarkably constant and compatible with a single black hole mass
+estimate, within the standard 0.5 dex uncertainty, across the 3 epochs
+for all the quasars.  This fact gives us confidence in the line
+fitting methods.}
+
 \begin{figure}
@@
   \centering
-  \begin{tabular}{l l l r}
-    \hline
-    \hline
-    Object       & MJD & $L_{\rm bol}$&  $\eta_{\rm Edd}$  \\
-    \hline
-                     & 53498 & 47.22     &  $-$0.61   \\
- J1205+3422 & 58538 &  46.07    &   $-$1.76  \\   %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
-                     & 58693 &  46.57    &  $-$1.26  \\                    
-    \hline 
-                     & 54553 & 46.17   & $-$1.03  \\
-J1638+2827  & 55832 & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
-                     & 58583 & 46.50   & $-$0.69   \\
-    \hline 
-                     & 56189  & 46.23  &  $-$1.24 \\
-J2228+2201  & 56960 & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
-                     & 58693 & 46.83   &  $-$0.64 \\
+  \begin{tabular}{l l  cc    l     r}
+    \hline
+    \hline
+\multirow{2}{*}{Object} & \multirow{2}{*}{MJD} & $\log (M/M_{\odot})$ &  $\log (M/M_{\odot})$ & log($L_{\rm bol}$) &  \multirow{2}{*}{$\eta_{\rm Edd}$}  \\
+                                    &                                  &    QSFit                     &   Liter. value                &                             &    \\
+    \hline
+                                    & 53498                        &    9.39                      &  9.49$\pm$0.04$^{\dagger}$   &   47.22                  &  $-$0.61   \\
+ J1205+3422               & 58538                         &    9.78                     &   ---                                        &  46.07                  &   $-$1.76 \\  %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
+                                    & 58693                        &    9.39                      &                                                 &  46.57                &  $-$1.26  \\
+    \hline 
+                                    & 54553                        &   8.84                      &  8.74$\pm$0.15$\dagger$                     & 46.17   & $-$1.03  \\
+J1638+2827                 & 55832                       &    8.80                             &    9.13                                         & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
+                                    & 58583                        &   9.01                               &                          & 46.50   & $-$0.69   \\
+    \hline 
+                                     & 56189                       & 8.70                                & 8.73                         & 46.23  &  $-$1.24 \\
+J2228+2201                 & 56960                       &   9.39                                &                         & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
+                                     & 58693                      &  8.97                                &                         & 46.83   &  $-$0.64 \\
     \hline
@@
   \end{tabular}
-  \caption{Bolometric luminosities are given in either \citet{Shen2011} or
+  \caption{Virial Mass estimates, bolometric luminosities and Eddington ratios for the
+    three quasars. 
+    $\dagger$From \citet{Shen2011} SDSS DR7 Quasar catalog.
+    $\dagger$From \citet{Shen2011} SDSS DR7 Quasar catalog.
+    are given in either \citet{Shen2011} or
     \citet{Kozlowski2017} for the three CLQs. We scale these values using

### 2020-06-12 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
CIV_CLQs_rv1 virial mass update

@@
 extinction values are: $E(B-V) =0.013$ for J1205+3422; $E(B-V) =0.034$
-for J1638+2827 and $E(B-V) =0.041$ for J2228+2201.  as taken from the
+for J1638+2827 and $E(B-V) =0.041$ for J2228+2201, as taken from the
 \href{http://ned.ipac.caltech.edu/}{NASA/IPAC Extragalactic Database} 
@@
 ``broad'' components, causing the latter to have much larger widths,
-$\sim 10,000$~km~s$^{-1}$.  Finally, neglecting such a narrow
+$\sim$10,000~km~s$^{-1}$.  Finally, neglecting such a narrow
 component ensures a consistent model across all epochs.
@@
 calculate single-epoch black hole mass estimates, show any
-variation. This approach assumes that the broad-line region (BLR) is
-virialized \citep[e.g.][]{Shen2011, Calderone2017}. The continuum
+variation.
+
+This approach assumes that the broad-line region (BLR) is
+virialized \citep[e.g.][]{Shen2011, Calderone2017}.
+{\bf However, the \civ\ line in particular for the broad emission lines is
+observed to have
+line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, 
+very strong blueshifts \citep[as mentioned in the Introduction, see ][]{Richards2011},
+and a component of the line profile that does not reverberate \citep[][]{Denney2012}
+blurring the picture of the BH mass estimation.
+With these key cavaets in mind, we acknowledge the black hole mass estimates
+will have a large error, likely $\sim$0.5 dex.
+}
+The continuum
 luminosity provides a proxy for the BLR radius, and the broad-line
@@
 \begin{equation}
-    \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}. 
+%  \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}.
+  \log \left( \frac{M_{\rm BH}}{M_{\odot}} \right)  = a + \log  \left[ \; \left(  \frac{L_{1450}} {10^{44} \; {\rm erg \; s^{-1}}}\right)^{\gamma} \, \right] + 2 \log \left( \frac{\rm {FWHM}}{{\rm km\; s^{-1}}} \right)
+  \label{eqn:virial_masses}
 \end{equation}
-\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as 0.660, 
+\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as $a=0.660$, 
 which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
-\citet{Kozlowski2017} calculate $\gamma=0.53$ and the offset as 0.64. 
+\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
+but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
+both the DR7 Quasar catalog and DR12 Quasar catalog.
 \citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
@@
 
-The virial product for the \civ\ 
-CLQs is reported in the last column of Table~\ref{tab:QSFit-results}.
-{\bf Here, since our purpose is to check if this measurement varies significantly
-across epochs, we use $\gamma=0.5$ as the power-law slope and
-are not directly concerned with the offset.
+We report a virial product for the \civ\ CLQs in the last column of
+Table~\ref{tab:QSFit-results}.  {\bf Since our purpose is to check if
+this measurement varies significantly across epochs, here we use
+$\gamma=0.5$ as the power-law slope and are not directly concerned
+with the offset.
 %%
@@
 \civ\ estimates were deemed potentially unreliable. The object showing
-the largest variation is J2228+2201, though even that source only
-spans a range of 0.48~dex.
-
+the largest variation is J2228+2201, with the BH mass estimate spanning a range of 0.66~dex.
+
+{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ Virial masses 
+calculated using equation~\ref{eqn:virial_masses}, the measured luminosites
+and FWHM from QSFit and the \citet{VestergaardPeterson2006} calibrations.
+}
+ %%
 \citet{Shen2011} and \citet{Kozlowski2017} report virial black hole
@@
     \hline
-\multirow{2}{*}{Object} & \multirow{2}{*}{MJD} & $\log (M/M_{\odot})$ &  $\log (M/M_{\odot})$ & log($L_{\rm bol}$) &  \multirow{2}{*}{$\eta_{\rm Edd}$}  \\
+\multirow{2}{*}{Object} & \multirow{2}{*}{MJD} & \multicolumn{2}{c}{$\log (M/M_{\odot})$} & log($L_{\rm bol}$) &  \multirow{2}{*}{$\eta_{\rm Edd}$}  \\
                                     &                                  &    QSFit               &   Liter. value               &                             &    \\
@@
  J1205+3422               & 58538                         &    9.78               &   ---                                        &  46.07                  &   $-$1.76 \\  %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
-                                    & 58693                        &    9.39                      &                                                 &  46.57                &  $-$1.26  \\
+                                    & 58693                        &    9.38               &   ---                                               &  46.57                &  $-$1.26  \\
     \hline 
                                     & 54553                        &   8.84                &  8.74$\pm$0.15$\dagger$                     & 46.17   & $-$1.03  \\
-J1638+2827                 & 55832                       &    8.80                             &    9.13                                         & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
-                                    & 58583                        &   9.01                               &                          & 46.50   & $-$0.69   \\
-    \hline 
-                                     & 56189                       & 8.70                                & 8.73                         & 46.23  &  $-$1.24 \\
-J2228+2201                 & 56960                       &   9.39                                &                         & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
-                                     & 58693                      &  8.97                                &                         & 46.83   &  $-$0.64 \\
+J1638+2827                 & 55832                       &    8.80                &    9.13$^{\ddagger}$                                         & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
+                                    & 58583                        &   9.01                &  ---                         & 46.50   & $-$0.69   \\
+    \hline 
+                                     & 56189                       & 8.70                 & 8.73$^{\ddagger}$                         & 46.23  &  $-$1.24 \\
+J2228+2201                 & 56960                       &  9.39                &   ---                       & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
+                                     & 58693                      &  8.97                    &    ---                      & 46.83   &  $-$0.64 \\
     \hline
@@
     three quasars. 
-    $\dagger$From \citet{Shen2011} SDSS DR7 Quasar catalog.
-    $\dagger$From \citet{Shen2011} SDSS DR7 Quasar catalog.
-    are given in either \citet{Shen2011} or
-    \citet{Kozlowski2017} for the three CLQs. We scale these values using
+    $\dagger$From the \citet{Shen2011} SDSS DR7 Quasar catalog.
+    $\ddagger$From the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
+%    are given in either \citet{Shen2011} or    \citet{Kozlowski2017} for the three CLQs.
+    We scale these values using
     our measured $\nu L_{\nu}$ continuum luminosity values.  From

### 2020-06-12 calculations/BH_VirialMasses.py

@@ -51,9 +51,9 @@ FWHM_CIV_err  = 219.283447265625
 logL_1450_1st = 46.619406410886775
 logL_1450_2nd = 45.457881896733994
 logL_1450_3rd = 45.9566485792052
-logL_CIV1_1st = 4700.
-logL_CIV1_2nd = 14900.
-logL_CIV1_3rd = 6980.
+FWHM_CIV_1st = 4700.
+FWHM_CIV_2nd = 14900.
+FWHM_CIV_3rd = 6980.
 
 #M_BH = a
 #np.log10((3.8503777798695754e+45/1e44)**0.53) + (2*np.log10(4180.7216796875))+0.66
@@ -73,9 +73,9 @@ print('log_MBH_S10_MgII_J12::   ',  log_MBH_S10_MgII_J12,  ' vs. 9.55834 in Shen
 print('log_MBH_VP06_CIV_J12::   ',  log_MBH_VP06_CIV_J12,  ' vs. 9.49350 in Shen et al. (2011)')
 print()
 
-log_MBH_QSFit_J12_1st  = a_VP06_CIV  + np.log10(( 10**logL_1450_1st /1e44)**b_VP06_CIV) + (2*np.log10(logL_CIV1_1st))
-log_MBH_QSFit_J12_2nd  = a_VP06_CIV  + np.log10(( 10**logL_1450_2nd /1e44)**b_VP06_CIV) + (2*np.log10(logL_CIV1_2nd))
-log_MBH_QSFit_J12_3rd  = a_VP06_CIV  + np.log10(( 10**logL_1450_3rd /1e44)**b_VP06_CIV) + (2*np.log10(logL_CIV1_3rd))
+log_MBH_QSFit_J12_1st  = a_VP06_CIV  + np.log10(( 10**logL_1450_1st /1e44)**b_VP06_CIV) + (2*np.log10(FWHM_CIV_1st))
+log_MBH_QSFit_J12_2nd  = a_VP06_CIV  + np.log10(( 10**logL_1450_2nd /1e44)**b_VP06_CIV) + (2*np.log10(FWHM_CIV_2nd))
+log_MBH_QSFit_J12_3rd  = a_VP06_CIV  + np.log10(( 10**logL_1450_3rd /1e44)**b_VP06_CIV) + (2*np.log10(FWHM_CIV_3rd))
 
 print
[…]

### 2020-07-07 tex/MNRAS_submission/rv1/reply2referee.txt
tex/MNRAS_submission/rv1 update

@@
 
-	   We have changed the Section 2 text.
+	   We have changed and corrected the Section 2 text.
 
@@
 
-       	  We thank the referee for their very thoughtful notes on this
-	  point. We have changed and updated the text with the comments above
+       	  We thank the referee for their very thoughtful notes on this point.
+	  We have changed and updated the text with the comments above
 	  taken into account.
@@
 
-      	  We agree with this comment and to help the reader, we have
-	  removed the (confusing) ``Ionization Potential'' column,
-	  while adding a column to the table noting the "Production
-	  Mechanism'' of each emission line. We have a (strong)
-	  preference to retain this table, but leave it as a decision
-	  to the Editor whether to do so.
+      	  We agree with this comment and to help the reader, in Table 1 we have removed the confusing ``Ionization Potential'' column,
+	  while adding a column to the table noting the "Production Mechanism'' of each emission line.
+	  We have a strong preference to retain this table, but leave it as a decision to the Editor as to whether to do so.
 
@@
 
-	  We have split the light curve and spectral figures up, have
-	  increased the size of the fonts, and have writen the names
-	  of the quasars in the approriate panels.
+	 As suggested, we have split the light curve and spectral figures up, increased the size of the fonts,
+         and have writen the names of the quasars in the approriate panels.
 
@@
 
-	 We have added a paragraph at the end of Section 2.4
-      	 detailing how the uncertainties in the spectral line quantities
-    	 are determined.
+	 We have added a paragraph at the end of Section 2.4 detailing how
+	 the uncertainties in the spectral line quantities are determined.
 
@@
 
-   	We have added key additional text and references here.
+   	Yes, this is an excellent point. We have updated and corrected the equation
+	and revised the relevant discussion, adding key text and references here.
 

### 2020-07-07 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
tex/MNRAS_submission/rv1 update

@@
 Photoionization followed by recombination determines the ionization
-level of carbon, and collisional excitation from the ground level of
-\civ\ determines the line intensity. Other processes do happen,
-(including radiative and three body recombination to the upper level
+level of carbon, and collisional excitation from the ions ground level 
+determines the line intensity. Other processes do happen,
+(including radiative and three body recombination to the upper levels 
 of the transition), but they are much slower unless the density is
@@
 iii} ion is 47.89 eV (3.519 Ry) and thus a photon with this energy
-($k_{\rm B} T \sim 5 \times10^{5}$ K) can create the triply ionised,
+($k_{\rm B} T \sim 5.6 \times10^{5}$ K) can create the triply ionised,
 \civ\ ion. Once the \civ\ ion is formed, collisional excitation leads to
@@
 
-\subsection{Virial Black Hole Masses}
-\label{sec:BH_masses} 
+\subsection{Virial Black Hole Masses}\label{sec:BH_masses} 
 The FWHMs of quasar broad lines are related to the mass of the SMBH
@@
 
-This approach assumes that the broad-line region (BLR) is
-virialized \citep[e.g.][]{Shen2011, Calderone2017}.
-{\bf However, the \civ\ line in particular for the broad emission lines is
-observed to have
-line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, 
-very strong blueshifts \citep[as mentioned in the Introduction, see ][]{Richards2011},
-and a component of the line profile that does not reverberate \citep[][]{Denney2012}
-blurring the picture of the BH mass estimation.
-With these key cavaets in mind, we acknowledge the black hole mass estimates
-will have a large error, likely $\sim$0.5 dex.
-}
+This approach assumes that the broad-line region (BLR) is virialized
+\citep[e.g.][]{Shen2008b, Shen2011, Calderone2017,
+Mejia-Restrepo2018}.  {\bf However, the \civ\ line is observed to have
+line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, very
+strong blueshifts \citep[as mentioned in the Introduction, see
+][]{Richards2011}, and a component of the line profile that does not
+reverberate \citep[][]{Denney2012}.  These issues make the virial BH
+mass estimate uncertain. \citet{Runnoe2013}, 
+\citet{Mejia-Restrepo2016}, \citet{Coatman2017}, 
+\citet{Mejia-Restrepo2018} and \citet{Grier2019} all present studies
+into improving \civ-based single-epoch black hole mass estimates. With
+these cavaets in mind, we acknowledge the BH mass estimates will have
+a large error, likely $\sim$0.5 dex. }
 The continuum
@@
 $\gamma=0.5$ as the power-law slope and are not directly concerned
-with the offset.
-%%
- The quoted uncertainties account only for the propagation of uncertainties in the continuum luminosities and line widths.
-However, typical uncertainties associated to single epoch virial mass are $\sim$~0.5 dex, hence} implying that the virial products for our three
-high-redshift CLQs are all remarkably constant and compatible with
-single black hole masses per source, even in those cases where the
-\civ\ estimates were deemed potentially unreliable. The object showing
-the largest variation is J2228+2201, with the BH mass estimate spanning a range of 0.66~dex.
-
-{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ Virial masses 
-calculated using equation~\ref{eqn:virial_masses}, the measured luminosites
-and FWHM from QSFit and the \citet{VestergaardPeterson2006} calibrations.
-}
- %%
-\citet{Shen2011} and \citet{Kozlowski2017} report virial black hole
-masses based on \mgii\ and \civ\ for the SDSS/BOSS observations of our
-targets. For J1205+3422, \citet{Shen2011} report $\log (M_{\rm BH,
-MgII}/M_{\odot}) = 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot})
-= 9.49 \pm 0.04$. We use the mean of five values --- three from our
-three epochs and two from \citet{Shen2011} --- to calculate an adopted
-SMBH mass of $\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.
-J1638+2827 also has two virial mass measurements from
-\citet{Shen2011}, as well as two measurements from
-\citet{Kozlowski2017}. The mean mass measurement adopted for
-J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot} = 9.09$. For J2228+2201,
-there are two \citet{Kozlowski2017} measurements, leading to a mean
-adopted mass of $\log(M_{\rm BH, vir}/M_{\odot} = 9.37$. We use these
-mean SMBH masses when calculating the Eddington ratios.
+with the offset.  The quoted uncertainties account only for the
+propagation of uncertainties in the continuum luminosities and line
+widths.  As noted above, with typical uncertainties associated to
+single epoch virial mass around $\sim$0.5 dex,} this implies that the
+virial products for our three high-redshift CLQs are all remarkably
+constant and compatible with single black hole masses per source, even
+in those cases where the \civ\ estimates were deemed potentially
+unreliable. The object showing the largest variation is J2228+2201,
+with the BH mass estimate spanning a range of 0.66~dex.
+
+{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ Virial
+masses calculated using equation~\ref{eqn:virial_masses}, the measured
+luminosites and FWHM from QSFit and the
+\citet{VestergaardPeterson2006} calibrations.} \citet{Shen2011} and
+\citet{Kozlowski2017} report virial black hole masses based on \mgii\
+and \civ\ for the SDSS/BOSS observations of our targets. For
+J1205+3422 (and MJD 53498), \citet{Shen2011} report $\log (M_{\rm BH, MgII}/M_{\odot})
+= 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot}) = 9.49 \pm
+0.04$.
+
+We use the mean of five values --- three from our three epochs
+and two from \citet{Shen2011} --- to calculate an adopted SMBH mass of
+$\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.  J1638+2827
+also has two virial mass measurements from \citet{Shen2011}, as well
+as two measurements from \citet{Kozlowski2017}. The mean mass
+measurement adopted for J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot}
+= 9.09$. For J2228+2201, there are two \citet{Kozlowski2017}
+measurements, leading to a mean adopted mass of $\log(M_{\rm BH,
+vir}/M_{\odot} = 9.37$. We use these mean SMBH masses when calculating
+the Eddington ratios.
 

### 2020-07-10 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
Big CIV MBH, Lbol, eta update

@@
 
-{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ Virial
-masses calculated using equation~\ref{eqn:virial_masses}, the measured
-luminosites and FWHM from QSFit and the
+{\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ virial
+  masses calculated using the measured
+luminosites and FWHM from QSFit, equation~\ref{eqn:virial_masses} and the
 \citet{VestergaardPeterson2006} calibrations.} \citet{Shen2011} and
@@
 = 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot}) = 9.49 \pm
-0.04$.
-
-We use the mean of five values --- three from our three epochs
-and two from \citet{Shen2011} --- to calculate an adopted SMBH mass of
-$\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.  J1638+2827
-also has two virial mass measurements from \citet{Shen2011}, as well
-as two measurements from \citet{Kozlowski2017}. The mean mass
-measurement adopted for J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot}
-= 9.09$. For J2228+2201, there are two \citet{Kozlowski2017}
-measurements, leading to a mean adopted mass of $\log(M_{\rm BH,
-vir}/M_{\odot} = 9.37$. We use these mean SMBH masses when calculating
-the Eddington ratios.
-
-From the virial mass estimates, all our objects have SMBH masses
-$M_{\rm BH} >10^{9} M_{\odot}$.  This is at the upper end of SMBH
-masses at all epochs, and towards the extreme of the mass distribution
-for $z\sim2$ quasars.  Figure~\ref{fig:CIV_MBHvsREW} compares the
-\civ\ EW versus the virial SMBH masses for our multi-epoch
-observations to a sample of $\approx$20,000 $z>1.5$ SDSS quasars from
-the QSFit catalog \citep{Calderone2017}.
+0.04$, while for J1638+2827 (MJD 54553) \citet{Shen2011} report 
+$\log (M_{\rm BH, MgII}/M_{\odot}) = 9.03 \pm 0.37$ and
+$\log(M_{\rm BH, CIV}/M_{\odot}) = 8.74 \pm 0.15$.
 
 {\bf The values in Table~\ref{tab:QSFit-results} are
-$\approx$0.27-0.30 dex higher than the estimates in
-Table~\label{tab:Eddington_ratios}, which is to be expected given the
+$\approx$0.3 dex higher than the estimates in
+Table~\ref{tab:Eddington_ratios}, which is to be expected given the
 difference of calibrations factors. In fact, the virial products are
@@
 fitting methods.}
+
+From the virial mass estimates, all our objects have SMBH masses $M_{\rm BH} >10^{9} M_{\odot}$.
+This is at the upper end of SMBH masses at all epochs, and towards the extreme of the mass distribution for $z\sim2$ quasars.
+Figure~\ref{fig:CIV_MBHvsREW} compares the luminosity \civ\ EW versus the virial SMBH masses for our multi-epoch
+observations to a sample of $\approx$20,000 $z>1.5$ SDSS quasars from
+the QSFit catalog \citep{Calderone2017}.
+
+{\bf With the black hole masses in hand, we can calculate the Eddington luminosities of 
+the three quasars. To be consistent with 
+For the Bolometric luminosity, $L_{\rm Bol}$, \citet{Shen2011} and 
+\citet{Kozlowski2017} use the bolometric corrections of BC$_{1350}$ = 3.81 
+from the composite spectral energy distribution (SED) in \citet{Richards2006b}.
+
+We report the black hole \civ\ virial masses, the bolometric luminosities
+and the Eddington ratios ($\eta=\log(L_{}/L_{Edd})$ in Table~\ref{tab:Eddington_ratios}. 
+}
+
+%We use the mean of five values --- three from our three epochs and two from \citet{Shen2011} --- to calculate an adopted SMBH mass of $\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.
+J1638+2827 also has two virial mass measurements from \citet{Shen2011}, as well as two measurements from \citet{Kozlowski2017}.
+The mean mass measurement adopted for J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot} = 9.09$.
+For J2228+2201, there are two \citet{Kozlowski2017} measurements, leading to a mean adopted mass of $\log(M_{\rm BH, vir}/M_{\odot} = 9.37$.
+We use these mean SMBH masses when calculating the Eddington ratios.
 
@@
 
+%%
+%%  These values are generated using the 
+%%
 \begin{table}
   \centering
-  \begin{tabular}{l l  cc    l     r}
-    \hline
-    \hline
-\multirow{2}{*}{Object} & \multirow{2}{*}{MJD} & \multicolumn{2}{c}{$\log (M/M_{\odot})$} & log($L_{\rm bol}$) &  \multirow{2}{*}{$\eta_{\rm Edd}$}  \\
-                                    &                                  &    QSFit               &   Liter. value               &                             &    \\
-    \hline
-                                    & 53498                        &    9.39                &  9.49$\pm$0.04$^{\dagger}$   &   47.22                  &  $-$0.61   \\
- J1205+3422               & 58538                         &    9.78               &   ---                                        &  46.07                  &   $-$1.76 \\  %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
-                                    & 58693                        &    9.38               &   ---                                               &  46.57                &  $-$1.26  \\
-    \hline 
-                                    & 54553                        &   8.84                &  8.74$\pm$0.15$\dagger$                     & 46.17   & $-$1.03  \\
-J1638+2827                 & 55832                       &    8.80                &    9.13$^{\ddagger}$                                         & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
-                                    & 58583                        &   9.01                &  ---                         & 46.50   & $-$0.69   \\
-    \hline 
-                                     & 56189                       & 8.70                 & 8.73$^{\ddagger}$                         & 46.23  &  $-$1.24 \\
-J2228+2201                 & 56960                       &  9.39                &   ---                       & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
-                                     & 58693                      &  8.97                    &    ---                      & 46.83   &  $-$0.64 \\
+  \begin{tabular}{l l  cc         r}
+    \hline
+    \hline
+                      &                  &                                      &                              & \\
+Object            & MJD           &  $\log (M/M_{\odot})$  & log($L_{\rm bol}$)  &  $\eta_{\rm Edd}$  \\
+                      &                  &                                      &                              & \\
+    \hline
+                      & $^{\dagger }$53498  &  9.49              &  47.22                  &  -0.378   \\
+                      & 53498                      &    9.39            &                    &  $-$0.61   \\
+ J1205+3422 & 58538                       &    9.78           &                      &   $-$1.76 \\  
+                     & 58693                         &    9.38          &                   &  $-$1.26  \\                    
+    \hline
+                     & $^{\dagger }$54553    &  8.74            &  46.17   & $-$0.677  \\
+                     & 54553                         &   8.84                 &             & $-$1.03  \\
+J1638+2827  & $^{\ddagger }$55832  &    9.13                  & 45.98   & $-$1.21  \\      
+                      & 55832                        &   8.80                  & 45.98   & $-$1.21  \\     
+                      & 58583                        &   9.01                  & 46.50   & $-$0.69   \\
+    \hline
+                         & $^{\ddagger }$56189   & 8.73                  & 46.23  &  $-$1.24 \\
+                         & 56189                         & 8.70                  & 46.23  &  $-$1.24 \\
+J2228+2201     & 56960                          &  9.39               & 47.34  & $-$0.12  \\      
+                         & 58693                         &  8.97               & 46.83   &  $-$0.64 \\
     \hline

### 2020-07-10 calculations/BH_VirialMasses.py

@@ -1,13 +1,17 @@
+'''
+  BLACK HOLE VIRIAL MASS ESTIMATES
+
+The virial BH mass calibrations and scaling relations used in this
+paper [Shen et al. 2011] are from McLure & Dunlop (2004, Hβ and Mg
+II), Vestergaard & Peterson (2006, Hβ and C IV), and Vestergaard &
+Osmer (2009, Mg II). 
+These are for quasars:
+ SDSS  J160544.68+342252.4
+
+'''
 
 import numpy as np
 
-'''
-Scaling relations
-The virial BH mass calibrations used in this paper [Shen et al. 2011]
-are from McLure & Dunlop (2004, Hβ and Mg ii), Vestergaard & Peterson
-(2006, Hβ and C iv), and Vestergaard & Osmer (2009, Mg ii). These
-calibrations have parameters:
-'''
 
 a_MD04_MgII = 0.505
 b_MD04_MgII = 0.62
@@ -21,119 +25,237 @@ b_S10_MgII = 0.62
 a_VP06_CIV = 0.660
 b_VP06_CIV = 0.53
 
-
+'''
+	From Shen et al. (2011) 
+	3.8. The Spectral Catalog
+	``BC_1350 = 3.81 from the composite spectral energy distribution (SED) in Richards et al. (2006a).''
+'''
 
 
 '''
      J 1 2 0 5 + 3 4 2 2 
 
-Okay, data from Shen et al. (2011) for
+Data from Shen et al. (2011) 
+Shen_dr7_bh_May_2010.fits
 ((PLATE == 2089) && (FIBER == 427) && (MJD == 53498))
-J120544.68+342252.4
 '''
-logL_MgII     = 44.45386264728122
-logL_MgII_err = 0.045117652479984116
-logL_CIV      = 44.896004599940575
-logL_CIV_err  = 0.01388080688529314
 
-logL_3000     = 46.368801937169536
-logL_3000_err = 0.008489474504106198
-logL_1350     = 46.634680779574154
-logL_1350err  = 0.004262343930953705
+log_L3000     = 46.368801937169536
+log_L3000_err = 0.008489474504106198
+log_L1350     = 46.634680779574154
[…]

### 2020-07-10 data/QSO_CIV_catalogs/matchingHam17toKoz17.py

@@ -47,13 +47,39 @@ Koz17_table.remove_column('IVAR_PSFFLUX')
 Koz17_table.remove_column('PSFMAG')
 Koz17_table.remove_column('ERR_PSFMAG')
 
+
+## Some nice DataFrame polish/manipulation
 Koz17_df    = DataFrame(np.array(Koz17_table))
 print('len(Koz17_df)', len(Koz17_df))
 
-## COlumns names are case senstive!
+## Columns names are case senstive!
 Koz17_df.rename(columns={'SDSS_NAME':'sdss_name'}, inplace=True)              
 
 ## Testing on a wee bit of the DataFrame...
 mini_merge = pd.merge(Ham17_df[0:100], Koz17_df[0:100], on="sdss_name")
 
 The_DF = pd.merge(Ham17_df, Koz17_df, on="sdss_name")
+
+
+## Just wanting to write a few things out to a simple text file. 
+file1 = open("temp.txt","w+") 
+    
+#for ii in range(len(Koz17)):     # if the full catalog is wanted!  
+for ii in range(100):
+    print(ii)
+
+    name        = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['SDSS_NAME']
+    REW         = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['rew']
+    bal_flag_vi = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['bal_flag_vi']
+    f1450       = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['f1450']
+    
+    if (len(name) > 0 and  bal_flag_vi <1) :
+        #print(ii, Koz17['SDSS_NAME'][ii], name, REW, f1450)
+        file1.write(str(ii)+str(Koz17['SDSS_NAME'][ii])+str(we_name)+str(we_rew))
+        file1.write(" {} {} {}  {} {} {}  {} {} {}  \n".format(ii, name, Koz17['RA'][ii], Koz17['DEC'][ii],
+                                                    #bal_flag_vi,
+                                                    REW, f1450, 
+                                                    Koz17['L1350'][ii], Koz17['LBol'][ii], #Koz17['eLBol'][ii],
+                                                    Koz17['nEdd'][ii]))
+file1.close() 
+

### 2020-07-10 data/QSO_CIV_catalogs/matchingHam17toKoz17_v0.py

@@ -1,54 +1,0 @@
-
-import numpy as np 
-from astropy.io import fits
-from astropy.io import ascii
-
-import matplotlib
-import matplotlib.pyplot as plt
-import matplotlib.lines  as mlines
-
-
-##  Hamann et al. (2017) ERQ BOSS DR12 catalog
-path       = '/cos_pc19a_npr/data/ERQs/Hamann2017_CIVcatalog/'
-filename   = 'C4N5REWs_DR12v11_MNRAS.fits'
-infile     = path+filename
-data_full  = fits.open(infile)
-Ham17_full = data_full[1].data
-
-## knocking out a couple of objects with bad REW values 
-#Ham17 = Ham17_full[np.where( (Ham17['rew'] >0.) & (Ham17['rew'] < 10000.)  )]
-Ham17 = Ham17_full
-
-
-##  Kozłowski_2017_ApJS_228_9.  BOSS DR12 "Value Added" catalog
-path       = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/QSO_CIV_catalogs/'
-filename   = 'SDSS-DR12Q-BH_extra.fits'
-infile     = path+filename
-data_full  = fits.open(infile)
-Koz17_full = data_full[1].data
-
-Koz17      = Koz17_full
-
-
-
-file1 = open("temp.txt","w+") 
-
-    
-#for ii in range(len(Koz17)):
-for ii in range(100):
-    print(ii)
-
-    name        = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['SDSS_NAME']
-    REW         = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['rew']
-    bal_flag_vi = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['bal_flag_vi']
-    f1450       = Ham17[np.where((Koz17['SDSS_NAME'][ii]  == Ham17['SDSS_NAME']))]['f1450']
-    
-    if (len(name) > 0 and  bal_flag_vi <1) :
-        #print(ii, Koz17['SDSS_NAME'][ii], name, REW, f1450)
-        file1.write(str(ii)+str(Koz17['SDSS_NAME'][ii])+str(we_name)+str(we_rew))
[…]

### 2020-07-10 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
BH_VirialMasses.py looking good...

@@
 
+The continuum
+luminosity provides a proxy for the BLR radius, and the broad-line
+width (FWHM) provides a proxy for the virial velocity.  This ``virial
+mass'' estimate is then expressed as:
+{\bf
+\begin{equation}
+%  \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}.
+  \log \left( \frac{M_{\rm BH}}{M_{\odot}} \right)  = a + \log  \left[ \; \left(  \frac{L_{1450}} {10^{44} \; {\rm erg \; s^{-1}}}\right)^{\gamma} \, \right] + 2 \log \left( \frac{\rm {FWHM}}{{\rm km\; s^{-1}}} \right)
+  \label{eqn:virial_masses}
+\end{equation}
+where $L_{1450}$ is the monochromatic (continuum) luminosity at 1450\AA\,
+and FWHM is the full width at half-maximum of the broad \civ\ emission line.
+The coefficient $\gamma$ and offset $a$ are generally deteremined empirically.
+
 This approach assumes that the broad-line region (BLR) is virialized
@@
 a large error, likely $\sim$0.5 dex. }
-The continuum
-luminosity provides a proxy for the BLR radius, and the broad-line
-width (FWHM) provides a proxy for the virial velocity.  This ``virial
-mass'' estimate is then expressed as:
-{\bf
-\begin{equation}
-%  \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}.
-  \log \left( \frac{M_{\rm BH}}{M_{\odot}} \right)  = a + \log  \left[ \; \left(  \frac{L_{1450}} {10^{44} \; {\rm erg \; s^{-1}}}\right)^{\gamma} \, \right] + 2 \log \left( \frac{\rm {FWHM}}{{\rm km\; s^{-1}}} \right)
-  \label{eqn:virial_masses}
-\end{equation}
-\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as $a=0.660$, 
-which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
-\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
-but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
-both the DR7 Quasar catalog and DR12 Quasar catalog.
-\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
-$z>1.3$ quasars that show significant lag measurements,
-and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
-their highest-confidence objects. }
 
@@
 
+\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as $a=0.660$, 
+which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
+\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
+but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
+both the DR7 Quasar catalog and DR12 Quasar catalog.
+\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
+$z>1.3$ quasars that show significant lag measurements,
+and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
+their highest-confidence objects. }
+
 {\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ virial
@@
   \end{tabular}
-  \caption{Virial Mass estimates, bolometric luminosities and Eddington ratios for the
+  \caption{The \civ\ virial mass estimates, bolometric luminosities and Eddington ratios for the
     three quasars.
+    The virial masses are calculated using the measured monochromatic luminosites and FWHM
     $\dagger$From the \citet{Shen2011} SDSS DR7 Quasar catalog.

### 2020-07-10 calculations/BH_VirialMasses.py

@@ -6,15 +6,24 @@ paper [Shen et al. 2011] are from McLure & Dunlop (2004, Hβ and Mg
 II), Vestergaard & Peterson (2006, Hβ and C IV), and Vestergaard &
 Osmer (2009, Mg II). 
 These are for quasars:
+ SDSS  J1205     +3422 
  SDSS  J160544.68+342252.4
+ SDSS  J222818.76+220102.9
 
 '''
-
 import numpy as np
 
+a_MD04_Hbeta = 0.672   ## not used here, qutoed for completeness 
+b_MD04_Hbeta = 0.61    ## not used here, qutoed for completeness 
 
-a_MD04_MgII = 0.505
-b_MD04_MgII = 0.62
+a_MD04_MgII  = 0.505
+b_MD04_MgII  = 0.62
+
+a_VP06_Hbeta = 0.910    ## not used here, qutoed for completeness 
+b_VP06_Hbeta = 0.50    ## not used here, qutoed for completeness 
+
+a_VP06_CIV = 0.660
+b_VP06_CIV = 0.53
 
 a_VO09_MgII = 0.860
 b_VO09_MgII = 0.50
@@ -22,8 +31,6 @@ b_VO09_MgII = 0.50
 a_S10_MgII = 0.740
 b_S10_MgII = 0.62
 
-a_VP06_CIV = 0.660
-b_VP06_CIV = 0.53
 
 '''
 	From Shen et al. (2011) 
@@ -40,101 +47,101 @@ Shen_dr7_bh_May_2010.fits
 ((PLATE == 2089) && (FIBER == 427) && (MJD == 53498))
 '''
 
-log_L3000     = 46.368801937169536
-log_L3000_err = 0.008489474504106198
-log_L1350     = 46.634680779574154
-log_L1350err  = 0.004262343930953705
+log_L3000_J12    = 46.368801937169536
+log_L3000err_J12 = 0.008489474504106198
+log_L1350_J12    = 46.634680779574154
+log_L1350err_J12 = 0.004262343930953705
 
-log_LMgII     = 44.45386264728122
-log_LMgII_err = 0.045117652479984116
-log_LCIV      = 44.896004599940575
-log_LCIV_err  = 0.01388080688529314
+log_LMgII_J12    = 44.45386264728122
[…]

### 2020-07-10 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
another key BH_VirialMasses.py and CIV_CLQs_rv1 update

@@
 may be a bias due to the limited wavelength range available which
-extends to rest-frame $\lambda \sim 1240$~\AA\ for the first epoch,
+extends to rest-frame $\lambda$$\sim$1240~\AA\ for the first epoch,
 while it extend to shorter wavelengths for the other epochs
-(respectively ~\AA\ and 1010~\AA).  This suggests that the emerging
+(respectively 1100~\AA\ and 1010~\AA).  This suggests that the emerging
 component is more prominent at UV wavelengths, and a sufficient
@@
 \civ\ line profile is reliably constrained, we find that the \civ\
-FWHM is approximately constant with maximum variations $\lesssim 1000$
+FWHM is approximately constant with maximum variations $\lesssim$1000 
 km s$^{-1}$, despite significantly larger line luminosity variations.
@@
 calculate single-epoch black hole mass estimates, show any
-variation.
-
-The continuum
-luminosity provides a proxy for the BLR radius, and the broad-line
-width (FWHM) provides a proxy for the virial velocity.  This ``virial
-mass'' estimate is then expressed as:
+variation. The continuum luminosity provides a proxy for the BLR
+radius, and the broad-line width (FWHM) provides a proxy for the
+virial velocity. This approach assumes that the broad-line region
+(BLR) is virialized \citep[e.g.][]{Shen2008b, Shen2011, Calderone2017,
+Mejia-Restrepo2018} and the virial mass estimate is then:
 {\bf
@@
 \end{equation}
-where $L_{1450}$ is the monochromatic (continuum) luminosity at 1450\AA\,
+where $L_{1450}$ is the monochromatic continuum luminosity at 1450\AA\,
 and FWHM is the full width at half-maximum of the broad \civ\ emission line.
@@
 
-This approach assumes that the broad-line region (BLR) is virialized
-\citep[e.g.][]{Shen2008b, Shen2011, Calderone2017,
-Mejia-Restrepo2018}.  {\bf However, the \civ\ line is observed to have
+ {\bf The \civ\ line is observed to have
 line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, very
@@
 
-We report a virial product for the \civ\ CLQs in the last column of
+We report the virial product for the \civ\ CLQs in the last column of
 Table~\ref{tab:QSFit-results}.  {\bf Since our purpose is to check if
@@
 
-\citet{VestergaardPeterson2006} have $\gamma=0.53$ and the offset as $a=0.660$, 
-which is widely adopted \citep[e.g.,][]{Chen2019, Yao2019}.
+For Equation~\ref{eqn:virial_masses}., \citet{VestergaardPeterson2006}
+measure $\gamma=0.53$ and the offset as $a=0.660$, and these estimates
+are widely adopted \citep[e.g.,][]{Shen2011, Chen2019, Yao2019}.
 \citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
@@
 
-From the virial mass estimates, all our objects have SMBH masses $M_{\rm BH} >10^{9} M_{\odot}$.
+From the virial mass estimates, all our objects have SMBH masses $M_{\rm BH} \approx 500\times10^{8} M_{\odot}$.
 This is at the upper end of SMBH masses at all epochs, and towards the extreme of the mass distribution for $z\sim2$ quasars.
@@
 
-{\bf With the black hole masses in hand, we can calculate the Eddington luminosities of 
-the three quasars. To be consistent with 
-For the Bolometric luminosity, $L_{\rm Bol}$, \citet{Shen2011} and 
-\citet{Kozlowski2017} use the bolometric corrections of BC$_{1350}$ = 3.81 
-from the composite spectral energy distribution (SED) in \citet{Richards2006b}.
-
-We report the black hole \civ\ virial masses, the bolometric luminosities
-and the Eddington ratios ($\eta=\log(L_{}/L_{Edd})$ in Table~\ref{tab:Eddington_ratios}. 
-}
-
-%We use the mean of five values --- three from our three epochs and two from \citet{Shen2011} --- to calculate an adopted SMBH mass of $\log (M_{\rm BH, vir}/M_{\odot}) = 9.73$ for J1205+3422.
-J1638+2827 also has two virial mass measurements from \citet{Shen2011}, as well as two measurements from \citet{Kozlowski2017}.
-The mean mass measurement adopted for J1638+2827 is $\log(M_{\rm BH, vir}/M_{\odot} = 9.09$.
-For J2228+2201, there are two \citet{Kozlowski2017} measurements, leading to a mean adopted mass of $\log(M_{\rm BH, vir}/M_{\odot} = 9.37$.
-We use these mean SMBH masses when calculating the Eddington ratios.
+{\bf With the black hole masses in hand, we can calculate the
+Eddington luminosities of the three quasars. To be consistent with For
+the Bolometric luminosity, $L_{\rm Bol}$, \citet{Shen2011} and
+\citet{Kozlowski2017} use the bolometric corrections of BC$_{1350}$ =
+3.81 (from the composite spectral energy distribution (SED) in
+\citet{Richards2006b}) and to be consistent with those measurements we
+adopt the same correction.  We report the the bolometric luminosities
+and the Eddington ratios, $\eta=\log(L_{}/L_{Edd})$, in
+Table~\ref{tab:Eddington_ratios}.  }
 
@@
   \centering
-  \begin{tabular}{l l  cc         r}
+  \begin{tabular}{l c cc l}
     \hline
@@
     \hline
-                      & $^{\dagger }$53498  &  9.49              &  47.22                  &  -0.378   \\
-                      & 53498                      &    9.39            &                    &  $-$0.61   \\
- J1205+3422 & 58538                       &    9.78           &                      &   $-$1.76 \\  
-                     & 58693                         &    9.38          &                   &  $-$1.26  \\                    
-    \hline
-                     & $^{\dagger }$54553    &  8.74            &  46.17   & $-$0.677  \\
-                     & 54553                         &   8.84                 &             & $-$1.03  \\
-J1638+2827  & $^{\ddagger }$55832  &    9.13                  & 45.98   & $-$1.21  \\      
-                      & 55832                        &   8.80                  & 45.98   & $-$1.21  \\     
-                      & 58583                        &   9.01                  & 46.50   & $-$0.69   \\
-    \hline
-                         & $^{\ddagger }$56189   & 8.73                  & 46.23  &  $-$1.24 \\
-                         & 56189                         & 8.70                  & 46.23  &  $-$1.24 \\
-J2228+2201     & 56960                          &  9.39               & 47.34  & $-$0.12  \\      
-                         & 58693                         &  8.97               & 46.83   &  $-$0.64 \\
+\multirow{4}{*}{J1205+3422} & 53498          &   9.49$^{\dagger }$   &   47.22$^{\dagger }$  & $-$0.38$^{\dagger }$   \\
+                                             &  53498        &   9.39                       &   47.20                      & $-$0.61   \\
+                                             & $^{*}$58538  &   9.78                       &  46.03                      & $-$1.84 \\  
+                                             & 58693            &  9.38                       &  46.54                      &  $-$0.95  \\                    
+    \hline
+\multirow{5}{*}{J1638+2827} & 54553            & 8.74$^{\dagger }$     &  46.17$^{\dagger }$   & $-$0.68$^{\dagger }$  \\
+                                              & 54553            & 8.84                        &   46.19    & $-$0.75  \\
+                                             & 55832           & 9.13$^{\ddagger }$  &    46.72    & $-$0.72$^{\ddagger }$  \\      
+                                             & 55832          & 8.80                         &   45.99    & $-$0.91 \\     
+                                             & 58583           & 9.01                        &    46.52    & $-$0.60   \\
+    \hline
+\multirow{4}{*}{ J2228+2201} & 56189         & 8.73$^{\ddagger }$ & 46.23$^{\ddagger }$  &  $-$1.32$^{\ddagger }$ \\
+                                              &  56189      & 8.70                       & 45.51                        &  $-$1.29 \\
+                                              & 56960         &  9.39                      &  46.54                        & $-$0.95  \\      
+                                              & 58693          &  8.97                      & 46.03                         &  $-$1.05 \\
     \hline
@@
     three quasars.
-    The virial masses are calculated using the measured monochromatic luminosites and FWHM
-    $\dagger$From the \citet{Shen2011} SDSS DR7 Quasar catalog.
-    $\ddagger$From the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
-%    are given in either \citet{Shen2011} or    \citet{Kozlowski2017} for the three CLQs.
-    We scale these values using
-    our measured $\nu L_{\nu}$ continuum luminosity values.  From
-    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
-      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
-      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
-      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
+    The virial masses are calculated using the measured 1450\AA\ monochromatic luminosites and \civ\ FWHM
+    as reported by QSFit, with $^{*}$ designating low SNR line measurements.
+        $\dagger$Values from the \citet{Shen2011} SDSS DR7 Quasar catalog.
+    $\ddagger$Values from the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
+    The Eddington luminosity is 
     $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
@@
 The \civ\ line is one of the strongest collisionally excited lines in
-quasar spectra \citep[e.g.,][]{HamannFerland1999}.
-{\bf Early measurements from e.g., 
-  \citet{PoggePeterson1992} and \citet{Peterson1997book}, 
-  using the well-studied Seyfert galaxy NGC 5548,
-  suggested the location of \civ\ emission was 
-%  probes the photoionisation environment
-  produced by the innermost disk, with the line emission
-  responding to the underlying continuum emission in only
-  a matter of $\sim$ 8 days. 
-as indicated by reverberation mapping time-delay measurements.
-%{\bf (a) I would recommend citing some representative papers to support the statement made in the first sentence of section 4.2 about the lag of the C IV line.
-The most appropriate papers are those dealing with quasars of comparable luminosity (and probably comparable redshift) as the quasars studied here.
-I am somewhat skeptical of this statement because the papers that I consulted.}
-However, more recent measurements from e.g. \citet[][and references therein]{Grier2019},
-suggest that the lag between the \civ\ line and the continuum are of order $>100$ observed-frame days. 
-which would place the \civ emitting region far from the inner accretion disk.
-Importantly, many quasars in the \citet{Grier2019} sample are of
-comparable redshift and luminosity to SDSS J1205+3422, J1638+2827, and J2228+2201.}
+quasar spectra \citep[e.g.,][]{HamannFerland1999}.  {\bf Early
+measurements from e.g., \citet{PoggePeterson1992} and
+\citet{Peterson1997book}, using the well-studied Seyfert galaxy NGC
+5548, suggested the location of \civ\ emission was produced by the
+innermost disk, with the line emission responding to the underlying
+continuum emission in only a matter of $\sim$8 days.  as indicated by
+reverberation mapping time-delay measurements.  However, more recent
+measurements from e.g. \citet[][and references therein]{Grier2019},
+suggest that the lag between the \civ\ line and the continuum are of
+order $>100$ observed-frame days.  which would place the \civ emitting
+region far from the inner accretion disk.  Importantly, many quasars
+in the \citet{Grier2019} sample are of comparable redshift and
+luminosity to SDSS J1205+3422, J1638+2827, and J2228+2201.}
 
@@
 changing-look phenomena. \citet{NodaDone2018} go on to make a
-connection between state changes in Galactic binaries and CLQs.
-%
-In Galactic binaries spectral hardening
-corresponds to the soft-to-hard state transition in black hole
-binaries, which occurs at $L / L_{\rm Edd} \sim 0.02$ (i.e.,
-$\eta_{\rm Edd} \sim -1.7$).  During this state transition, the inner
-disc evaporates into an advection-dominated accretion flow, while the
-overall drop in luminosity appears consistent with the hydrogen
-ionisation disc instability.  \citet{NodaDone2018} predict that
-changing-look AGNs are similarly associated with state transitions at
-$L / L_{\rm Edd}$ of a few percent.
+connection between state changes in Galactic binaries and CLQs.  In
+Galactic binaries spectral hardening corresponds to the soft-to-hard
+state transition in black hole binaries, which occurs at $L / L_{\rm
+Edd} \sim 0.02$ (i.e., $\eta_{\rm Edd} \sim -1.7$).  During this state
+transition, the inner disc evaporates into an advection-dominated
+accretion flow, while the overall drop in luminosity appears
+consistent with the hydrogen ionisation disc instability.
+\citet{NodaDone2018} predict that changing-look AGNs are similarly
+associated with state transitions at $L / L_{\rm Edd}$ of a few
+percent.
 

### 2020-07-10 calculations/BH_VirialMasses.py

@@ -72,7 +72,6 @@ log_LBolerr_J12  = 0.004262343930953705
 log_BHmass_J12   = 9.493502740592843      ##   LOGBH_CIV_VP06 from Shen et al. (2011)
 
 log_LEdd_J12     = np.log10(1.26e38)+log_BHmass_J12    ## ``For pure ionized hydrogen''
-
 log_EddRatio_J12 = -0.3782675304606329
 
 ## Values from QSFit
@@ -97,19 +96,19 @@ log_MBH_VP06_CIV_J12   = a_VP06_CIV  + np.log10(( 10**log_L1350_J12 /1e44)**b_VP
 print('\n\n\n')
 print('  J 1 2 0 5  + 3 4 2 2   ')
 print()
-print('log_MBH_MD04_MgII_J12::  ', log_MBH_MD04_MgII_J12, '  vs. ', LOGBH_MGII_MD04_J12_Shen11 ,' in Shen et al. (2011)')
-print('log_MBH_VO09_MgII_J12::  ', log_MBH_VO09_MgII_J12, '  vs. ', LOGBH_MGII_VO09_J12_Shen11 ,' in Shen et al. (2011)')
-print('log_MBH_S10_MgII_J12::   ', log_MBH_S10_MgII_J12,  '  vs. ', LOGBH_MGII_S10_J12_Shen11  ,' in Shen et al. (2011)')
-print('log_MBH_VP06_CIV_J12::   ', log_MBH_VP06_CIV_J12,  '  vs. ', LOGBH_CIV_VP06_J12_Shen11  ,' in Shen et al. (2011)')
+print('log_MBH_MD04_MgII_J12::  ', log_MBH_MD04_MgII_J12, '  vs. ', LOGBH_MGII_MD04_J12_Shen11 ,' in Shen et al. (2011)', '     ', ((10**log_MBH_MD04_MgII_J12)/(10**LOGBH_MGII_MD04_J12_Shen11)*100), 'per cent')
+print('log_MBH_VO09_MgII_J12::  ', log_MBH_VO09_MgII_J12, '  vs. ', LOGBH_MGII_VO09_J12_Shen11 ,' in Shen et al. (2011)', '     ', ((10**log_MBH_VO09_MgII_J12)/(10**LOGBH_MGII_VO09_J12_Shen11)*100), 'per cent')
[…]

### 2020-07-29 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
getting close to resubmisson

@@
   \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/CIV_CLQs_MBHvsREW_20200519.png}
+  {figures/CIV_CLQs_MBHvsREW_20200710.png}
    \vspace{-12pt}
    \caption[]{
-     Colored density cloud shows virial black hole masses of
+     Virial black hole masses of 
      $\approx$20,000 $z>1.5$ quasars from QSFit catalogue
@@
 
-For Equation~\ref{eqn:virial_masses}., \citet{VestergaardPeterson2006}
+For Equation~\ref{eqn:virial_masses}, \citet{VestergaardPeterson2006}
 measure $\gamma=0.53$ and the offset as $a=0.660$, and these estimates
@@
 
-From the virial mass estimates, all our objects have SMBH masses $M_{\rm BH} \approx 500\times10^{8} M_{\odot}$.
-This is at the upper end of SMBH masses at all epochs, and towards the extreme of the mass distribution for $z\sim2$ quasars.
-Figure~\ref{fig:CIV_MBHvsREW} compares the luminosity \civ\ EW versus the virial SMBH masses for our multi-epoch
-observations to a sample of $\approx$20,000 $z>1.5$ SDSS quasars from
-the QSFit catalog \citep{Calderone2017}.
+From the virial mass estimates, all our objects have SMBH masses
+$M_{\rm BH} \approx 500\times10^{8} M_{\odot}$.  This is at the upper
+end of SMBH masses at all epochs, and towards the extreme of the mass
+distribution for $z\sim2$ quasars.  Figure~\ref{fig:CIV_MBHvsREW}
+compares the luminosity \civ\ EW versus the virial SMBH masses for our
+multi-epoch observations to a sample of $\approx$20,000 $z>1.5$ SDSS
+quasars from the QSFit catalog \citep{Calderone2017}.
 
@@
 \multirow{4}{*}{J1205+3422} & 53498          &   9.49$^{\dagger }$   &   47.22$^{\dagger }$  & $-$0.38$^{\dagger }$   \\
-                                             &  53498        &   9.39                       &   47.20                      & $-$0.61   \\
+                                             &  53498        &   9.39                       &   47.20                      & $-$0.29   \\
                                              & $^{*}$58538  &   9.78                       &  46.03                      & $-$1.84 \\  
@@
 observations, the majority of which are assumed to be in equilibrium.
-{\bf \citet{Grier2019}, }
 
@@
   \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
-  {figures/MJD_vs_Eddington_20191211}
+  {figures/MJD_vs_Eddington_20200710}
   \vspace{-12pt}
@@
 Apart from J1205+3422 on MJD 58538, we see all the \civ\ CLQ epochs
-are above $L / L_{\rm Edd} \sim 5$\%. As we have noted throughout, the
+are above $L / L_{\rm Edd} \sim$5\%. As we have noted throughout, the
 spectrum for J1205+3422 on MJD 58538 has low SNR, so while this object
@@
 conclusively confirm.  Nevertheless, and taking the J1205+3422
-spectrum at face-value, we note that all the \civ\ CLQs are well above
-$\sim1\%$ in Eddington luminosity and thus the suggested ``Low/Hard
+spectrum at face-value, we note that all the \civ\ CLQs are above
+$\sim$1\% in Eddington luminosity and thus the suggested ``Low/Hard
 State'' boundary.
@@
   J1205+3422 on MJD 58538, even in their low state, 
-  the \civ\ CLQs are above $\sim5$\% in Eddington luminosity. 
+  the \civ\ CLQs are above $\sim$5\% in Eddington luminosity. 
 \end{itemize}

### 2020-07-29 calculations/BH_VirialMasses.py

@@ -115,9 +115,9 @@ log_MBH_QSFit_J12_1st  = a_VP06_CIV  + np.log10(( 10**log_L1450_J12_1st /1e44)**
 log_MBH_QSFit_J12_2nd  = a_VP06_CIV  + np.log10(( 10**log_L1450_J12_2nd /1e44)**b_VP06_CIV) + (2*np.log10(FWHM_CIV_J12_2nd))
 log_MBH_QSFit_J12_3rd  = a_VP06_CIV  + np.log10(( 10**log_L1450_J12_3rd /1e44)**b_VP06_CIV) + (2*np.log10(FWHM_CIV_J12_3rd))
 
-print('log_MBH_QSFit_J12 1st epoch (using VP06) ',  log_MBH_QSFit_J12_1st, '   vs.   9.66  currently in Table 3 (',  9.66-log_MBH_QSFit_J12_1st, 'diff)')
-print('log_MBH_QSFit_J12 2nd epoch (using VP06) ',  log_MBH_QSFit_J12_2nd, '   vs   10.08  currently in Table 3 (', 10.08-log_MBH_QSFit_J12_2nd, 'diff)')
-print('log_MBH_QSFit_J12 3rd epoch (using VP06) ',  log_MBH_QSFit_J12_3rd, '   vs.   9.67  currently in Table 3 (',  9.67-log_MBH_QSFit_J12_3rd, 'diff)')
+print('log_MBH_QSFit_J12 1st epoch (using VP06) ',  log_MBH_QSFit_J12_1st, '    vs.   9.66  currently in Table 3 (',  9.66-log_MBH_QSFit_J12_1st, 'diff)')
+print('log_MBH_QSFit_J12 2nd epoch (using VP06) ',  log_MBH_QSFit_J12_2nd, '  vs   10.08  currently in Table 3 (', 10.08-log_MBH_QSFit_J12_2nd, 'diff)')
+print('log_MBH_QSFit_J12 3rd epoch (using VP06) ',  log_MBH_QSFit_J12_3rd, '  vs.   9.67  currently in Table 3 (',  9.67-log_MBH_QSFit_J12_3rd, 'diff)')
 print()
 
 ## Eddington Luminosity. For pure ionized hydrogen, 

### 2020-07-29 plots/hexbin_plots/Baldwin/Baldwin_hexbin.py

@@ -70,7 +70,7 @@ log_L1350_Koz17 = data['L1350']
 ## CONT*__LUM::  1450, 2245, 3000, 4210 or 5100:
 ## AGN continuum (Section 2.2) νLν luminosities and their uncertainties, in units of 1042 erg s−1
 ## 
-path        = '/cos_pc19a_npr/programs/quasars/CIV_CLQs/data/QSO_CIV_catalogs/'
+path        = '../../../../../../data/QSFit/'
 filename    = 'qsfit_1.2.4.fits'
 infile      = path+filename
 sdata_full  = fits.open(infile)
@@ -184,6 +184,8 @@ print("p-value         : %f" % p_value)
 print("Standard errro  : %f" % std_err)
 print()
 
+print('No. of objects in regression: ', len(x))
+print()
 #plt.plot(x, (slope*x + intercept), 'r')
 ## "Fitting", by eye, the the CLQs points
 ## plt.plot(x, ((-.38*x) + (intercept+1.1)), 'r', linestyle=':', zorder=0)

### 2020-07-29 plots/hexbin_plots/MBH_REW/MBH_REW_hexbin.py

@@ -38,7 +38,7 @@ CLQs_MBH        = CLQs['MBH']
 ## CONT*__LUM::  1450, 2245, 3000, 4210 or 5100:
 ## AGN continuum (Section 2.2) νLν luminosities and their uncertainties, in units of 1042 erg s−1
 ## 
-path        = '../../../data/QSO_CIV_catalogs/'
+path        = '../../../../../../data/QSFit/'
 filename    = 'qsfit_1.2.4.fits'
 infile      = path+filename
 sdata_full  = fits.open(infile)
@@ -134,8 +134,9 @@ print("The intercept is: %f" % intercept)
 print("R-squared       : %f" % r_value**2)
 print("p-value         : %f" % p_value)
 print("Standard errro  : %f" % std_err)
-print()
 
+print('No. of objects in regression: ', len(x))
+print()
 #plt.plot(x, (slope*x + intercept), 'r')
 ## for the label...
 slope_str     = str(np.around(slope, decimals=3))
@@ -144,8 +145,8 @@ R_sq          = str(np.around((r_value**2), decimals=3))
         
 
 ## AXES LIMITS 
-xmin =   7.30   ## Log MBH
-xmax =  10.88   ## Log MBH
+xmin =   7.10   ## Log MBH  ##  7.30 for arXiv:1912.05310v1 and other early 2020 versions 
+xmax =  10.22   ## Log MBH  ## 10.88 for arXiv:1912.05310v1 and other early 2020 versions 
 ymin =  0.4
 ymax =  2.95    
 ax.axis([xmin, xmax, ymin, ymax])

### 2020-07-29 tex/MNRAS_submission/rv1/reply2referee.txt
getting close to resubmisson
reply2referee.txt updated

@@
-		We thank the Review and Scientific Editor for their
+		We thank the Reviewer and Scientific Editor for their
 		comments and suggestions.  In particular we thank the
@@
 
-	   We have changed and corrected the Section 2 text.
+	   We have modified the Section 2 text.
 
@@
 
-(i) I recommend expanding on the the sentence "This allowed us to predict the photometric magnitudes at the epochs of the SDSS spectra for each source." I presume that the damped random walk model was used to INTERPOLATE between adjacent points in the light cure.
+(i) I recommend expanding on the the sentence "This allowed us to predict the photometric magnitudes at the epochs of the SDSS spectra for each source." I presume that the damped random walk model was used to INTERPOLATE between adjacent points in the light curve.
 If so, it would be useful to state that explicitly.
@@
 	 As suggested, we have split the light curve and spectral figures up, increased the size of the fonts,
-         and have writen the names of the quasars in the approriate panels.
+         and have written the names of the quasars in the appropriate panels.
 
@@
 	 We have added a paragraph at the end of Section 2.4 detailing how
-	 the uncertainties in the spectral line quantities are determined.
+	 the uncertainties in the spectral line quantities were determined.
 
@@
 
-   	Yes, this is an excellent point. We have updated and corrected the equation
-	and revised the relevant discussion, adding key text and references here.
+   	Yes, this is an excellent point.
+	We have (significantly) updated and corrected the equation and
+	revised the relevant discussion, adding key text and recent 
+	references here.
 

### 2020-07-29 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
almost there...

@@
       probabilities.
-      {\bf The physical mechanism for the generation of the emission lines
-        e.g., full ionization, collisionally excitation (``Collisional Ex.'' in the rable) or recombination are also given in
+      {\bf The physical mechanism for the generation of the emission lines, 
+        e.g., full ionization, collisional excitation or recombination, are given in
       the last column.}
@@
 AGN \citep{PoggePeterson1992}. The ensemble and intrinsic Baldwin effect 
-has been observed in the \civ\ broad absorption line quasar population,
+has been observed in the \civ\ broad absorption line quasar population. 
 However, dramatic changes in the 
@@
 {\bf 
- Most of the strong lines in the rest-frame near-UV spectrum of quasars are
-collisionally excited, including C\,{\sc iii}, C\,{\sc iv} and N\,{\sc
-v}.  The \heii~$\lambda$1640 recombination line is among the exceptions.
-
 Photoionization followed by recombination determines the ionization
-level of carbon, and collisional excitation from the ions ground level 
-determines the line intensity. Other processes do happen,
+level of carbon, and collisional excitation from the ions' ground level 
+determines the line intensity. Other processes do happen 
 (including radiative and three body recombination to the upper levels 
@@
 the production of the 1548.202 and 1550.774~\AA\ \civ\ doublet.
+
+ Most of the strong lines in the rest-frame near-UV spectrum of quasars are
+collisionally excited, including \ciii, C\,{\sc iv} and N\,{\sc
+v}.  The \heii$\lambda$1640 recombination line is among the exceptions.
 }
-%%
 Details of the atomic transitions and physical mechanisms that produce
@@
 {\bf A statistical search using optical light curves to initiate spectroscopic follow-up
-  observations is proving an efficient CLQ finder, and by design
+  observations is proving an efficient CLQ finder, and, by design, 
 our data sources and overall methodology, are in common to the recent
@@
 }
-%
+
 In this section we present the photometric data used to select the
 CLQs and give details of the multiwavelength data where we have it.
-{\bf We use data from the Catalina Real-time Transient Survey, PanSTARRS,
-  the Zwicky Transient Facility, the WISE mission and SDSS.}
-We then give details of the spectroscopic data including emission
-lines measurements.
-
-\subsection{Photometry}
-\subsubsection{Optical Photometry}
 We use optical data from the Catalina Real-time Transient Survey
@@
 \citep[ZTF;][]{Bellm2019_ZTFOverview}. 
-
+We also use data from the {\it WISE} mission and SDSS. 
+We then give details of the spectroscopic data including emission
+lines measurements.
+
+\subsection{Photometry}
+\subsubsection{Optical Photometry}
 The CRTS archive\footnote{http://catalinadata.org} contains the
@@
 Schmidt in Australia. CRTS covers up to $\sim$2500 deg$^2$ per night,
-with four exposures per visit, separated by 10 min. The survey observes
-over 21 nights per lunation. The data are broadly calibrated to
-Johnson $V$ \citep[for details, see][]{Drake2013} and the current CRTS
-data set contains time series for approximately 400 million sources to
-$V \sim 20$ above Declination $\delta > -30$deg from 2003 to 2016 May (observed with CSS
-and MLS) and 100 million sources to $V \sim 19$ in the Southern sky
-from 2005 to 2013 (from SSS). CRTS has been extensively used to study 
-quasar variability \citep[e.g.,][]{Graham2014, Graham2015, Graham2015Nature,
-Graham2017, Graham2020, Stern2017, Stern2018, Ross2018}.
+with four exposures per visit, separated by 10 min. The survey
+observes over 21 nights per lunation. The data are broadly calibrated
+to Johnson $V$ \citep[for details, see][]{Drake2013} and the current
+CRTS data set contains time series for approximately 400 million
+sources to $V \sim 20$ above Declination $\delta > -30$ deg from 2003
+to 2016 May (observed with CSS and MLS) and 100 million sources to $V
+\sim 19$ in the Southern sky from 2005 to 2013 (from SSS). CRTS has
+been extensively used to study quasar variability
+\citep[e.g.,][]{Graham2014, Graham2015, Graham2015Nature, Graham2017,
+Graham2020, Stern2017, Stern2018, Ross2018}.
 
@@
 
-The Zwicky Transient Facility (ZTF; http://ztf.caltech.edu) is a new
-robotic time-domain sky survey capable of visiting the entire visible
-sky north of $-$30 deg declination every night. ZTF observes the sky in
+ZTF\footnote{http://ztf.caltech.edu) is a new} is a robotic 
+time-domain sky survey capable of visiting the entire visible sky
+north of $-$30 deg declination every night. ZTF observes the sky in
 the $g$, $r$, and $i$-bands at different cadences depending on the
@@
 \subsubsection{Mid-Infrared Photometry}
-Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning
+We use mid-infrared data (3.4 and 4.6$\mu$m) from the beginning
 of the {\it WISE} mission \citep[2010 January; ][]{Wright2010} through
@@
 full-sky approximately once every six months (a ``sky pass''), albeit
-it with a gab between 2011 February and 2013 October when the
+it with a gap between 2011 February and 2013 October when the
 satellite was placed in hibernation. Hence, our light curves have a
@@
 we focused on a method and threshold which selects the most promising
-candidates, with no claim of completeness, in a number suitable to be
-inspected visually.}
+candidates, with no claim of completeness, for visual inspection.}
 
@@
 uncertainties at the epochs of the SDSS spectra for each source
-\citep[see][]{Rasmussen_Williams2006}.}
-%%
-Candidate objects with $|\Delta V| > 0.3$ magnitude were then selected
-for visual inspection, {\bf looking for at least a 33\% change in flux
+\citep[see][]{Rasmussen_Williams2006}.} Candidate objects with
+$|\Delta V| > 0.3$ magnitude were then selected for visual
+inspection. {\bf This corresponds to at least a 33\% change in flux
 between the two epochs. Approximately 1\% of quasars should show this
-level of significant variability over the timescales considered
+level of variability over the timescales considered
 \citep{Graham2017}.}
@@
 timescales \citep[e.g.,][]{Barth2011}. However, due to the
-high-redshift of our quasars, \oiii is not available to us to use for
-scaling the spectra.  Instead, we use photometric data from the ZTF
+high-redshift of our quasars, \oiii is not available to us for
+scaling the spectra.  Instead, we use photometric data from ZTF
 since our Palomar and Keck data were all taken after MJD 57500.  This
@@
 spectrophotometric standards observed on the same nights.  {\bf We 
-note the resulting uncertainty in flux calibration is 2-5\%.  This
-uncertainty is not propagated into measurements.}
+  estimate the resulting uncertainty in flux calibration is $\sim$5\%.
+  This uncertainty is not propagated into measurements.}
 
@@
 estimates as well as width, velocity offset and EWs of 20 emission
-lines, including \civ, \ciii, and {Mg\,{\sc ii}}. We process and fit
+lines, including \civ, C\,{\sc iii}], and {Mg\,{\sc ii}}. We process and fit
 all nine spectra (3 quasars with 3 epochs) using the lastest version
@@
 {\bf As described in \citet{Calderone2017}, the uncertainties in the
-measured quantities are determined by two methods; a Fisher matrix
+measured quantities are determined by two methods: a Fisher matrix
 method and a Monte Carlo resampling method.  One might expect
 correlations among model parameters, e.g. emission-line luminosities
-and widths, and thus the Fisher matrix method to underestimates the
-errors.  However, upon investigation, the parameters of the involved
-model components (a power-law for the continuum, and a single
-Lorentzian profile for the emission lines) show negligible
-correlations, hence we use the Fisher matrix method to estimate the
-uncertainties on the model parameters.  Section 2.8.3 and Appendix B4
-of \citet{Calderone2017} gives further details and compares the Fisher
-matrix and Monte Carlo resampling uncertainties and distributions.}
+and widths, potentially causing the Fisher matrix method to
+underestimate the errors.  However, upon investigation, the parameters
+of the involved model components (a power-law for the continuum and a
+single Lorentzian profile for the emission lines) show negligible
+correlations. Therefore, we use the Fisher matrix method to estimate
+the uncertainties on the model parameters.  Section 2.8.3 and Appendix
+B4 of \citet{Calderone2017} gives further details and compares the
+Fisher matrix and Monte Carlo resampling uncertainties and
+distributions.}
 
@@
 curves for three high-redshift CLQ quasars.
-
+%%
 Figure~\ref{fig:civ_clqs_J12_spec} shows the rest-frame spectra for
@@
 \approx 18.0$, blue-sloped quasar with broad Si\,{\sc iv}/O\,{\sc iv},
-\civ, C\,{\sc iii}, and Mg\,{\sc ii}.  \civ\ has a blueshift of
+\civ, C\,{\sc iii}], and Mg\,{\sc ii} emission.  \civ\ has a blueshift of
 $\approx$580$\pm$80 km s$^{-1}$.  By 2019, however, the optical
@@
 observations in 2019.  Note that \civ\ is extremely faint in the 2019
-February spectrum, but that night suffered from poor conditions.
+February spectrum (MJD 58538), but that night suffered from poor conditions.
 
@@
 the initial epoch spectrum, \civ\ is broad and bright, as is C\,{\sc
-iii}. However, $\approx$400 rest-frame days later, the broad \civ\ and
+iii}]. However, $\approx$400 rest-frame days later, the broad \civ\ and
 \ciii\ emission lines have faded, the continuum slope around 1400\AA\
@@
 over the course of 538 days in the rest-frame, the broad emission,
-while still very present, reduces in line flux the UV/blue continuum
+while still very present, reduces in line flux and the UV/blue continuum
 diminishes.  However, the third epoch still corresponds to a source
@@
     The long-dashed red line is the continuum fit, with the solid orange
-    line giving the overall fit. The short-dashed vertical lines gives the
+    line giving the overall fit. The short-dashed vertical lines give the
     rest wavelengths of the \civ\ doublet. }
@@
 extinction values are: $E(B-V) =0.013$ for J1205+3422; $E(B-V) =0.034$
-for J1638+2827 and $E(B-V) =0.041$ for J2228+2201, as taken from the
+for J1638+2827, and $E(B-V) =0.041$ for J2228+2201, as taken from the
 \href{http://ned.ipac.caltech.edu/}{NASA/IPAC Extragalactic Database} 
@@
 All \civ\ lines are fitted with a single, broad, Lorentzian profile.
-This allows us to account for the central peak of the \civ\ line.  No
-additional narrow components are considered for several reasons.
-First, in the epochs of highest brightness, such a ``narrow''
-component would have FWHM $\sim$ 2000-3000~km~s$^{-1}$, i.e. values
-exceeding the usual widths of genuine narrow lines ($\lesssim
-1000$~km~s$^{-1}$). Second, allowing a second component to have such
-large widths would make that component highly degenerate with the
-``broad'' components, causing the latter to have much larger widths,
-$\sim$10,000~km~s$^{-1}$.  Finally, neglecting such a narrow
-component ensures a consistent model across all epochs.
-
-Both the quasar continuum (evaluated at 1450\AA), and the \civ\ line
+This allows us to account for the central peak of the \civ\ line.
+After experimenting, we decided not to include additional narrow
+components for several reasons.  First, in the epochs of highest
+brightness, such a ``narrow'' component would have FWHM $\sim$
+2000-3000~km~s$^{-1}$, i.e. values exceeding the usual widths of
+genuine narrow lines ($\lesssim 1000$~km~s$^{-1}$). Second, allowing a
+second component to have such large widths would make that component
+highly degenerate with the ``broad'' components, causing the latter to
+have much larger widths, $\sim$10,000~km~s$^{-1}$.  Finally,
+neglecting such a narrow component ensures a consistent model across
+all epochs.
+
+Both the quasar continuum (evaluated at 1450\AA) and the \civ\ line
 luminosities follow a similar evolution, with a ratio of $\sim$20-30,
@@
 extends to rest-frame $\lambda$$\sim$1240~\AA\ for the first epoch,
-while it extend to shorter wavelengths for the other epochs
-(respectively 1100~\AA\ and 1010~\AA).  This suggests that the emerging
-component is more prominent at UV wavelengths, and a sufficient
-wavelength coverage is required to detect it. In all cases where the
-\civ\ line profile is reliably constrained, we find that the \civ\
-FWHM is approximately constant with maximum variations $\lesssim$1000 
-km s$^{-1}$, despite significantly larger line luminosity variations.
+while it extends to shorter wavelengths for the other epochs
+(respectively 1100~\AA\ and 1010~\AA).  This is consistent with the
+emerging component being more prominent at UV wavelengths, and
+suggests a sufficient wavelength coverage is required to detect it. In
+all cases where the \civ\ line profile is reliably constrained, we
+find that the \civ\ FWHM is approximately constant with maximal 
+variations $\lesssim$1000 km s$^{-1}$, despite significantly larger
+line luminosity variations.
 
@@
      Virial black hole masses of 
-     $\approx$20,000 $z>1.5$ quasars from QSFit catalogue
+     $\approx$20,000 $z>1.5$ quasars from the QSFit catalogue
      \citep{Calderone2017} compared to their \civ\ rest-frame equivalent
@@
 
- {\bf The \civ\ line is observed to have
-line asymmetry due to outflows \citep[e.g.,][]{Gaskell1982}, very
-strong blueshifts \citep[as mentioned in the Introduction, see
-][]{Richards2011}, and a component of the line profile that does not
-reverberate \citep[][]{Denney2012}.  These issues make the virial BH
-mass estimate uncertain. \citet{Runnoe2013}, 
-\citet{Mejia-Restrepo2016}, \citet{Coatman2017}, 
-\citet{Mejia-Restrepo2018} and \citet{Grier2019} all present studies
-into improving \civ-based single-epoch black hole mass estimates. With
-these cavaets in mind, we acknowledge the BH mass estimates will have
-a large error, likely $\sim$0.5 dex. }
+ {\bf The \civ\ line is observed to have line asymmetry due to
+outflows \citep[e.g.,][]{Gaskell1982}, very strong blueshifts
+\citep[as mentioned in the Introduction; see][]{Richards2011}, and a
+component of the line profile that does not reverberate
+\citep[][]{Denney2012}.  These issues make the \civ\ virial BH mass
+estimate uncertain. \citet{Runnoe2013}, \citet{Mejia-Restrepo2016},
+\citet{Coatman2017}, \citet{Mejia-Restrepo2018} and \citet{Grier2019}
+all present studies into improving \civ-based single-epoch black hole
+mass estimates. With these caveats in mind, we acknowledge the BH mass
+estimates will have a large error, likely $\sim$0.5 dex. }
 
@@
 are widely adopted \citep[e.g.,][]{Shen2011, Chen2019, Yao2019}.
-\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
-but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
-both the DR7 Quasar catalog and DR12 Quasar catalog.
-\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
-$z>1.3$ quasars that show significant lag measurements,
-and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
-their highest-confidence objects. }
+\citet{Kozlowski2017} have similar values to 
+\citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$, but
+note there is a problem with the \civ\ FWHMs for those quasars
+that are reported in both the DR7 Quasar catalog and DR12 Quasar
+catalog.  \citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$
+for their sample of high-redshift ($z>1.3$) quasars that show
+significant lag measurements, and $\gamma=0.52\pm0.04$ for their
+``gold sample'' of 16 of their highest-confidence objects. }
 
@@
 = 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot}) = 9.49 \pm
-0.04$, while for J1638+2827 (MJD 54553) \citet{Shen2011} report 
+0.04$, while for J1638+2827 (MJD 54553), \citet{Shen2011} report 
 $\log (M_{\rm BH, MgII}/M_{\odot}) = 9.03 \pm 0.37$ and
 $\log(M_{\rm BH, CIV}/M_{\odot}) = 8.74 \pm 0.15$.
+These are all within $\approx 0.1 - 0.6$ dex of the values we
+calculated for these epochs.
 
@@
 From the virial mass estimates, all our objects have SMBH masses
-$M_{\rm BH} \approx 500\times10^{8} M_{\odot}$.  This is at the upper
+$M_{\rm BH} \approx 5 - 60 \times10^{8} M_{\odot}$.  This is at the upper
 end of SMBH masses at all epochs, and towards the extreme of the mass
@@
 {\bf With the black hole masses in hand, we can calculate the
-Eddington luminosities of the three quasars. To be consistent with For
-the Bolometric luminosity, $L_{\rm Bol}$, \citet{Shen2011} and
+Eddington luminosities of the three quasars. To be consistent with the 
+bolometric luminosity, $L_{\rm bol}$, reported in \citet{Shen2011} and
 \citet{Kozlowski2017} use the bolometric corrections of BC$_{1350}$ =
-3.81 (from the composite spectral energy distribution (SED) in
-\citet{Richards2006b}) and to be consistent with those measurements we
+3.81 \citep[from the composite spectral energy distribution
+in][]{Richards2006b} and to be consistent with those measurements we
 adopt the same correction.  We report the the bolometric luminosities
-and the Eddington ratios, $\eta=\log(L_{}/L_{Edd})$, in
+and the Eddington ratios, $\eta=\log(L_{}/L_{\rm Edd})$, in
 Table~\ref{tab:Eddington_ratios}.  }
@@
 the FWHM of the \civ\ emission line in the BOSS DR12 quasar sample
-from the catalogue of \citet{Hamann2017}.  Other than the two low
-quality, suspect observations, the multi-epoch observations of our
-high-redshift CLQs are all consistent with the bulk of the BOSS DR12
-sample.
+from the catalogue of \citet{Hamann2017}.  Other than the low quality,
+suspect observation, the multi-epoch observations of our high-redshift
+CLQs are all consistent with the bulk of the BOSS DR12 sample.
 
@@
     The virial masses are calculated using the measured 1450\AA\ monochromatic luminosites and \civ\ FWHM
-    as reported by QSFit, with $^{*}$ designating low SNR line measurements.
-        $\dagger$Values from the \citet{Shen2011} SDSS DR7 Quasar catalog.
-    $\ddagger$Values from the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
+    as reported by QSFit, with $^{*}$ designating the low SNR line measurements.
+    $\dagger$ designates values from the \citet{Shen2011} SDSS DR7 Quasar catalog.
+    $\ddagger$ designates values from the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
     The Eddington luminosity is 
@@
    \vspace{-12pt}
-   \caption[]{\civ\ equivalent width versus underlying continuum luminosity,
-     commonly referred to as the Baldwin plot.  The continuum luminosities
-     are from \citet{Calderone2017}.  The rest-frame EW (REW) measurements
-     are from Table~\ref{tab:QSFit-results}.  Symbols as in
-     Figure~\ref{fig:CIV_MBHvsREW}.
-     % The dashed red line has slope     $\beta=-0.38$.
+   \caption[]{\civ\ (rest-frame) equivalent width versus underlying
+     continuum luminosity, commonly referred to as the Baldwin plot.  The
+     continuum luminosities are from \citet{Calderone2017}.  The rest-frame
+     EW (REW) measurements are from Table~\ref{tab:QSFit-results}.  Symbols
+     as in Figure~\ref{fig:CIV_MBHvsREW}.
    }
@@
 
-We add the measurements from the three \civ\ CLQ at each epoch
+We add the measurements from the three \civ\ CLQs at each epoch
 to Figure~\ref{fig:CIV_Baldwin}. All three quasars at all three epochs
@@
 {\it intrinsic} Baldwin effect \citep[e.g.,][]{Goad2004, Rakic2017}.
-%% Subject to small number statistics, the slope of the intrinsic Baldwin effect for these three high-redshift \civ\ CLQs is somewhat steeper than the population trends, with $\beta \approx-0.38$, shown by the dashed red line in Figure~\ref{fig:CIV_Baldwin}.
 
@@
 \section{Discussion}
-\subsection{Continuum and Line Changes: Comparisons to recent Observations}
+\subsection{Continuum and Line Changes: Comparisons to Recent Observations}
 The top row of Figure~\ref{fig:QSFit-results} demonstrates that both
@@
 \citet{Trakhtenbrot2019} report on the quasar 1ES~1927+654 at
-$z=0.02$, which was initially seen to lack broad emission lines and
-line-of-sight obscuration, i.e, it was a ``type 2'' quasar. This
+$z=0.02$, which was initially seen to lack broad emission lines, i.e, it was a ``type 2'' quasar. This
 object was then seen to spectroscopically change with the appearance
@@
 \citet{Trakhtenbrot2019} find no evidence for broad UV emission lines
-in their source, including neither \civ, \ciii, nor \mgii.  The
+in their source, including neither \civ, C\,{\sc iii}], nor \mgii.  The
 authors attribute the lack of broad UV emission lines to dust within

### 2020-07-30 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
Paper RE-SUBMITTED

@@
 
-\iffalse
-\begin{table}
-  \begin{centering}
-    \begin{tabular}{l r}
-      \hline
-      \hline
-      Transition & Energy Required \\
-                      &   / eV (Ryd)\\
-     \hline
-     \ciii $\rightarrow $ \civ  & 47.89     (3.52) \\
-      \civ   $\rightarrow $ \cv &  64.49   (4.74) \\
-      \cv  $ \rightarrow $ \cvi & 392.09   (28.8) \\
-      \niii $\rightarrow $ \niv  & 47.44  (3.49) \\
-	\niv $\rightarrow $ \nv &  77.47  (5.69)  \\
-      \nv $\rightarrow $ \nvi  &  97.89   (7.19) \\
-            \hline
-      \hline
-    \end{tabular}
-    \caption{Ionisation Energies for Carbon and Nitrogen.
-	These are the energies that are needed to go 
-	from the species on the left and create the ion on the right. }
-  \end{centering}
-\end{table}
-\fi
-
 CLQs to date have primarily been defined according to the
@@
 
-{\bf 
-Photoionization followed by recombination determines the ionization
-level of carbon, and collisional excitation from the ions' ground level 
-determines the line intensity. Other processes do happen 
+{\bf Photoionization followed by recombination determines the
+ionization level of carbon, and collisional excitation from the ions'
+ground level determines the line intensity. Other processes do happen
 (including radiative and three body recombination to the upper levels
@@
 extremely high \citep[e.g., ][and H. Netzer,
-priv. comm.]{Dopita_Sutherland2003book}. The ionization potential of C\,{\sc
-iii} ion is 47.89 eV (3.519 Ry) and thus a photon with this energy
-($k_{\rm B} T \sim 5.6 \times10^{5}$ K) can create the triply ionised,
-\civ\ ion. Once the \civ\ ion is formed, collisional excitation leads to
-the production of the 1548.202 and 1550.774~\AA\ \civ\ doublet.
-
- Most of the strong lines in the rest-frame near-UV spectrum of quasars are
-collisionally excited, including \ciii, C\,{\sc iv} and N\,{\sc
-v}.  The \heii$\lambda$1640 recombination line is among the exceptions.
-}
-Details of the atomic transitions and physical mechanisms that produce
-strong rest-frame UV/optical lines in quasars are given in
-Table~\ref{tab:atomic_lines}.
+priv. comm.]{Dopita_Sutherland2003book}. The ionization potential of
+C\,{\sc iii} ion is 47.89 eV (3.519 Ry) and thus a photon with this
+energy ($k_{\rm B} T \sim 5.6 \times10^{5}$ K) can create the triply
+ionised, \civ\ ion. Once the \civ\ ion is formed, collisional
+excitation leads to the production of the 1548.202 and 1550.774~\AA\
+\civ\ doublet.
+
+Most of the strong lines in the rest-frame near-UV spectrum of quasars
+are collisionally excited, including \ciii, C\,{\sc iv} and N\,{\sc
+v}.  The \heii$\lambda$1640 recombination line is among the
+exceptions.} Details of the atomic transitions and physical mechanisms
+that produce strong rest-frame UV/optical lines in quasars are given
+in Table~\ref{tab:atomic_lines}.
 
@@
 \section{CLQ Selection and Line Measurements}
-{\bf A statistical search using optical light curves to initiate spectroscopic follow-up
-  observations is proving an efficient CLQ finder, and, by design, 
-our data sources and overall methodology, are in common to the recent
-\citet{Ross2018}, \citet{Stern2018} and \citet{Graham2020} papers.
-}
+{\bf A statistical search using optical light curves to initiate
+spectroscopic follow-up observations is proving an efficient CLQ
+finder, and, by design, our data sources and overall methodology, are
+in common to the recent \citet{Ross2018}, \citet{Stern2018} and
+\citet{Graham2020} papers.}
 
@@
 correlations. Therefore, we use the Fisher matrix method to estimate
-the uncertainties on the model parameters.  Section 2.8.3 and Appendix
-B4 of \citet{Calderone2017} gives further details and compares the
-Fisher matrix and Monte Carlo resampling uncertainties and
-distributions.}
+the uncertainties on the model parameters.}
 
@@
 \begin{equation}
-%  \log(M) = \log \left[c\left(  \frac{\nu L_\nu}{10^{42} {\rm erg\ s^{-1}}} \right)^{\gamma}  \left( \frac{\rm FWHM}{10^3 {\rm km\ s^{-1}}} \right)^2 \right] + {\rm constant}.
   \log \left( \frac{M_{\rm BH}}{M_{\odot}} \right)  = a + \log  \left[ \; \left(  \frac{L_{1450}} {10^{44} \; {\rm erg \; s^{-1}}}\right)^{\gamma} \, \right] + 2 \log \left( \frac{\rm {FWHM}}{{\rm km\; s^{-1}}} \right)
@@
 \end{equation}
-where $L_{1450}$ is the monochromatic continuum luminosity at 1450\AA\,
-and FWHM is the full width at half-maximum of the broad \civ\ emission line.
-The coefficient $\gamma$ and offset $a$ are generally deteremined empirically.
+where $L_{1450}$ is the monochromatic continuum luminosity at
+1450\AA\, and FWHM is the full width at half-maximum of the broad
+\civ\ emission line.  The coefficient $\gamma$ and offset $a$ are
+generally deteremined empirically.
 
@@
 {\bf In Table~\ref{tab:Eddington_ratios} we report the \civ\ virial
-  masses calculated using the measured
-luminosites and FWHM from QSFit, equation~\ref{eqn:virial_masses} and the
+masses calculated using the measured luminosites and FWHM from QSFit,
+equation~\ref{eqn:virial_masses} and the
 \citet{VestergaardPeterson2006} calibrations.} \citet{Shen2011} and
@@
 and \civ\ for the SDSS/BOSS observations of our targets. For
-J1205+3422 (and MJD 53498), \citet{Shen2011} report $\log (M_{\rm BH, MgII}/M_{\odot})
-= 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot}) = 9.49 \pm
-0.04$, while for J1638+2827 (MJD 54553), \citet{Shen2011} report 
-$\log (M_{\rm BH, MgII}/M_{\odot}) = 9.03 \pm 0.37$ and
-$\log(M_{\rm BH, CIV}/M_{\odot}) = 8.74 \pm 0.15$.
-These are all within $\approx 0.1 - 0.6$ dex of the values we
-calculated for these epochs.
-
-{\bf The values in Table~\ref{tab:QSFit-results} are
-$\approx$0.3 dex higher than the estimates in
-Table~\ref{tab:Eddington_ratios}, which is to be expected given the
-difference of calibrations factors. In fact, the virial products are
-all remarkably constant and compatible with a single black hole mass
-estimate, within the standard 0.5 dex uncertainty, across the 3 epochs
-for all the quasars.  This fact gives us confidence in the line
-fitting methods.}
+J1205+3422 (and MJD 53498), \citet{Shen2011} report $\log (M_{\rm BH,
+MgII}/M_{\odot}) = 9.55 \pm 0.05$ and $\log(M_{\rm BH, CIV}/M_{\odot})
+= 9.49 \pm 0.04$, while for J1638+2827 (MJD 54553), \citet{Shen2011}
+report $\log (M_{\rm BH, MgII}/M_{\odot}) = 9.03 \pm 0.37$ and
+$\log(M_{\rm BH, CIV}/M_{\odot}) = 8.74 \pm 0.15$.  These are all
+within $\approx 0.1 - 0.6$ dex of the values we calculated for these
+epochs.
+
+{\bf The values in Table~\ref{tab:QSFit-results} are $\approx$0.3 dex
+higher than the estimates in Table~\ref{tab:Eddington_ratios}, which
+is to be expected given the difference of calibrations factors. In
+fact, the virial products are all remarkably constant and compatible
+with a single black hole mass estimate, within the standard 0.5 dex
+uncertainty, across the 3 epochs for all the quasars.}
 
@@
 and the Eddington ratios, $\eta=\log(L_{}/L_{\rm Edd})$, in
-Table~\ref{tab:Eddington_ratios}.  }
+Table~\ref{tab:Eddington_ratios}.}
 
@@
 Using the same dataset as \citet{MacLeod2019}, \citet{Homan2020}
-investigate the responsiveness of the \mgii\ broad emission line
+investigate the responsiveness of the \mgii broad emission line
 doublet in AGN on timescales of several years.  Again focussing on
 quasars that show large changes in their optical light-curves,
-\citet{Homan2020} find that \mgii\ clearly does respond to the
+\citet{Homan2020} find that \mgii clearly does respond to the
 continuum.  However, a key finding from \citet{Homan2020} is that the
@@
 than the continuum, or very little at all.  In the majority (72\%) of
-this highly variable sample, the behaviour of \mgii\ corresponds with
-that of H$\beta$.  However, there are also examples of \mgii\ showing
-variations while but H$\beta$ does not, and vice versa.
+this highly variable sample, the behaviour of \mgii corresponds with
+that of H$\beta$.  However, there are also examples of \mgii showing
+variations while H$\beta$ does not, and vice versa.
 
@@
 The \civ\ line is one of the strongest collisionally excited lines in
-quasar spectra \citep[e.g.,][]{HamannFerland1999}.  {\bf Early
-measurements from e.g., \citet{PoggePeterson1992} and
+quasar spectra \citep[e.g.,][]{HamannFerland1999}.
+%%
+{\bf Early measurements from e.g., \citet{PoggePeterson1992} and
 \citet{Peterson1997book}, using the well-studied Seyfert galaxy NGC
@@
 innermost disk, with the line emission responding to the underlying
-continuum emission in only a matter of $\sim$8 days.  as indicated by
-reverberation mapping time-delay measurements.  However, more recent
-measurements from e.g. \citet[][and references therein]{Grier2019},
-suggest that the lag between the \civ\ line and the continuum are of
-order $>100$ observed-frame days.  which would place the \civ emitting
-region far from the inner accretion disk.  Importantly, many quasars
-in the \citet{Grier2019} sample are of comparable redshift and
-luminosity to SDSS J1205+3422, J1638+2827, and J2228+2201.}
+continuum emission in only a matter of $\sim$8 days, as indicated by
+reverberation mapping time-delay measurements. NGC 5548 has an SMBH
+mass of $\sim$70$\times 10^{6} M_{\odot}$ \citep[][]{Horne2020} and
+the bolometric luminosity of NGC 5548 is between $\sim$0.2-10\% of the
+Eddington luminosity \citep{Ebrero2016, Fausnaugh2016}, giving a
+$\log(L_{\rm bol, NGC5448}$/ erg s$^{-1}$) = $\sim$43.2 - 44.9.
+Thus, the CIV CLQs have a central SMBH mass of $\sim$7-90$\times$ that
+of NGC 5548, and a bolometric luminosity $\sim$3-1400$\times$
+greater. Quasars in the recent \citet{Grier2019} study are of
+comparable redshift and luminosity to J1205+3422, J1638+2827, and
+J2228+2201. \citet{Grier2019} measure the lag between the \civ\ line
+and the continuum to be of order $>100$ observed-frame days.}
 
@@
 observed short timescale continuum variations, we must consider more
-complex models. We note that two of our sources (J1205+3422 and
-J2228+2201) have \civ\ EW and continuum luminosity changes which fall
-comfortably along a line, implying their variation is consistent with
-an intrinsic Baldwin effect (see Figure~\ref{fig:CIV_Baldwin}).
-%%
-{\bf The light-crossing time of the region that produces the \civ\ line is substantial,
-which translates into a delay between the variations of the continuum and
-the \civ\ line, and a smoothing of the light curve of the latter.
-%%
-Thus, if the excitation of the \civ\ line is driven by the changes in the
-continuum, the excited gas cannot reach an equilibrium
-excitation state as quickly as the continuum changes.}
+complex models. We note that one of our sources (J1205+3422) has \civ\
+EW and continuum luminosity changes which fall comfortably along a
+line, implying their variation is consistent with an intrinsic Baldwin
+effect (see Figure~\ref{fig:CIV_Baldwin}).
+{\bf The light-crossing time of the region that produces the \civ\
+line is substantial, which translates into a delay between the
+variations of the continuum and the \civ\ line, and a smoothing of the
+light curve of the latter.  Thus, if the excitation of the \civ\ line
+is driven by the changes in the continuum, the excited gas cannot
+reach an equilibrium excitation state as quickly as the continuum
+changes.}
 This makes the slope of the intrinsic Baldwin effect greater than that
@@
 inhomogeneous disk is responsible for the continuum variations, which
-then drive \civ\ variations, it implies that our objects are simply
-the extreme outliers produced by a process which occasionally, but
-rarely, produces very large hot or cool spots. The frequency of such
+then drive \civ\ variations, it implies that J1205+3422 is simply an
+extreme outlier produced by a process which occasionally, but rarely,
+produces very large hot or cool spots. The frequency of such
 occurrences can be used to constrain the slope and normalization of
@@
 
-The foregoing discussion directly applies to the two objects which
-maintain an intrinsic Baldwin effect relationship between \civ\ EW and
-continuum luminosity. However, J1638+2827 clearly does not maintain
-such a relationship --- indeed, the continuum and \civ\ EW appear
-somewhat correlated, rather than anti-correlated, in this source. This
-implies that the illumination of the \civ\ emitting region by a
-variable ionising continuum and the corresponding change in the
-photoionisation state alone cannot explain the collapse and recovery
-of the line.
+The foregoing discussion directly applies to J1205+3422, which
+maintains a clear intrinsic Baldwin effect relationship between \civ\
+EW and continuum luminosity (J2228+2201 may also be consistent with
+this picture, given the measurement uncertainties).  However,
+J1638+2827 clearly does not maintain such a relationship --- indeed,
+the continuum and \civ\ EW appear somewhat correlated, rather than
+anti-correlated, in this source. This implies that the illumination of
+the \civ\ emitting region by a variable ionising continuum and the
+corresponding change in the photoionisation state alone cannot explain
+the collapse and recovery of the line.
 
@@
 connection between state changes in Galactic binaries and CLQs.  In
-Galactic binaries spectral hardening corresponds to the soft-to-hard
+Galactic binaries, spectral hardening corresponds to the soft-to-hard
 state transition in black hole binaries, which occurs at $L / L_{\rm
@@
 
-Apart from J1205+3422 on MJD 58538, we see all the \civ\ CLQ epochs
-are above $L / L_{\rm Edd} \sim$5\%. As we have noted throughout, the
-spectrum for J1205+3422 on MJD 58538 has low SNR, so while this object
-could well have entered a `low-state', this is difficult to
-conclusively confirm.  Nevertheless, and taking the J1205+3422
-spectrum at face-value, we note that all the \civ\ CLQs are above
-$\sim$1\% in Eddington luminosity and thus the suggested ``Low/Hard
-State'' boundary.
+Apart from J1205+3422 on MJD 58538 (the observation obtained in poor
+conditions) we see all the \civ\ CLQ epochs are above $L / L_{\rm Edd}
+\sim$5\%. The spectrum for J1205+3422 on MJD 58538 has low SNR, so
+while this object could well have entered a `low-state', this is
+difficult to conclusively confirm.  Nevertheless, and taking the
+J1205+3422 spectrum at face-value, we note that all the \civ\ CLQs are
+above $\sim$1\% in Eddington luminosity and thus above the suggested
+``Low/Hard State'' boundary.
 
 While we note there is interest in plotting these accretion rates, and
-motivation from \citet{NodaDone2018} and \citet{Ruan2019a}, we very
-much caution on over-interpretation at this juncture. The point of
-this paper was to report on three very interesting CLQs.  Our object
-definitions are based on empirical, observed properties.  The
-potential for physical connections of accretion physics across the
-large-range of mass-scales is tantalising, but is left to future
-investigations.
+motivation from \citet{NodaDone2018} and \citet{Ruan2019a}, we caution
+against over-interpretation at this juncture. The point of this paper
+was to report on three very interesting CLQs.  Our object definitions
+are based on empirical, observed properties.  The potential for
+physical connections of accretion physics across the large-range of
+mass-scales is tantalising, but is left to future investigations.
 
@@
 There are now more observed examples of dramatic, dynamic changes in
-supermassive black hole systems e.g. CLQs/CSQs than Galactic X-ray
-Binaries.  While the timescales are expected to scale with black hole
-mass, whether the full physical system at large does, including the
-associated atomic physics, remains an open question.
+supermassive black hole systems, e.g. CLQs/CSQs, than there are
+Galactic X-ray Binaries.  While the timescales are expected to scale
+with black hole mass, whether the full physical system at large does,
+including the associated atomic physics, remains an open question.
 
@@
 
-%NPR dedicates this work, and indeed his previous research to his father.
-Dad had a deep love for science, mathematics and questioning the conventional wisdom.
-His support allowed me to become an astrophysicist and to have the adventures and discoveries we did.
-He is sorely missed.
+NPR dedicates this work, and indeed his previous research, to his
+father. Dad had a deep love for science, mathematics and questioning
+the conventional wisdom. His support allowed me to become an
+astrophysicist and to have the adventures and discoveries we did. He
+is sorely missed.
 
